### 2020-06-28 icra-2021.tex
initial commit

%%
%% Conference Paper for ICRA'21, May 16-22, Xi'an, China
%% 
%%

\documentclass[letterpaper,10pt,conference]{ieeeconf}

\IEEEoverridecommandlockouts

\newcommand{\stt}[1]{{\small\tt #1}} %\small\tt too small here
\newcommand{\powprof}{\stt{powprofiler}}
\newcommand{\figpath}{./figures}
\newcommand{\iu}{{i\mkern1mu}}
\let\labelindent\relax

\usepackage[inline]{enumitem}
\usepackage{booktabs}
\usepackage{flushend}
\usepackage{tikz}

%% citation packege
\usepackage{cite}

%% figures package
%\usepackage[pdftex]{graphicx}
%\graphicspath{{figures/}}
%\DeclareGraphicsExtensions{.pdf,.jpeg,.png}

%% math package
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}

%% pseudocode package
%\usepackage{algorithmic}

%% packages for alignment
%\usepackage{array}
%\usepackage{mdwmath}
%\usepackage{mdwtab}
%\usepackage{eqparbox}

%% packages for subfigures (eventually)
\usepackage[tight,footnotesize]{subfigure}
%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
%\usepackage[caption=false,font=footnotesize]{subfig}

%% package for urls
\usepackage{url}

\usepackage{textpos}

%% correct bad hyphenation here
\hyphenation{}

%% references (generates a bib file for bibtex)
\begin{filecontents}{\jobname.bib}
  @inproceedings{seewald2020mechanical,
    title={Mechanical and Computational Energy Estimation of a Fixed-Wing Drone}, 
    author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
    booktitle={Proceedings of the 2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
    pages={to appear},
    year={2020},
    organization={IEEE},
    url={https://adamseew.bitbucket.io/short/mechanical2020}
  }
  @inproceedings{seewald2020towards,
    title={Towards Mission-Aware Energy Assessment for Autonomous Drones}, 
    author={Seewald, Adam and Garcia de Marina, Hector and Hasan, Agus and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
    pages={submitted},
    year={2020}
  }
  @article{seewald2019coarse,
    title={Coarse-Grained Computation-Oriented Energy Modeling for Heterogeneous Parallel Embedded Systems},
    author={Seewald, Adam and Schultz, Ulrik Pagh and Ebeid, Emad and Midtiby, Henrik Skov},
    journal={International Journal of Parallel Programming},
    pages={1--22},
    year={2019},
    publisher={Springer}
  }
  @inproceedings{seewald2019component,
    title={Component-based computation-energy modeling for embedded systems},
    author={Seewald, Adam and Schultz, Ulrik Pagh and Roeder, Julius and Rouxel, Benjamin and Grelck, Clemens},
    booktitle={Proceedings Companion of the 2019 ACM SIGPLAN International Conference on Systems, Programming, Languages, and Applications: Software for Humanity},
    pages={5--6},
    year={2019},
    organization={ACM}
  }
  @inproceedings{boroujerdian2018compute,
    title={Why Compute Matters for UAV Energy Efficiency?},
    author={Boroujerdian, Behzad and Genc, Hasan and Krishnan, Srivatsan and Faust, Aleksandra and Reddi, Vijay Janapa},
    booktitle={2nd International Symposium on Aerial Robotics},
    year={2018}
  }
  @inproceedings{hajjaj2014review,
    title={Review of research in the area of agriculture mobile robots},
    author={Hajjaj, Sami Salama Hussen and Sahari, Khairul Salleh Mohamed},
    booktitle={The 8th International Conference on Robotic, Vision, Signal Processing \& Power Applications},
    pages={107--117},
    year={2014},
    organization={Springer}
  }
  @inproceedings{qingchun2012study,
    title={Study on strawberry robotic harvesting system},
    author={Qingchun, Feng and Wengang, Zheng and Quan, Qiu and Kai, Jiang and Rui, Guo},
    booktitle={2012 IEEE International Conference on Computer Science and Automation Engineering (CSAE)},
    volume={1},
    pages={320--324},
    year={2012},
    organization={IEEE}
  }
  @article{edan2000robotic,
    title={Robotic melon harvesting},
    author={Edan, Yael and Rogozin, Dima and Flash, Tamar and Miles, Gaines E},
    journal={IEEE Transactions on Robotics and Automation},
    volume={16},
    number={6},
    pages={831--835},
    year={2000},
    publisher={IEEE}
  }
  @inproceedings{aljanobi2010setup,
    title={A setup of mobile robotic unit for fruit harvesting},
    author={Aljanobi, AA and Al-Hamed, SA and Al-Suhaibani, SA},
    booktitle={19th International Workshop on Robotics in Alpe-Adria-Danube Region (RAAD 2010)},
    pages={105--108},
    year={2010},
    organization={IEEE}
  }
  @article{de2011design,
    title={Design and control of an apple harvesting robot},
    author={De-An, Zhao and Jidong, Lv and Wei, Ji and Ying, Zhang and Yu, Chen},
    journal={Biosystems engineering},
    volume={110},
    number={2},
    pages={112--122},
    year={2011},
    publisher={Elsevier}
  }
  @article{dong2011development,
    title={Development of a row guidance system for an autonomous robot for white asparagus harvesting},
    author={Dong, Fuhong and Heinemann, Wolfgang and Kasper, Roland},
    journal={Computers and Electronics in Agriculture},
    volume={79},
    number={2},
    pages={216--225},
    year={2011},
    publisher={Elsevier}
  }
  @inproceedings{li2008analysis,
    title={Analysis of workspace and kinematics for a tomato harvesting robot},
    author={Li, Zhiguo and Liu, Jizhan and Li, Pingping and Li, Wei},
    booktitle={2008 International Conference on Intelligent Computation Technology and Automation (ICICTA)},
    volume={1},
    pages={823--827},
    year={2008},
    organization={IEEE}
  }
  @article{puri2017agriculture,
    title={Agriculture drones: A modern breakthrough in precision agriculture},
    author={Puri, Vikram and Nayyar, Anand and Raja, Linesh},
    journal={Journal of Statistics and Management Systems},
    volume={20},
    number={4},
    pages={507--518},
    year={2017},
    publisher={Taylor \& Francis}
  }
  @inproceedings{mei2005case,
    title={A case study of mobile robot's energy consumption and conservation techniques},
    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Y Charlie and Lee, CS George},
    booktitle={ICAR'05. Proceedings., 12th International Conference on Advanced Robotics, 2005.},
    pages={492--497},
    year={2005},
    organization={IEEE}
  }
  @inproceedings{mei2004energy,
    title={Energy-efficient motion planning for mobile robots},
    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Y Charlie and Lee, CS George},
    booktitle={IEEE International Conference on Robotics and Automation, 2004. Proceedings. ICRA'04. 2004},
    volume={5},
    pages={4344--4349},
    year={2004},
    organization={IEEE}
  }
  @article{mei2006deployment,
    title={Deployment of mobile robots with energy and timing constraints},
    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Yu Charlie and Lee, CS George},
    journal={IEEE Transactions on robotics},
    volume={22},
    number={3},
    pages={507--522},
    year={2006},
    publisher={IEEE}
  }
  @inproceedings{uragun2011energy,
    title={Energy efficiency for unmanned aerial vehicles},
    author={Uragun, Balemir},
    booktitle={2011 10th International Conference on Machine Learning and Applications and Workshops},
    volume={2},
    pages={316--320},
    year={2011},
    organization={IEEE}
  }
  @inproceedings{kreciglowa2017energy,
    title={Energy efficiency of trajectory generation methods for stop-and-go aerial robot navigation},
    author={Kreciglowa, Nadia and Karydis, Konstantinos and Kumar, Vijay},
    booktitle={2017 International Conference on Unmanned Aircraft Systems (ICUAS)},
    pages={656--662},
    year={2017},
    organization={IEEE}
  }
  @article{kanellakis2017survey,
    title={Survey on computer vision for UAVs: Current developments and trends},
    author={Kanellakis, Christoforos and Nikolakopoulos, George},
    journal={Journal of Intelligent \& Robotic Systems},
    volume={87},
    number={1},
    pages={141--168},
    year={2017},
    publisher={Springer}
  }
  @article{sadrpour2013mission,
    title={Mission Energy Prediction for Unmanned Ground Vehicles Using Real-time Measurements and Prior Knowledge},
    author={Sadrpour, Amir and Jin, Jionghua and Ulsoy, A Galip},
    journal={Journal of Field Robotics},
    volume={30},
    number={3},
    pages={399--414},
    year={2013},
    publisher={Wiley Online Library}
  }
  @inproceedings{sadrpour2013experimental,
    title={Experimental validation of mission energy prediction model for unmanned ground vehicles},
    author={Sadrpour, Amir and Jin, Judy and Ulsoy, A Galip},
    booktitle={2013 American Control Conference},
    pages={5960--5965},
    year={2013},
    organization={IEEE}
  }
  @article{berenz2012autonomous,
    title={Autonomous battery management for mobile robots based on risk and gain assessment},
    author={Berenz, Vincent and Tanaka, Fumihide and Suzuki, Kenji},
    journal={Artificial Intelligence Review},
    volume={37},
    number={3},
    pages={217--237},
    year={2012},
    publisher={Springer}
  }
  @inproceedings{kim2005energy,
    title={Energy-saving 3-step velocity control algorithm for battery-powered wheeled mobile robots},
    author={Kim, Chong Hui and Kim, Byung Kook},
    booktitle={Proceedings of the 2005 IEEE international conference on robotics and automation},
    pages={2375--2380},
    year={2005},
    organization={IEEE}
  }
  @inproceedings{kim2008minimum,
    title={Minimum-energy translational trajectory planning for battery-powered three-wheeled omni-directional mobile robots},
    author={Kim, Hongjun and Kim, Byung-Kook},
    booktitle={2008 10th International Conference on Control, Automation, Robotics and Vision},
    pages={1730--1735},
    year={2008},
    organization={IEEE}
  }
  @article{morales2009power,
    title={Power consumption modeling of skid-steer tracked mobile robots on rigid terrain},
    author={Morales, Jesus and Martinez, Jorge L and Mandow, Anthony and Garc{\'\i}a-Cerezo, Alfonso J and Pedraza, Salvador},
    journal={IEEE Transactions on Robotics},
    volume={25},
    number={5},
    pages={1098--1108},
    year={2009},
    publisher={IEEE}
  }
  @book{wahab2015energy,
    title={Energy modeling of differential drive robots},
    author={Wahab, Mudasser and Rios-Gutierrez, Fernando and El Shahat, Adel},
    year={2015},
    publisher={IEEE}
  }
  @article{rao2003battery,
    title={Battery modeling for energy aware system design},
    author={Rao, Ravishankar and Vrudhula, Sarma and Rakhmatov, Daler},
    journal={Computer},
    volume={36},
    number={12},
    pages={77--87},
    year={2003},
    publisher={IEEE}
  }
  @inproceedings{chiasson2003estimating,
    title={Estimating the state of charge of a battery},
    author={Chiasson, John and Vairamohan, Baskar},
    booktitle={Proceedings of the 2003 American Control Conference, 2003.},
    volume={4},
    pages={2863--2868},
    year={2003},
    organization={IEEE}
  }
  @inproceedings{pang2001battery,
    title={Battery state-of-charge estimation},
    author={Pang, Shuo and Farrell, Jay and Du, Jie and Barth, Matthew},
    booktitle={Proceedings of the 2001 American control conference.(Cat. No. 01CH37148)},
    volume={2},
    pages={1644--1649},
    year={2001},
    organization={IEEE}
  }
  @article{partovibakhsh2014adaptive,
    title={An adaptive unscented Kalman filtering approach for online estimation of model parameters and state-of-charge of lithium-ion batteries for autonomous mobile robots},
    author={Partovibakhsh, Maral and Liu, Guangjun},
    journal={IEEE Transactions on Control Systems Technology},
    volume={23},
    number={1},
    pages={357--363},
    year={2014},
    publisher={IEEE}
  }
  @inproceedings{zhang2009battery,
    title={Battery state estimation using unscented kalman filter},
    author={Zhang, Fei and Liu, Guangjun and Fang, Lijin},
    booktitle={2009 IEEE International Conference on Robotics and Automation},
    pages={1863--1868},
    year={2009},
    organization={IEEE}
  }
  @inproceedings{hasan2018exogenous,
    title={Exogenous kalman filter for state-of-charge estimation in lithium-ion batteries},
    author={Hasan, Agus and Skriver, Martin and Johansen, Tor Arne},
    booktitle={2018 IEEE Conference on Control Technology and Applications (CCTA)},
    pages={1403--1408},
    year={2018},
    organization={IEEE}
  }
  @inproceedings{nardi2015introducing,
    title={Introducing SLAMBench, a performance and accuracy benchmarking methodology for SLAM},
    author={Nardi, Luigi and Bodin, Bruno and Zia, M Zeeshan and Mawer, John and Nisbet, Andy and Kelly, Paul HJ and Davison, Andrew J and Luj{\'a}n, Mikel and O'Boyle, Michael FP and Riley, Graham and others},
    booktitle={2015 IEEE International Conference on Robotics and Automation (ICRA)},
    pages={5783--5790},
    year={2015},
    organization={IEEE}
  }
  @online{px4,
    author={PX4},
    title={{PX4} open-source autopilot},
    url={https://px4.io/},
    urldate={2016-09-01}
  }
  @online{papa,
    author={Paparazzi},
    title={{UAV} open-source project},
    url={http://wiki.paparazziuav.org/},
    urldate={2016-09-01}
  }
  @online{nano,
    author={NVIDIA},
    title={{NVIDIA Jetson Nano} developer kit},
    url={https://developer.nvidia.com/embedded/jetson-nano-developer-kit},
    urldate={2020-02-02}
  }
  @online{opterra,
    author={Horizon Hobby},
    title={{Opterra} 2m Wing BNF Basic},
    url={https://www.horizonhobby.com/opterra-2m-wing-bnf-basic-p-efl11150},
    urldate={2020-02-02}
  }
  @online{meier2013mavlink,
    title={Mavlink: Micro air vehicle communication protocol},
    author={Meier, Lorenz and Camacho, J and Godbolt, B and Goppert, J and Heng, L and Lizarraga, M and others},
    url={https://mavlink.io/},
    urldate={2020-02-02}
  }
  https://mavlink.io/
  @article{ullah2018pednet,
    title={Pednet: A spatio-temporal deep convolutional neural network for pedestrian segmentation},
    author={Ullah, Mohib and Mohammed, Ahmed and Alaya Cheikh, Faouzi},
    journal={Journal of Imaging},
    volume={4},
    number={9},
    pages={107},
    year={2018},
    publisher={Multidisciplinary Digital Publishing Institute}
  }
  @inproceedings{sandler2018mobilenetv2,
    title={Mobilenetv2: Inverted residuals and linear bottlenecks},
    author={Sandler, Mark and Howard, Andrew and Zhu, Menglong and Zhmoginov, Andrey and Chen, Liang-Chieh},
    booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
    pages={4510--4520},
    year={2018}
  }
  @inproceedings{quigley2009ros,
    title={ROS: an open-source Robot Operating System},
    author={Quigley, Morgan and Conley, Ken and Gerkey, Brian and Faust, Josh and Foote, Tully and Leibs, Jeremy and Wheeler, Rob and Ng, Andrew Y},
    booktitle={ICRA workshop on open source software},
    volume={3},
    number={3.2},
    pages={5},
    year={2009}
  }
  @book{stengel1994optimal,
    title={Optimal control and estimation},
    author={Stengel, Robert F},
    year={1994},
    publisher={Courier Corporation}
  }
  @book{simon2006optimal,
    title={Optimal state estimation: Kalman, H infinity, and nonlinear approaches},
    author={Simon, Dan},
    year={2006},
    publisher={John Wiley \& Sons}
  }
  @inproceedings{de2017guidance,
    title={Guidance algorithm for smooth trajectory tracking of a fixed wing UAV flying in wind flows},
    author={De Marina, Hector Garcia and Kapitanyuk, Yuri A and Bronz, Murat and Hattenberger, Gautier and Cao, Ming},
    booktitle={2017 IEEE international conference on robotics and automation (ICRA)},
    pages={5740--5745},
    year={2017},
    organization={IEEE}
  }

\end{filecontents}

\title{\LARGE \bf
***
}

%% author names and affiliations
\author{
  Adam Seewald$^{1}$, Hector Garcia de Marina, and Ulrik Pagh Schultz
  \thanks{$^{1}$Corresponding author; email: {\tt\small ads@mmmi.sdu.dk}}
  \thanks{Adam Seewald, Ulrik Pagh Schultz are with the SDU UAS Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense, Denmark.}
  \thanks{Hector Garcia de Marina is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
}

\begin{document}

%% make the title area
\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}

  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract\\
  abstract
\end{abstract}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

*

%%%%%%%%%%%%%%%%%%%%%%
\section{State of the Art}
\label{sec:related}

*

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
\label{sec:estimation}

To evaluate the energy consumption of different flight phases, we use a third-order Fourier series, as the energy evolution in a flying scenario often presents periodic patterns~\cite{seewald2020towards}. More specifically, in a survey application, the fixed-wing drone performs ellipsoidal flying trajectories at a fixed height while steering over one of the unconstricted axes. The trajectory is periodic in the sense that the system uncertainty factors, which might impact the predicted energy, such as wind conditions, temperature, and other atmospheric interferences, are alike to those observed performing a similar trajectory under the same conditions.

The third-order Fourier series represents the power in function of time and can be expressed in the following form:
\begin{equation}\label{eq:1}
  f(t)=\sum_{n=0}^{3}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
\end{equation}
with $\xi$ the characteristic time, $a_n, b_n$ for $n\in\{0,\dotsc,3\}$ the Fourier series coefficient, and:
\begin{equation}
  \xi,a_n,b_n,t,f(t)\in\mathbb{R}.
\end{equation}

\subsection{Problem Definition}

For the purpose of optimal analysis, the non-linear model expressed by Equation~(\ref{eq:1}) can be expressed using an equivalent linear time-varying state-space model, expressed in the following form:
\begin{equation}\begin{split}\label{eq:3}
  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t),\\
  y(t)&=C\mathbf{q}(t)+v(t),
\end{split}\end{equation}
where $y$ is the energy evolution of the controlled system, $w$ the process noise (i.e., atmospheric interferences), $v$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently. Moreover:
\begin{equation}\begin{split}
  \mathbf{q}(t)&=\begin{bmatrix}
    a_0(t) & b_0(t) & \hspace{1.1ex}\cdots\hspace{1.1ex} & a_3(t) & b_3(t) & \hspace{.6ex}\vline & \xi
  \end{bmatrix}^T,\\
  A_i&=\begin{bmatrix}0 & i \\ -i^2 & 0\end{bmatrix}\hspace{-.5ex},\,
  A=\left[\begin{array}{cccccc}
    \mathbf{0} & \mathbf{0} & \mathbf{0} & \mathbf{0} & \vline & \mathbf{0} \\
    \mathbf{0} & A_1 & \mathbf{0} & \mathbf{0} & \vline & \mathbf{0} \\
    \mathbf{0} & \mathbf{0} & A_2 & \mathbf{0} & \vline & \mathbf{0} \\
    \mathbf{0} & \mathbf{0} & \mathbf{0} & A_3 & \vline & \mathbf{0} \\ \hline
    \mathbf{0} & \mathbf{0} & \mathbf{0} & \mathbf{0} & \vline & 0
  \end{array}\right]\hspace{-.6ex},
  \\
  {}&\hspace{14.6ex}C=\begin{bmatrix}
    1 & 0 & \cdots & 1 & 0 & \vline & 0
  \end{bmatrix},\\
\end{split}\end{equation}
with the state $\mathbf{q}$ being the evolution of the Fourier series coefficient in time, $A, C$ the state transition matrix, and the output matrix respectively. Furthermore, the last row and column of the matrix $A$ contain zero row vectors and columns vectors respectively, and:
\begin{equation}\begin{split}
  A&\in\mathbb{R}^{9\times 9},\\
  \mathbf{q}(t), C&\in\mathbb{R}^9.
\end{split}\end{equation}
Motivated by the fact that the system of interest is sampled at discrete times and for the sake of simplicity, we consider the discretized version of the Equation~(\ref{eq:3}) by employing the following expression:
\begin{equation}\label{eq:6}\begin{split}
  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k,\\
  y_k&=C\mathbf{q}_k+v_k.
\end{split}\end{equation}

As the system was observed to behave stochastically, with the process and measurement noise evolving in a normal distribution, a Kalman filter~\cite{stengel1994optimal, simon2006optimal} is employed to predict the state $\hat{\mathbf{q}}$. Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eq:6}) due to the presence of uncertainty.

The prediction is done using the following expression:
\begin{subequations}\label{eq:7}\begin{align}
  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:7a}\\
  P_{k+1}^-&=AP_kA^T+Q,\label{eq:7b}
\end{align}\end{subequations}
where $\hat{\mathbf{q}}_k^-, \hat{\mathbf{q}}_k$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k$ the error covariance matrix (i.e., the variance of the estimate before measurement).

The estimation of the state and the update of the predicted output is done using the following expression:
\begin{subequations}\label{eq:8}\begin{align}
  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:8b}\\
  P_{k+1}&=(I-G_{k+1}C)P_{k+1}^-,\\
  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:8d}
\end{align}
\end{subequations}
where $K_k$ is the gain of the Kalman filter, and $I$ the identity matrix. The noise covariance matrixes $Q,R$ indicates the process noise and sensor noise covariance respectively, and:
\begin{equation}\label{eq:9}\begin{split}
  k&\in\mathbb{Z}^{\geq 0},\\
  Q,P_k^-,P_k&\in\mathbb{R}^{9\times 9},\\
  K_k,\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k&\in\mathbb{R}^9,\\
  w_k,v_k,R,\hat{y}_k&\in\mathbb{R}.\\
\end{split}\end{equation}

Equations~(\ref{eq:7}--\ref{eq:9}) converges to the predicted energy evolution as follows. An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data. It is worth considering that an appropriate guess of these parameters allows the system to converge to the desired energy evolution in a shorter amount of time. The tuning parameters $Q,R$ are also derived from the collected data and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.

At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:7a})~and~(\ref{eq:7b}) respectively. The value of $\hat{\mathbf{q}}_1$ is then used in Equation~(\ref{eq:8b}) to estimate the current state along with the measurment from the sensor $y_0$, where the sensor noise covariance matrix $R$ accounts for the amount of uncertainity in the measurement. The estimated ouput $\hat{y}_0$ is then obtained from Equation~(\ref{eq:8d}). The algorithm is iterative. At time $k=1$ the values $\hat{\mathbf{q}}=1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.

Two different components of the overall energy consumption are being modeled in our analysis, an approach that has been extensively reviewed in our previous work~\cite{seewald2019coarse, seewald2019component, seewald2020mechanical, seewald2020towards}. A mechanical energy model accounts for the energy by reason of the physical system being moved in space, whereas a computational energy model accounts for the computations. The main goal is to derive a control action $\mathbf{u}$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\kappa(\hat{\mathbf{q}})$. This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) derived later in this chapter.

\noindent---

\subsection{Equations of Motion}

For ease of reference, given a point in a 2D Euclidean coordinate system $\mathbf{p}=\begin{bmatrix}x&y\end{bmatrix}^T$, with respect to some inertial frame $\mathcal{O}_N$, we consider a simple elliptical explicit trajectory expression $\varphi$ defined by the equation:
\begin{equation}\label{eq:10}
  \varphi(\mathbf{p})=\frac{x-x_e}{r_m^2}+\frac{y-y_e}{r_M^2}-1,
\end{equation}
where $x_e, y_e$ are the coordinates of the center of the ellipse with respect to $\mathcal{O}_N$, and $r_m, r_M$ are the minor and major radius respectively. The equation of motion is expressed using a non-holonomic model presented in~\cite{de2017guidance}:
\begin{equation}\label{eq:11}\begin{split}
  \dot{\mathbf{p}}(t)&=sm\left( \psi(t) \right)+h,\\
  \dot{\psi}(t)&=u_m(t),
\end{split}
\end{equation}
where $s$ depicts the airspeed, $m(\psi(t))=\begin{bmatrix}\cos{\psi}&\sin{\psi}\end{bmatrix}^T$ the attitude yaw angle, $h$ a constant which represents the wind, and:
\begin{equation}\begin{split}
  \psi(t)&\in(-\pi,\pi],\\
  r_m,r_M,x_e,y_e,\mathbf{p}(t),m(\psi(t))&\in\mathbb{R}^2,\\
  u_m(t),h&\in\mathbb{R}.
\end{split}
\end{equation}

Given a desired trajectory expressed in~(\ref{eq:10}), an arbitrary point in space $\mathbf{p}$, and it's ground velocity $\dot{\mathbf{p}}$, considering the equation of motion in~(\ref{eq:11}), the control action is likewise derived in~\cite{de2017guidance}:
\begin{equation}\begin{split}
  u_m(t)&=u(\mathbf{p},\dot{\mathbf{p}},\psi)\\
        &=\frac{\lVert \dot{\mathbf{p}}\rVert}{s\cos{\beta}}\left(\dot{\chi}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TR\hat{\dot{\mathbf{p}}}\right),
\end{split}
\end{equation}
where $\hat{\dot{\mathbf{p}}}=\dot{\mathbf{p}}/\lVert\dot{\mathbf{p}}\rVert$,

\subsection{Computational Energy Model}

The energy due to the computational units of the system is obtained with \powprof{}, an open-source modeling tool that measures empirically a number of software configuration and build an energy model accordingly~\cite{seewald2019coarse}. A multivariate linear interpolation is derived automatically by \powprof{}, while being accessed online at the hand of a lookup table in the optimal control algorithm presented later. The robotics system in such an analysis composes a number of computationally expensive ROS nodes, allowing to vary the amount of computations changing node-specific quality of service (QoS) values. For the sake of simplicity and to allow an easy integration in an existing ROS system, the QoS values are utilizing ROS middleware, meaning that defined ROS parameters are intended specifically as QoS ranges.

Let us define $\mathrm{QoS}_i\in\mathbb{Z}^{\geq 0},\,\forall i\in\{0,\dots,r\}$ the $i$-th QoS range, $g_c(\mathrm{QoS}_i)\in\mathbb{R}^{\geq 0}$ the instantaneous energy value obtained interogating \powprof{} online, and $\mathbf{u}_c$ the set of $r$ QoS values the system is composed of. The computational energy component can be hence described using the following expression:
\begin{equation}
  E_c(\mathbf{u}_c)=\sum_{i=0}^{r}{g_c(\mathrm{QoS}_i)},
\end{equation}
TODO

%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
\label{sec:experimental}

*

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Work}
\label{sec:conclusion}

*

%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgment}

This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).

\bibliographystyle{IEEEtran}
\bibliography{\jobname} 
\vspace{0.1ex}

\end{document}

### 2020-07-09 icra-2021.tex
updates

@@
 \usepackage{amssymb}
+\usepackage{arydshln}
 
@@
 
+% what I want to do with words.
+% diggested version of the technical details
+% strory goes to the introduction
+% depends
+% big picture in the introduction to agree what specifically I am trying to do right now
 *
@@
 *
+% equation number just just for illustrate the reader just to introduce and support - this is an offline method
+% but we need it in real time while we are flying
+% we write number one as number 4
+% one of the things is to figure out what are the states
+% t
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
+% once the introduction 
 \section{Model}
@@
 
-To evaluate the energy consumption of different flight phases, we use a third-order Fourier series, as the energy evolution in a flying scenario often presents periodic patterns~\cite{seewald2020towards}.
-More specifically, in a survey application, the fixed-wing drone performs ellipsoidal flying trajectories at a fixed height while steering over one of the unconstricted axes.
-The trajectory is periodic in the sense that the system uncertainty factors, which might impact the predicted energy, such as wind conditions, temperature, and other atmospheric interferences, are alike to those observed performing a similar trajectory under the same conditions.
+The model presented in this section deals with the motion and the energy using two distinct systems, subject to the same process noise $w$ (i.e., the atmospheric interferences such as wind).
 
-The third-order Fourier series represents the power in function of time and can be expressed in the following form:
-\begin{equation}\label{eq:1}
-  f(t)=\sum_{n=0}^{3}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
+The motion defines a trajectory and a position $\mathbf{p}$; the trajectory is expressed through explicit trajectory equation $\varphi$, while the position determines a vehicle frame $\mathcal{O}_V$ in the 2D Euler space relative to an inertial frame $\mathcal{O}_W$.
+For the sake of simplicity, it is assumed that the $z$-axis is constrained to a specific altitude $h$, with the system being free to evolve in the $x,y$-axes (i.e., the drone is flying, performing a mission, at a given height).
+A motion guidance action is derived using vector field design, enabling the convergence to the desired trajectory anywhere in $\mathcal{O}_W$.
+
+The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis and its state-space representation.
+This component is decomposed in the energy needed for the actuation (i.e., the mechanical energy), and the computations (i.e., the computational energy).
+A control action, which varies quality of service (QoS) levels of the software being executed, is derived for this purpose.
+The main goal is to tune the explicit energy equation allowing to maximize the computational and mechanical outcome of the mission while trying to minimize the eventuality of battery discharge.
+
+\subsection{Motion and Guidance Model}
+The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described by the following non-holonomic model:
+\begin{equation}\label{eqq:1}\begin{cases}
+  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+w(t),\\
+  \dot{\psi}(t)&=u(t),
+\end{cases}
 \end{equation}
-with $\xi$ the characteristic time, $a_n, b_n$ for $n\in\{0,\dotsc,3\}$ the Fourier series coefficient, and:
+where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which express the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
+
+Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be hence defined:
+\begin{equation}\label{eqq:2}
+  \mathcal{P}:=\{\mathbf{p}:\|\varphi(\mathbf{p})\|<c+\varepsilon\},
+\end{equation}
+as the set of points that follows the trajectory $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}^{\geq 0}$.
+
+Given a set of discrete values $c_i$, the space relative to $\mathcal{O}_W$ can be covered by all the trajectories $\varphi(\mathbf{p})=c_i$ within specific boundaries $c_m\leq c_i\leq c_M$.
+
+The concept of a trajectory is used later to design a controller that selects $c_i$ value with the highest energy value under the energy budget constraints defined in the next subsection.
+Here we design a guidance action $u$ that allows following such trajectory.
+The guidance is derived using the vector field approach presented in~\cite{de2017guidance}.
+The algorithm heads to $\mathcal{P}$ using a vector field based on the minimization of the norm in Equation~(\ref{eqq:2}).
+
+Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is hence defined as a desired velocity vector
+\begin{equation}\label{eqq:3}
+  \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
+    0&1\\-1&0
+  \end{bmatrix},
+\end{equation}
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., it's vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}^{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
+
+The direction the velocity vector $\dot{\mathbf{p}}$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interferences.
+
+Let us further define $\hat{\mathbf{p}}:=\mathbf{p}/\|\mathbf{p}\|$, the desired course heading rate $\dot{\chi_d}$ is computed by sensing the position $\mathbf{p}$, the ground velocity $\dot{\mathbf{p}}$, and is expressed
+\begin{equation}\label{eqq:4}\begin{split}
+  &\dot{\chi}(\mathbf{p},\dot{\mathbf{p}})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
+  &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^T\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,
+\end{split}
+\end{equation} 
+where $H(\cdot)$ is defined as the Hessian operator, with the physical meaning being that the curvature of the desired trajectory has to be known in order to be tracked.
+
+Under the assumption of the airspeed $s=\|w(t)\|$ for $t>0$ (i.e., the constant airspeed being greater than the norm of the wind), the guidance action defines how fast the drone converges to the desired trajectory and can be expressed
 \begin{equation}
-  \xi,a_n,b_n,t,f(t)\in\mathbb{R}.
+  u(\dot{\mathbf{p}},\mathbf{p},\psi)=\frac{\|\mathbf{p}\|}{s\cos{\beta}}\left( \dot{\mathbf{\chi}}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
 \end{equation} 
+where $k_d\in\mathbb{R}^{\geq 0}$ is the gain which adjusts the speed of convergence of the drone to the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the slideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
 
-\subsection{Problem Definition}
+---
 
-For the purpose of optimal analysis, the non-linear model expressed by Equation~(\ref{eq:1}) can be expressed using an equivalent linear time-varying state-space model, expressed in the following form:
-\begin{equation}\begin{split}\label{eq:3}
+\subsection{Energy Model}
+
+We consider a Fourier series of an arbitrary order $r$ to evaluate the energy spent performing a given motion and software configuration
+\begin{equation}\label{eqq:6}
+  f(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
+\end{equation}
+where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.
+The Fourier analysis allows to account for the periodicity of the mission, with a trajectory $\mathcal{P}$ being reitared over time.
+
+The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent linear time-varying state-space model, expressed in the following form:
+\begin{equation}\label{eqq:7}\begin{cases}
   \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t),\\
   y(t)&=C\mathbf{q}(t)+v(t),
+\end{cases}\end{equation}
+where $y(t)\in\mathbb{R}^{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise from the system in Equation~(\ref{eqq:1}), $v(t)\in\mathbb{R}^{\geq 0}$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
+The state $\mathbf{q}$ respresents the evolution of the Fourier series coefficients in time, which can be expressed along the state transition matrix, and the output matrix as follows
+\begin{equation}\begin{split}
+  \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
+    a_0 & \vline & a_1 & b_1 & \cdots & a_r & b_r
+  \end{array}\right],\\
+  A&=\left[\begin{array}{ccccc}
+    1          & \vline & \mathbf{0} & \cdots & \mathbf{0} \\\hline
+    \mathbf{0} & \vline & A_1        & \cdots & \mathbf{0} \\
+    \vdots     & \vline & \vdots     & \vdots & \vdots     \\
+    \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
+  \end{array}\right],\,A_n=\begin{bmatrix}0 & n \\ -n^2 & 0\end{bmatrix},\\
+  C&=\left[\begin{array}{ccccccc}
+    1 & \vline & 1 & 0 & \cdots & 1 & 0
+  \end{array}\right],
 \end{split}\end{equation}
-where $y$ is the energy evolution of the controlled system, $w$ the process noise (i.e., atmospheric interferences), $v$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
-Moreover:
-\begin{equation}\begin{split}
-  \mathbf{q}(t)&=\begin{bmatrix}
-    a_0(t) & b_0(t) & \hspace{1.1ex}\cdots\hspace{1.1ex} & a_3(t) & b_3(t) & \hspace{.6ex}\vline & \xi
-  \end{bmatrix}^T,\\
-  A_i&=\begin{bmatrix}0 & i \\ -i^2 & 0\end{bmatrix}\hspace{-.5ex},\,
-  A=\left[\begin{array}{cccccc}
-    \mathbf{0} & \mathbf{0} & \mathbf{0} & \mathbf{0} & \vline & \mathbf{0} \\
-    \mathbf{0} & A_1 & \mathbf{0} & \mathbf{0} & \vline & \mathbf{0} \\
-    \mathbf{0} & \mathbf{0} & A_2 & \mathbf{0} & \vline & \mathbf{0} \\
-    \mathbf{0} & \mathbf{0} & \mathbf{0} & A_3 & \vline & \mathbf{0} \\ \hline
-    \mathbf{0} & \mathbf{0} & \mathbf{0} & \mathbf{0} & \vline & 0
-  \end{array}\right]\hspace{-.6ex},
-  \\
-  {}&\hspace{14.6ex}C=\begin{bmatrix}
-    1 & 0 & \cdots & 1 & 0 & \vline & 0
-  \end{bmatrix},\\
-\end{split}\end{equation}
-with the state $\mathbf{q}$ being the evolution of the Fourier series coefficient in time, $A, C$ the state transition matrix, and the output matrix respectively.
-Furthermore, the last row and column of the matrix $A$ contain zero row vectors and columns vectors respectively, and:
-\begin{equation}\begin{split}
-  A&\in\mathbb{R}^{9\times 9},\\
-  \mathbf{q}(t), C&\in\mathbb{R}^9.
-\end{split}\end{equation}
-Motivated by the fact that the system of interest is sampled at discrete times and for the sake of simplicity, we consider the discretized version of the Equation~(\ref{eq:3}) by employing the following expression:
-\begin{equation}\label{eq:6}\begin{split}
+where $\mathbf{q}\in\mathbb{R}^l$ given $l:=2r+1$, $A\in\mathbb{R}^{l\times l}$ is the state transmission matrix, $C\in\mathbb{R}^l$ is the output matrix respectively.
+Furthermore, the first row and column of the matrix $A$ contain a zeros row vectors and columns vectors respectively.
+
+Motivated by the fact that the system of interest is sampled at discrete time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1}~and~\ref{eqq:7}) by employing the following expression:
+\begin{subequations}\begin{align}
+  &\begin{cases}
+  \mathbf{p}_{k+1}&=s\Psi(\psi_k)+w_k,\\
+  \psi_{k+1}&=u_k,
+  \end{cases}\tag{9b}\label{eqq:9b}\\
+  &\begin{cases}
   \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k,\\
   y_k&=C\mathbf{q}_k+v_k.
-\end{split}\end{equation}
+  \end{cases}
+\end{align}\end{subequations}
 
 As the system was observed to behave stochastically, with the process and measurement noise evolving in a normal distribution, a Kalman filter~\cite{stengel1994optimal, simon2006optimal} is employed to predict the state $\hat{\mathbf{q}}$.
-Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eq:6}) due to the presence of uncertainty.
+Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
 
 The prediction is done using the following expression:
-\begin{subequations}\label{eq:7}\begin{align}
-  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:7a}\\
-  P_{k+1}^-&=AP_kA^T+Q,\label{eq:7b}
+\begin{subequations}\label{eqq:10}\begin{align}
+  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eqq:10a}\\
+  P_{k+1}^-&=AP_kA^T+Q,\label{eqq:10b}
 \end{align}\end{subequations}
-where $\hat{\mathbf{q}}_k^-, \hat{\mathbf{q}}_k$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k$ the error covariance matrix (i.e., the variance of the estimate before measurement).
+where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^l$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{l\times l}$ the error covariance matrix (i.e., the variance of the estimate before measurement).
 
 The estimation of the state and the update of the predicted output is done using the following expression:
-\begin{subequations}\label{eq:8}\begin{align}
+\begin{subequations}\label{eqq:11}\begin{align}
   K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:8b}\\
+  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
   P_{k+1}&=(I-G_{k+1}C)P_{k+1}^-,\\
-  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:8d}
+  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
 \end{align}
 \end{subequations}
-where $K_k$ is the gain of the Kalman filter, and $I$ the identity matrix. The noise covariance matrixes $Q,R$ indicates the process noise and sensor noise covariance respectively, and:
-\begin{equation}\label{eq:9}\begin{split}
-  k&\in\mathbb{Z}^{\geq 0},\\
-  Q,P_k^-,P_k&\in\mathbb{R}^{9\times 9},\\
-  K_k,\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k&\in\mathbb{R}^9,\\
-  w_k,v_k,R,\hat{y}_k&\in\mathbb{R}.\\
-\end{split}\end{equation}
+where $K_k\in\mathbb{R}^l$ is the gain of the Kalman filter, and $I$ the identity matrix.
+The noise covariance matrixes $Q\in\mathbb{R}^{l\times l},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}$ is the estimated energy.
 
-Equations~(\ref{eq:7}--\ref{eq:9}) converges to the predicted energy evolution as follows.
+Equation~(\ref{eqq:10}) converges to the predicted energy evolution as follows.
 An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
@@
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:7a})~and~(\ref{eq:7b}) respectively.
-The value of $\hat{\mathbf{q}}_1$ is then used in Equation~(\ref{eq:8b}) to estimate the current state along with the measurment from the sensor $y_0$, where the sensor noise covariance matrix $R$ accounts for the amount of uncertainity in the measurement.
-The estimated ouput $\hat{y}_0$ is then obtained from Equation~(\ref{eq:8d}).
+At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
+The value of $\hat{\mathbf{q}}_1$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the measurment from the sensor $y_0$, where the sensor noise covariance matrix $R$ accounts for the amount of uncertainity in the measurement.
+The estimated ouput $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
 The algorithm is iterative.
@@
 The main goal is to derive a control action $\mathbf{u}$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\kappa(\hat{\mathbf{q}})$.
-This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) derived later in this chapter.
+This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) derived later in this section.
 
-\noindent---
+---
 
-\subsection{Equations of Motion}
-
-For ease of reference, given a point in a 2D Euclidean coordinate system $\mathbf{p}=\begin{bmatrix}x&y\end{bmatrix}^T$, with respect to some inertial frame $\mathcal{O}_N$, we consider a simple elliptical explicit trajectory expression $\varphi$ defined by the equation:
-\begin{equation}\label{eq:10}
-  \varphi(\mathbf{p})=\frac{x-x_e}{r_m^2}+\frac{y-y_e}{r_M^2}-1,
-\end{equation}
-where $x_e, y_e$ are the coordinates of the center of the ellipse with respect to $\mathcal{O}_N$, and $r_m, r_M$ are the minor and major radius respectively.
-The equation of motion is expressed using a non-holonomic model presented in~\cite{de2017guidance}:
-\begin{equation}\label{eq:11}\begin{split}
-  \dot{\mathbf{p}}(t)&=sm\left( \psi(t) \right)+h,\\
-  \dot{\psi}(t)&=u_m(t),
-\end{split}
-\end{equation}
-where $s$ depicts the airspeed, $m(\psi(t))=\begin{bmatrix}\cos{\psi}&\sin{\psi}\end{bmatrix}^T$ the attitude yaw angle, $h$ a constant which represents the wind, and:
-\begin{equation}\begin{split}
-  \psi(t)&\in(-\pi,\pi],\\
-  r_m,r_M,x_e,y_e,\mathbf{p}(t),m(\psi(t))&\in\mathbb{R}^2,\\
-  u_m(t),h&\in\mathbb{R}.
-\end{split}
-\end{equation}
-
-Given a desired trajectory expressed in~(\ref{eq:10}), an arbitrary point in space $\mathbf{p}$, and it's ground velocity $\dot{\mathbf{p}}$, considering the equation of motion in~(\ref{eq:11}), the control action is likewise derived in~\cite{de2017guidance}:
-\begin{equation}\begin{split}
-  u_m(t)&=u(\mathbf{p},\dot{\mathbf{p}},\psi)\\
-        &=\frac{\lVert \dot{\mathbf{p}}\rVert}{s\cos{\beta}}\left(\dot{\chi}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TR\hat{\dot{\mathbf{p}}}\right),
-\end{split}
-\end{equation}
-where $\hat{\dot{\mathbf{p}}}=\dot{\mathbf{p}}/\lVert\dot{\mathbf{p}}\rVert$,
-
-\subsection{Computational Energy Model}
+\subsection{Computational Model}
 

### 2020-07-12 icra-2021.tex
finished model, but final proof read needed (still)

@@
 \usepackage{arydshln}
+\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
 
@@
 \end{equation}
-as the set of points that follows the trajectory $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}^{\geq 0}$.
+as the set of points that follows the trajectory $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
 
-Given a set of discrete values $c_i$, the space relative to $\mathcal{O}_W$ can be covered by all the trajectories $\varphi(\mathbf{p})=c_i$ within specific boundaries $c_m\leq c_i\leq c_M$.
+Given a set of discrete values $c$, the space relative to $\mathcal{O}_W$ can be covered by all the trajectories $\mathcal{P}$ within specific boundaries $\underline{c}\leq c\leq \overline{c}$, where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
 
-The concept of a trajectory is used later to design a controller that selects $c_i$ value with the highest energy value under the energy budget constraints defined in the next subsection.
+The concept of a trajectory is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints defined in the next subsection.
 Here we design a guidance action $u$ that allows following such trajectory.
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., it's vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}^{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., it's vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
 
@@
 Under the assumption of the airspeed $s=\|w(t)\|$ for $t>0$ (i.e., the constant airspeed being greater than the norm of the wind), the guidance action defines how fast the drone converges to the desired trajectory and can be expressed
-\begin{equation}
+\begin{equation}\label{eqq:5}
   u(\dot{\mathbf{p}},\mathbf{p},\psi)=\frac{\|\mathbf{p}\|}{s\cos{\beta}}\left( \dot{\mathbf{\chi}}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
 \end{equation} 
-where $k_d\in\mathbb{R}^{\geq 0}$ is the gain which adjusts the speed of convergence of the drone to the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the slideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
+where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of convergence of the drone to the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the slideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
 
@@
 
-We consider a Fourier series of an arbitrary order $r$ to evaluate the energy spent performing a given motion and software configuration
+We consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$ to evaluate the energy spent performing a given motion and software configuration
 \begin{equation}\label{eqq:6}
@@
 \end{cases}\end{equation}
-where $y(t)\in\mathbb{R}^{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise from the system in Equation~(\ref{eqq:1}), $v(t)\in\mathbb{R}^{\geq 0}$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise from the system in Equation~(\ref{eqq:1}), $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
 The state $\mathbf{q}$ respresents the evolution of the Fourier series coefficients in time, which can be expressed along the state transition matrix, and the output matrix as follows
@@
     \mathbf{0} & \vline & A_1        & \cdots & \mathbf{0} \\
-    \vdots     & \vline & \vdots     & \vdots & \vdots     \\
+    \vdots     & \vline & \vdots     & \ddots & \vdots     \\
     \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
@@
 \end{split}\end{equation}
-where $\mathbf{q}\in\mathbb{R}^l$ given $l:=2r+1$, $A\in\mathbb{R}^{l\times l}$ is the state transmission matrix, $C\in\mathbb{R}^l$ is the output matrix respectively.
+where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, $C\in\mathbb{R}^j$ is the output matrix respectively.
 Furthermore, the first row and column of the matrix $A$ contain a zeros row vectors and columns vectors respectively.
 
-Motivated by the fact that the system of interest is sampled at discrete time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1}~and~\ref{eqq:7}) by employing the following expression:
+Motivated by the fact that the system of interest is sampled at discrete time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1}~and~\ref{eqq:7}) by employing the following expression
 \begin{subequations}\begin{align}
@@
 \end{align}\end{subequations}
-where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^l$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{l\times l}$ the error covariance matrix (i.e., the variance of the estimate before measurement).
+where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate before measurement).
 
@@
 \end{subequations}
-where $K_k\in\mathbb{R}^l$ is the gain of the Kalman filter, and $I$ the identity matrix.
-The noise covariance matrixes $Q\in\mathbb{R}^{l\times l},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}$ is the estimated energy.
+where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
+The noise covariance matrixes $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
 
@@
 
----
-
 \subsection{Computational Model}
 
-The energy due to the computational units of the system is obtained with \powprof{}, an open-source modeling tool that measures empirically a number of software configuration and build an energy model accordingly~\cite{seewald2019coarse}.
-A multivariate linear interpolation is derived automatically by \powprof{}, while being accessed online at the hand of a lookup table in the optimal control algorithm presented later.
-The robotics system in such an analysis composes a number of computationally expensive ROS nodes, allowing to vary the amount of computations changing node-specific quality of service (QoS) values.
-For the sake of simplicity and to allow an easy integration in an existing ROS system, the QoS values are utilizing ROS middleware, meaning that defined ROS parameters are intended specifically as QoS ranges.
+A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically a number of software configuration and build an energy model accordingly~\cite{seewald2019coarse}.
+The tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
+An existing ROS system composes a number of computationally expensive ROS nodes, allowing to vary the amount of computations changing node-specific quality of service (QoS) values.
+The tool builds the energy model using a file specification which specifies per each ROS node a QoS range.
 
-Let us define $\mathrm{QoS}_i\in\mathbb{Z}^{\geq 0},\,\forall i\in\{0,\dots,r\}$ the $i$-th QoS range, $g_c(\mathrm{QoS}_i)\in\mathbb{R}^{\geq 0}$ the instantaneous energy value obtained interogating \powprof{} online, and $\mathbf{u}_c$ the set of $r$ QoS values the system is composed of.
-The computational energy component can be hence described using the following expression:
+Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action as
+\begin{equation}\label{eqq:12}
+  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma\}\right\},
+\end{equation}
+where $\text{QoS}_n(t):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time $t$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of at time $k$.
+Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interogating \powprof{}.
+The computational energy component can be hence described
+\begin{equation}\begin{split}
+  g(\mathcal{C}_{k})&:=\{g\left(0,\text{QoS}_0(k)\right),\dots,g\left(\sigma,\text{QoS}_\sigma(k)\right)\},\\
+  y_c(t)&=\sum_{x\in g\left(\mathcal{C}_{\ceil{t}}\right)}{x},
+\end{split}\end{equation}
+where $\ceil{\cdot}$ is the ceiling function that returns the least integer greater than or equal to the argument.
+
+The QoS parameters $\mathcal{C}_k$ can be subject to different constraints at different states.
+Physically, this means that the drone can perform the ROS nodes within different QoS ranges while flying different phases of a mission
+\begin{equation}\label{eqq:14}
+  \underline{\text{QoS}}_n(k)\leq \text{QoS}_n(k)\leq \overline{\text{QoS}}_n(k),\,\forall n\in\{0,\cdots,\sigma\},
+\end{equation}
+where the values $\underline{\text{QoS}}_n(k),\overline{\text{QoS}}_n(k)$ are retrived from the mission specification.
+
+The control action is constructed in two steps.
+Equation~(\ref{eqq:12}) defines the control due to the computational model.
+The control due to the energy model, which describes the energy of the mechanical elements of the drone $\mathcal{M}$, is derived in the following subsection.
+
+\subsection{Control Action}
+
+Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathbf{u}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circonference, and semi-major and minor axis of an ellipse.
+The set of these parameters can be expressed
+\begin{equation}\label{eqq:14}
+  \mathcal{M}_k:=\{\mathbf{u}_k : \varphi_k(\mathbf{p}_k^0,\mathbf{u}_k)=c_k\},
+\end{equation}
+where $c$ is being defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ is the optimal point which lets the trajectory explicit function $\varphi_k$ converge to the value $c$.
+
+The explicit trajectory equation $\varphi_k$ can be different for different states $k$, meaning the vector field and guidance action, from Equations~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
+Alike Equation~(\ref{eqq:14}), the parameters $\mathbf{u}_k=\{u_{k,1},\dots,u_{k,\rho_k}\}$ at time $k$ are constrained
 \begin{equation}
-  E_c(\mathbf{u}_c)=\sum_{i=0}^{r}{g_c(\mathrm{QoS}_i)},
+  \underline{u}_{k,n}\leq u_{k,n}\leq \overline{u}_{k,n}\,\forall n\in\{0,\cdots,\rho_k\},
 \end{equation}
-TODO
+where the values $\underline{u}_{k,n},\overline{u}_{k,n}$ are also retrived from the mission specifcation.
+
+It is worth considering that the number of parameters at state $k$ is also a parameter of the state.
+This is for the sake of generality, as the mission specification might contain different explicit equations for different states.
+Meaning that the drone might follow in an ellipse function thorought the mission and heading a linear function while landing.
+
+The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}) respectively, are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
+\begin{equation}\begin{split}
+  \mathbf{u}_k&=\left[\begin{array}{cc}
+    g\left(\mathcal{C}_k\right) & \mathcal{M}_k
+  \end{array}\right]^T,\\
+  B&=\left[\begin{array}{ccccccc}
+    1 & \cdots & 1 & \vline & 0 & \cdots & 0\\\hline
+    0 & \cdots & 0 & \vline & 0 & \cdots & 0\\
+    \vdots & \ddots & \vdots & \vline & \vdots & \ddots & \vdots\\
+    0 & \cdots & 0 & \vline & 0 & \cdots & 0
+  \end{array}\right],
+\end{split}
+\end{equation}
+where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:9b}).
+The first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$.
+This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}).
+The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which hovewever will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
 

### 2020-07-12 icra-2021.tex
minor fix

@@
 \end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:9b}).
-The first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$.
+where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equations~(\ref{eqq:7})~and~(\ref{eqq:9b}).
+Moreover, the first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$.
 This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}).

### 2020-07-13 icra-2021.tex
proofreading done

@@
     url={https://adamseew.bitbucket.io/short/mechanical2020}
-  }
-  @inproceedings{seewald2020towards,
-    title={Towards Mission-Aware Energy Assessment for Autonomous Drones}, 
-    author={Seewald, Adam and Garcia de Marina, Hector and Hasan, Agus and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    pages={submitted},
-    year={2020}
   }
@@
   }
-
+  @book{rawlings2017model,
+    title={Model predictive control: theory, computation, and design},
+    author={Rawlings, James Blake and Mayne, David Q and Diehl, Moritz},
+    volume={2},
+    year={2017},
+    publisher={Nob Hill Publishing Madison, WI}
+  }
 \end{filecontents}
@@
 \author{
-  Adam Seewald$^{1}$, Hector Garcia de Marina, and Ulrik Pagh Schultz
-  \thanks{$^{1}$Corresponding author; email: {\tt\small ads@mmmi.sdu.dk}}
+  Adam Seewald$^{*}$, Hector Garcia de Marina, and Ulrik Pagh Schultz
+  \thanks{$^{*}$Corresponding author; email: {\tt\small ads@mmmi.sdu.dk}}
   \thanks{Adam Seewald, Ulrik Pagh Schultz are with the SDU UAS Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense, Denmark.}
@@
 
-The model presented in this section deals with the motion and the energy using two distinct systems, subject to the same process noise $w$ (i.e., the atmospheric interferences such as wind).
+The model presented in this section deals with the motion and the energy using two different systems, subject to the same process noise $w$ (i.e., the atmospheric interference such as wind).
 
@@
 
-The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis and its state-space representation.
-This component is decomposed in the energy needed for the actuation (i.e., the mechanical energy), and the computations (i.e., the computational energy).
+The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis in its state-space representation.
+This component is decomposed in the energy needed for the actuation (i.e., the mechanical energy), and the computations (i.e., the computational energy), an approach that has been extensively reviewed in our previous work~\cite{seewald2019coarse, seewald2019component, seewald2020mechanical}.
 A control action, which varies quality of service (QoS) levels of the software being executed, is derived for this purpose.
@@
 \subsection{Motion and Guidance Model}
-The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described by the following non-holonomic model:
+The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described by the following non-holonomic model
 \begin{equation}\label{eqq:1}\begin{cases}
-  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+w(t),\\
-  \dot{\psi}(t)&=u(t),
-\end{cases}
+  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+w(t)\\
+  \dot{\psi}(t)&=u(t)
+\end{cases},
 \end{equation}
-where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which express the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
+where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which indicates the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
 
-Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be hence defined:
+Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be hence defined
 \begin{equation}\label{eqq:2}
@@
 \end{equation}
-as the set of points that follows the trajectory $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
+as the set of points that follows the explicit trajectory equation $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
 
@@
 
-Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is hence defined as a desired velocity vector
+Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is hence defined as the desired velocity vector
 \begin{equation}\label{eqq:3}
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., it's vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
 
-The direction the velocity vector $\dot{\mathbf{p}}$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interferences.
+The direction the velocity vector $\dot{\mathbf{p}}$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interference.
 
@@
 \end{equation} 
-where $H(\cdot)$ is defined as the Hessian operator, with the physical meaning being that the curvature of the desired trajectory has to be known in order to be tracked.
+where $H(\cdot)$ is defined as the Hessian operator; the physical meaning is that the curvature of the desired trajectory has to be known in order to be tracked.
 
-Under the assumption of the airspeed $s=\|w(t)\|$ for $t>0$ (i.e., the constant airspeed being greater than the norm of the wind), the guidance action defines how fast the drone converges to the desired trajectory and can be expressed
+Under the assumption of the airspeed $s>\|w(t)\|$ for $t>0$ (i.e., the constant airspeed is greater than the norm of the wind), the guidance action defines how fast the drone converges to the desired trajectory and can be expressed
 \begin{equation}\label{eqq:5}
@@
 \end{equation} 
-where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of convergence of the drone to the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the slideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
+where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
 
@@
 
-We consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$ to evaluate the energy spent performing a given motion and software configuration
+To evaluate the energy spent performing a given motion and software configuration we consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$
 \begin{equation}\label{eqq:6}
@@
 where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.
-The Fourier analysis allows to account for the periodicity of the mission, with a trajectory $\mathcal{P}$ being reitared over time.
+The Fourier analysis allows accounting for the periodicity of the mission, with a trajectory $\mathcal{P}$ being reiterated over time.
 
-The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent linear time-varying state-space model, expressed in the following form:
+The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent time-varying state-space model in the following form
 \begin{equation}\label{eqq:7}\begin{cases}
-  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t),\\
-  y(t)&=C\mathbf{q}(t)+v(t),
-\end{cases}\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise from the system in Equation~(\ref{eqq:1}), $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise, and the control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
-The state $\mathbf{q}$ respresents the evolution of the Fourier series coefficients in time, which can be expressed along the state transition matrix, and the output matrix as follows
+  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t)\\
+  y(t)&=C\mathbf{q}(t)+v(t)
+\end{cases},\end{equation}
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise.
+The control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
+The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix as follows
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
-where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, $C\in\mathbb{R}^j$ is the output matrix respectively.
-Furthermore, the first row and column of the matrix $A$ contain a zeros row vectors and columns vectors respectively.
+where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
+Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and columns vectors respectively.
 
-Motivated by the fact that the system of interest is sampled at discrete time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1}~and~\ref{eqq:7}) by employing the following expression
+Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1})~and~(\ref{eqq:7}) by employing the following expression
 \begin{subequations}\begin{align}
-  &\begin{cases}
-  \mathbf{p}_{k+1}&=s\Psi(\psi_k)+w_k,\\
-  \psi_{k+1}&=u_k,
-  \end{cases}\tag{9b}\label{eqq:9b}\\
-  &\begin{cases}
-  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k,\\
-  y_k&=C\mathbf{q}_k+v_k.
-  \end{cases}
+  &\begin{cases}\label{eqq:9a}
+  \mathbf{p}_{k+1}&=s\Psi(\psi_k)+w_k\\
+  \psi_{k+1}&=u_k
+  \end{cases},\\
+  &\begin{cases}\label{eqq:9b}
+  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k\\
+  y_k&=C\mathbf{q}_k+v_k
+  \end{cases}.
 \end{align}\end{subequations}
@@
 As the system was observed to behave stochastically, with the process and measurement noise evolving in a normal distribution, a Kalman filter~\cite{stengel1994optimal, simon2006optimal} is employed to predict the state $\hat{\mathbf{q}}$.
-Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
+Such a state, along with the predicted output $\hat{y}$ differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
 
-The prediction is done using the following expression:
+The prediction is done using the following expression
 \begin{subequations}\label{eqq:10}\begin{align}
@@
 
-The estimation of the state and the update of the predicted output is done using the following expression:
+The estimation of the state and the update of the predicted output is done using the following expression
 \begin{subequations}\label{eqq:11}\begin{align}
@@
 where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
-The noise covariance matrixes $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
+The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
 
@@
 At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
-The value of $\hat{\mathbf{q}}_1$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the measurment from the sensor $y_0$, where the sensor noise covariance matrix $R$ accounts for the amount of uncertainity in the measurement.
-The estimated ouput $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
+The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (the energy sensor of the flight controller is employed), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
+The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
 The algorithm is iterative.
-At time $k=1$ the values $\hat{\mathbf{q}}=1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
+At time $k=1$ the values $\hat{\mathbf{q}}_1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
 
-Two different components of the overall energy consumption are being modeled in our analysis, an approach that has been extensively reviewed in our previous work~\cite{seewald2019coarse, seewald2019component, seewald2020mechanical, seewald2020towards}.
-A mechanical energy model accounts for the energy by reason of the physical system being moved in space, whereas a computational energy model accounts for the computations.
-The main goal is to derive a control action $\mathbf{u}$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\kappa(\hat{\mathbf{q}})$.
-This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) derived later in this section.
+In the light of Equations~(\ref{eqq:9a})~and~(\ref{eqq:9b}), the main goal stated earlier in this section can be updated.
+We aim to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$~\cite{rawlings2017model}.
+This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) algorithm derived in the next section.
+Before, we need to define a generic control action $\mathbf{u}$.
 
@@
 
-A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically a number of software configuration and build an energy model accordingly~\cite{seewald2019coarse}.
-The tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
-An existing ROS system composes a number of computationally expensive ROS nodes, allowing to vary the amount of computations changing node-specific quality of service (QoS) values.
-The tool builds the energy model using a file specification which specifies per each ROS node a QoS range.
+A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically software configurations and builds an energy model accordingly~\cite{seewald2019coarse}.
+Specifically, the tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
+The system is modeled as follows.
+An existing ROS system composes several computationally expensive ROS nodes, allowing to vary the number of computations changing the node-specific quality of service (QoS) values via ROS parameters.
+The tool builds the energy model using mission specification which, besides other mission parameters, specifies per each ROS node a QoS range.
 
@@
 where $\text{QoS}_n(t):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time $t$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of at time $k$.
-Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interogating \powprof{}.
+Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
 The computational energy component can be hence described
@@
 \end{equation}
-where the values $\underline{\text{QoS}}_n(k),\overline{\text{QoS}}_n(k)$ are retrived from the mission specification.
+where the values $\underline{\text{QoS}}_n(k),\overline{\text{QoS}}_n(k)$ are retrieved from the mission specification.
 
@@
 
-Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathbf{u}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circonference, and semi-major and minor axis of an ellipse.
+Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathbf{u}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
 The set of these parameters can be expressed
@@
 \end{equation}
-where $c$ is being defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ is the optimal point which lets the trajectory explicit function $\varphi_k$ converge to the value $c$.
+where $c$ is defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ are the optimal points which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
 
-The explicit trajectory equation $\varphi_k$ can be different for different states $k$, meaning the vector field and guidance action, from Equations~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
+The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equations~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
 Alike Equation~(\ref{eqq:14}), the parameters $\mathbf{u}_k=\{u_{k,1},\dots,u_{k,\rho_k}\}$ at time $k$ are constrained
@@
 \end{equation}
-where the values $\underline{u}_{k,n},\overline{u}_{k,n}$ are also retrived from the mission specifcation.
+where the values $\underline{u}_{k,n},\overline{u}_{k,n}$ are also retrieved from the mission specification.
 
@@
 This is for the sake of generality, as the mission specification might contain different explicit equations for different states.
-Meaning that the drone might follow in an ellipse function thorought the mission and heading a linear function while landing.
+Meaning that the drone might follow an ellipse function throughout the mission and heading a linear function while landing.
 
@@
 This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}).
-The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which hovewever will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
+The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
 

### 2020-07-14 icra-2021.tex
just got rid of the annoying delimiter
a more thorough proofreading

@@
 \subsection{Motion and Guidance Model}
-The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described by the following non-holonomic model
+The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described using the following non-holonomic model
 \begin{equation}\label{eqq:1}\begin{cases}
@@
 \end{equation}
-where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which indicates the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
+where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
 
-Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be hence defined
+Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be defined
 \begin{equation}\label{eqq:2}
@@
 \end{equation}
-as the set of points that follows the explicit trajectory equation $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
+as the set of points that follows an explicit trajectory equation $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
 
-Given a set of discrete values $c$, the space relative to $\mathcal{O}_W$ can be covered by all the trajectories $\mathcal{P}$ within specific boundaries $\underline{c}\leq c\leq \overline{c}$, where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
+Given a set of discrete values $c$, $\mathcal{O}_W$ can be covered by all the trajectories $\mathcal{P}$ within specific boundaries $\underline{c}\leq c\leq \overline{c}$, where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
 
-The concept of a trajectory is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints defined in the next subsection.
+The concept of a trajectory is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints.
 Here we design a guidance action $u$ that allows following such trajectory.
-The guidance is derived using the vector field approach presented in~\cite{de2017guidance}.
-The algorithm heads to $\mathcal{P}$ using a vector field based on the minimization of the norm in Equation~(\ref{eqq:2}).
+The guidance is derived using the vector field approach also presented in~\cite{de2017guidance}.
+The algorithm heads to $\mathcal{P}$ by the means of minimizing the norm in Equation~(\ref{eqq:2}).
 
-Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is hence defined as the desired velocity vector
+Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is defined as the desired velocity vector
 \begin{equation}\label{eqq:3}
@@
 
-Under the assumption of the airspeed $s>\|w(t)\|$ for $t>0$ (i.e., the constant airspeed is greater than the norm of the wind), the guidance action defines how fast the drone converges to the desired trajectory and can be expressed
+Under the assumption of the airspeed $s>\|w(t)\|$ for $t>0$ (i.e., the constant airspeed is greater than the norm of the wind), the guidance action can be expressed
 \begin{equation}\label{eqq:5}
@@
 \end{equation} 
-where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of the vector field $\dot{\mathbf{p}}_d$ to the desired trajectory, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
-
----
+where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of $\dot{\mathbf{p}}_d$, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
 
@@
 
-To evaluate the energy spent performing a given motion and software configuration we consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$
+To evaluate the energy spent performing given actuation and computations we consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$
 \begin{equation}\label{eqq:6}
@@
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the controlled system, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise.
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise.
 The control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
-The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix as follows
+The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix
 \begin{equation}\begin{split}
@@
 where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
-Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and columns vectors respectively.
+Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and column vectors respectively.
 
-Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1})~and~(\ref{eqq:7}) by employing the following expression
-\begin{subequations}\begin{align}
+Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1})~and~(\ref{eqq:7})
+\begin{subequations}\label{eqq:9}\begin{align}
   &\begin{cases}\label{eqq:9a}
@@
 As the system was observed to behave stochastically, with the process and measurement noise evolving in a normal distribution, a Kalman filter~\cite{stengel1994optimal, simon2006optimal} is employed to predict the state $\hat{\mathbf{q}}$.
-Such a state, along with the predicted output $\hat{y}$ differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
+Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
 
-The prediction is done using the following expression
+The prediction is done using
 \begin{subequations}\label{eqq:10}\begin{align}
@@
 
-The estimation of the state and the update of the predicted output is done using the following expression
+The estimation of the state and the update of the predicted output is done using
 \begin{subequations}\label{eqq:11}\begin{align}
@@
 
-Equation~(\ref{eqq:10}) converges to the predicted energy evolution as follows.
+Equations~(\ref{eqq:10}--\ref{eqq:11}) converge to the predicted energy evolution as follows.
 An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
 It is worth considering that an appropriate guess of these parameters allows the system to converge to the desired energy evolution in a shorter amount of time.
-The tuning parameters $Q,R$ are also derived from the collected data and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
+The tuning parameters $Q,R$ are also derived from the collected data, and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
-The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (the energy sensor of the flight controller is employed), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
+At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equations~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
+The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (we use the energy sensor of the flight controller), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
 The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
@@
 
-In the light of Equations~(\ref{eqq:9a})~and~(\ref{eqq:9b}), the main goal stated earlier in this section can be updated.
+In the light of Equations~(\ref{eqq:9}--\ref{eqq:11}), the main goal stated earlier in this section can be updated.
 We aim to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$~\cite{rawlings2017model}.
@@
 The system is modeled as follows.
-An existing ROS system composes several computationally expensive ROS nodes, allowing to vary the number of computations changing the node-specific quality of service (QoS) values via ROS parameters.
+An existing ROS system composes several computationally expensive ROS nodes, allowing to vary the number of computations changing some node-specific quality of service (QoS) values via ROS parameters.
 The tool builds the energy model using mission specification which, besides other mission parameters, specifies per each ROS node a QoS range.
 
-Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action as
+Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action
 \begin{equation}\label{eqq:12}
@@
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
-The computational energy component can be hence described
+The computational energy component can be described
 \begin{equation}\begin{split}
@@
 The control action is constructed in two steps.
-Equation~(\ref{eqq:12}) defines the control due to the computational model.
-The control due to the energy model, which describes the energy of the mechanical elements of the drone $\mathcal{M}$, is derived in the following subsection.
+Equation~(\ref{eqq:12}) defines the control due to the computations.
+The control due to the actuation, which describes the energy of the mechanical elements of the drone $\mathcal{M}$, is derived in the following subsection.
 
@@
 
-Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathbf{u}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
+Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
 The set of these parameters can be expressed
@@
 \end{equation}
-where $c$ is defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ are the optimal points which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
+where $c$ is defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
 
@@
 
-It is worth considering that the number of parameters at state $k$ is also a parameter of the state.
+It is worth considering that the number of parameters at state $k$ is a parameter of the state.
 This is for the sake of generality, as the mission specification might contain different explicit equations for different states.
-Meaning that the drone might follow an ellipse function throughout the mission and heading a linear function while landing.
+For instance, the drone might follow an ellipse function throughout the mission and heading a linear function while landing.
 
-The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}) respectively, are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
+The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
 \begin{equation}\begin{split}

### 2020-07-14 icra-2021.tex
fixed some misspelled 'Equations' words

@@
 
-Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equations~(\ref{eqq:1})~and~(\ref{eqq:7})
+Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equation~(\ref{eqq:1})~and~(\ref{eqq:7})
 \begin{subequations}\label{eqq:9}\begin{align}
@@
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equations~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
+At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
 The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (we use the energy sensor of the flight controller), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
@@
 
-The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equations~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
+The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equation~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
 Alike Equation~(\ref{eqq:14}), the parameters $\mathbf{u}_k=\{u_{k,1},\dots,u_{k,\rho_k}\}$ at time $k$ are constrained
@@
 \end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equations~(\ref{eqq:7})~and~(\ref{eqq:9b}).
+where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}).
 Moreover, the first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$.

### 2020-07-16 icra-2021.tex
added the matlab script, minor fix to the text

@@
     a_0 & \vline & a_1 & b_1 & \cdots & a_r & b_r
-  \end{array}\right],\\
+  \end{array}\right]^T,\\
   A&=\left[\begin{array}{ccccc}
@@
 \end{align}\end{subequations}
-where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate before measurement).
+where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
 
@@
   \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
-  P_{k+1}&=(I-G_{k+1}C)P_{k+1}^-,\\
+  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
   \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}

### 2020-07-16 matlab/evolution.m

@@ -1,0 +1,69 @@
+
+%% system definition
+
+r = input('Fourier series order r: ');
+j = 2*r + 1;
+
+An = @(n) [ 0 1 ; -1 0 ];
+A  = zeros(j);
+A(1,1) = 1;
+C = [1];
+
+for i = 1:r
+    A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
+    C = [C 1 0];
+end
+
+%% getting energy data
+
+file = csvread(uigetfile('.csv'));
+column = input('Which column contains energy: ');
+file = file(:, [column]);
+ts = input('At what time step [ms]: ');
+tf = (1 / ts) * 1000 * size(file, 1);
+file = imresize(file, [100, 1]);
+t = transpose(linspace (0, tf, 100));
+
+%% initial guess
+
+q0 = ones(j, 1);
+P0 = eye(j);
+%u=...
+
+% process noise and sensor noise
+Q = eye(j);
+R = 1;
+
+% predicted energy evolution
+y = [];
+
+%% kalman filter estimatation
+ 
+for y0_sensor = transpose(file)
+    
+    % prediction
+    q1_minus = A * q0; %+B*u0
+    P1_minus = A * P0 * transpose(A) + Q;
+    
+    % estimation
+    K1 = (P1_minus * transpose(C)) / (C * P1_minus * transpose(C) + R);
+    q1 = q1_minus + K1 * (y0_sensor - C * q1_minus);
+    P1 = (eye(j) + K1 * C) * P1_minus;
+    y0_estimate = C * q1;
+    
+    % updating values for the next iteration
+    q0 = q1;
+    P0 = P1;
+    y = [y y0_estimate];
+end
+
+%% plots
+
+plot(t, file);
+hold on;
+plot (t, y);
+
+legend('data', 'observer');
+
+
+

### 2020-07-17 matlab/evolution.m
updated equation 8 with characteristic time, updated matlab script

@@ -3,8 +3,9 @@
 
 r = input('Fourier series order r: ');
 j = 2*r + 1;
+xi = 10;
 
-An = @(n) [ 0 1 ; -1 0 ];
+An = @(n) [ 0 n/xi ; -n^2/xi^2 0 ];
 A  = zeros(j);
 A(1,1) = 1;
 C = [1];

### 2020-08-01 matlab/build_ck.m
updated matlab script

@@ -1,8 +1,9 @@
 
-function [u, g] = read_spec(spec, prof, t) 
-%mission.m Reads a mission specification file along with the output from
-%   powprof. Thus builds a vector of all the possible controls and their 
-%   power consumption. The control vector is normalized over the systems
+function [ckgck] = build_ck(spec, prof, t) 
+%build_ck.m Reads a mission specification file along with the output from
+%   powprof. Builds a vector of all the possible computational controls 
+%   [Ck in Equation (12)] and their  power consumption [g(Ck) in 
+%   Equation (13)]. The control vector is normalized over the systems
 %   time, for the purpose of simulation.
 %
 % Inputs:
@@ -12,26 +13,25 @@ function [u, g] = read_spec(spec, prof, t)
 %   t      : time used for the purpose of simulation
 %
 % Outputs:
-%   comp   : The computational energy component u = {ui | ui = QoS for 
-%                                                        all i in {0, ..., 
-%                                                                  k}     }
-   
+%   ckgck  : All the possible combinations of the QoS Ck, along with their
+%            istantaneous power consumption from powprof g(Ck)
+%   
     u = [];
     
+    % iterates for each line in the mission specification
     for i = 1:size(spec, 1)
-        % iterates for each line in the mission specification
         
+        % iterates for each time interval
         for j = spec(i, 1):spec(i, 2)
-            % iterates for each time interval
             
+            % makes all the possible combinations of controls of QoS
             u1 = [];
             for k = 3:2:size(spec, 2)
-                % makes all the possible combinations of controls of QoS
                 
-                uu = spec(i, k): ...
-                     prof(2, end - 1) - prof(1, end - 1):spec(i, k + 1);
                 % for the purpose of simulation the same step as in powprof
                 % is used (which can be easily adapted when using powprof)
+                uu = spec(i, k): ...
+                     prof(2, end - 1) - prof(1, end - 1):spec(i, k + 1);
                 
                 if (isempty(u1))
                     u1 = transpose(uu);
@@ -43,20 +43,24 @@ function [u, g] = read_spec(spec, prof, t)
                 end
             end
             
-            tt = ones(size(u1, 1), 1) * j;
-            
-            u1 = [ u1 zeros(size(u1, 1), 1) ];
             % filling the control with the energy data
+            u1 = [ u1 zeros(size(u1, 1), 1) ];
+            
             for k = 1:size(prof, 1)                
[…]

### 2020-08-01 matlab/build_model.m

@@ -1,0 +1,72 @@
+
+function [y, qq0] = build_model(r, mech, u, q0, P0, Q, R, t, eps)
+%build_model.m Builds the energy model [Equation (9b)] using Kalman Filter 
+%   as state observer [Equations (10--11)]
+%
+% Inputs:
+%   r      : the Fourier series order [Eqaution (6)]
+%   mech   : mechanical energy vector [W]. I.e., the data from flying the
+%            drone in simulation or data from real flights logging the
+%            flight controller
+%   u      : control [Equation (9b)]
+%   q0     : initial guess of the estimate of the state
+%   P0     : vatiance of the guessed estimate
+%   Q      : process noise covariance
+%   R      : sensor noise covariance
+%   t      : time used for the purpose of simulation
+%   eps    : used to return qq0
+%
+% Outputs:
+%   y      : energy evolution
+%   qq0    : the first estimated state value [Equation (8)] differs from
+%            mech < eps
+%
+
+    % TODO: u!
+    % system defintion
+    j = 2*r + 1;
+    xi = 10;
+
+    An = @(n) [ 0 n/xi ; -n^2/xi^2 0 ];
+    A  = zeros(j);
+    A(1,1) = 1;
+    C = [1];
+
+    for i = 1:r
+        A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
+        C = [C 1 0];
+    end
+
+    clear i, An;
+    
+    % predicted energy evolution
+    y = [];
+
+    qq0 = [];
+    
+    % kalman filter estimatation
+    for y0_sensor = transpose(mech)
+    
+        % prediction
+        q1_minus = A * q0; %+B*u0
+        P1_minus = A * P0 * transpose(A) + Q;
+    
+        % estimation
+        K1 = (P1_minus * transpose(C)) / (C * P1_minus * transpose(C) + R);
+        q1 = q1_minus + K1 * (y0_sensor - C * q1_minus);
+        P1 = (eye(j) + K1 * C) * P1_minus;
+        y0_estimate = C * q1;
+    
+        % updating values for the next iteration
+        q0 = q1;
+        P0 = P1;
+        y = [y y0_estimate];
+    
+        if (and(isempty(qq0), abs(y0_estimate - y0_sensor) < 0.001))
+            qq0 = q0;
+        end
+    end
+
+    clear j showed;
+
+end

### 2020-08-01 matlab/energy.m

@@ -1,103 +1,0 @@
-
-%
-%  Implementation Energy Model simulation in Matlab
-%
-disp('Energy Model simulation')
-
-%% system definition
-
-r = input('Fourier series order r: ');
-j = 2*r + 1;
-xi = 10;
-
-An = @(n) [ 0 n/xi ; -n^2/xi^2 0 ];
-A  = zeros(j);
-A(1,1) = 1;
-C = [1];
-
-for i = 1:r
-    A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
-    C = [C 1 0];
-end
-
-clear i, An;
-
-%% getting mechanical energy data
-
-disp('Input mechanical energy data [csv]');
-file = csvread(uigetfile('.csv'));
-column = input('Which column contains energy: ');
-file = file(:, [column]);
-ts = input('At what time step [ms]: ');
-tf = (1 / ts) * 1000 * size(file, 1);
-file = imresize(file, [100, 1]);
-t = transpose(linspace (0, tf, 100));
-
-clear column;
-
-%% getting computational energy data
-disp('Input computational energy data (from powprof) [csv]');
-file2 = csvread(uigetfile('.csv'));
-disp('Input mission specification [csv]');
-file3 = csvread(uigetfile('.csv'));
-
-read_spec(file3, file2, t);
-
-%% initial guess
-
-q0 = ones(j, 1);
-P0 = eye(j);
-%u=...
-
-% process noise and sensor noise
-Q = eye(j);
-R = 1;
-
-% predicted energy evolution
-y = [];
-
-%% kalman filter estimatation
-
-showed = 0;
-
-for y0_sensor = transpose(file)
-    
-    % prediction
-    q1_minus = A * q0; %+B*u0
-    P1_minus = A * P0 * transpose(A) + Q;
-    
-    % estimation
-    K1 = (P1_minus * transpose(C)) / (C * P1_minus * transpose(C) + R);
-    q1 = q1_minus + K1 * (y0_sensor - C * q1_minus);
-    P1 = (eye(j) + K1 * C) * P1_minus;
-    y0_estimate = C * q1;
-    
-    % updating values for the next iteration
-    q0 = q1;
-    P0 = P1;
-    y = [y y0_estimate];
-    
-    if (abs(y0_estimate - y0_sensor) < 0.001)
-        if (showed == 0)
-            showed = 1;
-            disp('At iteration');
-            disp(size(y,2));
[…]

### 2020-08-01 matlab/main.m

@@ -1,0 +1,58 @@
+
+%mainai.m
+% Simulation in Matlab, use data directory to pass the required data in
+% the simulation. If you use the combo c_e (computational_energy.cvs...), 
+% m_e, m_s in simulation1, then use r = 3, column = 1, and ts = 200
+%
+
+%%
+disp('Model simulation')
+
+r = input('Fourier series order r: ');
+
+% getting mechanical energy data
+
+disp('Input mechanical energy data [csv]');
+[bn, folder] = uigetfile('.csv');
+file = csvread(fullfile([folder, bn]));
+
+column = input('Which column contains energy: ');
+file = file(:, [column]);
+
+ts = input('At what time step [ms]: ');
+tf = (1 / ts) * 1000 * size(file, 1);
+file = imresize(file, [100, 1]);
+t = transpose(linspace (0, tf, 100));
+
+clear column;
+
+% getting computational energy data
+disp('Input computational energy data (from powprof) [csv]');
+[bn, folder] = uigetfile('.csv');
+file2 = csvread(fullfile([folder, bn]));
+
+disp('Input mission specification [csv]');
+[bn, folder] = uigetfile('.csv');
+file3 = csvread(fullfile([folder, bn]));
+
+ckgck = build_ck(file3, file2, t);
+
+% initial guess
+j = 2*r + 1;
+q0 = ones(j, 1);
+P0 = eye(j);
+
+% process noise and sensor noise
+Q = eye(j);
+R = 1;
+
+% predicted energy evolution
+[y, qq0] = build_model(r, file,  ckgck(:, end), q0, P0, Q, R, t, 0.001);
+
+%%
+plot(t, file);
+clear file;
+hold on;
+plot (t, y);
+
+legend('data', 'observer');

### 2020-08-02 matlab/build_ck.m
added controls to the model

@@ -24,6 +24,15 @@ function [ckgck] = build_ck(spec, prof, t)
         % iterates for each time interval
         for j = spec(i, 1):spec(i, 2)
             
+            % just for the purpose of simulation; you generatre all the
+            % possible combinations of computational control for the
+            % simulated time (and not all the times) 
+            if (~any(floor(t) == j))
+                continue;
+            end
+            jj = t(any(floor(t) == j, 2));
+            jj = jj(1);
+            
             % makes all the possible combinations of controls of QoS
             u1 = [];
             for k = 3:2:size(spec, 2)
@@ -52,7 +61,7 @@ function [ckgck] = build_ck(spec, prof, t)
                       ), end) = prof(k, end);
             end
             
-            tt = ones(size(u1, 1), 1) * j;
+            tt = ones(size(u1, 1), 1) * jj;
             
             u = [ u; tt u1 ];
             
@@ -60,7 +69,6 @@ function [ckgck] = build_ck(spec, prof, t)
         end
     end
     
-    % TODO: normalizing over the simulation time!
     ckgck = u;
     
 end

### 2020-08-02 matlab/build_model.m

@@ -1,5 +1,5 @@
 
-function [y, qq0] = build_model(r, mech, u, q0, P0, Q, R, t, eps)
+function [y, qq0] = build_model(r, mech, gck, mk, q0, P0, Q, R, t, eps)
 %build_model.m Builds the energy model [Equation (9b)] using Kalman Filter 
 %   as state observer [Equations (10--11)]
 %
@@ -36,6 +36,11 @@ function [y, qq0] = build_model(r, mech, u, q0, P0, Q, R, t, eps)
         A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
         C = [C 1 0];
     end
+    
+    % control action [Equation (17)]
+    u = @(k) [gck(k); transpose(mk(k))];
+    B = [ 1                 zeros(1, size(mk, 2)); ...
+          zeros(j - 1, 1)   zeros(j - 1, size(mk, 2))  ];
 
     clear i, An;
     
@@ -45,23 +50,28 @@ function [y, qq0] = build_model(r, mech, u, q0, P0, Q, R, t, eps)
     qq0 = [];
     
     % kalman filter estimatation
+    k = 1;
     for y0_sensor = transpose(mech)
-    
+        % getting the control at time k
+        u0 = u(k);
+        
         % prediction
-        q1_minus = A * q0; %+B*u0
+        q1_minus = A * q0 + B*u0;
         P1_minus = A * P0 * transpose(A) + Q;
     
         % estimation
         K1 = (P1_minus * transpose(C)) / (C * P1_minus * transpose(C) + R);
-        q1 = q1_minus + K1 * (y0_sensor - C * q1_minus);
+        q1 = q1_minus + K1 * (y0_sensor + u0(1) - C * q1_minus);
         P1 = (eye(j) + K1 * C) * P1_minus;
         y0_estimate = C * q1;
     
         % updating values for the next iteration
         q0 = q1;
         P0 = P1;
+        k = k + 1;
+        
         y = [y y0_estimate];
-    
+        
         if (and(isempty(qq0), abs(y0_estimate - y0_sensor) < 0.001))
             qq0 = q0;
         end

### 2020-08-02 matlab/main.m

@@ -35,6 +35,7 @@ disp('Input mission specification [csv]');
 [bn, folder] = uigetfile('.csv');
 file3 = csvread(fullfile([folder, bn]));
 
+% computational model
 ckgck = build_ck(file3, file2, t);
 
 % initial guess
@@ -46,12 +47,25 @@ P0 = eye(j);
 Q = eye(j);
 R = 1;
 
+% TODO: this selects just the highest possible control for each time
+% interval, which is not optimal; this would be part of the optimal control
+% policy once it's done
+gck = [];
+for i = 1:size(t, 1)
+    cckgck = ckgck(any(ckgck(:, 1) == t(i), 2), end);
+    
+    gck = [gck; cckgck(end)];
+end
+
+%TODO: the mechanical components of the control
+mk = zeros(size(t, 1), 1);
+
 % predicted energy evolution
-[y, qq0] = build_model(r, file,  ckgck(:, end), q0, P0, Q, R, t, 0.001);
+[y, qq0] = build_model(r, file,  gck, mk, q0, P0, Q, R, t, 0.001);
 
 %%
-plot(t, file);
-clear file;
+plot(t, file + gck);
+clear file file2 file3;
 hold on;
 plot (t, y);
 

### 2020-08-02 icra-2021.tex
updated equation 8 with characteristic time, updated matlab script
updated some formulas (for instance 13 was wrong...)

@@
     \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
-  \end{array}\right],\,A_n=\begin{bmatrix}0 & n \\ -n^2 & 0\end{bmatrix},\\
+  \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
   C&=\left[\begin{array}{ccccccc}
@@
   K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
+  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
   P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
@@
 where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
+$y_k^s,y_k^c$ are the energy readings: $y_k^s$ the flight controller sensor, i.e., the energy needed for the actuation, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eqq:13}) later in this section.
 The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
@@
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
-The computational energy component can be described
-\begin{equation}\begin{split}
-  g(\mathcal{C}_{k})&:=\{g\left(0,\text{QoS}_0(k)\right),\dots,g\left(\sigma,\text{QoS}_\sigma(k)\right)\},\\
-  y_c(t)&=\sum_{x\in g\left(\mathcal{C}_{\ceil{t}}\right)}{x},
+The computational energy component can be defined
+\begin{equation}\label{eqq:13}\begin{split}
+  y_k^c:&=g\left(\text{QoS}_0\left(k\right),\dots,\text{QoS}_\sigma\left(k\right)\right)=g\left(\mathcal{C}_{k}\right).\\
 \end{split}\end{equation}
-where $\ceil{\cdot}$ is the ceiling function that returns the least integer greater than or equal to the argument.
 
@@
   B&=\left[\begin{array}{ccccccc}
-    1 & \cdots & 1 & \vline & 0 & \cdots & 0\\\hline
-    0 & \cdots & 0 & \vline & 0 & \cdots & 0\\
-    \vdots & \ddots & \vdots & \vline & \vdots & \ddots & \vdots\\
-    0 & \cdots & 0 & \vline & 0 & \cdots & 0
+    1 & \vline & 0 & \cdots & 0\\\hline
+    0 & \vline & 0 & \cdots & 0\\
+    \vdots & \vline & \vdots & \ddots & \vdots\\
+    0 & \vline & 0 & \cdots & 0
   \end{array}\right],
@@
 \end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}).
-Moreover, the first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$.
+where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}).
+Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$.
 This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}).

### 2020-08-02 matlab/build_ck.m

@@ -14,7 +14,7 @@ function [ckgck] = build_ck(spec, prof, t)
 %
 % Outputs:
 %   ckgck  : All the possible combinations of the QoS Ck, along with their
-%            istantaneous power consumption from powprof g(Ck)
+%            instantaneous power consumption from powprof g(Ck)
 %   
     u = [];
     
@@ -24,7 +24,7 @@ function [ckgck] = build_ck(spec, prof, t)
         % iterates for each time interval
         for j = spec(i, 1):spec(i, 2)
             
-            % just for the purpose of simulation; you generatre all the
+            % just for the purpose of simulation; you generate all the
             % possible combinations of computational control for the
             % simulated time (and not all the times) 
             if (~any(floor(t) == j))

### 2020-08-02 matlab/build_model.m

@@ -4,13 +4,13 @@ function [y, qq0] = build_model(r, mech, gck, mk, q0, P0, Q, R, t, eps)
 %   as state observer [Equations (10--11)]
 %
 % Inputs:
-%   r      : the Fourier series order [Eqaution (6)]
+%   r      : the Fourier series order [Equation (6)]
 %   mech   : mechanical energy vector [W]. I.e., the data from flying the
 %            drone in simulation or data from real flights logging the
 %            flight controller
 %   u      : control [Equation (9b)]
 %   q0     : initial guess of the estimate of the state
-%   P0     : vatiance of the guessed estimate
+%   P0     : variance of the guessed estimate
 %   Q      : process noise covariance
 %   R      : sensor noise covariance
 %   t      : time used for the purpose of simulation
@@ -22,8 +22,7 @@ function [y, qq0] = build_model(r, mech, gck, mk, q0, P0, Q, R, t, eps)
 %            mech < eps
 %
 
-    % TODO: u!
-    % system defintion
+    % system definition
     j = 2*r + 1;
     xi = 10;
 
@@ -49,7 +48,7 @@ function [y, qq0] = build_model(r, mech, gck, mk, q0, P0, Q, R, t, eps)
 
     qq0 = [];
     
-    % kalman filter estimatation
+    % Kalman filter estimation
     k = 1;
     for y0_sensor = transpose(mech)
         % getting the control at time k

### 2020-09-02 matlab/build_gdn.m
fixes to the matlab script and a minor typo in the text

@@ -1,73 +1,0 @@
-
-function [] = build_gdn(E, ke, varphi, x, y)
-   
-    dvarphi = gradient(varphi, [x y]);
-    
-    dpd = E * dvarphi - ke * varphi * dvarphi;
-    
-    [xp yp] = meshgrid(0:.5:25, 0:.5:25);
-
-    points = reshape(cat(2, xp', yp'), [], 2);
-
-    clear xp yp;
-
-    figure;
-
-    
-    title('vector field with constant v');
-
-    varphi_plot = ezplot(varphi, [0 25]);
-    set(varphi_plot, 'Color', 'black', 'LineWidth', 2)
-
-    xlim([0 25]);
-    ylim([0 25]);
-
-    hold on;
-
-    dpdx = [];
-    dpdy = [];
-    
-    for i = 1:size(points, 1)
-    
-        p = transpose(points(i, :));
-        
-        x = p(1);
-        y = p(2);
-        
-        pd = double(subs(dpd));
-    
-        angle = atand(pd(2) / pd(1));
-    
-        if (isnan(angle)) % center of the ellipse
-            continue;
-        end
-    
-        %ha = annotation('arrow');
-        %ha.Parent = gca;
-        %ha.Color = [170 170 170] / 255;
-    
-        if (pd(1) < 0 && pd(2) < 0)
-            angle = 180 + angle;
-        end
-    
-        if (pd(1) < 0 && pd(2) > 0)
-            angle = 180 + angle;
-        end
-  
-        %ha.X = [p(1) p(1)+0.45*cosd(angle)];
-        %ha.Y = [p(2) p(2)+0.45*sind(angle)];
-        
-        dpdx = [dpdx [p(1); p(1) + 0.45 * cosd(angle)]];
-        dpdy = [dpdy [p(2); p(2) + 0.45 * sind(angle)]];
-        
-
-        %plot([p(1); p(1)+0.45*cosd(angle)],[p(2); p(2)+0.45*sind(angle)]); 
-        
-        %ha.LineWidth  = 1;
-        %ha.HeadWidth  = 2;
-        %ha.HeadLength = 4;
-    end
-    
-    plot(dpdx, dpdy); 
-    
-end

### 2020-09-02 matlab/build_gdn2.m

@@ -1,99 +1,29 @@
 
-function [] = build_gdn(E, ke, varphi, min, max)
+function [dpd, pdangle] = build_gdn2(E, ke, varphi, points)
     
     syms x y;
     
+    % gradient
     dvarphi = gradient(varphi, [x y]);
     
     dpd = E * dvarphi - ke * varphi * dvarphi;
     
-    [xp yp] = meshgrid(min:(abs(min) + abs(max)) / 50:max, min:(abs(min) + abs(max)) / 50:max);
-
-    points = reshape(cat(2, xp', yp'), [], 2);
-
-    clear xp yp;
-
-    figure;
-    
-    title('vector field with constant v');
-
-    varphi_plot2 = fimplicit(varphi);
-    set(varphi_plot2, 'Color', [.85 .85 .85], 'LineWidth', 10);
-    
-    hold on;
-    
-    varphi_plot = fimplicit(varphi);
-    set(varphi_plot, 'Color', 'black', 'LineWidth', 1.2);
-    
-    xlim([min max]);
-    ylim([min max]);
-        
     x = transpose(points(:, 1));
     y = transpose(points(:, 2));
-        
+    
     pd = transpose(double(subs(dpd)));
     
-    angle = atand(pd(:,2) ./ pd(:,1));
+    angle = atand(pd(:, 2) ./ pd(:, 1));
     
-    angle(and(pd(:,1) < 0, pd(:,2) < 0)) = angle(and(pd(:,1) < 0, pd(:,2) < 0)) + 180;
-   
-    %if (pd(1) < 0 && pd(2) < 0)
+    angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) = angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) + 180;
     
-    angle(and(pd(:,1) < 0, pd(:,2) > 0)) = angle(and(pd(:,1) < 0, pd(:,2) > 0)) + 180;
+    % corresponds to if (pd(1) < 0 && pd(2) < 0) ...
     
-    %if (pd(1) < 0 && pd(2) > 0)
+    angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) = angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) + 180;
+    
+    % corresponds to if (pd(1) < 0 && pd(2) > 0) ...
      
     angle = transpose(angle);
-    
-    % just plots
-    
[…]

### 2020-09-02 matlab/gdn.m

@@ -1,96 +1,0 @@
-
-E = [ 0 1; -1 0 ];
-
-ke = 1.5;
-
-varphi = @(p) ([1 0]*p - 12.5)^2/6^2 + ([0 1]*p - 12.5)^2/8^2 - 1;
-
-dvarphi = @(p) [2*[1 0]*p/6^2 - 25/6^2; 2*[0 1]*p/8^2 - 25/8^2];
-
-dpd = @(p, ke) E * dvarphi(p) - ke * varphi(p) * dvarphi(p);
-
-[x y] = meshgrid(0:.5:25, 0:.5:25);
-
-points = reshape(cat(2, x', y'), [], 2);
-
-clear x y;
-
-figure;
-
-title('vector field (aka desired velocity vector)');
-
-xlim([0 25]);
-ylim([0 25]);
-
-hold on;
-
-for i = 1:size(points, 1)
-    
-    p = transpose(points(i, :));
-    
-    pd = dpd(p, ke);
-    
-    ha = annotation('arrow');
-    ha.Parent = gca;
-    ha.Color = [170 170 170] / 255;
-    
-    ha.X = [p(1) p(1)+pd(1)];
-    ha.Y = [p(2) p(2)+pd(2)]; 
-
-    ha.LineWidth  = 1;
-    ha.HeadWidth  = 2;
-    ha.HeadLength = 4;
-end
-
-figure;
-
-title('vector field with constant v');
-
-varphi_plot = ezplot('(x-12.5)^2/6^2+(y-12.5)^2/8^2=1',[0 25]);
-set(varphi_plot, 'Color', 'black', 'LineWidth', 2)
-
-[x y] = meshgrid(0:0.5:25, 0:0.5:25);
-
-points = reshape(cat(2, x', y'), [], 2);
-
-xlim([0 25]);
-ylim([0 25]);
-
-hold on;
-
-for i = 1:size(points, 1)
-    
-    p = transpose(points(i, :));
-    
-    pd = dpd(p, ke);
-    
-    angle = atand(pd(2) / pd(1));
-    
-    if (isnan(angle)) % center of the ellipse
-        continue;
-    end
-    
-    ha = annotation('arrow');
-    ha.Parent = gca;
-    ha.Color = [170 170 170] / 255;
-    
-    if (pd(1) < 0 && pd(2) < 0)
-        angle = 180 + angle;
-    end
-    
[…]

### 2020-09-02 matlab/main.m

@@ -1,5 +1,5 @@
 
-%mainai.m
+%main.m
 % Simulation in Matlab, use data directory to pass the required data in
 % the simulation. If you use the combo c_e (computational_energy.cvs...), 
 % m_e, m_s in simulation1, then use r = 3, column = 1, and ts = 200
@@ -70,3 +70,25 @@ hold on;
 plot (t, y);
 
 legend('data', 'observer');
+
+%%
+
+syms x y;
+varphi = ((x - 200) * cosd(12) + (y - 200) * sind(12))^2 / 120^2 + ((x - 200)*sind(12) - (y - 200) * cosd(12))^2 / 170^2 - 1;
+
+min = 0;
+max = 400;
+
+% create all the points I want to use to build gdn
+[xp yp] = meshgrid(min:(abs(min) + abs(max)) / 50:max, min:(abs(min) + abs(max)) / 50:max);
+points = reshape(cat(2, xp', yp'), [], 2);
+clear xp yp;
+
+E = [0 1; -1 0];
+ke = 1.5;
+[dpd, pdangle] = build_gdn2(E, ke, varphi, points);
+plot_gdn2(E, ke, varphi, points, pdangle, 0, 400, 10000, 20, [400; 400])
+
+
+
+

### 2020-09-02 matlab/plot_gdn2.m

@@ -1,0 +1,69 @@
+
+function [] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
+        
+    figure;
+    
+    % just a nice effect nothing more...
+    varphi_plot2 = fimplicit(varphi);
+    set(varphi_plot2, 'Color', [.85 .85 .85], 'LineWidth', 10);
+    
+    hold on;
+    
+    varphi_plot = fimplicit(varphi);
+    set(varphi_plot, 'Color', 'black', 'LineWidth', 1.2);
+    
+    xlim([min max]);
+    ylim([min max]);
+        
+    x = transpose(points(:, 1));
+    y = transpose(points(:, 2));
+        
+    %% the vector field (of pd)
+    % a crazy workaround to plot those arrows...
+    
+    coeff = 0.45 * (max - min) / 25;
+    coeffm = 0.20 * (max - min) / 25;
+    coeffM = 0.30 * (max - min) / 25;
+    
+    dpdx = [x; x + coeff * cosd(pdangle)];
+    dpdy = [y; y + coeff * sind(pdangle)];
+    
+    arrowlxx = [x + coeffM * cosd(pdangle); dpdx(2, :)];
+    arrowlxy = [y + coeffm * sind(pdangle); dpdy(2, :)];
+    
+    arrowrxx = [x + coeffm * cosd(pdangle); dpdx(2, :)];
+    arrowrxy = [y + coeffM * sind(pdangle); dpdy(2, :)];
+    
+    plot(dpdx, dpdy, 'Color', [0.3010, 0.7450, 0.9330]);
+    
+    plot(arrowlxx, arrowlxy, 'Color', [0.3010, 0.7450, 0.9330]);
+    plot(arrowrxx, arrowrxy, 'Color', [0.3010, 0.7450, 0.9330]);
+    
+    %% animation
+    
+    xd = [1 0] * p;
+    yd = [0 1] * p;
+    
+    xdd = xd;
+    ydd = yd;
+    
+    for i=1:andu
+        x = xd;
+        y = yd;
+        [dpd, pdangle] = build_gdn2(E, ke, varphi, [x y]);
+        pd = transpose(double(subs(dpd)));
+        
+        pdangle = transpose(pdangle);
+        
+        xd = [xd + s * .1 * cosd(pdangle)];
+        yd = [yd + s * .1 * sind(pdangle)];
+        
+        xdd = [xdd; xd];
[…]

### 2020-09-08 icra-2021.tex
fixes to the matlab script and a minor typo in the text
changes to the text (implementing finally the comments...)

@@
   }
+  @inproceedings{morbidi2016minimum,
+    title={Minimum-energy path generation for a quadrotor UAV},
+    author={Morbidi, Fabio and Cano, Roel and Lara, David},
+    booktitle={2016 IEEE International Conference on Robotics and Automation (ICRA)},
+    pages={1492--1498},
+    year={2016},
+    organization={IEEE}
+  }
+
 \end{filecontents}
@@
 % big picture in the introduction to agree what specifically I am trying to do right now
-*
+
+Mobile robots are increasingly used in a broad range of applications.
+The growing demand for autonomy of such devices challenges traditional methodologies, soliciting the development of new and unprecedented techniques.
+The presented approach proposes a \emph{mission-aware energy planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the robot's energy consumption and autonomy.
+The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs).
+The approach ideally accounts for a mission extension by adapting the TEEs and QoS as the robot batteries drain.
+
+Energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning.
+Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a specific class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
+In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands through a mission-aware perspective.
+Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+
+The algorithm relies on the assumptions of the mission--a set of tasks the mobile robot is supposed to perform--being \emph{periodic} and \emph{uncertain}.
+The periodicity is directly observed by e.g., the mobile robot traveling in repetitive patterns executing a set of assigned tasks, and the uncertainty accounts for the environmental interference, with e.g., a fixed-wing drone drifting due to windy weather.
+The algorithm proposes a Fourier series to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to address the uncertainty assumption.
+
+% Robots critically depend on battery for the completion of their mission, the duration of which is proportional to the state of the power source
+
+% Modeling mechanical and computational energy separately allows tradeoffs between the two to be expressed, such as performing additional onboard computations to reduce the amount of mechanical energy needed to complete the mission.
+
+% The increasing demand for autonomy, challenge the traditional computational model and perhaps justify the presented approach.
+
+% Preliminary data using a terrestrial fixed-wing craft indicates a potential mission extension of up to 13 minutes over 1 hour flight by switching to the lowest QoS, with the computations accounting for up to 23% of the total energy.
+The approach ideally accounts for the extension by adapting the trajectory and the computations as the robot batteries drain.
 
 %%%%%%%%%%%%%%%%%%%%%%
-\section{State of the Art}
-\label{sec:related}
+%\section{State of the Art}
+%\label{sec:related}
 
-*
+%*
 % equation number just just for illustrate the reader just to introduce and support - this is an offline method
@@
 
-The model presented in this section deals with the motion and the energy using two different systems, subject to the same process noise $w$ (i.e., the atmospheric interference such as wind).
+The algorithm utilizes the model to estimate the robot's position in space and its energy evolution in time.
 
-The motion defines a trajectory and a position $\mathbf{p}$; the trajectory is expressed through explicit trajectory equation $\varphi$, while the position determines a vehicle frame $\mathcal{O}_V$ in the 2D Euler space relative to an inertial frame $\mathcal{O}_W$.
+Given a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which affects the position allowing the motion along the 3-axis--is built upon the direction to follow, derived using vector field~\cite{de2017guidance}.
+
+---
+
+%The motion defines a trajectory and a position $\mathbf{p}$; the trajectory is expressed through explicit trajectory equation $\varphi$, while the position determines a vehicle frame $\mathcal{O}_V$ in the 2D Euler space relative to an inertial frame $\mathcal{O}_W$.
 For the sake of simplicity, it is assumed that the $z$-axis is constrained to a specific altitude $h$, with the system being free to evolve in the $x,y$-axes (i.e., the drone is flying, performing a mission, at a given height).
@@
 
-The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis in its state-space representation.
+%The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis in its state-space representation.
 This component is decomposed in the energy needed for the actuation (i.e., the mechanical energy), and the computations (i.e., the computational energy), an approach that has been extensively reviewed in our previous work~\cite{seewald2019coarse, seewald2019component, seewald2020mechanical}.
@@
 \begin{equation}\label{eqq:4}\begin{split}
-  &\dot{\chi}(\mathbf{p},\dot{\mathbf{p}})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
+  &\dot{\chi}(\dot{\mathbf{p}},\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
   &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^T\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,

### 2020-09-09 icra-2021.tex
friday's countdown (aka preparing a stable version for internal review [1])

@@
 
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{cor}{Corollary}
+\newtheorem{conj}{Conjecture}[section]
+\newtheorem{defn}{Definition}[section]
+\newtheorem{exmp}{Example}[section]
+\newtheorem{rem}{Remark}
+
 %% references (generates a bib file for bibtex)
@@
     author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    booktitle={Proceedings of the 2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
+    booktitle={2020 4th IEEE International Conference on Robotic Computing (IRC)},
     pages={to appear},
@@
 \author{
-  Adam Seewald$^{*}$, Hector Garcia de Marina, and Ulrik Pagh Schultz
-  \thanks{$^{*}$Corresponding author; email: {\tt\small ads@mmmi.sdu.dk}}
-  \thanks{Adam Seewald, Ulrik Pagh Schultz are with the SDU UAS Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense, Denmark.}
-  \thanks{Hector Garcia de Marina is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
+  Adam Seewald$^{1}$, Hector Garcia de Marina$^{2}$, and Ulrik Pagh Schultz$^{1}$
+  \thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).
+  }
+  \thanks{$^{1}$Adam Seewald, Ulrik Pagh Schultz are with the SDU UAS Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense, Denmark.
+Email: {\tt\small ads@mmmi.sdu.dk}.}
+  \thanks{$^{2}$Hector Garcia de Marina is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
 }
@@
 The presented approach proposes a \emph{mission-aware energy planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the robot's energy consumption and autonomy.
-The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs).
-The approach ideally accounts for a mission extension by adapting the TEEs and QoS as the robot batteries drain.
+The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters.
+The approach ideally accounts for a mission extension by adapting the QoS and TEEs parameters as the robot batteries drain.
 
@@
 
-Given a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which affects the position allowing the motion along the 3-axis--is built upon the direction to follow, derived using vector field~\cite{de2017guidance}.
+Starting with a position in space $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
+To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).
 
----
+The energy evolution $\mathbf{q}\in\mathbb{R}^j$ spent to perform such guidance action is described using Fourier analysis (the meaning of $j$ will be explained to the reader in Subsection~\ref{sec:energy-model}) and is decomposed in the energy due to the trajectory (TEEs), and the computations (QoS)--an approach that has been adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing craft~\cite{seewald2020mechanical}.
 
-%The motion defines a trajectory and a position $\mathbf{p}$; the trajectory is expressed through explicit trajectory equation $\varphi$, while the position determines a vehicle frame $\mathcal{O}_V$ in the 2D Euler space relative to an inertial frame $\mathcal{O}_W$.
-For the sake of simplicity, it is assumed that the $z$-axis is constrained to a specific altitude $h$, with the system being free to evolve in the $x,y$-axes (i.e., the drone is flying, performing a mission, at a given height).
-A motion guidance action is derived using vector field design, enabling the convergence to the desired trajectory anywhere in $\mathcal{O}_W$.
+\subsection{Position in space and guidance action}
+\label{sec:position}
 
-%The energy $\mathbf{q}$ spent to perform such guidance action is later derived using Fourier analysis in its state-space representation.
-This component is decomposed in the energy needed for the actuation (i.e., the mechanical energy), and the computations (i.e., the computational energy), an approach that has been extensively reviewed in our previous work~\cite{seewald2019coarse, seewald2019component, seewald2020mechanical}.
-A control action, which varies quality of service (QoS) levels of the software being executed, is derived for this purpose.
-The main goal is to tune the explicit energy equation allowing to maximize the computational and mechanical outcome of the mission while trying to minimize the eventuality of battery discharge.
-
-\subsection{Motion and Guidance Model}
-The position $\mathbf{p}$, derived from~\cite{de2017guidance}, is described using the following non-holonomic model
+For exemplification, we consider a non-holonomic 2D model of a fixed-wing craft flying at an assigned altitude $h\in\mathbb{R}_{>0}$.
+We will show, after the results, the requirement being eased to an arbitrary mobile robot model
 \begin{equation}\label{eqq:1}\begin{cases}
   \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+w(t)\\
-  \dot{\psi}(t)&=u(t)
+  \dot{\psi}(t)&=u(\mathbf{p}(t))
 \end{cases},
 \end{equation}
-where $\mathbf{p}(t)\in\mathbb{R}^2$ is a point in $\mathcal{O}_W$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of $\mathcal{O}_V$.
+where $\mathbf{p}(t)\in\mathbb{R}^2$ (against a more generic $\mathbb{R}^3$ introduced earlier), $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of the craft.
 
-Let us define a generic continuously differentiable function $\varphi:\mathbb{R}^2\rightarrow\mathbb{R}$. The desired trajectory $\mathcal{P}$ can be defined
+Let us define $\mathcal{P}$ the area which discloses all the possible paths within the boundaries $\underline{c}\in\mathbb{R}_{\leq 0},\overline{c}\in\mathbb{R}_{\geq 0}$
 \begin{equation}\label{eqq:2}
-  \mathcal{P}:=\{\mathbf{p}:\|\varphi(\mathbf{p})\|<c+\varepsilon\},
+  \mathcal{P}:=\{\mathbf{p}:\underline{c}\leq\varphi(\mathbf{p})\leq\overline{c}\},
 \end{equation}
-as the set of points that follows an explicit trajectory equation $\varphi(\mathbf{p})=c$ within a given $\varepsilon\in\mathbb{R}_{\geq 0}$.
+where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
 
-Given a set of discrete values $c$, $\mathcal{O}_W$ can be covered by all the trajectories $\mathcal{P}$ within specific boundaries $\underline{c}\leq c\leq \overline{c}$, where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
+The concept of area between the bounds is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints.
+Here we design a guidance action $u$ that allows following $\varphi$ in such area by the means of minimizing the norm $\|\varphi(\mathbf{p})\|$.
 
-The concept of a trajectory is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints.
-Here we design a guidance action $u$ that allows following such trajectory.
-The guidance is derived using the vector field approach also presented in~\cite{de2017guidance}.
-The algorithm heads to $\mathcal{P}$ by the means of minimizing the norm in Equation~(\ref{eqq:2}).
-
-Let us define $\varPhi:=\varphi(\mathbf{p})$. The vector field is defined as the desired velocity vector
+Let us define $\varPhi:=\varphi(\mathbf{p})$. The direction to follow is expressed as the desired velocity vector
 \begin{equation}\label{eqq:3}
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence of the vector field to the desired trajectory.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence.
 
@@
 \begin{equation}\label{eqq:4}\begin{split}
-  &\dot{\chi}(\dot{\mathbf{p}},\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
+  &\dot{\chi}(\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
   &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^T\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,
@@
 \begin{equation}\label{eqq:5}
-  u(\dot{\mathbf{p}},\mathbf{p},\psi)=\frac{\|\mathbf{p}\|}{s\cos{\beta}}\left( \dot{\mathbf{\chi}}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
+  u(\mathbf{p},\psi)=\frac{\|\mathbf{p}\|}{s\cos{\beta}}\left( \dot{\mathbf{\chi}}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
 \end{equation} 
@@
 
-\subsection{Energy Model}
+\subsection{Energy evolution due to trajectory}
+\label{sec:energy-model}
 
-To evaluate the energy spent performing given actuation and computations we consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r$
+To evaluate the energy spent due to trajectory and computations, let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
 \begin{equation}\label{eqq:6}
@@
 where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.
-The Fourier analysis allows accounting for the periodicity of the mission, with a trajectory $\mathcal{P}$ being reiterated over time.
 
@@
 \begin{equation}\label{eqq:7}\begin{cases}
-  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t)\\
-  y(t)&=C\mathbf{q}(t)+v(t)
+  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)\\%+w(t)\\
+  y(t)&=C\mathbf{q}(t)%+v(t)
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise.
-The control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently.
-The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix
-\begin{equation}\begin{split}
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled.
+The control $\mathbf{u}$ along with the input matrix $B$ are defined later in Subsection~\ref{sec:control-action}, the state $\mathbf{q}$ mimics the original Fourier series coefficients, and
+\begin{equation}\label{eqq:8}\begin{split}
   \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
@@
 
-Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equation~(\ref{eqq:1})~and~(\ref{eqq:7})
+Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equation~(\ref{eqq:7}) and add the uncertainty
 \begin{subequations}\label{eqq:9}\begin{align}
@@
   \mathbf{p}_{k+1}&=s\Psi(\psi_k)+w_k\\
-  \psi_{k+1}&=u_k
+  \psi_{k+1}&=u_k(p_k)
   \end{cases},\\
@@
   y_k&=C\mathbf{q}_k+v_k
-  \end{cases}.
+  \end{cases},
 \end{align}\end{subequations}
+where $w_k\in\mathbb{R}$ accounts for the environment uncertainty, and $v_k\in\mathbb{R}$ for the measurement error.
 
-As the system was observed to behave stochastically, with the process and measurement noise evolving in a normal distribution, a Kalman filter~\cite{stengel1994optimal, simon2006optimal} is employed to predict the state $\hat{\mathbf{q}}$.
-Such a state, along with the predicted output $\hat{y}$, differs from the model state $\mathbf{q}$ and measured output $y$ in Equation~(\ref{eqq:9b}) due to the presence of uncertainty.
+The instantaneous energy can be obtained from the model~(\ref{eqq:9b}) as a linear combination of the state.
 
-The prediction is done using
-\begin{subequations}\label{eqq:10}\begin{align}
-  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eqq:10a}\\
-  P_{k+1}^-&=AP_kA^T+Q,\label{eqq:10b}
-\end{align}\end{subequations}
-where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
+\begin{lem}\label{lem:2.1}
+  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eqq:8}) along their evolution~(\ref{eqq:9b}) at time instant $k$ depends on the instantaneous energy consumption.
+Suppose the two behave ideally (with no environment uncertainty and measurement error)
+  \begin{equation}
+    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,0}\|\iff y_{k,0}\geq y_{k,1}.
+  \end{equation}
+\end{lem}
+\begin{proof}
+  *\\
+\end{proof}
 
-The estimation of the state and the update of the predicted output is done using
-\begin{subequations}\label{eqq:11}\begin{align}
-  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
-  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
-  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
-\end{align}
-\end{subequations}
-where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
-$y_k^s,y_k^c$ are the energy readings: $y_k^s$ the flight controller sensor, i.e., the energy needed for the actuation, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eqq:13}) later in this section.
-The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
+\begin{thm}\label{thm:2.2}
+  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
+  Assume a mobile robot performs a periodic mission free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise Lemma~\ref{lem:2.1}, the model behaves ideally. 
+  Then the instantaneous energy is a linear combination of the state
+  \begin{equation}
+    y_k=C\mathbf{q}_k=\sum_{n=0}^r{a_n},
+  \end{equation}
+  where $a_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a pre-assigned arbitrary order, and $C$ is described by Equation~(\ref{eqq:8}).
+\end{thm}
+\begin{proof}
+  *\\
+\end{proof}
 
-Equations~(\ref{eqq:10}--\ref{eqq:11}) converge to the predicted energy evolution as follows.
-An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
-It is worth considering that an appropriate guess of these parameters allows the system to converge to the desired energy evolution in a shorter amount of time.
-The tuning parameters $Q,R$ are also derived from the collected data, and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
+\subsection{Energy evolution due to computations}
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
-The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (we use the energy sensor of the flight controller), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
-The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
-The algorithm is iterative.
-At time $k=1$ the values $\hat{\mathbf{q}}_1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
-
-In the light of Equations~(\ref{eqq:9}--\ref{eqq:11}), the main goal stated earlier in this section can be updated.
-We aim to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$~\cite{rawlings2017model}.
-This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) algorithm derived in the next section.
-Before, we need to define a generic control action $\mathbf{u}$.
-
-\subsection{Computational Model}
-
-A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically software configurations and builds an energy model accordingly~\cite{seewald2019coarse}.
+A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically software configurations and builds an energy model, presented in authors' previous work~\cite{seewald2019coarse}.
 Specifically, the tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
@@
 
-\subsection{Control Action}
+\subsection{Control action}
+\label{sec:control-action}
 
@@
 
+\section{Algorithm}
+
+\subsection{State estimation}
+
+As the environment uncertainty and measurement error evolve in a normal distribution, we use a Kalman filter~\cite{stengel1994optimal, simon2006optimal} for the purpose of state estimation.
+
+The prediction is done using
+\begin{subequations}\label{eqq:10}\begin{align}
+  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eqq:10a}\\
+  P_{k+1}^-&=AP_kA^T+Q,\label{eqq:10b}
+\end{align}\end{subequations}
+where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
+
+The estimation of the state and the update of the predicted output is done using
+\begin{subequations}\label{eqq:11}\begin{align}
+  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
+  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
+  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
+  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
+\end{align}
+\end{subequations}
+where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
+$y_k^s,y_k^c$ are the energy readings: $y_k^s$ the flight controller sensor, i.e., the energy needed for the actuation, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eqq:13}) later in this section.
+The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the uncertainty and measurement error covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
+
+Equations~(\ref{eqq:10}--\ref{eqq:11}) converge to the predicted energy evolution as follows.
+An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
+It is worth considering that an appropriate guess of these parameters allows the system to converge to the desired energy evolution in a shorter amount of time.
+The tuning parameters $Q,R$ are also derived from the collected data, and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
+
+At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
+The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (we use the energy sensor of the flight controller), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
+The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
+The algorithm is iterative.
+At time $k=1$ the values $\hat{\mathbf{q}}_1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
+
+In the light of Equations~(\ref{eqq:9}--\ref{eqq:11}), the main goal stated earlier in this section can be updated.
+We aim to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$~\cite{rawlings2017model}.
+This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) algorithm derived in the next section.
+Before, we need to define a generic control action $\mathbf{u}$.
+
+\subsection{Optimal control action}
+
+*
+
+\subsection{Deployment algorithm}
+
+*
+
 %%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgment}
-
-This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).
-
 \bibliographystyle{IEEEtran}
@@
 
+\newpage
+
 \end{document}

### 2020-09-09 icra-2021.tex
friday's countdown (aka preparing a stable version for internal review [2])

@@
 \newtheorem{prop}[thm]{Proposition}
+\newtheorem{assm}[thm]{Assumption}
 \newtheorem{cor}{Corollary}
@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 
-To evaluate the energy spent due to trajectory and computations, let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
+To evaluate the energy spent due to trajectory and computations, we formalize the following realistic assumption introduced in Section~\ref{sec:intro}.
+\begin{assm}\label{assm:2.1}
+The mission the mobile robots perform is periodic, in the sense that it presents repetitive patterns.
+\end{assm}
+
+Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
 \begin{equation}\label{eqq:6}
@@
   Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
-  Assume a mobile robot performs a periodic mission free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise Lemma~\ref{lem:2.1}, the model behaves ideally. 
-  Then the instantaneous energy is a linear combination of the state
+  Assume Assumption~\ref{assm:2.1} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise in Lemma~\ref{lem:2.1}, the model behaves ideally. 
+  Then, the instantaneous energy consumption is a linear combination of the state
   \begin{equation}
@@
 The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
-\begin{equation}\begin{split}
-  \mathbf{u}_k&=\left[\begin{array}{cc}
-    g\left(\mathcal{C}_k\right) & \mathcal{M}_k
-  \end{array}\right]^T,\\
-  B&=\left[\begin{array}{ccccccc}
+\begin{equation}
+  \mathbf{u}_k=\left[\begin{array}{c}
+    g\left(\mathcal{C}_k\right) \\\hline \mathcal{M}_k
+  \end{array}\right],\,\,\,
+  B=\left[\begin{array}{ccccccc}
     1 & \vline & 0 & \cdots & 0\\\hline
@@
   \end{array}\right],
-\end{split}
 \end{equation}
@@
 \section{Algorithm}
+
+*
 

### 2020-09-10 icra-2021.tex
friday's countdown (aka preparing a stable version for internal review [3])

@@
 
+The algorithm relies on the assumptions of the mission--a set of tasks the mobile robot is supposed to perform--being \emph{periodic} and \emph{uncertain}.
+The periodicity is directly observed by e.g., the mobile robot traveling in repetitive patterns executing a set of assigned tasks, and the uncertainty accounts for the environmental interference, with e.g., a fixed-wing craft drifting due to windy weather.
+The algorithm proposes a Fourier series to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to address the uncertainty assumption.
+
 Energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning.
@@
 
-The algorithm relies on the assumptions of the mission--a set of tasks the mobile robot is supposed to perform--being \emph{periodic} and \emph{uncertain}.
-The periodicity is directly observed by e.g., the mobile robot traveling in repetitive patterns executing a set of assigned tasks, and the uncertainty accounts for the environmental interference, with e.g., a fixed-wing drone drifting due to windy weather.
-The algorithm proposes a Fourier series to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to address the uncertainty assumption.
+% [Ad:] I am actually thinking whenever I should put a section with problem statement or I can just leave it nicely in the model?
 
-% Robots critically depend on battery for the completion of their mission, the duration of which is proportional to the state of the power source
-
-% Modeling mechanical and computational energy separately allows tradeoffs between the two to be expressed, such as performing additional onboard computations to reduce the amount of mechanical energy needed to complete the mission.
-
-% The increasing demand for autonomy, challenge the traditional computational model and perhaps justify the presented approach.
-
-% Preliminary data using a terrestrial fixed-wing craft indicates a potential mission extension of up to 13 minutes over 1 hour flight by switching to the lowest QoS, with the computations accounting for up to 23% of the total energy.
-The approach ideally accounts for the extension by adapting the trajectory and the computations as the robot batteries drain.
-
-%%%%%%%%%%%%%%%%%%%%%%
-%\section{State of the Art}
-%\label{sec:related}
-
-%*
-% equation number just just for illustrate the reader just to introduce and support - this is an offline method
-% but we need it in real time while we are flying
-% we write number one as number 4
-% one of the things is to figure out what are the states
-% t
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% once the introduction 
+%%%%%%%%%%%%%%%
 \section{Model}
-\label{sec:estimation}
+\label{sec:model}
 
@@
 
-Starting with a position in space $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
+Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
 To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).
 
-The energy evolution $\mathbf{q}\in\mathbb{R}^j$ spent to perform such guidance action is described using Fourier analysis (the meaning of $j$ will be explained to the reader in Subsection~\ref{sec:energy-model}) and is decomposed in the energy due to the trajectory (TEEs), and the computations (QoS)--an approach that has been adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing craft~\cite{seewald2020mechanical}.
+The energy evolution $\mathbf{q}\in\mathbb{R}^j$ spent to perform such guidance action is derived using Fourier analysis (the meaning of $j$ will be explained to the reader in Subsection~\ref{sec:energy-model}) and is decomposed in the energy due to the trajectory (TEEs), and the computations (QoS)--an approach that has been adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing craft~\cite{seewald2020mechanical}.
 
@@
 We will show, after the results, the requirement being eased to an arbitrary mobile robot model
-\begin{equation}\label{eqq:1}\begin{cases}
-  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+w(t)\\
+\begin{equation}\label{eq:uav-kinem}\begin{cases}
+  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+d(t)\\
   \dot{\psi}(t)&=u(\mathbf{p}(t))
@@
 \end{equation}
-where $\mathbf{p}(t)\in\mathbb{R}^2$ (against a more generic $\mathbb{R}^3$ introduced earlier), $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of the craft.
+where $\mathbf{p}(t)\in\mathbb{R}^2$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, $d$ is the wind vector where we assume $\|d\|<s$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of the craft.
 
 Let us define $\mathcal{P}$ the area which discloses all the possible paths within the boundaries $\underline{c}\in\mathbb{R}_{\leq 0},\overline{c}\in\mathbb{R}_{\geq 0}$
-\begin{equation}\label{eqq:2}
+\begin{equation}\label{eq:area}
   \mathcal{P}:=\{\mathbf{p}:\underline{c}\leq\varphi(\mathbf{p})\leq\overline{c}\},
@@
 Let us define $\varPhi:=\varphi(\mathbf{p})$. The direction to follow is expressed as the desired velocity vector
-\begin{equation}\label{eqq:3}
+\begin{equation}\label{eq:pd}
   \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
@@
 Let us further define $\hat{\mathbf{p}}:=\mathbf{p}/\|\mathbf{p}\|$, the desired course heading rate $\dot{\chi_d}$ is computed by sensing the position $\mathbf{p}$, the ground velocity $\dot{\mathbf{p}}$, and is expressed
-\begin{equation}\label{eqq:4}\begin{split}
-  &\dot{\chi}(\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
-  &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^T\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,
+\begin{equation}\label{eq:chid}\begin{split}
+  &\dot{\chi}_d(\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
+  &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^TE\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,
 \end{split}
@@
 Under the assumption of the airspeed $s>\|w(t)\|$ for $t>0$ (i.e., the constant airspeed is greater than the norm of the wind), the guidance action can be expressed
-\begin{equation}\label{eqq:5}
-  u(\mathbf{p},\psi)=\frac{\|\mathbf{p}\|}{s\cos{\beta}}\left( \dot{\mathbf{\chi}}_d(\dot{\mathbf{p}},\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
+\begin{equation}\label{eq:uav-cont}
+  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d(\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
 \end{equation} 
-where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of $\dot{\mathbf{p}}_d$, $\beta=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eqq:4}).
+where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of $\dot{\mathbf{p}}_d$, $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eq:chid}).
 
@@
 
-To evaluate the energy spent due to trajectory and computations, we formalize the following realistic assumption introduced in Section~\ref{sec:intro}.
-\begin{assm}\label{assm:2.1}
+To evaluate the energy we formalize the following realistic assumption introduced in Section~\ref{sec:intro}.
+\begin{assm}\label{assm:periodic}
 The mission the mobile robots perform is periodic, in the sense that it presents repetitive patterns.
@@
 Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
-\begin{equation}\label{eqq:6}
+\begin{equation}\label{eq:fourier}
   f(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
@@
 
-The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent time-varying state-space model in the following form
-\begin{equation}\label{eqq:7}\begin{cases}
+The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent time-varying state-space model in the following form
+\begin{equation}\label{eq:state-perf}\begin{cases}
   \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)\\%+w(t)\\
@@
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled.
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy evolution of the system being controlled.
+We will see later in the Theorem~\ref{thm:state-vs-energy} that the instantaneous energy can be obtained from the model as a linear combination of the state.
 The control $\mathbf{u}$ along with the input matrix $B$ are defined later in Subsection~\ref{sec:control-action}, the state $\mathbf{q}$ mimics the original Fourier series coefficients, and
-\begin{equation}\label{eqq:8}\begin{split}
+\begin{equation}\label{eq:state-details}\begin{split}
   \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
-    a_0 & \vline & a_1 & b_1 & \cdots & a_r & b_r
+    \alpha_0 & \vline & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
   \end{array}\right]^T,\\
@@
 
-Motivated by the fact that the system of interest is sampled discrete-time, and for the sake of simplicity, we consider the discretized version of Equation~(\ref{eqq:7}) and add the uncertainty
-\begin{subequations}\label{eqq:9}\begin{align}
-  &\begin{cases}\label{eqq:9a}
-  \mathbf{p}_{k+1}&=s\Psi(\psi_k)+w_k\\
-  \psi_{k+1}&=u_k(p_k)
-  \end{cases},\\
-  &\begin{cases}\label{eqq:9b}
+Motivated by the fact that the system of interest is sampled discrete-time, we consider the discretized version of Equation~(\ref{eq:state-perf}) and add the uncertainty
+\begin{equation}\label{eq:state-unct}
+  \begin{cases}
   \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k\\
@@
   \end{cases},
-\end{align}\end{subequations}
+\end{equation}
 where $w_k\in\mathbb{R}$ accounts for the environment uncertainty, and $v_k\in\mathbb{R}$ for the measurement error.
 
-The instantaneous energy can be obtained from the model~(\ref{eqq:9b}) as a linear combination of the state.
+The instantaneous energy can be obtained from the model~(\ref{eq:state-unct}) as a linear combination of the state.
 
-\begin{lem}\label{lem:2.1}
-  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eqq:8}) along their evolution~(\ref{eqq:9b}) at time instant $k$ depends on the instantaneous energy consumption.
-Suppose the two behave ideally (with no environment uncertainty and measurement error)
+\begin{lem}\label{lem:state-vs-energy}
+  Suppose the system behaves ideally (with no environment uncertainty and measurement error).
+  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eq:state-details}) along their evolution~(\ref{eq:state-unct}) at time instant $k$ depends on the instantaneous energy consumption
   \begin{equation}
@@
 
-\begin{thm}\label{thm:2.2}
-  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
-  Assume Assumption~\ref{assm:2.1} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise in Lemma~\ref{lem:2.1}, the model behaves ideally. 
-  Then, the instantaneous energy consumption is a linear combination of the state
-  \begin{equation}
-    y_k=C\mathbf{q}_k=\sum_{n=0}^r{a_n},
-  \end{equation}
-  where $a_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a pre-assigned arbitrary order, and $C$ is described by Equation~(\ref{eqq:8}).
-\end{thm}
-\begin{proof}
-  *\\
-\end{proof}
+\subsection{Energy evolution due to computations}
+\label{sec:computations-model}
 
-\subsection{Energy evolution due to computations}
-
-A computational energy model is built using \powprof{}\footnote{\label{cross-ref:powprof-link}\url{https://bitbucket.org/adamseew/powprofiler}}, an open-source modeling tool that measures empirically software configurations and builds an energy model, presented in authors' previous work~\cite{seewald2019coarse}.
+A computational energy model is built using \powprof{}, an open-source modeling tool that measures empirically software configurations and builds an energy model, presented in authors' previous work~\cite{seewald2019coarse}.
 Specifically, the tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
@@
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
-The computational energy component can be defined
+The instantaneous computational energy component can be defined
 \begin{equation}\label{eqq:13}\begin{split}
@@
 The QoS parameters $\mathcal{C}_k$ can be subject to different constraints at different states.
-Physically, this means that the drone can perform the ROS nodes within different QoS ranges while flying different phases of a mission
+Physically, this means that the robot can perform the ROS nodes within different QoS ranges while flying different phases of a mission
 \begin{equation}\label{eqq:14}
@@
 
-The control action is constructed in two steps.
+The control action is built in two steps.
 Equation~(\ref{eqq:12}) defines the control due to the computations.
-The control due to the actuation, which describes the energy of the mechanical elements of the drone $\mathcal{M}$, is derived in the following subsection.
+The control due to the trajectory is specific to the system being analyzed, for instance on the model of the fixed-wing craft in~(\ref{eq:uav-kinem}), along its control in Equation~(\ref{eq:chid})~and~(\ref{eq:uav-cont}).
+A generalization which accounts for the variations in the TEE $\varphi$ of a generic model by means of the TEEs parameters is derived in the following subsection.
 
@@
 \end{equation}
-where $c$ is defined in Equation~(\ref{eqq:2}), and $\mathbf{p}^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
+where $c$ is defined in Equation~(\ref{eq:area}), and $\mathbf{p}^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
 
-The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equation~(\ref{eqq:3})~and~(\ref{eqq:5}) respectively, will account for the sudden change of trajectory during the mission.
+The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equation~(\ref{eq:pd})~and~(\ref{eq:uav-cont}) respectively, will account for the sudden change of trajectory during the mission.
 Alike Equation~(\ref{eqq:14}), the parameters $\mathbf{u}_k=\{u_{k,1},\dots,u_{k,\rho_k}\}$ at time $k$ are constrained
@@
 
-The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
+The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eq:state-unct}) using the input matrix
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}).
+where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eq:state-perf})~and~(\ref{eq:state-unct}).
 Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$.
-This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}).
+This adds the computational model component to the energy evolution in the system in Equation~(\ref{eq:state-unct}).
 The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
@@
 *
+
+\begin{thm}\label{thm:state-vs-energy}
+  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
+  Assume Assumption~\ref{assm:periodic} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eq:area}), and is following $\varphi$ with the direction $\hat{\mathbf{p}}_d$ defined in~\ref{eq:pd}.
+Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.
+  Then, the instantaneous energy consumption is a linear combination of the state
+  \begin{equation}
+    y_k=C\mathbf{q}_k=\sum_{n=0}^r{\alpha_n},
+  \end{equation}
+  where $\alpha_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a preassigned arbitrary order from~(\ref{eq:fourier}), and $C$ is described by Equation~(\ref{eq:state-details}).
+\end{thm}
+\begin{proof}
+  *\\
+\end{proof}
 

### 2020-09-10 icra-2021.tex
friday's countdown (well, at least I tried)

@@
 Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action
-\begin{equation}\label{eqq:12}
-  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma\}\right\},
+\begin{equation}\label{eq:qos-def}
+  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma-1\}\right\},
 \end{equation}
@@
 The instantaneous computational energy component can be defined
-\begin{equation}\label{eqq:13}\begin{split}
-  y_k^c:&=g\left(\text{QoS}_0\left(k\right),\dots,\text{QoS}_\sigma\left(k\right)\right)=g\left(\mathcal{C}_{k}\right).\\
+\begin{equation}\label{eq:energy-comp}\begin{split}
+  y_k^c:&=g\left(\text{QoS}_0\left(k\right),\dots,\text{QoS}_{\sigma-1}\left(k\right)\right)=g\left(\mathcal{C}_{k}\right).\\
 \end{split}\end{equation}
@@
 Physically, this means that the robot can perform the ROS nodes within different QoS ranges while flying different phases of a mission
-\begin{equation}\label{eqq:14}
-  \underline{\text{QoS}}_n(k)\leq \text{QoS}_n(k)\leq \overline{\text{QoS}}_n(k),\,\forall n\in\{0,\cdots,\sigma\},
-\end{equation}
+\begin{equation}\label{eq:qos-lims}\begin{split}
+  \underline{\text{QoS}}_n(k)\leq \,&\text{QoS}_n(k)\leq \overline{\text{QoS}}_n(k),\\
+  &\forall n\in\{0,\cdots,\sigma-1\},
+\end{split}\end{equation}
 where the values $\underline{\text{QoS}}_n(k),\overline{\text{QoS}}_n(k)$ are retrieved from the mission specification.
@@
 The control action is built in two steps.
-Equation~(\ref{eqq:12}) defines the control due to the computations.
+Equation~(\ref{eq:qos-def}) defines the control due to the computations.
 The control due to the trajectory is specific to the system being analyzed, for instance on the model of the fixed-wing craft in~(\ref{eq:uav-kinem}), along its control in Equation~(\ref{eq:chid})~and~(\ref{eq:uav-cont}).
@@
 
-Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
-The set of these parameters can be expressed
-\begin{equation}\label{eqq:14}
-  \mathcal{M}_k:=\{\mathbf{u}_k : \varphi_k(\mathbf{p}_k^0,\mathbf{u}_k)=c_k\},
-\end{equation}
-where $c$ is defined in Equation~(\ref{eq:area}), and $\mathbf{p}^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge to the value $c$ (i.e., points over the trajectory).
+Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ TEE parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
+Let us define $\mathbf{u}_{k,n}:=\{u_{k,0},\dots,u_{k,n-1},u_{k,n}^0,u_{k,n+1},\dots,u_{k,\rho_k-1}\}$, the set of these parameters can be expressed
+\begin{equation}\label{eq:tee-def}\begin{split}
+  \mathcal{M}_k:=\{u_{k,n} : \,
+  &\varphi_k(\mathbf{p}_{k,n}^0,\mathbf{u}_{k,n})\in\mathcal{P}\\
+  &\forall n\in\{0,\dots,\rho_k-1\}\},
+\end{split}\end{equation}
+where $\mathbf{p}_k^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge under any optimal TEE parameter $u_k^0$.
+Physically $\mathcal{M}_k$ contains all the controls generating the points over the area $\mathcal{P}$ defined in Equation~(\ref{eq:area}).
 
 The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equation~(\ref{eq:pd})~and~(\ref{eq:uav-cont}) respectively, will account for the sudden change of trajectory during the mission.
-Alike Equation~(\ref{eqq:14}), the parameters $\mathbf{u}_k=\{u_{k,1},\dots,u_{k,\rho_k}\}$ at time $k$ are constrained
-\begin{equation}
-  \underline{u}_{k,n}\leq u_{k,n}\leq \overline{u}_{k,n}\,\forall n\in\{0,\cdots,\rho_k\},
-\end{equation}
-where the values $\underline{u}_{k,n},\overline{u}_{k,n}$ are also retrieved from the mission specification.
 
@@
 This is for the sake of generality, as the mission specification might contain different explicit equations for different states.
-For instance, the drone might follow an ellipse function throughout the mission and heading a linear function while landing.
+For instance, the fixed-wing craft might follow an ellipse function throughout the mission and heading a linear function while landing.
 
-The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eq:state-unct}) using the input matrix
+The TEE parameters and QoS, $\mathcal{M}$ and $\mathcal{C}$ defined in Equation~(\ref{eq:tee-def})~and~(\ref{eq:qos-def}), are incorporated in the system in Equation~(\ref{eq:state-unct}) using the input matrix
 \begin{equation}
@@
 Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$.
-This adds the computational model component to the energy evolution in the system in Equation~(\ref{eq:state-unct}).
-The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
+This adds the computational model component to the energy evolution in the system.
+The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors $y^s$ defined in Subsection~\ref{sec:state-est} and adjust the energy evolution accordingly.
 
@@
 
-*
+The main goal of the algorithm is to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$--estimated from sensors' measurements--from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$.
+This is achieved by solving online a finite horizon optimal control problem by the hand of a modification of a model predictive control (MPC) algorithm~\cite{rawlings2017model}.
+
+Let us proof formally an important finding from Section~\ref{sec:model} extensively used in the algorithm.
+
+% [Ad:] I am actually not entirely sure if the thm should be here (and if it makes sense).
+Aka proving formally that what we do is actually what we expect; so perhaps it does make sense but I would like your opinion before spending time on the demonstrations...
+Same for the lemma.
+% [Ad:] And here I had the doubt if to place the thm just straight after the lemma or here.
+I places it here as this is actually the main contribution -> the energy model working.
+Does it make any sense?
 
@@
   \end{equation}
-  where $\alpha_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a preassigned arbitrary order from~(\ref{eq:fourier}), and $C$ is described by Equation~(\ref{eq:state-details}).
+  where $\alpha_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a preassigned arbitrary order from~(\ref{eq:fourier}), and $C$ is described in Equation~(\ref{eq:state-details}).
 \end{thm}
@@
 \subsection{State estimation}
+\label{sec:state-est}
 
@@
 The prediction is done using
-\begin{subequations}\label{eqq:10}\begin{align}
-  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eqq:10a}\\
-  P_{k+1}^-&=AP_kA^T+Q,\label{eqq:10b}
+\begin{subequations}\label{eq:kalman-pred}\begin{align}
+  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:kalman-pred1}\\
+  P_{k+1}^-&=AP_kA^T+Q,\label{eq:kalman-pred2}
 \end{align}\end{subequations}
@@
 The estimation of the state and the update of the predicted output is done using
-\begin{subequations}\label{eqq:11}\begin{align}
+\begin{subequations}\label{eq:kalman-est}\begin{align}
   K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
+  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:kalman-est2}\\
   P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
-  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
+  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:kalman-est4}
 \end{align}
@@
 where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
-$y_k^s,y_k^c$ are the energy readings: $y_k^s$ the flight controller sensor, i.e., the energy needed for the actuation, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eqq:13}) later in this section.
+$y_k^s,y_k^c$ are the instantaneous energy readings: $y_k^s\in\mathbb{R}_{\geq 0}$ the robot sensor, i.e., the energy due to the trajectory, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eq:energy-comp}).
 The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the uncertainty and measurement error covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
 
-Equations~(\ref{eqq:10}--\ref{eqq:11}) converge to the predicted energy evolution as follows.
+Equations~(\ref{eq:kalman-pred}--\ref{eq:kalman-est}) converge to the predicted energy evolution as follows.
 An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
-It is worth considering that an appropriate guess of these parameters allows the system to converge to the desired energy evolution in a shorter amount of time.
+It is worth considering that an appropriate guess of these parameters allows the algorithm to converge to the desired energy evolution in a shorter amount of time.
 The tuning parameters $Q,R$ are also derived from the collected data, and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eqq:10a})~and~(\ref{eqq:10b}) respectively.
-The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eqq:11b}) to estimate the current state along with the data from the sensor $y_0$ (we use the energy sensor of the flight controller), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
-The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eqq:11d}).
+At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:kalman-pred1})~and~(\ref{eq:kalman-pred2}) respectively.
+The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eq:kalman-est2}) to estimate the current state along with the data from the sensor $y_0$ (e.g., the energy sensor of the flight controller of the fixed-wing craft), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
+The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eq:kalman-est4}).
 The algorithm is iterative.
 At time $k=1$ the values $\hat{\mathbf{q}}_1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
-
-In the light of Equations~(\ref{eqq:9}--\ref{eqq:11}), the main goal stated earlier in this section can be updated.
-We aim to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$ from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$~\cite{rawlings2017model}.
-This is achieved by solving online a finite horizon optimal control problem by the hand of a model predictive control (MPC) algorithm derived in the next section.
-Before, we need to define a generic control action $\mathbf{u}$.
 

### 2020-09-17 icra-2021.tex
stating the problem (1)

@@
 
-Mobile robots are increasingly used in a broad range of applications.
-The growing demand for autonomy of such devices challenges traditional methodologies, soliciting the development of new and unprecedented techniques.
-The presented approach proposes a \emph{mission-aware energy planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the robot's energy consumption and autonomy.
+Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}.
+Although researchers have satisfied some of these demands applying mobile robots in applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, more complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Planning a mission for UAVs operating in such scenarios is a challenging task.
+It usually requires advanced levels of autonomy--with the UAV being required e.g., to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
+The presented approach proposes a \emph{mission-aware energy planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption and autonomy.
+
+---
+
 The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters.
@@
 
-Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euler space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
+Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
 To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).

### 2020-09-21 icra-2021.tex
some changes in the introduction

@@
   }
+  @inproceedings{daponte2019review,
+    title={A review on the use of drones for precision agriculture},
+    author={Daponte, Pasquale and De Vito, Luca and Glielmo, Luigi and Iannelli, Luigi and Liuzza, Davide and Picariello, Francesco and Silano, Giuseppe},
+    booktitle={IOP Conference Series: Earth and Environmental Science},
+    volume={275},
+    number={1},
+    pages={012022},
+    year={2019},
+    organization={IOP Publishing}
+  }
 
@@
 Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}.
-Although researchers have satisfied some of these demands applying mobile robots in applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, more complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Researchers have fulfilled some of these demands applying mobile robots in agricultural applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 Planning a mission for UAVs operating in such scenarios is a challenging task.
-It usually requires advanced levels of autonomy--with the UAV being required e.g., to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
-The presented approach proposes a \emph{mission-aware energy planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption and autonomy.
-
----
+It usually requires advanced levels of autonomy--with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
+Currently, UAVs in precision agriculture use-cases are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
+The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.
 
 The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters.
-The approach ideally accounts for a mission extension by adapting the QoS and TEEs parameters as the robot batteries drain.
+The approach ideally accounts for a mission extension by adapting the QoS and TEEs as the UAV batteries drain.
+Preliminary data using a terrestrial fixed-wing UAV indicates a potential extension of up to 13 minutes over 1 hour by switching to the lowest QoS.
 
-The algorithm relies on the assumptions of the mission--a set of tasks the mobile robot is supposed to perform--being \emph{periodic} and \emph{uncertain}.
-The periodicity is directly observed by e.g., the mobile robot traveling in repetitive patterns executing a set of assigned tasks, and the uncertainty accounts for the environmental interference, with e.g., a fixed-wing craft drifting due to windy weather.
-The algorithm proposes a Fourier series to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to address the uncertainty assumption.
+The algorithm relies on the assumptions of the mission--a path and a set of tasks the UAV is supposed to perform--being \emph{periodic} and \emph{uncertain}.
+The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
+We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to cope with the uncertainty assumption.
+The algorithm selects the controls--the QoS and TEEs--dynamically using a modified tube-based output model predictive control (MPC), which ensures that state estimation error does not result in transgression of the control and state constraints.
 
-Energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning.
-Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a specific class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
+Although underrepresented in precision agriculture and related literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning.
+Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
 In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands through a mission-aware perspective.
+Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
 Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-
-% [Ad:] I am actually thinking whenever I should put a section with problem statement or I can just leave it nicely in the model?
 

### 2020-09-21 icra-2021.tex
some changes in the introduction (2)

@@
 Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}.
-Researchers have fulfilled some of these demands applying mobile robots in agricultural applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 Planning a mission for UAVs operating in such scenarios is a challenging task.
-It usually requires advanced levels of autonomy--with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
-Currently, UAVs in precision agriculture use-cases are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
+It usually requires advanced levels of autonomy, with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying, along with strictly limited energy budgets.
+Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
 The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.
 
-The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters.
-The approach ideally accounts for a mission extension by adapting the QoS and TEEs as the UAV batteries drain.
-Preliminary data using a terrestrial fixed-wing UAV indicates a potential extension of up to 13 minutes over 1 hour by switching to the lowest QoS.
-
-The algorithm relies on the assumptions of the mission--a path and a set of tasks the UAV is supposed to perform--being \emph{periodic} and \emph{uncertain}.
-The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
-We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to cope with the uncertainty assumption.
-The algorithm selects the controls--the QoS and TEEs--dynamically using a modified tube-based output model predictive control (MPC), which ensures that state estimation error does not result in transgression of the control and state constraints.
-
-Although underrepresented in precision agriculture and related literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning.
+Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning.
 Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
 In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
-Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
+Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+
+The algorithm adapts the energy dynamically, replanning mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+It ideally accounts for a mission extension by adapting both QoS and TEEs as the UAV flyes and its batteries drain.
+Firstly, the algorithm adapts QoS requiring the UAV to comprise robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters.
+Secondly, it adapts TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path.
+Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
+Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
+
+The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters boundaries--being \emph{periodic} and \emph{uncertain}.
+The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
+We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
+The algorithm selects the controls (QoS and TEEs) dynamically using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
+
+The remainder of the paper is organized as follows.
+A suitable energy model for the path and the computations is showed in Section~\ref{sec:model}.
+The algorithm that uses the energy model to address dynamic mission planning is proposed in Section~\ref{sec:algo}.
+Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance.
+The paper finishes with some conclusions in Section~\ref{sec:conclusion}.
 
@@
   \begin{equation}
-    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,0}\|\iff y_{k,0}\geq y_{k,1}.
+    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,1}\|\iff y_{k,0}\geq y_{k,1}.
   \end{equation}
@@
 \section{Algorithm}
+\label{sec:algo}
 

### 2020-09-21 icra-2021.tex
some changes in the introduction (3)

@@
 Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
-Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory in Mei.~et.~al.~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots in Sadrpour.~et.~al.~\cite{sadrpour2013mission,sadrpour2013experimental}.
 
-The algorithm adapts the energy dynamically, replanning mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+The algorithm accounts for the energy due to the path similarly to Met~et.~al.
+but includes the computations in a broad mission planning setting, like the one in Sadrpour~et.~al.
+It adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
 It ideally accounts for a mission extension by adapting both QoS and TEEs as the UAV flyes and its batteries drain.
@@
 
-The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters boundaries--being \emph{periodic} and \emph{uncertain}.
+The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}.
 The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.

### 2020-09-22 icra-2021.tex
fixing text in the Introduction (yes, still in the Introduction)

@@
 Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}.
-Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 Planning a mission for UAVs operating in such scenarios is a challenging task.
-It usually requires advanced levels of autonomy, with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying, along with strictly limited energy budgets.
+It usually requires advanced levels of autonomy--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
 Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
-The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.
+The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that overcomes the traditional planning and addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.
 
@@
 Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
-In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
-Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory in Mei.~et.~al.~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots in Sadrpour.~et.~al.~\cite{sadrpour2013mission,sadrpour2013experimental}.
+In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
+The algorithm inspires notably by the technique of coupling the energy due to the computations performed and trajectory traveled, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 
-The algorithm accounts for the energy due to the path similarly to Met~et.~al.
-but includes the computations in a broad mission planning setting, like the one in Sadrpour~et.~al.
-It adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
-It ideally accounts for a mission extension by adapting both QoS and TEEs as the UAV flyes and its batteries drain.
-Firstly, the algorithm adapts QoS requiring the UAV to comprise robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters.
-Secondly, it adapts TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path.
+The proposed algorithm adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain.
+The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters.
+It optimizes TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path.
 Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
@@
 We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm selects the controls (QoS and TEEs) dynamically using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
+The algorithm selects the controls (the QoS and TEEs) using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
 

### 2020-09-22 icra-2021.tex
very minor grammar fix in Introduction

@@
 Planning a mission for UAVs operating in such scenarios is a challenging task.
-It usually requires advanced levels of autonomy--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets.
+It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying.
 Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
@@
 
+---
 %%%%%%%%%%%%%%%

### 2020-09-22 icra-2021.tex
some fixes until 'position in space and guidance action'

@@
 Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
-The algorithm inspires notably by the technique of coupling the energy due to the computations performed and trajectory traveled, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+The technique of coupling the energy due to the computations performed and trajectory traveled inspires notably the algorithm, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 
-The proposed algorithm adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+The proposed algorithm alters the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
 It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain.
@@
 The remainder of the paper is organized as follows.
-A suitable energy model for the path and the computations is showed in Section~\ref{sec:model}.
-The algorithm that uses the energy model to address dynamic mission planning is proposed in Section~\ref{sec:algo}.
+A suitable model for the energy and position of the UAV is showed in Section~\ref{sec:model}.
+The algorithm that uses the model and implements the dynamic mission planning is proposed in Section~\ref{sec:algo}.
 Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance.
@@
 
----
 %%%%%%%%%%%%%%%
@@
 
-The algorithm utilizes the model to estimate the robot's position in space and its energy evolution in time.
+The algorithm uses the model to estimate the UAV's position in space and its energy evolution in time.
 
-Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}.
-To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).
+Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
+some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using a vector field~\cite{de2017guidance}.
+Before the guidance action, we need to define the path: a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).
 
-The energy evolution $\mathbf{q}\in\mathbb{R}^j$ spent to perform such guidance action is derived using Fourier analysis (the meaning of $j$ will be explained to the reader in Subsection~\ref{sec:energy-model}) and is decomposed in the energy due to the trajectory (TEEs), and the computations (QoS)--an approach that has been adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing craft~\cite{seewald2020mechanical}.
+The energy evolution $\mathbf{q}\in\mathbb{R}^j$ is built using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decomposed in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-09-23 icra-2021.tex
minor fixes

@@
 
-Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}.
-Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
+In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 Planning a mission for UAVs operating in such scenarios is a challenging task.
@@
 Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning.
-Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
+Generally, they account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
 In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
@@
 Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
-some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using a vector field~\cite{de2017guidance}.
-Before the guidance action, we need to define the path: a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).
+some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the motion along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}.
+The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).
 
-The energy evolution $\mathbf{q}\in\mathbb{R}^j$ is built using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decomposed in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+We build the energy evolution $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 

### 2020-09-23 icra-2021.tex
Ulrik's review implemented

@@
 
-Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
-In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
-Planning a mission for UAVs operating in such scenarios is a challenging task.
-It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying.
-Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
-The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that overcomes the traditional planning and addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.
+Mission planning for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task.
+It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
+Currently, UAVs operating in outdoor scenarios are often semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
+The current state of practice in mission planning for UAVs has prompted us to proposes an \emph{energy-aware dynamic mission planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.
 
-Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning.
-Generally, they account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}.
-In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
-The technique of coupling the energy due to the computations performed and trajectory traveled inspires notably the algorithm, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Energy planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning.
+Generally, these algorithms account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2004energy}.
+And computations are only expected to increase in future scenarios.
+For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Further, past mission planning approaches also limit to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, and to the class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Unlike these approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.
 
-The proposed algorithm alters the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
-It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain.
-The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters.
-It optimizes TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path.
+The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain.
+The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
+It optimizes TEEs--an abstraction of the path to follow--and moves the UAV using a vector field that converges smoothly to the path.
 Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
-Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
+Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
 
@@
 The remainder of the paper is organized as follows.
+The dynamic mission planning problem is set in Section~\ref{sec:prob}.
 A suitable model for the energy and position of the UAV is showed in Section~\ref{sec:model}.
-The algorithm that uses the model and implements the dynamic mission planning is proposed in Section~\ref{sec:algo}.
+The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}.
 Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance.
 The paper finishes with some conclusions in Section~\ref{sec:conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Problem Statement}
+\label{sec:prob}
+
+\begin{center}\vspace{.2cm}---\emph{this section is not good (needs work)}---\vspace{.6cm}\end{center}
+
+Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
+In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 
@@
 
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
-
 \subsection{Position in space and guidance action}
@@
 
-For exemplification, we consider a non-holonomic 2D model of a fixed-wing craft flying at an assigned altitude $h\in\mathbb{R}_{>0}$.
-We will show, after the results, the requirement being eased to an arbitrary mobile robot model
+We consider a non-holonomic 2D model of the fixed-wing UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
 \begin{equation}\label{eq:uav-kinem}\begin{cases}
-  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+d(t)\\
+  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+\mathbf{d}(t)\\
   \dot{\psi}(t)&=u(\mathbf{p}(t))
@@
 \end{equation}
-where $\mathbf{p}(t)\in\mathbb{R}^2$, $s\in\mathbb{R}$ describes the airspeed assumed constant, $\psi(t)\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi(t))=\begin{bmatrix}\cos{\psi(t)} & \sin{\psi(t)}\end{bmatrix}^T$, $d$ is the wind vector where we assume $\|d\|<s$, and $u\in\mathbb{R}$ the guidance action which denotes the angular velocity $\dot{\psi}$ of the craft.
+where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$ of the UAV.
 
-Let us define $\mathcal{P}$ the area which discloses all the possible paths within the boundaries $\underline{c}\in\mathbb{R}_{\leq 0},\overline{c}\in\mathbb{R}_{\geq 0}$
+Let us define $\mathcal{P}_k$, the area that discloses all the possible deviations form the $k$-th TEE 
 \begin{equation}\label{eq:area}
-  \mathcal{P}:=\{\mathbf{p}:\underline{c}\leq\varphi(\mathbf{p})\leq\overline{c}\},
+  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p})\leq\overline{c}_k\},
 \end{equation}
-where $\underline{a},\overline{a}$ returns the upper bound and lower bound limit of $a$ from the mission specification, which is a lookup table.
+where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints.
+$\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification, a lookup table.
 
-The concept of area between the bounds is used later to design a controller that selects $c$ with the highest energy value under the energy budget constraints.
-Here we design a guidance action $u$ that allows following $\varphi$ in such area by the means of minimizing the norm $\|\varphi(\mathbf{p})\|$.
+The algorithm uses the concept to select $c$ with the highest energy value under the energy budget constraints.
+Assume at time $k$ the algorithm selects the TEE $\varphi_k$ with the highest energy value being $c_k$, we design a guidance action $u$ that follows $\varphi_k$ by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
 
-Let us define $\varPhi:=\varphi(\mathbf{p})$. The direction to follow is expressed as the desired velocity vector
+Let us define $\varPhi:=\varphi_k(\mathbf{p})$. The direction to follow can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain which adjusts the speed of convergence.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 
-The direction the velocity vector $\dot{\mathbf{p}}$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interference.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interference.
 
@@
 \end{equation} 
-where $H(\cdot)$ is defined as the Hessian operator; the physical meaning is that the curvature of the desired trajectory has to be known in order to be tracked.
+where $H(\cdot)$ is defined as the Hessian operator and $\dot{\mathbf{p}}_d:=\dot{\mathbf{p}}_d(\mathbf{p})$ for brevity; the physical meaning is that the curvature of the desired trajectory has to be known in order to be tracked.
 
-Under the assumption of the airspeed $s>\|w(t)\|$ for $t>0$ (i.e., the constant airspeed is greater than the norm of the wind), the guidance action can be expressed
+The guidance action can be expressed
 \begin{equation}\label{eq:uav-cont}
-  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d(\mathbf{p})+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
+  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
 \end{equation} 
-where $k_d\in\mathbb{R}_{\geq 0}$ is the gain which adjusts the speed of the convergence of $\dot{\mathbf{p}}_d$, $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d$ is given in Equation~(\ref{eq:chid}).
+where $k_d\in\mathbb{R}_{\geq 0}$ is the gain to adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-09-23 icra-2021.tex
Ulrik's review implemented (2)

@@
 It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
-Currently, UAVs operating in outdoor scenarios are often semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}.
-The current state of practice in mission planning for UAVs has prompted us to proposes an \emph{energy-aware dynamic mission planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.
+Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}.
+Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs that highlights the increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.
 

### 2020-09-24 icra-2021.tex
maybe the problem statement works?

@@
 Generally, these algorithms account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2004energy}.
-And computations are only expected to increase in future scenarios.
 For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
 Further, past mission planning approaches also limit to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, and to the class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-Unlike these approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.
+Yet, computations of such systems are only expected to increase in the near future.
+Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.
 
 The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
-Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain.
+Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain.
 The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
@@
 
-\begin{center}\vspace{.2cm}---\emph{this section is not good (needs work)}---\vspace{.6cm}\end{center}
+We consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
+In practice, complex monitoring strategies are often implemented utilizing UAVs and are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 
-Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
-In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+The UAV flies in ellipses shifted in time--a survey pattern optimized for the craft's dynamics--detects obstacles using a convolutional neural network (CNN) and informs ground mobile robots employed for future harvesting.
 
-%%%%%%%%%%%%%%%
-\section{Model}
+\subsection{Position and energy state}
 \label{sec:model}
 
-The algorithm uses the model to estimate the UAV's position in space and its energy evolution in time.
+We use the state to estimate the UAV's position in space and the energy evolution in time.
+Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
+some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the \emph{position evolution} along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}.
+The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$.
+To this end, the TEE is satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points.
 
-Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
-some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the motion along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}.
-The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).
-
-We build the energy evolution $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+We build the \emph{energy evolution} $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 
-We consider a non-holonomic 2D model of the fixed-wing UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
+We consider a non-holonomic 2D model of the UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
 \begin{equation}\label{eq:uav-kinem}\begin{cases}
@@
 
-Let us define $\varPhi:=\varphi_k(\mathbf{p})$. The direction to follow can be expressed as the desired velocity vector
+Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to follow can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation} 
-where $k_d\in\mathbb{R}_{\geq 0}$ is the gain to adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
+where $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, $k_d\in\mathbb{R}_{\geq 0}$ adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
 

### 2020-09-24 icra-2021.tex
fixed up until ...computations (proofreading now)

@@
 The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
-It optimizes TEEs--an abstraction of the path to follow--and moves the UAV using a vector field that converges smoothly to the path.
+It optimizes TEEs--an abstraction of the path to follow--and guides the UAV using a vector field that converges smoothly to the path.
 Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
@@
 The remainder of the paper is organized as follows.
-The dynamic mission planning problem is set in Section~\ref{sec:prob}.
-A suitable model for the energy and position of the UAV is showed in Section~\ref{sec:model}.
+The dynamic mission planning problem is set in Section~\ref{sec:prob}, along a suitable model for the energy and position of the UAV.
 The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}.
@@
 
-The UAV flies in ellipses shifted in time--a survey pattern optimized for the craft's dynamics--detects obstacles using a convolutional neural network (CNN) and informs ground mobile robots employed for future harvesting.
+The UAV flies in ellipses shifted in time--a survey pattern optimized for the craft's dynamics--detects obstacles using a convolutional neural network (CNN) and informs grounded mobile robots employed for future harvesting.
 
@@
 
-We use the state to estimate the UAV's position in space and the energy evolution in time.
+We use the state to estimate the UAV's position in space and the energy in time.
 Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
@@
 
-We build the \emph{energy evolution} $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+We build the \emph{energy evolution} $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
-\subsection{Position in space and guidance action}
+\subsection{Position evolution and guidance action}
 \label{sec:position}
@@
 \end{equation}
-where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$ of the UAV.
+where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$.
 
@@
 \end{equation}
-where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints.
-$\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification, a lookup table.
+where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints: $\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification, a lookup table.
 
 The algorithm uses the concept to select $c$ with the highest energy value under the energy budget constraints.
-Assume at time $k$ the algorithm selects the TEE $\varphi_k$ with the highest energy value being $c_k$, we design a guidance action $u$ that follows $\varphi_k$ by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
+Assume at time $k$ the algorithm selects the TEE $\varphi_k$ with the highest energy value being $c_k$, we design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
 
-Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to follow can be expressed as the desired velocity vector
+Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to the TEE to follow can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
-
 \subsection{Energy evolution due to trajectory}
@@
 
-To evaluate the energy we formalize the following realistic assumption introduced in Section~\ref{sec:intro}.
-\begin{assm}\label{assm:periodic}
-The mission the mobile robots perform is periodic, in the sense that it presents repetitive patterns.
+The energy evolution analysis necessitates the following realistic assumption.
+\begin{assm}\label{assm:periodic} The position evolution is periodic, in the sense that it presents repetitive patterns.
 \end{assm}
+Formally, given two time instants $k_1,k_2\in\mathbb{R}_{\geq 0}$ such that $k_1>k_2$ and a value $n\in\mathbb{R}_{\geq 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$ such that
+\begin{equation}
+  \|\mathbf{p}(t)-\mathbf{p}(t+n)\|= e\,\,\,\forall t\in\{k_1,...,k_2\}.
+\end{equation}
+We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$.
 
-Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
+Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
 \begin{equation}\label{eq:fourier}
@@
 
-The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent time-varying state-space model in the following form
+The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear time-invariant state-space model
 \begin{equation}\label{eq:state-perf}\begin{cases}
@@
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy evolution of the system being controlled.
-We will see later in the Theorem~\ref{thm:state-vs-energy} that the instantaneous energy can be obtained from the model as a linear combination of the state.
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption of the system being controlled.
+We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state.
 The control $\mathbf{u}$ along with the input matrix $B$ are defined later in Subsection~\ref{sec:control-action}, the state $\mathbf{q}$ mimics the original Fourier series coefficients, and
+
 \begin{equation}\label{eq:state-details}\begin{split}
-  \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
-    \alpha_0 & \vline & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
+  \mathbf{q}(t)&=\left[\begin{array}{cccccc}
+    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
   \end{array}\right]^T,\\
-  A&=\left[\begin{array}{ccccc}
-    1          & \vline & \mathbf{0} & \cdots & \mathbf{0} \\\hline
-    \mathbf{0} & \vline & A_1        & \cdots & \mathbf{0} \\
-    \vdots     & \vline & \vdots     & \ddots & \vdots     \\
-    \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
+  A&=\left[\begin{array}{cccc}
+    1&    &       &  \\
+     & A_1&       &  \\
+     &    & \ddots&  \\
+     &    &       & A_r 
   \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
-  C&=\left[\begin{array}{ccccccc}
-    1 & \vline & 1 & 0 & \cdots & 1 & 0
+  C&=\left[\begin{array}{cccccc}
+    1 & 1 & 0 & \cdots & 1 & 0
   \end{array}\right],
@@
 where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
-Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and column vectors respectively.
+In matrix $A$, the first value is one, $A_n$ farther on the diagonal, and zero for the remaining.
 
-Motivated by the fact that the system of interest is sampled discrete-time, we consider the discretized version of Equation~(\ref{eq:state-perf}) and add the uncertainty
+We further model the system of Equation~(\ref{eq:state-perf}) plus disturbances with the following discrete time model
 \begin{equation}\label{eq:state-unct}
   \begin{cases}
-  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+w_k\\
+  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
   y_k&=C\mathbf{q}_k+v_k
@@
 \end{equation}
-where $w_k\in\mathbb{R}$ accounts for the environment uncertainty, and $v_k\in\mathbb{R}$ for the measurement error.
-
-The instantaneous energy can be obtained from the model~(\ref{eq:state-unct}) as a linear combination of the state.
+where $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ account for unknown state and output disturbances.
+In the case of the system behaving ideally (i.e., with zero disturbances), we expect a set of states evolving accordingly to their output.
+Such observation is summarized in the following Lemma.
 
 \begin{lem}\label{lem:state-vs-energy}
-  Suppose the system behaves ideally (with no environment uncertainty and measurement error).
-  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eq:state-details}) along their evolution~(\ref{eq:state-unct}) at time instant $k$ depends on the instantaneous energy consumption
+  Suppose the system of Equation~(\ref{eq:state-unct}) evolves with no disturbances ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
   \begin{equation}
@@
 \begin{proof}
-  *\\
+  \begin{center}\vspace{.2cm}``\emph{The easy proof is trivial and is left as an exercise to the reader :P}''\vspace{.6cm}\end{center}
 \end{proof}
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-09-24 icra-2021.tex
fixed up until control action (and still proofreading)

@@
 We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm selects the controls (the QoS and TEEs) using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
+The algorithm selects the controls (the QoS and TEEs) using a robust output feedback model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
 
@@
 
-We use the state to estimate the UAV's position in space and the energy in time.
+We use the state to estimate the UAV's position in space and energy in time.
 Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
@@
 \end{equation}
-where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints: $\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification, a lookup table.
+where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints: $\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification.
+In particular, the specification contains TEEs along the ROS nodes configuration and a lookup table for TEEs and QoS parameters (the former are the above mentioned $c$s, the latter explained in Subsection~\ref{sec:computations-model}).
 
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varPhi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 
@@
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption of the system being controlled.
+where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption.
 We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state.
@@
 where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
-In matrix $A$, the first value is one, $A_n$ farther on the diagonal, and zero for the remaining.
+In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remaining.
 
@@
 
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
-
 \subsection{Energy evolution due to computations}
@@
 
-A computational energy model is built using \powprof{}, an open-source modeling tool that measures empirically software configurations and builds an energy model, presented in authors' previous work~\cite{seewald2019coarse}.
-Specifically, the tool builds a multivariate linear interpolation which is accessed online at the hand of a lookup table in the optimal control algorithm.
-The system is modeled as follows.
-An existing ROS system composes several computationally expensive ROS nodes, allowing to vary the number of computations changing some node-specific quality of service (QoS) values via ROS parameters.
-The tool builds the energy model using mission specification which, besides other mission parameters, specifies per each ROS node a QoS range.
+The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds an energy model.
+Specifically, the tool builds a multivariate linear interpolation from the mission specification.
+It hence requires the user to implement a ROS system with one or more computationally expensive ROS nodes which change the computational load by node-specific ROS parameters (QoS).
 
@@
 \begin{equation}\label{eq:qos-def}
-  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma-1\}\right\},
+  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\,\,\forall n\in\{0,\dots,\sigma-1\}\right\},
 \end{equation}
-where $\text{QoS}_n(t):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time $t$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of at time $k$.
+where $\text{QoS}_n(k):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of.
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
@@
 The QoS parameters $\mathcal{C}_k$ can be subject to different constraints at different states.
-Physically, this means that the robot can perform the ROS nodes within different QoS ranges while flying different phases of a mission
+Physically, this means that the UAV can perform the ROS nodes within different QoS ranges in time while flying
 \begin{equation}\label{eq:qos-lims}\begin{split}
@@
 
-The control action is built in two steps.
-Equation~(\ref{eq:qos-def}) defines the control due to the computations.
-The control due to the trajectory is specific to the system being analyzed, for instance on the model of the fixed-wing craft in~(\ref{eq:uav-kinem}), along its control in Equation~(\ref{eq:chid})~and~(\ref{eq:uav-cont}).
-A generalization which accounts for the variations in the TEE $\varphi$ of a generic model by means of the TEEs parameters is derived in the following subsection.
-
 \subsection{Control action}
 \label{sec:control-action}
+
+We build the control action $\mathbf{u}$ from Equation~(\ref{eq:state-perf})~and~(\ref{eq:state-unct}) in two steps.
+In Equation~(\ref{eq:qos-def}) we defined the control due to the computations, here we do the same for the trajectory.
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-10-06 scripts/MAIN.m
ordering the scripts for simulations and cleaning

@@ -2,173 +2,48 @@
 % Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
 
 
-%% Energy sim, input data
+%% Simulations selection
 
 % Hint: use default values (just press enter when asked anything and don't 
 % input any file)
 
 % Hint: always good idea to start with a clear command
 
-disp('[E    ] Energy sim');
-disp('[  E> ] Input data');
-
-% Fourier series order (see eq:fourier)
-r = input('[   ? ] Fourier series order r: ');
-if isempty(r)
-    r = 3; % default order
-end
-
-% Characteristic time
-xi = input('[   ? ] Characteristic time xi: ');
-if isempty(xi)
-    xi = 10; % Characteristic time
-end
-
-% The value of y from the sensor. This is the former mechanical energy; the
-% former computational energy [i.e., the energy from the embedded
-% companion is obtained from the modeling tool's csv file].
-disp('[   $ ] Input sensor energy data [csv]');
-[bn, folder] = uigetfile('.csv');
-if bn == 0
-    % default: data from the paparazzi simulation on 12/12/18 09:53:01
-    % credit: Amit Ferencz Appel
-    file = csvread('../data/simulation1/pprz_energy.csv');
-else
-    file = csvread(fullfile([folder, bn]));
-end
-
-if bn == 0
-    column = 1; % default column
-else
-    column = input('[   ? ] Which column contains energy: ');
-end
-    file = file(:, [column]);
-
-if bn == 0
-    ts = 200; % default time step
-else 
-    ts = input('[   ? ] At what time step [ms]: ');
-end
-ts = ts / 1000;
-tf = ts * size(file, 1); % leaving here just for exemplification
-t = 1:1:size(file, 1); % discretizing, use ts to get the original
-
-meas = file;
-
-clear column file tf;
-
-% The value of the model from the modeling tool (powprof); former
-% computational energy.
-disp('[   $ ] Input computational energy data (from powprof) [csv]');
-[bn, folder] = uigetfile('.csv');
-if bn == 0
-    file2 = csvread('../data/simulation1/computational_energy.csv');
-else
-    file2 = csvread(fullfile([folder, bn]));
-end
-
-% Mission specification
-disp('[   $ ] Input mission specification [csv]')
-[bn, folder] = uigetfile('.csv');
-if bn == 0
-    file3 = csvread('../data/simulation1/mission_specification.csv');
[…]

### 2020-10-06 scripts/energy/MAIN.m

@@ -1,0 +1,169 @@
+%MAIN
+% Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
+
+
+%% Energy sim, input data
+
+disp('[E    ] Energy sim');
+disp('[  E> ] Input data');
+
+% Fourier series order (see eq:fourier)
+r = input('[   ? ] Fourier series order r: ');
+if isempty(r)
+    r = 3; % default order
+end
+
+% Characteristic time
+xi = input('[   ? ] Characteristic time xi: ');
+if isempty(xi)
+    xi = 10; % Characteristic time
+end
+
+% The value of y from the sensor. This is the former mechanical energy; the
+% former computational energy [i.e., the energy from the embedded
+% companion is obtained from the modeling tool's csv file].
+disp('[   $ ] Input sensor energy data [csv]');
+[bn, folder] = uigetfile('.csv');
+if bn == 0
+    % default: data from the paparazzi simulation on 12/12/18 09:53:01
+    % credit: Amit Ferencz Appel
+    file = csvread('../../data/simulation1/pprz_energy.csv');
+else
+    file = csvread(fullfile([folder, bn]));
+end
+
+if bn == 0
+    column = 1; % default column
+else
+    column = input('[   ? ] Which column contains energy: ');
+end
+    file = file(:, [column]);
+
+if bn == 0
+    ts = 200; % default time step
+else 
+    ts = input('[   ? ] At what time step [ms]: ');
+end
+ts = ts / 1000;
+tf = ts * size(file, 1); % leaving here just for exemplification
+t = 1:1:size(file, 1); % discretizing, use ts to get the original
+
+meas = file;
+
+clear column file tf;
+
+% The value of the model from the modeling tool (powprof); former
+% computational energy.
+disp('[   $ ] Input computational energy data (from powprof) [csv]');
+[bn, folder] = uigetfile('.csv');
+if bn == 0
+    file2 = csvread('../../data/simulation1/computational_energy.csv');
+else
+    file2 = csvread(fullfile([folder, bn]));
+end
+
+% Mission specification
+disp('[   $ ] Input mission specification [csv]')
+[bn, folder] = uigetfile('.csv');
+if bn == 0
+    file3 = csvread('../../data/simulation1/mission_specification.csv');
+else
+    file3 = csvread(fullfile([folder, bn]));
+end
+
+clear bn folder;
+
+selection = 0;
[…]

### 2020-10-06 scripts/position/MAIN.m

@@ -1,0 +1,48 @@
+%MAIN
+% Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
+
+
+%% Position sim
+
+disp('[P    ] Position sim');
+
+selection = 0;
+           
+
+%% Selection of subroutine
+ 
+% Runs if one runs just MAIN instead of selectively running sections...
+
+[indx] = listdlg ...
+    (   'PromptString', {'Select a subroutine'}, ...
+        'SelectionMode', 'single', 'ListString', ...
+        { ...
+            'OP1: given TEE generate GDN, plot, animate', ...
+            'OP2: ', ...
+        }, ... 
+        'ListSize', [350 150] ...
+    );
+selection = 1;
+
+% Now comes these subroutines:
+
+
+%% Position sim, OP1
+
+% Vector field simulation from a defined TEE, plot and possible animation
+
+if or(selection == 0, indx == 1)
+
+    OP1;
+end
+
+
+%% Position sim, OP2
+
+% 
+
+if or(selection == 0, indx == 2)
+
+    OP2;
+end
+

### 2020-10-06 scripts/position/OP1.m

@@ -1,0 +1,89 @@
+%OP1
+% Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
+%
+% Vector field simulation from a defined TEE, plot and possible animation
+
+
+%% Build the model 
+
+fprintf(['[ OP1 ] Vector field simulation from a defined TEE, plot and\n' ...
+         '        possible animation\n']);
+disp( '[     ] Build the model');
+
+syms x y;
+
+varphi = input('[   ? ] Type the TEE: ');
+
+if isempty(varphi)
+   
+    min = 0;
+    max = 400;
+    varphi = ((x - 200) * cosd(12) + (y - 200) * sind(12))^2 / 120^2 + ...
+        ((x - 200)*sind(12) - (y - 200) * cosd(12))^2 / 170^2 - 1; 
+    % default TEE, an ellipse
+else
+    
+    min = input('[   ? ] The min value: ');
+    max = input('[   ? ] And the max value: ');
+end
+
+% create all the points used to build the vector field
+
+[xp yp] = meshgrid(...
+    min:(abs(min) + abs(max)) / 50:max, min:(abs(min) + abs(max)) / 50:max...
+                  );
+              
+points = reshape(cat(2, xp', yp'), [], 2);
+clear xp yp;
+
+E = [0 1; -1 0]; % default rotation matrix
+
+ke = input('[   ? ] Gain to adjust speed of convergence: ');
+if isempty(ke)
+   ke = 1.5; % default gain to adjust speed of convergence
+end
+
+% Builds the vector field
+[dpd, pdangle] = build_gdn2(E, ke, varphi, points);
+
+
+%% Plot and animate
+
+disp('[     ] Plot and animate');
+fprintf(['[   ! ] Dependencies: ration matrix E, gain ke, TEE varphi,\n' ...
+        '        points, the angle of the vector field pdangle, the min\n' ...
+        '        and max value\n']);
+
+if strcmp(questdlg('Show the animation?', 'Animate', 'Yes', 'No', 'Yes'),...
+           'Yes'...
+         )
+
+    answer = inputdlg({'start coordinate x:', 'start coordinate y:'}, ...
+                      'Starting point', [1 35], {'0', '0'} ...
+                     );
+
+    if isempty(answer)
+        strp = [0; 0];
+    else
+        strp = str2double(answer);
+    end
+    
+    clear answer;
+    
+    andu = input('[   ? ] Animation duration: ');
[…]

### 2020-10-06 scripts/position/build_gdn2.m

@@ -1,0 +1,44 @@
+function [dpd, pdangle] = build_gdn2(E, ke, varphi, points)
+%BUILD_GDN2 Creates the vector field
+%
+% Inputs:
+%   E:      rotation matrix
+%   ke:     gain to adjust speed of convergence
+%   varphi: TEE
+%   points: vector of points where the function generates the vector field
+%   
+%
+% Outputs:
+%   dpd:    desired velocity vector (generated from points)
+%   pdangle:angle saying where the desired velocity vector is pointing
+%
+    syms x y;
+    
+    dvarphi = gradient(varphi, [x y]); % gradient
+    
+    dpd = E * dvarphi - ke * varphi * dvarphi;
+    
+    x = transpose(points(:, 1));
+    y = transpose(points(:, 2));
+    
+    pd = transpose(double(subs(dpd)));
+    
+    angle = atand(pd(:, 2) ./ pd(:, 1));
+    
+    % One has to do the following operation, as the sign is not preserved
+    % in the atand function above
+    
+    % Corresponds to if (pd(1) < 0 && pd(2) < 0) ...
+    angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) = ...
+        angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) + 180;
+    
+    % And this corresponds to if (pd(1) < 0 && pd(2) > 0) ...
+    angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) = ...
+        angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) + 180;
+     
+    angle = transpose(angle);
+    pdangle = angle;
+    dpd = pd;
+    
+end
+

### 2020-10-06 scripts/position/plot_gdn2.m

@@ -1,0 +1,79 @@
+function [] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
+% PLOT_GDN2 Plots the vector field, and eventually animates it
+%
+% Inputs:
+%   E:      rotation matrix
+%   ke:     gain to adjust speed of convergence
+%   varphi: TEE
+%   points: vector of points where the function generates the vector field
+%   pdangle:vector of desired velocity angles
+%   min:    position (x and y) of the start of the vector field plot
+%   max:    position of the end of the vector field plot
+%   andu:   animation duration (use 0 if no animation required)
+%   s:      cruise speed in m/s
+%   p:      starting point (for the anumation)
+%
+    figure;
+    
+    % Just a nice effect nothing more...
+    varphi_plot2 = fimplicit(varphi);
+    set(varphi_plot2, 'Color', [.85 .85 .85], 'LineWidth', 10);
+    
+    hold on;
+    
+    varphi_plot = fimplicit(varphi);
+    set(varphi_plot, 'Color', 'black', 'LineWidth', 1.2);
+    
+    xlim([min max]);
+    ylim([min max]);
+        
+    x = transpose(points(:, 1));
+    y = transpose(points(:, 2));
+        
+    
+    % And just a crazy workaround to plot the arrows...
+    coeff = 0.45 * (max - min) / 25;
+    coeffm = 0.20 * (max - min) / 25;
+    coeffM = 0.30 * (max - min) / 25;
+    
+    dpdx = [x; x + coeff * cosd(pdangle)];
+    dpdy = [y; y + coeff * sind(pdangle)];
+    
+    arrowlxx = [x + coeffM * cosd(pdangle); dpdx(2, :)];
+    arrowlxy = [y + coeffm * sind(pdangle); dpdy(2, :)];
+    
+    arrowrxx = [x + coeffm * cosd(pdangle); dpdx(2, :)];
+    arrowrxy = [y + coeffM * sind(pdangle); dpdy(2, :)];
+    
+    plot(dpdx, dpdy, 'Color', [0.3010, 0.7450, 0.9330]);
+    
+    plot(arrowlxx, arrowlxy, 'Color', [0.3010, 0.7450, 0.9330]);
+    plot(arrowrxx, arrowrxy, 'Color', [0.3010, 0.7450, 0.9330]);
+    
+    % Here is the eventual animation
+    xd = [1 0] * p;
[…]

### 2020-10-06 scripts/MAIN.m
I definitely had to make this essential commit...

@@ -9,10 +9,11 @@
 
 % Hint: always good idea to start with a clear command
 
-fprintf(['\t\t+-------------------------------------------------+\n' ...
-         '\t\t|                   E A D M P A                   |\n' ...
-         '\t\t| Energy-Aware Dynamic Mission Planning Algorithm |\n' ...
-         '\t\t+-------------------------------------------------+\n\n']);%51
+fprintf(['\t\t+---------------------------------------------+\n' ...
+         '\t\t|            E A D M P A   S I M              |\n' ...
+         '\t\t|    Energy-Aware Dynamic Mission Planning    |\n' ...
+         '\t\t|            Algorithm Simulator              |\n' ...
+         '\t\t+---------------------------------------------+\n\n']);%51
  
 [indx] = listdlg ...
     (   'PromptString', {'Select a simulation'}, ...
@@ -26,18 +27,18 @@ fprintf(['\t\t+-------------------------------------------------+\n' ...
 
 if indx == 1
     
-    fprintf(['\t\t               +-------------------+\n' ...
-             '\t\t               | Energy simulation |\n' ...
-             '\t\t               +-------------------+\n\n']);%21
+    fprintf(['\t\t             +-------------------+\n' ...
+             '\t\t             | Energy simulation |\n' ...
+             '\t\t             +-------------------+\n\n']);%21
     
     disp('[>    ] Invoking energy sim');
     cd energy;
     MAIN;    
 elseif indx == 2
     
-    fprintf(['\t\t              +---------------------+\n' ...
-             '\t\t              | Position simulation |\n' ...
-             '\t\t              +---------------------+\n\n']);%23
+    fprintf(['\t\t            +---------------------+\n' ...
+             '\t\t            | Position simulation |\n' ...
+             '\t\t            +---------------------+\n\n']);%23
     
     disp('[>    ] Invoking position sim');
     cd position;

### 2020-10-07 scripts/position/MAIN.m
added the last functionality in the script which was missing from the old version (loading data from pprz)

@@ -18,7 +18,7 @@ selection = 0;
         'SelectionMode', 'single', 'ListString', ...
         { ...
             'OP1: given TEE generate GDN, plot, animate', ...
-            'OP2: ', ...
+            'OP2: path from Paparazzi autopilot, GDN, plot, animate', ...
         }, ... 
         'ListSize', [350 150] ...
     );
@@ -39,7 +39,8 @@ end
 
 %% Position sim, OP2
 
-% 
+% 3D, 2D, and vector field simulations from a paparazzi autopilot logs,
+% possibly animated
 
 if or(selection == 0, indx == 2)
 

### 2020-10-07 scripts/position/OP1.m

@@ -53,7 +53,7 @@ disp('[     ] Plot and animate');
 fprintf(['[   ! ] Dependencies: ration matrix E, gain ke, TEE varphi,\n' ...
         '        points, the angle of the vector field pdangle, the min\n' ...
         '        and max value\n']);
-
+    
 if strcmp(questdlg('Show the animation?', 'Animate', 'Yes', 'No', 'Yes'),...
            'Yes'...
          )
@@ -79,10 +79,15 @@ if strcmp(questdlg('Show the animation?', 'Animate', 'Yes', 'No', 'Yes'),...
     if isempty(s)
         s = 20; % default cruise speed
     end
+    
+    figure;
 
     plot_gdn2(E, ke, varphi, points, pdangle, ...
         min, max, andu, s, strp);
 else
+    
+    figure;
+    
     plot_gdn2(E, ke, varphi, points, pdangle, ...
         min, max, 0, 0, [0; 0]);
 end

### 2020-10-07 scripts/position/OP2.m

@@ -1,0 +1,208 @@
+%OP2
+% Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
+%
+% 3D, 2D, and vector field simulations from a paparazzi autopilot logs,
+% possibly animated
+
+%% Build the model
+
+fprintf(['[ OP1 ] 3D, 2D, and vector field simulations from a paparazzi\n' ... 
+         '        autopilot logs, possibly animated\n']);
+
+ah = input('[   ? ] Battery capacity [Ah]: ');
+if isempty(ah)
+    ah = 2.5; % default battery capacity (2500 mAh)
+end
+     
+% retriving paparazzi log
+disp('[   $ ] Input Paparazzi autopilot log [data]');
+[bn, folder] = uigetfile('.data');
+if bn == 0
+    % default: data from the paparazzi simulation on 12/12/18 09:53:01
+    % credit: Amit Ferencz Appel
+    [p w segments circles] = ...
+        load_pprz('../../data/simulation1/18_12_12__09_53_01_SD.data', ah);
+else    
+    [p w segments circles] = ...
+        load_pprz(fullfile([folder, bn]), ah);
+end
+
+answer = inputdlg({'Mission started [s]:', 'Mission stopped [s]:'}, ...
+                   'Mission time', [1 35], {'0', sprintf('%.2f',p(end, 1))} ...
+                 );
+
+if isempty(answer)
+    strp = [680; 1000];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+% filter data about the cruise (default are ~ 490.5->1226)
+p(p(:, 1) < strp(1), :) = [];
+p(p(:, 1) > strp(2), :) = [];
+
+w(w(:, 1) < strp(1), :) = [];
+w(w(:, 1) > strp(2), :) = [];
+
+segments(segments(:, 1) < strp(1), :) = [];
+segments(segments(:, 1) > strp(2), :) = [];
+
+circles(circles(:, 1) < strp(1), :) = [];
+circles(circles(:, 1) > strp(2), :) = [];
+
+% normalizing and merging
+% units are now: x, y (utm normalized in cm), altitude (cm)
+% so it's expressed in cm, meaning this is the way to get in in meters
+% data from NAV, so no more normalization needed... Except for height
+%p(:, 2) = p(:, 2) - min(p(:, 2));
+%p(:, 3) = p(:, 3) - min(p(:, 3));
+%p(:, 2) = p(:, 2) / 100;
[…]

### 2020-10-07 scripts/position/load_pprz.m

@@ -1,0 +1,102 @@
+
+function [p, w, segments, circles] = load_pprz(fn, ah)
+%LOAD_PPRZ loads the position, power, and the mission (a set of straight 
+% lines initial and final points and circles centers and radiuses) from a
+% paparazzi autopilot logs
+% (see: http://wiki.paparazziuav.org/wiki/Logs)
+%
+% Inputs:
+%   fn:  file name where the log is stored [data]
+%   ah:  battery capacity [ah]
+%
+% Outputs:
+%   p:       positions (time [s], relative to home x [m], y [m], 
+%            altitude [m])
+%   w:       power (time [s], instantaneous power drain [W]
+%   segments:straight lines in the mission (time [s], first point x, y [m],
+%            second point x, y [m])
+%   circles: circles in the mission (time [s], center x, y [m], radius [m])
+%
+
+    fid = fopen(fn,'r');
+   
+    i = 1;
+    b_ = 1;
+    s_ = 1;
+    c_ = 1;
+    n_ = 1;
+
+    while feof(fid) == 0
+        tline = fgetl(fid);
+   
+        if  (length(findstr(tline, 'GPS_SOL'))) > 0
+            continue;
+        end
+        
+        if ( length(findstr(tline, 'GPS')) ) > 0
+            GPS(i, :) = textscan(tline, ...
+                '%f %*d %*s %d %d %d %d %d %d %d %d %d %d', 1);
+            i = i + 1;
+        end
+        
+        if  (length(findstr(tline, 'NAVIGATION_REF'))) > 0
+            continue;
+        end
+        
+        if ( length(findstr(tline, 'NAVIGATION')) ) > 0
+            NAV(n_, :) = textscan(tline, ...
+                '%f %*d %*s %d %d %d %d %d %d %d %d', 1);
+            n_ = n_ + 1;
+        end
+   
+        if ( length(findstr(tline, 'BAT')) ) > 0
+            BAT(b_, :) = textscan(tline, ...
+                '%f %*d %*s %d %d %d %d %d %d %d %d', 1);            
+            b_ = b_ + 1;
+        end
+        
+        if ( length(findstr(tline, 'CIRCLE')) ) > 0
+            CIR(c_, :) = textscan(tline, '%f %*d %*s %d %d %d', 1);
+            c_ = c_ + 1;
+        end
+        
+        
[…]

### 2020-10-07 scripts/position/plot_gdn2.m

@@ -13,7 +13,6 @@ function [] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
 %   s:      cruise speed in m/s
 %   p:      starting point (for the anumation)
 %
-    figure;
     
     % Just a nice effect nothing more...
     varphi_plot2 = fimplicit(varphi);

### 2020-10-07 matlab/animations/animate.m
cleaning (this should have been done a long time ago)

@@ -1,84 +1,0 @@
-
-% load data from pprz log
-[p w segments circles] = loadpprz('18_12_12__09_53_01_SD.data', 2.5);
-
-% filter data about the cruise (~490.5->1226)
-p(p(:, 1) < 680, :) = [];
-p(p(:, 1) > 1000, :) = [];
-
-w(w(:, 1) < 680, :) = [];
-w(w(:, 1) > 1000, :) = [];
-
-segments(segments(:, 1) < 680, :) = [];
-segments(segments(:, 1) > 1000, :) = [];
-
-circles(circles(:, 1) < 680, :) = [];
-circles(circles(:, 1) > 1000, :) = [];
-
-% normalizing and merging
-% units are now: x, y (utm normalized in cm), altitude (cm)
-% so it's expressed in cm, meaning this is the way to get in in meters
-% data from NAV, so no more normalization needed... Except for height
-%p(:, 2) = p(:, 2) - min(p(:, 2));
-%p(:, 3) = p(:, 3) - min(p(:, 3));
-%p(:, 2) = p(:, 2) / 100;
-%p(:, 3) = p(:, 3) / 100;
-p(:, 4) = p(:, 4) / 100;
-
-%% animation
-delay = p(2, 1) - p(1, 1);
-    
-figure(1);
- 
-for i=1:size(p(:, 1))
-    
-    subplot(2, 2, [1 2]);
-    plot3(p(1:i, 2), p(1:i, 3), p(1:i, 4))
-    %title(datestr(p(i, 1) / (24 * 60 * 60), 'HH:MM:SS'));
-    
-    xlim([min(p(:, 2)) max(p(:, 2))]);
-    ylim([min(p(:, 3)) max(p(:, 3))]);
-    zlim([0 max(p(:, 4))]);
-    
-    subplot(2, 2, 3);
-    plot(p(1:i, 2), p(1:i, 3))
-    %title(p(i, 1));
-    
-    xlim([min(p(:, 2)) max(p(:, 2))]);
-    ylim([min(p(:, 3)) max(p(:, 3))]);
-    
-    if any(fix(circles(:, 1)) == fix(p(i, 1)))
-        subplot(2, 2, 3);
-        syms x y;
-        circle = circles(fix(circles(:, 1)) == fix(p(i, 1)), 2:end);
-        
-        f = (x - circle(1))^2 + (y - circle(2))^2 - circle(3)^2;
-        
-        subplot(2, 2, 4);
-    
-        fimplicit(f);
[…]

### 2020-10-07 matlab/animations/loadpprz.m

@@ -1,94 +1,0 @@
-
-function [p, w, segments, circles] = loadpprz(fn, ah)
-
-    fid = fopen(fn,'r');
-   
-    i = 1;
-    b_ = 1;
-    s_ = 1;
-    c_ = 1;
-    n_ = 1;
-
-    while feof(fid) == 0
-        tline = fgetl(fid);
-   
-        if  (length(findstr(tline, 'GPS_SOL'))) > 0
-            continue;
-        end
-        
-        if ( length(findstr(tline, 'GPS')) ) > 0
-            GPS(i, :) = textscan(tline, '%f %*d %*s %d %d %d %d %d %d %d %d %d %d', 1);
-            i = i + 1;
-        end
-        
-        if  (length(findstr(tline, 'NAVIGATION_REF'))) > 0
-            continue;
-        end
-        
-        if ( length(findstr(tline, 'NAVIGATION')) ) > 0
-            NAV(n_, :) = textscan(tline, '%f %*d %*s %d %d %d %d %d %d %d %d', 1);
-            n_ = n_ + 1;
-        end
-   
-        if ( length(findstr(tline, 'BAT')) ) > 0
-            BAT(b_, :) = textscan(tline, '%f %*d %*s %d %d %d %d %d %d %d %d', 1);            
-            b_ = b_ + 1;
-        end
-        
-        if ( length(findstr(tline, 'CIRCLE')) ) > 0
-            CIR(c_, :) = textscan(tline, '%f %*d %*s %d %d %d', 1);
-            c_ = c_ + 1;
-        end
-        
-        
-        if ( length(findstr(tline, 'SEGMENT')) ) > 0
-            SEG(s_, :) = textscan(tline, '%f %*d %*s %d %d %d %d', 1);            
-            s_ = s_ + 1;
-        end
-    end
-
-    fclose(fid);
-    clear i _b;
-    
-    % x
-    % x = double(cell2mat(GPS(:, 3)));
-    % or
-    x = double(cell2mat(NAV(:, 4)));
-    % y
-    % y = double(cell2mat(GPS(:, 4)));
-    % or
-    y = double(cell2mat(NAV(:, 5)));
-    % z (altitude)
-    z = double(cell2mat(GPS(:, 7)));
-    
-    % TODO this thing of taking 5th element is just a temporary fix
[…]

### 2020-10-07 matlab/build_ck.m

@@ -1,74 +1,0 @@
-
-function [ckgck] = build_ck(spec, prof, t) 
-%build_ck.m Reads a mission specification file along with the output from
-%   powprof. Builds a vector of all the possible computational controls 
-%   [Ck in Equation (12)] and their  power consumption [g(Ck) in 
-%   Equation (13)]. The control vector is normalized over the systems
-%   time, for the purpose of simulation.
-%
-% Inputs:
-%   spec   : mission specification
-%   prof   : output from powprof (I expect this comes unchanged from
-%            powprof [which means ordered])
-%   t      : time used for the purpose of simulation
-%
-% Outputs:
-%   ckgck  : All the possible combinations of the QoS Ck, along with their
-%            instantaneous power consumption from powprof g(Ck)
-%   
-    u = [];
-    
-    % iterates for each line in the mission specification
-    for i = 1:size(spec, 1)
-        
-        % iterates for each time interval
-        for j = spec(i, 1):spec(i, 2)
-            
-            % just for the purpose of simulation; you generate all the
-            % possible combinations of computational control for the
-            % simulated time (and not all the times) 
-            if (~any(floor(t) == j))
-                continue;
-            end
-            jj = t(any(floor(t) == j, 2));
-            jj = jj(1);
-            
-            % makes all the possible combinations of controls of QoS
-            u1 = [];
-            for k = 3:2:size(spec, 2)
-                
-                % for the purpose of simulation the same step as in powprof
-                % is used (which can be easily adapted when using powprof)
-                uu = spec(i, k): ...
-                     prof(2, end - 1) - prof(1, end - 1):spec(i, k + 1);
-                
-                if (isempty(u1))
-                    u1 = transpose(uu);
-                else
-                    u1 = repmat(u1, size(uu, 2), 1);
-                    uu = repmat(uu, size(u1, 1) / size(uu, 2), 1);
-                    uu = uu(:);
-                    u1 = [ u1 uu ];
-                end
-            end
-            
-            % filling the control with the energy data
-            u1 = [ u1 zeros(size(u1, 1), 1) ];
-            
-            for k = 1:size(prof, 1)                
-                u1(all( ...
-                        u1(:, 1:end - 1) == prof(k, 1:end - 1), 2 ...
-                      ), end) = prof(k, end);
-            end
-            
-            tt = ones(size(u1, 1), 1) * jj;
-            
-            u = [ u; tt u1 ];
-            
-            clear tt uu u1 ui;
-        end
-    end
-    
-    ckgck = u;
-    
-end

### 2020-10-07 matlab/build_gdn2.m

@@ -1,29 +1,0 @@
-
-function [dpd, pdangle] = build_gdn2(E, ke, varphi, points)
-    
-    syms x y;
-    
-    % gradient
-    dvarphi = gradient(varphi, [x y]);
-    
-    dpd = E * dvarphi - ke * varphi * dvarphi;
-    
-    x = transpose(points(:, 1));
-    y = transpose(points(:, 2));
-    
-    pd = transpose(double(subs(dpd)));
-    
-    angle = atand(pd(:, 2) ./ pd(:, 1));
-    
-    angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) = angle(and(pd(:, 1) < 0, pd(:, 2) < 0)) + 180;
-    
-    % corresponds to if (pd(1) < 0 && pd(2) < 0) ...
-    
-    angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) = angle(and(pd(:, 1) < 0, pd(:, 2) > 0)) + 180;
-    
-    % corresponds to if (pd(1) < 0 && pd(2) > 0) ...
-     
-    angle = transpose(angle);
-    pdangle = angle;
-    dpd = pd;
-end

### 2020-10-07 matlab/build_model.m

@@ -1,81 +1,0 @@
-
-function [y, qq0] = build_model(r, mech, gck, mk, q0, P0, Q, R, t, eps)
-%build_model.m Builds the energy model [Equation (9b)] using Kalman Filter 
-%   as state observer [Equations (10--11)]
-%
-% Inputs:
-%   r      : the Fourier series order [Equation (6)]
-%   mech   : mechanical energy vector [W]. I.e., the data from flying the
-%            drone in simulation or data from real flights logging the
-%            flight controller
-%   u      : control [Equation (9b)]
-%   q0     : initial guess of the estimate of the state
-%   P0     : variance of the guessed estimate
-%   Q      : process noise covariance
-%   R      : sensor noise covariance
-%   t      : time used for the purpose of simulation
-%   eps    : used to return qq0
-%
-% Outputs:
-%   y      : energy evolution
-%   qq0    : the first estimated state value [Equation (8)] differs from
-%            mech < eps
-%
-
-    % system definition
-    j = 2*r + 1;
-    xi = 10;
-
-    An = @(n) [ 0 n/xi ; -n^2/xi^2 0 ];
-    A  = zeros(j);
-    A(1,1) = 1;
-    C = [1];
-
-    for i = 1:r
-        A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
-        C = [C 1 0];
-    end
-    
-    % control action [Equation (17)]
-    u = @(k) [gck(k); transpose(mk(k))];
-    B = [ 1                 zeros(1, size(mk, 2)); ...
-          zeros(j - 1, 1)   zeros(j - 1, size(mk, 2))  ];
-
-    clear i, An;
-    
-    % predicted energy evolution
-    y = [];
-
-    qq0 = [];
-    
-    % Kalman filter estimation
-    k = 1;
-    for y0_sensor = transpose(mech)
-        % getting the control at time k
-        u0 = u(k);
-        
-        % prediction
-        q1_minus = A * q0 + B*u0;
-        P1_minus = A * P0 * transpose(A) + Q;
-    
-        % estimation
-        K1 = (P1_minus * transpose(C)) / (C * P1_minus * transpose(C) + R);
-        q1 = q1_minus + K1 * (y0_sensor + u0(1) - C * q1_minus);
-        P1 = (eye(j) + K1 * C) * P1_minus;
-        y0_estimate = C * q1;
-    
-        % updating values for the next iteration
[…]

### 2020-10-07 matlab/main.m

@@ -1,94 +1,0 @@
-
-%main.m
-% Simulation in Matlab, use data directory to pass the required data in
-% the simulation. If you use the combo c_e (computational_energy.cvs...), 
-% m_e, m_s in simulation1, then use r = 3, column = 1, and ts = 200
-%
-
-%%
-disp('Model simulation')
-
-r = input('Fourier series order r: ');
-
-% getting mechanical energy data
-
-disp('Input mechanical energy data [csv]');
-[bn, folder] = uigetfile('.csv');
-file = csvread(fullfile([folder, bn]));
-
-column = input('Which column contains energy: ');
-file = file(:, [column]);
-
-ts = input('At what time step [ms]: ');
-tf = (1 / ts) * 1000 * size(file, 1);
-file = imresize(file, [100, 1]);
-t = transpose(linspace (0, tf, 100));
-
-clear column;
-
-% getting computational energy data
-disp('Input computational energy data (from powprof) [csv]');
-[bn, folder] = uigetfile('.csv');
-file2 = csvread(fullfile([folder, bn]));
-
-disp('Input mission specification [csv]');
-[bn, folder] = uigetfile('.csv');
-file3 = csvread(fullfile([folder, bn]));
-
-% computational model
-ckgck = build_ck(file3, file2, t);
-
-% initial guess
-j = 2*r + 1;
-q0 = ones(j, 1);
-P0 = eye(j);
-
-% process noise and sensor noise
-Q = eye(j);
-R = 1;
-
-% TODO: this selects just the highest possible control for each time
-% interval, which is not optimal; this would be part of the optimal control
-% policy once it's done
-gck = [];
-for i = 1:size(t, 1)
-    cckgck = ckgck(any(ckgck(:, 1) == t(i), 2), end);
-    
-    gck = [gck; cckgck(end)];
-end
-
-%TODO: the mechanical components of the control
-mk = zeros(size(t, 1), 1);
-
-% predicted energy evolution
-[y, qq0] = build_model(r, file,  gck, mk, q0, P0, Q, R, t, 0.001);
-
-%%
-plot(t, file + gck);
-clear file file2 file3;
-hold on;
-plot (t, y);
-
-legend('data', 'observer');
-
-%%
-
-syms x y;
[…]

### 2020-10-07 matlab/plot_gdn2.m

@@ -1,69 +1,0 @@
-
-function [] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
-        
-    figure;
-    
-    % just a nice effect nothing more...
-    varphi_plot2 = fimplicit(varphi);
-    set(varphi_plot2, 'Color', [.85 .85 .85], 'LineWidth', 10);
-    
-    hold on;
-    
-    varphi_plot = fimplicit(varphi);
-    set(varphi_plot, 'Color', 'black', 'LineWidth', 1.2);
-    
-    xlim([min max]);
-    ylim([min max]);
-        
-    x = transpose(points(:, 1));
-    y = transpose(points(:, 2));
-        
-    %% the vector field (of pd)
-    % a crazy workaround to plot those arrows...
-    
-    coeff = 0.45 * (max - min) / 25;
-    coeffm = 0.20 * (max - min) / 25;
-    coeffM = 0.30 * (max - min) / 25;
-    
-    dpdx = [x; x + coeff * cosd(pdangle)];
-    dpdy = [y; y + coeff * sind(pdangle)];
-    
-    arrowlxx = [x + coeffM * cosd(pdangle); dpdx(2, :)];
-    arrowlxy = [y + coeffm * sind(pdangle); dpdy(2, :)];
-    
-    arrowrxx = [x + coeffm * cosd(pdangle); dpdx(2, :)];
-    arrowrxy = [y + coeffM * sind(pdangle); dpdy(2, :)];
-    
-    plot(dpdx, dpdy, 'Color', [0.3010, 0.7450, 0.9330]);
-    
-    plot(arrowlxx, arrowlxy, 'Color', [0.3010, 0.7450, 0.9330]);
-    plot(arrowrxx, arrowrxy, 'Color', [0.3010, 0.7450, 0.9330]);
-    
-    %% animation
-    
-    xd = [1 0] * p;
-    yd = [0 1] * p;
-    
-    xdd = xd;
-    ydd = yd;
-    
-    for i=1:andu
-        x = xd;
-        y = yd;
-        [dpd, pdangle] = build_gdn2(E, ke, varphi, [x y]);
-        pd = transpose(double(subs(dpd)));
-        
-        pdangle = transpose(pdangle);
-        
-        xd = [xd + s * .1 * cosd(pdangle)];
-        yd = [yd + s * .1 * sind(pdangle)];
-        
-        xdd = [xdd; xd];
[…]

### 2020-10-07 icra-2021.tex
updated the intro (and working on the problem definition a bit)

@@
 \title{\LARGE \bf
-***
+Energy-Aware Dynamic Mission Planning Algorithm for UAVs
 }
@@
 
-Mission planning for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task.
-It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
+Planning a mission for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task.
+It requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
 Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}.
@@
 
-Energy planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning.
-Generally, these algorithms account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2004energy}.
-For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Further, past mission planning approaches also limit to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, and to the class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning.
+Generally, these algorithms output an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
+For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Furthermore, past mission planning algorithms--which include a broader concept of a mission being a set of tasks along with a motion plan--also focus on the trajectory~\cite{mei2005case,mei2006deployment}, and apply to the narrow class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 Yet, computations of such systems are only expected to increase in the near future.
-Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.
+Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs, correlate the extensively studied energy planning to the growing computational demands, and validate its findings using several UAVs.
 
@@
 We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm selects the controls (the QoS and TEEs) using a robust output feedback model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
+The algorithm outputs the controls (the QoS and TEEs parameters) using a robust output feedback model predictive control (MPC).
 
@@
 
+\begin{center}\vspace{.2cm}---\emph{I'll move this subsec under eq 9, it doesn't make sense now and my brain stopped working for this evening}---\vspace{.6cm}\end{center}
+
 \subsection{Control action}
@@
 
-Given a generic trajectory equation $\varphi$, the trajectory can be modeled by $\rho$ TEE parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
-Let us define $\mathbf{u}_{k,n}:=\{u_{k,0},\dots,u_{k,n-1},u_{k,n}^0,u_{k,n+1},\dots,u_{k,\rho_k-1}\}$, the set of these parameters can be expressed
-\begin{equation}\label{eq:tee-def}\begin{split}
-  \mathcal{M}_k:=\{u_{k,n} : \,
-  &\varphi_k(\mathbf{p}_{k,n}^0,\mathbf{u}_{k,n})\in\mathcal{P}\\
-  &\forall n\in\{0,\dots,\rho_k-1\}\},
-\end{split}\end{equation}
-where $\mathbf{p}_k^0$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge under any optimal TEE parameter $u_k^0$.
-Physically $\mathcal{M}_k$ contains all the controls generating the points over the area $\mathcal{P}$ defined in Equation~(\ref{eq:area}).
+Let us re-define the TEE introduced first in Subsection~\ref{sec:model} as a function $\varphi_k:\mathbb{R}^3\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of the position and $\rho$ TEE parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
+Given $\mathbf{u}_{k}:=\{u_{k,0},\dots,u_{k,\rho-1}\}$, the set of these parameters at time instant $k$ can be expressed
+\begin{equation}\label{eq:tee-def}
+  \mathcal{M}_k:=\{u_k\in\mathbf{u}_k : \varphi_k(\mathbf{p},\mathbf{u}_k)\in\mathcal{P}_k\},
+\end{equation}
+where $\mathbf{p}\in\mathcal{P}_k$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge under any optimal TEE parameter $u_k^0$.
+Physically, $\mathcal{M}_k$ contains all the controls generating the points over the area $\mathcal{P}$ defined in Equation~(\ref{eq:area}).
 
@@
   \mathbf{u}_k=\left[\begin{array}{c}
-    g\left(\mathcal{C}_k\right) \\\hline \mathcal{M}_k
+    g\left(\mathcal{C}_k\right)-g\left(\mathcal{C}_{k-1}\right) \\\hline \mathcal{M}_k
   \end{array}\right],\,\,\,

### 2020-10-08 icra-2021.tex
preparing a decent state for the meeting tomorrow

@@
 Planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning.
-Generally, these algorithms output an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
+Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
 For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
@@
 Yet, computations of such systems are only expected to increase in the near future.
-Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs, correlate the extensively studied energy planning to the growing computational demands, and validate its findings using several UAVs.
+Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs, correlate the extensively studied energy planning to the growing computational demands, and validate its findings using UAVs.
 
@@
 
-The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}.
+The algorithm relies on the assumptions of the mission--a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}.
 The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
 We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm outputs the controls (the QoS and TEEs parameters) using a robust output feedback model predictive control (MPC).
+The algorithm selects the controls (the QoS and TEEs parameters) using a robust output feedback model predictive control (MPC).
 
 The remainder of the paper is organized as follows.
-The dynamic mission planning problem is set in Section~\ref{sec:prob}, along a suitable model for the energy and position of the UAV.
+The dynamic mission planning problem is set in Section~\ref{sec:prob}.
+A suitable model for the energy and position of the UAV in Section~\ref{sec:model}.
 The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}.
@@
 Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
-In practice, complex monitoring strategies are often implemented utilizing UAVs and are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
+Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 
-The UAV flies in ellipses shifted in time--a survey pattern optimized for the craft's dynamics--detects obstacles using a convolutional neural network (CNN) and informs grounded mobile robots employed for future harvesting.
+The algorithm inputs the mission
+\begin{equation}
+  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{i=1,\dots,\rho}(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}):\,\forall k\in\mathbb{T}\right\},
+\end{equation}
+where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$.
 
-\subsection{Position and energy state}
+% Approx at this latitude I would actually either put something on the lines 'in the presented problem TEEs and QoS parameters corresponds to this and that...
+Thoughts?
+Because it sounds to me better if we put this into the experimental results section rather than here
+
+It outputs the correction to the position and the instantaneous energy consumption, while it adapts the controls $\mathbf{u}_k:=(c_k,\text{QoS}_{k,1},\dots,\text{QoS}_{k,\rho})$, the TEE and QoS parameters.
+
+%%%%%%%%%%%%%%%
+\section{Model}
 \label{sec:model}
 
-We use the state to estimate the UAV's position in space and energy in time.
+The state is the UAV's position in space and the energy evolution in time.
+Despite we show a linear relation between instantaneous energy and energy evolution, the two are different.
+We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
+
 Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
 some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the \emph{position evolution} along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}.
-The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$.
-To this end, the TEE is satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points.
+We build the path with the TEE, being such function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points.
 
@@
 
-\subsection{Position evolution and guidance action}
+\subsection{Position evolution}
 \label{sec:position}
@@
 
-Let us define $\mathcal{P}_k$, the area that discloses all the possible deviations form the $k$-th TEE 
+Let us define $\mathcal{P}_k$, the set that delimits all the possible deviations form the $k$-th TEE
 \begin{equation}\label{eq:area}
-  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p})\leq\overline{c}_k\},
+  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\rho})\leq\overline{c}_k\},
 \end{equation}
-where $\underline{c}_k\in\mathbb{R}_{\leq 0},\overline{c}_k\in\mathbb{R}_{\geq 0}$ are the constraints: $\underline{a},\overline{a}$ returns the upper and lower bound of $a$ from the user-defined mission specification.
-In particular, the specification contains TEEs along the ROS nodes configuration and a lookup table for TEEs and QoS parameters (the former are the above mentioned $c$s, the latter explained in Subsection~\ref{sec:computations-model}).
+where $\underline{c}_k,\overline{c}_k$ are the bounds where the TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
 
-The algorithm uses the concept to select $c$ with the highest energy value under the energy budget constraints.
-Assume at time $k$ the algorithm selects the TEE $\varphi_k$ with the highest energy value being $c_k$, we design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
+The algorithm uses the concept to select $\varphi(\mathbf{p},\mathbf{c}_k)=c_k\in\mathbb{R}$ s.t.
+$\mathbf{p}\in\mathcal{P}_k$ with the highest energy value under the energy budget constraints.
+We design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
 
-Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to the TEE to follow can be expressed as the desired velocity vector
+Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to follow can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varPhi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+
+% Next 3 paragraph are unnecessary; but I am struggling what to do with the control not being defined in (2). Thoughts on this? Can I just put the desired velocity vector as the control?
 
@@
 where $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, $k_d\in\mathbb{R}_{\geq 0}$ adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 
@@
 In Equation~(\ref{eq:qos-def}) we defined the control due to the computations, here we do the same for the trajectory.
-
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-10-08 icra-2021.tex
paper fixed with latests

@@
 The algorithm inputs the mission
-\begin{equation}
-  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{i=1,\dots,\rho}(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}):\,\forall k\in\mathbb{T}\right\},
+\begin{equation}\label{eq:mission}
+  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{n=0,\dots,\rho-1}(\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}):\,\forall k\in\mathbb{T}\right\},
 \end{equation}
@@
 
-It outputs the correction to the position and the instantaneous energy consumption, while it adapts the controls $\mathbf{u}_k:=(c_k,\text{QoS}_{k,1},\dots,\text{QoS}_{k,\rho})$, the TEE and QoS parameters.
+It outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.
 
@@
 
-\subsection{Position evolution}
+\subsection{Trajectory}
 \label{sec:position}
@@
 \begin{equation}\label{eq:area}
-  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\rho})\leq\overline{c}_k\},
+  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\sigma})\leq\overline{c}_k\},
 \end{equation}
-where $\underline{c}_k,\overline{c}_k$ are the bounds where the TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
+where $\underline{c}_k,\overline{c}_k$ are the bounds from $\mathcal{M}$ that disclose the are over which the TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
 
@@
 The energy evolution analysis necessitates the following realistic assumption.
-\begin{assm}\label{assm:periodic} The position evolution is periodic, in the sense that it presents repetitive patterns.
+\begin{assm}\label{assm:periodic} The trajectory is periodic, in the sense that it presents repetitive patterns.
 \end{assm}
-Formally, given two time instants $k_1,k_2\in\mathbb{R}_{\geq 0}$ such that $k_1>k_2$ and a value $n\in\mathbb{R}_{\geq 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$ such that
+Formally, given two time instants $k_1,k_2\in\mathbb{T}$ s.t. $k_1>k_2$ and a value $n\in\mathbb{R}_{\geq 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
 \begin{equation}
-  \|\mathbf{p}(t)-\mathbf{p}(t+n)\|= e\,\,\,\forall t\in\{k_1,...,k_2\}.
+  \|\mathbf{p}_{k}-\mathbf{p}_{k+n}\|= e\,\,\,\forall k\in[k_1,k_2].
 \end{equation}
-We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$.
+We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$ or omitted under specific conditions.
 
-Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
+Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy estimation of such a periodic trajectory
 \begin{equation}\label{eq:fourier}
@@
 
-The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear time-invariant state-space model
+Suppose no disturbances in form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting otherwise for the unknown state and output.
+The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
 \begin{equation}\label{eq:state-perf}\begin{cases}
-  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)\\%+w(t)\\
-  y(t)&=C\mathbf{q}(t)%+v(t)
+  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
+  y_k&=C\mathbf{q}_k+v_k
 \end{cases},\end{equation}
-where $y(t)\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption.
+where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption.
 We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state.
-The control $\mathbf{u}$ along with the input matrix $B$ are defined later in Subsection~\ref{sec:control-action}, the state $\mathbf{q}$ mimics the original Fourier series coefficients, and
-
+The state $\mathbf{q}$ mimics the original Fourier series coefficients, and
 \begin{equation}\label{eq:state-details}\begin{split}
-  \mathbf{q}(t)&=\left[\begin{array}{cccccc}
+  \mathbf{q}_k&=\left[\begin{array}{cccccc}
     \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
@@
 \end{split}\end{equation}
-where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
+where $\mathbf{q}_k\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
 In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remaining.
 
-We further model the system of Equation~(\ref{eq:state-perf}) plus disturbances with the following discrete time model
-\begin{equation}\label{eq:state-unct}
-  \begin{cases}
-  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
-  y_k&=C\mathbf{q}_k+v_k
-  \end{cases},
-\end{equation}
-where $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ account for unknown state and output disturbances.
-In the case of the system behaving ideally (i.e., with zero disturbances), we expect a set of states evolving accordingly to their output.
-Such observation is summarized in the following Lemma.
+The control $\mathbf{u}$ along with the input matrix
+\begin{equation}\label{eq:state-control}\begin{split}  
+  \mathbf{u}_k&=\begin{bmatrix}g(\text{QoS}_k)-g(\text{QoS}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T\\
+  B&=\left[\begin{array}{cccc}
+    1&         &       &  \\
+     & \omega_{k,1}&       &  \\
+     &         & \ddots&  \\
+     &         &       & \omega_{k,\sigma}
+  \end{array}\right]
+\end{split}\end{equation}
+where $\text{QoS}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{-1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}$ and $B\in\mathbb{R}^{j\times l}$.
+Moreover, the first item on the diagonal is one, while the others are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE parameter to the instantaneous energy.
+Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
+The energy due to the change of explicit trajectory equation parameters is merely a linear combination of the gain factor and the value of the TEE.
+Nevertheless, the change updates the trajectory which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
+
+In the case of the system behaving ideally (i.e., with zero disturbances), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
 
@@
 The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds an energy model.
-Specifically, the tool builds a multivariate linear interpolation from the mission specification.
-It hence requires the user to implement a ROS system with one or more computationally expensive ROS nodes which change the computational load by node-specific ROS parameters (QoS).
+Specifically, the tool builds a linear interpolation, one per each task.
+It hence requires the user to implement the mission as a ROS system with one or more ROS nodes which change the computational load by node-specific ROS parameters (QoS).
 
-Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action
+Suppose the system is composed of $\sigma$ ROS nodes. Let us define a computational control action
 \begin{equation}\label{eq:qos-def}
-  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\,\,\forall n\in\{0,\dots,\sigma-1\}\right\},
+  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_{k,n}\,\,\,\forall n\in\{0,\dots,\sigma-1\},\,\forall k\in\mathbb{T}\right\},
 \end{equation}
-where $\text{QoS}_n(k):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of.
+where $\text{QoS}_n(k):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values.
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
@@
 \begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^c:&=g\left(\text{QoS}_0\left(k\right),\dots,\text{QoS}_{\sigma-1}\left(k\right)\right)=g\left(\mathcal{C}_{k}\right).\\
+  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathcal{C}_{k}\right).\\
 \end{split}\end{equation}
@@
 \begin{equation}\label{eq:qos-lims}\begin{split}
-  \underline{\text{QoS}}_n(k)\leq \,&\text{QoS}_n(k)\leq \overline{\text{QoS}}_n(k),\\
-  &\forall n\in\{0,\cdots,\sigma-1\},
+  \underline{\text{QoS}}_{k,n}\leq \,&\text{QoS}_{k,n}\leq \overline{\text{QoS}}_{k,n},\\
+  &\forall n\in\{0,\cdots,\sigma-1\},\,\forall k\in\mathbb{T},
 \end{split}\end{equation}
-where the values $\underline{\text{QoS}}_n(k),\overline{\text{QoS}}_n(k)$ are retrieved from the mission specification.
-
-\begin{center}\vspace{.2cm}---\emph{I'll move this subsec under eq 9, it doesn't make sense now and my brain stopped working for this evening}---\vspace{.6cm}\end{center}
-
-\subsection{Control action}
-\label{sec:control-action}
-
-We build the control action $\mathbf{u}$ from Equation~(\ref{eq:state-perf})~and~(\ref{eq:state-unct}) in two steps.
-In Equation~(\ref{eq:qos-def}) we defined the control due to the computations, here we do the same for the trajectory.
-
-Let us re-define the TEE introduced first in Subsection~\ref{sec:model} as a function $\varphi_k:\mathbb{R}^3\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of the position and $\rho$ TEE parameters $\mathcal{M}\in\mathbb{R}^\rho$, e.g., the constants of a linear function, the radius of a circle, and semi-major and minor axis of an ellipse.
-Given $\mathbf{u}_{k}:=\{u_{k,0},\dots,u_{k,\rho-1}\}$, the set of these parameters at time instant $k$ can be expressed
-\begin{equation}\label{eq:tee-def}
-  \mathcal{M}_k:=\{u_k\in\mathbf{u}_k : \varphi_k(\mathbf{p},\mathbf{u}_k)\in\mathcal{P}_k\},
-\end{equation}
-where $\mathbf{p}\in\mathcal{P}_k$ is any optimal point which let the trajectory explicit function $\varphi_k$ converge under any optimal TEE parameter $u_k^0$.
-Physically, $\mathcal{M}_k$ contains all the controls generating the points over the area $\mathcal{P}$ defined in Equation~(\ref{eq:area}).
-
-The explicit trajectory equation $\varphi_k$ can be different at different states $k$, meaning the vector field and guidance action, from Equation~(\ref{eq:pd})~and~(\ref{eq:uav-cont}) respectively, will account for the sudden change of trajectory during the mission.
-
-It is worth considering that the number of parameters at state $k$ is a parameter of the state.
-This is for the sake of generality, as the mission specification might contain different explicit equations for different states.
-For instance, the fixed-wing craft might follow an ellipse function throughout the mission and heading a linear function while landing.
-
-The TEE parameters and QoS, $\mathcal{M}$ and $\mathcal{C}$ defined in Equation~(\ref{eq:tee-def})~and~(\ref{eq:qos-def}), are incorporated in the system in Equation~(\ref{eq:state-unct}) using the input matrix
-\begin{equation}
-  \mathbf{u}_k=\left[\begin{array}{c}
-    g\left(\mathcal{C}_k\right)-g\left(\mathcal{C}_{k-1}\right) \\\hline \mathcal{M}_k
-  \end{array}\right],\,\,\,
-  B=\left[\begin{array}{ccccccc}
-    1 & \vline & 0 & \cdots & 0\\\hline
-    0 & \vline & 0 & \cdots & 0\\
-    \vdots & \vline & \vdots & \ddots & \vdots\\
-    0 & \vline & 0 & \cdots & 0
-  \end{array}\right],
-\end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eq:state-perf})~and~(\ref{eq:state-unct}).
-Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$.
-This adds the computational model component to the energy evolution in the system.
-The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors $y^s$ defined in Subsection~\ref{sec:state-est} and adjust the energy evolution accordingly.
+where the values $\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}$ are retrieved from the mission $\mathcal{M}$.
 
@@
 
-The main goal of the algorithm is to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$--estimated from sensors' measurements--from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$.
+%The main goal of the algorithm is to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$--estimated from sensors' measurements--from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$.
 This is achieved by solving online a finite horizon optimal control problem by the hand of a modification of a model predictive control (MPC) algorithm~\cite{rawlings2017model}.
@@
 \end{proof}
+
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-10-08 icra-2021.tex
typos, a lot of typos...

@@
 \end{equation}
-where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$.
+where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f\in\mathbb{R}_{\geq 0}$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan--an ordered pair), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$ (a set of also ordered pairs).
 
@@
 \end{equation}
-where $\underline{c}_k,\overline{c}_k$ are the bounds from $\mathcal{M}$ that disclose the are over which the TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
+where $\underline{c}_k,\overline{c}_k$ are the bounds from the mission $\mathcal{M}$, that disclose the area where TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
 
-The algorithm uses the concept to select $\varphi(\mathbf{p},\mathbf{c}_k)=c_k\in\mathbb{R}$ s.t.
-$\mathbf{p}\in\mathcal{P}_k$ with the highest energy value under the energy budget constraints.
-We design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
+The algorithm uses the concept to select $\varphi(\mathbf{p},\mathbf{c}_k)=c_k\in\mathbb{R}$ with the highest energy value under the energy budget constraints.
 
-Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to follow can be expressed as the desired velocity vector
+For the purpose, we design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
+Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$.
+The direction to follow can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation}
-We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$ or omitted under specific conditions.
+We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.
 
@@
 We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state.
-The state $\mathbf{q}$ mimics the original Fourier series coefficients, and
+The state $\mathbf{q}$ mimics the original Fourier series coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
@@
 \begin{equation}\label{eq:state-control}\begin{split}  
-  \mathbf{u}_k&=\begin{bmatrix}g(\text{QoS}_k)-g(\text{QoS}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T\\
+  \mathbf{u}_k&=\begin{bmatrix}g(\mathcal{C}_k)-g(\mathcal{C}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T\\
   B&=\left[\begin{array}{cccc}
-    1&         &       &  \\
-     & \omega_{k,1}&       &  \\
+    1& \omega_{k,1}& \cdots& \omega_{k,\sigma}  \\
+     &            0&       &  \\
      &             & \ddots&  \\
-     &         &       & \omega_{k,\sigma}
+     &             &       & 0
   \end{array}\right]
 \end{split}\end{equation}
-where $\text{QoS}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{-1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}$ and $B\in\mathbb{R}^{j\times l}$.
-Moreover, the first item on the diagonal is one, while the others are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE parameter to the instantaneous energy.
+where $\mathcal{C}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{-1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
+Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE parameter to the instantaneous energy.
 Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
@@
 Nevertheless, the change updates the trajectory which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
+The linearity simulates how a variation affects the energy, for instance, a decrement in the radius of a circular TEE will add a negative contribution, the simulate the lowering of instantaneous energy consumption.
 
@@
 \begin{lem}\label{lem:state-vs-energy}
-  Suppose the system of Equation~(\ref{eq:state-unct}) evolves with no disturbances ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
+  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no disturbances ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
   \begin{equation}
@@
 Specifically, the tool builds a linear interpolation, one per each task.
-It hence requires the user to implement the mission as a ROS system with one or more ROS nodes which change the computational load by node-specific ROS parameters (QoS).
+It hence requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters (QoS).
 
@@
 \end{equation}
-where $\text{QoS}_n(k):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values.
+where $\text{QoS}_{k,n}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values.
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
@@
 \begin{thm}\label{thm:state-vs-energy}
-  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
-  Assume Assumption~\ref{assm:periodic} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eq:area}), and is following $\varphi$ with the direction $\hat{\mathbf{p}}_d$ defined in~\ref{eq:pd}.
+  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{T}$.
+  Assume Assumption~\ref{assm:periodic} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eq:area}), and is following $\varphi$ with the direction $\dot{\mathbf{p}}_d$ defined in~\ref{eq:pd}.
 Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.

### 2020-10-12 icra-2021.tex
fixes from the last meeting (attempt 1)

@@
 \usepackage{url}
+
+%% hyperref
+% and an override to make hyperref work with ieeeconf.cls
+\makeatletter
+\let\NAT@parse\undefined
+\makeatother
+\usepackage{hyperref}
 
@@
 It optimizes TEEs--an abstraction of the path to follow--and guides the UAV using a vector field that converges smoothly to the path.
-Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
+%Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
 Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
-
-The algorithm relies on the assumptions of the mission--a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}.
+It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
 The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
 We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm selects the controls (the QoS and TEEs parameters) using a robust output feedback model predictive control (MPC).
+The algorithm selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).
+
+To show case the algorithm we consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
+The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
+The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis.
+Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
+Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
 
 The remainder of the paper is organized as follows.
-The dynamic mission planning problem is set in Section~\ref{sec:prob}.
-A suitable model for the energy and position of the UAV in Section~\ref{sec:model}.
+The dynamic mission planning overview is set in Section~\ref{sec:prob}, along a suitable model for the energy and position of the UAV.
 The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Problem Statement}
+\section{Mission Planning Overview}
 \label{sec:prob}
 
-We consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
-Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
-The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
-Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
-
-The algorithm inputs the mission
+The mission is a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints
 \begin{equation}\label{eq:mission}
@@
 
-It outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.
+The algorithm inputs the mission and outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.
 
 %%%%%%%%%%%%%%%
-\section{Model}
+\subsection{Model}
 \label{sec:model}

### 2020-10-13 icra-2021.tex
fixes, fixes, and again fixes...

@@
 
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
 %% correct bad hyphenation here
@@
     organization={ACM}
-  }
-  @inproceedings{boroujerdian2018compute,
-    title={Why Compute Matters for UAV Energy Efficiency?},
-    author={Boroujerdian, Behzad and Genc, Hasan and Krishnan, Srivatsan and Faust, Aleksandra and Reddi, Vijay Janapa},
-    booktitle={2nd International Symposium on Aerial Robotics},
-    year={2018}
   }
@@
   }
-  @inproceedings{uragun2011energy,
-    title={Energy efficiency for unmanned aerial vehicles},
-    author={Uragun, Balemir},
-    booktitle={2011 10th International Conference on Machine Learning and Applications and Workshops},
-    volume={2},
-    pages={316--320},
-    year={2011},
-    organization={IEEE}
-  }
   @inproceedings{kreciglowa2017energy,
@@
     organization={IEEE}
-  }
-  @article{kanellakis2017survey,
-    title={Survey on computer vision for UAVs: Current developments and trends},
-    author={Kanellakis, Christoforos and Nikolakopoulos, George},
-    journal={Journal of Intelligent \& Robotic Systems},
-    volume={87},
-    number={1},
-    pages={141--168},
-    year={2017},
-    publisher={Springer}
   }
@@
   }
-  @article{berenz2012autonomous,
-    title={Autonomous battery management for mobile robots based on risk and gain assessment},
-    author={Berenz, Vincent and Tanaka, Fumihide and Suzuki, Kenji},
-    journal={Artificial Intelligence Review},
-    volume={37},
-    number={3},
-    pages={217--237},
-    year={2012},
-    publisher={Springer}
-  }
   @inproceedings{kim2005energy,
@@
   }
-  @article{morales2009power,
-    title={Power consumption modeling of skid-steer tracked mobile robots on rigid terrain},
-    author={Morales, Jesus and Martinez, Jorge L and Mandow, Anthony and Garc{\'\i}a-Cerezo, Alfonso J and Pedraza, Salvador},
-    journal={IEEE Transactions on Robotics},
-    volume={25},
-    number={5},
-    pages={1098--1108},
-    year={2009},
-    publisher={IEEE}
-  }
   @book{wahab2015energy,
@@
     publisher={IEEE}
-  }
-  @article{rao2003battery,
-    title={Battery modeling for energy aware system design},
-    author={Rao, Ravishankar and Vrudhula, Sarma and Rakhmatov, Daler},
-    journal={Computer},
-    volume={36},
-    number={12},
-    pages={77--87},
-    year={2003},
-    publisher={IEEE}
-  }
-  @inproceedings{chiasson2003estimating,
-    title={Estimating the state of charge of a battery},
-    author={Chiasson, John and Vairamohan, Baskar},
-    booktitle={Proceedings of the 2003 American Control Conference, 2003.},
-    volume={4},
-    pages={2863--2868},
-    year={2003},
-    organization={IEEE}
-  }
-  @inproceedings{pang2001battery,
-    title={Battery state-of-charge estimation},
-    author={Pang, Shuo and Farrell, Jay and Du, Jie and Barth, Matthew},
-    booktitle={Proceedings of the 2001 American control conference.(Cat. No. 01CH37148)},
-    volume={2},
-    pages={1644--1649},
-    year={2001},
-    organization={IEEE}
-  }
-  @article{partovibakhsh2014adaptive,
-    title={An adaptive unscented Kalman filtering approach for online estimation of model parameters and state-of-charge of lithium-ion batteries for autonomous mobile robots},
-    author={Partovibakhsh, Maral and Liu, Guangjun},
-    journal={IEEE Transactions on Control Systems Technology},
-    volume={23},
-    number={1},
-    pages={357--363},
-    year={2014},
-    publisher={IEEE}
-  }
-  @inproceedings{zhang2009battery,
-    title={Battery state estimation using unscented kalman filter},
-    author={Zhang, Fei and Liu, Guangjun and Fang, Lijin},
-    booktitle={2009 IEEE International Conference on Robotics and Automation},
-    pages={1863--1868},
-    year={2009},
-    organization={IEEE}
-  }
-  @inproceedings{hasan2018exogenous,
-    title={Exogenous kalman filter for state-of-charge estimation in lithium-ion batteries},
-    author={Hasan, Agus and Skriver, Martin and Johansen, Tor Arne},
-    booktitle={2018 IEEE Conference on Control Technology and Applications (CCTA)},
-    pages={1403--1408},
-    year={2018},
-    organization={IEEE}
-  }
-  @inproceedings{nardi2015introducing,
-    title={Introducing SLAMBench, a performance and accuracy benchmarking methodology for SLAM},
-    author={Nardi, Luigi and Bodin, Bruno and Zia, M Zeeshan and Mawer, John and Nisbet, Andy and Kelly, Paul HJ and Davison, Andrew J and Luj{\'a}n, Mikel and O'Boyle, Michael FP and Riley, Graham and others},
-    booktitle={2015 IEEE International Conference on Robotics and Automation (ICRA)},
-    pages={5783--5790},
-    year={2015},
-    organization={IEEE}
   }
@@
   }
-  https://mavlink.io/
   @article{ullah2018pednet,
@@
 
-% what I want to do with words.
-% diggested version of the technical details
-% strory goes to the introduction
-% depends
-% big picture in the introduction to agree what specifically I am trying to do right now
+Planning a mission for unmanned aerial vehicles (UAVs) operating outdoors is a challenging task.
+Scenarios such as precision agriculture, search and rescue, and surveillance require advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
+Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}.
+Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
+The algorithm attempts to combine and generalize some of the past body of knowledge on robot planning, and highlights the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
 
-Planning a mission for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task.
-It requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
-Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}.
-Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs that highlights the increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.
+Planning algorithms for mobile robots broadly are not a new concept, in that they are correlated to such topics as trajectory generation and path planning.
+Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to few robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
+For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Furthermore, past mission planning algorithms--which include a broader concept of a mission being a set of tasks along with a motion plan--also focus on the trajectory~\cite{mei2005case,mei2006deployment}, and apply to few robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Yet, computations of such systems are only expected to increase in the near future.
 
-Planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning.
-Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
-For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Furthermore, past mission planning algorithms--which include a broader concept of a mission being a set of tasks along with a motion plan--also focus on the trajectory~\cite{mei2005case,mei2006deployment}, and apply to the narrow class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-Yet, computations of such systems are only expected to increase in the near future.
-Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs, correlate the extensively studied energy planning to the growing computational demands, and validate its findings using UAVs.
-
-The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path.
+The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) values of the onboard computations, and the trajectory-explicit equations (TEEs) adjustments of the motion plan.
 Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain.
 The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
-It optimizes TEEs--an abstraction of the path to follow--and guides the UAV using a vector field that converges smoothly to the path.
-%Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis.
-Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
+It optimizes TEEs--an abstraction of the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
 It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
 The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
-We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption.
-The algorithm selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).
+It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator.
+It selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).
 
-To show case the algorithm we consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
-Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}.
-The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
+In the spirit of reducing waste, costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
+The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a monitoring mission optimized for the craft's dynamics.
 The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis.
-Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
@@
 The remainder of the paper is organized as follows.
-The dynamic mission planning overview is set in Section~\ref{sec:prob}, along a suitable model for the energy and position of the UAV.
-The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}.
-Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance.
+The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the energy and position.
+The algorithm that uses the model and solves the dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
+Section~\ref{sec:experimental} presents the result and showcase the performance.
 The paper finishes with some conclusions in Section~\ref{sec:conclusion}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Mission Planning Overview}
@@
 
-The mission is a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints
-\begin{equation}\label{eq:mission}
-  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{n=0,\dots,\rho-1}(\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}):\,\forall k\in\mathbb{T}\right\},
+Let the mission be defined by a generic continuous twice differentiable TEE $\varphi$ (being such function satisfied $\varphi\rightarrow 0$ for all the approaching points) and a set of $\sigma$ tasks.
+Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
+At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is formally defined as the ordered list
+\begin{equation}\label{eq:mission}\begin{split}
+  \mathcal{M}_k:=\{(\varphi,\psi_1,...,\psi_\sigma)\mid\exists&\,\,\varphi\in\mathbb{C}_k,\,\\&\psi_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
+\end{split}\end{equation}
+where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is a formulation for the TEE $\varphi$ adjustments constraints, and $\mathbb{S}_{k,i}:=[\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ for the $i$-th task QoS value constraints.
+
+The overall plan is the union of all the missions: a set of TEEs, tasks, and TEEs and QoS parameters. If the system is sampled discrete-time for simplicity
+\begin{equation}
+  \mathcal{M}:=\bigcup_{i\in[tf]}{\mathcal{M}_i},
 \end{equation}
-where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f\in\mathbb{R}_{\geq 0}$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan--an ordered pair), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$ (a set of also ordered pairs).
+the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the control in function of the TEE and QoS parameters--an action performed evolving the mission state.
 
-% Approx at this latitude I would actually either put something on the lines 'in the presented problem TEEs and QoS parameters corresponds to this and that...
-Thoughts?
-Because it sounds to me better if we put this into the experimental results section rather than here
-
-The algorithm inputs the mission and outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.
-
-%%%%%%%%%%%%%%%
-\subsection{Model}
+\subsection{Mission state}
 \label{sec:model}
 
-The state is the UAV's position in space and the energy evolution in time.
-Despite we show a linear relation between instantaneous energy and energy evolution, the two are different.
+The mission state is the UAV's position in space and the energy evolution in time.
+Despite we show a linear relation between the instantaneous energy and the energy evolution, the two are different.
 We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
-Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t.
-some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the \emph{position evolution} along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}.
-We build the path with the TEE, being such function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points.
+Consider the position $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$, the set
+\begin{equation}\label{eq:area}
+  \mathcal{P}_k:=\{\mathbf{p}\mid\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
+\end{equation}
+delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$.
 
-We build the \emph{energy evolution} $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
-
-\subsection{Trajectory}
-\label{sec:position}
-
-We consider a non-holonomic 2D model of the UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
-\begin{equation}\label{eq:uav-kinem}\begin{cases}
-  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+\mathbf{d}(t)\\
-  \dot{\psi}(t)&=u(\mathbf{p}(t))
-\end{cases},
-\end{equation}
-where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$.
-
-Let us define $\mathcal{P}_k$, the set that delimits all the possible deviations form the $k$-th TEE
-\begin{equation}\label{eq:area}
-  \mathcal{P}_k:=\{\mathbf{p}:\underline{c}_k\leq\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\sigma})\leq\overline{c}_k\},
-\end{equation}
-where $\underline{c}_k,\overline{c}_k$ are the bounds from the mission $\mathcal{M}$, that disclose the area where TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ is free to evolve using controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\sigma}$.
-
-The algorithm uses the concept to select $\varphi(\mathbf{p},\mathbf{c}_k)=c_k\in\mathbb{R}$ with the highest energy value under the energy budget constraints.
-
-For the purpose, we design a guidance action $u$ that heads to such TEE by minimizing the norm $\|\varphi_k(\mathbf{p})-c_k\|$.
-Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$.
-The direction to follow can be expressed as the desired velocity vector
+The algorithm uses the concept to select $\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ with the highest energy value under the constraints, and \emph{evolves the position} using the vector field of $\varPhi:=\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ and deriving the direction to follow.
+It can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varPhi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient at the point $\mathbf{p}$, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference.
 
-% Next 3 paragraph are unnecessary; but I am struggling what to do with the control not being defined in (2). Thoughts on this? Can I just put the desired velocity vector as the control?
-
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\chi\in(-\pi,\pi]$ due to the atmospheric interference.
-
-Let us further define $\hat{\mathbf{p}}:=\mathbf{p}/\|\mathbf{p}\|$, the desired course heading rate $\dot{\chi_d}$ is computed by sensing the position $\mathbf{p}$, the ground velocity $\dot{\mathbf{p}}$, and is expressed
-\begin{equation}\label{eq:chid}\begin{split}
-  &\dot{\chi}_d(\mathbf{p})=-E\frac{\dot{\mathbf{p}}_d}{\|\dot{\mathbf{p}}_d\|^2}\cdot\\
-  &\hspace{2ex}\left( E\hat{\dot{\mathbf{p}}}_d\hat{\dot{\mathbf{p}}}_d^TE\left( (E-k_e\varPhi)H(\varPhi)\dot{\mathbf{p}}-k_e\nabla\varPhi^T\dot{\mathbf{p}}\nabla\varPhi \right) \right)^T,
-\end{split}
-\end{equation} 
-where $H(\cdot)$ is defined as the Hessian operator and $\dot{\mathbf{p}}_d:=\dot{\mathbf{p}}_d(\mathbf{p})$ for brevity; the physical meaning is that the curvature of the desired trajectory has to be known in order to be tracked.
-
-The guidance action can be expressed
-\begin{equation}\label{eq:uav-cont}
-  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
-\end{equation} 
-where $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, $k_d\in\mathbb{R}_{\geq 0}$ adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
+The algorithm \emph{evolves the energy} using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader in the next subsection) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 
-The energy evolution analysis necessitates the following realistic assumption.
-\begin{assm}\label{assm:periodic} The trajectory is periodic, in the sense that it presents repetitive patterns.
-\end{assm}
-Formally, given two time instants $k_1,k_2\in\mathbb{T}$ s.t. $k_1>k_2$ and a value $n\in\mathbb{R}_{\geq 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
-\begin{equation}
-  \|\mathbf{p}_{k}-\mathbf{p}_{k+n}\|= e\,\,\,\forall k\in[k_1,k_2].
-\end{equation}
-We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.
-
-Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy estimation of such a periodic trajectory
+Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy estimation of the mission
 \begin{equation}\label{eq:fourier}
@@
   B&=\left[\begin{array}{cccc}
-    1& \omega_{k,1}& \cdots& \omega_{k,\sigma}  \\
+    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
      &            0&       &  \\
@@
 Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE parameter to the instantaneous energy.
+
+The energy evolution analysis necessitates the following realistic assumption.
+\begin{assm}\label{assm:periodic} 
+Given two time instants $k_1,k_2\in[t_f]$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{R}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
+\begin{equation}
+  \abs{y_{k}-y_{k+n}}= e\,\,\,\forall k\in[k_1,k_2].
+\end{equation}
+\end{assm}
+Physically, the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns.
+We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.
+
 Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
@@
 
-In the case of the system behaving ideally (i.e., with zero disturbances), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
+In the case of the system behaving ideally (i.e., with zero uncertainty), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
 
 \begin{lem}\label{lem:state-vs-energy}
-  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no disturbances ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
+  Given two time instants $k_1,k_2\in[t_f]$, suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
   \begin{equation}
-    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,1}\|\iff y_{k,0}\geq y_{k,1}.
+    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
   \end{equation}
@@
 \end{proof}
-
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 

### 2020-10-13 icra-2021.tex
late night fix

@@
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
-The algorithm attempts to combine and generalize some of the past body of knowledge on robot planning, and highlights the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
+The algorithm attempts to combine and generalize some of the past body of knowledge on the mobile robot planning problem, and highlights the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
 
@@
 The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) values of the onboard computations, and the trajectory-explicit equations (TEEs) adjustments of the motion plan.
-Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain.
+Our goal is a mission extension by optimizing both QoS and TEEs parameters as the UAV flies and its batteries drain.
 The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
@@
 The remainder of the paper is organized as follows.
-The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the energy and position.
+The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
 The algorithm that uses the model and solves the dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
@@
 
-Let the mission be defined by a generic continuous twice differentiable TEE $\varphi$ (being such function satisfied $\varphi\rightarrow 0$ for all the approaching points) and a set of $\sigma$ tasks.
+Let the mission be defined by a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks.
 Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
@@
 \end{split}\end{equation}
-where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is a formulation for the TEE $\varphi$ adjustments constraints, and $\mathbb{S}_{k,i}:=[\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ for the $i$-th task QoS value constraints.
+where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEE $\varphi$ adjustments constraints set, and $\mathbb{S}_{k,i}:=[\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS value constraints set.
 
-The overall plan is the union of all the missions: a set of TEEs, tasks, and TEEs and QoS parameters. If the system is sampled discrete-time for simplicity
+The overall plan is the union of all the missions. If for simplicity the system is sampled discrete-time
 \begin{equation}
@@
 \end{equation}
-delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$.
+delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (TEEs adjustments), being such function satisfied for all the approaching points.
 
-The algorithm uses the concept to select $\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ with the highest energy value under the constraints, and \emph{evolves the position} using the vector field of $\varPhi:=\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ and deriving the direction to follow.
-It can be expressed as the desired velocity vector
+The algorithm uses the concept to select $\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ with the highest energy value under the constraints.
+It guides the UAV to the new position deriving the direction to follow using the vector field of $\varPhi:=\varphi_k(\mathbf{p},\mathbf{c}_k^0)$.
+Such direction can be expressed as the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient at the point $\mathbf{p}$, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+where $\nabla\varPhi\in\mathbb{R}^2$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference.
 
-The algorithm \emph{evolves the energy} using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader in the next subsection) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader in the next subsection) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 
-Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy estimation of the mission
+Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy modeling of the mission
 \begin{equation}\label{eq:fourier}
-  f(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
+  h(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
 \end{equation}
-where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.
+where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ the Fourier series coefficients.
 
-Suppose no disturbances in form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting otherwise for the unknown state and output.
+Suppose no uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting otherwise for the unknown state and output is present.
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
@@
 where $\mathbf{q}_k\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
-In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remaining.
+In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remainder.
 
@@
 \begin{equation}\label{eq:state-control}\begin{split}  
-  \mathbf{u}_k&=\begin{bmatrix}g(\mathcal{C}_k)-g(\mathcal{C}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T\\
+  \mathbf{u}_k&=\begin{bmatrix}g(\mathcal{C}_k)-g(\mathcal{C}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
   B&=\left[\begin{array}{cccc}
@@
      &             &       & 0
-  \end{array}\right]
+  \end{array}\right],
 \end{split}\end{equation}
-where $\mathcal{C}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{-1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
-Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE parameter to the instantaneous energy.
+where $\mathcal{C}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
+Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE adjustment to the instantaneous energy.
 
@@
 Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
-The energy due to the change of explicit trajectory equation parameters is merely a linear combination of the gain factor and the value of the TEE.
+The energy due to the change of TEEs parameters is merely a linear combination of the gain factor and the value of the TEE adjustment.
 Nevertheless, the change updates the trajectory which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
-The linearity simulates how a variation affects the energy, for instance, a decrement in the radius of a circular TEE will add a negative contribution, the simulate the lowering of instantaneous energy consumption.
+The linearity simulates how a variation affects the energy, for instance, a decrement in the radius of a circular TEE adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
 
-In the case of the system behaving ideally (i.e., with zero uncertainty), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
+In the case of the system behaving ideally (i.e., with no uncertainty), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
 
 \begin{lem}\label{lem:state-vs-energy}
-  Given two time instants $k_1,k_2\in[t_f]$, suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds, then
+  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Given two time instants $k_1,k_2\in[t_f]$
   \begin{equation}

### 2020-10-14 icra-2021.tex
fixing text

@@
 %% math package
-\usepackage[cmex10]{amsmath}
+\usepackage{amsmath}
 \usepackage{mathtools}
@@
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
+
+\let\proof\relax
+\let\endproof\relax
+\usepackage{amsthm}
 
@@
 
+\renewcommand{\qedsymbol}{$\blacksquare$}
+
+\theoremstyle{definition}
 \newtheorem{thm}{Theorem}[section]
@@
 
-The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) values of the onboard computations, and the trajectory-explicit equations (TEEs) adjustments of the motion plan.
-Our goal is a mission extension by optimizing both QoS and TEEs parameters as the UAV flies and its batteries drain.
-The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes.
-It optimizes TEEs--an abstraction of the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
+The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the computations, and the trajectory-explicit equations (TEEs) adjustments.
+In the remainder of the paper, we strictly adopt the following notation.
+We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and to the current trajectory as TEE.
+Our goal is a mission extension by optimizing both computations and adjustments as the UAV flies and its batteries drain.
+First, the algorithm optimizes computations requiring the UAV to include robot operating system (ROS) nodes.
+Then, it optimizes adjustments--a way to alter the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
 It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
@@
 It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator.
-It selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).
+It selects the controls (computations and adjustments) using robust output feedback model predictive control (MPC).
 
@@
 The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis.
-Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
+Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
 
@@
 The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
-The algorithm that uses the model and solves the dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
+The algorithm that uses the model and solves the mobile robot dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
 Section~\ref{sec:experimental} presents the result and showcase the performance.
@@
 
-Let the mission be defined by a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks.
+Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$.
 Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
-At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is formally defined as the ordered list
+
+\begin{defn}[Mission]\label{def:mission}
+  At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
@@
   \end{split}\end{equation}
-where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEE $\varphi$ adjustments constraints set, and $\mathbb{S}_{k,i}:=[\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS value constraints set.
+  where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set.
+\end{defn}
 
@@
 \begin{equation}
-  \mathcal{M}:=\bigcup_{i\in[tf]}{\mathcal{M}_i},
+  \mathcal{M}:=\bigcup_{i\in[t_f]}{\mathcal{M}_i},
 \end{equation}
-the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the control in function of the TEE and QoS parameters--an action performed evolving the mission state.
+the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the controls--an action performed evolving the mission state.
 
@@
 \begin{equation}\label{eq:area}
-  \mathcal{P}_k:=\{\mathbf{p}\mid\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
+  \mathcal{P}_k:=\{\mathbf{p}_k\mid\varphi_k(\mathbf{p}_k,c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
 \end{equation}
-delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (TEEs adjustments), being such function satisfied for all the approaching points.
+delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$, being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$.
 
-The algorithm uses the concept to select $\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ with the highest energy value under the constraints.
-It guides the UAV to the new position deriving the direction to follow using the vector field of $\varPhi:=\varphi_k(\mathbf{p},\mathbf{c}_k^0)$.
-Such direction can be expressed as the desired velocity vector
+The algorithm uses the concept to select the adjustments s.t.
+$\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$ has the highest energy value.
+It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the vector field of $\varPhi:=\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$, deriving the direction to follow--the desired velocity vector
 \begin{equation}\label{eq:pd}
-  \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
+  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
     0&1\\-1&0
@@
 
-The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader in the next subsection) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 
-Suppose no uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting otherwise for the unknown state and output is present.
+Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting for the unknown state and output is not present.
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
@@
 \begin{equation}\label{eq:state-control}\begin{split}  
-  \mathbf{u}_k&=\begin{bmatrix}g(\mathcal{C}_k)-g(\mathcal{C}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
+  \mathbf{u}_k&=\begin{bmatrix}g(\mathbf{s}_k)-g(\mathbf{s}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
   B&=\left[\begin{array}{cccc}
@@
 \end{split}\end{equation}
-where $\mathcal{C}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
-Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE adjustment to the instantaneous energy.
+where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
+Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy.
 
 The energy evolution analysis necessitates the following realistic assumption.
-\begin{assm}\label{assm:periodic} 
+\begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
 Given two time instants $k_1,k_2\in[t_f]$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{R}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
@@
 \end{assm}
+
 Physically, the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns.
@@
 Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
-The energy due to the change of TEEs parameters is merely a linear combination of the gain factor and the value of the TEE adjustment.
-Nevertheless, the change updates the trajectory which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
-The linearity simulates how a variation affects the energy, for instance, a decrement in the radius of a circular TEE adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
+The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment.
+Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
+The linearity simulates how a variation affects the energy, for instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
 
@@
 Specifically, the tool builds a linear interpolation, one per each task.
-It hence requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters (QoS).
+It requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters.
+A way to simulate the change of the computations.
 
-Suppose the system is composed of $\sigma$ ROS nodes. Let us define a computational control action
+The mission $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}).
+These tasks are in fact simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$.
+Let us define the computations
 \begin{equation}\label{eq:qos-def}
-  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_{k,n}\,\,\,\forall n\in\{0,\dots,\sigma-1\},\,\forall k\in\mathbb{T}\right\},
+  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid s_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\right\},
 \end{equation}
-where $\text{QoS}_{k,n}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values.
+where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, and $\mathbf{s}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$.
+
 Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
@@
 \begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathcal{C}_{k}\right).\\
+  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
 \end{split}\end{equation}
 
-The QoS parameters $\mathcal{C}_k$ can be subject to different constraints at different states.
-Physically, this means that the UAV can perform the ROS nodes within different QoS ranges in time while flying
-\begin{equation}\label{eq:qos-lims}\begin{split}
-  \underline{\text{QoS}}_{k,n}\leq \,&\text{QoS}_{k,n}\leq \overline{\text{QoS}}_{k,n},\\
-  &\forall n\in\{0,\cdots,\sigma-1\},\,\forall k\in\mathbb{T},
-\end{split}\end{equation}
-where the values $\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}$ are retrieved from the mission $\mathcal{M}$.
+\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
 
@@
 This is achieved by solving online a finite horizon optimal control problem by the hand of a modification of a model predictive control (MPC) algorithm~\cite{rawlings2017model}.
+
+Given mission starting point $\mathcal{M}_0$, the algorithm selects the $\mathbf{s}_k$ and $\mathbf{c}_k$ (computations and adjustments) and produce a valid state evolution
+\begin{equation}\begin{split}
+  \mathbf{u}:=\{(\mathbf{p}_k,\mathbf{c}_k,\mathbf{s}_k)\mid&(\varphi(\mathbf{p}_k,\mathbf{c}_k),\Psi(\mathbf{s_k}))\in\mathcal{M}_k\Longrightarrow\\
+  &(\varphi(\mathbf{p}_{k+1},\mathbf{c}_{k+1}),\Psi(\mathbf{s}_{k+1}))\in\mathcal{M}_{k+1}\\
+  {}&\forall k\in[t_f-1]\}.
+\end{split}\end{equation}
 

### 2020-10-14 icra-2021.tex
fixing text (2)

@@
 \end{equation}
-the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the controls--an action performed evolving the mission state.
+the algorithm inputs $\mathcal{M}$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
 
@@
 \end{split}\end{equation}
-where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
+where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
 Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy.
@@
 
-In the case of the system behaving ideally (i.e., with no uncertainty), we expect a set of states evolving accordingly to their outputs. Such observation is summarized in the following Lemma.
+In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy evolution) evolving accordingly to its output (instantaneous energy consumption).
+Such observation is summarized in the following Lemma.
 
-\begin{lem}\label{lem:state-vs-energy}
+\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
   Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Given two time instants $k_1,k_2\in[t_f]$
@@
 
-The mission $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}).
-These tasks are in fact simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$.
+The plan $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}).
+These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations.
 Let us define the computations
 \begin{equation}\label{eq:qos-def}
-  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid s_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\right\},
+  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]\right\},
 \end{equation}
-where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, and $\mathbf{s}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$.
+where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ being $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.
 
@@
 
-\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
-
+%%%%%%%%%%%%%%%%%%%
 \section{Algorithm}
@@
 
-Given mission starting point $\mathcal{M}_0$, the algorithm selects the $\mathbf{s}_k$ and $\mathbf{c}_k$ (computations and adjustments) and produce a valid state evolution
+Given an initial mission $\mathcal{M}_1$ (TEE $\varphi_1$, tasks $\Psi$, computations $\mathbf{s}_1\in\mathbb{S}_1$, and adaptations $\mathbf{c}_1\in\mathbb{C}_1$), the algorithm produce a valid mission evolution.
+
+\begin{defn}[Valid mission evolution]\label{def:valid}
+  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid
   \begin{equation}\begin{split}
-  \mathbf{u}:=\{(\mathbf{p}_k,\mathbf{c}_k,\mathbf{s}_k)\mid&(\varphi(\mathbf{p}_k,\mathbf{c}_k),\Psi(\mathbf{s_k}))\in\mathcal{M}_k\Longrightarrow\\
-  &(\varphi(\mathbf{p}_{k+1},\mathbf{c}_{k+1}),\Psi(\mathbf{s}_{k+1}))\in\mathcal{M}_{k+1}\\
-  {}&\forall k\in[t_f-1]\}.
+    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
+    &\Longrightarrow(\varphi(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{k}\}.
   \end{split}\end{equation}
+\end{defn}
 
-Let us proof formally an important finding from Section~\ref{sec:model} extensively used in the algorithm.
+Note that the position evolution can be computed directly from Equation~(\ref{eq:pd}).
+If the velocity is $v\in\mathbb{R}_{\geq 0}$, and starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
 
-% [Ad:] I am actually not entirely sure if the thm should be here (and if it makes sense).
-Aka proving formally that what we do is actually what we expect; so perhaps it does make sense but I would like your opinion before spending time on the demonstrations...
-Same for the lemma.
-% [Ad:] And here I had the doubt if to place the thm just straight after the lemma or here.
-I places it here as this is actually the main contribution -> the energy model working.
-Does it make any sense?
+Let us proof that if the mission evolution is valid, the instantaneous energy consumption is a linear combination of the state from the Equation~(\ref{eq:state-perf}).
 
-\begin{thm}\label{thm:state-vs-energy}
-  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\sigma}\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{T}$.
-  Assume Assumption~\ref{assm:periodic} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eq:area}), and is following $\varphi$ with the direction $\dot{\mathbf{p}}_d$ defined in~\ref{eq:pd}.
+\begin{thm}[State output linearity]\label{thm:state-vs-energy}
+  Consider the mission from Definition~\ref{def:mission}, the valid mission evolution from~\ref{def:valid}, and assume Assumption~\ref{assm:periodic} holds.
 Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.
-  Then, the instantaneous energy consumption is a linear combination of the state
-  \begin{equation}
-    y_k=C\mathbf{q}_k=\sum_{n=0}^r{\alpha_n},
-  \end{equation}
-  where $\alpha_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a preassigned arbitrary order from~(\ref{eq:fourier}), and $C$ is described in Equation~(\ref{eq:state-details}).
+  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathcal{M}_k$ produce a valid mission evolution $\mathcal{M}_{k+1}\,\forall k\in[t_f-1]$.
 \end{thm}
@@
 
-\subsection{State estimation}
-\label{sec:state-est}
+%\subsection{State estimation}
+%\label{sec:state-est}
 
-As the environment uncertainty and measurement error evolve in a normal distribution, we use a Kalman filter~\cite{stengel1994optimal, simon2006optimal} for the purpose of state estimation.
+%As the environment uncertainty and measurement error evolve in a normal distribution, we use a Kalman filter~\cite{stengel1994optimal, simon2006optimal} for the purpose of state estimation.
 
-The prediction is done using
-\begin{subequations}\label{eq:kalman-pred}\begin{align}
-  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:kalman-pred1}\\
-  P_{k+1}^-&=AP_kA^T+Q,\label{eq:kalman-pred2}
-\end{align}\end{subequations}
-where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
+%The prediction is done using
+%\begin{subequations}\label{eq:kalman-pred}\begin{align}
+%  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:kalman-pred1}\\
+%  P_{k+1}^-&=AP_kA^T+Q,\label{eq:kalman-pred2}
+%\end{align}\end{subequations}
+%where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
 
-The estimation of the state and the update of the predicted output is done using
-\begin{subequations}\label{eq:kalman-est}\begin{align}
-  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:kalman-est2}\\
-  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
-  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:kalman-est4}
-\end{align}
-\end{subequations}
-where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
+%The estimation of the state and the update of the predicted output is done using
+%\begin{subequations}\label{eq:kalman-est}\begin{align}
+%  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
+%  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:kalman-est2}\\
+%  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
+%  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:kalman-est4}
+%\end{align}
+%\end{subequations}
+%where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
 $y_k^s,y_k^c$ are the instantaneous energy readings: $y_k^s\in\mathbb{R}_{\geq 0}$ the robot sensor, i.e., the energy due to the trajectory, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eq:energy-comp}).
@@
 
-Equations~(\ref{eq:kalman-pred}--\ref{eq:kalman-est}) converge to the predicted energy evolution as follows.
+%Equations~(\ref{eq:kalman-pred}--\ref{eq:kalman-est}) converge to the predicted energy evolution as follows.
 An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
@@
 
-At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:kalman-pred1})~and~(\ref{eq:kalman-pred2}) respectively.
+%At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:kalman-pred1})~and~(\ref{eq:kalman-pred2}) respectively.
 The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eq:kalman-est2}) to estimate the current state along with the data from the sensor $y_0$ (e.g., the energy sensor of the flight controller of the fixed-wing craft), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
@@
 
-\subsection{Optimal control action}
+%\subsection{Optimal control action}
 
-*
+%*
 

### 2020-10-14 icra-2021.tex
fixes, done for today zzzzzz

@@
 It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator.
-It selects the controls (computations and adjustments) using robust output feedback model predictive control (MPC).
+It output the controls sequence (computations and adjustments) using robust output feedback model predictive control (MPC).
 
@@
 The algorithm that uses the model and solves the mobile robot dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
-Section~\ref{sec:experimental} presents the result and showcase the performance.
+Section~\ref{sec:experimental} presents the result and showcase the performances.
 The paper finishes with some conclusions in Section~\ref{sec:conclusion}.
@@
 \begin{defn}[Mission]\label{def:mission}
-  At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is defined as the ordered list
+  At a time instant $k\in[1,t_f)\subseteq\mathbb{R}_{\geq 1}$, the mission is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
@@
 \end{equation}
-the algorithm inputs $\mathcal{M}$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
+the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
 
@@
 The mission state is the UAV's position in space and the energy evolution in time.
-Despite we show a linear relation between the instantaneous energy and the energy evolution, the two are different.
+Despite we show a linear relation between the instantaneous energy and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different.
 We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
@@
 \end{equation}
-delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$, being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$.
+delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$).
 
@@
 
-Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting for the unknown state and output is not present.
+Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting for the unknown state and output is absent.
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
@@
 \end{cases},\end{equation}
-where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption.
-We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state.
-The state $\mathbf{q}$ mimics the original Fourier series coefficients
+where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ mimics the original Fourier series coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
@@
 \begin{proof}
-  \begin{center}\vspace{.2cm}``\emph{The easy proof is trivial and is left as an exercise to the reader :P}''\vspace{.6cm}\end{center}
+  *
 \end{proof}
@@
 \end{equation}
-where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ being $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.
+where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.
 
@@
 
-Note that the position evolution can be computed directly from Equation~(\ref{eq:pd}).
-If the velocity is $v\in\mathbb{R}_{\geq 0}$, and starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
+Note that the controls sequence $\mathbf{u}_k^a$ differs from the control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
+Moreover, the position evolution can be computed directly from Equation~(\ref{eq:pd}).
+If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
 

### 2020-10-15 icra-2021.tex
some minor things in the text here and there

@@
 Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$.
-Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
+Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
 
@@
 
+Note that the controls sequence $\mathbf{u}_k^a:=(\mathbf{c}_{k},\mathbf{s}_{k})$--an output of the algorithm--differs from the nominal control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
+
 The energy evolution analysis necessitates the following realistic assumption.
@@
 The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment.
-Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution accordingly.
-The linearity simulates how a variation affects the energy, for instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
+Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution.
+For instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
 
 In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy evolution) evolving accordingly to its output (instantaneous energy consumption).
-Such observation is summarized in the following Lemma.
+An observation summarized in the following Lemma.
 
@@
 The plan $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}).
-These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations.
-Let us define the computations
+These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations
 \begin{equation}\label{eq:qos-def}
@@
 \begin{defn}[Valid mission evolution]\label{def:valid}
-  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid
+  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid if its control sequence is valid
   \begin{equation}\begin{split}
@@
 
-Note that the controls sequence $\mathbf{u}_k^a$ differs from the control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
-Moreover, the position evolution can be computed directly from Equation~(\ref{eq:pd}).
+Note the position evolution can be computed directly from Equation~(\ref{eq:pd}).
 If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.

### 2020-10-15 icra-2021.tex
the sketch of the algorithm

@@
 %\usepackage{algorithmic}
+\usepackage{algpseudocode}
 
@@
 \newtheorem{rem}{Remark}
+
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
 
@@
 \begin{equation}\label{eq:fourier}
-  h(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
+  h(t)=\sum_{n=0}^{r}{a_n\cos\left({nt/\xi}\right)+b_n\sin{\left({nt/\xi}\right)}},
 \end{equation}
@@
 \begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
+  y_k^s:=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
 \end{split}\end{equation}
@@
 
+\subsection{Output constraints set}
+
+Recall the model in Equation~(\ref{eq:state-perf}).
+We stated the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
+This is generally untrue.
+Physical UAVs are bounded by strict battery limitations.
+
+Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
+\begin{equation}\begin{split}
+  \mathrm{SoC}_k=-\left(V-
+  \sqrt{
+    V^2-
+    4R\tilde{V}y_kV^{-1}}
+  \right)/2RQ_c,\\ 
+\end{split}\end{equation}
+where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
+We define the output constraints set
+\begin{equation}
+  \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+\end{equation}
+where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy.
 \subsection{Deployment algorithm}
+
+\begin{center}\textit{Ok, so I need to fix this algorithm properly. But the sketch is there (the position is missing but I'll make a wrapper tomorrow morning)!}\end{center}
+
+\begin{algorithmic}[1]
+  \Procedure{}{$\mathcal{M}_1$, $\mathbf{p}_1$, $\mathbf{q}_1$, $K$, $v$, $\varepsilon$}
+  \State $k\gets 2$
+  \State $\mathbf{z}_{k-1},\hat{\mathbf{q}}_{k-1}\gets \mathbf{q}_1$
+  \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$
+  \While{$k \leq t_f$}
+    \Do
+      \State $\mathbf{v}\gets\argmax_{\mathbf{v}}{\sum_{i=k-1}^{k+N-2}}{l(\mathbf{z}_i,\mathbf{v}_i)+V_f(\mathbf{z}_{N+1})}$
+      \State $\mathbf{u}_{k-1}\gets \mathbf{v}+K(\hat{\mathbf{q}}_{k-1}-\mathbf{z}_{k-1})$
+      \State $\hat{\mathbf{q}}_k^-\gets A\hat{\mathbf{q}}_{k-1} + B\mathbf{u}_{k-1}$
+      \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}
+        \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\overline{\mathbf{u}}^a_{k-1}$
+        \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$
+
+      \EndIf
+    \doWhile{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}
+
+    \If{$\abs{y_k^m-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
+      \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$
+    \Else 
+      \State $P_k^-\gets AP_{k-1}A^T+Q$
+      \State $L\gets P_k^-C^T/(CP_k^-C^T+R)$
+      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+L(y_k^m-C\hat{\mathbf{q}}_k^-)$
+      $\mathbf{z}_{k-1}$
+      \State $P_k\gets(I+LC)P_k^-$
+    \EndIf
+    \State $\mathbf{z}_k\gets A\mathbf{z}_{k-1}+B\mathbf{u}_{k-1}$
+    \State $\mathbf{y}\gets\mathbf{y}\cup C\hat{\mathbf{q}}_k$
+    \State $k\gets k + 1$
+  \EndWhile % <---
+  %\State $r\gets a\bmod b$
+  %\State $\mathcal{M}_1\gets a\bmod b$
+  %\While{$r\not=0$}\Comment{We have the answer if r is 0}
+  %State $a\gets b$
+  %\State $b\gets r$
+  %\State $r\gets a\bmod b$
+  %\EndWhile\label{euclidendwhile}
+  %\State \textbf{return} $b$\Comment{The gcd is b}
+  \EndProcedure
+\end{algorithmic}
 

### 2020-10-19 icra-2021.tex
added overview figure and addressed some of the Hector's comments

@@
 
-In the spirit of reducing waste, costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+In the spirit of reducing costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
 Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
-The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a monitoring mission optimized for the craft's dynamics.
-The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis.
+The mission consists of a UAV flying in circles and lines covering a polygon, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
+The algorithm plans the mission controlling the processing rate, the radius of the circles, and the distance between the lines.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
@@
 
-Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$.
-Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.
+Let a mission's stage be a generic continuous twice differentiable TEE $\varphi$ and a set of tasks $\psi_1,\dots,\psi_{\sigma}$.
+Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{0,1,\dots,\,\cdot\,\}$, $[\,\cdot\,]^+$ the set $\{0\}/[\,\cdot\,]$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the lower and upper bound of $\,\cdot\,$.
+If $\,\cdot\,$ is a value, the bounds are user defined and retrieved from a lookup table; if a set, they correspond to minimum and maximum of the set.
 
-\begin{defn}[Mission]\label{def:mission}
-  At a time instant $k\in[1,t_f)\subseteq\mathbb{R}_{\geq 1}$, the mission is defined as the ordered list
+\begin{defn}[Stage and mission]\label{def:mission}
+  At a time instant $k\in[0,t_f)$, the \emph{stage} is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_k:=\{(\varphi,\psi_1,...,\psi_\sigma)\mid\exists&\,\,\varphi\in\mathbb{C}_k,\,\\&\psi_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
+    \mathcal{M}_k:=\{(\varphi_k&(\,\cdot\,),\psi_1(\,\cdot\,),...,\psi_\sigma(\,\cdot\,))\mid\\\exists\,\,&\varphi_k(\,\cdot\,)\in\mathbb{C}_k,\,\\&\,\psi_i(\,\cdot\,)\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
   \end{split}\end{equation}
   where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set.
+The parameters of the TEE $\varphi_k$ are defined in Subsection~\ref{sec:model}, of the tasks $\psi_1,\dots,\psi_\sigma$ in~\ref{sec:computations-model}.
+
+  The \emph{mission} is the union of all the stages, along with a function $\lambda:\mathbb{R}^2\rightarrow\mathcal{M}_k$ which maps a point $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
+some inertial navigation frame $\mathcal{O}_W$ to a specific stage.
+If for simplicity the system is sampled discrete-time
+  \begin{equation}
+    \mathcal{M}:=(\lambda(\mathbf{p}),\bigcup_{i\in[t_f]}{\mathcal{M}_i}),
+  \end{equation}
+  the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
 \end{defn}
 
-The overall plan is the union of all the missions. If for simplicity the system is sampled discrete-time
-\begin{equation}
-  \mathcal{M}:=\bigcup_{i\in[t_f]}{\mathcal{M}_i},
-\end{equation}
-the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
+\begin{figure}[t]
+  \centering
+  \input{\figpath/icra-2021_overview.tikz}
+  \caption{Overview}
+  \label{fig:overview}
+\end{figure}
 
-\subsection{Mission state}
+\subsection{State: position and energy}
 \label{sec:model}
 
-The mission state is the UAV's position in space and the energy evolution in time.
-Despite we show a linear relation between the instantaneous energy and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different.
+The state is the UAV's position in space and the energy evolution in time.
+Despite we show a linear relation between the instantaneous energy consumption and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different.
 We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
-Consider the position $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$, the set
+Consider the position $\mathbf{p}$, the set
 \begin{equation}\label{eq:area}
@@
 where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
-Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy.
+Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
 
@@
 
-Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}.
-The instantaneous computational energy component can be defined
+Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained interrogating \powprof{}
 \begin{equation}\label{eq:energy-comp}\begin{split}
@@
 \end{equation}
-where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy.
+where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
 \subsection{Deployment algorithm}

### 2020-10-20 icra-2021.tex
updating the algorithm section and some consistency fixes

@@
 where $\nabla\varPhi\in\mathbb{R}^2$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind $w\in\mathbb{R}$.
 
@@
 
-Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy modeling of the mission
+Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy consumption modeling of the mission
 \begin{equation}\label{eq:fourier}
@@
 
-The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds an energy model.
+The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds a computational energy consumption model.
 Specifically, the tool builds a linear interpolation, one per each task.
@@
 
-%The main goal of the algorithm is to find an optimal control action $\mathbf{u}^0$ for the current state $\hat{\mathbf{q}}$--estimated from sensors' measurements--from the optimal control law $\mathbf{u}^0=:\kappa(\hat{\mathbf{q}})$.
-This is achieved by solving online a finite horizon optimal control problem by the hand of a modification of a model predictive control (MPC) algorithm~\cite{rawlings2017model}.
+Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the algorithm produce a valid mission.
 
-Given an initial mission $\mathcal{M}_1$ (TEE $\varphi_1$, tasks $\Psi$, computations $\mathbf{s}_1\in\mathbb{S}_1$, and adaptations $\mathbf{c}_1\in\mathbb{C}_1$), the algorithm produce a valid mission evolution.
-
-\begin{defn}[Valid mission evolution]\label{def:valid}
-  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid if its control sequence is valid
+\begin{defn}[Valid mission]\label{def:valid}
+  A mission is valid if for every stage $\mathcal{M}_{k-1}$ in $k\in[t_f]^+$ there exist a control sequence $\mathbf{u}_k^{a}$ which produce the stage $\mathcal{M}_k$
   \begin{equation}\begin{split}
@@
 
-Note the position evolution can be computed directly from Equation~(\ref{eq:pd}).
-If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
-
-Let us proof that if the mission evolution is valid, the instantaneous energy consumption is a linear combination of the state from the Equation~(\ref{eq:state-perf}).
+Let us proof that if the mission is valid, the instantaneous energy consumption is a linear combination of the state from the Equation~(\ref{eq:state-perf}).
 
 \begin{thm}[State output linearity]\label{thm:state-vs-energy}
-  Consider the mission from Definition~\ref{def:mission}, the valid mission evolution from~\ref{def:valid}, and assume Assumption~\ref{assm:periodic} holds.
+  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, and assume Assumption~\ref{assm:periodic} holds.
 Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.
-  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathcal{M}_k$ produce a valid mission evolution $\mathcal{M}_{k+1}\,\forall k\in[t_f-1]$.
+  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathcal{M}_k$ produce a valid mission $\mathcal{M}_{k+1}\,\forall k\in[t_f-1]$.
 \end{thm}
@@
 
-\begin{center}\textit{Ok, so I need to fix this algorithm properly. But the sketch is there (the position is missing but I'll make a wrapper tomorrow morning)!}\end{center}
+\begin{algorithmic}[1]
+  \Procedure{Step}{$\mathcal{M}_{k-1}$, $\mathbf{q}_{k-1}$, $\mathbf{u}_{k-1}^a$, $\mathbf{u}_{k-2}^a$, $P_{k-1}$}\label{alg:step}
 
-\begin{algorithmic}[1]
-  \Procedure{}{$\mathcal{M}_1$, $\mathbf{p}_1$, $\mathbf{q}_1$, $K$, $v$, $\varepsilon$}
-  \State $k\gets 2$
-  \State $\mathbf{z}_{k-1},\hat{\mathbf{q}}_{k-1}\gets \mathbf{q}_1$
-  \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$
-  \While{$k \leq t_f$}
-    \Do
-      \State $\mathbf{v}\gets\argmax_{\mathbf{v}}{\sum_{i=k-1}^{k+N-2}}{l(\mathbf{z}_i,\mathbf{v}_i)+V_f(\mathbf{z}_{N+1})}$
-      \State $\mathbf{u}_{k-1}\gets \mathbf{v}+K(\hat{\mathbf{q}}_{k-1}-\mathbf{z}_{k-1})$
-      \State $\hat{\mathbf{q}}_k^-\gets A\hat{\mathbf{q}}_{k-1} + B\mathbf{u}_{k-1}$
-      \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}
-        \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\overline{\mathbf{u}}^a_{k-1}$
-        \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$
+  \State $\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$\label{alg:max_cont_sequence}
 
+  \State $\mathbf{u}^0_{k-1}\gets\argmax_{\mathbf{u}}{\sum_{i=k-1}^{k+N-2}{l(\mathbf{q}_i,\mathbf{u}_i)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
+
+  \State $\hat{\mathbf{q}}_k^-\gets A\hat{\mathbf{q}}_{k-1} + B\mathbf{u}^0_{k-1}$
+  \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}\label{alg:output_constraints}
+    \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\{\overline{\mathbf{u}}^a_{k-1}\}$
+    \State\Return{\Call{Step}{$\mathcal{M}_{k-1}$, $\mathbf{q}_{k-1}$, $\mathbf{u}^a_{k-1}$, $\mathbf{u}_{k-2}^a$,$P_{k-1}$}}
+  \Else
+    \If{$\abs{y_k^m-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
+      \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$\label{alg:evolution}
+    \Else 
+      \State $P_k^-\gets AP_{k-1}A^T+Q$\label{alg:kalman_start}
+      \State $K\gets P_k^-C^T/(CP_k^-C^T+R)$
+      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+K(y_k^m-C\hat{\mathbf{q}}_k^-)$
+      \State $P_k\gets(I+KC)P_k^-$\label{alg:kalman_end}
     \EndIf
-    \doWhile{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}
-
-    \If{$\abs{y_k^m-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
-      \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$
-    \Else 
-      \State $P_k^-\gets AP_{k-1}A^T+Q$
-      \State $L\gets P_k^-C^T/(CP_k^-C^T+R)$
-      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+L(y_k^m-C\hat{\mathbf{q}}_k^-)$
-      $\mathbf{z}_{k-1}$
-      \State $P_k\gets(I+LC)P_k^-$
+    \State $\mathbf{u}_{k}^a\gets \mathbf{u}_{k-1}^a$
+    \State\Return{$(\hat{\mathbf{q}}_k,\mathbf{u}_k^a)$}
   \EndIf
-    \State $\mathbf{z}_k\gets A\mathbf{z}_{k-1}+B\mathbf{u}_{k-1}$
-    \State $\mathbf{y}\gets\mathbf{y}\cup C\hat{\mathbf{q}}_k$
-    \State $k\gets k + 1$
-  \EndWhile % <---
   %\State $r\gets a\bmod b$
@@
   \EndProcedure
+  \Procedure{EADMPA}{$\mathcal{M}_0$, $\mathbf{p}_0$, $\mathbf{q}_0$}
+  \State $k\gets 0$
+%  \State $\mathbf{y}\gets \{\emptyset\}$
+  \State $\mathbf{u}_{k-1}^a\gets\{\emptyset\}$
+  \State $\mathbf{u}_{k}^a\gets \{(\mathbf{c}_0,\mathbf{s}_0)\mid(\varphi_0(\mathbf{p}_{0},\mathbf{c}_{0}),\Psi(\mathbf{s_{0}}))\in\mathcal{M}_{0}\}$
+  \State $\mathcal{M}_k\gets\mathcal{M}_0$
+  \State $\mathbf{p}_k\gets\mathbf{p}_0$
+  \State $\mathbf{q}_k\gets\mathbf{q}_0$
+  \While{$k \leq t_f$}
+
+    \State $(\mathbf{q}_k,\mathbf{u}_k^a)\gets$\Call{Step}{$\mathbf{q}_{k}$, $\mathbf{u}^a_{k}$, $\mathbf{u}_{k-1}^a$}
+    \State $\mathbf{p}_{k}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$
+    \State $\mathbf{u}_{k-1}^a\gets\mathbf{u}_{k}^a$
+
+%    \State $\mathbf{y}\gets\mathbf{y}\cup C\hat{\mathbf{q}}_k$
+    \State $k\gets k + 1$
+  \EndWhile 
+  \EndProcedure
 \end{algorithmic}
 
-*
+%The algorithm per each time step updates the state. The position at line
+
+Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the control sequence at the time step $k-1$.
+Line~\ref{alg:mpc} uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the optimal control $\mathbf{u}^0$ for a given horizon $N$ from the cost function
+\begin{equation}\begin{split}
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^TQ\mathbf{q}_k+\mathbf{u}_k^TR\mathbf{u}_k),\\
+  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TP_f\mathbf{q}_k)
+\end{split}\end{equation}
+where matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are all positive definite.
+
+Follows a check if the mission can finish without the eventuality of the battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}.
+The control sequence is then eventually updated.
+
+Before the algorithm returns the energy evolution and the control sequence, a state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} (lines~\ref{alg:kalman_start}--\ref{alg:kalman_end})--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverging from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
+
+Note the position evolution can be computed directly from Equation~(\ref{eq:pd}).
+If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
 

### 2020-10-20 icra-2021.tex
updating the algorithm (2)

@@
 \begin{algorithmic}[1]
-  \Procedure{Step}{$\mathcal{M}_{k-1}$, $\mathbf{q}_{k-1}$, $\mathbf{u}_{k-1}^a$, $\mathbf{u}_{k-2}^a$, $P_{k-1}$}\label{alg:step}
+  \Procedure{Step}{$\mathbf{q}_{k-1}$, $\mathbf{u}_{k-1}^a$, $\mathbf{u}_{k-2}^a$, $P_{k-1}$}\label{alg:step}
 
@@
     \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\{\overline{\mathbf{u}}^a_{k-1}\}$
-    \State\Return{\Call{Step}{$\mathcal{M}_{k-1}$, $\mathbf{q}_{k-1}$, $\mathbf{u}^a_{k-1}$, $\mathbf{u}_{k-2}^a$,$P_{k-1}$}}
+    \State\Return{\Call{Step}{$\mathbf{q}_{k-1}$, $\mathbf{u}^a_{k-1}$, $\mathbf{u}_{k-2}^a$,$P_{k-1}$}}\label{alg:recursion}
   \Else
@@
       \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$\label{alg:evolution}
+      \State $P_k\gets P_k^-$
     \Else 
@@
     \State $\mathbf{u}_{k}^a\gets \mathbf{u}_{k-1}^a$
-    \State\Return{$(\hat{\mathbf{q}}_k,\mathbf{u}_k^a)$}
+    \State\Return{$(\hat{\mathbf{q}}_k,P_k,\mathbf{u}_k^a)$}
   \EndIf
-  %\State $r\gets a\bmod b$
-  %\State $\mathcal{M}_1\gets a\bmod b$
-  %\While{$r\not=0$}\Comment{We have the answer if r is 0}
-  %State $a\gets b$
-  %\State $b\gets r$
-  %\State $r\gets a\bmod b$
-  %\EndWhile\label{euclidendwhile}
-  %\State \textbf{return} $b$\Comment{The gcd is b}
   \EndProcedure
-  \Procedure{EADMPA}{$\mathcal{M}_0$, $\mathbf{p}_0$, $\mathbf{q}_0$}
+\vspace*{1ex}
+  \Procedure{EADMPA}{$\mathcal{M}$, $\mathbf{p}_0$, $\mathbf{q}_0$}
   \State $k\gets 0$
@@
   \State $\mathbf{u}_{k-1}^a\gets\{\emptyset\}$
-  \State $\mathbf{u}_{k}^a\gets \{(\mathbf{c}_0,\mathbf{s}_0)\mid(\varphi_0(\mathbf{p}_{0},\mathbf{c}_{0}),\Psi(\mathbf{s_{0}}))\in\mathcal{M}_{0}\}$
-  \State $\mathcal{M}_k\gets\mathcal{M}_0$
   \State $\mathbf{p}_k\gets\mathbf{p}_0$
@@
 
-    \State $(\mathbf{q}_k,\mathbf{u}_k^a)\gets$\Call{Step}{$\mathbf{q}_{k}$, $\mathbf{u}^a_{k}$, $\mathbf{u}_{k-1}^a$}
-    \State $\mathbf{p}_{k}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$
+    \State $\mathbf{u}_{k}^a\gets \{\mathbf{u}_{k}^a\mid(\varphi_k(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s_{k}}))\in\mathcal{M}_{k}\subseteq\mathcal{M}\}$
+    \State $(\mathbf{q}_k,P_k,\mathbf{u}_k^a)\gets$\Call{Step}{$\mathbf{q}_{k}$, $\mathbf{u}^a_{k}$, $\mathbf{u}_{k-1}^a$, $P_k$}\label{alg:en}
+    \State $\mathbf{p}_{k}\gets\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$\label{alg:pos}
     \State $\mathbf{u}_{k-1}^a\gets\mathbf{u}_{k}^a$
@@
 
-%The algorithm per each time step updates the state. The position at line
+The algorithm per each time step updates the state.
+The position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}.
+Note the position can be computed directly from Equation~(\ref{eq:pd}).
+If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
 
-Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the control sequence at the time step $k-1$.
-Line~\ref{alg:mpc} uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the optimal control $\mathbf{u}^0$ for a given horizon $N$ from the cost function
+In detail, initial guesses for $\mathbf{q}_0$ and $P_0\in\mathbb{R}^{j\times j}$ are derived empirically.
+Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the current control sequence.
+Line~\ref{alg:mpc} uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the optimal control $\mathbf{u}^0$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function
 \begin{equation}\begin{split}
   l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^TQ\mathbf{q}_k+\mathbf{u}_k^TR\mathbf{u}_k),\\
-  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TP_f\mathbf{q}_k)
+  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TP_f\mathbf{q}_k),
 \end{split}\end{equation}
@@
 
-Follows a check if the mission can finish without the eventuality of the battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}.
-The control sequence is then eventually updated.
+Follows a check if the mission can finish without the eventuality of the battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control sequence being eventually updated and the process reiterated at line~\ref{alg:recursion}.
 
-Before the algorithm returns the energy evolution and the control sequence, a state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} (lines~\ref{alg:kalman_start}--\ref{alg:kalman_end})--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverging from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
-
-Note the position evolution can be computed directly from Equation~(\ref{eq:pd}).
-If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
+Before the next step a state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
 

### 2020-10-20 icra-2021.tex
ok state but proofreading needed (need to buy groceries now though)

@@
 The mission consists of a UAV flying in circles and lines covering a polygon, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
-The algorithm plans the mission controlling the processing rate, the radius of the circles, and the distance between the lines.
+The algorithm plans the mission controlling the processing rate, and the radius of the circles which affects the distance between the lines.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
+Figure~\ref{fig:overview} shows an initial slice of such a mission.
+The UAV first converges to the circular TEE $\varphi_0$, and later shifts to TEE $\varphi_0^+$, as e.g., windy weather required the adjustment of the control sequence to avoid battery depletion.
 
@@
   \input{\figpath/icra-2021_overview.tikz}
-  \caption{Overview}
+  \caption{The mission consists of circles and lines that forms a survey pattern.
+The UAV heads to $\varphi_0$ initially using the desired velocity vector $\dot{\mathbf{p}}_d$, but it later heads to $\varphi_0^+$ reducing the radius $c_{0,0}$ to satisfy the battery constraints (indeed the energy coefficients $\mathbf{q}_0$ evolution is higher then $\mathbf{q}_0^+$).
+The UAV then converges to $\varphi_1$, to $\varphi_3$, and so on until it covers the polygon (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
   \label{fig:overview}
@@
 
-The state is the UAV's position in space and the energy evolution in time.
-Despite we show a linear relation between the instantaneous energy consumption and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different.
+The state is the UAV's position in space and the energy coefficients in time.
+Despite we show a linear relation between the instantaneous energy consumption and the energy coefficients (Theorem~\ref{thm:state-vs-energy}), the two are different.
 We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
-Consider the position $\mathbf{p}$, the set
+The set
 \begin{equation}\label{eq:area}
@@
 \end{equation}
-delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$).
+delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (gray area in Figure~\ref{fig:overview}), being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$.
 
@@
 \end{split}\end{equation}
-where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$.
+where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$.
 Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
@@
 The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment.
-Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution.
+Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy coefficients.
 For instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
 
-In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy evolution) evolving accordingly to its output (instantaneous energy consumption).
+In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption).
 An observation summarized in the following Lemma.
@@
 \end{split}\end{equation}
+Moreover, $g(\{\emptyset\})=0$.
 
@@
 \end{proof}
-
-%\subsection{State estimation}
-%\label{sec:state-est}
-
-%As the environment uncertainty and measurement error evolve in a normal distribution, we use a Kalman filter~\cite{stengel1994optimal, simon2006optimal} for the purpose of state estimation.
-
-%The prediction is done using
-%\begin{subequations}\label{eq:kalman-pred}\begin{align}
-%  \hat{\mathbf{q}}_{k+1}^-&=A\hat{\mathbf{q}}_{k}+B\mathbf{u}_k,\label{eq:kalman-pred1}\\
-%  P_{k+1}^-&=AP_kA^T+Q,\label{eq:kalman-pred2}
-%\end{align}\end{subequations}
-%where $\hat{\mathbf{q}}_k^-,\hat{\mathbf{q}}_k\in\mathbb{R}^j$ depicts the estimate of the state before and after measurement (or simply estimate), and $P_k,P_k^-\in\mathbb{R}^{j\times j}$ the error covariance matrix (i.e., the variance of the estimate).
-
-%The estimation of the state and the update of the predicted output is done using
-%\begin{subequations}\label{eq:kalman-est}\begin{align}
-%  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
-%  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eq:kalman-est2}\\
-%  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
-%  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eq:kalman-est4}
-%\end{align}
-%\end{subequations}
-%where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix.
-$y_k^s,y_k^c$ are the instantaneous energy readings: $y_k^s\in\mathbb{R}_{\geq 0}$ the robot sensor, i.e., the energy due to the trajectory, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eq:energy-comp}).
-The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the uncertainty and measurement error covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.
-
-%Equations~(\ref{eq:kalman-pred}--\ref{eq:kalman-est}) converge to the predicted energy evolution as follows.
-An initial guess of the values $\hat{\mathbf{q}}_0,P_0$ is derived empirically from collected data.
-It is worth considering that an appropriate guess of these parameters allows the algorithm to converge to the desired energy evolution in a shorter amount of time.
-The tuning parameters $Q,R$ are also derived from the collected data, and may differ due to i.e., different sensors used to measure the instantaneous energy consumption, or different atmospheric conditions accounting for the process noise.
-
-%At time $k=0$, the initial estimate before measurement of the state and of the error covariance matrix is updated in Equation~(\ref{eq:kalman-pred1})~and~(\ref{eq:kalman-pred2}) respectively.
-The value of $\hat{\mathbf{q}}_1^-$ is then used in Equation~(\ref{eq:kalman-est2}) to estimate the current state along with the data from the sensor $y_0$ (e.g., the energy sensor of the flight controller of the fixed-wing craft), where the sensor noise covariance matrix $R$ accounts for the amount of uncertainty in the measurement.
-The estimated output $\hat{y}_0$ is then obtained from Equation~(\ref{eq:kalman-est4}).
-The algorithm is iterative.
-At time $k=1$ the values $\hat{\mathbf{q}}_1,P_1$ computed at previous step are used to estimate the values $\hat{\mathbf{q}}_2,P_2,$ and $y_1$.
-
-%\subsection{Optimal control action}
-
-%*
 
@@
 
-The algorithm per each time step updates the state.
-The position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}.
-Note the position can be computed directly from Equation~(\ref{eq:pd}).
+Per each time step, the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control sequence s.t.
+the mission is still valid.
+Note that the position can be computed directly from Equation~(\ref{eq:pd}).
 If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
@@
 \end{split}\end{equation}
-where matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are all positive definite.
+where matrices $P_f,Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are all positive definite.
 
-Follows a check if the mission can finish without the eventuality of the battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control sequence being eventually updated and the process reiterated at line~\ref{alg:recursion}.
+Follows a check if the mission can finish without the eventuality of battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control sequence being eventually updated and the process reiterated at line~\ref{alg:recursion}.
 
-Before the next step a state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
+Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
 

### 2020-10-21 icra-2021.tex
proofreading

@@
 The mission consists of a UAV flying in circles and lines covering a polygon, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
-The algorithm plans the mission controlling the processing rate, and the radius of the circles which affects the distance between the lines.
+The algorithm plans the mission controlling the processing rate and the radius of the circles, affecting the distance between the lines.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
 Figure~\ref{fig:overview} shows an initial slice of such a mission.
-The UAV first converges to the circular TEE $\varphi_0$, and later shifts to TEE $\varphi_0^+$, as e.g., windy weather required the adjustment of the control sequence to avoid battery depletion.
+The UAV first heads to the circular TEE $\varphi_0$, and later shifts to TEE $\varphi_0^+$, as e.g., windy weather required the adjustment of the control sequence to avoid battery depletion.
 
@@
 The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
-The algorithm that uses the model and solves the mobile robot dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
+The algorithm that uses the model and solves the UAV dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
 Section~\ref{sec:experimental} presents the result and showcase the performances.
@@
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_k:=\{(\varphi_k&(\,\cdot\,),\psi_1(\,\cdot\,),...,\psi_\sigma(\,\cdot\,))\mid\\\exists\,\,&\varphi_k(\,\cdot\,)\in\mathbb{C}_k,\,\\&\,\psi_i(\,\cdot\,)\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
+    \mathcal{M}_k:=\{(\varphi_k&(\,\cdot\,),\psi_1(\,\cdot\,),...,\psi_\sigma(\,\cdot\,))\mid\\\exists\,\,&\varphi_k(\,\cdot\,)\in\mathbb{C}_k,\,\\&\,\psi_i(\,\cdot\,)\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]^+\},
   \end{split}\end{equation}
@@
   \end{equation}
-  the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
+  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
 \end{defn}
@@
 The UAV heads to $\varphi_0$ initially using the desired velocity vector $\dot{\mathbf{p}}_d$, but it later heads to $\varphi_0^+$ reducing the radius $c_{0,0}$ to satisfy the battery constraints (indeed the energy coefficients $\mathbf{q}_0$ evolution is higher then $\mathbf{q}_0^+$).
-The UAV then converges to $\varphi_1$, to $\varphi_3$, and so on until it covers the polygon (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
+The UAV then converges to $\varphi_1$, $\varphi_2$, $\varphi_3$, and so on until it covers the polygon (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
   \label{fig:overview}
@@
 
-The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 \end{split}\end{equation}
-where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$.
+where $\mathbf{s}_k,g(\,\cdot\,)$ are defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$.
 Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
@@
 In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption).
-An observation summarized in the following Lemma.
+An observation summarized in the following Lemma, where we use norm to compare two energy coefficients vectors.
 
@@
 
-The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds a computational energy consumption model.
+The energy cost of the computations (set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds a computational energy consumption model.
 Specifically, the tool builds a linear interpolation, one per each task.
@@
 \begin{equation}\label{eq:qos-def}
-  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]\right\},
+  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]^+\right\},
 \end{equation}
-where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.
+where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]^+}{\mathbb{S}_{k,i}}$.
 
@@
 \begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^s:=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
+  y_k^s:=g\left(\text{QoS}_{k,1},\dots,\text{QoS}_{k,\sigma}\right)=g\left(\mathbf{s}_{k}\right).\\
 \end{split}\end{equation}
@@
 
-Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the algorithm produce a valid mission.
+Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the algorithm produce a set of control sequences $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
 \begin{defn}[Valid mission]\label{def:valid}
-  A mission is valid if for every stage $\mathcal{M}_{k-1}$ in $k\in[t_f]^+$ there exist a control sequence $\mathbf{u}_k^{a}$ which produce the stage $\mathcal{M}_k$
+  A mission is valid if for every stage $\mathcal{M}_{k-1}$ in $k\in[t_f]^+$ there exist a control sequence $\mathbf{u}_k^{a}$ that produce the next stage $\mathcal{M}_k$
   \begin{equation}\begin{split}
-    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
+    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid& \,\exists\,\mathbf{c}_{k-1}\in\mathbb{C}_{k-1}, \mathbf{s}_{k-1}\in\mathbb{S}_{k-1}\text{ and}\\
+    &(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
     &\Longrightarrow(\varphi(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{k}\}.
@@
 Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.
-  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathcal{M}_k$ produce a valid mission $\mathcal{M}_{k+1}\,\forall k\in[t_f-1]$.
+  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathbf{u}_k^a$ allows to produce stage $\mathcal{M}_{k+1}$ from $\mathcal{M}_k\,\forall k\in[t_f-1]$.
 \end{thm}
@@
     V^2-
-    4R\tilde{V}y_kV^{-1}}
-  \right)/2RQ_c,\\ 
+    4R_r\tilde{V}y_kV^{-1}}
+  \right)/2R_rQ_c,\\ 
 \end{split}\end{equation}
-where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
+where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
 We define the output constraints set

### 2020-10-21 icra-2021.tex
and we have a proof! (and a theorem that seems to work)

@@
 
-In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption).
+%In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption).
 An observation summarized in the following Lemma, where we use norm to compare two energy coefficients vectors.
 
-\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
-  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Given two time instants $k_1,k_2\in[t_f]$
-  \begin{equation}
-    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
-  \end{equation}
-\end{lem}
-\begin{proof}
-  *
-\end{proof}
-
+%\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
+%  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Then
+%  \begin{equation}
+%    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
+%  \end{equation}
+%\end{lem}
+%\begin{proof}
+%  Suppose $y_{k_1}\geq y_{k_2}$ is true.
+Given $k=k_1, k+n=k_2$, $y_{k}=\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}$.
+Moreover, the time evolution of the model in Equation~(\ref{eq:state-perf}) can be expressed $y_{k+n}=(\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1(n)\alpha_{k,1}+\dots+p_r(n)\alpha_{k,r}$, where $p_r(n):=\prod_{i=1}^{n/2}{r^3/\xi^3}$ depends on the order of a given coefficient and $n$.
+%  Hence, $\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1\alpha_{k,1}+\dots+p_r\alpha_{k,r}$.
+%
+%  The magnitudes are $\|\mathbf{q}_{k}\|=(\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2)^{1/2}$ and $\|\mathbf{q}_{k+n}\|=((\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2(n)\alpha_{k,1}^2+p_1^2(n)\beta_{k,1}^2+\dots+p_r^2(n)\alpha_{k,r}^2+p_r^2(n)\beta_{k,r}^2)^{1/2}$.
+%  By still inspecting the Equation~(\ref{eq:state-perf}), the coefficient $p_r^2(n)\beta_{k,r}^2$ can be expressed as a function of coefficients $\alpha$, $p_r^2(n)\beta_{k,r}^2=$
+%  
+%  Hence $\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2\alpha_{k,1}^2+p_1^2\beta_{k,1}^2+\dots+p_r^2\alpha_{k,r}^2+p_r^2\beta_{k,r}^2$ and $()$.
+%
+%\end{proof}
+% Lol wrong... Doesn't make sense this lemma at all...
+%
 \subsection{Energy evolution due to computations}
@@
 \begin{thm}[State output linearity]\label{thm:state-vs-energy}
-  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, and assume Assumption~\ref{assm:periodic} holds.
-Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally.
-  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathbf{u}_k^a$ allows to produce stage $\mathcal{M}_{k+1}$ from $\mathcal{M}_k\,\forall k\in[t_f-1]$.
+  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, assume Assumption~\ref{assm:periodic} holds, the model behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state is $\mathbf{q}_0=\begin{bmatrix}
+    y_0^m/j & (1/2)y_0^m/j & \cdots & (1/2)y_0^m/j
+  \end{bmatrix}^T$ where $y_0^m\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^m$ can be the initial measurement or the measurement from a previous instance of the algorithm}, and the mission is valid.
+  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
 \end{thm}
 \begin{proof}
-  *\\
+  The proof is based on mathematical induction. 
+  \emph{(Base case)}.
+We proof that $y_0=y_0^m$.
+Recall the definition of the state in Equation~(\ref{eq:state-details}).
+The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^m/j+(1/2)y_0^m/j+\cdots+(1/2)y_0^m/j=y_0^m$.
+
+  \emph{(Induction step)}.
+By inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(n)\alpha_{0,r}$, where
+  \begin{equation}
+    p_r(k):=\begin{cases}
+      \prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for even }k\\
+      (r/\xi)\prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for odd }k
+    \end{cases},
+  \end{equation}
+  Using $\mathbf{q}_0$ leads to $y_{k}=(y_0^m/j+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^m/j+\dots+p_r(k)(1/2)y_0^m/j=y_{k}^m$.
+
+  We prove now that the instantaneous energy consumption at $k+1$ is still a linear combination of the state $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)\beta_{k,1}+\dots+(r/\xi)\beta_{k,r}$.
+Notice that the coefficients $\alpha,\beta$ have an equivalent evolution (indeed this allows to simulate the periodicity) and $\beta_{k,r}=p_r(k)\beta_{0,r}$.
+The output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$.
+The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$.
+Using $\mathbf{q}_0$ leads to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^m+\dots+p_r(k+1)(1/2)y_0^m=y_{k+1}^m$, alike the previous statement ($y_k^m=y_{k+1}^m$), but at instant $k+1$.
 \end{proof}

### 2020-10-21 icra-2021.tex
and we have a proof! (2)

@@
 
-\begin{thm}[State output linearity]\label{thm:state-vs-energy}
-  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, assume Assumption~\ref{assm:periodic} holds, the model behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state is $\mathbf{q}_0=\begin{bmatrix}
+\begin{thm}[State, output linearity]\label{thm:state-vs-energy}
+  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}.
+Assume Assumption~\ref{assm:periodic} holds, the model behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state is $\mathbf{q}_0=\begin{bmatrix}
     y_0^m/j & (1/2)y_0^m/j & \cdots & (1/2)y_0^m/j
@@
   \emph{(Induction step)}.
-By inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(n)\alpha_{0,r}$, where
+By inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where by omitting the sign
   \begin{equation}
@@
       (r/\xi)\prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for odd }k
-    \end{cases},
+    \end{cases}.
   \end{equation}
@@
 
-  We prove now that the instantaneous energy consumption at $k+1$ is still a linear combination of the state $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)\beta_{k,1}+\dots+(r/\xi)\beta_{k,r}$.
+  We prove now that the instantaneous energy consumption at $k+1$ is still a linear combination of the state.
+We express the output in function of the previous state $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)\beta_{k,1}+\dots+(r/\xi)\beta_{k,r}$.
 Notice that the coefficients $\alpha,\beta$ have an equivalent evolution (indeed this allows to simulate the periodicity) and $\beta_{k,r}=p_r(k)\beta_{0,r}$.
-The output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$.
+Thus, the output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$.
 The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$.

### 2020-10-22 icra-2021.tex
polish session

@@
 
-Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the algorithm produce a set of control sequences $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a set of control sequences $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
@@
 
-Let us proof that if the mission is valid, the instantaneous energy consumption is a linear combination of the state from the Equation~(\ref{eq:state-perf}).
+Let us proof that if the mission is valid, the instantaneous energy consumption can be modeled as linear combination of the state from the Equation~(\ref{eq:state-perf}) for all $k\in[t_f]$.
 
-\begin{thm}[State, output linearity]\label{thm:state-vs-energy}
+\begin{thm}[Periodic energy model]\label{thm:state-vs-energy}
   Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}.
-Assume Assumption~\ref{assm:periodic} holds, the model behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state is $\mathbf{q}_0=\begin{bmatrix}
-    y_0^m/j & (1/2)y_0^m/j & \cdots & (1/2)y_0^m/j
-  \end{bmatrix}^T$ where $y_0^m\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^m$ can be the initial measurement or the measurement from a previous instance of the algorithm}, and the mission is valid.
+Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^m/j$ for the first coefficient where $y_0^m\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^m$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^m/j$ for all the others, and the mission is valid.
   Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
@@
   The proof is based on mathematical induction. 
-  \emph{(Base case)}.
-We proof that $y_0=y_0^m$.
+  Base case: we proof that $y_0=y_0^m$.
 Recall the definition of the state in Equation~(\ref{eq:state-details}).
@@
 
-  \emph{(Induction step)}.
-By inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where by omitting the sign
-  \begin{equation}
-    p_r(k):=\begin{cases}
-      \prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for even }k\\
-      (r/\xi)\prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for odd }k
+  Induction step: by inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where $\forall n\in\mathbb{Z}_{\geq 2}$
+  \begin{equation}\label{eq:proof-pr}
+    p_r(n):=\begin{cases}
+      \prod_{i=1}^{n/2}{r^3/\xi^3}&\text{ for even }n\\
+      (r/\xi)\prod_{i=1}^{(n-1)/2}{r^3/\xi^3}&\text{ for odd }n
     \end{cases}.
   \end{equation}
-  Using $\mathbf{q}_0$ leads to $y_{k}=(y_0^m/j+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^m/j+\dots+p_r(k)(1/2)y_0^m/j=y_{k}^m$.
+
+  Suppose $k$ is even and the theorem holds up to $k$.
+Initial energy coefficients state $\mathbf{q}_0$ leads to $y_{k}=(y_0^m/j+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^m/j+\dots+p_r(k)(1/2)y_0^m/j=y_{k}^m$.
 
@@
 Thus, the output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$.
-The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$.
-Using $\mathbf{q}_0$ leads to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^m+\dots+p_r(k+1)(1/2)y_0^m=y_{k+1}^m$, alike the previous statement ($y_k^m=y_{k+1}^m$), but at instant $k+1$.
+The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$ using the definition of $p_r$ in Equation~(\ref{eq:proof-pr}).
+Again, the state $\mathbf{q}_0$ leads to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^m+\dots+p_r(k+1)(1/2)y_0^m=y_{k+1}^m$, alike the previous statement ($y_k^m=y_{k+1}^m$), but at instant $k+1$.
+The proof for odd $k$ is equivalent.
 \end{proof}
@@
 
-Recall the model in Equation~(\ref{eq:state-perf}).
-We stated the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
-This is generally untrue.
-Physical UAVs are bounded by strict battery limitations.
+We stated earlier the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$. This is generally untrue. Physical UAVs are bounded by strict battery limitations.
 
@@
 
-Per each time step, the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control sequence s.t.
-the mission is still valid.
+Per each time step, the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control sequence.
 Note that the position can be computed directly from Equation~(\ref{eq:pd}).
@@
 
-In detail, initial guesses for $\mathbf{q}_0$ and $P_0\in\mathbb{R}^{j\times j}$ are derived empirically.
+In detail, initial guess for $P_0\in\mathbb{R}^{j\times j}$ is positive definite and derived empirically, for $\mathbf{q}_0$ an initial measurement is distributed to the coefficients (see Theorem~\ref{thm:state-vs-energy}).
 Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the current control sequence.
@@
 \end{split}\end{equation}
-where matrices $P_f,Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are all positive definite.
+where matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are positive definite.
 
@@
 
-Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$.
+Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$, or sensor measurements are unavailable ($y_k^m=0$).
 

### 2020-10-23 figures/video/generate.sh
added the short presentation of the initial instance of the algorithm

@@ -1,0 +1,51 @@
+#!/bin/bash
+rm generated/*
+
+gnuplot -e "
+    set datafile separator ',';
+    set term svg size 200,200;
+    unset title;
+    set xrange [-133:95];
+    set xtics 20*3 center offset -.4,.5;
+    set yrange [-76:231];
+    set ytics 60 center offset -1.6,0;
+    set grid ytics,xtics;
+    set xlabel 'x (m)' rotate parallel center offset -1.4,.9;
+    set ylabel 'y (m)' rotate parallel center offset 1.8,-1.1;
+    stats '../../data/simulation2/path_sim.csv' nooutput;
+    print floor(STATS_records);
+    do for [i=1:4] {
+        outfile = sprintf('generated/path%d.svg',i);
+        set output outfile;
+        set object 1 ellipse center -45,146  size 140,140 front fs empty border lc rgb 'green';
+        plot  '../../data/simulation2/path_sim.csv' using 1:2 every ::1::i w l notitle lc rgb 'red';
+    };
+"
+
+gnuplot -e "
+    set datafile separator ',';
+    set term svg size 200,200;
+    unset title;
+    set xrange [-133:95];
+    set xtics 20*3 center offset -.4,.5;
+    set yrange [-76:231];
+    set ytics 60 center offset -1.6,0;
+    set grid ytics,xtics;
+    set xlabel 'x (m)' rotate parallel center offset -1.4,.9;
+    set ylabel 'y (m)' rotate parallel center offset 1.8,-1.1;
+    stats '../../data/simulation2/path_sim.csv' nooutput;
+    print floor(STATS_records);
+    do for [i=5:11] {
+        outfile = sprintf('generated/path%d.svg',i);
+        set output outfile;
+        set arrow from -115, graph 0 to -115, graph 1 nohead lc rgb 'green';
+        plot  '../../data/simulation2/path_sim.csv' using 1:2 every ::1::i w l notitle lc rgb 'red';
+    };
+"
+
+for i in generated/*.svg; do svg2tikz --figonly $i > $i.tikz; done
+
+sed -i -- 's/y\ (m)/\\rotatebox{90}{y\ (m)}/g' generated/*.tikz
+
+#plot '../../data/simulation2/varphi0_gdn.csv' using 1:2:3:4 with vectors head filled lt 2 notitle;
+

### 2020-10-23 scripts/position/OP1.m

@@ -29,9 +29,16 @@ end
 
 % create all the points used to build the vector field
 
+items = input('[   ? ] Number of arrows to plot per axis: ');
+
+if isempty(items)
+   
+    items = 50;
+end
+
 [xp yp] = meshgrid(...
-    min:(abs(min) + abs(max)) / 50:max, min:(abs(min) + abs(max)) / 50:max...
-                  );
+    min:(abs(min) + abs(max)) / items:max,... 
+    min:(abs(min) + abs(max)) / items:max);
               
 points = reshape(cat(2, xp', yp'), [], 2);
 clear xp yp;
@@ -88,7 +95,7 @@ else
     
     figure;
     
-    plot_gdn2(E, ke, varphi, points, pdangle, ...
+    [dpdx, dpdy] = plot_gdn2(E, ke, varphi, points, pdangle, ...
         min, max, 0, 0, [0; 0]);
 end
 

### 2020-10-23 scripts/position/plot_gdn2.m

@@ -1,4 +1,4 @@
-function [] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
+function [dpdx, dpdy] = plot_gdn2(E, ke, varphi, points, pdangle, min, max, andu, s, p)
 % PLOT_GDN2 Plots the vector field, and eventually animates it
 %
 % Inputs:

### 2020-10-24 icra-2021.tex
implemented all latest Hector's suggestions

@@
 The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
-It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator.
-It output the controls sequence (computations and adjustments) using robust output feedback model predictive control (MPC).
+It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to approximately evolve also periodically--and the uncertainty with a state estimator.
+It output the control input (computations and adjustments) using robust output feedback model predictive control (MPC).
 
@@
 The algorithm plans the mission controlling the processing rate and the radius of the circles, affecting the distance between the lines.
+Figure~\ref{fig:overview} shows an initial slice of such a mission.
+The UAV first heads to a circular TEE with a given radius, which is later reduced, as e.g., windy weather required the adjustment of the control input to avoid battery depletion.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
-Figure~\ref{fig:overview} shows an initial slice of such a mission.
-The UAV first heads to the circular TEE $\varphi_0$, and later shifts to TEE $\varphi_0^+$, as e.g., windy weather required the adjustment of the control sequence to avoid battery depletion.
 
@@
 
-Let a mission's stage be a generic continuous twice differentiable TEE $\varphi$ and a set of tasks $\psi_1,\dots,\psi_{\sigma}$.
-Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{0,1,\dots,\,\cdot\,\}$, $[\,\cdot\,]^+$ the set $\{0\}/[\,\cdot\,]$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the lower and upper bound of $\,\cdot\,$.
-If $\,\cdot\,$ is a value, the bounds are user defined and retrieved from a lookup table; if a set, they correspond to minimum and maximum of the set.
+The mission consists of different stages. At each stage the robot must follow a path and do some tasks.
+
+Let the path at stage $i$ be characterized by a generic continuous twice differentiable TEE $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ and the tasks by $\psi_1,\dots,\psi_{\sigma}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ functions.
+Moreover, let $[a]$ be the set $\{0,1,\dots,a\}$, $[a]^+$ the set $\{0\}/[a]$, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a lookup table.
 
 \begin{defn}[Stage and mission]\label{def:mission}
-  At a time instant $k\in[0,t_f)$, the \emph{stage} is defined as the ordered list
+  A \emph{stage} $i$ at time instant $k$ is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_k:=\{(\varphi_k&(\,\cdot\,),\psi_1(\,\cdot\,),...,\psi_\sigma(\,\cdot\,))\mid\\\exists\,\,&\varphi_k(\,\cdot\,)\in\mathbb{C}_k,\,\\&\,\psi_i(\,\cdot\,)\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]^+\},
+    \mathcal{M}_i:=\{(\varphi_i&(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),\\
+      \psi_1&(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma}))\mid\\
+      \exists\,\,\varphi&_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
+      \psi&_j(s_{i,j})\in\mathbb{S}_{i,j}\,\forall j\in[\sigma]^+\},
   \end{split}\end{equation}
-  where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set.
-The parameters of the TEE $\varphi_k$ are defined in Subsection~\ref{sec:model}, of the tasks $\psi_1,\dots,\psi_\sigma$ in~\ref{sec:computations-model}.
+  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{i,j}:=[\underline{s}_{i,j},\overline{s}_{i,j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th task QoS set.
+The parameters of the TEE $\varphi_i$ are defined in Subsection~\ref{sec:model}, of the tasks $\psi_1,\dots,\psi_\sigma$ in~\ref{sec:computations-model}.
 
-  The \emph{mission} is the union of all the stages, along with a function $\lambda:\mathbb{R}^2\rightarrow\mathcal{M}_k$ which maps a point $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
+  The \emph{mission} is the union of all the stages, along with a function $\lambda:\mathbb{R}^2\rightarrow\mathcal{M}_i$ which maps a point $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
 some inertial navigation frame $\mathcal{O}_W$ to a specific stage.
-If for simplicity the system is sampled discrete-time
+For simplicity the system is sampled discrete-time and $l$ is the total number of stages
   \begin{equation}
-    \mathcal{M}:=(\lambda(\mathbf{p}),\bigcup_{i\in[t_f]}{\mathcal{M}_i}),
+    \mathcal{M}:=(\lambda(\mathbf{p}),\bigcup_{i\in[l]}{\mathcal{M}_i}),
   \end{equation}
-  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
+  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
 \end{defn}
@@
 \begin{equation}\label{eq:area}
-  \mathcal{P}_k:=\{\mathbf{p}_k\mid\varphi_k(\mathbf{p}_k,c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
+  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
 \end{equation}
-delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (gray area in Figure~\ref{fig:overview}), being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$.
+delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (gray area in Figure~\ref{fig:overview}), being the TEE satisfied for all the approaching points $\varphi_i\rightarrow\mathbb{C}_i$.
 
 The algorithm uses the concept to select the adjustments s.t.
-$\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$ has the highest energy value.
-It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the vector field of $\varPhi:=\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$, deriving the direction to follow--the desired velocity vector
+$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest energy value.
+It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the vector field of $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, deriving the direction to follow--the desired velocity vector
 \begin{equation}\label{eq:pd}
@@
 
-The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^m$ derived from Fourier analysis (the meaning of $m$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 \begin{equation}\label{eq:fourier}
-  h(t)=\sum_{n=0}^{r}{a_n\cos\left({nt/\xi}\right)+b_n\sin{\left({nt/\xi}\right)}},
+  h(k)=\sum_{i=0}^{r}{a_i\cos\left({ik/\xi}\right)+b_i\sin{\left({ik/\xi}\right)}},
 \end{equation}
-where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ the Fourier series coefficients.
+where $\xi\in\mathbb{R}$ is the characteristic time, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
-Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting for the unknown state and output is absent.
+Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ accounting for the unknown state and output is absent.
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
@@
      &    &       & A_r 
-  \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
+  \end{array}\right],\,A_i=\begin{bmatrix}0 & \frac{i}{\xi} \\ -\frac{i^2}{\xi^2} & 0\end{bmatrix},\\
   C&=\left[\begin{array}{cccccc}
@@
 \end{split}\end{equation}
-where $\mathbf{q}_k\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix.
-In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remainder.
+where $\mathbf{q}_k\in\mathbb{R}^m$ given $m:=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+In matrix $A$, the first value is one, $A_i$ is later on the diagonal, and zero in the remainder.
 
-The control $\mathbf{u}$ along with the input matrix
+Suppose at time instant $k$ the mission reached stage $i$ and the control input is $\mathbf{u}_k^a=(\mathbf{c}_k,\mathbf{s}_k)$. The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}  
@@
   B&=\left[\begin{array}{cccc}
-    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
+    1& \omega_{i,1}& \cdots& \omega_{i,\rho}  \\
      &            0&       &  \\
@@
 \end{split}\end{equation}
-where $\mathbf{s}_k,g(\,\cdot\,)$ are defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$.
-Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
+where $\mathbf{s}_k,g(\mathbf{s}_k)$ are defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^n$ is the control given $n:=1+\rho$, and $B\in\mathbb{R}^{m\times n}$.
+Moreover, the first item is one, while the others on the first row are gain factors $\omega_{i}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
 
-Note that the controls sequence $\mathbf{u}_k^a:=(\mathbf{c}_{k},\mathbf{s}_{k})$--an output of the algorithm--differs from the nominal control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
+Note that the control input $\mathbf{u}_k^a:=(\mathbf{c}_{k},\mathbf{s}_{k})$--an output of the algorithm--differs from the nominal control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
 
@@
 \begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
-Given two time instants $k_1,k_2\in[t_f]$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{R}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
+Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}_{\geq 0}$
 \begin{equation}
@@
 Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
-The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment.
-Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy coefficients.
+The energy due to the adjustments is merely a linear combination of the gain factor $\omega$ and the adjustment.
+Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the state.
 For instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
 
-%In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption).
-An observation summarized in the following Lemma, where we use norm to compare two energy coefficients vectors.
-
-%\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
-%  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Then
-%  \begin{equation}
-%    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
-%  \end{equation}
-%\end{lem}
-%\begin{proof}
-%  Suppose $y_{k_1}\geq y_{k_2}$ is true.
-Given $k=k_1, k+n=k_2$, $y_{k}=\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}$.
-Moreover, the time evolution of the model in Equation~(\ref{eq:state-perf}) can be expressed $y_{k+n}=(\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1(n)\alpha_{k,1}+\dots+p_r(n)\alpha_{k,r}$, where $p_r(n):=\prod_{i=1}^{n/2}{r^3/\xi^3}$ depends on the order of a given coefficient and $n$.
-%  Hence, $\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1\alpha_{k,1}+\dots+p_r\alpha_{k,r}$.
-%
-%  The magnitudes are $\|\mathbf{q}_{k}\|=(\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2)^{1/2}$ and $\|\mathbf{q}_{k+n}\|=((\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2(n)\alpha_{k,1}^2+p_1^2(n)\beta_{k,1}^2+\dots+p_r^2(n)\alpha_{k,r}^2+p_r^2(n)\beta_{k,r}^2)^{1/2}$.
-%  By still inspecting the Equation~(\ref{eq:state-perf}), the coefficient $p_r^2(n)\beta_{k,r}^2$ can be expressed as a function of coefficients $\alpha$, $p_r^2(n)\beta_{k,r}^2=$
-%  
-%  Hence $\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2\alpha_{k,1}^2+p_1^2\beta_{k,1}^2+\dots+p_r^2\alpha_{k,r}^2+p_r^2\beta_{k,r}^2$ and $()$.
-%
-%\end{proof}
-% Lol wrong... Doesn't make sense this lemma at all...
-%
 \subsection{Energy evolution due to computations}
@@
 It requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters.
-A way to simulate the change of the computations.
 
-The plan $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}).
-These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations
+The mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
+These tasks are simulated by ROS nodes $\Psi(\mathbf{s}_i):=\left(\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\right)$, in fact they input the desired and output the actual computations
 \begin{equation}\label{eq:qos-def}
-  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]^+\right\},
+  \mathbf{s}_i:=\left\{s_{i,1},\dots ,s_{i,\sigma}\mid \psi_j(s_{i,j})\in\mathbb{S}_{i}\,\forall j\in[\sigma]^+\right\},
 \end{equation}
-where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]^+}{\mathbb{S}_{k,i}}$.
+where $s_{i,j}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $j$-th desired computation at stage $i$, $\mathbf{s}_i\in\mathbb{S}_i\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the union of all QoS sets given $\mathbb{S}_i:=\bigcup_{j\in[\sigma]^+}{\mathbb{S}_{i,j}}$.
 
-Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained interrogating \powprof{}
+Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the actual instantaneous computational energy consumption value obtained interrogating \powprof{}
 \begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^s:=g\left(\text{QoS}_{k,1},\dots,\text{QoS}_{k,\sigma}\right)=g\left(\mathbf{s}_{k}\right).\\
+  y_k^s:=g\left(\Psi(\mathbf{s}_i)\right)=g\left(\mathbf{s}_{k}\right).\\
 \end{split}\end{equation}
@@
 
-Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a set of control sequences $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a set of control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
 \begin{defn}[Valid mission]\label{def:valid}
-  A mission is valid if for every stage $\mathcal{M}_{k-1}$ in $k\in[t_f]^+$ there exist a control sequence $\mathbf{u}_k^{a}$ that produce the next stage $\mathcal{M}_k$
+  A mission is valid if for every stage $\mathcal{M}_{i-1},\,i\in[l]^+$ there exist a control input $\mathbf{u}_k^{a}$ that produce the next stage $\mathcal{M}_i$
   \begin{equation}\begin{split}
-    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid& \,\exists\,\mathbf{c}_{k-1}\in\mathbb{C}_{k-1}, \mathbf{s}_{k-1}\in\mathbb{S}_{k-1}\text{ and}\\
-    &(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
-    &\Longrightarrow(\varphi(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{k}\}.
+    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi_i(\mathbf{p}_{k-1},\mathbf{c}_{i-1}),\Psi(\mathbf{s_{i-1}}))\in\mathcal{M}_{i-1}\\
+    &\Longrightarrow(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{i}),\Psi(\mathbf{s}_{i}))\in\mathcal{M}_{i}\}.
   \end{split}\end{equation}
@@
 
-Let us proof that if the mission is valid, the instantaneous energy consumption can be modeled as linear combination of the state from the Equation~(\ref{eq:state-perf}) for all $k\in[t_f]$.
+Let us proof that if the mission is valid, the instantaneous energy consumption can be modeled as linear combination of the state from the Equation~(\ref{eq:state-perf}).
 
@@
   Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}.
-Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^m/j$ for the first coefficient where $y_0^m\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^m$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^m/j$ for all the others, and the mission is valid.
+Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^a/m$ for the first coefficient where $y_0^a\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^a$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^a/m$ for all the others, and the mission is valid.
   Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
@@
   The proof is based on mathematical induction. 
-  Base case: we proof that $y_0=y_0^m$.
+  Base case: we proof that $y_0=y_0^a$.
 Recall the definition of the state in Equation~(\ref{eq:state-details}).
-The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^m/j+(1/2)y_0^m/j+\cdots+(1/2)y_0^m/j=y_0^m$.
+The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^a/m+(1/2)y_0^a/m+\cdots+(1/2)y_0^a/m=y_0^a$.
 
-  Induction step: by inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where $\forall n\in\mathbb{Z}_{\geq 2}$
+  Induction step: by inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where $\forall t\in\mathbb{Z}_{\geq 2}$
   \begin{equation}\label{eq:proof-pr}
-    p_r(n):=\begin{cases}
-      \prod_{i=1}^{n/2}{r^3/\xi^3}&\text{ for even }n\\
-      (r/\xi)\prod_{i=1}^{(n-1)/2}{r^3/\xi^3}&\text{ for odd }n
+    p_r(t):=\begin{cases}
+      \prod_{i=1}^{t/2}{r^3/\xi^3}&\text{ for even }t\\
+      (r/\xi)\prod_{i=1}^{(t-1)/2}{r^3/\xi^3}&\text{ for odd }t
     \end{cases}.
@@
   Suppose $k$ is even and the theorem holds up to $k$.
-Initial energy coefficients state $\mathbf{q}_0$ leads to $y_{k}=(y_0^m/j+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^m/j+\dots+p_r(k)(1/2)y_0^m/j=y_{k}^m$.
+Initial energy coefficients state $\mathbf{q}_0$ leads to $y_{k}=(y_0^a/m+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^a/m+\dots+p_r(k)(1/2)y_0^a/m=y_{k}^a$.
 
@@
 The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$ using the definition of $p_r$ in Equation~(\ref{eq:proof-pr}).
-Again, the state $\mathbf{q}_0$ leads to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^m+\dots+p_r(k+1)(1/2)y_0^m=y_{k+1}^m$, alike the previous statement ($y_k^m=y_{k+1}^m$), but at instant $k+1$.
+Again, the state $\mathbf{q}_0$ leads to $y_{k+1}=(y_0^a/m+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^a/m+\dots+p_r(k+1)(1/2)y_0^a/m=y_{k+1}^a$, alike the previous statement, but at instant $k+1$.
 The proof for odd $k$ is equivalent.
@@
 \end{equation}
-where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
+and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
 \subsection{Deployment algorithm}
@@
 
-  \State $\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$\label{alg:max_cont_sequence}
+  \State $\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\max{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$\label{alg:max_cont_sequence}
 
@@
   \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}\label{alg:output_constraints}
-    \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\{\overline{\mathbf{u}}^a_{k-1}\}$
+    \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\{\max{\mathbf{u}}^a_{k-1}\}$
     \State\Return{\Call{Step}{$\mathbf{q}_{k-1}$, $\mathbf{u}^a_{k-1}$, $\mathbf{u}_{k-2}^a$,$P_{k-1}$}}\label{alg:recursion}
   \Else
-    \If{$\abs{y_k^m-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
+    \If{$\abs{y_k^a-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
       \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$\label{alg:evolution}
@@
       \State $K\gets P_k^-C^T/(CP_k^-C^T+R)$
-      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+K(y_k^m-C\hat{\mathbf{q}}_k^-)$
+      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+K(y_k^a-C\hat{\mathbf{q}}_k^-)$
       \State $P_k\gets(I+KC)P_k^-$\label{alg:kalman_end}
@@
 
-    \State $\mathbf{u}_{k}^a\gets \{\mathbf{u}_{k}^a\mid(\varphi_k(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s_{k}}))\in\mathcal{M}_{k}\subseteq\mathcal{M}\}$
+    \State $\mathbf{u}_{k}^a\gets \{\mathbf{u}_{k}^a\mid(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{i}),\Psi(\mathbf{s_{i}}))\in\lambda(\mathbf{p}_k)\}$
     \State $(\mathbf{q}_k,P_k,\mathbf{u}_k^a)\gets$\Call{Step}{$\mathbf{q}_{k}$, $\mathbf{u}^a_{k}$, $\mathbf{u}_{k-1}^a$, $P_k$}\label{alg:en}
@@
 
-Per each time step, the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control sequence.
+Per each time step $k$ (the final time $t_f$ is unknown), the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control input.
 Note that the position can be computed directly from Equation~(\ref{eq:pd}).
@@
 
-In detail, initial guess for $P_0\in\mathbb{R}^{j\times j}$ is positive definite and derived empirically, for $\mathbf{q}_0$ an initial measurement is distributed to the coefficients (see Theorem~\ref{thm:state-vs-energy}).
-Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the current control sequence.
+In detail, initial guess for $P_0\in\mathbb{R}^{j\times j}$ is positive definite and derived empirically, for $\mathbf{q}_0$ the initial measurement is distributed to the coefficients (see Theorem~\ref{thm:state-vs-energy}).
+Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the current control input.
 Line~\ref{alg:mpc} uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the optimal control $\mathbf{u}^0$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function
@@
 
-Follows a check if the mission can finish without the eventuality of battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control sequence being eventually updated and the process reiterated at line~\ref{alg:recursion}.
+Follows a check if the mission can finish without the eventuality of battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control input being eventually updated and the process reiterated at line~\ref{alg:recursion}.
 
-Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^m\in\mathbb{R}$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$, or sensor measurements are unavailable ($y_k^m=0$).
+Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^a$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$, or sensor measurements are unavailable ($y_k^a=0$).
 
 %%%%%%%%%%%%%%%%%%%%
-\section{Evaluation}
+\section{Results}
 \label{sec:experimental}

### 2020-10-25 icra-2021.tex
updated the overview figure with suggestions
updated figure positioning
updated the captuin

@@
 
+\begin{figure*}[t]
+  \centering
+  \input{\figpath/icra-2021_overview2.tikz}
+  \caption{The mission consists of circles and lines that cover a polygon.
+The UAV heads to $\varphi_0$ initially, using the desired velocity vector $\dot{\mathbf{p}}_d$.
+It later heads to $\varphi_0^-$ reducing the radius $c_{0,1}$ to satisfy the battery constraints (indeed the energy coefficients $\mathbf{q}_{k_2}$ evolution is higher then $\mathbf{q}_{k_3}$).
+The UAV then converges to $\varphi_1$ in stage $\mathcal{M}_1$, $\varphi_2$ in stage $\mathcal{M}_2$, and so on (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
+  \label{fig:overview}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 \end{defn}
-
-\begin{figure}[t]
-  \centering
-  \input{\figpath/icra-2021_overview.tikz}
-  \caption{The mission consists of circles and lines that forms a survey pattern.
-The UAV heads to $\varphi_0$ initially using the desired velocity vector $\dot{\mathbf{p}}_d$, but it later heads to $\varphi_0^+$ reducing the radius $c_{0,0}$ to satisfy the battery constraints (indeed the energy coefficients $\mathbf{q}_0$ evolution is higher then $\mathbf{q}_0^+$).
-The UAV then converges to $\varphi_1$, $\varphi_2$, $\varphi_3$, and so on until it covers the polygon (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
-  \label{fig:overview}
-\end{figure}
 

### 2020-10-25 icra-2021.tex
proofreading

@@
   \input{\figpath/icra-2021_overview2.tikz}
-  \caption{The mission consists of circles and lines that cover a polygon.
+  \caption{The mission consists of circles and lines covering a polygon.
 The UAV heads to $\varphi_0$ initially, using the desired velocity vector $\dot{\mathbf{p}}_d$.
@@
 The UAV first heads to a circular TEE with a given radius, which is later reduced, as e.g., windy weather required the adjustment of the control input to avoid battery depletion.
+Computations might also significantly impact the battery.
 Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
@@
   \end{equation}
-  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
+  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
 \end{defn}
@@
 \end{equation}
-delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (gray area in Figure~\ref{fig:overview}), being the TEE satisfied for all the approaching points $\varphi_i\rightarrow\mathbb{C}_i$.
+delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$, being the TEE satisfied for all the approaching points $\varphi_i\rightarrow\mathbb{C}_i$ (gray area in Figure~\ref{fig:overview}).
 
@@
 \end{equation}
-where $\nabla\varPhi\in\mathbb{R}^2$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+where $\nabla\varPhi$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind $w\in\mathbb{R}$.
@@
      &    &       & A_r 
-  \end{array}\right],\,A_i=\begin{bmatrix}0 & \frac{i}{\xi} \\ -\frac{i^2}{\xi^2} & 0\end{bmatrix},\\
+  \end{array}\right],\,A_i=\begin{bmatrix}0 & i/\xi \\ -i^2/\xi^2 & 0\end{bmatrix},\\
   C&=\left[\begin{array}{cccccc}
@@
 where $\mathbf{s}_k,g(\mathbf{s}_k)$ are defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^n$ is the control given $n:=1+\rho$, and $B\in\mathbb{R}^{m\times n}$.
-Moreover, the first item is one, while the others on the first row are gain factors $\omega_{i}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
+Moreover, the first item of $B$ is one, while the others on the first row are gain factors $\omega_{i}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
 
@@
 
-The energy evolution analysis necessitates the following realistic assumption.
+Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
+The energy due to the adjustments is merely a linear combination of the gain factor $\omega$ and the adjustment.
+Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the state.
+For instance, a decrement in the adjustment radius of the circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
+
+The energy consumption modeling of the mission necessitates the following realistic assumption.
 \begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
@@
 
-Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
-The energy due to the adjustments is merely a linear combination of the gain factor $\omega$ and the adjustment.
-Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the state.
-For instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
-
 \subsection{Energy evolution due to computations}
@@
 
-The energy cost of the computations (set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds a computational energy consumption model.
-Specifically, the tool builds a linear interpolation, one per each task.
+The energy cost of the computations (set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
+The tool measures software configurations empirically and builds a computational energy consumption model: a linear interpolation, one per each task.
 It requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters.
 
-The mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
+Specifically, the mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
 These tasks are simulated by ROS nodes $\Psi(\mathbf{s}_i):=\left(\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\right)$, in fact they input the desired and output the actual computations
@@
 
-Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a set of control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
@@
   \begin{equation}\begin{split}
-    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi_i(\mathbf{p}_{k-1},\mathbf{c}_{i-1}),\Psi(\mathbf{s_{i-1}}))\in\mathcal{M}_{i-1}\\
-    &\Longrightarrow(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{i}),\Psi(\mathbf{s}_{i}))\in\mathcal{M}_{i}\}.
+    \mathbf{u}^a_{k}=\{&(\mathbf{c}_{k},\mathbf{s}_{k})\mid\,\exists n\in\mathbb{Z}_{>0},\\&(\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n}))\in\mathcal{M}_{i-1}\\
+    &\Longrightarrow(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{i}\}.
   \end{split}\end{equation}

### 2020-10-25 figures/energy/generate.sh
fixed overview figure, and added some results figures

@@ -1,0 +1,28 @@
+#!/bin/bash
+rm generated/*
+
+gnuplot -e "
+    set datafile separator ',';
+    set term svg size 320,320;
+    set border linewidth 1.5;
+    set style line 11 lc rgb '#808080' lt 1;
+    set border 3 back ls 11;
+    set tics nomirror out scale 0.75;
+    set style line 12 lc rgb'#808080' lt 0 lw 1;
+    set grid back ls 12;
+    unset title;
+    set xrange [0:320];
+    set xtics 60 center offset -.4,.5;
+    set yrange [25:45];
+    set ytics 5 center offset -1.6,0;
+    set grid ytics,xtics;
+    set xlabel 'Time (sec)' rotate parallel center offset -1.4,.9;
+    set ylabel 'Power (W)' rotate parallel center offset 1.8,-1.1;
+    set output 'generated/max_qos_tees.svg';
+    plot '../../data/simulation2/max_qos_tees.csv' using 1:2 w l title 'estimated' lc rgb 'black', '' using 1:3 w l title 'data' lc rgb 'red';
+"
+
+
+for i in generated/*.svg; do svg2tikz --figonly $i > $i.tikz; done
+
+sed -i -- 's/y\ (m)/\\rotatebox{90}{y\ (m)}/g' generated/*.tikz

### 2020-10-25 figures/trajectory/generate.sh

@@ -1,0 +1,28 @@
+#!/bin/bash
+rm generated/*
+
+gnuplot -e "
+    set datafile separator ',';
+    set term svg size 320,320;
+    set border linewidth 1.5;
+    set style line 11 lc rgb '#808080' lt 1;
+    set border 3 back ls 11;
+    set tics nomirror out scale 0.75;
+    set style line 12 lc rgb'#808080' lt 0 lw 1;
+    set grid back ls 12;
+    unset title;
+    set xrange [-133:95];
+    set xtics 20*3 center offset -.4,.5;
+    set yrange [-76:231];
+    set ytics 60 center offset -1.6,0;
+    set grid ytics,xtics;
+    set xlabel 'x (m)' rotate parallel center offset -1.4,.9;
+    set ylabel 'y (m)' rotate parallel center offset 1.8,-1.1;
+    set output 'generated/trajectory.svg';
+    plot  '../../data/simulation2/path_sim.csv' using 1:2 w l notitle lc rgb 'black';
+"
+
+
+for i in generated/*.svg; do svg2tikz --figonly $i > $i.tikz; done
+
+sed -i -- 's/y\ (m)/\\rotatebox{90}{y\ (m)}/g' generated/*.tikz

### 2020-10-26 figures/energy/generate.sh
shaping the results

@@ -1,9 +1,8 @@
 #!/bin/bash
-rm generated/*
 
 gnuplot -e "
     set datafile separator ',';
-    set term svg size 320,320;
+    set term qt size 320,220;
     set border linewidth 1.5;
     set style line 11 lc rgb '#808080' lt 1;
     set border 3 back ls 11;
@@ -12,17 +11,48 @@ gnuplot -e "
     set grid back ls 12;
     unset title;
     set xrange [0:320];
-    set xtics 60 center offset -.4,.5;
-    set yrange [25:45];
-    set ytics 5 center offset -1.6,0;
-    set grid ytics,xtics;
-    set xlabel 'Time (sec)' rotate parallel center offset -1.4,.9;
-    set ylabel 'Power (W)' rotate parallel center offset 1.8,-1.1;
-    set output 'generated/max_qos_tees.svg';
-    plot '../../data/simulation2/max_qos_tees.csv' using 1:2 w l title 'estimated' lc rgb 'black', '' using 1:3 w l title 'data' lc rgb 'red';
+    set xtics 60 center offset .6,.5 font 'Times,11';
+    set yrange [29:44];
+    set ytics 3 center offset -.3,0 font 'Times,11';
+    set grid ytics, xtics;
+    set xlabel 'Time (sec)' rotate parallel center offset -1.4,.9 font 'Times,11';
+    set ylabel 'Power (W)' rotate parallel center offset .5,-.1 font 'Times,11';
+    set key font 'Times,8';
+    plot '../../data/simulation2/max_qos_tees.csv' using 1:2 w l title 'Data' lc rgb 'black', '' using 1:3 w l title 'Estimated' lc rgb 'red' lw .5;
+    pause -1;
 "
 
+gnuplot -e "
+    set datafile separator ',';
+    set term qt size 320,220;
+    set border linewidth 1.5;
+    set style line 11 lc rgb '#808080' lt 1;
+    set border 3 back ls 11;
+    set tics nomirror out scale 0.75;
+    set style line 12 lc rgb'#808080' lt 0 lw 1;
+    set grid back ls 12;
+    unset title;
+    set xrange [0:320];
+    set xtics 60 center offset .6,.5 font 'Times,11';
+    set yrange [18000:25000];
+    set ytics ('18' 18000, '20' 20000, '22' 22000, '24' 24000) center offset -.3,0 font 'Times,11';
+    set grid ytics, xtics;
+    set xlabel 'Time (sec)' rotate parallel center offset -1.4,.9 font 'Times,11';
[…]

### 2020-10-26 figures/trajectory/generate.sh

@@ -1,9 +1,8 @@
 #!/bin/bash
-rm generated/*
 
 gnuplot -e "
     set datafile separator ',';
-    set term svg size 320,320;
+    set term qt size 280,280;
     set border linewidth 1.5;
     set style line 11 lc rgb '#808080' lt 1;
     set border 3 back ls 11;
@@ -12,17 +11,16 @@ gnuplot -e "
     set grid back ls 12;
     unset title;
     set xrange [-133:95];
-    set xtics 20*3 center offset -.4,.5;
-    set yrange [-76:231];
-    set ytics 60 center offset -1.6,0;
+    set xtics 20*3 center offset .6,.5 font 'Times,8';
+    set yrange [-76:260];
+    set ytics 60 center offset -.3,0 font 'Times,8';
     set grid ytics,xtics;
-    set xlabel 'x (m)' rotate parallel center offset -1.4,.9;
-    set ylabel 'y (m)' rotate parallel center offset 1.8,-1.1;
-    set output 'generated/trajectory.svg';
-    plot  '../../data/simulation2/path_sim.csv' using 1:2 w l notitle lc rgb 'black';
+    set xlabel 'x (m)' rotate parallel center offset -1.4,.9 font 'Times,11';
+    set ylabel 'y (m)' rotate parallel center offset 1.8,-1.1 font 'Times,11';    set key font 'Times,8';
+    plot  '../../data/simulation2/path_sim.csv' using 1:2 w l title 'Trajectory' lc rgb 'black';
+    pause -1;
 "
 
+#for i in generated/*.svg; do svg2tikz --figonly $i > $i.tikz; done
 
-for i in generated/*.svg; do svg2tikz --figonly $i > $i.tikz; done
-
-sed -i -- 's/y\ (m)/\\rotatebox{90}{y\ (m)}/g' generated/*.tikz
+#sed -i -- 's/y\ (m)/\\rotatebox{90}{y\ (m)}/g' generated/*.tikz

### 2020-10-26 scripts/energy/evolve_sys.m

@@ -1,0 +1,39 @@
+function [y, q] = evolve_sys(A, B, C, u, q0, t)
+%ESTIMATE_KF Discrete-time linear Kalman filter state estimation
+% (see: Dan Simon, Optimal State Estimation [ISBN: 9780471708582], p.128)
+%
+% Inputs:
+%   A:   state matrix
+%   B:   control matrix
+%   C:   output matrix
+%   u:   control vector (must contain one value per each item in t)
+%   t:   time vector
+%
+% Outputs:
+%   y:   instantaneous energy consumption (evolution in time)
+%   q:   state (also evolution in time)
+%
+
+    % predicted instantaneous energy consumption evolution in time
+    y = [];
+    
+    % estimated state evolution in time
+    q = [];
+    
+    for k = t
+        % getting the control at time k
+        u0 = u(k);
+        
+        % prediction
+        q1 = A * q0 + B * u0;
+        y1 = C * q1;
+        
+        y = [y y1];
+        q = [q q1];
+        
+        q0 = q1;
+        
+    end
+
+end
+

### 2020-10-26 figures/energy/generate.sh
just updated the plots

@@ -26,17 +26,16 @@ gnuplot -e "
     set datafile separator ',';
     set term qt size 320,220;
     set border linewidth 1.5;
-    set style line 11 lc rgb '#808080' lt 1;
+    set style line 11 lc rgb '#909090' lt 1;
     set border 3 back ls 11;
     set tics nomirror out scale 0.75;
-    set style line 12 lc rgb'#808080' lt 0 lw 1;
-    set grid back ls 12;
+    set style line 12 lc rgb'#909090' lt 0 lw 1;
+    
     unset title;
     set xrange [0:320];
     set xtics 60 center offset .6,.5 font 'Times,11';
     set yrange [18000:25000];
     set ytics ('18' 18000, '20' 20000, '22' 22000, '24' 24000) center offset -.3,0 font 'Times,11';
-    set grid ytics, xtics;
     set xlabel 'Time (sec)' rotate parallel center offset -1.4,.9 font 'Times,11';
     set ylabel 'Energy (kJ)' rotate parallel center offset .5,-.1 font 'Times,11';
     set key font 'Times,8';

### 2020-10-26 icra-2021.tex
fixed overview figure, and added some results figures
shaping the results
implemented mpc; and some random fixes here and there (well; I need to double check the mpc... But it took long so for now I am happy :D)

@@
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_i:=\{(\varphi_i&(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),\\
+    \mathcal{M}_i:=\{(\varphi_i(&\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),\\
       \psi_1&(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma}))\mid\\
-      \exists\,\,\varphi&_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
-      \psi&_j(s_{i,j})\in\mathbb{S}_{i,j}\,\forall j\in[\sigma]^+\},
+      \exists\,\,&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
+      &\psi_j(s_{i,j})\in\mathbb{S}_{i,j}\,\forall j\in[\sigma]^+\},
   \end{split}\end{equation}
@@
 
-Physically, the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns.
+Physically this means that the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns.
 We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.
@@
 
-Given an initial stage $\mathcal{M}_0$ (TEE $\varphi_0$, tasks $\Psi$, computations $\mathbf{s}_0\in\mathbb{S}_0$, and adaptations $\mathbf{c}_0\in\mathbb{C}_0$), the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given the stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$) for all $i\in[l]$, the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
@@
 and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
+
+\begin{figure*}[h]
+  \centering
+  \hspace{-5ex}\subfigure[.]
+  {
+    \input{\figpath/energy/est_vs_joules.tikz}
+    \label{fig:energy-max}
+  }
+  \subfigure[.]
+  {
+    \input{\figpath/energy/max_qos_tees3.tikz}
+    \label{fig:energy-max}
+  }
+  \caption{.}
+\end{figure*}
+
 \subsection{Deployment algorithm}
@@
 
+In this section
+
+\begin{figure}[h]
+  \centering
+  \input{\figpath/trajectory/trajectory3.tikz}
+  \label{fig:trajectory}
+  \caption{.}
+\end{figure}
+
 *

### 2020-10-26 scripts/energy/MAIN.m

@@ -87,8 +87,8 @@ selection = 0;
             'OP1: fixed max controls, kf no animation', ...
             'OP2: fixed max controls, kf animation', ...
             'OP3: fixed max controls, akf no animation', ...
-            'OP4: fixed max controls, akf no animation, f(ts)=energy' ...
-
+            'OP4: energy in fun. of estimation stop time, same as OP4', ...
+            'OP5: variable controls (computations) same as OP4'
         }, ... 
         'ListSize', [350 150] ...
     );
@@ -203,4 +203,23 @@ if or(selection == 0, indx == 4)
     
     csvwrite([yy(:,1) yy(:,2) ones(size(yy,1),1)*sum(meas)], '../data/simulation2/est_vs_joules.csv');
     
+end
+
+%% Energy sim, OP5
+
+if or(selection == 0, indx == 5)
+
+    OP5;
+
+    disp('[  E> ] Plot of the results');
+    disp('[   ! ] Dependencies: y, meas, gck, ts');
+
+    figure;
+
+    plot(t * ts, meas); %+ gck);
+    hold on;
+    plot(t * ts, y);
+    hold off;
+
+    legend('data', 'observer');
 end

### 2020-10-26 scripts/energy/OP5.m

@@ -1,0 +1,113 @@
+%OP5
+% Simulation of the Energy-Aware Dynamic Mission Planning Algorithm
+%
+
+
+%% Build the model 
+
+fprintf(['[ OP5 ] \n' ...
+         '        \n']);
+disp( '[     ] Build the model');
+fprintf(['[   ! ] Dependencies: mission specification, the value of the\n' ...
+         '        model from the modeling tool, t\n']);
+
+% The former computational model (per each time step all the
+% possibilities)
+ckgck = build_ck(file3, file2, t);
+
+clear file2 file3;
+
+gck = [];
+for i = 1:t(end)
+    cckgck = ckgck(any(ckgck(:, 1) == t(i), 2), end);
+    
+    gck = [gck; cckgck(end)];
+end
+
+%TODO: the former mechanical components of the control
+mk = zeros(size(t, 2), 1);
+
+%% Output MPC
+
+disp('[     ] Output MPC');
+disp('[   ! ] Dependencies: A, B, C, control vector u, sensor data meas, t');
+
+eps = input('[   ? ] Input epsilon: ');
+if isempty(eps)
+    eps = 1/3; % default eps [W tolerance]
+end
+
+N = input('[   ? ] Input the horizon: ');
+if isempty(N)
+    N = 10; % default horizon
+end
+
+% gck is the control input sequnce (OP5 adapts the computations)
+    
+[A, B, C, u, h] = build_model(r, xi, gck, mk); 
+
+% initial guess
+[q0, P0, Q, R] = guess_kf(meas(1), size(A, 1));
+
+% why meas + gck? Including both contributions; the former conputational
+% and mechanical energy from the sensor
+
+cckgck = [];
+
+% MPC tuning matrices
+Rm = eye(size(B,2));
+Qm = eye(size(q0,1));
+Pf = Qm;
+
+y = [];
+q = [];
+ua = [];
+for k=1:t(end)
+   
+    % line 28
+    cckgck = ckgck(any(ckgck(:, 1) == k, 2), end);
+        
+    % iteration over all the possible controls
+    v = [];
+    for current_gck=transpose(cckgck)
+        vv = 0;    
+        qk = q0;
+        
+        vv = vv + .5*(transpose(qk)*Qm*qk+current_gck*current_gck);
+        
+        for l=1:N-1
+            for all_gck=transpose(ckgck(any(ckgck(:, 1) == k + l, 2), end))
+                all_gck = [all_gck; 0]; % simulate also the adaptations
[…]

### 2020-10-26 scripts/energy/estimate_kf.m

@@ -1,4 +1,4 @@
-function [y, q] = estimate_kf(A, B, C, u, q0, P0, Q, R, meas, t, eps)
+function [y, q, P1] = estimate_kf(A, B, C, u, q0, P0, Q, R, meas, t, eps)
 %ESTIMATE_KF Discrete-time linear Kalman filter state estimation
 % (see: Dan Simon, Optimal State Estimation [ISBN: 9780471708582], p.128)
 %
@@ -19,8 +19,11 @@ function [y, q] = estimate_kf(A, B, C, u, q0, P0, Q, R, meas, t, eps)
 % Outputs:
 %   y:   instantaneous energy consumption (evolution in time)
 %   q:   state (also evolution in time)
+%   P1:  variance of the guessed estimate at next step
 %
-    
+
+    P1 = [];
+
     % predicted instantaneous energy consumption evolution in time
     y = [];
     

### 2020-10-31 icra-2021.tex
implementing Ulrik's comments

@@
     year={2019},
-    publisher={Springer}
+    publisher={Springer},
+    url={https://adamseew.bitbucket.io/short/coarse2019}
   }
@@
     year={2019},
-    organization={ACM}
+    organization={ACM},
+    url={https://adamseew.bitbucket.io/short/component2019}
   }
@@
   }
-
+  @inproceedings{zamanakos2020energy,
+    title={Energy-Aware Design of Vision-Based Autonomous Tracking and Landing of a UAV}, 
+    author={Zamanakos, Georgios and Seewald, Adam and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
+    booktitle={2020 4th IEEE International Conference on Robotic Computing (IRC)},
+    pages={to appear},
+    year={2020},
+    organization={IEEE},
+    url={https://adamseew.bitbucket.io/short/energy2020}
+  }
 \end{filecontents}
@@
 }
-
 \begin{document}
@@
 Planning a mission for unmanned aerial vehicles (UAVs) operating outdoors is a challenging task.
-Scenarios such as precision agriculture, search and rescue, and surveillance require advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying.
-Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}.
+Scenarios such as precision agriculture, search and rescue, and surveillance require advanced levels of autonomy but have limited energy budgets.
+A typical example would be a UAV used to inform its ground-based actors of patterns detected while flying.
+Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
-The algorithm attempts to combine and generalize some of the past body of knowledge on the mobile robot planning problem, and highlights the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
+The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems, and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
 
-Planning algorithms for mobile robots broadly are not a new concept, in that they are correlated to such topics as trajectory generation and path planning.
-Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to few robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the systems' energy being influenced by the computations over bare motion~\cite{mei2005case}.
-For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Furthermore, past mission planning algorithms--which include a broader concept of a mission being a set of tasks along with a motion plan--also focus on the trajectory~\cite{mei2005case,mei2006deployment}, and apply to few robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-Yet, computations of such systems are only expected to increase in the near future.
+Planning algorithms for mobile robots are a related to topics such as trajectory generation and path planning.
+Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}, but in practice apply to few robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by on-board computations and not only bare motion~\cite{mei2005case}.
+For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+Mission planning algorithms, which includes a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to few robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Given the availability of powerful GPU-equipped mobile hardware, the use of on-board computations is expected to increase in the near future.
+% todo cite
+% todo add paragraph telling the algo (title)
 
-The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the computations, and the trajectory-explicit equations (TEEs) adjustments.
-In the remainder of the paper, we strictly adopt the following notation.
-We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and to the current trajectory as TEE.
-Our goal is a mission extension by optimizing both computations and adjustments as the UAV flies and its batteries drain.
-First, the algorithm optimizes computations requiring the UAV to include robot operating system (ROS) nodes.
-Then, it optimizes adjustments--a way to alter the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
+The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the on-board computations, and the trajectory-explicit equations (TEEs) adjustments.
+In the remainder of the paper, we adopt the following notation.
+We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.
+Our goal is to complete the mission with highest possible computations and adjustments as the UAV flies and its batteries drain.
+The algorithm both optimizes computations in the form of robot operating system (ROS) nodes, and it optimizes adjustments--a way to alter the trajectory--guiding the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
 It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
-The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather.
-It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to approximately evolve also periodically--and the uncertainty with a state estimator.
-It output the control input (computations and adjustments) using robust output feedback model predictive control (MPC).
+Periodicity is often observed, e.g., when the UAV is flying in repetitive patterns for a monitoring or search and rescue mission.
+Uncertainty accounts for the environmental interference, e.g., a fixed-wing UAV drifting due to windy weather.
+The algorithm addresses the periodicity by modeling the energy with Fourier analysis: the mission is periodic, so we expect the energy to also approximately evolve periodically.
+The uncertainty is addressed with a state estimator.
+The algorithm outputs the control input (adjustments and computations) using output model predictive control (MPC).
 
-In the spirit of reducing costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+In the spirit of reducing costs and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
 Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
-The mission consists of a UAV flying in circles and lines covering a polygon, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics.
-The algorithm plans the mission controlling the processing rate and the radius of the circles, affecting the distance between the lines.
+The mission is structured as follows.
+Trajectory-wise, the UAV flies in circles and lines covering a polygon.
+Computationally-wise, it detects obstacles using a convolutional neural network (CNN), and informs grounded mobile robots employed for harvesting.
+The algorithm plans the mission controlling the processing rate and the radius of the circles (affecting the distance between the lines).
 Figure~\ref{fig:overview} shows an initial slice of such a mission.
-The UAV first heads to a circular TEE with a given radius, which is later reduced, as e.g., windy weather required the adjustment of the control input to avoid battery depletion.
-Computations might also significantly impact the battery.
-Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.
+The UAV first heads to a circular TEE with a given radius, which is later reduced as, e.g., windy weather requires the adjustment of the control input to avoid battery depletion.
+Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations (see Section~\ref{sec:experimental}).
 
@@
 
-The mission consists of different stages. At each stage the robot must follow a path and do some tasks.
+We assume that the mission consists of different stages. At each stage the robot must follow a path and do some tasks.
 
-Let the path at stage $i$ be characterized by a generic continuous twice differentiable TEE $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ and the tasks by $\psi_1,\dots,\psi_{\sigma}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ functions.
-Moreover, let $[a]$ be the set $\{0,1,\dots,a\}$, $[a]^+$ the set $\{0\}/[a]$, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a lookup table.
+Let the path at stage $i$ be characterized by a generic continuous twice differentiable TEE $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ and the tasks by functions $\psi_1,\dots,\psi_{\sigma}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$.
+Moreover, let $[a]$ be the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a lookup table.
 
 \begin{defn}[Stage and mission]\label{def:mission}
-  A \emph{stage} $i$ at time instant $k$ is defined as the ordered list
+  A \emph{stage} $\mathcal{M}_i$ at time instant $k$ of a mission $\mathcal{M}$ is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_i:=\{(\varphi_i(&\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),\\
-      \psi_1&(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma}))\mid\\
-      \exists\,\,&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
+    \mathcal{M}_i:=\{\langle\varphi_i(\mathbf{p}_k,c&_{i,1},\dots,c_{i,\rho}),\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle\\\mid
+      \exists\,\,\mathbf{p}_k,\,&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
       &\psi_j(s_{i,j})\in\mathbb{S}_{i,j}\,\forall j\in[\sigma]^+\},
@@
   where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{i,j}:=[\underline{s}_{i,j},\overline{s}_{i,j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th task QoS set.
-The parameters of the TEE $\varphi_i$ are defined in Subsection~\ref{sec:model}, of the tasks $\psi_1,\dots,\psi_\sigma$ in~\ref{sec:computations-model}.
+$\mathbf{p}_k:=(x,y)$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
+some inertial navigation frame $\mathcal{O}_W$.
+The parameters of the TEE $\varphi_i$ are the point and the adjustments (Subsection~\ref{sec:model}).
+The parameters of the tasks $\psi_1,\dots,\psi_\sigma$ are the computations (Subsection~\ref{sec:computations-model}).
 
-  The \emph{mission} is the union of all the stages, along with a function $\lambda:\mathbb{R}^2\rightarrow\mathcal{M}_i$ which maps a point $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
-some inertial navigation frame $\mathcal{O}_W$ to a specific stage.
-For simplicity the system is sampled discrete-time and $l$ is the total number of stages
-  \begin{equation}
-    \mathcal{M}:=(\lambda(\mathbf{p}),\bigcup_{i\in[l]}{\mathcal{M}_i}),
-  \end{equation}
-  the algorithm inputs $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
+  The \emph{mission} is then $\mathcal{M}:\mathbb{R}^2\rightarrow\mathcal{M}_i$ a function which maps the point $\mathbf{p}_k$ to a specific stage $\mathcal{M}_i$.
+
+  For simplicity the system is sampled in discrete time.
+The algorithm takes as input $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
 \end{defn}
@@
 The state is the UAV's position in space and the energy coefficients in time.
-Despite we show a linear relation between the instantaneous energy consumption and the energy coefficients (Theorem~\ref{thm:state-vs-energy}), the two are different.
-We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
+We show a linear relation between the instantaneous energy consumption and the energy coefficients in Theorem~\ref{thm:state-vs-energy}, but the two are different.
+We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
@@
 \end{equation}
-delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$, being the TEE satisfied for all the approaching points $\varphi_i\rightarrow\mathbb{C}_i$ (gray area in Figure~\ref{fig:overview}).
+delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
 
-The algorithm uses the concept to select the adjustments s.t.
-$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest energy value.
-It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the vector field of $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, deriving the direction to follow--the desired velocity vector
+The algorithm uses the set from Equation~\text{eq:area} to select the optimal adjustments $\mathbf{c}_i^0$ s.t.
+$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption under the battery constraints.
+It guides the UAV to the new position $\mathbf{p}_{k+1}$ computing the vector field of the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$.
+It uses the vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$ to derive the direction to follow in the form of velocity vector
 \begin{equation}\label{eq:pd}
@@
 \end{equation}
-where $\nabla\varPhi$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind $w\in\mathbb{R}$.
+where $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:overview}).
 
-The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^m$ derived from Fourier analysis (the meaning of $m$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^m$ derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and decomposes the evolution in energy due to the trajectory and computations.
+This approach is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
@@
 
-Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy consumption modeling of the mission
+Let us consider a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy consumption modeling of the mission
 \begin{equation}\label{eq:fourier}
@@
 \end{equation}
-where $\xi\in\mathbb{R}$ is the characteristic time, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the modeled instantaneous energy consumption, $\xi\in\mathbb{R}$ is the fundamental frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
-Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ accounting for the unknown state and output is absent.
+Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero).
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
-\begin{equation}\label{eq:state-perf}\begin{cases}
-  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
-  y_k&=C\mathbf{q}_k+v_k
-\end{cases},\end{equation}
+\begin{equation}\label{eq:state-perf}\begin{split}
+  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k,\\
+  y_k&=C\mathbf{q}_k+v_k,
+\end{split}\end{equation}
 where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ mimics the original Fourier series coefficients
@@
 \end{split}\end{equation}
-where $\mathbf{q}_k\in\mathbb{R}^m$ given $m:=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the first value is one, $A_i$ is later on the diagonal, and zero in the remainder.
+where $\mathbf{q}_k\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+In matrix $A$, the top left entry is one, the diagonal entries are defined by $A_1,\dots,A_r$, and zero the remaining entries are zero.
 
-Suppose at time instant $k$ the mission reached stage $i$ and the control input is $\mathbf{u}_k^a=(\mathbf{c}_k,\mathbf{s}_k)$. The control along with the input matrix
+Suppose at time instant $k$ the mission reached stage $i$ and the control input is $\mathbf{u}_k^a:=\langle\mathbf{c}_k,\mathbf{s}_k\rangle$. The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}  
@@
 \end{split}\end{equation}
-where $\mathbf{s}_k,g(\mathbf{s}_k)$ are defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^n$ is the control given $n:=1+\rho$, and $B\in\mathbb{R}^{m\times n}$.
-Moreover, the first item of $B$ is one, while the others on the first row are gain factors $\omega_{i}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
+where $\mathbf{s}_k,g(\mathbf{s}_k)$ are the computations and the instantaneous computational energy consumption (Subsection~\ref{sec:computations-model}), $\mathbf{u}_k\in\mathbb{R}^n$ is the control given $n=1+\rho$, and $B\in\mathbb{R}^{m\times n}$.
+Moreover, the top-left entry of $B$ is one, while the others on the first row are gain factors $\Omega_{i}:=\{\omega_{i,1},\dots, \omega_{i,\rho}\}\in\mathbb{R}^\rho$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
 
-Note that the control input $\mathbf{u}_k^a:=(\mathbf{c}_{k},\mathbf{s}_{k})$--an output of the algorithm--differs from the nominal control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.
+Equation~(\ref{eq:state-control}) accounts for the energy due to the adjustments and computations.
+The difference $g(\mathbf{s}_k)-g(\mathbf{s}_{k-1})$ quantifies the change in the instantaneous computational energy consumption.
+Similarly, $\Omega_i(\mathbf{c}_k-\mathbf{c}_{k-1})$ quantifies the change in the instantaneous trajectory energy consumption.
+For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the adjustment radius of the circle $c_{0,1}$ adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption $\omega_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
 
-Equation~(\ref{eq:state-control}) accounts for the energy due to the computations.
-The energy due to the adjustments is merely a linear combination of the gain factor $\omega$ and the adjustment.
-Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the state.
-For instance, a decrement in the adjustment radius of the circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.
+Note from Equation~(\ref{eq:state-control}) that the control input $\mathbf{u}_k^a$ differs from the nominal control $\mathbf{u}_k$ in Equation~(\ref{eq:state-perf}).
+The first is an output of the algorithm.
+The second is a function that maps two consecutive control inputs to the difference in instantaneous energy consumption $\mathbf{u}_k:\mathbb{R}^{2\rho}\times\mathbb{Z}_{\geq 0}^{2\sigma}\rightarrow\mathbb{R}^{\rho+1}$.
 
-The energy consumption modeling of the mission necessitates the following realistic assumption.
+The energy consumption modeling of the mission necessitates the following assumption.
 \begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
-Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}_{\geq 0}$
+Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
 \begin{equation}
-  \abs{y_{k}-y_{k+n}}= e\,\,\,\forall k\in[k_1,k_2].
+  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2].
 \end{equation}
@@
 
-Physically this means that the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns.
-We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.
+Physically this means that the time evolution of the instantaneous energy consumption is assumed to be approximately periodic.
 
@@
 
-The energy cost of the computations (set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
-The tool measures software configurations empirically and builds a computational energy consumption model: a linear interpolation, one per each task.
-It requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters.
+The energy cost of the computations (the set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
+The tool measures the instantaneous computational energy consumption of software components within the QoS sets.
+It builds an energy model: a linear interpolation, one per each task.
+In a ROS based system, it requires the user to implement one or more ROS nodes changing the computational load by node-specific ROS parameters.
+The approach has been tested in simulation in our previous work~\cite{zamanakos2020energy}.
 
 Specifically, the mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
-These tasks are simulated by ROS nodes $\Psi(\mathbf{s}_i):=\left(\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\right)$, in fact they input the desired and output the actual computations
+These tasks are implemented by software components (such as ROS nodes) $\Psi(\mathbf{s}_i):=\langle\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle$.
+They input the desired and output the actual computations
 \begin{equation}\label{eq:qos-def}
-  \mathbf{s}_i:=\left\{s_{i,1},\dots ,s_{i,\sigma}\mid \psi_j(s_{i,j})\in\mathbb{S}_{i}\,\forall j\in[\sigma]^+\right\},
+  \mathbf{s}_i:=\left\{\langle s_{i,1},\dots ,s_{i,\sigma}\rangle\mid \psi_j(s_{i,j})\in\mathbb{S}_{i}\,\forall j\in[\sigma]^+\right\},
 \end{equation}
@@
 
-Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the actual instantaneous computational energy consumption value obtained interrogating \powprof{}
+For instance, if the task $\psi_1$ is a CNN object detector, $s_{1,1}$ corresponds to the computation frames-per-second (fps) rate changing the detection frequency.
+The algorithm output the control input which contains the desired fps rate $s_{1,1}\in\mathbb{S}_{1,1}$.
+The task $\psi_1(s_{1,1})$ output the actual fps rate $s_{k,1}$ which might differ from the desired one (e.g., the CNN object detector might not be able to reach a high fps rate with the current computational resources).
+
+Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the actual instantaneous computational energy consumption value obtained using \powprof{}
 \begin{equation}\label{eq:energy-comp}\begin{split}
@@
 
-Given the stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$) for all $i\in[l]$, the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given $l$ stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$) for all $i\in[l]$, the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
@@
   \begin{equation}\begin{split}
-    \mathbf{u}^a_{k}=\{&(\mathbf{c}_{k},\mathbf{s}_{k})\mid\,\exists n\in\mathbb{Z}_{>0},\\&(\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n}))\in\mathcal{M}_{i-1}\\
-    &\Longrightarrow(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{i}\}.
+    \mathbf{u}^a_{k}=\{&\langle\mathbf{c}_{k},\mathbf{s}_{k}\rangle\mid\,\exists n\in\mathbb{Z}_{>0},\\&\langle\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n})\rangle\in\mathcal{M}_{i-1}\\
+    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k})\rangle\in\mathcal{M}_{i}\}.
   \end{split}\end{equation}

### 2020-11-05 scripts/MAIN.m
updated the simulator

@@ -19,6 +19,7 @@ fprintf(['\t\t+---------------------------------------------+\n' ...
     (   'PromptString', {'Select a simulation'}, ...
         'SelectionMode', 'single', 'ListString', ...
         { ...
+            'Simulator', ...
             'Energy', ...
             'Position ', ...
         }, ... 
@@ -26,6 +27,14 @@ fprintf(['\t\t+---------------------------------------------+\n' ...
     );
 
 if indx == 1
+        
+    fprintf(['\t\t             +---------------+\n' ...
+             '\t\t             | The simulator |\n' ...
+             '\t\t             +---------------+\n\n']);%21
+    
+    disp('[>    ] Invoking the simulator');
+    SIM;    
+elseif indx == 2
     
     fprintf(['\t\t             +-------------------+\n' ...
              '\t\t             | Energy simulation |\n' ...
@@ -33,8 +42,9 @@ if indx == 1
     
     disp('[>    ] Invoking energy sim');
     cd energy;
-    MAIN;    
-elseif indx == 2
+    MAIN;
+    cd ..;
+elseif indx == 3
     
     fprintf(['\t\t            +---------------------+\n' ...
              '\t\t            | Position simulation |\n' ...
@@ -43,8 +53,8 @@ elseif indx == 2
     disp('[>    ] Invoking position sim');
     cd position;
     MAIN;
+    cd ..;
 end
 
-cd ..;
 disp('[>    ] Sim done');
  

### 2020-11-05 scripts/energy/output_mpc.m

@@ -1,5 +1,5 @@
-function [y, q, ua, meas, P1, q0] = output_mpc(A, B, C, ck, q0, P0, Q, R, meas, ...
-    Rm, Qm, Pf, t, eps, N)
+function [y, q, ua, meas, P1, q0] = output_mpc(A, B, C, ck, q0, P0, Q, ...
+    R, meas, Rm, Qm, Pf, t, eps, N)
 %OUTPUT_MPC Output MPC algorithm (see MPC Rawlings and Mayne, 2009, p. 382)
 %
 % Inputs:

### 2020-11-05 scripts/simulate.m

@@ -82,12 +82,15 @@ function [k pos pow est ua] = simulate(varphi, trigger, trajparams, mpcparams, s
     % direction is constant
     windx = .1 * windspeed * cosd(winddir);
     windy = .1 * windspeed * sind(winddir);
+    
+    y = []; % model output
+    q = []; % model state
 
     for varphii = transpose(varphi) % per each TEE
         
         varphii = split(varphii, ";");
         
-        fprintf('varphi_%d((%d,%d)):=%s\n', i, nowpos(1), nowpos(2), varphii(3));
+        fprintf('varphi%d((%d,%d)):=%s\n', i, nowpos(1), nowpos(2), varphii(3));
         
         E = [0 -1; 1 0];
         if contains(varphii(2), '270')
@@ -163,10 +166,54 @@ function [k pos pow est ua] = simulate(varphi, trigger, trajparams, mpcparams, s
                 %[~, ~, ~, yy, P1, q0] = output_mpc(A, B, C, si, q0, P0, ...
                 %    Q, R, pow, ...
                 %    Rm, Qm, Pf, k/10, eps, N);
+                
+                %y = []; % instantaneous energy consumption (evolution in 
+                        % time)
+                %q = []; % state (also evolution in time)
+                %ua = []; % control input sequence
+                
+                % iteration over all the possible controls
+                % this instruction corresponds to argmax in algorithm (line
+                % 3)
+                %v = [];
+                %for current_si = transpose(si(any(si(:, 1) == i, 2), end))
+                %    qk = q0;
+                    
+                %    vv = .5 * (trasnpose(qk) * Qm * qk + transpose(current_si) * Rm * current_si);
+                    
+                    % this instruction corresponds to the sum 
+                %    for l = 1 : N - 1
+                        
+                %    end
+                %end
+                    
+                % first we need to interate over all the ppp
             
                 % plotting the estimated energy
                 %subplot(2,2,4);
                 %plot(linspace(0, k/10, size(yy, 1)), yy(:, 1))
+                
+                % for now I do just the estimation with the model and later
+                % implement the rest of the MPC
+                yy = [];
+                P1 = [];
+                
+                [yy, qq0, P1] = estimate_kf(A, B, C, u, q0, P0, Q, R, ...
+                    pow(k), k, eps);
+                
+                y = [y; yy];
+                q0 = qq0;
+        
+                if ~isempty(P1) % if it's empty, no KF just evolutin (<= epsilon)
+                    P0 = P1;
[…]

### 2020-11-06 icra-2021.tex
finally implemented all the Ulrik's comments

@@
     author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    booktitle={2020 4th IEEE International Conference on Robotic Computing (IRC)},
-    pages={to appear},
+    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
+    pages={135--142},
     year={2020},
@@
     author={Zamanakos, Georgios and Seewald, Adam and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    booktitle={2020 4th IEEE International Conference on Robotic Computing (IRC)},
-    pages={to appear},
+    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
+    pages={294--297},
     year={2020},
@@
 The UAV heads to $\varphi_0$ initially, using the desired velocity vector $\dot{\mathbf{p}}_d$.
-It later heads to $\varphi_0^-$ reducing the radius $c_{0,1}$ to satisfy the battery constraints (indeed the energy coefficients $\mathbf{q}_{k_2}$ evolution is higher then $\mathbf{q}_{k_3}$).
+It later heads to $\varphi_0^-$ reducing the radius $c_{0,1}$ to satisfy the battery constraints.
 The UAV then converges to $\varphi_1$ in stage $\mathcal{M}_1$, $\varphi_2$ in stage $\mathcal{M}_2$, and so on (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
@@
 
-Planning a mission for unmanned aerial vehicles (UAVs) operating outdoors is a challenging task.
+Planning a dynamic mission for unmanned aerial vehicles (UAVs) operating outdoors is a challenging task.
 Scenarios such as precision agriculture, search and rescue, and surveillance require advanced levels of autonomy but have limited energy budgets.
-A typical example would be a UAV used to inform its ground-based actors of patterns detected while flying.
-Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
+A typical example of a mission with these limitations is a UAV flying a trajectory and performing some on-board computations.
+For instance, the UAV might detect some patterns and inform other, ground-based, actors.
+Planning a dynamic mission for such UAV involves finding optimal tradeoffs between the trajectory and computations.
+However, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
@@
 
-Planning algorithms for mobile robots are a related to topics such as trajectory generation and path planning.
-Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}, but in practice apply to few robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by on-board computations and not only bare motion~\cite{mei2005case}.
+Planning algorithms for mobile robots are related to topics such as trajectory generation and path planning.
+Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a small number of robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by computations and not only bare motion~\cite{mei2005case}.
 For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Mission planning algorithms, which includes a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to few robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-Given the availability of powerful GPU-equipped mobile hardware, the use of on-board computations is expected to increase in the near future.
-% todo cite
-% todo add paragraph telling the algo (title)
+Mission planning algorithms, which include a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Given the availability of powerful GPU-equipped mobile hardware, the use of computations is expected to increase in the near future.
 
-The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the on-board computations, and the trajectory-explicit equations (TEEs) adjustments.
+The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and the following mission specification parameters.
+The Quality of Service (QoS) computations parameters are relative to the tasks, and trajectory-explicit equations (TEEs) adjustments parameters to the path.
+The proposed algorithm replans the initial mission plan dynamically as the energy budget changes due to atmospheric interferences.
 In the remainder of the paper, we adopt the following notation.
 We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.
-Our goal is to complete the mission with highest possible computations and adjustments as the UAV flies and its batteries drain.
+Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain.
 The algorithm both optimizes computations in the form of robot operating system (ROS) nodes, and it optimizes adjustments--a way to alter the trajectory--guiding the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
 It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
-Periodicity is often observed, e.g., when the UAV is flying in repetitive patterns for a monitoring or search and rescue mission.
-Uncertainty accounts for the environmental interference, e.g., a fixed-wing UAV drifting due to windy weather.
+Periodicity is often observed, e.g., when the UAV is flying in repetitive patterns for monitoring or search and rescue scenarios.
+Uncertainty accounts for the atmospheric interference, e.g., a fixed-wing UAV drifting due to windy weather.
 The algorithm addresses the periodicity by modeling the energy with Fourier analysis: the mission is periodic, so we expect the energy to also approximately evolve periodically.
@@
 
-We assume that the mission consists of different stages. At each stage the robot must follow a path and do some tasks.
+We assume that the initial mission plan consists of different stages. At each stage the robot must follow a path and do some tasks.
 
@@
 
-The algorithm uses the set from Equation~\text{eq:area} to select the optimal adjustments $\mathbf{c}_i^0$ s.t.
-$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption under the battery constraints.
-It guides the UAV to the new position $\mathbf{p}_{k+1}$ computing the vector field of the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$.
-It uses the vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$ to derive the direction to follow in the form of velocity vector
+The algorithm uses the set from Equation~(\ref{eq:area}) to select the optimal adjustments $\mathbf{c}_i^0$ s.t.
+$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and deriving the direction to follow in the form of velocity vector
 \begin{equation}\label{eq:pd}
@@
 
+\subsection{Energy evolution due to trajectory}
+\label{sec:energy-model}
+
 The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^m$ derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and decomposes the evolution in energy due to the trajectory and computations.
 This approach is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
-
-\subsection{Energy evolution due to trajectory}
-\label{sec:energy-model}
 
@@
 
-Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero).
+\begin{lem}[Fourier series, harmonic oscillator equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero).
 The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
@@
 \end{split}\end{equation}
-where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ mimics the original Fourier series coefficients
+where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
@@
 where $\mathbf{q}_k\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the top left entry is one, the diagonal entries are defined by $A_1,\dots,A_r$, and zero the remaining entries are zero.
+In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.
+\end{lem}
+\begin{proof}
+  *
+\end{proof}
 
@@
 The first is an output of the algorithm.
-The second is a function that maps two consecutive control inputs to the difference in instantaneous energy consumption $\mathbf{u}_k:\mathbb{R}^{2\rho}\times\mathbb{Z}_{\geq 0}^{2\sigma}\rightarrow\mathbb{R}^{\rho+1}$.
+The second is a function that maps two consecutive control inputs to the difference in instantaneous energy consumption $\mathbf{u}_k:\mathbb{R}^{2\rho}\times\mathbb{Z}_{\geq 0}^{2\sigma}\rightarrow\mathbb{R}^{1+\rho}$.
 
@@
 Specifically, the mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
-These tasks are implemented by software components (such as ROS nodes) $\Psi(\mathbf{s}_i):=\langle\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle$.
+These tasks are implemented by software components (such as ROS nodes in a ROS based system) $\Psi(\mathbf{s}_i):=\langle\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle$.
 They input the desired and output the actual computations
@@
 For instance, if the task $\psi_1$ is a CNN object detector, $s_{1,1}$ corresponds to the computation frames-per-second (fps) rate changing the detection frequency.
-The algorithm output the control input which contains the desired fps rate $s_{1,1}\in\mathbb{S}_{1,1}$.
-The task $\psi_1(s_{1,1})$ output the actual fps rate $s_{k,1}$ which might differ from the desired one (e.g., the CNN object detector might not be able to reach a high fps rate with the current computational resources).
+The algorithm outputs the control input which contains the desired fps rate $s_{1,1}\in\mathbb{S}_{1,1}$.
+The task $\psi_1(s_{1,1})$ outputs the actual fps rate $s_{k,1}$ which might differ from the desired one (e.g., the CNN object detector might not be able to reach a high fps rate with the current computational resources).
 
-Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the actual instantaneous computational energy consumption value obtained using \powprof{}
+Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
 \begin{equation}\label{eq:energy-comp}\begin{split}
@@
 \end{split}\end{equation}
-Moreover, $g(\{\emptyset\})=0$.
+Moreover, let $g(\{\emptyset\})$ be zero.
 
@@
 
-Given $l$ stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$) for all $i\in[l]$, the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
+Given $l$ stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$ for all $i\in[l]$), the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
 
@@
 
-We stated earlier the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$. This is generally untrue. Physical UAVs are bounded by strict battery limitations.
+We stated earlier the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
+This is generally untrue.
+Physical UAVs are bounded by strict energy budgets due to battery limitations.
 

### 2020-11-06 scripts/SIM.m

@@ -100,5 +100,5 @@ si2 = build_ck(si, file2, 0:1:i);
 
 figure;
 
-[k pos pow est ua] = simulate(varphi, trigger, strp, strp2, si2, ci);
+simulate(varphi, trigger, strp, strp2, si2, ci);
 

### 2020-11-10 icra-2021.tex
updated the intro

@@
 
-Planning a dynamic mission for unmanned aerial vehicles (UAVs) operating outdoors is a challenging task.
-Scenarios such as precision agriculture, search and rescue, and surveillance require advanced levels of autonomy but have limited energy budgets.
-A typical example of a mission with these limitations is a UAV flying a trajectory and performing some on-board computations.
-For instance, the UAV might detect some patterns and inform other, ground-based, actors.
-Planning a dynamic mission for such UAV involves finding optimal tradeoffs between the trajectory and computations.
-However, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
+Many scenarios involving unmanned aerial vehicles (UAVs) such as precision agriculture, search and rescue, and surveillance require high autonomy but have limited energy budgets.
+A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computations with little human interaction.
+For instance, the UAV might detect ground patterns and inform other ground-based actors.
+Energy-aware dynamic mission planning finds optimal tradeoffs between the trajectory, computations, and energy requirements.
+Current generic planning solutions for UAVs flying outdoors do not plan the mission dynamically, nor are energy-aware.
+They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
-The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems, and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
+The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
 
-Planning algorithms for mobile robots are related to topics such as trajectory generation and path planning.
-Generally, these algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a small number of robots~\cite{kim2005energy}, and focus on optimizing motion control for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by computations and not only bare motion~\cite{mei2005case}.
+Planning algorithms literature for mobile robots is by now large and related to topics such as trajectory generation and path planning.
+Generally, the algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}.
+However, they apply to a small number of robots~\cite{kim2005energy}, and focus on planning the trajectory for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by computations~\cite{mei2005case}.
+Given the availability of powerful GPU-equipped mobile hardware, the use of computations is expected to increase in the near future.
+Mission planning algorithms, which include a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-Mission planning algorithms, which include a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-Given the availability of powerful GPU-equipped mobile hardware, the use of computations is expected to increase in the near future.
 
-The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and the following mission specification parameters.
+The proposed algorithm unfolds as follows.
+The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters.
 The Quality of Service (QoS) computations parameters are relative to the tasks, and trajectory-explicit equations (TEEs) adjustments parameters to the path.
-The proposed algorithm replans the initial mission plan dynamically as the energy budget changes due to atmospheric interferences.
+The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences.
 In the remainder of the paper, we adopt the following notation.
@@
 Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain.
-The algorithm both optimizes computations in the form of robot operating system (ROS) nodes, and it optimizes adjustments--a way to alter the trajectory--guiding the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
+
+The algorithm optimizes computations built as software components that run on a UAV's companion embedded device.
+Then, it optimizes adjustments--a way to alter the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
 It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
-Periodicity is often observed, e.g., when the UAV is flying in repetitive patterns for monitoring or search and rescue scenarios.
-Uncertainty accounts for the atmospheric interference, e.g., a fixed-wing UAV drifting due to windy weather.
-The algorithm addresses the periodicity by modeling the energy with Fourier analysis: the mission is periodic, so we expect the energy to also approximately evolve periodically.
-The uncertainty is addressed with a state estimator.
-The algorithm outputs the control input (adjustments and computations) using output model predictive control (MPC).
+Uncertainty accounts for atmospheric interference.
+E.g., a fixed-wing UAV drifts due to windy weather.
+Periodicity accounts for the mission's repetitive patterns.
+Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., a monitoring or search and rescue mission).
+The algorithm addresses the latter by modeling the energy with Fourier analysis.
+The mission is periodic, so we expect the energy to approximately evolve periodically.
+It addresses uncertainty with a state estimator and outputs the control input (adjustments and computations) using output model predictive control (MPC).
 

### 2020-11-10 icra-2021.tex
updated the text

@@
   }
+  @inproceedings{seewald2020beyond,
+    title={Beyond Traditional Energy Planning: the Weight of Computations in Planetary Exploration},
+    author={Seewald, Adam},
+    booktitle={IROS Workshop on Planetary Exploration Robots: Challenges and Opportunities (PLANROBO20)},
+    year={2020},
+    organization={ETH Zurich, Department of Mechanical and Process Engineering},
+    url={https://adamseew.bitbucket.io/short/beyond2020}
+  }
+  @inproceedings{lindemann2005smoothly,
+    title={Smoothly blending vector fields for global robot navigation},
+    author={Lindemann, Stephen R and LaValle, Steven M},
+    booktitle={Proceedings of the 44th IEEE Conference on Decision and Control},
+    pages={3553--3559},
+    year={2005},
+    organization={IEEE}
+  }
+  @article{gonccalves2010vector,
+    title={Vector fields for robot navigation along time-varying curves in $n$-dimensions},
+    author={Gon{\c{c}}alves, Vin{\'\i}cius M and Pimenta, Luciano CA and Maia, Carlos A and Dutra, Bruno CO and Pereira, Guilherme AS},
+    journal={IEEE Transactions on Robotics},
+    volume={26},
+    number={4},
+    pages={647--659},
+    year={2010},
+    publisher={IEEE}
+  }
+  @inproceedings{panagou2014motion,
+    title={Motion planning and collision avoidance using navigation vector fields},
+    author={Panagou, Dimitra},
+    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
+    pages={2513--2518},
+    year={2014},
+    organization={IEEE}
+  }
+  @inproceedings{zhou2014vector,
+    title={Vector field following for quadrotors using differential flatness},
+    author={Zhou, Dingjiang and Schwager, Mac},
+    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
+    pages={6567--6572},
+    year={2014},
+    organization={IEEE}
+  }
+  @article{kapitanyuk2017guiding,
+    title={A guiding vector-field algorithm for path-following control of nonholonomic mobile robots},
+    author={Kapitanyuk, Yuri A and Proskurnikov, Anton V and Cao, Ming},
+    journal={IEEE Transactions on Control Systems Technology},
+    volume={26},
+    number={4},
+    pages={1372--1385},
+    year={2017},
+    publisher={IEEE}
+  }
 \end{filecontents}
@@
 Energy-aware dynamic mission planning finds optimal tradeoffs between the trajectory, computations, and energy requirements.
-Current generic planning solutions for UAVs flying outdoors do not plan the mission dynamically, nor are energy-aware.
+However, current generic planning solutions for UAVs flying outdoors do not plan the mission dynamically, nor are energy-aware.
 They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
-The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy.
+The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.
 
@@
 
-The proposed algorithm unfolds as follows.
-The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters.
-The Quality of Service (QoS) computations parameters are relative to the tasks, and trajectory-explicit equations (TEEs) adjustments parameters to the path.
+The proposed algorithm contributes to the UAV mission planning problem as follows.
+The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters: the Quality of Service (QoS) computations are relative to the tasks.
+The trajectory-explicit equations (TEEs) adjustments are relative to the path.
+The computations specify a given task's computational level.
+The adjustments are a way to alter the TEE.
 The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences.
+The goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain.
+The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature.
+It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
+The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
 In the remainder of the paper, we adopt the following notation.
 We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.
-Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain.
 
-The algorithm optimizes computations built as software components that run on a UAV's companion embedded device.
-Then, it optimizes adjustments--a way to alter the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory.
-It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}.
-Uncertainty accounts for atmospheric interference.
-E.g., a fixed-wing UAV drifts due to windy weather.
-Periodicity accounts for the mission's repetitive patterns.
-Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., a monitoring or search and rescue mission).
-The algorithm addresses the latter by modeling the energy with Fourier analysis.
+The algorithm contributes to the planning literature further with a periodic energy model that accounts for the uncertainty (atmospheric interference).
+Mission periodicity is usually present due to the mission's repetitive patterns~\cite{seewald2020mechanical}.
+Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
 The mission is periodic, so we expect the energy to approximately evolve periodically.
-It addresses uncertainty with a state estimator and outputs the control input (adjustments and computations) using output model predictive control (MPC).
+The observation applies broadly; repetitive patterns have been observed in scenarios as far as space rovers~\cite{seewald2020beyond}.
+The algorithm addresses the periodicity through Fourier analysis.
+The uncertainty with a state estimator.
+It outputs the control input (adjustments and computations) using output model predictive control (MPC).
 
 In the spirit of reducing costs and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
-Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
+Precision agriculture is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
 The mission is structured as follows.
 Trajectory-wise, the UAV flies in circles and lines covering a polygon.
-Computationally-wise, it detects obstacles using a convolutional neural network (CNN), and informs grounded mobile robots employed for harvesting.
-The algorithm plans the mission controlling the processing rate and the radius of the circles (affecting the distance between the lines).
+Computationally-wise, it detects obstacles using a convolutional neural network (CNN) and informs grounded mobile robots employed for harvesting.
+The algorithm plans the mission; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
 Figure~\ref{fig:overview} shows an initial slice of such a mission.
@@
 The parameters of the tasks $\psi_1,\dots,\psi_\sigma$ are the computations (Subsection~\ref{sec:computations-model}).
+Note that while the TEE can differ for each stage, the tasks remain the same.
+However, the user can inhibit or enable a task varying QoS set.
 

### 2020-11-11 icra-2021.tex
changed a par in intro, this reads better

@@
 
-The proposed algorithm contributes to the UAV mission planning problem as follows.
+Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain. 
+The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature.
+It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
+The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
 The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters: the Quality of Service (QoS) computations are relative to the tasks.
@@
 The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences.
-The goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain.
-The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature.
-It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
-The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
 In the remainder of the paper, we adopt the following notation.

### 2020-11-11 icra-2021.tex
a sketch of a proof but I need to finish

@@
     organization={IEEE},
+    DOI={10.1109/IRC.2020.00028},
     url={https://adamseew.bitbucket.io/short/mechanical2020}
   }
+
   @article{seewald2019coarse,
@@
     publisher={Springer},
+    DOI={10.1007/s10766-019-00645-y},
     url={https://adamseew.bitbucket.io/short/coarse2019}
@@
     organization={ACM},
+    DOI={10.1145/3359061.3362775},
     url={https://adamseew.bitbucket.io/short/component2019}
@@
     organization={IEEE},
+    DOI={10.1109/IRC.2020.00054},
     url={https://adamseew.bitbucket.io/short/energy2020}
   }
+
   @inproceedings{seewald2020beyond,
@@
     booktitle={IROS Workshop on Planetary Exploration Robots: Challenges and Opportunities (PLANROBO20)},
+    pages={3},
     year={2020},
-    organization={ETH Zurich, Department of Mechanical and Process Engineering},
+    publisher={ETH Zurich, Department of Mechanical and Process Engineering},
+    DOI={10.3929/ethz-b-000450120},
     url={https://adamseew.bitbucket.io/short/beyond2020}
@@
     publisher={IEEE}
+  }
+  @book{kuo1967automatic,
+    title={Automatic Control Systems},
+    author={Kuo, B.C.},
+    isbn={9780130549730},
+    lccn={67016388},
+    series={Electrical engineering series},
+    year={1967},
+    publisher={Prentice-Hall}
   }
@@
 
-\begin{lem}[Fourier series, harmonic oscillator equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero).
-The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
+Consider a linear time-invariant (LTI) state-space model
 \begin{equation}\label{eq:state-perf}\begin{split}
@@
 In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.
+
+\begin{lem}[Fourier series, LTI state-space equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero) and the control is zero.
+The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using the LTI state-space model in Equation~(\ref{eq:state-perf})
 \end{lem}
 \begin{proof}
-  *
+  We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form.
+
+  $e^{ik}=\cos{k}+i\sin{k}$ expresses the well-known Euler's formula, therefore $e^{-ik}=\cos{k}-i\sin{k}$.
+We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively.
+This leads
+  \begin{equation}
+    h(k)=a_0+\sum_{n=1}^r{e^{ink}(a_n-ib_n)/2},
+  \end{equation}
+where $i$ is the imaginary unit, and $h(k)\in\mathbb{C}$.
+
+Consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$.
+The solution at time $k$ can be expressed $\mathbf{q}=e^{Ak}\mathbf{q}_0$.
+Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expression derived using a standard textbook~\cite{kuo1967automatic}.
+
 \end{proof}

### 2020-11-12 icra-2021.tex
cleaned and added an appendix

@@
 %% pseudocode package
-%\usepackage{algorithmic}
 \usepackage{algpseudocode}
@@
 \algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
+
+% just lines in pseudocode...
+\usepackage{etoolbox}
+
+\makeatletter
+% start with some helper code
+% This is the vertical rule that is inserted
+\newcommand*{\algrule}[1][\algorithmicindent]{%
+  \makebox[#1][l]{%
+    \hspace*{.2em}% <------------- This is where the rule starts from
+    \vrule height .75\baselineskip depth .25\baselineskip
+  }
+}
+
+\newcount\ALG@printindent@tempcnta
+\def\ALG@printindent{%
+    \ifnum \theALG@nested>0% is there anything to print
+    \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
+    % do nothing
+    \else
+    \unskip
+    % draw a rule for each indent level
+    \ALG@printindent@tempcnta=1
+    \loop
+    \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
+    \advance \ALG@printindent@tempcnta 1
+    \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax
+    \repeat
+    \fi
+    \fi
+}
+% the following line injects our new indent handling code in place of the default spacing
+\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
+\patchcmd{\ALG@doentity}{\item[]\nointerlineskip}{}{}{} % no spurious vertical space
+% end vertical rule patch for algorithmicx
+\makeatother
+
+% for blank page
+
+\usepackage{afterpage}
 
@@
   A mission is valid if for every stage $\mathcal{M}_{i-1},\,i\in[l]^+$ there exist a control input $\mathbf{u}_k^{a}$ that produce the next stage $\mathcal{M}_i$
-  \begin{equation}\begin{split}
+  \begin{equation}\begin{split}\label{eq:mission-valid}
     \mathbf{u}^a_{k}=\{&\langle\mathbf{c}_{k},\mathbf{s}_{k}\rangle\mid\,\exists n\in\mathbb{Z}_{>0},\\&\langle\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n})\rangle\in\mathcal{M}_{i-1}\\
@@
 and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
-
-\begin{figure*}[h]
-  \centering
-  \hspace{-5ex}\subfigure[.]
-  {
-    \input{\figpath/energy/est_vs_joules.tikz}
-    \label{fig:energy-max}
-  }
-  \subfigure[.]
-  {
-    \input{\figpath/energy/max_qos_tees3.tikz}
-    \label{fig:energy-max}
-  }
-  \caption{.}
-\end{figure*}
 
@@
 
-In this section
+Some preliminary results are discussed. Further analysis and re-implementation of the functionality of the algorithm is needed.
 
@@
   \input{\figpath/trajectory/trajectory3.tikz}
+  \caption{The true trajectory. The trajectory is retrieved from the flight log.}
   \label{fig:trajectory}
-  \caption{.}
 \end{figure}
 
-*
+\begin{figure}[h]
+  \centering
+  \input{\figpath/energy/max_qos_tees3.tikz}
+  \caption{Derived energy consumption from the sensors (throttle).
+Red line is the estimated value.
+We use KF for state estimation when the difference between the sensor and model value is $>\varepsilon$.
+Otherwise we evolve the state without noise.}
+  \label{fig:energy-max}
+\end{figure}
 
@@
 
+\leavevmode\thispagestyle{empty}\newpage % just for now
+
 \bibliographystyle{IEEEtran}
 \bibliography{\jobname}
-\vspace{0.1ex}
 
-\newpage
+\leavevmode\thispagestyle{empty}\newpage
+
+\appendices
+\section{Mission Plan Format}
+
+In this appendix we discuss how to specify an initial mission plan with an example of a survey mission.
+The reader can later execute the initial mission plan using the simulator in Appendix~\ref{app:simulator}.
+The initial mission plan is user-defined.
+It specifies the trajectory and tasks of a mission along the QoS and TEEs sets.
+
+Recall that the mission is composed of a set of stages (Subsection~\ref{sec:prob}).
+The plan has a variable number of entries per each stage.
+Suppose we want to plan the mission in Figures~\ref{fig:overview},~\ref{fig:trajectory}.
+The first line
+\begin{algorithmic}[1]
+  \State\textbf{\texttt{0.0003;90;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
+\end{algorithmic}
+corresponds to TEE $\varphi_0(\mathbf{p}_k,c_{0,1}):=(x+45)^2+(y-146)^2-4900+c_{0,1}$ in the initial stage $\mathcal{M}_0$.
+The TEE is a circle.
+The gain is $k_e=3\cdot 10^{-4}$, and the rotation is of ninety degrees--we use the rotation matrix $E$ from Equation~(\ref{eq:pd}).
+Note that line~\ref{code:firstcircle} further specifies the adjustment {\tt\textbf{c1}} of the radius of the circle.
+It corresponds to $c_{0,1}$ in Definition~\ref{def:mission} (zero numerates the stage, one the adjustment).
+
+The following line
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:firstcircle}
+  \State\textbf{\texttt{-sqrt(4900+c1)-45,146}}\label{code:trigger}
+\end{algorithmic}
+specifies the triggering point.
+{\tt\textbf{sqrt}} is the square root.
+The UAV reaches the triggering point within a given $\varepsilon$ (the tolerance), and the algorithm switches to the next stage $\mathcal{M}_1$.
+The algorithm ensures that the overall mission is still valid--Equation~(\ref{eq:mission-valid}).
+It ensure that the TEEs and QoS constraints sets are satisfied with the generated control input.
+Note that the triggering point is in function of the adjustment {\tt\textbf{c1}}.
+This is necessary, an adjustment in one stage affects the overall flight.
+
+Let us assume the system has two tasks.
+One task is the CNN object detection algorithm.
+Its computation $s_{0,1}$ is the fps rate.
+Another task is the variable key-size encryption algorithm.
+Its computation $s_{0,2}$ is the key-size.
+Then in mission plan
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:trigger}
+  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset}
+  \State\textbf{\texttt{[2,10]}}\label{code:qos1set}
+  \State\textbf{\texttt{[32,448]}}\label{code:qos2set}
+\end{algorithmic}
+the line~\ref{code:teeset} corresponds to TEE $\varphi_0$'s set $\mathbb{C}_0=[-3\cdot10^3,0]$.
+The algorithm selects $c_{0,1}$ in $\mathbb{C}_0$.
+The line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,1}$ for the computation $s_{0,1}$.
+The line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,2}$ for the computation $s_{0,2}$.
+The lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of adjustments and computations.
+The lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\mathcal{M}_0$.
+
+Once the UAV reaches the triggering point (line~\ref{code:trigger}) and there are no further lines, the algorithm terminates. If there are further lines, the stage switches to $\mathcal{M}_1$
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:qos2set}
+  \State\textbf{\texttt{0.05;270;x+sqrt(4900+c1)+45}}\label{code:tee2}
+  \State\textbf{\texttt{-sqrt(4900+c1)-45,11}}\label{code:trigger2}
+  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset2}
+  \State\textbf{\texttt{[2,10]}}
+  \State\textbf{\texttt{[32,448]}}\label{code:qosset12}
+\end{algorithmic}
+line~\ref{code:tee2} corresponds to TEE $\varphi_1(\mathbf{p}_k,c_{0,1}):=x+\sqrt{4900+c_{0,1}}+45$, a linear equation that intersects the triggering point (line~\ref{code:trigger}).
+The gain is $k_e=5\cdot 10^{-2}$, and the rotation is opposite to line~\ref{code:firstcircle}.
+The algorithm computes $-E$ from the rotation matrix in Equation~\ref{eq:pd}.
+
+The gain is different from the one used in $\varphi_0$ as different equations require different convergence rate.
+When we follow a circle it is desirable to turn the rotation direction in advance.
+When we follow a straight line, it is more desirable to head to the line and turn the rotation direction while closer to the line.
+We refer to the simulator in Appendix~\ref{app:simulator} for more details on how to tune the gain $k_e$.
+The reader can simulate different rates and see how they affect the flight.
+The rotation is likewise different.
+In fact, the rotation matrix $E$ points upwards in the space and heads to the counter-clockwise direction.
+The rotation matrix $-E$ points downwards and head to the clockwise direction.
+
+The triggering point of the stage $\mathcal{M}_1$ at line~\ref{code:trigger2} also depends on the adjustment {\tt\textbf{c1}}.
+The lines~\ref{code:teeset2}--\ref{code:qosset12} specifies the constraints sets.
+They are expressed the same way as lines~\ref{code:teeset}--\ref{code:qos2set}.
+They have to be specified explicitly for each stage, although they don't change.
+The current implementation of the algorithm has no other means to distinguish different constraints sets.
+
+Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the stage switches to $\mathcal{M}_2$
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:qosset12}
+  \State\textbf{\texttt{0.0003;90;(x+sqrt(4900+c1)-30)\^{}2}}
+  \textbf{\texttt{\hspace*{14ex}+(y-11)\^{}2-5625}}\label{code:tee3}
+  \State\textbf{\texttt{-sqrt(4900+c1)+105,11}}
+  \State\textbf{\texttt{[-3*10\^{}3,0]}}
+  \State\textbf{\texttt{[2,10]}}
+  \State\textbf{\texttt{[32,448]}}\label{code:qosset32}
+\end{algorithmic}
+line~\ref{code:tee3} corresponds to TEE $\varphi_2(\mathbf{p}_k,c_{0,1}):=(x+\sqrt{4900+c_{0,1}}-30)^2+(y-11)^2-5625$, a circle of fixed size that changes the coordinates in function of the adjustment {\tt\textbf{c1}}.
+The rotation is counter-clockwise, alike $\varphi_0$.
+
+The lines
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:qosset32}
+  \State\textbf{\texttt{0.05;90;x+sqrt(4900+c1)-105}}\label{code:tee4}
+  \State\textbf{\texttt{-sqrt(4900+c1)+105,147}}
+  \State\textbf{\texttt{[-3*10\^{}3,0]}}
+  \State\textbf{\texttt{[2,10]}}
+  \State\textbf{\texttt{[32,448]}}\label{code:qosset42}
+  \State\textbf{\texttt{0.0003;90;(x-sqrt(4900+c1)+105)\^{}2}}
+  \textbf{\texttt{\hspace*{14ex}+(y-147)\^{}2-4900+c1}}\label{code:tee5}
+  \State\textbf{\texttt{-3*sqrt(4900+c1)+105,147}}\label{code:triggerlast}
+  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset5}
+\end{algorithmic}
+defines the stages $\mathcal{M}_3$ and $\mathcal{M}_4$.
+Line~\ref{code:tee4} corresponds to TEE $\varphi_3(\mathbf{p}_k,c_{0,1}):=x+\sqrt{4900+c_{0,1}}-105$.
+Line~\ref{code:tee5} corresponds to TEE $\varphi_4(\mathbf{p}_k,c_{0,1}):=(x-\sqrt{4900+c_{0,1}}+105)^2+(y-147)^2-4900+c_{0,1}$.
+
+Note that the survey mission example changes the radius of the circular TEE $\varphi_0$ through the parameter $c_{0,1}$.
+It also changes the radius of $\varphi_4$ in the same way.
+The other TEEs ($\varphi_1,\varphi_2,\varphi_3$) displacement changes the displacement altering the distance between the lines in the survey.
+A familiar pattern from Figure~\ref{fig:overview}.
+For simplicity, we suppose line~\ref{code:triggerlast} describe the last point of the mission.
+We further suppose the user does not desire to process any task in the last stage $\mathcal{M}_4$.
+To inhibit the computations
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:teeset5}
+  \State\textbf{\texttt{[0,0]}}
+  \State\textbf{\texttt{[0,0]}}
+\end{algorithmic}
+
+The following stages are constructed using the same principle.
+Th stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius.
+For $i:=\{1,3,5,\dots\}$ TEE line.
+For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius.
+
+Once the reader is familiar with the initial mission plan format, a further abstraction is needed before we can simulate a mission in Appendix~\ref{app:simulator}.
+The algorithm needs to know how to model the tasks--the software components.
+
+\section{Components Specification Format}
+
+*
+
+\section{Simulator}
+\label{app:simulator}
+
+*
 

### 2020-11-13 icra-2021.tex
fixes to the appendix

@@
 
-In this appendix we discuss how to specify an initial mission plan with an example of a survey mission.
+We discuss how to specify an initial mission plan with an example of a survey mission.
 The reader can later execute the initial mission plan using the simulator in Appendix~\ref{app:simulator}.
-The initial mission plan is user-defined.
+The plan is user-defined.
 It specifies the trajectory and tasks of a mission along the QoS and TEEs sets.
 
-Recall that the mission is composed of a set of stages (Subsection~\ref{sec:prob}).
+Recall that the mission is composed of a set of stages (Section~\ref{sec:prob}).
 The plan has a variable number of entries per each stage.
-Suppose we want to plan the mission in Figures~\ref{fig:overview},~\ref{fig:trajectory}.
+We plan the mission in Figures~\ref{fig:overview},~\ref{fig:trajectory}.
 The first line
@@
 Note that the triggering point is in function of the adjustment {\tt\textbf{c1}}.
-This is necessary, an adjustment in one stage affects the overall flight.
-
-Let us assume the system has two tasks.
+This is necessary; an adjustment in one stage affects the overall flight.
+
+Let us assume the mission has two tasks.
 One task is the CNN object detection algorithm.
@@
 \end{algorithmic}
-the line~\ref{code:teeset} corresponds to TEE $\varphi_0$'s set $\mathbb{C}_0=[-3\cdot10^3,0]$.
-The algorithm selects $c_{0,1}$ in $\mathbb{C}_0$.
-The line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,1}$ for the computation $s_{0,1}$.
-The line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,2}$ for the computation $s_{0,2}$.
-The lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of adjustments and computations.
-The lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\mathcal{M}_0$.
+line~\ref{code:teeset} corresponds to TEE $\varphi_0$'s set $\mathbb{C}_0=[-3\cdot10^3,0]$.
+The algorithm selects $c_{0,1}\in\mathbb{C}_0$.
+Line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,1}$ for the computation $s_{0,1}$.
+Line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,2}$ for the computation $s_{0,2}$.
+Lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of adjustments and computations.
+Lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\mathcal{M}_0$.
 
@@
 The gain is different from the one used in $\varphi_0$ as different equations require different convergence rate.
-When we follow a circle it is desirable to turn the rotation direction in advance.
-When we follow a straight line, it is more desirable to head to the line and turn the rotation direction while closer to the line.
+When we follow a circle it is useful to turn the rotation direction in advance.
+When we follow a straight line, it is preferable to turn the rotation direction closer to the line.
 We refer to the simulator in Appendix~\ref{app:simulator} for more details on how to tune the gain $k_e$.
-The reader can simulate different rates and see how they affect the flight.
+The reader can simulate different rates to see how they affect the flight.
 The rotation is likewise different.
-In fact, the rotation matrix $E$ points upwards in the space and heads to the counter-clockwise direction.
-The rotation matrix $-E$ points downwards and head to the clockwise direction.
+In fact, the rotation matrix $E$ points upwards in the space.
+It guides the UAV in the counter-clockwise direction (see Figure~\ref{fig:overview}; the UAV is traveling counter-clockwise).
+The rotation matrix $-E$ points downwards and guides the UAV in the clockwise direction.
 
 The triggering point of the stage $\mathcal{M}_1$ at line~\ref{code:trigger2} also depends on the adjustment {\tt\textbf{c1}}.
-The lines~\ref{code:teeset2}--\ref{code:qosset12} specifies the constraints sets.
+Lines~\ref{code:teeset2}--\ref{code:qosset12} specifies the constraints sets.
 They are expressed the same way as lines~\ref{code:teeset}--\ref{code:qos2set}.
@@
 
-Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the stage switches to $\mathcal{M}_2$
+Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the algorithm switches the stage to $\mathcal{M}_2$
 \begin{algorithmic}[1]
@@
 It also changes the radius of $\varphi_4$ in the same way.
-The other TEEs ($\varphi_1,\varphi_2,\varphi_3$) displacement changes the displacement altering the distance between the lines in the survey.
+The other TEEs ($\varphi_1,\varphi_2,\varphi_3$) displacement alters the distance between the lines in the survey.
 A familiar pattern from Figure~\ref{fig:overview}.
-For simplicity, we suppose line~\ref{code:triggerlast} describe the last point of the mission.
+For simplicity, we suppose line~\ref{code:triggerlast} describes the last point of the mission.
 We further suppose the user does not desire to process any task in the last stage $\mathcal{M}_4$.
@@
 
-The following stages are constructed using the same principle.
+If there are any following stages in the survey, they are constructed the same way.
 Th stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius.
-For $i:=\{1,3,5,\dots\}$ TEE line.
-For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius.
-
-Once the reader is familiar with the initial mission plan format, a further abstraction is needed before we can simulate a mission in Appendix~\ref{app:simulator}.
-The algorithm needs to know how to model the tasks--the software components.
+For $i:=\{1,3,5,\dots\}$ TEE line with variable displacement.
+For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius and variable displacement.
+
+We need a further abstraction before we can simulate a mission in Appendix~\ref{app:simulator}. The algorithm needs to know how to model the tasks--the software components.
 
@@
 
-*
+We discuss how to execute the initial mission plan and the component specification in the simulator.
+The reader can use the simulator to simulate different environmental interference and their effects on the mission.
+
+The simulator is written in MATLAB and released under MIT license.
+It implements the algorithm (Subsection~\ref{sec:algo}) providing a position $\mathbf{p}_k$ at each time step $k$ and an energy sensor's value $y_k^a$.
+It is derived from empirical data.
+It is an abstraction of the physical observations.
+
+The user is prompted to initialize the trajectory and the algortihm.
 

### 2020-11-16 icra-2021.tex
proofing

@@
   }
+  @article{moler2003nineteen,
+    title={Nineteen dubious ways to compute the exponential of a matrix, twenty-five years later},
+    author={Moler, Cleve and Van Loan, Charles},
+    journal={SIAM review},
+    volume={45},
+    number={1},
+    pages={3--49},
+    year={2003},
+    publisher={SIAM}
+  }
+  @book{ogata2002modern,
+    title={Modern Control Engineering},
+    author={Ogata, K.},
+    isbn={9780130432452},
+    lccn={2001021683},
+    year={2002},
+    publisher={Prentice Hall}
+  }
 \end{filecontents}
@@
      &    &       & A_r 
-  \end{array}\right],\,A_i=\begin{bmatrix}0 & i/\xi \\ -i^2/\xi^2 & 0\end{bmatrix},\\
+  \end{array}\right],\,A_i=\begin{bmatrix}1 & 1 \\ -i^2/\xi^2 & 1\end{bmatrix},\\
   C&=\left[\begin{array}{cccccc}
@@
 \begin{proof}
-  We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form.
-
-  $e^{ik}=\cos{k}+i\sin{k}$ expresses the well-known Euler's formula, therefore $e^{-ik}=\cos{k}-i\sin{k}$.
+We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form using  The well-known Euler's formula $e^{ik}=\cos{k}+i\sin{k}$, therefore $e^{-ik}=\cos{k}-i\sin{k}$~\cite{ogata2002modern}.
 We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively.
@@
   \begin{equation}
-    h(k)=a_0+\sum_{n=1}^r{e^{ink}(a_n-ib_n)/2},
+    h(k)=a_0+\sum_{j=1}^r{e^{ijk}(a_j-ib_j)/2},
   \end{equation}
@@
 
-Consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$.
+Let us consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$.
 The solution at time $k$ can be expressed $\mathbf{q}=e^{Ak}\mathbf{q}_0$.
-Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expression derived using a standard textbook~\cite{kuo1967automatic}.
+Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbook~\cite{kuo1967automatic}.
+To solve the matrix exponential $e^{Ak}$ let us consider the an eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
+
+Matrix decomposition methods works on the similarity transformation of the form $A=VDV^{-1}$.
+The power series definition of $e^{Ak}$ implies $e^{Ak}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}.
+Let us consider the non-singular matrix $V$ whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_1 & \dots & v_m\end{bmatrix}$.
+We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, where $\lambda_j$ is the $j$-th eigenvalue of $A$.
+
+We use the same approach in terms of $\dot{\mathbf{q}}=A\mathbf{q}$.
+Initial condition can be expressed $\mathbf{q}_0=\sum_{j=1}^m{\gamma_jv_j}$, and the generic solution $\mathbf{q}_k=\sum_{j=0}^m{\gamma_je^{\lambda_jk}v_j}$.
+The coefficients $\gamma_j$ are obtained solving $V\mathbf{\gamma}=\mathbf{q}_0$.
+
+Let us further consider the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c=A-I$, where $I$ is a properly sized- identity matrix.
+Let us express the output at time instant $k$ of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state
+\begin{equation}
+  y_k=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_jk}v_j}
+\end{equation}
 

### 2020-11-16 icra-2021.tex
proofing (2)

@@
 \begin{proof}
-We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form using  The well-known Euler's formula $e^{ik}=\cos{k}+i\sin{k}$, therefore $e^{-ik}=\cos{k}-i\sin{k}$~\cite{ogata2002modern}.
+We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form with the well-known Euler's formula $e^{ik}=\cos{k}+i\sin{k}$, $e^{-ik}=\cos{k}-i\sin{k}$~\cite{ogata2002modern}.
 We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively.
 This leads
-  \begin{equation}
+  \begin{equation}\label{eq:proof-complex}
     h(k)=a_0+\sum_{j=1}^r{e^{ijk}(a_j-ib_j)/2},
@@
 
-Let us consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$.
-The solution at time $k$ can be expressed $\mathbf{q}=e^{Ak}\mathbf{q}_0$.
+Let us consider a simplified, continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$, and an initial guess $\mathbf{q}_0$.
+$A_c$ is defined as the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c:=A-I$, where $I$ is a properly sized identity matrix.
+The solution at time $k$ can be expressed $\mathbf{q}=e^{A_ck}\mathbf{q}_0$.
 Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbook~\cite{kuo1967automatic}.
-To solve the matrix exponential $e^{Ak}$ let us consider the an eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
-
-Matrix decomposition methods works on the similarity transformation of the form $A=VDV^{-1}$.
-The power series definition of $e^{Ak}$ implies $e^{Ak}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}.
-Let us consider the non-singular matrix $V$ whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_1 & \dots & v_m\end{bmatrix}$.
-We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, where $\lambda_j$ is the $j$-th eigenvalue of $A$.
-
-We use the same approach in terms of $\dot{\mathbf{q}}=A\mathbf{q}$.
-Initial condition can be expressed $\mathbf{q}_0=\sum_{j=1}^m{\gamma_jv_j}$, and the generic solution $\mathbf{q}_k=\sum_{j=0}^m{\gamma_je^{\lambda_jk}v_j}$.
-The coefficients $\gamma_j$ are obtained solving $V\mathbf{\gamma}=\mathbf{q}_0$.
-
-Let us further consider the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c=A-I$, where $I$ is a properly sized- identity matrix.
+To solve the matrix exponential $e^{A_ck}$, we use the an eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
+
+The method works on the similarity transformation of the form $A_c=VDV^{-1}$.
+The power series definition of $e^{A_ck}$ implies $e^{A_ck}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}.
+We consider the non-singular matrix $V$, whose columns are eigenvectors of $A_c$; $V:=\begin{bmatrix}v_1 & \dots & v_m\end{bmatrix}$.
+We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, where $\lambda_j$ is the $j$-th eigenvalue of $A_c$.
+
+We use the same approach in terms of $\dot{\mathbf{q}}=A_c\mathbf{q}$.
+Initial condition can be expressed $\mathbf{q}_0=\mathbf{\gamma}V$.
+The expression is used to obtain the value of the coefficients of the vector $\mathbf{\gamma}$.
+The generic solution is $\mathbf{q}_k=\mathbf{\gamma}e^{\mathbf{\lambda}k}V$.
+
 Let us express the output at time instant $k$ of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state
-\begin{equation}
-  y_k=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_jk}v_j}
+\begin{equation}\label{eq:proof-output}
+  y_k=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_jk}v_j},
 \end{equation}
+we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
 
@@
 \leavevmode\thispagestyle{empty}\newpage % just for now
+\leavevmode\thispagestyle{empty}\newpage
 

### 2020-11-18 icra-2021.tex
finally proofed (such a relief)

@@
 \documentclass[letterpaper,10pt,conference]{ieeeconf}
-
 \IEEEoverridecommandlockouts
@@
 }
+
 \begin{document}
@@
 
-Let us consider a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy consumption modeling of the mission
+Let us consider a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{Z}_{> 0}$ for the purpose of energy consumption modeling of the mission
 \begin{equation}\label{eq:fourier}
-  h(k)=\sum_{i=0}^{r}{a_i\cos\left({ik/\xi}\right)+b_i\sin{\left({ik/\xi}\right)}},
+  h(k)=a_0/T+(2/T)\sum_{j=1}^{r}{\left(a_j\cos{\omega jk}+b_j\sin{\omega jk}\right)},
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the modeled instantaneous energy consumption, $\xi\in\mathbb{R}$ is the fundamental frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the modeled instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
@@
      &    &       & A_r 
-  \end{array}\right],\,A_i=\begin{bmatrix}1 & 1 \\ -i^2/\xi^2 & 1\end{bmatrix},\\
+  \end{array}\right],\,A_j\begin{bmatrix}1 & \omega j \\ -\omega j & 1\end{bmatrix},\\
   C&=\left[\begin{array}{cccccc}
@@
 \begin{proof}
-We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form with the well-known Euler's formula $e^{ik}=\cos{k}+i\sin{k}$, $e^{-ik}=\cos{k}-i\sin{k}$~\cite{ogata2002modern}.
-We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively.
-This leads
-  \begin{equation}\label{eq:proof-complex}
-    h(k)=a_0+\sum_{j=1}^r{e^{ijk}(a_j-ib_j)/2},
-  \end{equation}
-where $i$ is the imaginary unit, and $h(k)\in\mathbb{C}$.
-
-Let us consider a simplified, continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$, and an initial guess $\mathbf{q}_0$.
+We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
+With $t=\omega jk$, we find the expression for $\cos{\omega jk}=(e^{i\omega jk}+e^{-i\omega jk})/2$ and $\sin{\omega jk}=(e^{i\omega jk}-e^{-i\omega jk})/(2i)$ by substitution of $\sin{\omega jk}$ and $\cos{\omega jk}$ respectively.
+This leads~\cite{kuo1967automatic}
+\begin{equation}\begin{split}\label{eq:proof-complex}
+  h(k)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jk}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jk}(a_j+ib_j)},
+ \end{split}\end{equation}
+where $i$ is the imaginary unit.
+
+Let us consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$, and an initial guess $\mathbf{q}_0$.
 $A_c$ is defined as the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c:=A-I$, where $I$ is a properly sized identity matrix.
 The solution at time $k$ can be expressed $\mathbf{q}=e^{A_ck}\mathbf{q}_0$.
-Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbook~\cite{kuo1967automatic}.
-To solve the matrix exponential $e^{A_ck}$, we use the an eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
-
-The method works on the similarity transformation of the form $A_c=VDV^{-1}$.
+Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
+To solve the matrix exponential $e^{A_ck}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
+
+The method works on the similarity transformation $A_c=VDV^{-1}$.
 The power series definition of $e^{A_ck}$ implies $e^{A_ck}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}.
-We consider the non-singular matrix $V$, whose columns are eigenvectors of $A_c$; $V:=\begin{bmatrix}v_1 & \dots & v_m\end{bmatrix}$.
-We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, where $\lambda_j$ is the $j$-th eigenvalue of $A_c$.
-
-We use the same approach in terms of $\dot{\mathbf{q}}=A_c\mathbf{q}$.
-Initial condition can be expressed $\mathbf{q}_0=\mathbf{\gamma}V$.
-The expression is used to obtain the value of the coefficients of the vector $\mathbf{\gamma}$.
-The generic solution is $\mathbf{q}_k=\mathbf{\gamma}e^{\mathbf{\lambda}k}V$.
-
-Let us express the output at time instant $k$ of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state
+We consider the non-singular matrix $V$, whose columns are eigenvectors of $A_c$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$.
+We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$, where $\lambda_j$ is the $j$-th eigenvalue of $A_c$.
+$\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j-I$.
+We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and thus $AV=VD$.
+
+We apply the approach in terms of the continuous form of Euqation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$.
+Initial guess is expressed $\mathbf{q}_0=\mathbf{\gamma}V$ as a combination of eigenvectors.
+The generic solution is $\mathbf{q}_k=\mathbf{\gamma}e^{Dk}V$.
+
+Let us express the output at time $k$ of the continuous equivalent of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state $y=C\mathbf{q}$
 \begin{equation}\label{eq:proof-output}
-  y_k=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_jk}v_j},
+  y=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_j^0k}v_j^0}+\sum_{j=1}^r{\gamma_je^{\lambda_j^1k}v_j^1},
 \end{equation}
 we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
+
+The matrix $A_c$ is a block diagonal matrix, and we can express its determinant as the multiplication of the determinants of its blocks $\det{(A_c)}=\det{(0)}\times\det{(A_1-I)}\times\cdots\times\det{(A_r-I)}$.
+We proof each block separately.
+
+First, we proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
+We find the eigenvalue from $\det(0-\lambda I)=0$, which is $\lambda_0=0$.
+The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0/T=\gamma_0$.
+
+Then, we proof that all the terms in the sum of both the Equations~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+
+For the first block $A_1-I$, we find the eigenvalues from $\det(A_1-(1+\lambda)I)=0$.
+The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
+The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}-i&1\end{bmatrix}^T$.
+The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$.
+Again, we find the subvector $\gamma_1$ of the vector $\gamma$ such that the equivalences $(1/T)e^{i\omega k}(a_1-ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $(1/T)e^{-i\omega k}(a_1+ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
+They hold for $\gamma_1=(1/T)\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+
+The proof for the remaining $r-1$ blocks is equivalent.
+
+The discretized version $A$ of the matrix $A_c$ can be expressed $A=A_c+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs with $A=e^{A_ck}$}).
+We thus conclude that the lemma holds.
 

### 2020-11-19 icra-2021.tex
ah troubles with the model...

@@
   \end{array}\right],\,A_j\begin{bmatrix}1 & \omega j \\ -\omega j & 1\end{bmatrix},\\
-  C&=\left[\begin{array}{cccccc}
-    1 & 1 & 0 & \cdots & 1 & 0
+  C&=(1/T)\left[\begin{array}{cccccc}
+    1 & \cdots & 1
   \end{array}\right],
@@
 We consider the non-singular matrix $V$, whose columns are eigenvectors of $A_c$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$.
-We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$, where $\lambda_j$ is the $j$-th eigenvalue of $A_c$.
+We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$.
+$\lambda_0$ is the eigenvalue associated to the first item of $A_c$.
 $\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j-I$.
-We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and thus $AV=VD$.
-
-We apply the approach in terms of the continuous form of Euqation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$.
-Initial guess is expressed $\mathbf{q}_0=\mathbf{\gamma}V$ as a combination of eigenvectors.
+We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
+
+We apply the approach in terms of the continuous equivalent of the model in Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$.
+Initial guess is expressed as a combination of eigenvectors $\mathbf{q}_0=\mathbf{\gamma}V$.
 The generic solution is $\mathbf{q}_k=\mathbf{\gamma}e^{Dk}V$.
 
-Let us express the output at time $k$ of the continuous equivalent of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state $y=C\mathbf{q}$
-\begin{equation}\label{eq:proof-output}
-  y=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_j^0k}v_j^0}+\sum_{j=1}^r{\gamma_je^{\lambda_j^1k}v_j^1},
-\end{equation}
+Let us express the output at time $k$ as a linear combination of the state $y=C\mathbf{q}=C\gamma e^{Dk}V$
+\begin{equation}\label{eq:proof-output}\begin{split}
+  y=\gamma_0e^{\lambda_0k}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^0k}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^1k}v_j^1},
+\end{split}\end{equation}
 we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
 
-The matrix $A_c$ is a block diagonal matrix, and we can express its determinant as the multiplication of the determinants of its blocks $\det{(A_c)}=\det{(0)}\times\det{(A_1-I)}\times\cdots\times\det{(A_r-I)}$.
+The matrix $A_c$ is a block diagonal matrix, so we can express its determinant as the multiplication of the determinants of its blocks $\det{(A_c)}=\det{(0)}\times\det{(A_1-I)}\times\cdots\times\det{(A_r-I)}$.
 We proof each block separately.
@@
 The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$.
-We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0/T=\gamma_0$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0=\gamma_0$.
 
@@
 The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$.
-Again, we find the subvector $\gamma_1$ of the vector $\gamma$ such that the equivalences $(1/T)e^{i\omega k}(a_1-ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $(1/T)e^{-i\omega k}(a_1+ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
-They hold for $\gamma_1=(1/T)\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+Again, we find the subvector $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega k}(a_1-ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $e^{-i\omega k}(a_1+ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
+They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
 
@@
 
-The discretized version $A$ of the matrix $A_c$ can be expressed $A=A_c+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs with $A=e^{A_ck}$}).
+The discretized version $A$ of the matrix $A_c$ can be expressed $A=A_c+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs rather than an approximation with $A=e^{A_ck}$}).
 We thus conclude that the lemma holds.

### 2020-11-19 scripts/energy/build_model.m

@@ -20,7 +20,7 @@ function [A, B, C, u, h] = build_model(r, xi, gck, mk)
     % system definition
     j = 2*r + 1;
 
-    An = @(n) [ 0 n/xi ; -n^2/xi^2 0 ];
+    An = @(n) [ 1 n/xi ; -n/xi 1 ];
     A  = zeros(j);
     A(1,1) = 1;
     C = [1];
@@ -32,10 +32,12 @@ function [A, B, C, u, h] = build_model(r, xi, gck, mk)
     
     for i = 1:r
         A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
-        C = [C 1 0];
-        h = h + q(2 * i) * cos(i * k / xi) + ...
-                q(2 * i + 1) * sin(i * k / xi);
+        C = [C 1 1];
+        h = h + 1 * q(2 * i) * cos(i * k / xi) + ...
+                1 * q(2 * i + 1) * sin(i * k / xi);
     end
+    
+    C = 1/100 * C;
     
     clear k;
     

### 2020-11-19 scripts/energy/evolve_sys.m

@@ -7,6 +7,7 @@ function [y, q] = evolve_sys(A, B, C, u, q0, t)
 %   B:   control matrix
 %   C:   output matrix
 %   u:   control vector (must contain one value per each item in t)
+%   q0:  initial guess
 %   t:   time vector
 %
 % Outputs:

### 2020-11-19 scripts/energy/guess_kf.m

@@ -20,6 +20,8 @@ function [q0, P0, Q, R] = guess_kf(meas1, j)
     q0(1) = meas1 * ((j -1) / j);
     q0(2:end) = meas1 * (1 / ((j - 1) * j));
     
+    q0 = q0 * 100;
+    
     P0 = eye(j) .* q0 * 10^-1;
     
     % process noise and sensor noise

### 2020-11-19 scripts/lemma.m

@@ -1,0 +1,69 @@
+
+
+% using this script to temporarily proof the lemma
+
+a0 = 10;
+a0 = qt(1);
+a1 = 1.43;
+a1 = qt(2);
+
+b1 = 1.43;
+b1 = qt(3);
+
+T = 100;
+
+o = 2*pi/T;
+
+h = @(k) a0/T + 2*(a1*cosd(o*k) + b1*sind(o*k))/T; 
+               % 2*(a2*cosd(o*2*k) + b2*sind(o*2*k))/T + ...
+                %2*(a3*cosd(o*3*k) + b3*sind(o*3*k))/T;
+              
+c = @(k) a0/T + (exp(1i*o*k)*(a1 - 1i*b1))/T + ...
+                (exp(-1i*o*k)*(a1 + 1i*b1))/T;
+                %(exp(1i*o*2*k)*(a2 - 1i*b2))/T + ...
+                %(exp(-1i*o*2*k)*(a2 + 1i*b2))/T + ...
+                %(exp(1i*o*3*k)*(a3 - 1i*b3))/T + ...
+                %(exp(-1i*o*3*k)*(a3 + 1i*b3))/T;
+              
+x = 1:1000;
+y = h(x);
+              
+figure;
+plot(x, y);
+
+Aj = @(j) [ 1 o*j ; -o*j 1 ];
+A  = zeros(3);
+A(1,1) = 1;
+C = 1;
+
+for i = 1:1
+    A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = Aj(i); 
+    C = [C 1 1];
+end
+
+q0 = [a0; a1; b1];    
+C = 1/T * C;
+
+yy = [];
+    
+q = [];
+    
+for k = x
+    q1 = A * q0;
+    y1 = C * q1;
+        
+    yy = [yy y1];
+    q = [q q1];
+        
+    q0 = q1;    
+end
+
+figure;
+plot(x, yy);
+
+yyy = c(x);
+
+
+figure;
+plot(x, yyy);
+

### 2020-11-19 scripts/lemma2.m

@@ -1,0 +1,75 @@
+
+
+% using this script to temporarily proof the lemma
+
+a0 = 10;
+a0 = qt(1);
+a1 = 1.43;
+a1 = qt(2);
+a2 = 1.43;
+a2 = qt(3);
+a3 = 1.43;
+a3 = qt(4);
+b1 = 1.43;
+b1 = qt(5);
+b2 = 1.43;
+b2 = qt(6);
+b3 = 1.43;
+b3 = qt(7);
+T = 100;
+
+o = 2*pi/T;
+
+h = @(k) a0/T + 2*(a1*cosd(o*k) + b1*sind(o*k))/T + ...
+                2*(a2*cosd(o*2*k) + b2*sind(o*2*k))/T + ...
+                2*(a3*cosd(o*3*k) + b3*sind(o*3*k))/T;
+              
+c = @(k) a0/T + (exp(1i*o*k)*(a1 - 1i*b1))/T + ...
+                (exp(-1i*o*k)*(a1 + 1i*b1))/T + ...
+                (exp(1i*o*2*k)*(a2 - 1i*b2))/T + ...
+                (exp(-1i*o*2*k)*(a2 + 1i*b2))/T + ...
+                (exp(1i*o*3*k)*(a3 - 1i*b3))/T + ...
+                (exp(-1i*o*3*k)*(a3 + 1i*b3))/T;
+              
+x = 1:1000;
+y = h(x);
+              
+figure;
+plot(x, y);
+
+Aj = @(j) [ 1 o*j ; -o*j 1 ];
+A  = zeros(7);
+A(1,1) = 1;
+C = 1;
+
+for i = 1:3
+    A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = Aj(i); 
+    C = [C 1 1];
+end
+
+q0 = [a0; a1; b1; a2; b2; a3; b3];    
+C = 1/T * C;
+
+yy = [];
+    
+q = [];
+    
+for k = x
+    q1 = A * q0;
+    y1 = C * q1;
+        
+    yy = [yy y1];
+    q = [q q1];
+        
+    q0 = q1;    
+end
+
+figure;
+plot(x, yy);
+
+yyy = c(x);
+
+
+figure;
+plot(x, yyy);
+

### 2020-11-23 icra-2021.tex
fixes to the lemma but still more fixes to come

@@
 %%
-%% Conference Paper for ICRA'21, May 16-22, Xi'an, China
+%% 
 %% 
@@
 
-Let us consider a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{Z}_{> 0}$ for the purpose of energy consumption modeling of the mission
+Let us consider a periodic signal of period $T\in\mathbb{Z}_{> 0}$ representing the energy consumption, and Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ and for the purpose of energy consumption modeling of the signal
 \begin{equation}\label{eq:fourier}
-  h(k)=a_0/T+(2/T)\sum_{j=1}^{r}{\left(a_j\cos{\omega jk}+b_j\sin{\omega jk}\right)},
+  h(t)=a_0/T+(2/T)\sum_{j=1}^{r}{\left(a_j\cos{\omega jt}+b_j\sin{\omega jt}\right)},
 \end{equation}
@@
 \begin{equation}\label{eq:state-perf}\begin{split}
-  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k,\\
-  y_k&=C\mathbf{q}_k+v_k,
+  \dot{\mathbf{q}}&=A\mathbf{q}+B\mathbf{u}+\mathbf{w},\\
+  y&=C\mathbf{q}+v,
 \end{split}\end{equation}
-where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
+where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
-  \mathbf{q}_k&=\left[\begin{array}{cccccc}
+  \mathbf{q}&=\left[\begin{array}{cccccc}
     \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
@@
   A&=\left[\begin{array}{cccc}
-    1&    &       &  \\
+    0&    &       &  \\
      & A_1&       &  \\
@@
      &    &       & A_r 
-  \end{array}\right],\,A_j\begin{bmatrix}1 & \omega j \\ -\omega j & 1\end{bmatrix},\\
+  \end{array}\right],\,A_j\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},\\
   C&=(1/T)\left[\begin{array}{cccccc}
-    1 & \cdots & 1
+    1 & 1 & 0 &\cdots & 1 & 0
   \end{array}\right],
 \end{split}\end{equation}
-where $\mathbf{q}_k\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+where $\mathbf{q}\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
 In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.
 
-\begin{lem}[Fourier series, LTI state-space equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero) and the control is zero.
-The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using the LTI state-space model in Equation~(\ref{eq:state-perf})
+\begin{lem}[Representations equivalence]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero.
+Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$.
+Then Equation~(\ref{eq:fourier}) describes the same signal as Equation~(\ref{eq:state-perf}).
 \end{lem}
-\begin{proof}
-We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
-With $t=\omega jk$, we find the expression for $\cos{\omega jk}=(e^{i\omega jk}+e^{-i\omega jk})/2$ and $\sin{\omega jk}=(e^{i\omega jk}-e^{-i\omega jk})/(2i)$ by substitution of $\sin{\omega jk}$ and $\cos{\omega jk}$ respectively.
-This leads~\cite{kuo1967automatic}
-\begin{equation}\begin{split}\label{eq:proof-complex}
-  h(k)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jk}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jk}(a_j+ib_j)},
- \end{split}\end{equation}
-where $i$ is the imaginary unit.
-
-Let us consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$, and an initial guess $\mathbf{q}_0$.
-$A_c$ is defined as the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c:=A-I$, where $I$ is a properly sized identity matrix.
-The solution at time $k$ can be expressed $\mathbf{q}=e^{A_ck}\mathbf{q}_0$.
-Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
-To solve the matrix exponential $e^{A_ck}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
-
-The method works on the similarity transformation $A_c=VDV^{-1}$.
-The power series definition of $e^{A_ck}$ implies $e^{A_ck}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}.
-We consider the non-singular matrix $V$, whose columns are eigenvectors of $A_c$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$.
-We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$.
-$\lambda_0$ is the eigenvalue associated to the first item of $A_c$.
-$\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j-I$.
-We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
-
-We apply the approach in terms of the continuous equivalent of the model in Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A_c\mathbf{q}$.
-Initial guess is expressed as a combination of eigenvectors $\mathbf{q}_0=\mathbf{\gamma}V$.
-The generic solution is $\mathbf{q}_k=\mathbf{\gamma}e^{Dk}V$.
-
-Let us express the output at time $k$ as a linear combination of the state $y=C\mathbf{q}=C\gamma e^{Dk}V$
-\begin{equation}\label{eq:proof-output}\begin{split}
-  y=\gamma_0e^{\lambda_0k}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^0k}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^1k}v_j^1},
-\end{split}\end{equation}
-we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
-
-The matrix $A_c$ is a block diagonal matrix, so we can express its determinant as the multiplication of the determinants of its blocks $\det{(A_c)}=\det{(0)}\times\det{(A_1-I)}\times\cdots\times\det{(A_r-I)}$.
-We proof each block separately.
-
-First, we proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
-We find the eigenvalue from $\det(0-\lambda I)=0$, which is $\lambda_0=0$.
-The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$.
-We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0=\gamma_0$.
-
-Then, we proof that all the terms in the sum of both the Equations~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
-
-For the first block $A_1-I$, we find the eigenvalues from $\det(A_1-(1+\lambda)I)=0$.
-The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
-The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}-i&1\end{bmatrix}^T$.
-The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$.
-Again, we find the subvector $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega k}(a_1-ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $e^{-i\omega k}(a_1+ib_1)=\gamma_1e^{i\omega k}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
-They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
-
-The proof for the remaining $r-1$ blocks is equivalent.
-
-The discretized version $A$ of the matrix $A_c$ can be expressed $A=A_c+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs rather than an approximation with $A=e^{A_ck}$}).
-We thus conclude that the lemma holds.
-
-\end{proof}
+
+The equivalence of the models is trivial and the coefficients are chosen such that the two Equations produce the same expression.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof.
+
+Let us consider the discretized version $A_d$ of the matrix $A$ can be expressed $A_d=A+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs rather than an approximation with $A=e^{A_ck}$}).
+% where to place this...
+Maybe in the algorithm...
+% and write little more how, why you discretized...
 
@@
 \leavevmode\thispagestyle{empty}\newpage % just for now
-\leavevmode\thispagestyle{empty}\newpage
 
@@
 \appendices
+
+\section{Proof of Lemma~\ref{lem:eqv}}
+\label{app:proof-eqv}
+
+This appendix is a formal proof of Lemma~\ref{lem:eqv}.
+
+The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ such that the coefficients $a_0,\dots,b_r$ are the same as the coefficients $\alpha_0,\dots,\beta_r$.
+
+We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
+With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively.
+This leads~\cite{kuo1967automatic}
+\begin{equation}\begin{split}\label{eq:proof-complex}
+  h(t)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jt}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}(a_j+ib_j)},
+ \end{split}\end{equation}
+where $i$ is the imaginary unit.
+
+The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$.
+Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
+To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
+
+The method works on the similarity transformation $A_c=VDV^{-1}$.
+The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}.
+We consider the non-singular matrix $V$, whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$.
+We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$.
+$\lambda_0$ is the eigenvalue associated to the first item of $A$.
+$\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j$.
+We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
+
+We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$.
+Initial guess is expressed as a combination of eigenvectors $\mathbf{q}_0=\mathbf{\gamma}V$.
+The generic solution is $\mathbf{q}=\mathbf{\gamma}e^{Dt}V$.
+% to rewrite this so it's exactly as in the proof
+
+Let us consider the linear combination of all the coefficients of the state at time $t$. This can be expressed in the following form
+\begin{equation}\label{eq:proof-output}\begin{split}
+  \gamma_0e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^1t}v_j^1},
+\end{split}\end{equation}
+we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
+% the V and gamma are wrong sizes.
+You put zeros so you fill them (look at the sheet where you sketched it before)
+
+The matrix $A$ is a block diagonal matrix, so we can express its determinant as the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
+We proof the first determinant and the others separately.
+
+We proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
+We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
+The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0=\gamma_0$.
+
+Then, we proof that all the terms in the sum of both the Equations~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+
+For the first block $A_1$, we find the eigenvalues from $\det(A_1-\lambda I)=0$.
+The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
+The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}-i&1\end{bmatrix}^T$.
+The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$.
+Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
+They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+
+The proof for the remaining $r-1$ blocks is equivalent.
+
+We thus conclude that the lemma holds.
+
+\qed
+
 \section{Mission Plan Format}

### 2020-11-23 scripts/lemma.m

@@ -2,28 +2,34 @@
 
 % using this script to temporarily proof the lemma
 
-a0 = 10;
-a0 = qt(1);
-a1 = 1.43;
-a1 = qt(2);
+a0 = 2000;
+%a0 = qt(1);
+a1 = 200;
+%a1 = qt(2);
 
-b1 = 1.43;
-b1 = qt(3);
+b1 = 200;
+%b1 = qt(3);
+
+a2 = 200;
+b2 = 200;
+
+a3 = 200;
+b3 = 200;
 
 T = 100;
 
 o = 2*pi/T;
 
-h = @(k) a0/T + 2*(a1*cosd(o*k) + b1*sind(o*k))/T; 
-               % 2*(a2*cosd(o*2*k) + b2*sind(o*2*k))/T + ...
-                %2*(a3*cosd(o*3*k) + b3*sind(o*3*k))/T;
+h = @(k) a0/T + 2*(a1*cos(o*k) + b1*sin(o*k))/T + ...
+                2*(a2*cos(o*2*k) + b2*sin(o*2*k))/T + ...
+                2*(a3*cos(o*3*k) + b3*sin(o*3*k))/T;
               
 c = @(k) a0/T + (exp(1i*o*k)*(a1 - 1i*b1))/T + ...
-                (exp(-1i*o*k)*(a1 + 1i*b1))/T;
-                %(exp(1i*o*2*k)*(a2 - 1i*b2))/T + ...
-                %(exp(-1i*o*2*k)*(a2 + 1i*b2))/T + ...
-                %(exp(1i*o*3*k)*(a3 - 1i*b3))/T + ...
-                %(exp(-1i*o*3*k)*(a3 + 1i*b3))/T;
+                (exp(-1i*o*k)*(a1 + 1i*b1))/T + ...
+                (exp(1i*o*2*k)*(a2 - 1i*b2))/T + ...
+                (exp(-1i*o*2*k)*(a2 + 1i*b2))/T + ...
+                (exp(1i*o*3*k)*(a3 - 1i*b3))/T + ...
+                (exp(-1i*o*3*k)*(a3 + 1i*b3))/T;
               
 x = 1:1000;
 y = h(x);
@@ -31,38 +37,42 @@ y = h(x);
 figure;
 plot(x, y);
 
-Aj = @(j) [ 1 o*j ; -o*j 1 ];
-A  = zeros(3);
[…]

### 2020-11-24 icra-2021.tex
fixed that proof finally (now I can forget it I hope...)

@@
 
-\begin{lem}[Representations equivalence]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero.
+\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero.
 Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$.
@@
 \end{lem}
-
+\begin{proof}
 The equivalence of the models is trivial and the coefficients are chosen such that the two Equations produce the same expression.
 We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof.
+\end{proof}
 
@@
 
-This appendix is a formal proof of Lemma~\ref{lem:eqv}.
-
-The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ such that the coefficients $a_0,\dots,b_r$ are the same as the coefficients $\alpha_0,\dots,\beta_r$.
-
-We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
+We propose a formal proof of Lemma~\ref{lem:eqv}.
+The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ in Equation~(\ref{eq:state-details}).
+We write these elements such that the coefficients of the series $a_0,\dots,b_r$ are the same as the coefficients of the state $\alpha_0,\dots,\beta_r$.
+
+Let us re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
 With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively.
@@
 The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$.
-Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
+Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
 To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
 
-The method works on the similarity transformation $A_c=VDV^{-1}$.
+The method works on the similarity transformation $A=VDV^{-1}$.
 The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}.
@@
 $\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j$.
-We can write $A_cv_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
-
-We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$.
-Initial guess is expressed as a combination of eigenvectors $\mathbf{q}_0=\mathbf{\gamma}V$.
-The generic solution is $\mathbf{q}=\mathbf{\gamma}e^{Dt}V$.
-% to rewrite this so it's exactly as in the proof
-
-Let us consider the linear combination of all the coefficients of the state at time $t$. This can be expressed in the following form
+We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
+
+We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$. The linear combination of the initial guess and the generic solution
+\begin{equation*}\begin{split}
+  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}}\\
+  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}
+\end{split}\end{equation*}
+where $F=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is a properly sized vector of ones.
+
+Let us consider the second expression. It represents the linear combination of all the coefficients of the state at time $t$. It can also be expressed in the following form
 \begin{equation}\label{eq:proof-output}\begin{split}
-  \gamma_0e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_je^{\lambda_j^1t}v_j^1},
+  \gamma_0 e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
 \end{split}\end{equation}
-we proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
-% the V and gamma are wrong sizes.
-You put zeros so you fill them (look at the sheet where you sketched it before)
+
+We proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
 
@@
 We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
-The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=0\,\,\,\forall v_0$, thus we choose $v_0=1$.
-We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $a_0=\gamma_0$.
+The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=\begin{bmatrix} 0 & \cdots & 0 \end{bmatrix}\,\,\,\forall v_0$, thus we choose $v_0=\begin{bmatrix}1 & 0 & \cdots & 0\end{bmatrix}$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.
 
@@
 The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
-The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}-i&1\end{bmatrix}^T$.
-The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}i&1\end{bmatrix}^T$.
-Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}-i&1\end{bmatrix}^T$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1e^{i\omega t}\begin{bmatrix}i&1\end{bmatrix}^T$ hold.
+The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}0 & -i&1&0&\cdots&0\end{bmatrix}^T$.
+The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}0&i&1&0&\cdots&0\end{bmatrix}^T$.
+Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1 e^{i\omega t}v_1^0$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1 e^{i\omega t}v_1^1$ hold.
 They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
-
 The proof for the remaining $r-1$ blocks is equivalent.
 
+The initial guess is build such that the sum of the coefficients is the same in both the signals.
+The output matrix is built as follows.
+The coefficient $1/T$ accounts for the period in Equations~(\ref{eq:proof-complex}--\ref{eq:proof-output}) and~(\ref{eq:fourier}).
+At time instant zero, the coefficients $b_j$ are not present (and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$).
+Thus to match the outputs $h(t)=y(t)$ we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
 We thus conclude that the lemma holds.
+
+We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$).
+Even if both the signals $h$ and $y$ would be still periodic, they would not be equal.
 
@@
 If there are any following stages in the survey, they are constructed the same way.
-Th stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius.
+The stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius.
 For $i:=\{1,3,5,\dots\}$ TEE line with variable displacement.

### 2020-11-25 icra-2021.tex
trying to implement Ulrik's review (still to go)

@@
 
-Many scenarios involving unmanned aerial vehicles (UAVs) such as precision agriculture, search and rescue, and surveillance require high autonomy but have limited energy budgets.
+Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
 A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computations with little human interaction.
 For instance, the UAV might detect ground patterns and inform other ground-based actors.
-Energy-aware dynamic mission planning finds optimal tradeoffs between the trajectory, computations, and energy requirements.
-However, current generic planning solutions for UAVs flying outdoors do not plan the mission dynamically, nor are energy-aware.
+We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the trajectory, computations, and energy requirements.
+Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware.
 They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
@@
 
-Planning algorithms literature for mobile robots is by now large and related to topics such as trajectory generation and path planning.
+Planning algorithms literature for mobile robots includes topics such as trajectory generation and path planning.
 Generally, the algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}.
-However, they apply to a small number of robots~\cite{kim2005energy}, and focus on planning the trajectory for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being influenced by computations~\cite{mei2005case}.
+However, they apply to a small number of robots~\cite{kim2005energy}, and focus exclusively on planning the trajectory for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being significantly influenced by computations~\cite{mei2005case}.
 Given the availability of powerful GPU-equipped mobile hardware, the use of computations is expected to increase in the near future.
@@
 
-Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain. 
-The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature.
-It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
-The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
-The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters: the Quality of Service (QoS) computations are relative to the tasks.
-The trajectory-explicit equations (TEEs) adjustments are relative to the path.
-The computations specify a given task's computational level.
-The adjustments are a way to alter the TEE.
-The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences.
+Unlike most of the past planning algorithms literature, our algorithm plans both the computations and the trajectory.
+We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
+The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
+To express the trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE).
+We plan the computations of the tasks running on the UAV using a modeling tool presented in our previous work~\cite{seewald2019coarse} and explore the trade-offs with the trajectory.
+In our approach, the user specifies an initial mission plan--the TEEs, the energy budget, and some parameters.
+The parameters are the maximum, minimum, and current levels of the computations and trajectory.
+The energy budget is the battery capacity and some other battery parameters.
+The algorithm replans the initial mission plan as the remaining battery state of charge (SoC) unexpectedly changes due to, e.g., atmospheric interferences.
+Our goal is to complete the mission with the highest possible current computations and trajectory parameters as the UAV flies and its batteries drain.
 In the remainder of the paper, we adopt the following notation.
-We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.
-
-The algorithm contributes to the planning literature further with a periodic energy model that accounts for the uncertainty (atmospheric interference).
-Mission periodicity is usually present due to the mission's repetitive patterns~\cite{seewald2020mechanical}.
+We refer to the current computations and trajectory parameters as computations and trajectory parameters.
+We refer to just parameters when we deal with both the computations and trajectory parameters.
+We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets.
+There can be multiple or none computations sets per each task, and the same applies to the trajectory.
+The term parameters is not to be confused with the battery parameters, which we always mention explicitly.
+These are fixed values that are not replanned by the algorithm.
+
+% Ulrik, I don't agree with a main. The main contibution is the inclusion of computations and trajectory in the planning. Should I stress that? The periodicity helps us to achieve that.
+To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
+Mission periodicity is often present due to the mission's repetitive patterns~\cite{seewald2020mechanical}.
 Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
-The mission is periodic, so we expect the energy to approximately evolve periodically.
+Given that the mission is periodic, we expect the energy to approximately evolve periodically.
+% Adam you need to fix from here on xD
 The observation applies broadly; repetitive patterns have been observed in scenarios as far as space rovers~\cite{seewald2020beyond}.
@@
 \begin{proof}
-The equivalence of the models is trivial and the coefficients are chosen such that the two Equations produce the same expression.
-We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof.
+The equivalence of the models is trivial and the equality of the two signals is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof the equality.
 \end{proof}
@@
 \begin{equation}\label{eq:proof-output}\begin{split}
-  \gamma_0 e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
+  F\mathbf{q}(t)/T=\gamma_0 e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
 \end{split}\end{equation}
@@
 At time instant zero, the coefficients $b_j$ are not present (and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$).
-Thus to match the outputs $h(t)=y(t)$ we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
+To match the outputs $h(t)=y(t)$--or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$--we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
 We thus conclude that the lemma holds.
 
-We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$).
+We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=c\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $c\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant $c\in\mathbb{R}$).
 Even if both the signals $h$ and $y$ would be still periodic, they would not be equal.

### 2020-11-26 icra-2021.tex
ok I feel like the intro is fixed, now I need to fix the figure

@@
   }
+  @article{rizvi2017general,
+    title={A general-purpose graphics processing unit (gpgpu)-accelerated robotic controller using a low power mobile platform},
+    author={Rizvi, Syed Tahir Hussain and Cabodi, Gianpiero and Patti, Denis and Gulzar, Muhammad Majid},
+    journal={Journal of Low Power Electronics and Applications},
+    volume={7},
+    number={2},
+    pages={10},
+    year={2017},
+    publisher={Multidisciplinary Digital Publishing Institute}
+  }
+  @article{abramov2012real,
+    title={Real-time segmentation of stereo videos on a portable system with a mobile gpu},
+    author={Abramov, Alexey and Pauwels, Karl and Papon, Jeremie and Worgotter, Florentin and Dellen, Babette},
+    journal={IEEE Transactions on Circuits and Systems for Video Technology},
+    volume={22},
+    number={9},
+    pages={1292--1305},
+    year={2012},
+    publisher={IEEE}
+  }
+  @inproceedings{jaramillo2019visual,
+    title={Visual saliency with foveated images for fast object detection and recognition in mobile robots using low-power embedded GPUs},
+    author={Jaramillo-Avila, Uziel and Aitken, Jonathan M and Anderson, Sean R},
+    booktitle={2019 19th International Conference on Advanced Robotics (ICAR)},
+    pages={773--778},
+    year={2019},
+    organization={IEEE}
+  }
+  @inproceedings{satria2016real,
+    title={Real-time system-level implementation of a telepresence robot using an embedded GPU platform},
+    author={Satria, Muhammad Teguh and Gurumani, Swathi and Zheng, Wang and Tee, Keng Peng and Koh, Augustine and Yu, Pan and Rupnow, Kyle and Chen, Deming},
+    booktitle={2016 Design, Automation \& Test in Europe Conference \& Exhibition (DATE)},
+    pages={1445--1448},
+    year={2016},
+    organization={IEEE}
+  }
+
 \end{filecontents}
@@
 Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computations with little human interaction.
+A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computational tasks with little human interaction.
 For instance, the UAV might detect ground patterns and inform other ground-based actors.
+We refer to the computational tasks that can be dynamically replanned as computations.
 We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the trajectory, computations, and energy requirements.
@@
 However, they apply to a small number of robots~\cite{kim2005energy}, and focus exclusively on planning the trajectory for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being significantly influenced by computations~\cite{mei2005case}.
-Given the availability of powerful GPU-equipped mobile hardware, the use of computations is expected to increase in the near future.
-Mission planning algorithms, which include a broader concept of a mission being a set of tasks along with a motion plan, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Given the availability of powerful GPU-equipped mobile hardware~\cite{rizvi2017general}, the use of computations is expected to increase in the near future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
+Mission planning algorithms, which include a broader concept of a mission being a set of computations and trajectories, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
@@
 To express the trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE).
-We plan the computations of the tasks running on the UAV using a modeling tool presented in our previous work~\cite{seewald2019coarse} and explore the trade-offs with the trajectory.
-In our approach, the user specifies an initial mission plan--the TEEs, the energy budget, and some parameters.
+We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}.
+In our approach, the user specifies an initial mission plan--the TEEs,  computations, energy budget, and some parameters.
 The parameters are the maximum, minimum, and current levels of the computations and trajectory.
@@
 In the remainder of the paper, we adopt the following notation.
-We refer to the current computations and trajectory parameters as computations and trajectory parameters.
-We refer to just parameters when we deal with both the computations and trajectory parameters.
+We refer to the current computations and trajectory parameters simply as computations and trajectory parameters.
+We refer to parameters when we deal with both.
 We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets.
@@
 
-% Ulrik, I don't agree with a main. The main contibution is the inclusion of computations and trajectory in the planning. Should I stress that? The periodicity helps us to achieve that.
 To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
@@
 Given that the mission is periodic, we expect the energy to approximately evolve periodically.
-% Adam you need to fix from here on xD
-The observation applies broadly; repetitive patterns have been observed in scenarios as far as space rovers~\cite{seewald2020beyond}.
-The algorithm addresses the periodicity through Fourier analysis.
-The uncertainty with a state estimator.
-It outputs the control input (adjustments and computations) using output model predictive control (MPC).
+The observation applies broadly; we show how many UAV scenarios have a repetitive energy evolution.
+Moreover, we briefly investigate these patterns in some ground-based mobile robots.
+We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
+The algorithm outputs the parameters using output model predictive control (MPC).
 
@@
 The remainder of the paper is organized as follows.
-The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
+The overview of dynamic mission planning is provided in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
 The algorithm that uses the model and solves the UAV dynamic mission planning problem is proposed in Section~\ref{sec:algo}.

### 2020-11-26 icra-2021.tex
ach changed that intro again

@@
 
-Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computational tasks with little human interaction.
-For instance, the UAV might detect ground patterns and inform other ground-based actors.
+Often, unmanned aerial vehicle (UAV) planning algorithms generate a trajectory.
+We are interested in a different algorithm: one that plans a UAV mission.
+In such a mission, the UAV has to fly an assigned path--which can be composed of many trajectories--and compute some on-board computational tasks.
+Many scenarios involving UAVs, such as precision agriculture, search and rescue, and surveillance, necessitates mission planning, and are energy critical.
+For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
 We refer to the computational tasks that can be dynamically replanned as computations.
-We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the trajectory, computations, and energy requirements.
+We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements.
+The UAV can deviate from the path and change the computations within user-defined constraints.
 Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware.
 They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
-Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
+It is such a state of practice that has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
 The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.
@@
 These are fixed values that are not replanned by the algorithm.
+The algorithm outputs the parameters using output model predictive control (MPC).
 
 To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
+We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
 Mission periodicity is often present due to the mission's repetitive patterns~\cite{seewald2020mechanical}.
@@
 Given that the mission is periodic, we expect the energy to approximately evolve periodically.
-The observation applies broadly; we show how many UAV scenarios have a repetitive energy evolution.
-Moreover, we briefly investigate these patterns in some ground-based mobile robots.
-We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
-The algorithm outputs the parameters using output model predictive control (MPC).
+The observation applies broadly; we show different UAV scenarios with periodic energy signals. Moreover, we briefly investigate such signals in some ground-based mobile robots.
 

### 2020-11-26 icra-2021.tex
the provious version of intro was cleaner, so I placed the first paragraph pretty much as it was before the previous commit

@@
 
-Often, unmanned aerial vehicle (UAV) planning algorithms generate a trajectory.
-We are interested in a different algorithm: one that plans a UAV mission.
-In such a mission, the UAV has to fly an assigned path--which can be composed of many trajectories--and compute some on-board computational tasks.
-Many scenarios involving UAVs, such as precision agriculture, search and rescue, and surveillance, necessitates mission planning, and are energy critical.
+Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
+A typical example of a mission in these scenarios is a UAV flying a path--that can be composed of multiple trajectories--and performing some on-board computational tasks.
 For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
@@
 We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements.
-The UAV can deviate from the path and change the computations within user-defined constraints.
 Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware.
 They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
-It is such a state of practice that has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
+Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
 The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.
@@
 Given the availability of powerful GPU-equipped mobile hardware~\cite{rizvi2017general}, the use of computations is expected to increase in the near future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
-Mission planning algorithms, which include a broader concept of a mission being a set of computations and trajectories, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+Mission planning algorithms, which include a broader concept of a mission being a set of tasks and a path, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
 
-Unlike most of the past planning algorithms literature, our algorithm plans both the computations and the trajectory.
-We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
+Unlike most of the past planning algorithms literature, our algorithm plans both the computations and path.
+We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory.
 The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
-To express the trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE).
+To express a trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE).
 We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}.
-In our approach, the user specifies an initial mission plan--the TEEs,  computations, energy budget, and some parameters.
+In our approach, the user specifies an initial mission plan--the path using the TEEs, computations, energy budget, and some parameters.
 The parameters are the maximum, minimum, and current levels of the computations and trajectory.
@@
 We refer to the current computations and trajectory parameters simply as computations and trajectory parameters.
-We refer to parameters when we deal with both.
+We refer to both as parameters.
 We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets.
 There can be multiple or none computations sets per each task, and the same applies to the trajectory.
-The term parameters is not to be confused with the battery parameters, which we always mention explicitly.
+The term parameters should not be confused with the battery parameters, which we always mention explicitly.
 These are fixed values that are not replanned by the algorithm.

### 2020-11-27 icra-2021.tex
hopefully this is the last change to intro for long time...

@@
 Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of a mission in these scenarios is a UAV flying a path--that can be composed of multiple trajectories--and performing some on-board computational tasks.
+A typical example of a mission in these scenarios is a UAV flying a path and performing some on-board computational tasks.
 For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
@@
 
-Unlike most of the past planning algorithms literature, our algorithm plans both the computations and path.
+Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations.
 We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory.
 The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
-To express a trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE).
-We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}.
-In our approach, the user specifies an initial mission plan--the path using the TEEs, computations, energy budget, and some parameters.
-The parameters are the maximum, minimum, and current levels of the computations and trajectory.
+We denote the trajectory with a mathematical function that we refer to as the trajectory explicit equation (TEE).
+The path is composed of multiple TEEs.
+We express the computations with a modeling tool presented in our previous work~\cite{seewald2019coarse}.
+The algorithm alters the TEE and computations within some parameters using output model predictive control (MPC).
+These parameters are the maximum, minimum, and current levels of the TEE and computations.
+The user specifies the parameters in an initial mission plan with an energy budget.
 The energy budget is the battery capacity and some other battery parameters.
-The algorithm replans the initial mission plan as the remaining battery state of charge (SoC) unexpectedly changes due to, e.g., atmospheric interferences.
-Our goal is to complete the mission with the highest possible current computations and trajectory parameters as the UAV flies and its batteries drain.
 In the remainder of the paper, we adopt the following notation.
-We refer to the current computations and trajectory parameters simply as computations and trajectory parameters.
+We refer to the current TEE and computations parameters simply as TEE and computations parameters.
 We refer to both as parameters.
-We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets.
-There can be multiple or none computations sets per each task, and the same applies to the trajectory.
+We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets.
+There can be multiple or none computations sets per each task, and the same applies to the TEE.
 The term parameters should not be confused with the battery parameters, which we always mention explicitly.
 These are fixed values that are not replanned by the algorithm.
-The algorithm outputs the parameters using output model predictive control (MPC).
+Our goal is to complete the mission with the highest possible parameters as the UAV flies and its batteries drain.
 

### 2020-11-28 icra-2021.tex
so; I discovered checking the literature that mission and UAVs refers often to some military involvement. Of course I don't want to have nothing to do with this so mission has to go asap

@@
 \title{\LARGE \bf
-Energy-Aware Dynamic Mission Planning Algorithm for UAVs
+Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs
 }
@@
 Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of a mission in these scenarios is a UAV flying a path and performing some on-board computational tasks.
+A typical example of these scenarios is a UAV flying a path and performing some on-board computational tasks.
 For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
 We refer to the computational tasks that can be dynamically replanned as computations.
-We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements.
-Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware.
-They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}.
-Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs.
-The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.
+We are interested in energy-aware dynamic planning, which would find optimal tradeoffs between the path, computations, and energy requirements.
+Current generic planning solutions for outdoor UAVs do not plan path and computations dynamically, nor are energy-aware.
+They are often semi-autonomous; the plan is static and usually defined using planning software~\cite{daponte2019review}.
+Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
+The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV planning problem.
 
@@
 Given the availability of powerful GPU-equipped mobile hardware~\cite{rizvi2017general}, the use of computations is expected to increase in the near future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
-Mission planning algorithms, which include a broader concept of a mission being a set of tasks and a path, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
+More complex planning, which includes a broader concept of the plan being a set of tasks and a path, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
 For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
@@
 These parameters are the maximum, minimum, and current levels of the TEE and computations.
-The user specifies the parameters in an initial mission plan with an energy budget.
+The user specifies the parameters in an initial plan with an energy budget.
 The energy budget is the battery capacity and some other battery parameters.
@@
 There can be multiple or none computations sets per each task, and the same applies to the TEE.
+Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
 The term parameters should not be confused with the battery parameters, which we always mention explicitly.
 These are fixed values that are not replanned by the algorithm.
-Our goal is to complete the mission with the highest possible parameters as the UAV flies and its batteries drain.
-
-To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
+
+To achieve the energy-aware dynamic planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
 We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
-Mission periodicity is often present due to the mission's repetitive patterns~\cite{seewald2020mechanical}.
+Periodicity is often present due to the path and computations repetitive patterns~\cite{seewald2020mechanical}.
 Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
-Given that the mission is periodic, we expect the energy to approximately evolve periodically.
+Given that the plan is periodic, we expect the energy to approximately evolve periodically.
 The observation applies broadly; we show different UAV scenarios with periodic energy signals. Moreover, we briefly investigate such signals in some ground-based mobile robots.
 
-In the spirit of reducing costs and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV.
+In the spirit of reducing costs and resources, we showcase the algorithm using the problem of dynamic planning for a precision agriculture fixed-wing UAV.
 Precision agriculture is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
-The mission is structured as follows.
+The plan is structured as follows.
 Trajectory-wise, the UAV flies in circles and lines covering a polygon.
 Computationally-wise, it detects obstacles using a convolutional neural network (CNN) and informs grounded mobile robots employed for harvesting.
-The algorithm plans the mission; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:overview} shows an initial slice of such a mission.
+The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
+Figure~\ref{fig:overview} shows an initial slice of such a plan.
 The UAV first heads to a circular TEE with a given radius, which is later reduced as, e.g., windy weather requires the adjustment of the control input to avoid battery depletion.
@@
 The remainder of the paper is organized as follows.
-The overview of dynamic mission planning is provided in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
-The algorithm that uses the model and solves the UAV dynamic mission planning problem is proposed in Section~\ref{sec:algo}.
-Section~\ref{sec:experimental} presents the result and showcase the performances.
-The paper finishes with some conclusions in Section~\ref{sec:conclusion}.
+The overview of dynamic planning is provided in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
+The algorithm is proposed in Section~\ref{sec:algo}.
+Section~\ref{sec:experimental} presents the result and showcases the performances.
+We propose some conclusions in Section~\ref{sec:conclusion}.
+Finally, we provide some additional information in the Appendix~\ref{app:proof-eqv} and examples in the Appendix~\ref{app:simulator}.
+
+---
+%up is ok; down fixes to the text; main idea is to simplify how the plan is defined!
 
@@
 
-We assume that the initial mission plan consists of different stages. At each stage the robot must follow a path and do some tasks.
+We assume that the initial plan consists of different stages. At each stage the robot must follow the TEE within TEE sets and do the computations within the computations sets.
 
@@
 
-\begin{defn}[Stage and mission]\label{def:mission}
-  A \emph{stage} $\mathcal{M}_i$ at time instant $k$ of a mission $\mathcal{M}$ is defined as the ordered list
+\begin{defn}[Stage and plan]\label{def:mission}
+  A \emph{stage} $\mathcal{M}_i$ at time instant $k$ of a plan $\mathcal{M}$ is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
@@
 
-  The \emph{mission} is then $\mathcal{M}:\mathbb{R}^2\rightarrow\mathcal{M}_i$ a function which maps the point $\mathbf{p}_k$ to a specific stage $\mathcal{M}_i$.
+  The \emph{plan} is then $\mathcal{M}:\mathbb{R}^2\rightarrow\mathcal{M}_i$ a function which maps the point $\mathbf{p}_k$ to a specific stage $\mathcal{M}_i$.
 
   For simplicity the system is sampled in discrete time.
-The algorithm takes as input $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the mission state.
+The algorithm takes as input $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the plan state.
 \end{defn}
@@
 
-Suppose at time instant $k$ the mission reached stage $i$ and the control input is $\mathbf{u}_k^a:=\langle\mathbf{c}_k,\mathbf{s}_k\rangle$. The control along with the input matrix
+Suppose at time instant $k$ the plan reached stage $i$ and the control input is $\mathbf{u}_k^a:=\langle\mathbf{c}_k,\mathbf{s}_k\rangle$. The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}  
@@
 
-The energy consumption modeling of the mission necessitates the following assumption.
+The energy consumption modeling of the plan utilizes the following assumption.
 \begin{assm}[Energy evelution periodicity]\label{assm:periodic} 

### 2020-11-29 icra-2021.tex
fixes and added the state machine

@@
 \usepackage{tikz}
+\usetikzlibrary{automata,positioning,decorations.pathreplacing}
+\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
 
@@
 We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets.
+Again, we refer to both as parameters sets.
 There can be multiple or none computations sets per each task, and the same applies to the TEE.
@@
 
----
-%up is ok; down fixes to the text; main idea is to simplify how the plan is defined!
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Mission Planning Overview}
+\section{Planning Overview}
 \label{sec:prob}
 
-We assume that the initial plan consists of different stages. At each stage the robot must follow the TEE within TEE sets and do the computations within the computations sets.
-
-Let the path at stage $i$ be characterized by a generic continuous twice differentiable TEE $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ and the tasks by functions $\psi_1,\dots,\psi_{\sigma}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$.
-Moreover, let $[a]$ be the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a lookup table.
-
-\begin{defn}[Stage and plan]\label{def:mission}
-  A \emph{stage} $\mathcal{M}_i$ at time instant $k$ of a plan $\mathcal{M}$ is defined as the ordered list
+We assume that a user-specified initial plan consists of different stages. At each stage, the UAV must follow the TEE within TEE sets and do the computations within the computations sets.
+
+Let us suppose the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
+We then express the TEE as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the TEE parameters which returns a metric of the distance between the point and the nominal trajectory.
+We express and the computations as the value of the computations parameters.
+We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}), and the of the computations parameters in Subsection~\ref{sec:computations-model}.
+
+Let us further adopt the following mathematical notation.
+$[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a plan specification.
+The plan specification is a file which specifies all the stages and triggering points along the plan.
+We discuss the format in Subsection~\ref{sec:plan}.
+
+\begin{defn}[Stage, plan and triggering point]\label{def:mission}
+  A \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
-    \mathcal{M}_i:=\{\langle\varphi_i(\mathbf{p}_k,c&_{i,1},\dots,c_{i,\rho}),\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle\\\mid
-      \exists\,\,\mathbf{p}_k,\,&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
-      &\psi_j(s_{i,j})\in\mathbb{S}_{i,j}\,\forall j\in[\sigma]^+\},
+    \Gamma_i:=\{\langle&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),c_{i,\rho+1},\dots,c_{i,\rho+\sigma}\rangle\\\mid
+    &\,\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
+      &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathbb{S}_{i,j}\,\},
   \end{split}\end{equation}
-  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{i,j}:=[\underline{s}_{i,j},\overline{s}_{i,j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th task QoS set.
-$\mathbf{p}_k:=(x,y)$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
+  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the TEE set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation set.
+$\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
 some inertial navigation frame $\mathcal{O}_W$.
-The parameters of the TEE $\varphi_i$ are the point and the adjustments (Subsection~\ref{sec:model}).
-The parameters of the tasks $\psi_1,\dots,\psi_\sigma$ are the computations (Subsection~\ref{sec:computations-model}).
-Note that while the TEE can differ for each stage, the tasks remain the same.
-However, the user can inhibit or enable a task varying QoS set.
-
-  The \emph{plan} is then $\mathcal{M}:\mathbb{R}^2\rightarrow\mathcal{M}_i$ a function which maps the point $\mathbf{p}_k$ to a specific stage $\mathcal{M}_i$.
-
-  For simplicity the system is sampled in discrete time.
-The algorithm takes as input $\mathcal{M}$, initial position, and energy coefficients guess, and outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the plan state.
+We note that while the TEE can differ for each stage, the tasks remain the same.
+However, the user can inhibit or enable a computation varying its computation set.
+
+  The \emph{plan} is then a function which maps a point to a specific stage $\Gamma_i$.
+The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+  \begin{figure}[h]
+  \center
+  \begin{tikzpicture}[shorten >=1pt,node distance=12ex,on grid,auto] 
+    \node        (q_dots0) {$\cdots$};
+    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
+    \node[state] (q_1) [right=of q_0] {$\Gamma_{i+1}$};
+    \node        (q_dots1) [right=of q_1] {$\cdots$};   
+    \path[->]
+    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
+    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_1)    
+    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
+    (q_1) edge node {$\mathbf{p}_{\Gamma_{i+1}}$} (q_dots1)
+    (q_1) edge [loop above] node {$\mathbf{p}_{k}$} (q_1)
+    ; %end path 
+    \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
+    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma:\mathbb{R}^2\rightarrow\Gamma_i$};
+  \end{tikzpicture}
+  \caption{Finite state machine of the plan}
+  \label{fig:state-machine}
+  \end{figure}
+
+  A slice of a finite state machine in Figure~\ref{fig:state-machine} shows the transition between the stages.
+The triggering point $\mathbf{p}_{i-1}$ allows the transition to stage $\Gamma_i$.
+The UAV remains in the stage with any generic point $\mathbf{p}_k$.
+It eventually enters the stage $\Gamma_{i+1}$ with the triggerint point $\mathbf{p}_i$ and so on, until it reaches the last triggering point.
+
+  The algorithm takes as input $\Gamma,\bigcup_i{\Gamma_i}$, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation.
+It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
 \end{defn}
+
+\subsection{Plan specification file format}
+\label{sec:plan}
+
+We specify the stages $\bigcup_i{\Gamma_i}$, triggering points $\bigcup_i\mathbf{p}_{\Gamma_i}$, and the plan $\Gamma$ using a specific file format--the plan specification.
+We refer the reader to Appendix~\ref{app:plan-example} for an example.
+
+The first stage $\Gamma_1$ is specified as the first line of the file
+\begin{algorithmic}[1]
+  \State\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
+\end{algorithmic}
+where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the TEE.
+We refer the reader to the next subsection where we discuss the physical meaning of the convergence value and rotation.
+The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
+
+The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:stage}
+  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
+\end{algorithmic}
+where $x$ and $y$ are the two coordinates of the point. The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
+
+The following $\rho+\sigma$ lines
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:trigger-pt}
+  \State\textbf{\texttt{[$\underline{c}_i$,$\overline{c}_i$]}}\label{code:parameter-set}
+\end{algorithmic}
+specifies the lower $\underline{c}_i$ and upper $\overline{c}_i$ bound of the $i$-th parameter set.
+They are in ascending order and the TEE parameters sets are specified before the computations parameters sets.
+
+Follows the entries for stage $\Gamma_2$ (equivalent to lines~\ref{code:stage}--\ref{code:parameter-set}), $\Gamma_3$ and so on, until the last stage.
+We assume that the last triggering point is the final UAV position.
+
+% fixed up to here!
 
@@
 The equivalence of the models is trivial and the equality of the two signals is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
-We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof the equality.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof of the equality.
 \end{proof}
@@
 The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}0&i&1&0&\cdots&0\end{bmatrix}^T$.
-Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences $e^{i\omega t}(a_1-ib_1)=\gamma_1 e^{i\omega t}v_1^0$ and $e^{-i\omega t}(a_1+ib_1)=\gamma_1 e^{i\omega t}v_1^1$ hold.
-They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
-The proof for the remaining $r-1$ blocks is equivalent.
+Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences
+\begin{equation*}\begin{cases}
+  e^{i\omega t}(a_1-ib_1)&=\gamma_1 e^{i\omega t}v_1^0\\
+  e^{-i\omega t}(a_1+ib_1)&=\gamma_1 e^{i\omega t}v_1^1
+\end{cases}\end{equation*}
+hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$. The proof for the remaining $r-1$ blocks is equivalent.
 
@@
 
-We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=c\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $c\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant $c\in\mathbb{R}$).
+We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
 Even if both the signals $h$ and $y$ would be still periodic, they would not be equal.
@@
 
-\section{Mission Plan Format}
-
+\section{Plan Specification Example}
+\label{app:plan-example}
 We discuss how to specify an initial mission plan with an example of a survey mission.

### 2020-11-30 icra-2021.tex
fixing (need to change the control and the B matrix)

@@
 Let us further adopt the following mathematical notation.
-$[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a plan specification.
+$[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, $c^0$ the optimal value of parameter $c$,and $\underline{c},\overline{c}$ its lower and upper bound retrieved from a plan specification.
 The plan specification is a file which specifies all the stages and triggering points along the plan.
 We discuss the format in Subsection~\ref{sec:plan}.
+Moreover, we use the notation $c_{i,j}$ to specify the $j$-th item of the $i$-th parameters set $c_i$.
 
@@
 
-  The \emph{plan} is then a function which maps a point to a specific stage $\Gamma_i$.
+  The \emph{plan} is a finite state machine $\Gamma$ where the state-transition function $\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage.
 The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+
   \begin{figure}[h]
@@
     \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
-    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma:\mathbb{R}^2\rightarrow\Gamma_i$};
+    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma$};
   \end{tikzpicture}
@@
 
-  The algorithm takes as input $\Gamma,\bigcup_i{\Gamma_i}$, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation.
+  The algorithm takes as input the plan, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation.
 It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
@@
 \end{algorithmic}
-where $x$ and $y$ are the two coordinates of the point. The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
+where $x$ and $y$ are the two coordinates of the point.
+The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
+The coordinates can be expressed in function of the TEE parameters $c_1$.
+Generally, one can express the coordinates in function of any TEE parameters $c_i$, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
+
+\begin{figure}[h]
+  \center
+  \begin{tikzpicture}[shorten >=1pt,node distance=24ex,on grid,auto] 
+    \node        (q_dots0) {$\cdots$};
+    \node[state] (q_0) [right=of q_dots0] {$\langle\varphi_i,c_i\rangle$};
+    \node        (q_dots1) [right=of q_0] {$\cdots$};   
+    \path[->]
+    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1,\dots,c_{i-1})$} (q_0)
+    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1,\dots,c_{i})$} (q_dots1)    
+    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
+    ; %end path
+  \end{tikzpicture}
+  \caption{Detail of the stage $\Gamma_i$ in the finite state machine}
+  \label{fig:state-machine2}
+  \end{figure}
+
+We refer the reader to the example in Appendix~\ref{app:plan-example} for a detailed implementation.
+In the example, the first TEE parameter is propagated to all the following TEEs and triggering points.
 
@@
 
-The state is the UAV's position in space and the energy coefficients in time.
-We show a linear relation between the instantaneous energy consumption and the energy coefficients in Theorem~\ref{thm:state-vs-energy}, but the two are different.
-We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
-
-The set
+We describe the position with $x,y$ coordinates and the altitude $h$, and the energy with some energy coefficients which describes the energy evolution in time.
+Here we describe the position evolution using vector field~\cite{de2017guidance}.
+
+Let us assume the set
 \begin{equation}\label{eq:area}
@@
 delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
-
-The algorithm uses the set from Equation~(\ref{eq:area}) to select the optimal adjustments $\mathbf{c}_i^0$ s.t.
+Phisically, $\varphi_i$ is function of the two coordinates and is satisfied when a point $\mathbf{p}_k$ is on the TEE.
+The TEE parameters allows to change the TEE.
+They are a way to alter the nominal trajectory from the initial plan.
+
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $\mathbf{c}_i^0$ s.t.
 $\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
@@
 \end{equation}
-where $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:overview}).
+
+% fixed up to here!
+% idea; write control as parameters; write B as time-dependent, which multiplied TEE parameters gives energy due to trajectory (approx). By computations due to computations (from powprof).
 

### 2020-12-01 icra-2021.tex
working on the text

@@
 
-% fixed up to here!
-
-\subsection{State: position and energy}
+\subsection{State: position $\mathbf{p}$}
 \label{sec:model}
 
-We describe the position with $x,y$ coordinates and the altitude $h$, and the energy with some energy coefficients which describes the energy evolution in time.
-Here we describe the position evolution using vector field~\cite{de2017guidance}.
+We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.
 
@@
 delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
-Phisically, $\varphi_i$ is function of the two coordinates and is satisfied when a point $\mathbf{p}_k$ is on the TEE.
+Phisically, $\varphi_i$ is s function of the two coordinates and is satisfied when a point $\mathbf{p}_k$ is on the TEE.
+Physically, this means the UAV is flying exactly over the nominal trajectory.
 The TEE parameters allows to change the TEE.
-They are a way to alter the nominal trajectory from the initial plan.
-
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $\mathbf{c}_i^0$ s.t.
-$\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+They are a way to alter the nominal trajectory in the initial plan.
+
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $\mathbf{c}_i^0$, so $\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
 It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and deriving the direction to follow in the form of velocity vector
@@
 
-\subsection{Energy evolution due to trajectory}
+\subsection{State: energy $\mathbf{q}$}
 \label{sec:energy-model}
 
-The algorithm models the energy using as state energy coefficients $\mathbf{q}\in\mathbb{R}^m$ derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and decomposes the evolution in energy due to the trajectory and computations.
+We model the energy using some energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
+We refer to the instantaneous energy consumption evolution simply as energy signal.
+The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and decomposes the evolution in energy due to the path and computations.
 This approach is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
-Let us consider a periodic signal of period $T\in\mathbb{Z}_{> 0}$ representing the energy consumption, and Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ and for the purpose of energy consumption modeling of the signal
+We show a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}, but the two are different.
+We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
+
+Let us consider a periodic signal of period $T\in\mathbb{Z}_{> 0}$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
 \begin{equation}\label{eq:fourier}
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the modeled instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
-
-Consider a linear time-invariant (LTI) state-space model
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the signal, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+
+We use extensively the following assumption for the purpose of energy signal modeling.
+\begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
+Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
+\begin{equation}
+  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2].
+\end{equation}
+\end{assm}
+
+Physically this means that the time evolution of the instantaneous energy consumption is assumed to be approximately periodic.
+
+Let us consider a linear time-invariant (LTI) state-space model
 \begin{equation}\label{eq:state-perf}\begin{split}
@@
 \end{split}\end{equation}
-where $\mathbf{q}\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.
-
-\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zero) and the control is zero.
+where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros.
+
+\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zeros) and the control is zero.
 Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$.
@@
 
-Let us consider the discretized version $A_d$ of the matrix $A$ can be expressed $A_d=A+I$ for small enough values of time step (forward Euler approximation\footnote{One can guarantee to have the same outputs rather than an approximation with $A=e^{A_ck}$}).
-% where to place this...
-Maybe in the algorithm...
-% and write little more how, why you discretized...
-
-Suppose at time instant $k$ the plan reached stage $i$ and the control input is $\mathbf{u}_k^a:=\langle\mathbf{c}_k,\mathbf{s}_k\rangle$. The control along with the input matrix
+Let us consider the discretized version $A_d:=A\Delta t+I$ of the matrix $A$.
+We denote the continuous and discrete time with the standard notation $t,k$.
+We use the forward Euler approximation with a small enough value of the time step $\Delta t$.
+One can guarantee to have the same outputs rather than an approximation with $A=e^{At}$.
+
+Let us suppose that at time instant $k$ the plan reached $i$-th stage. The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}_k&=\begin{bmatrix}g(\mathbf{s}_k)-g(\mathbf{s}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
-  B&=\left[\begin{array}{cccc}
-    1& \omega_{i,1}& \cdots& \omega_{i,\rho}  \\
-     &            0&       &  \\
-     &             & \ddots&  \\
-     &             &       & 0
-  \end{array}\right],
+  \mathbf{u}&=\begin{bmatrix}c_{i,1} & \cdots & c_{i,\rho} & c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}^T,\\
+  B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
 \end{split}\end{equation}
-where $\mathbf{s}_k,g(\mathbf{s}_k)$ are the computations and the instantaneous computational energy consumption (Subsection~\ref{sec:computations-model}), $\mathbf{u}_k\in\mathbb{R}^n$ is the control given $n=1+\rho$, and $B\in\mathbb{R}^{m\times n}$.
-Moreover, the top-left entry of $B$ is one, while the others on the first row are gain factors $\Omega_{i}:=\{\omega_{i,1},\dots, \omega_{i,\rho}\}\in\mathbb{R}^\rho$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.
-
-Equation~(\ref{eq:state-control}) accounts for the energy due to the adjustments and computations.
-The difference $g(\mathbf{s}_k)-g(\mathbf{s}_{k-1})$ quantifies the change in the instantaneous computational energy consumption.
-Similarly, $\Omega_i(\mathbf{c}_k-\mathbf{c}_{k-1})$ quantifies the change in the instantaneous trajectory energy consumption.
-For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the adjustment radius of the circle $c_{0,1}$ adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\omega_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
-
-Note from Equation~(\ref{eq:state-control}) that the control input $\mathbf{u}_k^a$ differs from the nominal control $\mathbf{u}_k$ in Equation~(\ref{eq:state-perf}).
-The first is an output of the algorithm.
-The second is a function that maps two consecutive control inputs to the difference in instantaneous energy consumption $\mathbf{u}_k:\mathbb{R}^{2\rho}\times\mathbb{Z}_{\geq 0}^{2\sigma}\rightarrow\mathbb{R}^{1+\rho}$.
-
-The energy consumption modeling of the plan utilizes the following assumption.
-\begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
-Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
-\begin{equation}
-  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2].
-\end{equation}
-\end{assm}
-
-Physically this means that the time evolution of the instantaneous energy consumption is assumed to be approximately periodic.
+where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$, and $\mathbf{u}_{-1}=\mathbf{0}$.
+Moreover, the top row of $B$ contains gain factors $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho} & \nu_{i,\rho + 1}& \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}$, quantifying the contribution of a given parameter to the instantaneous energy consumption.
+The other entries of $B$ are zeros.
+
+Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
+For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{0,1}$--the radius of the circle--adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption $\nu_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
+The first $\rho$ gain factors quantifies the contribution of the $i$-th TEE parameters.
+A first guess of these parameters is derived empirically.
+They are later refined by the algorithm.
+The following $\sigma$ gain factors quantifies the contribution of the $i$-th computations parameters.
+They are derived using the modeling tool.
+We use the gain factors to select the optimal control $\mathbf{u}^0$.
 

### 2020-12-01 icra-2021.tex
working on the text (2)

@@
 
-\begin{figure*}[t]
-  \centering
-  \input{\figpath/icra-2021_overview2.tikz}
-  \caption{The mission consists of circles and lines covering a polygon.
+%\begin{figure*}[t]
+%  \centering
+%  \input{\figpath/icra-2021_overview2.tikz}
+%  \caption{The mission consists of circles and lines covering a polygon.
 The UAV heads to $\varphi_0$ initially, using the desired velocity vector $\dot{\mathbf{p}}_d$.
@@
 The UAV then converges to $\varphi_1$ in stage $\mathcal{M}_1$, $\varphi_2$ in stage $\mathcal{M}_2$, and so on (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
-  \label{fig:overview}
-\end{figure*}
+%  \label{fig:overview}
+%\end{figure*}
 
@@
 Current generic planning solutions for outdoor UAVs do not plan path and computations dynamically, nor are energy-aware.
-They are often semi-autonomous; the plan is static and usually defined using planning software~\cite{daponte2019review}.
+They are often semi-autonomous; the plan--the path and computations--is static and usually defined using planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
@@
 We refer to both as parameters.
-We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets.
-Again, we refer to both as parameters sets.
+We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets, and to both as parameters sets.
 There can be multiple or none computations sets per each task, and the same applies to the TEE.
@@
 We propose some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information in the Appendix~\ref{app:proof-eqv} and examples in the Appendix~\ref{app:simulator}.
+Finally, we provide some additional information and examples in the Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.
 
@@
 
-Let us suppose the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
+Let us further assume the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
 We then express the TEE as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the TEE parameters which returns a metric of the distance between the point and the nominal trajectory.
-We express and the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}), and the of the computations parameters in Subsection~\ref{sec:computations-model}.
-
-Let us further adopt the following mathematical notation.
-$[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, $c^0$ the optimal value of parameter $c$,and $\underline{c},\overline{c}$ its lower and upper bound retrieved from a plan specification.
-The plan specification is a file which specifies all the stages and triggering points along the plan.
-We discuss the format in Subsection~\ref{sec:plan}.
-Moreover, we use the notation $c_{i,j}$ to specify the $j$-th item of the $i$-th parameters set $c_i$.
+We express the computations as the value of the computations parameters.
+We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}), and of the computations parameters in Subsection~\ref{sec:computations-model}.
+
+Let us adopt the following mathematical notation.
+Given an integer $a$, $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$.
+$c_{i,j}$ specifues the $j$-th parameter of the $i$-th parameters set $c_i$.
+$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$, and $\underline{c_{i,j}},\overline{c_{i,j}}$ its lower and upper bounds.
+We store these bounds in the plan specification, which format we discuss in Subsection~\ref{sec:plan}.
+The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list of $n$ parameters.
 
@@
 some inertial navigation frame $\mathcal{O}_W$.
-We note that while the TEE can differ for each stage, the tasks remain the same.
-However, the user can inhibit or enable a computation varying its computation set.
 
@@
 The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+\end{defn}
 
@@
 The UAV remains in the stage with any generic point $\mathbf{p}_k$.
-It eventually enters the stage $\Gamma_{i+1}$ with the triggerint point $\mathbf{p}_i$ and so on, until it reaches the last triggering point.
-
-  The algorithm takes as input the plan, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation.
+It eventually enters the stage $\Gamma_{i+1}$ with the triggerint point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
+
+The algorithm takes as input the plan and some initial guesses that are necessary for the position and energy estimation.
 It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
-\end{defn}
 
@@
 
-We specify the stages $\bigcup_i{\Gamma_i}$, triggering points $\bigcup_i\mathbf{p}_{\Gamma_i}$, and the plan $\Gamma$ using a specific file format--the plan specification.
-We refer the reader to Appendix~\ref{app:plan-example} for an example.
-
-The first stage $\Gamma_1$ is specified as the first line of the file
+The algorithm reads the plan $\Gamma$ using a specific file format--the plan specification. We refer the reader to Appendix~\ref{app:plan-example} for an example.
+
+The first stage $\Gamma_1$ is expressed in the first line of the file
 \begin{algorithmic}[1]
@@
 The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
-The coordinates can be expressed in function of the TEE parameters $c_1$.
-Generally, one can express the coordinates in function of any TEE parameters $c_i$, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
+The coordinates can be expressed in function of the TEE parameters $c_{1,1},\dots,c_{1,\rho}$.
+Generally, one can express the coordinates in function of the $i$-th TEE parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous TEE parameters, propagating the information therein if necessary.
+See Figure~\ref{fig:state-machine2} where we neglected the $\sigma=0$ computations parameters for simplicity $c_i=c_{i,1},\dots,c_{i,\rho}$.
 
@@
 
-We refer the reader to the example in Appendix~\ref{app:plan-example} for a detailed implementation.
+We refer the reader again to the example in Appendix~\ref{app:plan-example} for a detailed implementation.
 In the example, the first TEE parameter is propagated to all the following TEEs and triggering points.
@@
   \setcounterref{ALG@line}{code:trigger-pt}
-  \State\textbf{\texttt{[$\underline{c}_i$,$\overline{c}_i$]}}\label{code:parameter-set}
+  \State\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
 \end{algorithmic}
-specifies the lower $\underline{c}_i$ and upper $\overline{c}_i$ bound of the $i$-th parameter set.
+specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bound of the $j$-th parameter set.
 They are in ascending order and the TEE parameters sets are specified before the computations parameters sets.
@@
 
-Let us assume the set
+Let us assume that the set
 \begin{equation}\label{eq:area}
@@
 \end{equation}
-delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
-Phisically, $\varphi_i$ is s function of the two coordinates and is satisfied when a point $\mathbf{p}_k$ is on the TEE.
+delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using the TEE parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
+$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the TEE.
 Physically, this means the UAV is flying exactly over the nominal trajectory.
@@
 They are a way to alter the nominal trajectory in the initial plan.
-
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $\mathbf{c}_i^0$, so $\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
-It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and deriving the direction to follow in the form of velocity vector
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $c_i^0$ (here we again neglect the $\sigma=0$ computations parameters for simplicity), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+
+We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and the direction to follow in the form of velocity vector
 \begin{equation}\label{eq:pd}
@@
 
-% fixed up to here!
-% idea; write control as parameters; write B as time-dependent, which multiplied TEE parameters gives energy due to trajectory (approx). By computations due to computations (from powprof).
-
 \subsection{State: energy $\mathbf{q}$}
@@
 We refer to the instantaneous energy consumption evolution simply as energy signal.
-The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and decomposes the evolution in energy due to the path and computations.
+The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series).
+Here we derive the energy model.
+Later we assess the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
 This approach is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
-We show a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}, but the two are different.
+We show a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}.
 We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
@@
 We use extensively the following assumption for the purpose of energy signal modeling.
-\begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
+\begin{assm}[Energy signal periodicity]\label{assm:periodic} 
 Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
@@
 
-Physically this means that the time evolution of the instantaneous energy consumption is assumed to be approximately periodic.
+Physically this means that the energy signal is assumed to be approximately periodic.
 
@@
 The equivalence of the models is trivial and the equality of the two signals is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
-We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof of the equality.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof of the equality where we justify the choices of the items of the matrices and of the initial guess.
 \end{proof}
@@
 We use the forward Euler approximation with a small enough value of the time step $\Delta t$.
-One can guarantee to have the same outputs rather than an approximation with $A=e^{At}$.
-
-Let us suppose that at time instant $k$ the plan reached $i$-th stage. The control along with the input matrix
+We note that one can guarantee to have the same outputs rather than an approximation with $A_d:=e^{At}$.
+
+Let us suppose that at time instant $k$ the plan reached $i$-th stage $\Gamma_i$. The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}
@@
 
-Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
-For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{0,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\nu_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
 The first $\rho$ gain factors quantifies the contribution of the $i$-th TEE parameters.
@@
 
-\subsection{Energy evolution due to computations}
+Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
+For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{0,1}$--the radius of the circle--adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption $\nu_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
+
+\subsection{Computations parameters energy contribution}
 \label{sec:computations-model}
 
-The energy cost of the computations (the set of tasks being executed on an embedded board on the UAV) is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
-The tool measures the instantaneous computational energy consumption of software components within the QoS sets.
-It builds an energy model: a linear interpolation, one per each task.
-In a ROS based system, it requires the user to implement one or more ROS nodes changing the computational load by node-specific ROS parameters.
-The approach has been tested in simulation in our previous work~\cite{zamanakos2020energy}.
-
-Specifically, the mission $\mathcal{M}$ contains a set of ordered lists with tasks (recall Definition~\ref{def:mission}).
-These tasks are implemented by software components (such as ROS nodes in a ROS based system) $\Psi(\mathbf{s}_i):=\langle\psi_1(s_{i,1}),\dots,\psi_\sigma(s_{i,\sigma})\rangle$.
-They input the desired and output the actual computations
-\begin{equation}\label{eq:qos-def}
-  \mathbf{s}_i:=\left\{\langle s_{i,1},\dots ,s_{i,\sigma}\rangle\mid \psi_j(s_{i,j})\in\mathbb{S}_{i}\,\forall j\in[\sigma]^+\right\},
+Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computations parameters which characterize the computations.
+We assess the energy cost of these computations using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
+We assume the UAV carries an embedded board that runs the computations.
+The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations sets and builds an energy model: a linear interpolation, one per each computation.
+
+Specifically, the computations are implemented by software components, such as ROS nodes in a ROS based system.
+The user implements these nodes such that they change the computational load by node-specific ROS parameters--the computations parameters.
+For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and it changes the detection frequency.
+We note that while the TEE can differ for each stage, the tasks remain the same.
+However, the user can inhibit or enable a computation varying its computation set.
+
+Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
+\begin{equation}\label{eq:energy-comp}
+  \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}^T=\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix}/\begin{bmatrix}c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}.
 \end{equation}
-where $s_{i,j}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $j$-th desired computation at stage $i$, $\mathbf{s}_i\in\mathbb{S}_i\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the union of all QoS sets given $\mathbb{S}_i:=\bigcup_{j\in[\sigma]^+}{\mathbb{S}_{i,j}}$.
-
-For instance, if the task $\psi_1$ is a CNN object detector, $s_{1,1}$ corresponds to the computation frames-per-second (fps) rate changing the detection frequency.
-The algorithm outputs the control input which contains the desired fps rate $s_{1,1}\in\mathbb{S}_{1,1}$.
-The task $\psi_1(s_{1,1})$ outputs the actual fps rate $s_{k,1}$ which might differ from the desired one (e.g., the CNN object detector might not be able to reach a high fps rate with the current computational resources).
-
-Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
-\begin{equation}\label{eq:energy-comp}\begin{split}
-  y_k^s:=g\left(\Psi(\mathbf{s}_i)\right)=g\left(\mathbf{s}_{k}\right).\\
-\end{split}\end{equation}
 Moreover, let $g(\{\emptyset\})$ be zero.
+
+\leavevmode\thispagestyle{empty}\newpage
+\leavevmode\thispagestyle{empty}\newpage
 
@@
 
-\leavevmode\thispagestyle{empty}\newpage
-
 \appendices

### 2020-12-02 icra-2021.tex
fixing the figures
fixes to the text

@@
 
-%\begin{figure*}[t]
-%  \centering
-%  \input{\figpath/icra-2021_overview2.tikz}
-%  \caption{The mission consists of circles and lines covering a polygon.
-The UAV heads to $\varphi_0$ initially, using the desired velocity vector $\dot{\mathbf{p}}_d$.
-It later heads to $\varphi_0^-$ reducing the radius $c_{0,1}$ to satisfy the battery constraints.
-The UAV then converges to $\varphi_1$ in stage $\mathcal{M}_1$, $\varphi_2$ in stage $\mathcal{M}_2$, and so on (the circle $\varphi_2$ is not visible in the figure; it connects $\varphi_1$ and $\varphi_3$).}
-%  \label{fig:overview}
-%\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%
@@
 We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory.
-The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}.
+The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
 We denote the trajectory with a mathematical function that we refer to as the trajectory explicit equation (TEE).
@@
 We refer to both as parameters.
-We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets, and to both as parameters sets.
-There can be multiple or none computations sets per each task, and the same applies to the TEE.
+We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE set and computations sets, and to both as parameters sets.
+There can be multiple or none computations parameters per each task, and the same applies to the TEE.
+There is one TEE set but multiple computations sets, one per each computation parameter.
 Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
@@
 We propose some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information and examples in the Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.
+Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.
 
@@
 
-We assume that a user-specified initial plan consists of different stages. At each stage, the UAV must follow the TEE within TEE sets and do the computations within the computations sets.
-
-Let us further assume the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
-We then express the TEE as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the TEE parameters which returns a metric of the distance between the point and the nominal trajectory.
+The algorithm takes as input a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation.
+At each stage, the UAV must follow the TEE within TEE set and do the computations within the computations sets.
+The algorithm outputs the new position, the instantaneous energy consumption, and the control.
+
+Let us assume the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
+We then express the TEE as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the TEE parameters.
+The TEE returns a metric of the distance between the point and the nominal trajectory.
 We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}), and of the computations parameters in Subsection~\ref{sec:computations-model}.
+We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}, and of the computations parameters in Subsection~\ref{sec:computations-model}.
 
@@
 $c_{i,j}$ specifues the $j$-th parameter of the $i$-th parameters set $c_i$.
-$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$, and $\underline{c_{i,j}},\overline{c_{i,j}}$ its lower and upper bounds.
+$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
 We store these bounds in the plan specification, which format we discuss in Subsection~\ref{sec:plan}.
@@
 
-\begin{defn}[Stage, plan and triggering point]\label{def:mission}
+\begin{defn}[Stage, plan, and triggering point]\label{def:mission}
   A \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
@@
   \end{tikzpicture}
-  \caption{Finite state machine of the plan}
+  \caption{The plan defined as a finite state machine}
   \label{fig:state-machine}
@@
 
-A slice of a finite state machine in Figure~\ref{fig:state-machine} shows the transition between the stages.
-The triggering point $\mathbf{p}_{i-1}$ allows the transition to stage $\Gamma_i$.
+A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages.
+The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to stage $\Gamma_i$.
 The UAV remains in the stage with any generic point $\mathbf{p}_k$.
@@
 
-The algorithm takes as input the plan and some initial guesses that are necessary for the position and energy estimation.
-It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
-
 \subsection{Plan specification file format}
@@
 
-The algorithm reads the plan $\Gamma$ using a specific file format--the plan specification. We refer the reader to Appendix~\ref{app:plan-example} for an example.
+The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format. We refer the reader to Appendix~\ref{app:plan-example} for an example.
 
@@
 where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the TEE.
-We refer the reader to the next subsection where we discuss the physical meaning of the convergence value and rotation.
+In the next subsection where we discuss the physical meaning of the convergence value and rotation.
 The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
@@
 Generally, one can express the coordinates in function of the $i$-th TEE parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous TEE parameters, propagating the information therein if necessary.
-See Figure~\ref{fig:state-machine2} where we neglected the $\sigma=0$ computations parameters for simplicity $c_i=c_{i,1},\dots,c_{i,\rho}$.
+See Figure~\ref{fig:state-machine2} where, for simplicity, we neglected the $\sigma=0$ computations parameters $c_i=c_{i,1},\dots,c_{i,\rho}$.
 
@@
   \center
-  \begin{tikzpicture}[shorten >=1pt,node distance=24ex,on grid,auto] 
+  \begin{tikzpicture}[shorten >=1pt,node distance=23ex,on grid,auto] 
     \node        (q_dots0) {$\cdots$};
-    \node[state] (q_0) [right=of q_dots0] {$\langle\varphi_i,c_i\rangle$};
+    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
     \node        (q_dots1) [right=of q_0] {$\cdots$};   
@@
 
-The following $\rho+\sigma$ lines
+The line
 \begin{algorithmic}[1]
   \setcounterref{ALG@line}{code:trigger-pt}
+  \State\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
+\end{algorithmic}
+specifies the lower $\underline{c}_{1}$ and upper $\overline{c}_{1}$ bounds of the TEE $\varphi_1$.
+
+The following $\sigma$ lines
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:tee-set}
   \State\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
 \end{algorithmic}
-specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bound of the $j$-th parameter set.
-They are in ascending order and the TEE parameters sets are specified before the computations parameters sets.
+specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bounds of the $j$-th computation parameter set. They are in ascending order.
+
+This means that for the first stage, the algorithm can alter the TEE satisfying $\varphi_1\in\mathbb{C}_1$, and it can alter the computations individually.
+In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.
 
@@
 They are a way to alter the nominal trajectory in the initial plan.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $c_i^0$ (here we again neglect the $\sigma=0$ computations parameters for simplicity), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
-
-We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and the direction to follow in the form of velocity vector
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+
+We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector
 \begin{equation}\label{eq:pd}
@@
 
+\begin{figure}[h]
+  \centering
+  \input{\figpath/path2.tikz}
+  \caption{Example of the alteration of a TEE parameter}
+  \label{fig:overview}
+\end{figure}
+
 \subsection{State: energy $\mathbf{q}$}
@@
 We model the energy using some energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
-We refer to the instantaneous energy consumption evolution simply as energy signal.
+We refer to the instantaneous energy consumption evolution simply as the energy signal.
 The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series).
-Here we derive the energy model.
-Later we assess the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
-This approach is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
-
-We show a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}.
+We enhance the energy model with the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
+
+We proof a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}.
 We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the signal, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
@@
 \end{split}\end{equation}
-where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
+where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption, and $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are the contributions of the noice.
+
+The state $\mathbf{q}$ are the energy coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
@@
 where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros.
-
-\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are zeros) and the control is zero.
+In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros.
+
+\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w},v$ are zeros) and the control is zero.
 Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$.
-Then Equation~(\ref{eq:fourier}) describes the same signal as Equation~(\ref{eq:state-perf}).
+Then, the signal $h$ in Equation~(\ref{eq:fourier}) is equal to the signal $y$ in Equation~(\ref{eq:state-perf}).
 \end{lem}
@@
 
-Let us suppose that at time instant $k$ the plan reached $i$-th stage $\Gamma_i$. The control along with the input matrix
+Let us suppose that at time instant $k$ the plan reached the $i$-th stage $\Gamma_i$.
+
+The control along with the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}
@@
 They are later refined by the algorithm.
-The following $\sigma$ gain factors quantifies the contribution of the $i$-th computations parameters.
+The following $\sigma$ gain factors quantifies the contribution of the computations parameters.
 They are derived using the modeling tool.
@@
 Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
-For instance, when the TEE $\varphi_0$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{0,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\nu_{0,1}(c_{0,1}-c_{0,1}^-)<0$.
+For instance, when the TEE $\varphi_1$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$.
 
@@
 Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computations parameters which characterize the computations.
-We assess the energy cost of these computations using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}.
+We assess the energy cost of these computations using \powprof{}, the open-source modeling tool.
+The tool is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+
 We assume the UAV carries an embedded board that runs the computations.
@@
 Specifically, the computations are implemented by software components, such as ROS nodes in a ROS based system.
-The user implements these nodes such that they change the computational load by node-specific ROS parameters--the computations parameters.
+The user implements these in the following fashion.
+They change the computational load by node-specific ROS parameters--the computations parameters.
+In a generic software component system, the computational load is mapped to arguments.
+In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
 For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and it changes the detection frequency.
@@
 
-Let us further define $g:\mathbb{Z}_{\geq 0}^{\sigma}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
+Let us further define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
 \begin{equation}\label{eq:energy-comp}

### 2020-12-09 icra-2021.tex
added illustrative abstract
changes in the intro

@@
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
+\usepackage{pifont}
 
@@
 For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
-We refer to the computational tasks that can be dynamically replanned as computations.
-We are interested in energy-aware dynamic planning, which would find optimal tradeoffs between the path, computations, and energy requirements.
-Current generic planning solutions for outdoor UAVs do not plan path and computations dynamically, nor are energy-aware.
-They are often semi-autonomous; the plan--the path and computations--is static and usually defined using planning software~\cite{daponte2019review}.
+We refer to such computational tasks that can be dynamically replanned and adapted as \emph{computations}.
+We are interested in the energy optimization of the path and computations under uncertainty and refer to it as energy-aware dynamic planning.
+Such planning would find optimal tradeoffs between the path, computations, and energy requirements.
+Current generic planning solutions for outdoor UAVs do not plan the path and computations dynamically, nor are they energy-aware.
+They are often semi-autonomous: the plan (the path and computations) is static and usually defined using planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
@@
 Generally, the algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}.
-However, they apply to a small number of robots~\cite{kim2005energy}, and focus exclusively on planning the trajectory for these robots~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being significantly influenced by computations~\cite{mei2005case}.
+However, they apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being significantly influenced by computations~\cite{mei2005case}.
 Given the availability of powerful GPU-equipped mobile hardware~\cite{rizvi2017general}, the use of computations is expected to increase in the near future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
@@
 
+\begin{figure}[t]
+  \centering
+  \input{\figpath/il_abstract.tikz}
+  \caption{Illustrative abstract. An initial plan is replanned in terms of both the path and computations.}
+  \label{fig:il-abs}
+\end{figure}
+
 Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations.
-We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory.
-The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
-We denote the trajectory with a mathematical function that we refer to as the trajectory explicit equation (TEE).
-The path is composed of multiple TEEs.
-We express the computations with a modeling tool presented in our previous work~\cite{seewald2019coarse}.
-The algorithm alters the TEE and computations within some parameters using output model predictive control (MPC).
-These parameters are the maximum, minimum, and current levels of the TEE and computations.
-The user specifies the parameters in an initial plan with an energy budget.
+We present here a brief summary of the algorithm.
+The user specifies the maximum, minimum, and current levels of some parameters relative to the path and computations in an initial plan with an energy budget.
+In Figure~\ref{fig:il-abs}, there are two parameters.
+The radius of the trajectory circle is relative to the trajectory.
+The quality of image detection is relative to the computations.
+The algorithm replans the initial plan within the constraints and the energy budget using output model predictive control (MPC).
 The energy budget is the battery capacity and some other battery parameters.
-In the remainder of the paper, we adopt the following notation.
-We refer to the current TEE and computations parameters simply as TEE and computations parameters.
-We refer to both as parameters.
-We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE set and computations sets, and to both as parameters sets.
-There can be multiple or none computations parameters per each task, and the same applies to the TEE.
-There is one TEE set but multiple computations sets, one per each computation parameter.
 Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
@@
 These are fixed values that are not replanned by the algorithm.
+To model the path we use multiple trajectories and denote each of them with a mathematical function.
+In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
+To model the computations we use a profiling tool presented in previous work~\cite{seewald2019coarse}.
+To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
+The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
 
@@
 We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
-Periodicity is often present due to the path and computations repetitive patterns~\cite{seewald2020mechanical}.
-Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
-Given that the plan is periodic, we expect the energy to approximately evolve periodically.
-The observation applies broadly; we show different UAV scenarios with periodic energy signals. Moreover, we briefly investigate such signals in some ground-based mobile robots.
+Periodicity is often present due to repetitive patterns in the plan~\cite{seewald2020mechanical}.
+Indeed, UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
+Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
+The observation applies broadly; we show different UAV scenarios that can produce such periodic energy signals (evolutions of the energy consumption).
+Moreover, we briefly investigate such signals in some ground-based mobile robots.
 
@@
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:overview} shows an initial slice of such a plan.
-The UAV first heads to a circular TEE with a given radius, which is later reduced as, e.g., windy weather requires the adjustment of the control input to avoid battery depletion.
-Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations (see Section~\ref{sec:experimental}).
+Figure~\ref{fig:il-abs} shows an initial slice of such a plan.
+Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}).
 
@@
 The algorithm takes as input a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation.
-At each stage, the UAV must follow the TEE within TEE set and do the computations within the computations sets.
+At each stage, the UAV must follow the trajectory within the trajectory constraints set and do the computations within the computations constraints sets.
+There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
+We refer to these omitting sets in the remainder of the paper.
 The algorithm outputs the new position, the instantaneous energy consumption, and the control.
@@
 
+\begin{figure}[h]
+  \centering
+  \input{\figpath/path2.tikz}
+  \caption{Example of the alteration of a TEE parameter}
+  \label{fig:tee1}
+\end{figure}
+
 We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.
@@
 \end{equation}
-delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using the TEE parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).
+delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using the TEE parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
 $\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the TEE.
@@
 where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:overview}).
-
-\begin{figure}[h]
-  \centering
-  \input{\figpath/path2.tikz}
-  \caption{Example of the alteration of a TEE parameter}
-  \label{fig:overview}
-\end{figure}
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
 
@@
 
-\leavevmode\thispagestyle{empty}\newpage
 \leavevmode\thispagestyle{empty}\newpage

### 2020-12-09 icra-2021.tex
changes to the structure to comply with the data-driven control approach Hector suggested

@@
 There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
-We refer to these omitting sets in the remainder of the paper.
 The algorithm outputs the new position, the instantaneous energy consumption, and the control.
 
-Let us assume the TEE at stage $i$ can be altered with $\rho$ TEE parameters and the computations with $\sigma$ computations parameters.
-We then express the TEE as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the TEE parameters.
-The TEE returns a metric of the distance between the point and the nominal trajectory.
+Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters and the computations with $\sigma$ computations parameters.
+We then express the trajectory as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the trajectory parameters.
+The function returns a metric of the distance between the point and the nominal trajectory.
 We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of TEE parameters in Subsection~\ref{sec:model}, and of the computations parameters in Subsection~\ref{sec:computations-model}.
+We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and the computations parameters in Subsection~\ref{sec:computations-model}.
 
@@
 Given an integer $a$, $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$.
-$c_{i,j}$ specifues the $j$-th parameter of the $i$-th parameters set $c_i$.
-$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
-We store these bounds in the plan specification, which format we discuss in Subsection~\ref{sec:plan}.
+$c_{i,j}$ specifies the $j$-th parameter of the $i$-th parameters set $c_i$.
+$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$ w.r.t.
+a given cost function $l$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
+We store these bounds in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
 The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list of $n$ parameters.
@@
   \end{split}\end{equation}
-  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the TEE set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation set.
+  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation set.
 $\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
@@
 
-\subsection{Plan specification file format}
-\label{sec:plan}
-
-The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format. We refer the reader to Appendix~\ref{app:plan-example} for an example.
-
-The first stage $\Gamma_1$ is expressed in the first line of the file
-\begin{algorithmic}[1]
-  \State\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
-\end{algorithmic}
-where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the TEE.
-In the next subsection where we discuss the physical meaning of the convergence value and rotation.
-The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
-
-The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
-\begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:stage}
-  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
-\end{algorithmic}
-where $x$ and $y$ are the two coordinates of the point.
-The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
-The coordinates can be expressed in function of the TEE parameters $c_{1,1},\dots,c_{1,\rho}$.
-Generally, one can express the coordinates in function of the $i$-th TEE parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous TEE parameters, propagating the information therein if necessary.
+Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
 See Figure~\ref{fig:state-machine2} where, for simplicity, we neglected the $\sigma=0$ computations parameters $c_i=c_{i,1},\dots,c_{i,\rho}$.
@@
 
-We refer the reader again to the example in Appendix~\ref{app:plan-example} for a detailed implementation.
-In the example, the first TEE parameter is propagated to all the following TEEs and triggering points.
-
-The line
-\begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:trigger-pt}
-  \State\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
-\end{algorithmic}
-specifies the lower $\underline{c}_{1}$ and upper $\overline{c}_{1}$ bounds of the TEE $\varphi_1$.
-
-The following $\sigma$ lines
-\begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:tee-set}
-  \State\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
-\end{algorithmic}
-specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bounds of the $j$-th computation parameter set. They are in ascending order.
-
-This means that for the first stage, the algorithm can alter the TEE satisfying $\varphi_1\in\mathbb{C}_1$, and it can alter the computations individually.
-In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.
-
-Follows the entries for stage $\Gamma_2$ (equivalent to lines~\ref{code:stage}--\ref{code:parameter-set}), $\Gamma_3$ and so on, until the last stage.
-We assume that the last triggering point is the final UAV position.
+We refer the reader to an example in Appendix~\ref{app:plan-example} for a detailed implementation.
+In the example, the first trajectory parameter is propagated to all the following trajectories and triggering points.
 
@@
   \input{\figpath/path2.tikz}
-  \caption{Example of the alteration of a TEE parameter}
+  \caption{Example of the alteration of a trajectory parameter}
   \label{fig:tee1}
@@
 \end{equation}
-delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using the TEE parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
-$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the TEE.
+delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
+$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory.
 Physically, this means the UAV is flying exactly over the nominal trajectory.
-The TEE parameters allows to change the TEE.
+The trajectory parameters allows to change the trajectory.
 They are a way to alter the nominal trajectory in the initial plan.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
 
@@
 
-The first $\rho$ gain factors quantifies the contribution of the $i$-th TEE parameters.
+The first $\rho$ gain factors quantifies the contribution of the $i$-th trajectory parameters.
 A first guess of these parameters is derived empirically.
@@
 Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
-For instance, when the TEE $\varphi_1$ is a circle (see Figure~\ref{fig:overview}), a decrement in the TEE parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
+For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
 It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$.
@@
 For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and it changes the detection frequency.
-We note that while the TEE can differ for each stage, the tasks remain the same.
+We note that while the trajectory can differ for each stage, the tasks remain the same.
 However, the user can inhibit or enable a computation varying its computation set.
@@
 
+\leavevmode\thispagestyle{empty}\newpage
 \leavevmode\thispagestyle{empty}\newpage
@@
 
+\section{Plan Specification Format}
+\label{app:plan-spec}
+
+The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format. We refer the reader to Appendix~\ref{app:plan-example} for an example.
+
+The first stage $\Gamma_1$ is expressed in the first line of the file
+\begin{algorithmic}[1]
+  \State\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
+\end{algorithmic}
+where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the trajectory.
+In the next subsection where we discuss the physical meaning of the convergence value and rotation.
+The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
+
+The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:stage}
+  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
+\end{algorithmic}
+where $x$ and $y$ are the two coordinates of the point.
+The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
+The coordinates can be expressed in function of the trajectory parameters $c_{1,1},\dots,c_{1,\rho}$.
+
+The line
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:trigger-pt}
+  \State\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
+\end{algorithmic}
+specifies the lower $\underline{c}_{1}$ and upper $\overline{c}_{1}$ bounds of the trajectory $\varphi_1$.
+
+The following $\sigma$ lines
+\begin{algorithmic}[1]
+  \setcounterref{ALG@line}{code:tee-set}
+  \State\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
+\end{algorithmic}
+specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bounds of the $j$-th computation parameter set. They are in ascending order.
+
+This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$, and it can alter the computations individually.
+In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.
+
+Follows the entries for stage $\Gamma_2$, $\Gamma_3$ and so on, until the last stage. We assume that the last triggering point is the final UAV position.
+
 \section{Plan Specification Example}
@@
 The plan has a variable number of entries per each stage.
-We plan the mission in Figures~\ref{fig:overview},~\ref{fig:trajectory}.
+We plan the mission in Figures~\ref{fig:il-abs},~\ref{fig:trajectory}.
 The first line
@@
 In fact, the rotation matrix $E$ points upwards in the space.
-It guides the UAV in the counter-clockwise direction (see Figure~\ref{fig:overview}; the UAV is traveling counter-clockwise).
+It guides the UAV in the counter-clockwise direction (see Figure~\ref{fig:tee1}; the UAV is traveling counter-clockwise).
 The rotation matrix $-E$ points downwards and guides the UAV in the clockwise direction.
@@
 The other TEEs ($\varphi_1,\varphi_2,\varphi_3$) displacement alters the distance between the lines in the survey.
-A familiar pattern from Figure~\ref{fig:overview}.
+A familiar pattern from Figure~\ref{fig:tee1}.
 For simplicity, we suppose line~\ref{code:triggerlast} describes the last point of the mission.

### 2020-12-09 icra-2021.tex
changes ... (2)

@@
 
+\leavevmode\thispagestyle{empty}\newpage
 \leavevmode\thispagestyle{empty}\newpage % just for now
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{IEEEtran}
 \bibliography{\jobname}
+
+\leavevmode\thispagestyle{empty}\newpage
+\leavevmode\thispagestyle{empty}\newpage
 
@@
 
-\section{Plan Specification Format}
+\section{Plan Specification}
+
+\subsection{Format}
 \label{app:plan-spec}
@@
 
-This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$, and it can alter the computations individually.
+This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$.
+It can alter the computations individually.
 In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.
 
-Follows the entries for stage $\Gamma_2$, $\Gamma_3$ and so on, until the last stage. We assume that the last triggering point is the final UAV position.
-
-\section{Plan Specification Example}
+Follows the entries for stage $\Gamma_2$ (equivalent to lines~\ref{code:stage}--\ref{code:parameter-set}), $\Gamma_3$ and so on, until the last stage.
+We assume that the last triggering point is the final UAV position.
+
+\subsection{Example}
 \label{app:plan-example}
+
 We discuss how to specify an initial mission plan with an example of a survey mission.
@@
 
-\section{Components Specification Format}
-
-*
-
 \section{Simulator}

### 2020-12-10 icra-2021.tex
consistency fixes and typos to the text

@@
 A typical example of these scenarios is a UAV flying a path and performing some on-board computational tasks.
-For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction.
+For instance, the UAV might detect ground patterns and notify other ground-based actors with little human interaction.
 We refer to such computational tasks that can be dynamically replanned and adapted as \emph{computations}.
-We are interested in the energy optimization of the path and computations under uncertainty and refer to it as energy-aware dynamic planning.
+We are interested in the energy optimization of the path and computations under uncertainty (atmospheric interferences) and refer to it as energy-aware dynamic planning.
 Such planning would find optimal tradeoffs between the path, computations, and energy requirements.
 Current generic planning solutions for outdoor UAVs do not plan the path and computations dynamically, nor are they energy-aware.
-They are often semi-autonomous: the plan (the path and computations) is static and usually defined using planning software~\cite{daponte2019review}.
+They are often semi-autonomous: the path and computations are static and usually defined using planning software~\cite{daponte2019review}.
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
@@
 More complex planning, which includes a broader concept of the plan being a set of tasks and a path, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-For UAVs specifically, rotorcrafts have gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
+For UAVs specifically, rotorcrafts have also gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
 
@@
 We present here a brief summary of the algorithm.
+To model the path we use multiple trajectories and denote each of them with a mathematical function.
+In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
+To model the computations we use a profiling tool presented in previous work~\cite{seewald2019coarse}.
 The user specifies the maximum, minimum, and current levels of some parameters relative to the path and computations in an initial plan with an energy budget.
@@
 These are fixed values that are not replanned by the algorithm.
-To model the path we use multiple trajectories and denote each of them with a mathematical function.
-In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
-To model the computations we use a profiling tool presented in previous work~\cite{seewald2019coarse}.
 To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
@@
 
-To achieve the energy-aware dynamic planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference).
+To achieve the energy-aware dynamic planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty.
 We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
@@
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
-The observation applies broadly; we show different UAV scenarios that can produce such periodic energy signals (evolutions of the energy consumption).
-Moreover, we briefly investigate such signals in some ground-based mobile robots.
+The observation applies broadly; we show different UAV scenarios that can produce such periodic energy consumption evolution.
+Moreover, we briefly investigate periodic energy consumption evolution in some ground-based mobile robots.
 
@@
 Trajectory-wise, the UAV flies in circles and lines covering a polygon.
-Computationally-wise, it detects obstacles using a convolutional neural network (CNN) and informs grounded mobile robots employed for harvesting.
+Computationally-wise, it detects obstacles using a convolutional neural network (CNN) and notifies grounded mobile robots employed for harvesting.
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:il-abs} shows an initial slice of such a plan.
+Figure~\ref{fig:il-abs} shows a slice of such a plan.
 Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}).
@@
 There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
-The algorithm outputs the new position, the instantaneous energy consumption, and the control.
+The algorithm outputs the new position, the instantaneous energy consumption, and the control (the parameters).
 
@@
 We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and the computations parameters in Subsection~\ref{sec:computations-model}.
+We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
 
@@
 a given cost function $l$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
-We store these bounds in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
 The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list of $n$ parameters.
@@
   \end{split}\end{equation}
-  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation set.
+  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraints set.
 $\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
@@
 
-  The \emph{plan} is a finite state machine $\Gamma$ where the state-transition function $\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage.
+  The \emph{plan} is a finite state machine $\Gamma$ where the state-transition function $\delta:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+  \begin{equation*}\delta(\Gamma_i,\mathbf{p}_k):=\begin{cases}
+    \Gamma_{i+1} & \text{if }\mathbf{p}_k=\mathbf{p}_{\Gamma_i}\\
+    \Gamma_i & \text{otherwise}
+  \end{cases}.\end{equation*}
   The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
@@
     (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_1)    
-    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
+    (q_0) edge [loop above] node {$\mathbf{p}_{k_1}$} (q_0)
     (q_1) edge node {$\mathbf{p}_{\Gamma_{i+1}}$} (q_dots1)
-    (q_1) edge [loop above] node {$\mathbf{p}_{k}$} (q_1)
+    (q_1) edge [loop above] node {$\mathbf{p}_{k_2}$} (q_1)
     ; %end path 
@@
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to stage $\Gamma_i$.
-The UAV remains in the stage with any generic point $\mathbf{p}_k$.
+The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$ and $\mathbf{p}_{k_2}$.
 It eventually enters the stage $\Gamma_{i+1}$ with the triggerint point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
@@
 Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
-See Figure~\ref{fig:state-machine2} where, for simplicity, we neglected the $\sigma=0$ computations parameters $c_i=c_{i,1},\dots,c_{i,\rho}$.
+See Figure~\ref{fig:state-machine2} where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
 
@@
 
+We store the plan in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
+
 \subsection{State: position $\mathbf{p}$}
 \label{sec:model}
+
+We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.
 
@@
   \input{\figpath/path2.tikz}
-  \caption{Example of the alteration of a trajectory parameter}
+  \caption{Illustrative example of the alteration of a trajectory parameter}
   \label{fig:tee1}
 \end{figure}
-
-We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.
 
@@
 where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
 
@@
 The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series).
-We enhance the energy model with the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
 
@@
 
-Let us consider a periodic signal of period $T\in\mathbb{Z}_{> 0}$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
+Once we illustrate the energy model, we enhance it with the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
+
+Let us consider a periodic signal of period $T\in\mathbb{R}_{> 0}$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
 \begin{equation}\label{eq:fourier}
@@
 Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
-\begin{equation}
-  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2].
-\end{equation}
+\begin{equation*}
+  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2],
+\end{equation*}
+for a small enough set $\mathbb{E}$.
 \end{assm}
@@
 \end{split}\end{equation}
-where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption, and $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are the contributions of the noice.
+where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption, and $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are the contributions of the uncertainty.
 
@@
 For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$.
+It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$, for a given $\nu_{1,1}\in\mathbb{R}_{<0}$.
 
@@
 Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computations parameters which characterize the computations.
-We assess the energy cost of these computations using \powprof{}, the open-source modeling tool.
-The tool is adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+We assess the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
 We assume the UAV carries an embedded board that runs the computations.
-The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations sets and builds an energy model: a linear interpolation, one per each computation.
+The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations constraints sets and builds an energy model: a linear interpolation, one per each computation.
 
 Specifically, the computations are implemented by software components, such as ROS nodes in a ROS based system.
-The user implements these in the following fashion.
-They change the computational load by node-specific ROS parameters--the computations parameters.
-In a generic software component system, the computational load is mapped to arguments.
+The user implements these nodes s.t.
+they change the computational load by node-specific ROS parameters--the computations parameters.
+In a generic software component system, the user maps the computational load to the arguments.
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and it changes the detection frequency.
-We note that while the trajectory can differ for each stage, the tasks remain the same.
-However, the user can inhibit or enable a computation varying its computation set.
-
-Let us further define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using \powprof{}
+For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and the tool changes the detection frequency to build a model.
+The model is then a linear multivariate interpolation for all the parameters.
+
+We note that while the trajectory can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation set.
+
+Let us further define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool.
+
+The gain factors that quantifies the contribution of the computations parameters
 \begin{equation}\label{eq:energy-comp}

### 2020-12-10 icra-2021.tex
re-written certain sections to be complaint with the data-driven control approach

@@
 The remainder of the paper is organized as follows.
-The overview of dynamic planning is provided in Section~\ref{sec:prob}, along with a suitable model for the position and energy.
+The overview of dynamic planning is provided in Section~\ref{sec:prob}, and a suitable model for the energy in Section~\ref{sec:energy-model}.
 The algorithm is proposed in Section~\ref{sec:algo}.
@@
 
-The algorithm takes as input a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation.
-At each stage, the UAV must follow the trajectory within the trajectory constraints set and do the computations within the computations constraints sets.
+The algorithm plans the path and computations from a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation.
+At each stage, the UAV must follow a trajectory within the trajectory constraints set and do the computations within the computations constraints sets.
 There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
-The algorithm outputs the new position, the instantaneous energy consumption, and the control (the parameters).
+The algorithm outputs the control (the parameters), the new position, and the energy consumption.
+The UAV utilizes the control to alter its energy consumption to meet the energy budget.
+The control is data-driven.
+Energy sensor data refine a perfect energy model used to predict future energy consumption and derive the optimal control.
 
@@
 
-\subsection{State: position $\mathbf{p}$}
-\label{sec:model}
-
-We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.
-
-\begin{figure}[h]
-  \centering
-  \input{\figpath/path2.tikz}
-  \caption{Illustrative example of the alteration of a trajectory parameter}
-  \label{fig:tee1}
-\end{figure}
-
-Let us assume that the set
-\begin{equation}\label{eq:area}
-  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
-\end{equation}
-delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
-$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory.
-Physically, this means the UAV is flying exactly over the nominal trajectory.
-The trajectory parameters allows to change the trajectory.
-They are a way to alter the nominal trajectory in the initial plan.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
-
-We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector
-\begin{equation}\label{eq:pd}
-  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
-    0&1\\-1&0
-  \end{bmatrix},
-\end{equation}
-where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
-
-\subsection{State: energy $\mathbf{q}$}
+\section{Periodic Energy Model}
 \label{sec:energy-model}
@@
 We refer to the instantaneous energy consumption evolution simply as the energy signal.
-The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series).
+The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and estimated using a state estimator (Kalman filter).
 
@@
 It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$, for a given $\nu_{1,1}\in\mathbb{R}_{<0}$.
+
+\subsection{Trajectory parameters energy contribution}
+\label{sec:model}
+
+\begin{figure}[h]
+  \centering
+  \input{\figpath/path2.tikz}
+  \caption{Illustrative example of the alteration of a trajectory parameter}
+  \label{fig:tee1}
+\end{figure}
+
+Let us assume that the set
+\begin{equation}\label{eq:area}
+  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
+\end{equation}
+delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
+$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory.
+Physically, this means the UAV is flying exactly over the nominal trajectory.
+The trajectory parameters allows to change the trajectory.
+They are a way to alter the nominal trajectory in the initial plan and thus alter the energy signal.
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+
+We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
+\begin{equation}\label{eq:pd}
+  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
+    0&1\\-1&0
+  \end{bmatrix},
+\end{equation}
+where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
 

### 2020-12-14 icra-2021.tex
added a double sized illustrative abstract (turn the first page against light) [Hector and Ulrik are gonna kill me xD]
forgot to include the tex file...
that illustrative abstract is hopefully done now

@@
 \usepackage{tikz}
-\usetikzlibrary{automata,positioning,decorations.pathreplacing}
+\usetikzlibrary{automata,positioning,decorations.pathreplacing,backgrounds}
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
@@
 
+%\tikz{\fill[blue] (0,0) circle (.7ex);\fill[green] (0,0) -- (90:.7ex) arc (90:270:.7ex) -- cycle;}
+
 \begin{figure}[t]
   \centering
-  \input{\figpath/il_abstract.tikz}
-  \caption{Illustrative abstract. An initial plan is replanned in terms of both the path and computations.}
+  \definecolor{c00FFFF}{RGB}{0,255,255}
+  \input{\figpath/il_abs.tikz}
+  \input{\figpath/il_abs_energy.tikz}
+  \caption{An initial plan of an agricultural scenario replanned in terms of both the path (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, travels a more accurate survey than \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}) and computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, elaborates more images per second than \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+In bottom right, the collected energy data of the UAV flying the scenario.}
   \label{fig:il-abs}
@@
 Moreover, let $g(\{\emptyset\})$ be zero.
-
-\leavevmode\thispagestyle{empty}\newpage
-\leavevmode\thispagestyle{empty}\newpage
 
@@
 
-\leavevmode\thispagestyle{empty}\newpage
-\leavevmode\thispagestyle{empty}\newpage % just for now
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-14 scripts/plots/generate_il_abs.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+
+gnuplot -e "
+    set datafile separator ',';
+    set term qt size 180,120;
+    set tics nomirror out scale 0.75;    
+    unset title;
+    set border lw .5;
+    set xrange [0:320];
+    set xtics 100 center offset .6,.5 font 'Times,8';
+    set yrange [19:41];
+    set ytics 5 center offset -.3,0 font 'Times,8';
+    set xlabel 'Time (sec)' rotate parallel center offset -.7,1.1 font 'Times,8';
+    set ylabel 'Power (W)' rotate parallel center offset 2.5,-.1 font 'Times,8';
+    set key font 'Times,8';
+    set multiplot;
+    plot 'periodic_energy.csv' using 1:2 w l notitle lc rgb 'black' lw .5;
+    set size 0.5, 0.5;
+    set origin 0.5, 0.5;
+    unset xtics;
+    unset ytics;
+    unset xlabel;
+    unset ylabel;
+    set xrange [-0.03:0.03];
+    set yrange [0:500];
+    plot 'spectrum.csv' using 1:2 w l notitle lc rgb 'black' lw .5;
+    unset multiplot;
+    pause -1;
+"

### 2020-12-14 scripts/plots/il_abs.m

@@ -1,0 +1,52 @@
+
+% matlab script to generate the plots in the illustrative abstract
+
+% read original data
+x = csvread('../../data/simulation1/pprz_throttle.csv');
+x = x(:,3); % the energy is in the 3rd column
+x2 = resample(x, 100, 640); % shrink data
+x2(1) = x(1); % make sure first value is the same in both
+
+% the plot with the energy it time
+t = linspace(0, 320, 100)';
+figure(1);
+plot(t, x2)
+xlabel('Time (sec)');
+ylabel('Power (W)');
+
+% spectral analysis
+period = 16; % this value is observed from data
+             % I looked where are the peaks
+xline(50);
+xline(100);
+xline(150);
+xline(200);
+xline(250);
+xline(300); % just some lines at the hypothetical period 
+
+fs = 1/period; % frequency
+y = fft(x - mean(x)); % discrete fourier transform of the energy signal
+
+n = length(x); % number of samples
+f = (0:n-1)*(fs/n); % frequency range
+power = abs(y).^2/n; % power of the DFT
+
+figure(2);
+plot(f,power)
+xlabel('Frequency')
+ylabel('Power')
+
+% power spectrum centered at 0 frequency (more insightful)
+y0 = fftshift(y);         % shift y values
+power0 = abs(y0).^2/n;    % 0-centered power
+n = 100; % taking just 10 frequencies
+f0 = (-n/2:n/2-1)*(fs/n); % 0-centered frequency range
+
+figure(3);
+plot(f0,power0((end-n)/2+1:(end+n)/2))
+xlabel('Frequency')
+ylabel('Power')
+
+csvwrite('periodic_energy.csv', [t x2]);
+csvwrite('spectrum.csv', [f0' power0((end-n)/2+1:(end+n)/2)]);
+

### 2020-12-15 icra-2021.tex
implementing Hector's and Ulrik's suggestions

--- 2020-12-10 icra-2021.tex
@@
 \newtheorem{exmp}{Example}[section]
+\newtheorem{pb}{Problem}[section]
 \newtheorem{rem}{Remark}
@@
   }
-
 \end{filecontents}
@@
 }
+
+\definecolor{c00FFFF}{RGB}{0,255,255}
 
@@
 Current generic planning solutions for outdoor UAVs do not plan the path and computations dynamically, nor are they energy-aware.
-They are often semi-autonomous: the path and computations are static and usually defined using planning software~\cite{daponte2019review}.
+They are often semi-autonomous: the path and computations are static and usually defined using planning software~\cite{daponte2019review} (for instance~\cite{papa} and~\cite{px4}).
 Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
 The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV planning problem.
+
+\begin{figure}[t]
+  \centering
+  \input{\figpath/il_abs.tikz}
+  \input{\figpath/il_abs_energy.tikz}
+  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, travels a more accurate survey than \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}) and computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, elaborates more images per second than \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+In bottom right, the collected energy data of the UAV flying the scenario, along the power spectrum (small rectangle) where the first frequency has been filtered.}
+  \label{fig:il-abs}
+\end{figure}
 
@@
 
-\begin{figure}[t]
-  \centering
-  \input{\figpath/il_abstract.tikz}
-  \caption{Illustrative abstract. An initial plan is replanned in terms of both the path and computations.}
-  \label{fig:il-abs}
-\end{figure}
-
 Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations.
@@
 To model the computations we use a profiling tool presented in previous work~\cite{seewald2019coarse}.
-The user specifies the maximum, minimum, and current levels of some parameters relative to the path and computations in an initial plan with an energy budget.
-In Figure~\ref{fig:il-abs}, there are two parameters.
-The radius of the trajectory circle is relative to the trajectory.
-The quality of image detection is relative to the computations.
-The algorithm replans the initial plan within the constraints and the energy budget using output model predictive control (MPC).
-The energy budget is the battery capacity and some other battery parameters.
-Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
-The term parameters should not be confused with the battery parameters, which we always mention explicitly.
-These are fixed values that are not replanned by the algorithm.
 To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
@@
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:il-abs} shows a slice of such a plan.
+Figure~\ref{fig:il-abs} shows a slice of such and the small plot shows the periodicity from the collected energy data.
+The small rectangle shows the spectrum power with the first frequency filtered, showing thus that three frequencies are mostly necessary to model the energy.
 Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}).
@@
 The remainder of the paper is organized as follows.
-The overview of dynamic planning is provided in Section~\ref{sec:prob}, and a suitable model for the energy in Section~\ref{sec:energy-model}.
+The overview of dynamic planning is provided in Section~\ref{sec:prob}, and the problem is set with some preliminaries in Section~\ref{sec:prelim}.
+A suitable model for the energy in Section~\ref{sec:energy-model}.
 The algorithm is proposed in Section~\ref{sec:algo}.
@@
 There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
-The algorithm outputs the control (the parameters), the new position, and the energy consumption.
+The user specifies the maximum, minimum, and current levels of some parameters relative to the path and computations in such plan with an energy budget.
+In Figure~\ref{fig:il-abs}, there are two parameters.
+The radius of the trajectory circle is relative to the trajectory (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;} and \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+The quality of image detection is relative to the computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;} and \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+The algorithm outputs the parameters (the control) using output model predictive control (MPC)~\cite{rawlings2017model}.
 The UAV utilizes the control to alter its energy consumption to meet the energy budget.
 The control is data-driven.
-Energy sensor data refine a perfect energy model used to predict future energy consumption and derive the optimal control.
+Energy sensor data estimates coefficients of the energy model used to predict future energy consumption and derive the control, replanning the initial plan in presence of uncertainty.
+The energy budget is the battery capacity and some other battery parameters.
+Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
+The term parameters should not be confused with the battery parameters, which we always mention explicitly.
+These are fixed values that are not replanned by the algorithm.
+
+\subsection{Preliminaries and Problem Definition}
+\label{sec:prelim}
 
@@
 
+In order to formulate the problem, we considerate some assumptions.
+
+\begin{assm}[Plan periodicity]\label{assm:periodic}
+  Given an initial plan $\Gamma$ consisting of $l$ stages $\Gamma_i$ s.t. $i\in[l]^+$ and a generic starting point $\mathbf{p}_k$, there exists an integer positive constant $k<l$ such that
+  \begin{equation*}
+    \varphi_i-\varphi_{k+i}=c_k,
+  \end{equation*}
+  where $c_1,\dots,c_k$ are arbitrary constant differences.
+\end{assm}
+
+Physically, this means that the plan is periodic, with periodicity $k$. From Assumption~\ref{assm:periodic}, follows the next lemma.
+
+\begin{lem}[Rank of the trajectory functions]
+  Suppose Assumption~\ref{assm:periodic} holds. Then
+  \begin{equation*}
+    \mathrm{rank}\begin{bmatrix}
+        \varphi_1 & \varphi_{k+1} & \cdots & \varphi_{(l-k)+1} \\ 
+        \varphi_2 & \varphi_{k+2} & \cdots & \varphi_{(l-k)+2} \\
+        \vdots & \vdots & \ddots & \vdots \\
+        \varphi_k & \varphi_{2k} & \cdots & \varphi_l   
+      \end{bmatrix}=2.
+  \end{equation*}
+\end{lem}
+\begin{proof} 
+  The proof follows directly from Assumption~\ref{assm:periodic}.
+The column rank of the matrix in the lemma is the dimension of its column space.
+This denotates the size of the set of all the possible linear combination of the column vectors.
+We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the values of the constant differences $c_1,\dots,c_k$ are the same for each $i$).
+\end{proof}
+
+The lemma shows an easy way to verify that a plan is periodic.
+
+\begin{pb}[UAV planning problem]
+  Consider an initial plan $\Gamma$ satisfying Assumption~\ref{assm:periodic}.
+We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ for the UAV planning problem.
+\end{pb}
+
 \section{Periodic Energy Model}
@@
 where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
-
-We use extensively the following assumption for the purpose of energy signal modeling.
-\begin{assm}[Energy signal periodicity]\label{assm:periodic} 
-Given two time instants $k_1,k_2$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{Z}_{> 0}$
-\begin{equation*}
-  \abs{y_{k}-y_{k+n}}\in\mathbb{E}\subset\mathbb{R}_{\geq 0} \,\,\,\forall k\in[k_1,k_2],
-\end{equation*}
-for a small enough set $\mathbb{E}$.
-\end{assm}
-
-Physically this means that the energy signal is assumed to be approximately periodic.
 

### 2020-12-15 icra-2021.tex
implementing Hector's and Ulrik's suggestions (2)

@@
 
-\begin{defn}[Stage, plan, and triggering point]\label{def:mission}
+\begin{defn}[Stage, plan, triggering, and final point]\label{def:mission}
   A \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
@@
   The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to last stage $\Gamma_l$ is called \emph{final point}.
 \end{defn}
@@
 The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$ and $\mathbf{p}_{k_2}$.
-It eventually enters the stage $\Gamma_{i+1}$ with the triggerint point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
+It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
 
@@
 \begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages $\Gamma_i$ s.t. $i\in[l]^+$ and a generic starting point $\mathbf{p}_k$, there exists an integer positive constant $k<l$ such that
+  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and current levels of parameters, there exists a constant $n\in\mathbb{Z}_{>0}, n<l$ such that
   \begin{equation*}
-    \varphi_i-\varphi_{k+i}=c_k,
+    \varphi_i-\varphi_{n+i}=d_i,\,\,\,\forall i\in[l]^+
   \end{equation*}
-  where $c_1,\dots,c_k$ are arbitrary constant differences.
+  where $d_1,\dots,d_l$ are arbitrary constant differences.
 \end{assm}
 
-Physically, this means that the plan is periodic, with periodicity $k$. From Assumption~\ref{assm:periodic}, follows the next lemma.
-
-\begin{lem}[Rank of the trajectory functions]
+Physically, this means that the plan is periodic.
+
+\begin{defn}[Period]\label{def:period}
+  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_i$ and $\varphi_{n+i}$ for an arbitrary $i\in[l]^+$.
+\end{defn}
+
+The algorithm measures the time between the stages $\Gamma_i$ and $\Gamma_{n+i}$ and assumes the initial period is one.
+
+From Assumption~\ref{assm:periodic}, follows the next proposition.
+
+\begin{prop}[Rank of the trajectory functions]\label{prop:rank}
   Suppose Assumption~\ref{assm:periodic} holds. Then
@@
     \mathrm{rank}\begin{bmatrix}
-        \varphi_1 & \varphi_{k+1} & \cdots & \varphi_{(l-k)+1} \\ 
-        \varphi_2 & \varphi_{k+2} & \cdots & \varphi_{(l-k)+2} \\
+        \varphi_1 & \varphi_{n+1} & \cdots & \varphi_{(l-n)+1} \\ 
+        \varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
         \vdots & \vdots & \ddots & \vdots \\
-        \varphi_k & \varphi_{2k} & \cdots & \varphi_l   
+        \varphi_n & \varphi_{2n} & \cdots & \varphi_l   
       \end{bmatrix}=2.
   \end{equation*}
-\end{lem}
+\end{prop}
 \begin{proof} 
@@
 The column rank of the matrix in the lemma is the dimension of its column space.
-This denotates the size of the set of all the possible linear combination of the column vectors.
-We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the values of the constant differences $c_1,\dots,c_k$ are the same for each $i$).
+It denotes the size of the set of all the possible linear combination of the column vectors.
+We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the values of the constant differences $d_1,\dots,d_l$ are the same for each $i$).
 \end{proof}
@@
 
-\begin{pb}[UAV planning problem]
-  Consider an initial plan $\Gamma$ satisfying Assumption~\ref{assm:periodic}.
+\begin{pb}[UAV planning problem]\label{pb}
+  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}.
 We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ for the UAV planning problem.
@@
 
-Let us consider a periodic signal of period $T\in\mathbb{R}_{> 0}$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
+Let us consider a periodic signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
 \begin{equation}\label{eq:fourier}
@@
 
-Let us consider a linear time-invariant (LTI) state-space model
+The energy signal can be modeled by Equation~\ref{eq:fourier} and the output of a linear model
 \begin{equation}\label{eq:state-perf}\begin{split}
-  \dot{\mathbf{q}}&=A\mathbf{q}+B\mathbf{u}+\mathbf{w},\\
-  y&=C\mathbf{q}+v,
+  \dot{\mathbf{q}}&=A\mathbf{q}+B\mathbf{u},\\
+  y&=C\mathbf{q},
 \end{split}\end{equation}
-where $y\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption, and $\mathbf{w}\in\mathbb{R}^m,v\in\mathbb{R}$ are the contributions of the uncertainty.
+where $y\in\mathbb{R}$ is the instantaneous energy consumption.
 
@@
 
-\begin{lem}[Signals equality]\label{lem:eqv}Suppose there is no state and output uncertainty (the contributions $\mathbf{w},v$ are zeros) and the control is zero.
-Suppose further matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is $\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}$.
+Linear model in Equation~\ref{eq:state-perf} allows us to include the control in the model of Equation~\ref{eq:fourier}.
+The algorithm uses the model to find the control sequence that results in the optimal parameters configuration (using MPC).
+
+\begin{lem}[Signals equality]\label{lem:eqv}Suppose control is zero, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is 
+  \begin{equation*}
+  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}^T.
+  \end{equation*} 
   Then, the signal $h$ in Equation~(\ref{eq:fourier}) is equal to the signal $y$ in Equation~(\ref{eq:state-perf}).
@@
 
-Given $l$ stages $\mathcal{M}_i$ (TEE $\varphi_i$, tasks $\Psi$, computations $\mathbf{s}_i\in\mathbb{S}_i$, and adaptations $\mathbf{c}_i\in\mathbb{C}_i$ for all $i\in[l]$), the main purpose of the algorithm is to output a control input sequence $\mathbf{u}^a:=\{\mathbf{u}_0^a,\mathbf{u}_1^a,\dots\}$ in a valid mission.
-
-\begin{defn}[Valid mission]\label{def:valid}
-  A mission is valid if for every stage $\mathcal{M}_{i-1},\,i\in[l]^+$ there exist a control input $\mathbf{u}_k^{a}$ that produce the next stage $\mathcal{M}_i$
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$, to solve Problem~\ref{pb}.
+
+----
+
+\begin{defn}[Valid control sequence]\label{def:valid}
+  A control sequence $\mathbf{u}$ is valid if for every stage $\Gamma_{i-1},\,i\in[l]^+$ if there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$
   \begin{equation}\begin{split}\label{eq:mission-valid}

### 2020-12-15 icra-2021.tex
implementing Hector's and Ulrik's suggestions (3)

@@
   Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}.
-We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ for the UAV planning problem.
+
+  We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
 \end{pb}
@@
 
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$, to solve Problem~\ref{pb}.
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to direct the UAV on a valid path: to solve Problem~\ref{pb}.
+
+\begin{defn}[Valid control sequence and path]\label{def:valid}
+  A \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[l]^+$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
+
+  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path}
+  \begin{equation}\begin{split}\label{eq:mission-valid}
+   \mathcal{P}:=\{\mathbf{p}_k\mid&\,\exists \mathbf{u}_k,n\in\mathbb{Z}_{>0},\\
+    &\langle\varphi_{i-1}\left(\mathbf{p}_{k-n}\right),\mathbf{u}_{k-n}\rangle\in\Gamma_{i-1}\\
+    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle\in\Gamma_i\},
+  \end{split}\end{equation}
+  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k,1},\dots,$ $c_{k,\rho}),c_{k,\rho+1},\dots,c_{k,\rho+\sigma}\rangle$.
+\end{defn}
+
+Let us proof that the plan is periodic and one period is valid, then the plan is valid.
+
+\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
+?
 
@@
 
-\begin{defn}[Valid control sequence]\label{def:valid}
-  A control sequence $\mathbf{u}$ is valid if for every stage $\Gamma_{i-1},\,i\in[l]^+$ if there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$
-  \begin{equation}\begin{split}\label{eq:mission-valid}
-    \mathbf{u}^a_{k}=\{&\langle\mathbf{c}_{k},\mathbf{s}_{k}\rangle\mid\,\exists n\in\mathbb{Z}_{>0},\\&\langle\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n})\rangle\in\mathcal{M}_{i-1}\\
-    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k})\rangle\in\mathcal{M}_{i}\}.
-  \end{split}\end{equation}
-\end{defn}
-
-Let us proof that if the mission is valid, the instantaneous energy consumption can be modeled as linear combination of the state from the Equation~(\ref{eq:state-perf}).
-
-\begin{thm}[Periodic energy model]\label{thm:state-vs-energy}
   Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}.

### 2020-12-16 icra-2021.tex
I must push this one :S
fixes to the assumption in overview sec

@@
 
-In order to formulate the problem, we considerate some assumptions.
+In order to formulate the problem, we considerate the assumption.
 
 \begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and current levels of parameters, there exists a constant $n\in\mathbb{Z}_{>0}, n<l$ such that
+  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and the current levels of all the parameters $c_{1,1},\dots,c_{l,\rho+\sigma}$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
   \begin{equation*}
-    \varphi_i-\varphi_{n+i}=d_i,\,\,\,\forall i\in[l]^+
+    \varphi_{(i-1)n+j}\approx \varphi_{in+j},\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
   \end{equation*}
-  where $d_1,\dots,d_l$ are arbitrary constant differences.
 \end{assm}
 
-Physically, this means that the plan is periodic.
+Physically, this means that the plan is periodic. We will see the assumption being eventually eased for non-periodic plans in Section~\ref{sec:experimental}.
 
 \begin{defn}[Period]\label{def:period}
-  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_i$ and $\varphi_{n+i}$ for an arbitrary $i\in[l]^+$.
+  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Assumption~\ref{assm:periodic}.
 \end{defn}
 
-The algorithm measures the time between the stages $\Gamma_i$ and $\Gamma_{n+i}$ and assumes the initial period is one.
+The algorithm measures the time between the stages and assumes the initial period is one.
+We note that periods between stages same stages but different $j$s might be different due to atmospheric interferences.
 
@@
 
-\begin{prop}[Rank of the trajectory functions]\label{prop:rank}
-  Suppose Assumption~\ref{assm:periodic} holds. Then
+\begin{prop}[Necessary and sufficient condition for periodicity]\label{prop:rank}
+  Suppose Assumption~\ref{assm:periodic} holds, then the plan $\Gamma$ is periodic if
+  \begin{equation*}
+    \varphi_{(i-1)n+j}-\varphi_{in+j}=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+  \end{equation*}
+  Moreover, if the plan $\Gamma$ is periodic then
   \begin{equation*}
@@
         \varphi_1 & \varphi_{n+1} & \cdots & \varphi_{(l-n)+1} \\ 
-        \varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
+        %\varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
         \vdots & \vdots & \ddots & \vdots \\
@@
 \end{prop}
-\begin{proof} 
-  The proof follows directly from Assumption~\ref{assm:periodic}.
-The column rank of the matrix in the lemma is the dimension of its column space.
+\begin{proof}($\Longleftarrow$) The column rank of the matrix in the lemma is the dimension of its column space.
 It denotes the size of the set of all the possible linear combination of the column vectors.
-We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the values of the constant differences $d_1,\dots,d_l$ are the same for each $i$).
+We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the difference $d_j$ is the same for any $i$).
+
+  ($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th ``shift''.
+This is equivalent to Assumption~\ref{assm:periodic}.
 \end{proof}
 
-The lemma shows an easy way to verify that a plan is periodic.
+The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for the periodicity.
+The algorithm finds $n$ starting from one and finding the value which satisfies the proposition.
 
 \begin{pb}[UAV planning problem]\label{pb}
-  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}.
-
+  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic}.
 We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
@@
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}&=\begin{bmatrix}c_{i,1} & \cdots & c_{i,\rho} & c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}^T,\\
+  \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T,\\
   B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
@@
 
-Let us proof that the plan is periodic and one period is valid, then the plan is valid.
+Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
 

### 2020-12-16 icra-2021.tex
fixing the paper with current changes

@@
 
-Physically, this means that the plan is periodic. We will see the assumption being eventually eased for non-periodic plans in Section~\ref{sec:experimental}.
+Physically, this means that the plan is periodic. We will see the assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
 
@@
 \end{prop}
-\begin{proof}($\Longleftarrow$) The column rank of the matrix in the lemma is the dimension of its column space.
+\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th ``shift''.
+This is equivalent to Assumption~\ref{assm:periodic}.
+
+($\Longleftarrow$) The column rank of the matrix in the proposition is the dimension of its column space.
 It denotes the size of the set of all the possible linear combination of the column vectors.
-We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the difference $d_j$ is the same for any $i$).
-
-  ($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th ``shift''.
-This is equivalent to Assumption~\ref{assm:periodic}.
+We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (from $\Longrightarrow$).
 \end{proof}
@@
 
+\begin{assm}\label{assm:valid}
+  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n-1]^+,\,j\in[n]^+$ s.t. $\Gamma_{(i-1)n+j},\dots,\Gamma_{in+j}$ is valid.
+\end{assm}
+
 \begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-?
+  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~\ref{eq:state-perf}, and the plan is periodic).
+Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
 
   ----
-
-  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}.
-Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^a/m$ for the first coefficient where $y_0^a\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^a$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^a/m$ for all the others, and the mission is valid.
-  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
 \end{thm}
@@
   The proof is based on mathematical induction. 
-  Base case: we proof that $y_0=y_0^a$.
-Recall the definition of the state in Equation~(\ref{eq:state-details}).
-The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^a/m+(1/2)y_0^a/m+\cdots+(1/2)y_0^a/m=y_0^a$.
-
-  Induction step: by inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(k)\alpha_{0,r}$, where $\forall t\in\mathbb{Z}_{\geq 2}$
-  \begin{equation}\label{eq:proof-pr}
-    p_r(t):=\begin{cases}
-      \prod_{i=1}^{t/2}{r^3/\xi^3}&\text{ for even }t\\
-      (r/\xi)\prod_{i=1}^{(t-1)/2}{r^3/\xi^3}&\text{ for odd }t
-    \end{cases}.
-  \end{equation}
-
-  Suppose $k$ is even and the theorem holds up to $k$.
-Initial energy coefficients state $\mathbf{q}_0$ leads to $y_{k}=(y_0^a/m+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^a/m+\dots+p_r(k)(1/2)y_0^a/m=y_{k}^a$.
-
-  We prove now that the instantaneous energy consumption at $k+1$ is still a linear combination of the state.
-We express the output in function of the previous state $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)\beta_{k,1}+\dots+(r/\xi)\beta_{k,r}$.
-Notice that the coefficients $\alpha,\beta$ have an equivalent evolution (indeed this allows to simulate the periodicity) and $\beta_{k,r}=p_r(k)\beta_{0,r}$.
-Thus, the output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$.
-The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$ using the definition of $p_r$ in Equation~(\ref{eq:proof-pr}).
-Again, the state $\mathbf{q}_0$ leads to $y_{k+1}=(y_0^a/m+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^a/m+\dots+p_r(k+1)(1/2)y_0^a/m=y_{k+1}^a$, alike the previous statement, but at instant $k+1$.
-The proof for odd $k$ is equivalent.
+  Base case:
+
+  Induction step:
+
 \end{proof}
@@
 
-Some preliminary results are discussed. Further analysis and re-implementation of the functionality of the algorithm is needed.
-
-\begin{figure}[h]
-  \centering
-  \input{\figpath/trajectory/trajectory3.tikz}
-  \caption{The true trajectory. The trajectory is retrieved from the flight log.}
-  \label{fig:trajectory}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \input{\figpath/energy/max_qos_tees3.tikz}
-  \caption{Derived energy consumption from the sensors (throttle).
+*
+
+%Some preliminary results are discussed. Further analysis and re-implementation of the functionality of the algorithm is needed.
+
+%\begin{figure}[h]
+%  \centering
+%  \input{\figpath/trajectory/trajectory3.tikz}
+%  \caption{The true trajectory. The trajectory is retrieved from the flight log.}
+%  \label{fig:trajectory}
+%\end{figure}
+
+%\begin{figure}[h]
+%  \centering
+%  \input{\figpath/energy/max_qos_tees3.tikz}
+%  \caption{Derived energy consumption from the sensors (throttle).
 Red line is the estimated value.
@@
 Otherwise we evolve the state without noise.}
-  \label{fig:energy-max}
-\end{figure}
+%  \label{fig:energy-max}
+%\end{figure}
 
@@
 
-We proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
+First, we proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
 We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
@@
 The initial guess is build such that the sum of the coefficients is the same in both the signals.
-The output matrix is built as follows.
-The coefficient $1/T$ accounts for the period in Equations~(\ref{eq:proof-complex}--\ref{eq:proof-output}) and~(\ref{eq:fourier}).
-At time instant zero, the coefficients $b_j$ are not present (and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$).
+In the output matrix, the frequency $1/T$ accounts for the period in Equations~(\ref{eq:proof-complex}--\ref{eq:proof-output}) and~(\ref{eq:fourier}).
+At time instant zero, the coefficients $b_j$ are not present and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$ (thus we multiply by a half the corresponding coefficients in $\mathbf{q}_0$).
 To match the outputs $h(t)=y(t)$--or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$--we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
@@
 
-The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format. We refer the reader to Appendix~\ref{app:plan-example} for an example.
+The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format.
 
@@
 where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the trajectory.
-In the next subsection where we discuss the physical meaning of the convergence value and rotation.
 The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
@@
 
-We discuss how to specify an initial mission plan with an example of a survey mission.
-The reader can later execute the initial mission plan using the simulator in Appendix~\ref{app:simulator}.
-The plan is user-defined.
-It specifies the trajectory and tasks of a mission along the QoS and TEEs sets.
-
-Recall that the mission is composed of a set of stages (Section~\ref{sec:prob}).
-The plan has a variable number of entries per each stage.
-We plan the mission in Figures~\ref{fig:il-abs},~\ref{fig:trajectory}.
-The first line
+We discuss how to specify an initial plan with an example of a survey scenario, equivalent to the one in Figure~\ref{fig:il-abs}.
+
+Recall that the plan is composed of a set of stages (Section~\ref{sec:prob}). It has a variable number of entries per each stage. The first line
 \begin{algorithmic}[1]
-  \State\textbf{\texttt{0.0003;90;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
+  \State\textbf{\texttt{0.0003;0;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
 \end{algorithmic}
-corresponds to TEE $\varphi_0(\mathbf{p}_k,c_{0,1}):=(x+45)^2+(y-146)^2-4900+c_{0,1}$ in the initial stage $\mathcal{M}_0$.
-The TEE is a circle.
-The gain is $k_e=3\cdot 10^{-4}$, and the rotation is of ninety degrees--we use the rotation matrix $E$ from Equation~(\ref{eq:pd}).
-Note that line~\ref{code:firstcircle} further specifies the adjustment {\tt\textbf{c1}} of the radius of the circle.
-It corresponds to $c_{0,1}$ in Definition~\ref{def:mission} (zero numerates the stage, one the adjustment).
+corresponds to the trajectory $\varphi_1(\mathbf{p}_k,c_{1,1}):=(x+45)^2+(y-146)^2-4900+c_{1,1}$ in the initial stage $\Gamma_1$.
+The trajectory is a circle.
+The gain is $k_e=3\cdot 10^{-4}$, and the rotation is counter-clockwise--we use the rotation matrix $E$ from Equation~(\ref{eq:pd}).
+We note that line~\ref{code:firstcircle} further specifies the parameter {\tt\textbf{c1}} of the radius of the circle.
+It corresponds to $c_{1,1}$ in Definition~\ref{def:mission}.
 
@@
 \end{algorithmic}
-specifies the triggering point.
+specifies the triggering point $\mathbf{p}_{\Gamma_1}$.
 {\tt\textbf{sqrt}} is the square root.
-The UAV reaches the triggering point within a given $\varepsilon$ (the tolerance), and the algorithm switches to the next stage $\mathcal{M}_1$.
-The algorithm ensures that the overall mission is still valid--Equation~(\ref{eq:mission-valid}).
-It ensure that the TEEs and QoS constraints sets are satisfied with the generated control input.
-Note that the triggering point is in function of the adjustment {\tt\textbf{c1}}.
-This is necessary; an adjustment in one stage affects the overall flight.
-
-Let us assume the mission has two tasks.
-One task is the CNN object detection algorithm.
-Its computation $s_{0,1}$ is the fps rate.
-Another task is the variable key-size encryption algorithm.
-Its computation $s_{0,2}$ is the key-size.
-Then in mission plan
+The UAV reaches the triggering point within a given $\varepsilon$ (the tolerance), and the algorithm switches to the next stage $\Gamma_2$.
+We note that the triggering point is in function of the parameter {\tt\textbf{c1}}.
+This is necessary; an change in a parameter in one stage affects the overall flight.
+
+Let us assume the scenario has two computations.
+One computation is the CNN object detection algorithm, and it can be planned by one parameter $c_{1,2}$, the fps rate.
+Another computation is the variable key-size encryption algorithm.
+It can be planned by one parameter $c_{1,2}$, the key-size.
+Then in the plan
 \begin{algorithmic}[1]
@@
 \end{algorithmic}
-line~\ref{code:teeset} corresponds to TEE $\varphi_0$'s set $\mathbb{C}_0=[-3\cdot10^3,0]$.
-The algorithm selects $c_{0,1}\in\mathbb{C}_0$.
-Line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,1}$ for the computation $s_{0,1}$.
-Line~\ref{code:qos1set} corresponds to the QoS set $\mathbb{S}_{0,2}$ for the computation $s_{0,2}$.
-Lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of adjustments and computations.
-Lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\mathcal{M}_0$.
-
-Once the UAV reaches the triggering point (line~\ref{code:trigger}) and there are no further lines, the algorithm terminates. If there are further lines, the stage switches to $\mathcal{M}_1$
+line~\ref{code:teeset} corresponds to the trajectory $\varphi_1$'s contraints set $\mathbb{C}_1=[-3\cdot10^3,0]$.
+The algorithm selects $c_{1,1}\in\mathbb{C}_1$.
+Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathbb{S}_{1,1}$ for the computation parameter $c_{1,2}$.
+Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathbb{S}_{1,2}$ for the computation parameter $c_{1,2}$.
+Lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of the parameters.
+Lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\Gamma_1$.
+
+Once the UAV reaches the triggering point (line~\ref{code:trigger}) and there are no further lines, the algorithm terminates (the last triggering point is the final point).
+If there are further lines, the stage switches to $\Gamma_2$
 \begin{algorithmic}[1]
   \setcounterref{ALG@line}{code:qos2set}
-  \State\textbf{\texttt{0.05;270;x+sqrt(4900+c1)+45}}\label{code:tee2}
+  \State\textbf{\texttt{0.05;1;x+sqrt(4900+c1)+45}}\label{code:tee2}
   \State\textbf{\texttt{-sqrt(4900+c1)-45,11}}\label{code:trigger2}
@@
 \end{algorithmic}
-line~\ref{code:tee2} corresponds to TEE $\varphi_1(\mathbf{p}_k,c_{0,1}):=x+\sqrt{4900+c_{0,1}}+45$, a linear equation that intersects the triggering point (line~\ref{code:trigger}).
+line~\ref{code:tee2} corresponds to the trajectory $\varphi_2(\mathbf{p}_k,c_{1,1}):=x+\sqrt{4900+c_{1,1}}+45$, a linear equation that intersects the triggering point (line~\ref{code:trigger}).
 The gain is $k_e=5\cdot 10^{-2}$, and the rotation is opposite to line~\ref{code:firstcircle}.
@@
 
-The gain is different from the one used in $\varphi_0$ as different equations require different convergence rate.
+The gain is different from the one used in $\varphi_1$ as different equations require different convergence rate.
 When we follow a circle it is useful to turn the rotation direction in advance.
 When we follow a straight line, it is preferable to turn the rotation direction closer to the line.
-We refer to the simulator in Appendix~\ref{app:simulator} for more details on how to tune the gain $k_e$.
-The reader can simulate different rates to see how they affect the flight.
 The rotation is likewise different.
@@
 
-The triggering point of the stage $\mathcal{M}_1$ at line~\ref{code:trigger2} also depends on the adjustment {\tt\textbf{c1}}.
+The triggering point of the stage $\Gamma_2$ at line~\ref{code:trigger2} also depends on the parameter {\tt\textbf{c1}}.
 Lines~\ref{code:teeset2}--\ref{code:qosset12} specifies the constraints sets.
@@
 
-Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the algorithm switches the stage to $\mathcal{M}_2$
+Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the algorithm switches the stage to $\Gamma_3$
 \begin{algorithmic}[1]
@@
 \end{algorithmic}
-line~\ref{code:tee3} corresponds to TEE $\varphi_2(\mathbf{p}_k,c_{0,1}):=(x+\sqrt{4900+c_{0,1}}-30)^2+(y-11)^2-5625$, a circle of fixed size that changes the coordinates in function of the adjustment {\tt\textbf{c1}}.
-The rotation is counter-clockwise, alike $\varphi_0$.
+line~\ref{code:tee3} corresponds to the trajectory $\varphi_3(\mathbf{p}_k,c_{1,1}):=(x+\sqrt{4900+c_{1,1}}-30)^2+(y-11)^2-5625$, a circle of fixed size that changes the coordinates in function of the parameter {\tt\textbf{c1}}.
+The rotation is counter-clockwise, alike $\varphi_1$.
 
@@
 \end{algorithmic}
-defines the stages $\mathcal{M}_3$ and $\mathcal{M}_4$.
-Line~\ref{code:tee4} corresponds to TEE $\varphi_3(\mathbf{p}_k,c_{0,1}):=x+\sqrt{4900+c_{0,1}}-105$.
-Line~\ref{code:tee5} corresponds to TEE $\varphi_4(\mathbf{p}_k,c_{0,1}):=(x-\sqrt{4900+c_{0,1}}+105)^2+(y-147)^2-4900+c_{0,1}$.
-
-Note that the survey mission example changes the radius of the circular TEE $\varphi_0$ through the parameter $c_{0,1}$.
-It also changes the radius of $\varphi_4$ in the same way.
-The other TEEs ($\varphi_1,\varphi_2,\varphi_3$) displacement alters the distance between the lines in the survey.
-A familiar pattern from Figure~\ref{fig:tee1}.
-For simplicity, we suppose line~\ref{code:triggerlast} describes the last point of the mission.
-We further suppose the user does not desire to process any task in the last stage $\mathcal{M}_4$.
+defines the stages $\Gamma_4$ and $\Gamma_5$.
+Line~\ref{code:tee4} corresponds to the trajectory $\varphi_4(\mathbf{p}_k,c_{1,1}):=x+\sqrt{4900+c_{1,1}}-105$.
+Line~\ref{code:tee5} corresponds to the trajectory $\varphi_4(\mathbf{p}_k,c_{0,1}):=(x-\sqrt{4900+c_{0,1}}+105)^2+(y-147)^2-4900+c_{0,1}$.
+
+We note that the survey scenario example changes the radius of the circular trajectory $\varphi_1$ through the parameter $c_{1,1}$.
+It also changes the radius of $\varphi_5$ in the same way (recall Assumption~\ref{assm:periodic}).
+The other trajectories ($\varphi_2,\varphi_3,\varphi_4$) displacement alters the distance between the lines in the survey.
+For simplicity, we suppose line~\ref{code:triggerlast} describes the final point.
+We further suppose the user does not desire to process any computation in the last stage $\Gamma_5$.
 To inhibit the computations
@@
 If there are any following stages in the survey, they are constructed the same way.
-The stages $\mathcal{M}_i$ for $i:=\{0,4,8,\dots\}$ contain TEE circle with variable radius.
-For $i:=\{1,3,5,\dots\}$ TEE line with variable displacement.
-For $i:=\{2,6,10,\dots\}$ TEE circle with fixed radius and variable displacement.
-
-We need a further abstraction before we can simulate a mission in Appendix~\ref{app:simulator}. The algorithm needs to know how to model the tasks--the software components.
-
-\section{Simulator}
-\label{app:simulator}
-
-We discuss how to execute the initial mission plan and the component specification in the simulator.
+The stages $\Gamma_i$ for $i:=\{0,4,8,\dots\}$ contain trajectory circle with variable radius.
+For $i:=\{1,3,5,\dots\}$ trajectory line with variable displacement.
+For $i:=\{2,6,10,\dots\}$ trajectory circle with fixed radius and variable displacement.
+
+%We need a further abstraction before we can simulate a mission in Appendix~\ref{app:simulator}. The algorithm needs to know how to model the tasks--the software components.
+
+%\section{Simulator}
+%\label{app:simulator}
+
+%We discuss how to execute the initial mission plan and the component specification in the simulator.
 The reader can use the simulator to simulate different environmental interference and their effects on the mission.
 
-The simulator is written in MATLAB and released under MIT license.
+%The simulator is written in MATLAB and released under MIT license.
 It implements the algorithm (Subsection~\ref{sec:algo}) providing a position $\mathbf{p}_k$ at each time step $k$ and an energy sensor's value $y_k^a$.
@@
 
-The user is prompted to initialize the trajectory and the algortihm.
+%The user is prompted to initialize the trajectory and the algortihm.
 

### 2020-12-17 scripts/energy/build_model.m
fixed some minor things

@@ -32,7 +32,7 @@ function [A, B, C, u, h] = build_model(r, xi, gck, mk)
     
     for i = 1:r
         A(2 * i : 2 * i + 1, 2 * i : 2 * i + 1) = An(i); 
-        C = [C 1 1];
+        C = [C 1 0];
         h = h + 1 * q(2 * i) * cos(i * k / xi) + ...
                 1 * q(2 * i + 1) * sin(i * k / xi);
     end

### 2020-12-18 icra-2021.tex
added new figure
fixed some minor things
implementing Ulrik's suggestions

@@
 \usepackage{hyperref}
+\makeatletter
+\newcommand*{\textlabel}[2]{%
+  \edef\@currentlabel{#1}% Set target label
+  \phantomsection% Correct hyper reference link
+  #1\label{#2}% Print and store label
+}
+\makeatother
 
@@
 
+% for bibliography (double column balances)
+
+\usepackage{balance}
+
 %% references (generates a bib file for bibtex)
@@
   \input{\figpath/il_abs_energy.tikz}
-  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, travels a more accurate survey than \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}) and computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, elaborates more images per second than \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:i}~travels a more accurate survey than~\ref{sth:ii}) and computations (\ref{sth:a}~elaborates more images per second than~\ref{sth:b}).
 In bottom right, the collected energy data of the UAV flying the scenario, along the power spectrum (small rectangle) where the first frequency has been filtered.}
@@
 Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations.
-We present here a brief summary of the algorithm.
-To model the path we use multiple trajectories and denote each of them with a mathematical function.
+To model the path we use multiple trajectories and denote each with a mathematical function.
 In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
@@
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
+In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along the power spectrum plot motivates out choice.
 The observation applies broadly; we show different UAV scenarios that can produce such periodic energy consumption evolution.
@@
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:il-abs} shows a slice of such and the small plot shows the periodicity from the collected energy data.
-The small rectangle shows the spectrum power with the first frequency filtered, showing thus that three frequencies are mostly necessary to model the energy.
+Figure~\ref{fig:il-abs} shows a slice of such plan.
 Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}).
@@
 The remainder of the paper is organized as follows.
-The overview of dynamic planning is provided in Section~\ref{sec:prob}, and the problem is set with some preliminaries in Section~\ref{sec:prelim}.
-A suitable model for the energy in Section~\ref{sec:energy-model}.
-The algorithm is proposed in Section~\ref{sec:algo}.
+The overview of dynamic planning, some preliminaries, and problem definition is provided in Section~\ref{sec:prob}.
+We show a suitable model for the energy in Section~\ref{sec:energy-model}, and propose the algorithm in Section~\ref{sec:algo}.
 Section~\ref{sec:experimental} presents the result and showcases the performances.
 We propose some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.
+Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:plan-spec}.
 
@@
 
-The algorithm plans the path and computations from a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation.
-At each stage, the UAV must follow a trajectory within the trajectory constraints set and do the computations within the computations constraints sets.
-There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter.
-The user specifies the maximum, minimum, and current levels of some parameters relative to the path and computations in such plan with an energy budget.
+The algorithm inputs an user-specified initial plan that consist of different stages.
+At each stage the UAV flies a trajectory, and does some computations.
+Per each stage the plan contains some parameters that allow to change the path and computations along an energy budget.
+These parameters are bounded.
+There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, which bound computations.
 In Figure~\ref{fig:il-abs}, there are two parameters.
-The radius of the trajectory circle is relative to the trajectory (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;} and \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
-The quality of image detection is relative to the computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;} and \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}).
+The radius of the trajectory circle is relative to the trajectory (\ref{sth:i}~and~\ref{sth:ii}).
+The quality of image detection is relative to the computations (\ref{sth:a}~and~\ref{sth:b}).
+
 The algorithm outputs the parameters (the control) using output model predictive control (MPC)~\cite{rawlings2017model}.
@@
 
-\subsection{Preliminaries and Problem Definition}
+\subsection{Plan definition}
 \label{sec:prelim}
@@
 The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list of $n$ parameters.
+
+\begin{figure}[h]
+  \centering
+  \input{\figpath/traj1.tikz}
+  \caption{Illustrative figure shows notation on a small initial slice of the plan in Figure~\ref{fig:il-abs}.}
+  \label{fig:traj1}
+\end{figure}
 
@@
 some inertial navigation frame $\mathcal{O}_W$.
+In Figure~\ref{fig:traj1} $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$,$\varphi_4$, and $\varphi_6$ are lines.
+They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
+The constaints set $\mathbb{C}_1,\mathbb{C}_2,\dots$ forms the set $\mathcal{P}_i$ which disclose the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be replanned with the parameters $c_{i,1},\dots,c_{i,\sigma}$ forming the path $\mathcal{P}$.
+We define the area $\mathcal{P}_i$ formally in Subsection~\ref{sec:model}.
 
@@
 
+\subsection{Problem formulation}
+
 In order to formulate the problem, we considerate the assumption.
@@
   \centering
-  \input{\figpath/path2.tikz}
-  \caption{Illustrative example of the alteration of a trajectory parameter}
+  \input{\figpath/traj2.tikz}
+  \caption{Illustrative figure shows of the alteration of the trajectory parameter $c_{1,1}$, the radius of the circle. The figure shows the alteration of the path from Figure~\ref{fig:il-abs}.}
   \label{fig:tee1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\balance
 \bibliographystyle{IEEEtran}
@@
 \leavevmode\thispagestyle{empty}\newpage
+\nobalance
 
@@
 \section{Plan Specification}
+\label{app:plan-spec}
 
 \subsection{Format}
-\label{app:plan-spec}
 

### 2020-12-19 icra-2021.tex
fixed some issue in the text

@@
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
-In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along the power spectrum plot motivates out choice.
-The observation applies broadly; we show different UAV scenarios that can produce such periodic energy consumption evolution.
+In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along the power spectrum plot motivates our choice.
+The observation applies broadly; we show different UAV scenarios that can produce a periodic energy consumption evolution.
 Moreover, we briefly investigate periodic energy consumption evolution in some ground-based mobile robots.
@@
 Figure~\ref{fig:il-abs} shows a slice of such plan.
-Computations significantly impact the battery, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}).
+Computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}), in presence of a standard battery.
 
 The remainder of the paper is organized as follows.
-The overview of dynamic planning, some preliminaries, and problem definition is provided in Section~\ref{sec:prob}.
+The overview of dynamic planning, some preliminaries, and problem definition are provided in Section~\ref{sec:prob}.
 We show a suitable model for the energy in Section~\ref{sec:energy-model}, and propose the algorithm in Section~\ref{sec:algo}.
-Section~\ref{sec:experimental} presents the result and showcases the performances.
+In Section~\ref{sec:experimental}, we present the result and showcases the performances.
 We propose some conclusions in Section~\ref{sec:conclusion}.
@@
 
-The algorithm inputs an user-specified initial plan that consist of different stages.
+The algorithm inputs a user-specified initial plan that consist of different stages.
 At each stage the UAV flies a trajectory, and does some computations.
-Per each stage the plan contains some parameters that allow to change the path and computations along an energy budget.
-These parameters are bounded.
+Per each stage the plan contains some parameters that allow to alter the path and computations along an energy budget.
+These alterations are bounded.
 There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, which bound computations.
@@
 The algorithm outputs the parameters (the control) using output model predictive control (MPC)~\cite{rawlings2017model}.
-The UAV utilizes the control to alter its energy consumption to meet the energy budget.
+The UAV utilizes the control to influence its energy consumption to meet the energy budget.
 The control is data-driven.
-Energy sensor data estimates coefficients of the energy model used to predict future energy consumption and derive the control, replanning the initial plan in presence of uncertainty.
+Energy sensor data estimates coefficients of the energy model used to predict future energy consumption in presence of uncertainty.
 The energy budget is the battery capacity and some other battery parameters.
+These are fixed values that are not replanned by the algorithm.
 Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
-The term parameters should not be confused with the battery parameters, which we always mention explicitly.
-These are fixed values that are not replanned by the algorithm.
 
@@
 \label{sec:prelim}
-
-Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters and the computations with $\sigma$ computations parameters.
-We then express the trajectory as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the trajectory parameters.
-The function returns a metric of the distance between the point and the nominal trajectory.
-We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
 
@@
 
+Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters and the computations with $\sigma$ computations parameters.
+We then express the trajectory as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the trajectory parameters.
+The function returns a metric of the distance between the point and the nominal trajectory.
+We express the computations as the value of the computations parameters.
+We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
+
 \begin{figure}[h]
@@
 \begin{defn}[Stage, plan, triggering, and final point]\label{def:mission}
-  A \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
+  The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
   \begin{equation}\label{eq:mission}\begin{split}
     \Gamma_i:=\{\langle&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),c_{i,\rho+1},\dots,c_{i,\rho+\sigma}\rangle\\\mid
-    &\,\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i,\,\\
-      &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathbb{S}_{i,j}\,\},
+    &\,\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathcal{C}_i,\,\\
+      &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathcal{S}_{i,j}\,\},
   \end{split}\end{equation}
-  where $\mathbb{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathbb{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraints set.
+  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraints set.
 $\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
 some inertial navigation frame $\mathcal{O}_W$.
-In Figure~\ref{fig:traj1} $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$,$\varphi_4$, and $\varphi_6$ are lines.
+In Figure~\ref{fig:traj1}, $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$,$\varphi_4$, and $\varphi_6$ are lines.
 They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
-The constaints set $\mathbb{C}_1,\mathbb{C}_2,\dots$ forms the set $\mathcal{P}_i$ which disclose the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be replanned with the parameters $c_{i,1},\dots,c_{i,\sigma}$ forming the path $\mathcal{P}$.
-We define the area $\mathcal{P}_i$ formally in Subsection~\ref{sec:model}.
-
-  The \emph{plan} is a finite state machine $\Gamma$ where the state-transition function $\delta:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+The constaints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\sigma}$ (gray area in the figure).
+
+  The \emph{plan} is a finite state machine (FSM) $\Gamma$ where the state-transition function $\delta:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
   \begin{equation*}\delta(\Gamma_i,\mathbf{p}_k):=\begin{cases}
@@
   The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+In Figure~\ref{fig:traj1}, $\mathbf{p}_{\Gamma_1}$ allows the transition between $\Gamma_1$ and $\Gamma_2$, $\mathbf{p}_{\Gamma_4}$ between $\Gamma_4$ and $\Gamma_5$, and $\mathbf{p}_{\Gamma_5}$ between $\Gamma_5$ and $\Gamma_6$.
 The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to last stage $\Gamma_l$ is called \emph{final point}.
@@
   \end{tikzpicture}
-  \caption{The plan defined as a finite state machine}
+  \caption{The plan defined as a FSM}
   \label{fig:state-machine}
@@
 
-A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages.
+A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages with the FSM.
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to stage $\Gamma_i$.
@@
   \end{tikzpicture}
-  \caption{Detail of the stage $\Gamma_i$ in the finite state machine}
+  \caption{Detail of the stage $\Gamma_i$ in the FSM}
   \label{fig:state-machine2}
@@
 
-In order to formulate the problem, we considerate the assumption.
+In order to formulate the problem, we considerate the next assumption.
 
@@
 
-The algorithm measures the time between the stages and assumes the initial period is one.
-We note that periods between stages same stages but different $j$s might be different due to atmospheric interferences.
+The algorithm measures the time between the stages and assumes the initial period is one. We note that periods might be different for different $j$s due to atmospheric interferences.
 
@@
 The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for the periodicity.
-The algorithm finds $n$ starting from one and finding the value which satisfies the proposition.
+The algorithm finds $n$ initializing it to one and finding the value which satisfies the proposition.
 
 \begin{pb}[UAV planning problem]\label{pb}
-  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic}.
-We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
+  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} that satisfies Assumption~\ref{assm:periodic}.
+We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and in the guidance to the path resulting from such plan for the UAV planning problem.
 \end{pb}
@@
 
-We proof a relation between the energy signal and the energy coefficients in Theorem~\ref{thm:state-vs-energy}.
+We proof a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
 We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
-Once we illustrate the energy model, we enhance it with the energy contribution of the computations in Subsection~\ref{sec:computations-model}.
+Once we illustrate the energy model, we enhance it with the energy contribution of the trajectory in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
 
@@
 
-The energy signal can be modeled by Equation~\ref{eq:fourier} and the output of a linear model
+The energy signal can be modeled by Equation~\ref{eq:fourier} and by the output of a linear model
 \begin{equation}\label{eq:state-perf}\begin{split}
@@
 
-Linear model in Equation~\ref{eq:state-perf} allows us to include the control in the model of Equation~\ref{eq:fourier}.
-The algorithm uses the model to find the control sequence that results in the optimal parameters configuration (using MPC).
+The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
+In fact, the algorithm uses the model to find the control sequence that results in the optimal parameters configuration (using MPC).
 
@@
   \end{equation*} 
-  Then, the signal $h$ in Equation~(\ref{eq:fourier}) is equal to the signal $y$ in Equation~(\ref{eq:state-perf}).
+  Then, the signal $h$ in Equation~(\ref{eq:fourier}) is equal to the output $y$ in Equation~(\ref{eq:state-perf}).
 \end{lem}
 \begin{proof}
-The equivalence of the models is trivial and the equality of the two signals is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+The equivalence of the models is trivial and the equality of the signal and output is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
 We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof of the equality where we justify the choices of the items of the matrices and of the initial guess.
@@
 They are derived using the modeling tool.
-We use the gain factors to select the optimal control $\mathbf{u}^0$.
-
-Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
-For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$, for a given $\nu_{1,1}\in\mathbb{R}_{<0}$.
 
@@
 
+Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
+For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$, for a given $\nu_{1,1}\in\mathbb{R}_{<0}$.
+This is then summed to the first coefficient $\alpha_0$, shifting the modeled energy.
+
 Let us assume that the set
 \begin{equation}\label{eq:area}
-  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
+  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathcal{C}_i\},
 \end{equation}
@@
 They are a way to alter the nominal trajectory in the initial plan and thus alter the energy signal.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
+The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
 
@@
 where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
 
@@
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and the tool changes the detection frequency to build a model.
-The model is then a linear multivariate interpolation for all the parameters.
+For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and the tool changes the detection frequency.
 
@@
 
-Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
+We assume that at least one period in the initial plan is valid.
 
@@
 
+Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
+
 \begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~\ref{eq:state-perf}, and the plan is periodic).
+  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
 Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
@@
 
-This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$.
+This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathcal{C}_1$.
 It can alter the computations individually.
-In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.
+In fact the $j$-th computation parameter has to be in $\mathcal{S}_{1,j}$.
 
@@
 \end{algorithmic}
-line~\ref{code:teeset} corresponds to the trajectory $\varphi_1$'s contraints set $\mathbb{C}_1=[-3\cdot10^3,0]$.
-The algorithm selects $c_{1,1}\in\mathbb{C}_1$.
-Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathbb{S}_{1,1}$ for the computation parameter $c_{1,2}$.
-Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathbb{S}_{1,2}$ for the computation parameter $c_{1,2}$.
+line~\ref{code:teeset} corresponds to the trajectory $\varphi_1$'s contraints set $\mathcal{C}_1=[-3\cdot10^3,0]$.
+The algorithm selects $c_{1,1}\in\mathcal{C}_1$.
+Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathcal{S}_{1,1}$ for the computation parameter $c_{1,2}$.
+Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathcal{S}_{1,2}$ for the computation parameter $c_{1,2}$.
 Lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of the parameters.

### 2020-12-22 scripts/plots/generate_il_abs.sh
update the illustrative abstract with Ulrik's suggestion

@@ -7,23 +7,23 @@ gnuplot -e "
     unset title;
     set border lw .5;
     set xrange [0:320];
-    set xtics 100 center offset .6,.5 font 'Times,8';
-    set yrange [19:41];
+    set xtics 100 center offset -.0,.5 font 'Times,8';
+    set yrange [19:31];
     set ytics 5 center offset -.3,0 font 'Times,8';
     set xlabel 'Time (sec)' rotate parallel center offset -.7,1.1 font 'Times,8';
     set ylabel 'Power (W)' rotate parallel center offset 2.5,-.1 font 'Times,8';
     set key font 'Times,8';
-    set multiplot;
     plot 'periodic_energy.csv' using 1:2 w l notitle lc rgb 'black' lw .5;
-    set size 0.5, 0.5;
-    set origin 0.5, 0.5;
-    unset xtics;
-    unset ytics;
-    unset xlabel;
+    pause -1;
+    set term qt size 160,120;
     unset ylabel;
+    unset ytics;
+    set xtics ('-2' -0.02, '0' 0, '2' 0.02) center offset -.1,.5 font 'Times,8';
+    set y2tics ('0' 0, '2' 200, '4' 400) center offset -.3,0 font 'Times,8';
+    set xlabel 'Frequency (cHz)' rotate parallel center offset .1,1.1 font 'Times,8';
+    set y2label 'Spectrum (hdB)' rotate parallel center offset -2,-.1 font 'Times,8';
     set xrange [-0.03:0.03];
-    set yrange [0:500];
-    plot 'spectrum.csv' using 1:2 w l notitle lc rgb 'black' lw .5;
-    unset multiplot;
+    set y2range [0:500];
+    plot 'spectrum.csv' using 1:2 w l notitle lc rgb 'black' lw .5 axes x1y2;
     pause -1;
 "

### 2020-12-22 scripts/plots/il_abs.m

@@ -44,8 +44,8 @@ f0 = (-n/2:n/2-1)*(fs/n); % 0-centered frequency range
 
 figure(3);
 plot(f0,power0((end-n)/2+1:(end+n)/2))
-xlabel('Frequency')
-ylabel('Power')
+xlabel('Frequency (Hz)')
+ylabel('Power (dB)')
 
 csvwrite('periodic_energy.csv', [t x2]);
 csvwrite('spectrum.csv', [f0' power0((end-n)/2+1:(end+n)/2)]);

### 2020-12-23 icra-2021.tex
update the illustrative abstract with Ulrik's suggestion
fixed typos here and there

@@
   \centering
-  \input{\figpath/il_abs.tikz}
-  \input{\figpath/il_abs_energy.tikz}
+  \begin{tikzpicture}
+    \node[inner sep=0pt] () at (0,0)
+        {\input{\figpath/il_abs.tikz}};
+    \node[inner sep=0pt] () at (-1.7,-5.5)
+        {\footnotesize \input{\figpath/il_abs_energy.tikz}};
+    \node[inner sep=0pt] () at (1.9,-5.5)
+        {\footnotesize \input{\figpath/il_abs_spectrum.tikz}};
+  \end{tikzpicture}
   \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:i}~travels a more accurate survey than~\ref{sth:ii}) and computations (\ref{sth:a}~elaborates more images per second than~\ref{sth:b}).
-In bottom right, the collected energy data of the UAV flying the scenario, along the power spectrum (small rectangle) where the first frequency has been filtered.}
+In bottom left, the collected energy data of the UAV flying the scenario, along the power spectrum (bottom right) where the first frequency has been filtered.}
   \label{fig:il-abs}
@@
 In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along the power spectrum plot motivates our choice.
-The observation applies broadly; we show different UAV scenarios that can produce a periodic energy consumption evolution.
-Moreover, we briefly investigate periodic energy consumption evolution in some ground-based mobile robots.
+The observation applies broadly; we briefly investigate periodic energy consumption evolutions in some ground-based mobile robots.
 
@@
 We show a suitable model for the energy in Section~\ref{sec:energy-model}, and propose the algorithm in Section~\ref{sec:algo}.
-In Section~\ref{sec:experimental}, we present the result and showcases the performances.
+In Section~\ref{sec:experimental}, we present the results and showcases the performances.
 We propose some conclusions in Section~\ref{sec:conclusion}.
@@
 Per each stage the plan contains some parameters that allow to alter the path and computations along an energy budget.
-These alterations are bounded.
+The alterations are bounded.
 There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, which bound computations.
@@
 The control is data-driven.
-Energy sensor data estimates coefficients of the energy model used to predict future energy consumption in presence of uncertainty.
-The energy budget is the battery capacity and some other battery parameters.
+Energy sensor data estimates some coefficients of an energy model used to predict future energy consumption in presence of uncertainty.
+The energy budget is the battery capacity and other battery parameters.
 These are fixed values that are not replanned by the algorithm.
@@
 some inertial navigation frame $\mathcal{O}_W$.
-In Figure~\ref{fig:traj1}, $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$,$\varphi_4$, and $\varphi_6$ are lines.
+In Figure~\ref{fig:traj1}, $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
 They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
-The constaints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\sigma}$ (gray area in the figure).
+The constaints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\rho}$ (gray area in the figure).
 
@@
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to stage $\Gamma_i$.
-The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$ and $\mathbf{p}_{k_2}$.
+The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
 It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
@@
 Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
-See Figure~\ref{fig:state-machine2} where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
+We show this in Figure~\ref{fig:state-machine2}, where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
 
@@
 
-From Assumption~\ref{assm:periodic}, follows the next proposition.
+From Assumption~\ref{assm:periodic} follows the next proposition.
 
@@
 
-We model the energy using some energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
+We model the energy using energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
 We refer to the instantaneous energy consumption evolution simply as the energy signal.
@@
 
-Let us consider a periodic signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the signal
+Let us consider a periodic signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the energy signal
 \begin{equation}\label{eq:fourier}
@@
 
-The energy signal can be modeled by Equation~\ref{eq:fourier} and by the output of a linear model
+The energy signal can be modeled by Equation~(\ref{eq:fourier}) and by the output of a linear model
 \begin{equation}\label{eq:state-perf}\begin{split}
@@
   \input{\figpath/traj2.tikz}
-  \caption{Illustrative figure shows of the alteration of the trajectory parameter $c_{1,1}$, the radius of the circle. The figure shows the alteration of the path from Figure~\ref{fig:il-abs}.}
+  \caption{Illustrative figure shows the alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (the alteration of the path from Figure~\ref{fig:il-abs}).}
   \label{fig:tee1}
@@
 We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
-\begin{equation}\label{eq:pd}
+\begin{equation*}\label{eq:pd}
   \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
@@
   \end{bmatrix},
-\end{equation}
+\end{equation*}
 where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
 
@@
 
-Specifically, the computations are implemented by software components, such as ROS nodes in a ROS based system.
-The user implements these nodes s.t.
-they change the computational load by node-specific ROS parameters--the computations parameters.
+The computations are implemented by software components, such as ROS nodes in a ROS based system.
+The user implements these nodes in such a way that they change the computational load with node-specific ROS parameters, the computations parameters.
 In a generic software component system, the user maps the computational load to the arguments.
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds frames-per-second (fps) rate and the tool changes the detection frequency.
+For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds to frames-per-second (fps) rate.
+The tool then changes the detection frequency.
 
@@
 The gain factors that quantifies the contribution of the computations parameters
-\begin{equation}\label{eq:energy-comp}
+\begin{equation*}\label{eq:energy-comp}
   \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}^T=\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix}/\begin{bmatrix}c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}.
-\end{equation}
+\end{equation*}
 Moreover, let $g(\{\emptyset\})$ be zero.
@@
   The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path}
-  \begin{equation}\begin{split}\label{eq:mission-valid}
+  \begin{equation*}\begin{split}\label{eq:mission-valid}
    \mathcal{P}:=\{\mathbf{p}_k\mid&\,\exists \mathbf{u}_k,n\in\mathbb{Z}_{>0},\\
@@
     &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle\in\Gamma_i\},
-  \end{split}\end{equation}
+  \end{split}\end{equation*}
   where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k,1},\dots,$ $c_{k,\rho}),c_{k,\rho+1},\dots,c_{k,\rho+\sigma}\rangle$.
@@
 Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
-
-  ----
 \end{thm}
@@
 Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation}\begin{split}
+\begin{equation*}\begin{split}
   \mathrm{SoC}_k=-\left(V-
@@
   \right)/2R_rQ_c,\\ 
-\end{split}\end{equation}
+\end{split}\end{equation*}
 where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
 We define the output constraints set
-\begin{equation}
+\begin{equation*}
   \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
-\end{equation}
+\end{equation*}
 and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
+
+----
 

### 2021-01-03 icra-2021.tex
generating the data from the simulations

@@
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
-In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along the power spectrum plot motivates our choice.
+In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along its power spectrum plot motivates our choice.
 The observation applies broadly; we briefly investigate periodic energy consumption evolutions in some ground-based mobile robots.
@@
 Figure~\ref{fig:il-abs} shows a slice of such plan.
-Computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}), in presence of a standard battery.
+We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}), in presence of a standard battery.
 
@@
 The alterations are bounded.
-There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, which bound computations.
+There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, that bound computations.
 In Figure~\ref{fig:il-abs}, there are two parameters.
@@
 
-The algorithm outputs the parameters (the control) using output model predictive control (MPC)~\cite{rawlings2017model}.
+The algorithm outputs the control (the parameters) using output model predictive control (MPC)~\cite{rawlings2017model}.
 The UAV utilizes the control to influence its energy consumption to meet the energy budget.
@@
 some inertial navigation frame $\mathcal{O}_W$.
-In Figure~\ref{fig:traj1}, $\varphi_1$ and $\varphi_5$ are circles and $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
+In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are trajectories.
+$\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
 They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
 The constaints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\rho}$ (gray area in the figure).
+This area is bounded by $\underline{c}_i,\overline{c}_i$, and can be different per each stage (in Figure~\ref{fig:traj1}, the area relative to $\Gamma_4$ is bounded by $\underline{c}_4,\overline{c}_4$).
 
@@
 The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
-It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the last triggering point.
-
-Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
-We show this in Figure~\ref{fig:state-machine2}, where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
+It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
 
@@
 
+Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
+We show this in Figure~\ref{fig:state-machine2}, where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
+
 We refer the reader to an example in Appendix~\ref{app:plan-example} for a detailed implementation.
@@
 
-We store the plan in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
+We store the initial plan in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
 
@@
 \begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and the current levels of all the parameters $c_{1,1},\dots,c_{l,\rho+\sigma}$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
-  \begin{equation*}
-    \varphi_{(i-1)n+j}\approx \varphi_{in+j},\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
-  \end{equation*}
+  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the parameters $c_{1,1},\dots,c_{1,\rho}$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
+  \begin{equation*}\begin{split}
+    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1)\approx\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1),\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+  \end{split}\end{equation*}
 \end{assm}
 
-Physically, this means that the plan is periodic. We will see the assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
+Physically, this means that the plan is approximately periodic. We will see the assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
 
@@
   Suppose Assumption~\ref{assm:periodic} holds, then the plan $\Gamma$ is periodic if
-  \begin{equation*}
-    \varphi_{(i-1)n+j}-\varphi_{in+j}=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
-  \end{equation*}
+  \begin{equation*}\begin{split}
+    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1)=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+  \end{split}\end{equation*}
   Moreover, if the plan $\Gamma$ is periodic then
@@
         \varphi_n & \varphi_{2n} & \cdots & \varphi_l   
-      \end{bmatrix}=2.
+      \end{bmatrix}=2,
   \end{equation*}
+  where the trajectories in the first column are evaluated  on $\mathbf{p},c_1$, in the second on $\mathbf{p}+\mathbf{d},c_1$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1$.
 \end{prop}
-\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th ``shift''.
+\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th constant difference.
 This is equivalent to Assumption~\ref{assm:periodic}.

### 2021-01-03 scripts/SIM2.m

@@ -39,8 +39,6 @@ maxpw = strp(7);
 minpw = strp(8); 
 trigeps = strp(9);
 
-clear strp;
-
 % asking data about the algorithm
 
 answer = inputdlg(...
@@ -49,20 +47,18 @@ answer = inputdlg(...
     {'3','1','10'}); % asking for initial data
 
 if isempty(answer)
-    strp = [3; 1; 10]; % default initial data
+    strp2 = [3; 1; 10]; % default initial data
 else
-    strp = str2double(answer);
+    strp2 = str2double(answer);
 end
 
 clear answer;
 
 % stroing data
 
-r = strp(1);
-eps = strp(2);
-N = strp(3);
-
-clear strp;
+r = strp2(1);
+eps = strp2(2);
+N = strp2(3);
 
 % asking for the plan specifization 
 
@@ -329,6 +325,41 @@ plot(linspace(0, k, size(pow, 1)), pow(:, 1))
 
 subplot(2,2,4);
 plot(linspace(0, k, size(y, 1)), y(:, 1))
+
+figure(2);
+subplot(7,1,1);
+plot(q(1,1:end))
+
+subplot(7,1,2);
+plot(q(2,1:end))
+
+subplot(7,1,3);
+plot(q(3,1:end))
+
+subplot(7,1,4);
+plot(q(4,1:end))
+
+subplot(7,1,5);
+plot(q(5,1:end))
+
+subplot(7,1,6);
+plot(q(6,1:end))
+
+subplot(7,1,7);
+plot(q(7,1:end))
+
+
+%% saving data
+
+csvwrite('position_simulation3A.csv', [pos(:, 1) pos(:, 2) pdanglelist]);
+
+csvwrite('energy_simulation3A.csv', [linspace(0, k, size(pow, 1)), ...
+    pow(:, 1)', y(:, 1)', q(1,1:end), q(2,1:end), q(3,1:end),     ...
+    q(4,1:end), q(5,1:end), q(6,1:end), q(7,1:end)]);
+
+csvwrite('trajdata_simulation3A.csv', strp);
+
+csvwrite('algdata_simulation3A.csv', strp2);
 
 
 %% model building function

### 2021-01-05 scripts/SIM2.m
fixing the results section

@@ -351,15 +351,15 @@ plot(q(7,1:end))
 
 %% saving data
 
-csvwrite('position_simulation3A.csv', [pos(:, 1) pos(:, 2) pdanglelist]);
+csvwrite('position_simulation3D.csv', [pos(:, 1) pos(:, 2) pdanglelist]);
 
-csvwrite('energy_simulation3A.csv', [linspace(0, k, size(pow, 1)), ...
+csvwrite('energy_simulation3D.csv', [linspace(0, k, size(pow, 1)), ...
     pow(:, 1)', y(:, 1)', q(1,1:end), q(2,1:end), q(3,1:end),     ...
     q(4,1:end), q(5,1:end), q(6,1:end), q(7,1:end)]);
 
-csvwrite('trajdata_simulation3A.csv', strp);
+csvwrite('trajdata_simulation3D.csv', strp);
 
-csvwrite('algdata_simulation3A.csv', strp2);
+csvwrite('algdata_simulation3D.csv', strp2);
 
 
 %% model building function

### 2021-01-11 icra-2021.tex
fixing the results section
fixing the results section (2)
implementing thhe latests fixes

@@
     \node[inner sep=0pt] () at (0,0)
-        {\input{\figpath/il_abs.tikz}};
-    \node[inner sep=0pt] () at (-1.7,-5.5)
-        {\footnotesize \input{\figpath/il_abs_energy.tikz}};
+        {\footnotesize \input{\figpath/il_abs.tikz}};
+    \node[inner sep=0pt] () at (-1.9,-5.5)
+        {\footnotesize \input{\figpath/il_abs_energy1.tikz}};
     \node[inner sep=0pt] () at (1.9,-5.5)
-        {\footnotesize \input{\figpath/il_abs_spectrum.tikz}};
+        {\footnotesize \input{\figpath/il_abs_spectrum1.tikz}};
   \end{tikzpicture}
-  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:i}~travels a more accurate survey than~\ref{sth:ii}) and computations (\ref{sth:a}~elaborates more images per second than~\ref{sth:b}).
+  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:ii}~travels a more accurate survey than~\ref{sth:iii}) and computations (\ref{sth:i}~elaborates more images per second than~\ref{sth:ii}).
 In bottom left, the collected energy data of the UAV flying the scenario, along the power spectrum (bottom right) where the first frequency has been filtered.}
@@
 In Figure~\ref{fig:il-abs}, there are two parameters.
-The radius of the trajectory circle is relative to the trajectory (\ref{sth:i}~and~\ref{sth:ii}).
-The quality of image detection is relative to the computations (\ref{sth:a}~and~\ref{sth:b}).
+The radius of the trajectory circle is relative to the trajectory (\ref{sth:ii}~and~\ref{sth:iii}).
+The quality of image detection is relative to the computations (\ref{sth:i}~and~\ref{sth:ii}).
 
@@
 Moreover, let $g(\{\emptyset\})$ be zero.
+
+\begin{figure*}
+  \begin{tikzpicture}
+    \node[inner sep=0pt] () at (0,7)
+        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
+    \node[inner sep=0pt] () at (0,0)
+        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
+    \node[inner sep=0pt] () at (7.9,0)
+        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
+  \end{tikzpicture}
+  \caption{.}
+\end{figure*}
 

### 2021-01-11 scripts/SIM2.m

@@ -195,6 +195,8 @@ time = 0;
 
 v = 0;
 
+periodlist = [];
+
 for traj = transpose(path)
         
     traj = split(traj, ";");
@@ -206,7 +208,7 @@ for traj = transpose(path)
     end
         
     ke = str2double(traj(1));
-        
+    
     while true
         
         time = time + delta;
@@ -214,22 +216,26 @@ for traj = transpose(path)
         if period < time
         
             period = time;
+            
+            periodlist = [periodlist; k period];
         
             [A C] = build_model(2*pi/period, r);
             Ad = A*delta+eye(2*r+1);
         
             % re-initialization of the KF
-            P0 = ones(size(q,1));
+            %P0 = ones(size(q,1));
             
         elseif mod(i, n) == 0
         
             period = time;
+            
+            periodlist = [periodlist; k period];
         
             [A C] = build_model(2*pi/period, r);
             Ad = A*delta+eye(2*r+1);
             
             % re-initialization of the KF
-            P0 = ones(size(q,1));
+            %P0 = ones(size(q,1));
         
             time = 1;
         
@@ -378,6 +384,6 @@ function [A, C] = build_model(omega,r)
         C = [C 1 0];
     end
     
-    C = 1/1 * C;
+    C = 1/((2*pi)/omega) * C;
 
 end

### 2021-01-11 scripts/SIM3.m

@@ -1,0 +1,28 @@
+
+pow = cswread('');
+
+delta = pow(2,1)-pow(1,1);
+
+for sens=transpose(pow)
+   
+end
+
+%% model building function
+
+function [A, C] = build_model(omega,r)
+
+    m = 2*r+1;
+
+    Aj = @(omega, j) [0 omega*j ; -omega*j 0];
+    A  = zeros(m);
+    A(1,1) = 0;
+    C = [1];
+
+    for i = 1:r
+        A(2*i : 2*i + 1, 2*i : 2*i + 1) = Aj(omega, i); 
+        C = [C 1 0];
+    end
+    
+    C = 1/((2*pi)/omega) * C;
+
+end

### 2021-01-11 scripts/plots/il_abs.m

@@ -25,7 +25,7 @@ xline(250);
 xline(300); % just some lines at the hypothetical period 
 
 fs = 1/period; % frequency
-y = fft(x - mean(x)); % discrete fourier transform of the energy signal
+y = fft(x); % discrete fourier transform of the energy signal
 
 n = length(x); % number of samples
 f = (0:n-1)*(fs/n); % frequency range
@@ -47,6 +47,6 @@ plot(f0,power0((end-n)/2+1:(end+n)/2))
 xlabel('Frequency (Hz)')
 ylabel('Power (dB)')
 
-csvwrite('periodic_energy.csv', [t x2]);
-csvwrite('spectrum.csv', [f0' power0((end-n)/2+1:(end+n)/2)]);
+%csvwrite('periodic_energy.csv', [t x2]);
+csvwrite('spectrum2.csv', [f0' power0((end-n)/2+1:(end+n)/2)]);
 

### 2021-01-11 scripts/simulate.m

@@ -88,6 +88,7 @@ function [k pos pow est ua] = simulate(varphi, trigger, trajparams, mpcparams, s
 
     for varphii = transpose(varphi) % per each TEE
         
+        pdanglelist = [pdanglelist; pdangle];
         varphii = split(varphii, ";");
         
         fprintf('varphi%d((%d,%d)):=%s\n', i, nowpos(1), nowpos(2), varphii(3));

### 2021-01-11 scripts/SIM2.m
implementing thhe latests fixes (2)

@@ -223,7 +223,7 @@ for traj = transpose(path)
             Ad = A*delta+eye(2*r+1);
         
             % re-initialization of the KF
-            %P0 = ones(size(q,1));
+            P0 = ones(size(q,1));
             
         elseif mod(i, n) == 0
         
@@ -235,7 +235,7 @@ for traj = transpose(path)
             Ad = A*delta+eye(2*r+1);
             
             % re-initialization of the KF
-            %P0 = ones(size(q,1));
+            P0 = ones(size(q,1));
         
             time = 1;
         
@@ -357,15 +357,17 @@ plot(q(7,1:end))
 
 %% saving data
 
-csvwrite('position_simulation3D.csv', [pos(:, 1) pos(:, 2) pdanglelist]);
+csvwrite('position_simulation3A.csv', [pos(:, 1) pos(:, 2) pdanglelist]);
 
-csvwrite('energy_simulation3D.csv', [linspace(0, k, size(pow, 1)), ...
-    pow(:, 1)', y(:, 1)', q(1,1:end), q(2,1:end), q(3,1:end),     ...
-    q(4,1:end), q(5,1:end), q(6,1:end), q(7,1:end)]);
+csvwrite('energy_simulation3A.csv', [linspace(0, k, size(pow, 1))', ...
+    pow(:, 1), y(:, 1), q(1,1:end)', q(2,1:end)', q(3,1:end)',     ...
+    q(4,1:end)', q(5,1:end)', q(6,1:end)', q(7,1:end)']);
 
-csvwrite('trajdata_simulation3D.csv', strp);
+csvwrite('trajdata_simulation3A.csv', strp);
 
-csvwrite('algdata_simulation3D.csv', strp2);
+csvwrite('algdata_simulation3A.csv', strp2);
+
+csvwrite('perioddata_simulation3A.csv', periodlist);
 
 
 %% model building function
@@ -383,7 +385,5 @@ function [A, C] = build_model(omega,r)
         A(2*i : 2*i + 1, 2*i : 2*i + 1) = Aj(omega, i); 
         C = [C 1 0];
     end
-    
-    C = 1/((2*pi)/omega) * C;
 
 end

### 2021-01-11 scripts/SIM3.m

@@ -1,28 +1,0 @@
-
-pow = cswread('');
-
-delta = pow(2,1)-pow(1,1);
-
-for sens=transpose(pow)
-   
-end
-
-%% model building function
-
-function [A, C] = build_model(omega,r)
-
-    m = 2*r+1;
-
-    Aj = @(omega, j) [0 omega*j ; -omega*j 0];
-    A  = zeros(m);
-    A(1,1) = 0;
-    C = [1];
-
-    for i = 1:r
-        A(2*i : 2*i + 1, 2*i : 2*i + 1) = Aj(omega, i); 
-        C = [C 1 0];
-    end
-    
-    C = 1/((2*pi)/omega) * C;
-
-end

### 2021-01-15 icra-2021.tex
added the plot with coefficients
added the edata with the time evolution of the model

@@
   \begin{tikzpicture}
-    \node[inner sep=0pt] () at (0,7)
+    \node[inner sep=0pt] () at (-1,7)
         {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
+      \node[inner sep=0pt] () at (4.8,7)
+        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
+    \node[inner sep=0pt] () at (9.3,7)
+        {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
     \node[inner sep=0pt] () at (0,0)

### 2021-01-15 scripts/plots/evolve_sim.m

@@ -1,0 +1,62 @@
+
+
+% load data from simulation 3 D (raw5)
+
+%load('../../data/simulation3/raw5/updated/simulation3D.mat');
+
+% load data from simulation 
+
+load('../../data/simulation3/raw2/updated/simulation3A.mat');
+
+qq0 = q(:, 200/delta);
+yy = [];
+
+ddelta = delta/5; % refinining the delta little more
+
+AAd = A*ddelta+eye(2*r+1);
+
+% get the estimated coefficients with KF at time 200 s on
+% that's the horizon of the plot in the results section in the papaer
+
+yyy = [];
+yyr = [];
+
+jj = 1;
+
+for j=20000:period/delta:length(q)
+    
+    qq0 = q(:, uint64(j));
+    yy = [];
+    
+    for ii=0:ddelta:200 % evolution up to the next 200 s
+
+        qq1 = AAd*qq0;
+        yy = [yy; C*qq1];
+        qq0 = qq1;
+    
+    end
+    
+    yyy = [yyy yy];
+    yyr = [yyr imresize(yy, [400 1])];
+    
+    figure(1)
+	plot(linspace(200, 400, length(yy)), yy)
+   
+    legendInfo{jj} = [num2str(uint64(j))]; 
+    
+    hold on;
+
+    figure(2)
+	plot(linspace(200, 400, length(yyr(:,jj))), yyr(:,jj))
+    
+    legendInfo{jj} = [num2str(uint64(j))]; 
+    jj = jj + 1;
+    
+    hold on;
+    
+end
+
+legend(legendInfo);
+
+csvwrite('evolution_simulation3A.csv', [linspace(200, 400, 400)' yyr]);
+

### 2021-01-17 icra-2021.tex
results for fixed plan ready

--- 2021-01-11 icra-2021.tex
@@
 \begin{figure*}
+  \hspace{-2ex}
   \begin{tikzpicture}
-    \node[inner sep=0pt] () at (0,7)
+    \node[inner sep=0pt] () at (0,0)
         {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3,-4) {\footnotesize {(a) path simulation, {\color{red}+} is the UAV location after 200 seconds}};
+    \node[inner sep=0pt] () at (8.3,-.02)
+        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (5.6,-4) {\footnotesize {(b) energy evolution simulation in 200 seconds interval}};
+  \end{tikzpicture}
+  \caption[Path and energy simulation of a static plan]{Path and energy simulations with different atmospheric conditions.
+Simulations are performed from collected data by variations of wind speed and direction.
+The path and computations are static}
+  \label{fig:res1}
+\end{figure*}
+\begin{figure*}
+  \begin{tikzpicture}
+    \node[inner sep=0pt] () at (6,0)
+        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(a) slice of the simulated energy along the estimated model}};
+    \node[inner sep=0pt] () at (10.6,.05)
+        {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(b) model evolution at different $k$s}};
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
-    \node[inner sep=0pt] () at (7.9,0)
         {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.6,-4) {\footnotesize {(c) coefficients evolution}};
   \end{tikzpicture}
-  \caption{.}
+  \caption[] {Evolution of the simulated energy data from Figure~\ref{fig:res1}, using the estimation first in~\ref{}, the data with no estimation predicting the future in~\ref{}, and evolution of the estimated coefficients in~\ref{}}
 \end{figure*}

### 2021-01-18 icra-2021.tex
updated figures in the paper

@@
 \begin{figure*}
-  \hspace{-2ex}
+  \hspace*{-2ex}
   \begin{tikzpicture}
@@
 The path and computations are static}
-  \label{fig:res1}
+  \label{fig:sim-static-plan}
 \end{figure*}
 \begin{figure*}
+  \hspace*{-3.4ex}
   \begin{tikzpicture}
+    \node[inner sep=0pt] () at (0,0)
+        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(\textlabel{a}{fig:evol-static-plan:a}) slice of the simulated energy along the estimated model}};
     \node[inner sep=0pt] () at (6,0)
         {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(a) slice of the simulated energy along the estimated model}};
-    \node[inner sep=0pt] () at (10.6,.05)
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(\textlabel{b}{fig:evol-static-plan:b}) model evolution at different $k$s}};
+    \node[inner sep=0pt] () at (10.8,.05)
         {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(b) model evolution at different $k$s}};
-    \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.6,-4) {\footnotesize {(c) coefficients evolution}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.6,-4) {\footnotesize {(\textlabel{c}{fig:evol-static-plan:c}) coefficients evolution}};
   \end{tikzpicture}
-  \caption[] {Evolution of the simulated energy data from Figure~\ref{fig:res1}, using the estimation first in~\ref{}, the data with no estimation predicting the future in~\ref{}, and evolution of the estimated coefficients in~\ref{}}
+  \caption[] {Evolution of the simulated energy data from Figure~\ref{fig:sim-static-plan}, using the estimation first in~\ref{fig:evol-static-plan:a}, the data with no estimation predicting the future in~\ref{fig:evol-static-plan:b}, and evolution of the estimated coefficients in~\ref{fig:evol-static-plan:c}}
+  \label{fig:evol-static-planned}
 \end{figure*}

### 2021-01-18 icra-2021.tex
update/fixed up to the Algorithm section

@@
 The alterations are bounded.
-There is one trajectory constraints set which bounds the path and multiple computations constraints sets, one per each computation parameter, that bound computations.
+There is one trajectory constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations.
 In Figure~\ref{fig:il-abs}, there are two parameters.
-The radius of the trajectory circle is relative to the trajectory (\ref{sth:ii}~and~\ref{sth:iii}).
-The quality of image detection is relative to the computations (\ref{sth:i}~and~\ref{sth:ii}).
+The radius of the trajectory circle is relative to the trajectory (\ref{sth:ii}~has indeed a shorter distance between the survey lines then~\ref{sth:iii}).
+The quality of image detection is relative to the computations (\ref{sth:i}~processes more images per second then~\ref{sth:ii}).
 
@@
 a given cost function $l$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
-The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list of $n$ parameters.
-
-Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters and the computations with $\sigma$ computations parameters.
+The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list $\langle c_i \rangle$ of $n$ parameters.
+
+Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computations parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
 We then express the trajectory as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the trajectory parameters.
@@
   \end{split}\end{equation}
-  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraints set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraints set.
+  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
 $\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
@@
 In Figure~\ref{fig:traj1}, $\mathbf{p}_{\Gamma_1}$ allows the transition between $\Gamma_1$ and $\Gamma_2$, $\mathbf{p}_{\Gamma_4}$ between $\Gamma_4$ and $\Gamma_5$, and $\mathbf{p}_{\Gamma_5}$ between $\Gamma_5$ and $\Gamma_6$.
-The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to last stage $\Gamma_l$ is called \emph{final point}.
+The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$ is called \emph{final point}.
 \end{defn}
@@
 A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages with the FSM.
-The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to stage $\Gamma_i$.
+The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to the stage $\Gamma_i$.
 The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
@@
     \path[->]
-    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1,\dots,c_{i-1})$} (q_0)
-    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1,\dots,c_{i})$} (q_dots1)    
+    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1^\rho,\dots,c_{i-1}^\rho)$} (q_0)
+    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1^\rho,\dots,c_{i}^\rho)$} (q_dots1)    
     (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
@@
 
-Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i,1},\dots,c_{i,\rho}$, or any previous trajectory parameters, propagating the information therein if necessary.
-We show this in Figure~\ref{fig:state-machine2}, where, for simplicity, we neglected the $\sigma=0$ computations parameters, so $c_i=c_{i,1},\dots,c_{i,\rho}$.
+Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
 
@@
 \begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the parameters $c_{1,1},\dots,c_{1,\rho}$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
+  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the trajectory parameters $c_1^\rho$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
   \begin{equation*}\begin{split}
-    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1)\approx\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1),\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)\approx\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho),\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
   \end{split}\end{equation*}
@@
 
-Physically, this means that the plan is approximately periodic. We will see the assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
+Physically, this means that the plan is approximately periodic.
+The justification for this strong assumptions originates from empirical data (we refer the reader back to the illustrative abstract in Figure~\ref{fig:il-abs}).
+It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over trajectories and computations attending some triggering events (such as detections).
+We will see this assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
 
@@
 \begin{prop}[Necessary and sufficient condition for periodicity]\label{prop:rank}
-  Suppose Assumption~\ref{assm:periodic} holds, then the plan $\Gamma$ is periodic if
+  The plan $\Gamma$ is periodic if
   \begin{equation*}\begin{split}
-    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1)=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
   \end{split}\end{equation*}
-  Moreover, if the plan $\Gamma$ is periodic then
+  Moreover, if the plan $\Gamma$ is periodic, then
   \begin{equation*}
@@
   \end{equation*}
-  where the trajectories in the first column are evaluated  on $\mathbf{p},c_1$, in the second on $\mathbf{p}+\mathbf{d},c_1$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1$.
+  where the trajectories in the first column are evaluated on $\mathbf{p},c_1^\rho$, in the second on $\mathbf{p}+\mathbf{d},c_1^\rho$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1^\rho$.
 \end{prop}
@@
 
-The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for the periodicity.
+The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for periodicity.
 The algorithm finds $n$ initializing it to one and finding the value which satisfies the proposition.
@@
 \begin{pb}[UAV planning problem]\label{pb}
-  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} that satisfies Assumption~\ref{assm:periodic}.
-We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and in the guidance to the path resulting from such plan for the UAV planning problem.
+  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission} that satisfies Assumption~\ref{assm:periodic}.
+We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and in the guidance to the path resulting from such plan for the UAV planning problem.
 \end{pb}
@@
 
+We refer to the instantaneous energy consumption evolution simply as the energy signal.
 We model the energy using energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
-We refer to the instantaneous energy consumption evolution simply as the energy signal.
-The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and estimated using a state estimator (Kalman filter).
+The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and estimated using a state estimator.
+%(Kalman filter); well, potentially here with simulated data one could use other estimators (least square filter would work I bet)
 
@@
 The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
-In fact, the algorithm uses the model to find the control sequence that results in the optimal parameters configuration (using MPC).
-
-\begin{lem}[Signals equality]\label{lem:eqv}Suppose control is zero, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is 
+The algorithm uses the model to find the control sequence that results in the optimal parameters configuration.
+%(using MPC)
+
+\begin{lem}[Signals equality]\label{lem:eqv}Suppose control $\mathbf{u}$ is a zero vector, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is 
   \begin{equation*}
@@
 The first $\rho$ gain factors quantifies the contribution of the $i$-th trajectory parameters.
-A first guess of these parameters is derived empirically.
-They are later refined by the algorithm.
 The following $\sigma$ gain factors quantifies the contribution of the computations parameters.
-They are derived using the modeling tool.
+We elucidate how we derive these factors in the next two subsections.
 
@@
 They are a way to alter the nominal trajectory in the initial plan and thus alter the energy signal.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).
-The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the optimal trajectory parameters $c_i^0$, such that $\varphi_i$ has the highest instantaneous energy consumption, while still respecting the energy budget.
+In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned (reduced to $c_{1,1}^-$), as e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
+The gain factors for the trajectory parameters from Equation~\ref{eq:state-control} are obtained
+\begin{equation}\label{eq:traj-gains}
+  \begin{bmatrix}\nu_{i,1} \\ \vdots \\ \nu_{i,\rho}\end{bmatrix}=(\overline{c}_i-\underline{c}_i)^{-1}\rho^{-1}y_{\underline{c}_i}\begin{bmatrix}c_{i,1} \\ \vdots \\ c_{i,\rho}\end{bmatrix},
+\end{equation}
+where $y_{\underline{c}_i}\in\mathbb{R}$ is the maximum energy consumption of the highest possible parameters level at $i$-th stage.
+The value is obtained empirically (an initial guess is made using an energy sensor).
+Whenever the parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific parameters.
 
@@
 We assume the UAV carries an embedded board that runs the computations.
-The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations constraints sets and builds an energy model: a linear interpolation, one per each computation.
+The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations constraint sets and builds an energy model: a linear interpolation, one per each computation.
 
 The computations are implemented by software components, such as ROS nodes in a ROS based system.
-The user implements these nodes in such a way that they change the computational load with node-specific ROS parameters, the computations parameters.
+The user implements these nodes such that they change the computational load with node-specific ROS parameters, the computations parameters.
 In a generic software component system, the user maps the computational load to the arguments.
@@
 
-Let us further define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool.
+Let us define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool. Moreover, let $g(\{\emptyset\})$ be zero.
 
@@
 \begin{equation*}\label{eq:energy-comp}
-  \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}^T=\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix}/\begin{bmatrix}c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}.
+  \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}=\begin{bmatrix}c_{i,\rho+1}^{-1} & & \\ & \ddots & \\ & & c_{i,\rho+\sigma}^{-1} \end{bmatrix}\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix},
 \end{equation*}
-Moreover, let $g(\{\emptyset\})$ be zero.
+where the matrix is a diagonal matrix of computations parameters.
 
@@
 
-\subsection{Output constraints set}
+\subsection{Output constraint set}
 
@@
 where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
-We define the output constraints set
+We define the output constrains set
 \begin{equation*}
@@
 
-Follows a check if the mission can finish without the eventuality of battery discharge (output constraints satisfaction) at line~\ref{alg:output_constraints}, with the control input being eventually updated and the process reiterated at line~\ref{alg:recursion}.
+Follows a check if the mission can finish without the eventuality of battery discharge (output constraint satisfaction) at line~\ref{alg:output_constraints}, with the control input being eventually updated and the process reiterated at line~\ref{alg:recursion}.
 

### 2021-01-19 icra-2021.tex
minor fix
typos, consistency, equations, and other fixes

@@
   \end{tikzpicture}
-  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:ii}~travels a more accurate survey than~\ref{sth:iii}) and computations (\ref{sth:i}~elaborates more images per second than~\ref{sth:ii}).
+  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:ii}~travels a more accurate survey than~\ref{sth:iii}), and computations (\ref{sth:i}~elaborates more images per second than~\ref{sth:ii}).
 In bottom left, the collected energy data of the UAV flying the scenario, along the power spectrum (bottom right) where the first frequency has been filtered.}
@@
 In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along its power spectrum plot motivates our choice.
-The observation applies broadly; we briefly investigate periodic energy consumption evolutions in some ground-based mobile robots.
 
@@
   \input{\figpath/traj1.tikz}
-  \caption{Illustrative figure shows notation on a small initial slice of the plan in Figure~\ref{fig:il-abs}.}
+  \caption{The notation on a small initial slice of the plan in Figure~\ref{fig:il-abs} in 2D.}
   \label{fig:traj1}
@@
   The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
-  \begin{equation}\label{eq:mission}\begin{split}
+  \begin{equation*}\begin{split}
     \Gamma_i:=\{\langle&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),c_{i,\rho+1},\dots,c_{i,\rho+\sigma}\rangle\\\mid
@@
       &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathcal{S}_{i,j}\,\},
-  \end{split}\end{equation}
+  \end{split}\end{equation*}
   where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
@@
 Physically, this means that the plan is approximately periodic.
-The justification for this strong assumptions originates from empirical data (we refer the reader back to the illustrative abstract in Figure~\ref{fig:il-abs}).
+The justification for this assumptions originates from empirical data (we refer the reader back to the illustrative abstract in Figure~\ref{fig:il-abs}).
 It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over trajectories and computations attending some triggering events (such as detections).
@@
 \end{defn}
-
-The algorithm measures the time between the stages and assumes the initial period is one. We note that periods might be different for different $j$s due to atmospheric interferences.
 
@@
 The algorithm finds $n$ initializing it to one and finding the value which satisfies the proposition.
+It then measures the time between the stages and assumes the initial period is one.
+The periods might be different for different $j$s due to atmospheric interferences.
 
@@
 We refer to the instantaneous energy consumption evolution simply as the energy signal.
-We model the energy using energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal.
+We model the energy using energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize such energy signal.
 The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and estimated using a state estimator.
@@
 
-Let us consider the discretized version $A_d:=A\Delta t+I$ of the matrix $A$.
+Let us consider for practical reasons the discretized version $A_d:=A\Delta t+I$ of the matrix $A$.
 We denote the continuous and discrete time with the standard notation $t,k$.
 We use the forward Euler approximation with a small enough value of the time step $\Delta t$.
-We note that one can guarantee to have the same outputs rather than an approximation with $A_d:=e^{At}$.
 
@@
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T,\\
+  \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T\hspace*{-1ex},\\
   B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
@@
 
-The first $\rho$ gain factors quantifies the contribution of the $i$-th trajectory parameters.
+In particular, the first $\rho$ gain factors quantifies the contribution of the $i$-th trajectory parameters.
 The following $\sigma$ gain factors quantifies the contribution of the computations parameters.
-We elucidate how we derive these factors in the next two subsections.
+We elucidate how we derive these factors in the next two subsections, in Equation~(\ref{eq:traj-gains}) and~(\ref{eq:energy-comp}).
 
@@
   \input{\figpath/traj2.tikz}
-  \caption{Illustrative figure shows the alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (the alteration of the path from Figure~\ref{fig:il-abs}).}
+  \caption{The alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (the alteration of the path from Figure~\ref{fig:il-abs}).}
   \label{fig:tee1}
@@
 For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption $\nu_{1,1}(c_{1,1}-c_{1,1}^-)<0$, for a given $\nu_{1,1}\in\mathbb{R}_{<0}$.
-This is then summed to the first coefficient $\alpha_0$, shifting the modeled energy.
+It thus simulates the lowering of instantaneous energy consumption ($\nu_{1,1}c_{1,1}>\nu_{1,1}c_{1,1}^-$), for a given $\nu_{1,1}$, that is then summed to the first coefficient $\alpha_0$, shifting the modeled energy.
 
@@
 In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned (reduced to $c_{1,1}^-$), as e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
-The gain factors for the trajectory parameters from Equation~\ref{eq:state-control} are obtained
+The gain factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are obtained
 \begin{equation}\label{eq:traj-gains}
@@
 where $y_{\underline{c}_i}\in\mathbb{R}$ is the maximum energy consumption of the highest possible parameters level at $i$-th stage.
-The value is obtained empirically (an initial guess is made using an energy sensor).
-Whenever the parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific parameters.
+The value is obtained empirically (e.g., using an energy sensor).
+Whenever the trajectory parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific trajectory parameters.
 
@@
 \end{equation*}
-where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
+where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences, such as wind ($w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
 
@@
 
-We assume the UAV carries an embedded board that runs the computations.
-The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computations constraint sets and builds an energy model: a linear interpolation, one per each computation.
-
-The computations are implemented by software components, such as ROS nodes in a ROS based system.
+For this purpose, we assume the UAV carries an embedded board that runs the computations.
+The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computation constraint sets and builds an energy model: a linear interpolation, one per each computation.
+
+The computations are implemented by software components, e.g., ROS nodes in a ROS based system.
 The user implements these nodes such that they change the computational load with node-specific ROS parameters, the computations parameters.
@@
 
-We note that while the trajectory can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation set.
+We note that while the trajectory can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation constraint set.
 
@@
 The gain factors that quantifies the contribution of the computations parameters
-\begin{equation*}\label{eq:energy-comp}
+\begin{equation}\label{eq:energy-comp}
   \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}=\begin{bmatrix}c_{i,\rho+1}^{-1} & & \\ & \ddots & \\ & & c_{i,\rho+\sigma}^{-1} \end{bmatrix}\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix},
-\end{equation*}
+\end{equation}
 where the matrix is a diagonal matrix of computations parameters.
+
+The factors thus add the computational energy component to the model in Equation~(\ref{eq:state-perf}).
 
@@
         {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (5.6,-4) {\footnotesize {(b) energy evolution simulation in 200 seconds interval}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (5.6,-4) {\footnotesize {(b) energy evolution simulation for 200 seconds interval}};
   \end{tikzpicture}
@@
 \begin{defn}[Valid control sequence and path]\label{def:valid}
-  A \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[l]^+$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
-
-  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path}
+  Given a close strictly positive discrete interval $[j-n,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[j-n,j]$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
+
+  The path $\mathcal{P}$ resulting from a valid control sequence is a \emph{valid path}
   \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_k\mid&\,\exists \mathbf{u}_k,n\in\mathbb{Z}_{>0},\\
-    &\langle\varphi_{i-1}\left(\mathbf{p}_{k-n}\right),\mathbf{u}_{k-n}\rangle\in\Gamma_{i-1}\\
-    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle\in\Gamma_i\},
+   \mathcal{P}:=\{\mathbf{p}_{k+1}\mid&\,\exists \mathbf{u}_k,\mathbf{p}_k,\\
+    &\langle\varphi_{i-1}\left(\mathbf{p}_{k}\right),\mathbf{u}_{k}\rangle\in\Gamma_{i-1}\\
+    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k+1}),\mathbf{u}_{k+1}\rangle\in\Gamma_i\},
   \end{split}\end{equation*}
-  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k,1},\dots,$ $c_{k,\rho}),c_{k,\rho+1},\dots,c_{k,\rho+\sigma}\rangle$.
+  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle$.
 \end{defn}
 
-We assume that at least one period in the initial plan is valid.
+Let us consider the assumption that at least one period in the user-defined initial plan is valid.
 
@@
 
-We stated earlier the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
+We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
 This is generally untrue.
@@
 
-Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
+Let us hence consider the state of charge (SoC) of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
 \begin{equation*}\begin{split}
@@
 where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
-We define the output constrains set
+
+\begin{defn}[Output constrain set]
+The output constrain set is then the set
 \begin{equation*}
@@
 and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
-
+\end{defn}
 ----

### 2021-01-19 icra-2021.tex
fixed the algorithm but need to fix the text around it in subsec deployment...

@@
 %% pseudocode package
-\usepackage{algpseudocode}
+\usepackage{algorithm,algorithmic}
+
+% counter to mantain the line numbering
+\renewcommand\thealgorithm{}
+\newcommand{\setalglineno}[1]{%
+  \setcounter{ALC@line}{\numexpr#1-1}}
 
@@
 \DeclareMathOperator*{\argmin}{arg\,min}
-
-\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
-
-% just lines in pseudocode...
-\usepackage{etoolbox}
-
-\makeatletter
-% start with some helper code
-% This is the vertical rule that is inserted
-\newcommand*{\algrule}[1][\algorithmicindent]{%
-  \makebox[#1][l]{%
-    \hspace*{.2em}% <------------- This is where the rule starts from
-    \vrule height .75\baselineskip depth .25\baselineskip
-  }
-}
-
-\newcount\ALG@printindent@tempcnta
-\def\ALG@printindent{%
-    \ifnum \theALG@nested>0% is there anything to print
-    \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-    % do nothing
-    \else
-    \unskip
-    % draw a rule for each indent level
-    \ALG@printindent@tempcnta=1
-    \loop
-    \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-    \advance \ALG@printindent@tempcnta 1
-    \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax
-    \repeat
-    \fi
-    \fi
-}
-% the following line injects our new indent handling code in place of the default spacing
-\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-\patchcmd{\ALG@doentity}{\item[]\nointerlineskip}{}{}{} % no spurious vertical space
-% end vertical rule patch for algorithmicx
-\makeatother
 
@@
 
-We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
+We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
 \begin{equation*}\label{eq:pd}
-  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
+  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
     0&1\\-1&0
@@
 \begin{equation*}
-  \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
 \end{equation*}
-and $\max{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
+and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
 \end{defn}
@@
 
+\begin{algorithm}
   \begin{algorithmic}[1]
-  \Procedure{Step}{$\mathbf{q}_{k-1}$, $\mathbf{u}_{k-1}^a$, $\mathbf{u}_{k-2}^a$, $P_{k-1}$}\label{alg:step}
-
-  \State $\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\max{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$\label{alg:max_cont_sequence}
-
-  \State $\mathbf{u}^0_{k-1}\gets\argmax_{\mathbf{u}}{\sum_{i=k-1}^{k+N-2}{l(\mathbf{q}_i,\mathbf{u}_i)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
-
-  \State $\hat{\mathbf{q}}_k^-\gets A\hat{\mathbf{q}}_{k-1} + B\mathbf{u}^0_{k-1}$
-  \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}\label{alg:output_constraints}
-    \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\{\max{\mathbf{u}}^a_{k-1}\}$
-    \State\Return{\Call{Step}{$\mathbf{q}_{k-1}$, $\mathbf{u}^a_{k-1}$, $\mathbf{u}_{k-2}^a$,$P_{k-1}$}}\label{alg:recursion}
-  \Else
-    \If{$\abs{y_k^a-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
-      \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$\label{alg:evolution}
-      \State $P_k\gets P_k^-$
-    \Else 
-      \State $P_k^-\gets AP_{k-1}A^T+Q$\label{alg:kalman_start}
-      \State $K\gets P_k^-C^T/(CP_k^-C^T+R)$
-      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+K(y_k^a-C\hat{\mathbf{q}}_k^-)$
-      \State $P_k\gets(I+KC)P_k^-$\label{alg:kalman_end}
-    \EndIf
-    \State $\mathbf{u}_{k}^a\gets \mathbf{u}_{k-1}^a$
-    \State\Return{$(\hat{\mathbf{q}}_k,P_k,\mathbf{u}_k^a)$}
-  \EndIf
-  \EndProcedure
-\vspace*{1ex}
-  \Procedure{EADMPA}{$\mathcal{M}$, $\mathbf{p}_0$, $\mathbf{q}_0$}
-  \State $k\gets 0$
-%  \State $\mathbf{y}\gets \{\emptyset\}$
-  \State $\mathbf{u}_{k-1}^a\gets\{\emptyset\}$
-  \State $\mathbf{p}_k\gets\mathbf{p}_0$
-  \State $\mathbf{q}_k\gets\mathbf{q}_0$
-  \While{$k \leq t_f$}
-
-    \State $\mathbf{u}_{k}^a\gets \{\mathbf{u}_{k}^a\mid(\varphi_i(\mathbf{p}_{k},\mathbf{c}_{i}),\Psi(\mathbf{s_{i}}))\in\lambda(\mathbf{p}_k)\}$
-    \State $(\mathbf{q}_k,P_k,\mathbf{u}_k^a)\gets$\Call{Step}{$\mathbf{q}_{k}$, $\mathbf{u}^a_{k}$, $\mathbf{u}_{k-1}^a$, $P_k$}\label{alg:en}
-    \State $\mathbf{p}_{k}\gets\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$\label{alg:pos}
-    \State $\mathbf{u}_{k-1}^a\gets\mathbf{u}_{k}^a$
-
-%    \State $\mathbf{y}\gets\mathbf{y}\cup C\hat{\mathbf{q}}_k$
-    \State $k\gets k + 1$
-  \EndWhile 
-  \EndProcedure
+    \STATE $\mathbf{p}_k\gets \mathbf{p}_0, \mathbf{q}_k\gets \mathbf{q}_0$
+    \FOR{$i\in[l]^+$}
+      \WHILE{$\mathbf{p}_k\neq\mathbf{p}_{\Gamma_i}$}
+        \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{i=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_i,\mathbf{u}_i)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
+        \STATE $\mathbf{u}\gets\{\mathbf{u}\cup\mathbf{u}_k\}$
+        \STATE $\hat{\mathbf{q}}_{k+1}\gets A\mathbf{q}_k+B\mathbf{u}_k$\label{alg:evolution}
+        \STATE $\mathbf{q}_{k+1}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k+1}$ and sensor data\label{alg:kalman_end}
+        \STATE $\mathbf{p}_{k}\gets\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$ \label{alg:pos}
+        \STATE $k\gets k+1$
+      \ENDWHILE
+    \ENDFOR
   \end{algorithmic}
+  \caption{Energy-Aware Dynamic Planning}    
+\end{algorithm}
 
@@
 \begin{algorithmic}[1]
-  \State\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
+  \STATE\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:stage}
-  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
+  \setcounterref{ALC@line}{code:stage}
+  \STATE\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:trigger-pt}
-  \State\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
+  \setcounterref{ALC@line}{code:trigger-pt}
+  \STATE\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:tee-set}
-  \State\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
+  \setcounterref{ALC@line}{code:tee-set}
+  \STATE\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \State\textbf{\texttt{0.0003;0;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
+  \STATE\textbf{\texttt{0.0003;0;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:firstcircle}
-  \State\textbf{\texttt{-sqrt(4900+c1)-45,146}}\label{code:trigger}
+  \setcounterref{ALC@line}{code:firstcircle}
+  \STATE\textbf{\texttt{-sqrt(4900+c1)-45,146}}\label{code:trigger}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:trigger}
-  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset}
-  \State\textbf{\texttt{[2,10]}}\label{code:qos1set}
-  \State\textbf{\texttt{[32,448]}}\label{code:qos2set}
+  \setcounterref{ALC@line}{code:trigger}
+  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset}
+  \STATE\textbf{\texttt{[2,10]}}\label{code:qos1set}
+  \STATE\textbf{\texttt{[32,448]}}\label{code:qos2set}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:qos2set}
-  \State\textbf{\texttt{0.05;1;x+sqrt(4900+c1)+45}}\label{code:tee2}
-  \State\textbf{\texttt{-sqrt(4900+c1)-45,11}}\label{code:trigger2}
-  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset2}
-  \State\textbf{\texttt{[2,10]}}
-  \State\textbf{\texttt{[32,448]}}\label{code:qosset12}
+  \setcounterref{ALC@line}{code:qos2set}
+  \STATE\textbf{\texttt{0.05;1;x+sqrt(4900+c1)+45}}\label{code:tee2}
+  \STATE\textbf{\texttt{-sqrt(4900+c1)-45,11}}\label{code:trigger2}
+  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset2}
+  \STATE\textbf{\texttt{[2,10]}}
+  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset12}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:qosset12}
-  \State\textbf{\texttt{0.0003;90;(x+sqrt(4900+c1)-30)\^{}2}}
+  \setcounterref{ALC@line}{code:qosset12}
+  \STATE\textbf{\texttt{0.0003;90;(x+sqrt(4900+c1)-30)\^{}2}}
   \textbf{\texttt{\hspace*{14ex}+(y-11)\^{}2-5625}}\label{code:tee3}
-  \State\textbf{\texttt{-sqrt(4900+c1)+105,11}}
-  \State\textbf{\texttt{[-3*10\^{}3,0]}}
-  \State\textbf{\texttt{[2,10]}}
-  \State\textbf{\texttt{[32,448]}}\label{code:qosset32}
+  \STATE\textbf{\texttt{-sqrt(4900+c1)+105,11}}
+  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}
+  \STATE\textbf{\texttt{[2,10]}}
+  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset32}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:qosset32}
-  \State\textbf{\texttt{0.05;90;x+sqrt(4900+c1)-105}}\label{code:tee4}
-  \State\textbf{\texttt{-sqrt(4900+c1)+105,147}}
-  \State\textbf{\texttt{[-3*10\^{}3,0]}}
-  \State\textbf{\texttt{[2,10]}}
-  \State\textbf{\texttt{[32,448]}}\label{code:qosset42}
-  \State\textbf{\texttt{0.0003;90;(x-sqrt(4900+c1)+105)\^{}2}}
+  \setcounterref{ALC@line}{code:qosset32}
+  \STATE\textbf{\texttt{0.05;90;x+sqrt(4900+c1)-105}}\label{code:tee4}
+  \STATE\textbf{\texttt{-sqrt(4900+c1)+105,147}}
+  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}
+  \STATE\textbf{\texttt{[2,10]}}
+  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset42}
+  \STATE\textbf{\texttt{0.0003;90;(x-sqrt(4900+c1)+105)\^{}2}}
   \textbf{\texttt{\hspace*{14ex}+(y-147)\^{}2-4900+c1}}\label{code:tee5}
-  \State\textbf{\texttt{-3*sqrt(4900+c1)+105,147}}\label{code:triggerlast}
-  \State\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset5}
+  \STATE\textbf{\texttt{-3*sqrt(4900+c1)+105,147}}\label{code:triggerlast}
+  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset5}
 \end{algorithmic}
@@
 \begin{algorithmic}[1]
-  \setcounterref{ALG@line}{code:teeset5}
-  \State\textbf{\texttt{[0,0]}}
-  \State\textbf{\texttt{[0,0]}}
+  \setcounterref{ALC@line}{code:teeset5}
+  \STATE\textbf{\texttt{[0,0]}}
+  \STATE\textbf{\texttt{[0,0]}}
 \end{algorithmic}

### 2021-01-20 icra-2021.tex
fixes to the algorithm section

@@
 Whenever the trajectory parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific trajectory parameters.
+Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters $c_i^\rho=\{\emptyset\}$.
 
 We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
-\begin{equation*}\label{eq:pd}
+\begin{equation}\label{eq:pd}
   \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
@@
   \end{bmatrix},
-\end{equation*}
+\end{equation}
 where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
@@
 
-Let us define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool. Moreover, let $g(\{\emptyset\})$ be zero.
+Let us define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool.
 
@@
 \end{equation}
-where the matrix is a diagonal matrix of computations parameters.
+where the matrix is a diagonal matrix of computations parameters. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters $c_i^\sigma=\{\emptyset\}$.
 
 The factors thus add the computational energy component to the model in Equation~(\ref{eq:state-perf}).
+
+%%%%%%%%%%%%%%%%%%%
+\section{Algorithm}
+\label{sec:algo}
+
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to direct the UAV on a valid path: to solve Problem~\ref{pb}.
+
+\begin{defn}[Valid control sequence and path]\label{def:valid}
+  Given a close strictly positive discrete interval $[j-n,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[j-n,j]$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
+
+  The path $\mathcal{P}$ resulting from a valid control sequence is a \emph{valid path}
+  \begin{equation*}\begin{split}\label{eq:mission-valid}
+   \mathcal{P}:=\{\mathbf{p}_{k+1}\mid&\,\exists \mathbf{u}_k,\mathbf{p}_k,\\
+    &\langle\varphi_{i-1}\left(\mathbf{p}_{k}\right),\mathbf{u}_{k}\rangle\in\Gamma_{i-1}\\
+    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k+1}),\mathbf{u}_{k+1}\rangle\in\Gamma_i\},
+  \end{split}\end{equation*}
+  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle$.
+\end{defn}
+
+Let us consider the assumption that at least one period in the user-defined initial plan is valid.
+
+\begin{assm}\label{assm:valid}
+  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n-1]^+,\,j\in[n]^+$ s.t. $\Gamma_{(i-1)n+j},\dots,\Gamma_{in+j}$ is valid.
+\end{assm}
+
+Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
+
+\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
+  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
+Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
+\end{thm}
+\begin{proof}
+  The proof is based on mathematical induction. 
+  Base case: *
+
+  Induction step: *
+
+\end{proof}
+
+\subsection{Output and control constraint sets}
+
+We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
+This is generally untrue.
+Physical UAVs are bounded by strict energy budgets due to battery limitations.
+
+Let us hence consider the state of charge (SoC) of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
+\begin{equation*}\begin{split}
+  \mathrm{SoC}_k=-\left(V-
+  \sqrt{
+    V^2-
+    4R_r\tilde{V}y_kV^{-1}}
+  \right)/2R_rQ_c,\\ 
+\end{split}\end{equation*}
+where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
+
+\begin{defn}[Output constrain set]
+The output constrain set is then the set
+\begin{equation*}
+  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+\end{equation*}
+and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
+
+The control constraint set is the trajectory contraint set for the trajectory parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
+\begin{equation*}
+  \mathcal{U}_k:=\begin{cases}
+    \mathcal{C}_i & \text{for } c_{i,j} \text{ with } j\leq\rho\\
+    \mathcal{S}_{i,j-\rho} & \text{for } c_{i,j} \text{ with } \rho<j\leq\sigma
+  \end{cases}.
+\end{equation*}
+\end{defn}
+
+\subsection{Deployment algorithm}
+
+\begin{algorithm}[t]
+  \caption{Energy-Aware Dynamic Planning}\label{alg}
+  \begin{algorithmic}[1]
+    \STATE $\mathbf{p}_{k-1}\gets \mathbf{p}_0, \mathbf{q}_{k-1}\gets \mathbf{q}_0, \mathbf{u}_{k-1}\gets \{\emptyset\}$\label{alg:init}
+    \FOR{$i\in[l]^+$}\label{alg:stages-loop}
+      \WHILE{$\mathbf{p}_{k-1}\neq\mathbf{p}_{\Gamma_i}$}
+        \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
+        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B_i(\mathbf{u}_{k}-\mathbf{u}_{k-1})$\label{alg:evolution}
+        \STATE $\mathbf{q}_{k}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k}$ and sensor data\label{alg:kalman_end}
+        \STATE $\mathbf{p}_{k}\gets\mathbf{p}_{k-1}\dot{\mathbf{p}}_d(\mathbf{p}_{k-1})/v$ \label{alg:pos}
+        \STATE $k\gets k+1$
+      \ENDWHILE
+    \ENDFOR
+  \end{algorithmic} 
+\end{algorithm}
+
+The algorithm first initializes the position, energy coefficients, and control (line~\ref{alg:init}).
+
+The position is updated at line~\ref{alg:pos}, using the expression from Equation~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
+The expression depends on the trajectory $\varphi_i$ from stage $\Gamma_i$.
+The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$.
+
+The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
+The a priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
+At line~\ref{alg:mpc}, the algorithm uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function
+\begin{equation}\label{eq:cost}\begin{split}
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k)+\\
+  &\hspace*{3.5ex}(1/2)(\mathbf{u}_k-\mathbf{u}_{k-1})^TB_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\\
+  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TA\mathbf{q}_k),
+\end{split}\end{equation}
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal.
+
+We note from Lemma~\ref{lem:eqv} that the expression in Equation~(\ref{eq:cost}) denotes the square of the predicted instantaneous energy consumption.
+Moreover, higher the horizon, higher the complexity and the accuracy of the control.
+
+We further note that at every step of the summary on line~\ref{alg:mpc} the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the trajectory and the computation constraint sets.
+In particular, at each steps it performs the subroutine
+\begin{algorithmic}
+  {\let\fmtlinenumber\mathalph 
+  \WHILE{$\overline{c}_i\notin\mathcal{U}_k,\, y_k\notin\mathcal{Y}_k$}\label{alg2:while}
+    \STATE $\overline{c}_i\gets\overline{c}_i-\delta$
+  \ENDWHILE
+  \STATE $\mathbf{u}_k\gets\overline{c}_i$}
+\end{algorithmic} 
+where to evaluate the inclusion in the output control set the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution} (we note that the condition can be written $\overline{c}_i\notin\mathcal{U}_k,\, C\mathbf{q}_k\notin\mathcal{Y}_k$).
+
+We finally note that one can express the tradeoffs between trajectory and computation parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with
+\begin{equation*}
+  F_i\mathbf{u}_k-e_i\geq 0,
+\end{equation*}
+where $e_i\in\mathbb{R}^n$ and $F_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $F_i$ is an identity matrix there is no relation between the parameters).
+
+%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%
-\section{Algorithm}
-\label{sec:algo}
-
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to direct the UAV on a valid path: to solve Problem~\ref{pb}.
-
-\begin{defn}[Valid control sequence and path]\label{def:valid}
-  Given a close strictly positive discrete interval $[j-n,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[j-n,j]$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
-
-  The path $\mathcal{P}$ resulting from a valid control sequence is a \emph{valid path}
-  \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_{k+1}\mid&\,\exists \mathbf{u}_k,\mathbf{p}_k,\\
-    &\langle\varphi_{i-1}\left(\mathbf{p}_{k}\right),\mathbf{u}_{k}\rangle\in\Gamma_{i-1}\\
-    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k+1}),\mathbf{u}_{k+1}\rangle\in\Gamma_i\},
-  \end{split}\end{equation*}
-  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle$.
-\end{defn}
-
-Let us consider the assumption that at least one period in the user-defined initial plan is valid.
-
-\begin{assm}\label{assm:valid}
-  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n-1]^+,\,j\in[n]^+$ s.t. $\Gamma_{(i-1)n+j},\dots,\Gamma_{in+j}$ is valid.
-\end{assm}
-
-Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
-
-\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
-Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
-\end{thm}
-\begin{proof}
-  The proof is based on mathematical induction. 
-  Base case:
-
-  Induction step:
-
-\end{proof}
-
-\subsection{Output constraint set}
-
-We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
-This is generally untrue.
-Physical UAVs are bounded by strict energy budgets due to battery limitations.
-
-Let us hence consider the state of charge (SoC) of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation*}\begin{split}
-  \mathrm{SoC}_k=-\left(V-
-  \sqrt{
-    V^2-
-    4R_r\tilde{V}y_kV^{-1}}
-  \right)/2R_rQ_c,\\ 
-\end{split}\end{equation*}
-where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
-
-\begin{defn}[Output constrain set]
-The output constrain set is then the set
-\begin{equation*}
-  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
-\end{equation*}
-and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
-\end{defn}
-----
-
-\subsection{Deployment algorithm}
-
-\begin{algorithm}
-  \begin{algorithmic}[1]
-    \STATE $\mathbf{p}_k\gets \mathbf{p}_0, \mathbf{q}_k\gets \mathbf{q}_0$
-    \FOR{$i\in[l]^+$}
-      \WHILE{$\mathbf{p}_k\neq\mathbf{p}_{\Gamma_i}$}
-        \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{i=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_i,\mathbf{u}_i)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
-        \STATE $\mathbf{u}\gets\{\mathbf{u}\cup\mathbf{u}_k\}$
-        \STATE $\hat{\mathbf{q}}_{k+1}\gets A\mathbf{q}_k+B\mathbf{u}_k$\label{alg:evolution}
-        \STATE $\mathbf{q}_{k+1}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k+1}$ and sensor data\label{alg:kalman_end}
-        \STATE $\mathbf{p}_{k}\gets\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$ \label{alg:pos}
-        \STATE $k\gets k+1$
-      \ENDWHILE
-    \ENDFOR
-  \end{algorithmic}
-  \caption{Energy-Aware Dynamic Planning}    
-\end{algorithm}
-
-Per each time step $k$ (the final time $t_f$ is unknown), the algorithm updates the state--the position at line~\ref{alg:pos} and the energy coefficients at line~\ref{alg:en}--and the control input.
-Note that the position can be computed directly from Equation~(\ref{eq:pd}).
-If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
-
-In detail, initial guess for $P_0\in\mathbb{R}^{j\times j}$ is positive definite and derived empirically, for $\mathbf{q}_0$ the initial measurement is distributed to the coefficients (see Theorem~\ref{thm:state-vs-energy}).
-Line~\ref{alg:max_cont_sequence} selects the maximum possible control from the current control input.
-Line~\ref{alg:mpc} uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the optimal control $\mathbf{u}^0$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function
-\begin{equation}\begin{split}
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^TQ\mathbf{q}_k+\mathbf{u}_k^TR\mathbf{u}_k),\\
-  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TP_f\mathbf{q}_k),
-\end{split}\end{equation}
-where matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}^{l\times l}$ are positive definite.
-
-Follows a check if the mission can finish without the eventuality of battery discharge (output constraint satisfaction) at line~\ref{alg:output_constraints}, with the control input being eventually updated and the process reiterated at line~\ref{alg:recursion}.
-
-Before the next step, state estimator--the discrete-time Kalman filter~\cite{simon2006optimal} at lines~\ref{alg:kalman_start}--\ref{alg:kalman_end}--predicts the state $\mathbf{q}$ if the modeled instantaneous energy consumption diverges from the sensor's value $y_k^a$ more than a given $\varepsilon\in\mathbb{R}_{\geq  0}$, or sensor measurements are unavailable ($y_k^a=0$).
-
-%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 *
-
-%Some preliminary results are discussed. Further analysis and re-implementation of the functionality of the algorithm is needed.
-
-%\begin{figure}[h]
-%  \centering
-%  \input{\figpath/trajectory/trajectory3.tikz}
-%  \caption{The true trajectory. The trajectory is retrieved from the flight log.}
-%  \label{fig:trajectory}
-%\end{figure}
-
-%\begin{figure}[h]
-%  \centering
-%  \input{\figpath/energy/max_qos_tees3.tikz}
-%  \caption{Derived energy consumption from the sensors (throttle).
-Red line is the estimated value.
-We use KF for state estimation when the difference between the sensor and model value is $>\varepsilon$.
-Otherwise we evolve the state without noise.}
-%  \label{fig:energy-max}
-%\end{figure}
 
@@
 The gain is $k_e=5\cdot 10^{-2}$, and the rotation is opposite to line~\ref{code:firstcircle}.
-The algorithm computes $-E$ from the rotation matrix in Equation~\ref{eq:pd}.
+The algorithm computes $-E$ from the rotation matrix in Equation~(\ref{eq:pd}).
 

### 2021-01-20 icra-2021.tex
proofread the current version

@@
 To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
-The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
+The use of vector fields for guidance is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
 
@@
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
-In Figure~\ref{fig:il-abs}, some collected data from a UAV flying a survey scenario along its power spectrum plot motivates our choice.
+In Figure~\ref{fig:il-abs}, some collected energy data from a UAV flying a survey scenario along its power spectrum motivates our choice.
 
@@
 In Section~\ref{sec:experimental}, we present the results and showcases the performances.
-We propose some conclusions in Section~\ref{sec:conclusion}.
+We then derive some conclusions in Section~\ref{sec:conclusion}.
 Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:plan-spec}.
@@
 In Figure~\ref{fig:il-abs}, there are two parameters.
-The radius of the trajectory circle is relative to the trajectory (\ref{sth:ii}~has indeed a shorter distance between the survey lines then~\ref{sth:iii}).
-The quality of image detection is relative to the computations (\ref{sth:i}~processes more images per second then~\ref{sth:ii}).
+One relative to the trajectory (\ref{sth:ii}~has indeed a shorter distance between the survey lines then~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second then~\ref{sth:ii}).
 
@@
 Given an integer $a$, $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$.
+Bold lower-case letters indicates vectors.
 $c_{i,j}$ specifies the $j$-th parameter of the $i$-th parameters set $c_i$.
@@
   \input{\figpath/traj1.tikz}
-  \caption{The notation on a small initial slice of the plan in Figure~\ref{fig:il-abs} in 2D.}
+  \caption{The notation on a small initial slice of the plan of Figure~\ref{fig:il-abs} in 2D.}
   \label{fig:traj1}
@@
 It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over trajectories and computations attending some triggering events (such as detections).
-We will see this assumption being eased for non-periodic plans in Section~\ref{sec:experimental}.
+We will see this assumption being eased in practice for non-periodic plans in Section~\ref{sec:experimental}.
 
 \begin{defn}[Period]\label{def:period}
-  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Assumption~\ref{assm:periodic}.
+  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Assumption~\ref{assm:periodic}.
 \end{defn}
@@
   \begin{equation*}\begin{split}
-    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
+    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
   \end{split}\end{equation*}
@@
 \end{prop}
-\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th constant difference.
+\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+e_j$ and $e_j$ is the $j$-th constant difference.
+It is the same for trajectories selected at each period.
 This is equivalent to Assumption~\ref{assm:periodic}.
@@
 \end{pb}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
-The algorithm uses the model to find the control sequence that results in the optimal parameters configuration.
-%(using MPC)
-
-\begin{lem}[Signals equality]\label{lem:eqv}Suppose control $\mathbf{u}$ is a zero vector, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is 
+
+\begin{lem}[Signal, output equality]\label{lem:eqv}Suppose control $\mathbf{u}$ is a zero vector, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is
   \begin{equation*}
@@
 \begin{proof}
-The equivalence of the models is trivial and the equality of the signal and output is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
-We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof of the equality where we justify the choices of the items of the matrices and of the initial guess.
+The equality of the signal and output is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess.
 \end{proof}
@@
 \end{split}\end{equation}
-where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$, and $\mathbf{u}_{-1}=\mathbf{0}$.
+where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$.
 Moreover, the top row of $B$ contains gain factors $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho} & \nu_{i,\rho + 1}& \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}$, quantifying the contribution of a given parameter to the instantaneous energy consumption.
@@
   \input{\figpath/traj2.tikz}
-  \caption{The alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (the alteration of the path from Figure~\ref{fig:il-abs}).}
+  \caption{The alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path from Figure~\ref{fig:il-abs}).}
   \label{fig:tee1}
@@
 For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption ($\nu_{1,1}c_{1,1}>\nu_{1,1}c_{1,1}^-$), for a given $\nu_{1,1}$, that is then summed to the first coefficient $\alpha_0$, shifting the modeled energy.
+It thus simulates the lowering of instantaneous energy consumption ($\nu_{1,1}c_{1,1}>\nu_{1,1}c_{1,1}^-$) for a given $\nu_{1,1}$, that is then summed to the first coefficient $\alpha_0$ in Equation~(\ref{eq:state-details}), shifting the modeled energy.
 
@@
 The trajectory parameters allows to change the trajectory.
-They are a way to alter the nominal trajectory in the initial plan and thus alter the energy signal.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the optimal trajectory parameters $c_i^0$, such that $\varphi_i$ has the highest instantaneous energy consumption, while still respecting the energy budget.
-In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned (reduced to $c_{1,1}^-$), as e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
+They are a way to alter the nominal trajectory in the initial plan and thus alter the energy.
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the trajectory parameters such that $\varphi_i$ has the highest instantaneous energy consumption, while still respecting the energy budget.
+In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
 The gain factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are obtained
@@
 Whenever the trajectory parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific trajectory parameters.
-Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters $c_i^\rho=\{\emptyset\}$.
+Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
 
@@
 where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences, such as wind ($w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
 
@@
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ corresponds to frames-per-second (fps) rate.
+For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ might correspond to frames-per-second (fps) rate.
 The tool then changes the detection frequency.
@@
 \end{equation}
-where the matrix is a diagonal matrix of computations parameters. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters $c_i^\sigma=\{\emptyset\}$.
+where the matrix is a diagonal matrix of computations parameters. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
 
@@
 
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to direct the UAV on a valid path: to solve Problem~\ref{pb}.
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on a valid path: to solve Problem~\ref{pb}.
 
@@
 
-\begin{defn}[Output constrain set]
+\begin{defn}[Output, control constrain sets]
 The output constrain set is then the set
@@
 
-We further note that at every step of the summary on line~\ref{alg:mpc} the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the trajectory and the computation constraint sets.
+We further note that at every step of the summary on line~\ref{alg:mpc} the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
 In particular, at each steps it performs the subroutine
@@
 
-We finally note that one can express the tradeoffs between trajectory and computation parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with
+We finally note that one can express the tradeoffs between trajectory and computation parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with the constraints
 \begin{equation*}
-  F_i\mathbf{u}_k-e_i\geq 0,
+  R_i\mathbf{u}_k-r_i\geq 0,
 \end{equation*}
-where $e_i\in\mathbb{R}^n$ and $F_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $F_i$ is an identity matrix there is no relation between the parameters).
+where $r_i\in\mathbb{R}^n$ and $R_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $R_i$ is the identity matrix, there is no relation between the parameters).
+
+The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available using the subroutine.
 

### 2021-01-21 icra-2021.tex
some fixes in the lemma's proof

@@
 
-We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions; $\dot{\mathbf{q}}=A\mathbf{q}$. The linear combination of the initial guess and the generic solution
-\begin{equation*}\begin{split}
+We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions made in the lemma (the control is a zero vector); $\dot{\mathbf{q}}=A\mathbf{q}$.
+The linear combination of the initial guess and the generic solution
+\begin{equation}\label{eq:proof-comb}\begin{split}
   F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}}\\
   F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}
-\end{split}\end{equation*}
+\end{split}\end{equation}
 where $F=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is a properly sized vector of ones.
 
-Let us consider the second expression. It represents the linear combination of all the coefficients of the state at time $t$. It can also be expressed in the following form
+Let us consider the second expression in Equation~(\ref{eq:proof-comb}).
+It represents the linear combination of all the coefficients of the state at time $t$.
+It can also be expressed in the following form
 \begin{equation}\label{eq:proof-output}\begin{split}
@@
 
-First, we proof that the first term of both the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) matches.
+Thereby we start by proofing that the first terms of the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
 We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
 The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=\begin{bmatrix} 0 & \cdots & 0 \end{bmatrix}\,\,\,\forall v_0$, thus we choose $v_0=\begin{bmatrix}1 & 0 & \cdots & 0\end{bmatrix}$.
-We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal, $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.
 
@@
 \end{cases}\end{equation*}
-hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$. The proof for the remaining $r-1$ blocks is equivalent.
+hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+
+The proof for the remaining $r-1$ blocks is equivalent.
 
 The initial guess is build such that the sum of the coefficients is the same in both the signals.
-In the output matrix, the frequency $1/T$ accounts for the period in Equations~(\ref{eq:proof-complex}--\ref{eq:proof-output}) and~(\ref{eq:fourier}).
+In the output matrix, the frequency $1/T$ accounts for the period in Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier}).
 At time instant zero, the coefficients $b_j$ are not present and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$ (thus we multiply by a half the corresponding coefficients in $\mathbf{q}_0$).
-To match the outputs $h(t)=y(t)$--or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$--we define $C=1/T\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
-We thus conclude that the lemma holds.
-
-We note that the signal would still be periodic with another linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
-Even if both the signals $h$ and $y$ would be still periodic, they would not be equal.
+To match the outputs $h(t)=y(t)$--or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$--we define $C=(1/T)\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
+We thus conclude that the signal and the output are equal, hence the lemma holds.
 
 \qed
+
+We note for practical reasons that the signal would still be periodic with another linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
 

### 2021-01-24 icra-2021.tex
updated the evolution plot
added period plots

@@
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
+        {\footnotesize\input{\figpath/results/ener_sim3_detail_2.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(\textlabel{a}{fig:evol-static-plan:a}) slice of the simulated energy along the estimated model}};
     \node[inner sep=0pt] () at (6,0)
-        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
+        {\footnotesize\input{\figpath/results/evol_sim3_2.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(\textlabel{b}{fig:evol-static-plan:b}) model evolution at different $k$s}};

### 2021-01-25 icra-2021.tex
minor fixes to the plots

--- 2021-01-21 icra-2021.tex
@@
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
+        {\footnotesize\input{\figpath/results/ener_sim3_detail_3.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(\textlabel{a}{fig:evol-static-plan:a}) slice of the simulated energy along the estimated model}};
     \node[inner sep=0pt] () at (6,0)
-        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
+        {\footnotesize\input{\figpath/results/evol_sim3_3.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(\textlabel{b}{fig:evol-static-plan:b}) model evolution at different $k$s}};
@@
         {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.6,-4) {\footnotesize {(\textlabel{c}{fig:evol-static-plan:c}) coefficients evolution}};
+    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.3,-4) {\footnotesize {(\textlabel{c}{fig:evol-static-plan:c}) path I coefficients evolution}};
   \end{tikzpicture}

### 2021-01-25 icra-2021.tex
fixing indexes in the algorithm

@@
 \begin{defn}[Valid control sequence and path]\label{def:valid}
-  Given a close strictly positive discrete interval $[j-n,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[j-n,j]$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
-
-  The path $\mathcal{P}$ resulting from a valid control sequence is a \emph{valid path}
+  Given a close strictly positive discrete interval $[j-n+1,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $j$ if for every stage $\Gamma_{i-1},\,i\in[j-n+1,j]$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
+
+  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path} on $j$
   \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_{k+1}\mid&\,\exists \mathbf{u}_k,\mathbf{p}_k,\\
-    &\langle\varphi_{i-1}\left(\mathbf{p}_{k}\right),\mathbf{u}_{k}\rangle\in\Gamma_{i-1}\\
-    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k+1}),\mathbf{u}_{k+1}\rangle\in\Gamma_i\},
+   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,&\forall i\in[j-n+1,j]\,\\&\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\}.
   \end{split}\end{equation*}
-  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle$.
 \end{defn}
@@
 
-\begin{assm}\label{assm:valid}
-  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n-1]^+,\,j\in[n]^+$ s.t. $\Gamma_{(i-1)n+j},\dots,\Gamma_{in+j}$ is valid.
+\begin{assm}[Period validity]\label{assm:valid}
+  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n]^+$ s.t. the period $\Gamma_{(i-1)n+1},\dots,\Gamma_{in}$ is valid.
 \end{assm}

### 2021-01-26 icra-2021.tex
some consistency fixes in the algorithm section

@@
 \begin{defn}[Valid control sequence and path]\label{def:valid}
-  Given a close strictly positive discrete interval $[j-n+1,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $j$ if for every stage $\Gamma_{i-1},\,i\in[j-n+1,j]$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
-
-  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path} on $j$
+  Given a close strictly positive discrete interval $\mathcal{J}:=[j-n+1,j]$ (for $j\in\mathbb{Z}_{>0},j\leq l$ and $n$ given in Assumption~\ref{assm:periodic}), a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $\mathcal{J}$ if for every stage $\Gamma_{i-1},\,i\in\mathcal{J}$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
+
+  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path} on $\mathcal{J}$
   \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,&\forall i\in[j-n+1,j]\,\\&\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\}.
+   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,\forall i\in\mathcal{J},\,\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\},
   \end{split}\end{equation*}
 \end{defn}
+where we recall that $\mathbf{u}_k=\begin{bmatrix}c_k^\rho & c_k^\sigma\end{bmatrix}^T$ from Equation~(\ref{eq:state-control}).
 

### 2021-01-26 sim_eq.tex
more tex

\documentclass[11pt,a4paper,titlepage]{article}

\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{amsmath,amsthm}
\usepackage{tikz}
\usetikzlibrary{babel}
\usetikzlibrary{shapes, arrows}
\textwidth= 15cm
\evensidemargin=0cm
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[hyperindex=true,breaklinks=true,colorlinks=true,linkcolor=blue]{hyperref}

\title{Equations for the sim}
\author{CIA Wanted}

\tikzstyle{block} = [draw, rectangle, minimum width=6em]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{algo}{Algorithm}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle
Hola
\end{document}

### 2021-01-26 sim_eq.tex
vertical motion

@@
 \maketitle
-Hola
+We split horizontal and vertical dynamics.
+
+\section{Vertical dynamics}
+\begin{equation}
+	a_v = \frac{1}{m} (L - W),
+\end{equation}
+where $a_v$ is the vertical acceleration in ms$^{-2}$, $m$ is the mass of the aircraft in Kg, and $L$ and $W$ are the lift and weight forces respectively in Newtons.
+\begin{equation}
+W = mg,
+\end{equation}
+where $g = 9.8 \, \text{ms}^{-2}$ is the gravity acceleration.
+\begin{equation}
+L = c_l v_s^2,
+\end{equation}
+where $c_l$ is a coefficient to be determined experimentally, and $v_s$ is the airspeed of the aircraft. We can assume that
+\begin{equation}
+	v_s = c_{th}\, (t_h + \Delta t_h) + w_{bx},
+\end{equation}
+where $(t_h + \Delta_h) \in [0,100]$ is the throttle signal and $c_{th}$ is a coefficient to be determined experimentally, and $w_{bx}$ is the component of the wind vector along the horizontal axis of the vehicle.
+We set $t_h$ to a nominal value, let us say $50$ and we use $\Delta t_h$ to control the altitude of the aircrat with a P controller, i.e.,
+\begin{equation}
+	\Delta t_h = k_p (h_d - h_c),
+\end{equation}
+where $k_p$ is a positive gain constant, and $h_d$ is the desired altitude and $h_c$ is the current altitude of the aircraft.
+
+\subsection{Euler integration}
+\begin{equation}
+	\begin{cases}
+		h(k+1) &= h(k) + v_s(k) \Delta T \\
+		v_s(k+1) & = v_s(k) + a_v(k) \Delta T
+	\end{cases}
+\end{equation}
+
 \end{document}

### 2021-01-26 sim_eq.tex
horizontal sim

@@
 \end{equation}
-where $k_p$ is a positive gain constant, and $h_d$ is the desired altitude and $h_c$ is the current altitude of the aircraft.
+where $k_p$ is a positive gain constant, and $h_d$ is the desired altitude and $h_c$ is the current altitude of the aircraft in meters.
 
@@
 		h(k+1) &= h(k) + v_s(k) \Delta T \\
-		v_s(k+1) & = v_s(k) + a_v(k) \Delta T
+		v_v(k+1) &= v_s(k) + a_v(k) \Delta T,
+	\end{cases}
+\end{equation}
+where $v_v$ is the vertical speed (do not confuse it with the airspeed $v_s$).
+
+\section{Horizontal dynamics}
+\begin{equation}
+	\begin{cases}
+		\dot p &= c_{th}(t_h + \Delta t_h) \begin{bmatrix}\cos(\theta) \\ \sin(\theta) \end{bmatrix} + w \\
+			\dot\theta &= u
+	\end{cases},
+\end{equation}
+where $p$ is the position of the aircraft in the plane, $\theta$ is the angle of the velocity vector in the plane, $w$ is the wind vector, and $u$ is the control action for steering the aircraft (path tracking controller).
+
+\subsection{Euler integration}
+\begin{equation}
+	\begin{cases}
+		p(k+1) &= p(k) + \dot p(k) \Delta T \\
+		\theta(k+1) &= \theta(k) + \dot\theta(k) \Delta T,
 	\end{cases}

### 2021-01-26 icra-2021.tex
updates to the control with the latest version of the algorithm

@@
   \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T\hspace*{-1ex},\\
-  B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
+  \mathbf{u}&:=\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i,\,\,\,B=\left[\begin{array}{c} \mathbf{1}\\\mathbf{0}\end{array}\right],
 \end{split}\end{equation}
-where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$.
-Moreover, the top row of $B$ contains gain factors $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho} & \nu_{i,\rho + 1}& \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}$, quantifying the contribution of a given parameter to the instantaneous energy consumption.
-The other entries of $B$ are zeros.
-
-In particular, the first $\rho$ gain factors quantifies the contribution of the $i$-th trajectory parameters.
-The following $\sigma$ gain factors quantifies the contribution of the computations parameters.
+where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$.
+Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row of ones.
+$\mathbf{u}$ is defined as a linear scale transformation from the parameters to the energy.
+In fact $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution of a given parameter to the instantaneous energy consumption.
+
+In particular, the first $\rho$ scaling factors quantifies the contribution of the $i$-th trajectory parameters.
+The following $\sigma$ scaling factors quantifies the contribution of the computations parameters.
 We elucidate how we derive these factors in the next two subsections, in Equation~(\ref{eq:traj-gains}) and~(\ref{eq:energy-comp}).
@@
 In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
-The gain factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are obtained
-\begin{equation}\label{eq:traj-gains}
-  \begin{bmatrix}\nu_{i,1} \\ \vdots \\ \nu_{i,\rho}\end{bmatrix}=(\overline{c}_i-\underline{c}_i)^{-1}\rho^{-1}y_{\underline{c}_i}\begin{bmatrix}c_{i,1} \\ \vdots \\ c_{i,\rho}\end{bmatrix},
-\end{equation}
-where $y_{\underline{c}_i}\in\mathbb{R}$ is the maximum energy consumption of the highest possible parameters level at $i$-th stage.
+The scaling factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are obtained
+\begin{equation}\label{eq:traj-gains}\begin{split}
+  \nu_{i,j}&=\left((y_{\overline{c}_i}-y_{\underline{c}_i})/(\overline{c}_i-\underline{c}_i)\right)/\rho,\\
+  \tau_{i,j}&=\left(\underline{c}_i(y_{\overline{c}_i}-y_{\underline{c}_i})/(\overline{c}_i-\underline{c}_i)-y_{\underline{c}_i}\right)/\rho,
+\end{split}\end{equation}
+$\forall j\in[\rho]^+$.
+Moreover, $y_{\overline{c}_i},y_{\underline{c}_i}\in\mathbb{R}$ are the maximum (and minimum) energy contribution of the highest (and lowest) change of parameters at $i$-th stage.
 The value is obtained empirically (e.g., using an energy sensor).
-Whenever the trajectory parameters are not equally distributed, one can define $y_{\underline{c}_i}$ as a diagonal matrix where the items of the diagonal are the highest possible levels of specific trajectory parameters.
+%Whenever the trajectory parameters are not equally distributed, one can define $(y_{\overline{c}_i}-y_{\underline{c}_i})$ as a the highest (and lowest) levels of specific trajectory parameters. 
 Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
@@
 
-The gain factors that quantifies the contribution of the computations parameters
-\begin{equation}\label{eq:energy-comp}
-  \begin{bmatrix}\nu_{i,\rho+1} \\ \vdots \\ \nu_{i,\rho+\sigma}\end{bmatrix}=\begin{bmatrix}c_{i,\rho+1}^{-1} & & \\ & \ddots & \\ & & c_{i,\rho+\sigma}^{-1} \end{bmatrix}\begin{bmatrix}g(c_{i,\rho+1}) \\ \vdots \\ g(c_{i,\rho+\sigma})\end{bmatrix},
-\end{equation}
-where the matrix is a diagonal matrix of computations parameters. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
+The scaling factors that quantifies the energy contribution of the computations parameters are derived similarly as in Equation~(\ref{eq:traj-gains})
+\begin{equation}\label{eq:energy-comp}\begin{split}
+  \nu_{i,\rho+j}&=(g(\overline{c}_i)-g(\underline{c}_i))/(\overline{c}_i-\underline{c}_i),\\
+  \tau_{i,\rho+j}&=\underline{c}_i(g(\overline{c}_i)-g(\underline{c}_i))/(\overline{c}_i-\underline{c}_i)-g(\underline{c}_i),
+\end{split}\end{equation}
+$\forall j\in[\sigma]^+$. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
 
@@
   \begin{algorithmic}[1]
-    \STATE $\mathbf{p}_{k-1}\gets \mathbf{p}_0, \mathbf{q}_{k-1}\gets \mathbf{q}_0, \mathbf{u}_{k-1}\gets \{\emptyset\}$\label{alg:init}
+    \STATE $\mathbf{p}_{k-1}\gets \mathbf{p}_0, \mathbf{q}_{k-1}\gets \mathbf{q}_0$
+    \STATE $\mathbf{u}_{k-2},\mathbf{u}_{k-1}\gets \{\emptyset\}$\label{alg:init}
     \FOR{$i\in[l]^+$}\label{alg:stages-loop}
@@
         \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
-        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B_i(\mathbf{u}_{k}-\mathbf{u}_{k-1})$\label{alg:evolution}
+        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B(\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i)$\label{alg:evolution}
         \STATE $\mathbf{q}_{k}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k}$ and sensor data\label{alg:kalman_end}
@@
 \begin{equation}\label{eq:cost}\begin{split}
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k)+\\
-  &\hspace*{3.5ex}(1/2)(\mathbf{u}_k-\mathbf{u}_{k-1})^TB_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\\
-  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^TA\mathbf{q}_k),
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k+\mathbf{u}^TB\mathbf{u}),\\
+  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k),
 \end{split}\end{equation}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal.
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal, and $\mathbf{u}$ is defined in Equation~(\ref{eq:state-control}).
 
@@
 \begin{algorithmic}
-  {\let\fmtlinenumber\mathalph 
+  \STATE $\mathbf{u}_k\gets\overline{c}_i$
   \WHILE{$\overline{c}_i\notin\mathcal{U}_k,\, y_k\notin\mathcal{Y}_k$}\label{alg2:while}
@@
   \ENDWHILE
-  \STATE $\mathbf{u}_k\gets\overline{c}_i$}
 \end{algorithmic} 
-where to evaluate the inclusion in the output control set the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution} (we note that the condition can be written $\overline{c}_i\notin\mathcal{U}_k,\, C\mathbf{q}_k\notin\mathcal{Y}_k$).
+where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of trajectory and computational parameters are reduced by the this step if they don't meet the constraints).
+To evaluate the inclusion in the output control set, the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution} (we note that the condition can be written $\overline{c}_i\notin\mathcal{U}_k,\, C\mathbf{q}_k\notin\mathcal{Y}_k$).
 

### 2021-01-27 scripts/SIM4.m
implementing the physics from Hector

@@ -1,0 +1,66 @@
+
+% simulation from the equations from Hector
+
+delta = 0.01;
+time = delta;
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = 1; % positive gain constant to be also determined experimentally
+
+th = 50; % nominal vlalue of the throttle
+
+hd = 25; % desired altitude [m]
+
+w = [1 0]; % wind vector (x, y axis velocity
+
+vv = [15]; % vertical velocity vector (initial 15 [m/s])
+h = [25]; % altitude vector (inital 25 [m])
+
+p = [0; 0]; % position in space (initial 0,0 [m])
+theta = [0.1]; % initial angle
+
+store = []; % just storing all the records for debugging
+
+while true
+    
+    dth = kp*(hd-h(end)); % dth is the change of throttle we use to adjust 
+                          % the altitude
+    
+    vs = cth*(th+dth)-w*[cos(theta(end)); sin(theta(end))]; % airspeed of  
+                                                            % the aircraft 
+                                                            % [m/s]
+    % Hector original formula was wbx; I changes it in -w*[cos(theta);
+    % sin(theta)] which substract the contribution of the wind
+    
+    L = cl*vs^2;
+    
+    av = (L-W)/m; % vertical accelaration [m/s^2]
+    
+    % verical dynamics
+    h = [h; h(end)+vv(end)*delta]; % integration with just Euler
+    vv = [vv; vs+av*delta];
+    
+    % you get the pdangle here in the old simulation instead of theta...
+    u = theta(end);
+    
+    % horizontal kinematics
+    p = [p p(:,end)+(cth*(th+dth)*...
+           [cos(theta(end)); sin(theta(end))]+w)*delta];
+    theta = [theta; theta(end)+u*delta];
+    
+    
+    store = [store; dth vs L av u];
+    
+    time = time + delta;
+    
+    if time >= 60 % 1 minute? It's over...
+        break;
+    end
+    
+end
+

### 2021-01-27 scripts/SIM4.m
just ordered a bit the new simulation

@@ -1,6 +1,7 @@
 
 % simulation from the equations from Hector
 
+%% init
 delta = 0.01;
 time = delta;
 
@@ -25,6 +26,8 @@ p = [0; 0]; % position in space (initial 0,0 [m])
 theta = [0.1]; % initial angle
 
 store = []; % just storing all the records for debugging
+
+%% sim
 
 while true
     
@@ -64,3 +67,11 @@ while true
     
 end
 
+%% plots
+
+subplot(1,2,1);
+plot(p(1,:), p(2,:))
+title('position');
+subplot(1,2,2);
+plot(store(:,1))
+title('change in throttle');

### 2021-01-27 scripts/SIM4.m
equations sim

@@ -1,9 +1,11 @@
 
 % simulation from the equations from Hector
 
+clear all; clc; close all;
+
 %% init
-delta = 0.01;
-time = delta;
+delta_T = 0.01;
+final_time = 120;
 
 m = 1; % mass of the aircraft [kg]
 W = m*9.8; % weight force [N]
@@ -12,66 +14,77 @@ cl = 9.8/15^2; % coefficient to be determined experimentally
 cth = 15/50; % same
 
 kp = 1; % positive gain constant to be also determined experimentally
-
-th = 50; % nominal vlalue of the throttle
-
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
 hd = 25; % desired altitude [m]
+u_theta = 0.1;
 
-w = [1 0]; % wind vector (x, y axis velocity
+w = [1;0]; % wind vector (x, y axis velocity
 
-vv = [15]; % vertical velocity vector (initial 15 [m/s])
-h = [25]; % altitude vector (inital 25 [m])
+vv = 2; % vertical velocity
+sh = 15; % horizontal speed
+h = 20; % altitude 
+p = [0; 0]; % position
+theta = 0.1; % initial angle
+vh = sh * [cos(theta);sin(theta)]; % initial velocity
 
-p = [0; 0]; % position in space (initial 0,0 [m])
-theta = [0.1]; % initial angle
 
-store = []; % just storing all the records for debugging
+log_time = 0:delta_T:final_time;
+log_vv = zeros(length(log_time), 1);
+log_h = log_vv;
+log_theta = log_vv;
+log_sh = log_vv;
+log_th_delta = log_vv;
+log_p = zeros(length(log_time), 2);
+log_vh = log_p;
+
+i = 1;
+log_vv(i) = vv;
+log_h(i) = h;
+log_theta(i) = theta;
+log_sh(i) = sh;
+log_th_delta(i) = th_delta;
+log_p(i, :) = p;
+log_vh(i, :) = vh;
+
 
 %% sim
 
-while true
-    
-    dth = kp*(hd-h(end)); % dth is the change of throttle we use to adjust 
-                          % the altitude
-    
-    vs = cth*(th+dth)-w*[cos(theta(end)); sin(theta(end))]; % airspeed of  
-                                                            % the aircraft 
-                                                            % [m/s]
[…]

### 2021-01-27 scripts/SIM4.m
better vertical controller

@@ -4,8 +4,8 @@
 clear all; clc; close all;
 
 %% init
-delta_T = 0.01;
-final_time = 120;
+delta_T = 1e-3;
+final_time = 240;
 
 m = 1; % mass of the aircraft [kg]
 W = m*9.8; % weight force [N]
@@ -13,7 +13,8 @@ W = m*9.8; % weight force [N]
 cl = 9.8/15^2; % coefficient to be determined experimentally
 cth = 15/50; % same
 
-kp = 1; % positive gain constant to be also determined experimentally
+kp = 5; % positive gain constant to be also determined experimentally
+kvv = 5;
 th_nominal = 50; % nominal vlalue of the throttle
 th_delta = 0;
 hd = 25; % desired altitude [m]
@@ -21,12 +22,14 @@ u_theta = 0.1;
 
 w = [1;0]; % wind vector (x, y axis velocity
 
-vv = 2; % vertical velocity
+vv = 0; % vertical velocity
 sh = 15; % horizontal speed
-h = 20; % altitude 
+h = 24; % altitude
 p = [0; 0]; % position
-theta = 0.1; % initial angle
+theta = 0; % initial angle
 vh = sh * [cos(theta);sin(theta)]; % initial velocity
+wbx = dot(w,[cos(theta), sin(theta)]);
+vs = cth*(th_nominal + th_delta) + wbx; % initial airspeed
 
 
 log_time = 0:delta_T:final_time;
@@ -53,11 +56,12 @@ log_vh(i, :) = vh;
 for time = delta_T:delta_T:final_time
 
 % Vertical dynamics
-th_delta = kp*(hd - h);
+th_delta = kp*(hd - h) - kvv *vv;
 wbx = dot(w,[cos(theta), sin(theta)]);
 vs = cth*(th_nominal + th_delta) + wbx;
 L = cl * vs*vs;
 av = 1/m * (L - W);
+
 vv = vv + av*delta_T;
 h = h + vv*delta_T;
 
@@ -82,9 +86,15 @@ end
 
 %% plots
 
-subplot(1,2,1);
+subplot(2,2,1);
 plot(log_p(:, 1), log_p(:, 2))
 title('position');
-subplot(1,2,2);
+subplot(2,2,2);
 plot(log_time, th_nominal + log_th_delta)
-title('delta throttle');
+title('Throttle');
+subplot(2,2,3);
+plot(log_time, log_vv);
+title('vertical speed');
+subplot(2,2,4);
+plot(log_time, log_h);
+title('altitude');

### 2021-01-27 sim_eq.tex
vertical controller

@@
 \begin{equation}
-	\Delta t_h = k_p (h_d - h_c),
+	\Delta t_h = k_p (h_d - h_c) - k_{vv} v_v,
 \end{equation}
-where $k_p$ is a positive gain constant, and $h_d$ is the desired altitude and $h_c$ is the current altitude of the aircraft in meters.
+where $k_p$ and $k_{vv}$ are positive gain constants, $h_d$ and $h_c$ are the desired and current altitudes in meters respectively, and $v_v$ is the vertical velocity in m/s.
 
@@
 		h(k+1) &= h(k) + v_s(k) \Delta T \\
-		v_v(k+1) &= v_s(k) + a_v(k) \Delta T,
+		v_v(k+1) &= v_v(k) + a_v(k) \Delta T,
 	\end{cases}
@@
 
-\section{Horizontal dynamics}
+\section{Horizontal kinematics}
 \begin{equation}

### 2021-01-28 scripts/SIM3.m
a first implementation of merging the simulations

@@ -1,0 +1,403 @@
+
+% SIM3
+
+
+%% init
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'horizontal speed [m/s]:','wind speed [m/s]:',...
+     'vehicle direction [angles]:','wind direction [angles]:',...
+     'start coordinate x [m]:','start coordinate y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]',...
+     'altitude [m]'...
+    }, ...
+    'path initialization',[1 40],...
+    {'20','5','270','90','-100','220','60','30','10', '25'}); 
+
+if isempty(answer)
+    strp = [20; 5; 270; 90; -100; 220; 60; 30; 10; 25]; % default
+                                                        % initial data
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+% asking data about the algorithm
+
+answer = inputdlg(...
+    {'order r:','epsilon:','horizon N:'},...
+    'model and algorithm initialization',[1 40],...
+    {'3','1','10'});
+
+if isempty(answer)
+    strp2 = [3; 1; 10]; % default initial data
+else
+    strp2 = str2double(answer);
+end
+
+clear answer;
+
+% stroing data
+
+delta_T = 1e-2;
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = 5; % positive gain constant to be also determined experimentally
+kvv = 5;
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+w = [strp(2)*cosd(strp(4));strp(2)*sind(strp(4))]; % wind vector 
+                                                   % (x, y axis velocity)
+
+vv = 0; % vertical velocity
+sh = strp(1); % horizontal speed
+h = strp(10); % altitude
+p = [strp(5); strp(6)]; % position
+theta = deg2rad(strp(3)); % initial angle
+vh = sh * [cos(theta);sin(theta)]; % initial velocity
[…]

### 2021-01-31 scripts/SIM2.m
preparing the new (complete algorithm) simulation

@@ -57,7 +57,7 @@ end
 
 clear answer;
 
-% stroing data
+% storing data
 
 r = strp2(1);
 eps = strp2(2);

### 2021-01-31 scripts/SIM3.m

@@ -44,7 +44,7 @@ end
 
 clear answer;
 
-% stroing data
+% storing data
 
 delta_T = 1e-2;
 
@@ -100,7 +100,7 @@ Q = ones(size(q,1));
 R = 1;
 
 
-% asking for the plan specifization (cancel to get the default one
+% asking for the plan specifization (cancel to get the default one)
 
 disp('plan specification');
 [bn folder] = uigetfile('.pln');
@@ -342,33 +342,25 @@ figure(1);
 % plotting the path
 subplot(2,2,[1 2]);
 plot(pos(:, 1), pos(:, 2), 'Color', 'r', 'LineWidth', 1.2)
-
 % plotting the energy and the estimated energy
 subplot(2,2,3);
 plot(linspace(0, k, size(pow, 1)), pow(:, 1))
-
 subplot(2,2,4);
 plot(linspace(0, k, size(y, 1)), y(:, 1))
 
 figure(2);
 subplot(7,1,1);
 plot(q(1,1:end))
-
 subplot(7,1,2);
 plot(q(2,1:end))
-
 subplot(7,1,3);
 plot(q(3,1:end))
-
 subplot(7,1,4);
 plot(q(4,1:end))
-
 subplot(7,1,5);
 plot(q(5,1:end))
-
 subplot(7,1,6);
 plot(q(6,1:end))
-
 subplot(7,1,7);
 plot(q(7,1:end))
 
@@ -377,8 +369,8 @@ plot(q(7,1:end))
 
 csvwrite('position_simulationNAME.csv', [pos(:, 1) pos(:, 2) hlist pdanglelist]);
 
-csvwrite('energy_simulationNAME.csv', [linspace(0, size(pow, 1)*delta, size(pow, 1))', ...
-    pow(:, 1), y(:, 1), q(1,1:end)', q(2,1:end)', q(3,1:end)',     ...
+csvwrite('energy_simulationNAME.csv', [linspace(0,size(pow, 1)*delta, size(pow, 1)).', ...
+    pow(:, 1), y(:, 1), q(1,1:end).', q(2,1:end).', q(3,1:end).',     ...
     q(4,1:end)', q(5,1:end)', q(6,1:end)', q(7,1:end)']);
 
 csvwrite('trajdata_simulationNAME.csv', strp);

### 2021-01-31 scripts/SIM4.m

@@ -20,11 +20,11 @@ th_delta = 0;
 hd = 25; % desired altitude [m]
 u_theta = 0.1;
 
-w = [1;0]; % wind vector (x, y axis velocity
+w = [10;0]; % wind vector (x, y axis velocity
 
 vv = 0; % vertical velocity
-sh = 15; % horizontal speed
-h = 24; % altitude
+sh = 20; % horizontal speed
+h = 0; % altitude
 p = [0; 0]; % position
 theta = 0; % initial angle
 vh = sh * [cos(theta);sin(theta)]; % initial velocity
@@ -70,7 +70,7 @@ sh = cth*(th_nominal + th_delta);
 pdot = sh*[cos(theta);sin(theta)] + w;
 
 p = p + pdot*delta_T;
-theta = theta + u_theta*delta_T;
+theta = theta + u_theta*delta_T; % 
 
 % Log
 i = i+1;

### 2021-01-31 scripts/SIM5.m

@@ -1,0 +1,352 @@
+
+% SIM5
+
+% complete simulation of the algo (old physics, not from Hector)
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle speed [m/s]:','wind speed [m/s]:',...
+     'vehicle direction [angles]:','wind direction [angles]:',...
+     'start coordinate x [m]:','start coordinate y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'20','5','270','90','-100','220','60','30','10'});
+
+if isempty(answer)
+    strp = [20; 5; 270; 90; -100; 220; 60; 30; 10];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+% asking data about the algorithm
+
+answer = inputdlg(...
+    {'order r:','epsilon:','horizon N:'},...
+    'model and algorithm initialization',[1 40],...
+    {'3','1','10'});
+
+if isempty(answer)
+    strp2 = [3; 1; 10]; % default initial data
+else
+    strp2 = str2double(answer);
+end
+
+clear answer;
+
+% storing data
+
+vs = strp(1); % desired vecrtical speed
+ws = strp(2); % wind speed
+vd = strp(3); % initial UAV direction 
+wd = strp(4); % wind direction
+start_x = strp(5); % starting position x
+start_y = strp(6); % y
+max_pw = strp(7); % maximum reachable power
+min_pw = strp(8); % minimum
+trig_eps = strp(9); % radius of the triggering point (it's a circular area)
+
+r = strp2(1); % model size (the bigger the more precise)
+eps = strp2(2); % optimization decrement step (to adapt control)
+N = strp2(3); % optimization horizon (for MPC)
+
+
+
+%%% building the model %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+delta_T =  1e-2;
+period = 1;
+[A C] = build_model(2*pi/1, r);
+syms q [2*r+1 1];
+% discretizing 
+Ad = A*delta_T+eye(2*r+1);
+% just a very approximate guesses!
[…]

### 2021-02-01 icra-2021.tex
preparing the new (complete algorithm) simulation
still implementing the full simulation plus some fixes to the text

@@
 Let us hence consider the state of charge (SoC) of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation*}\begin{split}
+\begin{equation}\label{eq:soc}\begin{split}
   \mathrm{SoC}_k=-\left(V-
@@
     V^2-
-    4R_r\tilde{V}y_kV^{-1}}
+    4R_r\tilde{V}y_k/V}
   \right)/2R_rQ_c,\\ 
-\end{split}\end{equation*}
-where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R_r\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity.
+\end{split}\end{equation}
+where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage measured in volts, $R_r\in\mathbb{R}$ the resistance measured in ohms, and $Q_c\in\mathbb{R}$ the constant nominal capacity measured in amperes per hour.
 
@@
 and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
-
-The control constraint set is the trajectory contraint set for the trajectory parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
+The SoC can be either obtained using an initial percentage decreased with Equation~(\ref{eq:soc}), or determined from the UAV.
+
+The control constraint set is the trajectory constraint set for the trajectory parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
 \begin{equation*}
@@
 \begin{equation}\label{eq:cost}\begin{split}
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k+\mathbf{u}^TB\mathbf{u}),\\
-  V_f(\mathbf{q}_k)&:=(1/2)(\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k),
+  V_f(\mathbf{q}_k)&:=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,\\
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=V_f(\mathbf{q}_k)+(1/2)\mathbf{u}^TB\mathbf{u},
 \end{split}\end{equation}
@@
 \begin{algorithmic}
-  \STATE $\mathbf{u}_k\gets\overline{c}_i$
   \WHILE{$\overline{c}_i\notin\mathcal{U}_k,\, y_k\notin\mathcal{Y}_k$}\label{alg2:while}
@@
   \ENDWHILE
+  \STATE $\mathbf{u}_k\gets\overline{c}_i$
 \end{algorithmic} 

### 2021-02-01 scripts/SIM5.m

@@ -210,7 +210,7 @@ for traj = transpose(path)
 
         period = time;
         [A C] = build_model(2*pi/period,r);
-        Ad = A*delta+eye(2*r+1);  
+        Ad = A*delta_T+eye(2*r+1);  
         time = 0;
         updated_period = 1;
     end
@@ -230,7 +230,7 @@ for traj = transpose(path)
         %%% vector field %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
         [dpd, pdangle] = build_gdn2(E,ke,str2sym(traj(3)),log_p(:,end).');
         log_pdangle = [log_pdangle;pdangle];
-        log_dpd = [log_dpd dpd];
+        log_dpd = [log_dpd; dpd];
         
         % dpd is the ideal direction... We have wind though
         % now if the time is sampled every second, the below expression
@@ -274,9 +274,14 @@ for traj = transpose(path)
         k = k+1;
         
         % reached the triggering point, going to stage i+1
-        if all(abs(log_p(end)-trigs(i,:)) <= trig_eps) 
+        if all(abs(log_p(:,end).'-trigs(i,:)) <= trig_eps) 
             break;
         end
+        
+        % reached the battery striking point (just trying)
+        %if all(abs(log_p(:,end).'-[-42.821 219.39]) <= 0.1)
+        %    1 == 1;
+        %end
     end
     
     i = i+1;
@@ -288,10 +293,10 @@ end
 
 figure(1);
 
-time_v = linspace(0,k,size(log_p,1));
+time_v = linspace(0,k*delta_T,length(log_pow));
 % plotting the path
 subplot(2,2,[1 2]);
-plot(log_p(:,1),log_p(:,2),'Color','r','LineWidth',1.2)
+plot(log_p(1,:),log_p(2,:),'Color','r','LineWidth',1.2)
 % plotting the energy and the estimated energy
 subplot(2,2,3);
 plot(time_v,log_pow(:,1))
@@ -318,12 +323,11 @@ plot(time_v,log_q(7,1:end))
 
 %% save
 
-csvwrite('position_simulationNAME.csv',[log_p(:,1).' log_p(:,2).' ...
-    log_pdangle log_dpd(:,1).' log_dpd(:,2).']);
[…]

### 2021-02-01 icra-2021.tex
implementing the dynamic simulation (lot of stuff to do, hopefully soon...)

@@
 \end{split}\end{equation}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal, and $\mathbf{u}$ is defined in Equation~(\ref{eq:state-control}).
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal, and $\mathbf{u}$ ($\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i$) is defined in Equation~(\ref{eq:state-control}).
 

### 2021-02-01 scripts/SIM5.m

@@ -193,6 +193,20 @@ wind_y = delta_T*ws*sind(wd);
 y = []; % model output
 q = []; % model state
 
+
+
+%%% params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% beaware this works only with the default plan and has to be changed for a
+% new one
+min_c1 = -3000;
+max_c1 = 0;
+c1 = max_c1;
+delta_params = 500;
+ %to fix all this
+
+
+%%% physics %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 for traj = transpose(path)
         
     traj = split(traj,";");
@@ -214,7 +228,7 @@ for traj = transpose(path)
         time = 0;
         updated_period = 1;
     end
-    
+        
     while true
         
         time = time+delta_T;
@@ -279,9 +293,9 @@ for traj = transpose(path)
         end
         
         % reached the battery striking point (just trying)
-        %if all(abs(log_p(:,end).'-[-42.821 219.39]) <= 0.1)
-        %    1 == 1;
-        %end
+        if all(abs(log_p(:,end).'-[-43.1845 212.027]) <= 0.1)
+            1 == 1;
+        end
     end
     
     i = i+1;

### 2021-02-07 icra-2021.tex
fixed soc formula

@@
     V^2-
-    4R_r\tilde{V}y_k/V}
-  \right)/2R_rQ_c,\\ 
+    4R_ry_k}
+  \right)/(2R_rQ_c),\\ 
 \end{split}\end{equation}
-where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage measured in volts, $R_r\in\mathbb{R}$ the resistance measured in ohms, and $Q_c\in\mathbb{R}$ the constant nominal capacity measured in amperes per hour.
+where $V\in\mathbb{R}$ is the internal battery 
+% and $\tilde{V}\in\mathbb{R}$ the stabilized 
+voltage measured in volts, $R_r\in\mathbb{R}$ the resistance measured in ohms, and $Q_c\in\mathbb{R}$ the constant nominal capacity measured in amperes per hour.
 

### 2021-02-08 icra-2021.tex
final algorithm rushed implementation

@@
   \nu_{i,\rho+j}&=(g(\overline{c}_i)-g(\underline{c}_i))/(\overline{c}_i-\underline{c}_i),\\
-  \tau_{i,\rho+j}&=\underline{c}_i(g(\overline{c}_i)-g(\underline{c}_i))/(\overline{c}_i-\underline{c}_i)-g(\underline{c}_i),
+  \tau_{i,\rho+j}&=\underline{c}_i(g(\underline{c}_i)-g(\overline{c}_i))/(\overline{c}_i-\underline{c}_i)+g(\underline{c}_i),
 \end{split}\end{equation}
@@
 
-Let us hence consider the state of charge (SoC) of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation}\label{eq:soc}\begin{split}
-  \mathrm{SoC}_k=-\left(V-
+Let us hence consider the state of charge (SoC) $b$ of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
+\begin{equation*}
+  b_k=b_{k-1}-k_b\left(V-
   \sqrt{
@@
     4R_ry_k}
-  \right)/(2R_rQ_c),\\ 
-\end{split}\end{equation}
-where $V\in\mathbb{R}$ is the internal battery 
+  \right)/(2R_rQ_c),
+\end{equation*}
+where $k_b$ is the battery coefficient determined experimentally,  $V\in\mathbb{R}$ is the internal battery 
 % and $\tilde{V}\in\mathbb{R}$ the stabilized 
@@
 \begin{equation*}
-  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,b_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
 \end{equation*}
-and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
-The SoC can be either obtained using an initial percentage decreased with Equation~(\ref{eq:soc}), or determined from the UAV.
+and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption. $b_{k-1}$ can be determined using a sensor.
 
@@
   V_f(\mathbf{q}_k)&:=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,\\
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=V_f(\mathbf{q}_k)+(1/2)\mathbf{u}^TB\mathbf{u},
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k+B\mathbf{u})^T\mathrm{diag}(C)(\mathbf{q}_k+B\mathbf{u}),\hspace*{-2ex}
 \end{split}\end{equation}

### 2021-02-08 scripts/SIM7.m

@@ -1,0 +1,603 @@
+
+% SIM7
+
+% complete simulation of the algo with control (new physics, from Hector)
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','0','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 0; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+% asking data about the algorithm
+
+answer = inputdlg(...
+    {'order r:','epsilon:','horizon N:'},...
+    'model and algorithm initialization',[1 40],...
+    {'3','1','60'});
+
+if isempty(answer)
+    strp2 = [3; 1; 60]; % default initial dSIM6ata
+else
+    strp2 = str2double(answer);
+end
+
+clear answer;
+
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001  .006 .07 .006 .07];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+r = strp2(1); % model size (the bigger the more precise)
+eps = strp2(2); % optimization decrement step (to adapt control)
+N = strp2(3); % optimization horizon (for MPC)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
[…]

### 2021-02-08 scripts/SIM7.m
params controllera

@@ -122,8 +122,9 @@ R = 1;
 % soc
 kb = .004; % battery coefficient
 b = @(y) -kb*(int_v-sqrt(int_v^2-4*res*y))/(2*res*qc);
-soc = linspace(1,.75,288);
-soc = [soc linspace(.743,.6,712)];
+soc = linspace(1,.78,228);
+soc = [soc linspace(.77,.57,10)]; % sudden battery drop
+soc = [soc linspace(.56,.47,762)];
 
 % scaling factors
 nu1 = 135/353; % traj param
@@ -223,6 +224,8 @@ reached = 0; % reached the end of the simulation
 %%% physics %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 path_C = 1; % also just simulation utility
+
+get_optcotrol = 1; % inhibits the controller whenever the limit is reached
 
 while true 
     
@@ -342,7 +345,8 @@ while true
         
         %%% params controller %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
         
-        if k*delta_T >= 60 % let the model to estimate the parameters for 
+        if get_optcotrol*k*delta_T >= 60 
+                           % let the model to estimate the parameters for 
                            % 1 minute
         
             costs = [0]; % result of the cost functions
@@ -355,24 +359,43 @@ while true
             bat_success = 0; % we do expect this to be N, meaning all the 
                              % controls in the sequence sattisfy the
                              % output constraint
-            while or(bat_success < N,...
-                    and(max_c1 == min_c1,max_c2 == min_c2))
-            
+            while 1
+                                          % output constraint respected 
+                                          % with the highest possible
+                                          % control
+                if bat_success == N
+                    break;
+                end
+                
+                if and(max_c1 <= min_c1,max_c2 <= min_c2) % lowest possible
+                                                          % control reached
+                    get_optcotrol = 0;
+                    break;
+                end
+
+                
                 b0 = soc(round(k*delta_T)+1);
+                qq0 = q0; % state
                 bat_success = 0;
                 for j=k-1:k+N-2
             
                     for jj=j+delta_T:delta_T:j+1
                         qq1 = Ad*qq0+B*u(c1,c1_old,c2,c2_old);
                         yy1 = C*qq1;
-                        b0 = b0+b(yy1);
+                        b0 = b0+delta_T*b(yy1);
[…]

### 2021-02-08 icra-2021.tex
fixes to the scaling factors in the text

@@
     0&    &       &  \\
-     & A_1&       &  \\
      &    & \ddots&  \\
@@
   \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T\hspace*{-1ex},\\
-  \mathbf{u}&:=\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i,\,\,\,B=\left[\begin{array}{c} \mathbf{1}\\\mathbf{0}\end{array}\right],
+  B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ & & & & & \end{bmatrix}\\
+  \mathbf{u}&:=\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i,\,\,\,
 \end{split}\end{equation}
 where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$.
-Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row of ones.
-$\mathbf{u}$ is defined as a linear scale transformation from the parameters to the energy.
-In fact $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution of a given parameter to the instantaneous energy consumption.
-
-In particular, the first $\rho$ scaling factors quantifies the contribution of the $i$-th trajectory parameters.
-The following $\sigma$ scaling factors quantifies the contribution of the computations parameters.
-We elucidate how we derive these factors in the next two subsections, in Equation~(\ref{eq:traj-gains}) and~(\ref{eq:energy-comp}).
+Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
+$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and the energy (for the remaining $\sigma$).
+
+We elucidate how we derive these factors in the next two subsections.
 
@@
 In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
-The scaling factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are obtained
-\begin{equation}\label{eq:traj-gains}\begin{split}
-  \nu_{i,j}&=\left((y_{\overline{c}_i}-y_{\underline{c}_i})/(\overline{c}_i-\underline{c}_i)\right)/\rho,\\
-  \tau_{i,j}&=\left(\underline{c}_i(y_{\overline{c}_i}-y_{\underline{c}_i})/(\overline{c}_i-\underline{c}_i)-y_{\underline{c}_i}\right)/\rho,
+
+The scaling factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are derived empirically (e.g., using the simulator).
+For the example in Figure~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
+The variation of the control hence results in an approximate measure of the plans' time variation
+\begin{equation}\label{eq:scale-traj}\begin{split}
+  \nu_{i,j}&=\left((\overline{t}-\underline{t}))/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
+  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
 \end{split}\end{equation} 
-$\forall j\in[\rho]^+$.
-Moreover, $y_{\overline{c}_i},y_{\underline{c}_i}\in\mathbb{R}$ are the maximum (and minimum) energy contribution of the highest (and lowest) change of parameters at $i$-th stage.
-The value is obtained empirically (e.g., using an energy sensor).
 %Whenever the trajectory parameters are not equally distributed, one can define $(y_{\overline{c}_i}-y_{\underline{c}_i})$ as a the highest (and lowest) levels of specific trajectory parameters. 
-Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
+$\forall j\in[\rho]^+$. Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
 
@@
 
-The scaling factors that quantifies the energy contribution of the computations parameters are derived similarly as in Equation~(\ref{eq:traj-gains})
-\begin{equation}\label{eq:energy-comp}\begin{split}
-  \nu_{i,\rho+j}&=(g(\overline{c}_i)-g(\underline{c}_i))/(\overline{c}_i-\underline{c}_i),\\
-  \tau_{i,\rho+j}&=\underline{c}_i(g(\underline{c}_i)-g(\overline{c}_i))/(\overline{c}_i-\underline{c}_i)+g(\underline{c}_i),
-\end{split}\end{equation}
-$\forall j\in[\sigma]^+$. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
+The scaling factors that quantifies the energy contribution of the computations parameters are derived similarly to Equation~(\ref{eq:scale-traj})
+\begin{equation*}\begin{split}
+  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
+  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
+\end{split}\end{equation*}
+$\forall j\in[\rho+1,\rho+\sigma]$. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
 

### 2021-02-08 scripts/SIM7.m

@@ -204,7 +204,7 @@ log_th_delta = th_delta;
 log_pdot = pdot;
 
 strp4 = [m W cl cth th_nominal th_delta hd h vv delta_T]; % saving 
-                                                            % parameters
+                                                          % parameters
 
 
 %% sim
@@ -360,12 +360,10 @@ while true
                              % controls in the sequence sattisfy the
                              % output constraint
             while 1
-                                          % output constraint respected 
-                                          % with the highest possible
-                                          % control
-                if bat_success == N
-                    break;
-                end
+                
+                if bat_success == N % output constraint respected with the
+                    break;          % highest possible control
+                end                
                 
                 if and(max_c1 <= min_c1,max_c2 <= min_c2) % lowest possible
                                                           % control reached

### 2021-02-08 icra-2021.tex
cleaning up the paper

@@
 We then derive some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:plan-spec}.
+Finally, we provide some additional information in Appendixes.
 
@@
 
-We refer the reader to an example in Appendix~\ref{app:plan-example} for a detailed implementation.
+%We refer the reader to an example in Appendix~\ref{app:plan-example} for a detailed implementation.
 In the example, the first trajectory parameter is propagated to all the following trajectories and triggering points.
 
-We store the initial plan in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
+%We store the initial plan in the plan specification, the format is described in Appendix~\ref{app:plan-spec}.
 
@@
 
-\section{Plan Specification}
-\label{app:plan-spec}
-
-\subsection{Format}
-
-The algorithm reads the plan $\Gamma$ from a file--the plan specification--with a specific file format.
-
-The first stage $\Gamma_1$ is expressed in the first line of the file
-\begin{algorithmic}[1]
-  \STATE\textbf{\texttt{$k_e$;$r$;$\varphi_1(\mathbf{p}_k,c_{1,1},\dots,c_{1,\rho})$}}\label{code:stage}
-\end{algorithmic}
-where $k_e$ is a convergence value, $r$ a rotation, and $\varphi_1$ the trajectory.
-The rotation is expressed in binary format with zero being the counter-clockwise rotation, one the clockwise rotation.
-
-The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:stage}
-  \STATE\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
-\end{algorithmic}
-where $x$ and $y$ are the two coordinates of the point.
-The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.
-The coordinates can be expressed in function of the trajectory parameters $c_{1,1},\dots,c_{1,\rho}$.
-
-The line
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:trigger-pt}
-  \STATE\textbf{\texttt{[$\underline{c}_1$,$\overline{c}_1$]}}\label{code:tee-set}
-\end{algorithmic}
-specifies the lower $\underline{c}_{1}$ and upper $\overline{c}_{1}$ bounds of the trajectory $\varphi_1$.
-
-The following $\sigma$ lines
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:tee-set}
-  \STATE\textbf{\texttt{[$\underline{c}_{1,j}$,$\overline{c}_{1,j}$]}}\label{code:parameter-set}
-\end{algorithmic}
-specifies the lower $\underline{c}_{1,j}$ and upper $\overline{c}_{1,j}$ bounds of the $j$-th computation parameter set. They are in ascending order.
-
-This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathcal{C}_1$.
-It can alter the computations individually.
-In fact the $j$-th computation parameter has to be in $\mathcal{S}_{1,j}$.
-
-Follows the entries for stage $\Gamma_2$ (equivalent to lines~\ref{code:stage}--\ref{code:parameter-set}), $\Gamma_3$ and so on, until the last stage.
-We assume that the last triggering point is the final UAV position.
-
-\subsection{Example}
-\label{app:plan-example}
-
-We discuss how to specify an initial plan with an example of a survey scenario, equivalent to the one in Figure~\ref{fig:il-abs}.
-
-Recall that the plan is composed of a set of stages (Section~\ref{sec:prob}). It has a variable number of entries per each stage. The first line
-\begin{algorithmic}[1]
-  \STATE\textbf{\texttt{0.0003;0;(x+45)\^{}2+(y-146)\^{}2-4900+c1}}\label{code:firstcircle}
-\end{algorithmic}
-corresponds to the trajectory $\varphi_1(\mathbf{p}_k,c_{1,1}):=(x+45)^2+(y-146)^2-4900+c_{1,1}$ in the initial stage $\Gamma_1$.
-The trajectory is a circle.
-The gain is $k_e=3\cdot 10^{-4}$, and the rotation is counter-clockwise--we use the rotation matrix $E$ from Equation~(\ref{eq:pd}).
-We note that line~\ref{code:firstcircle} further specifies the parameter {\tt\textbf{c1}} of the radius of the circle.
-It corresponds to $c_{1,1}$ in Definition~\ref{def:mission}.
-
-The following line
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:firstcircle}
-  \STATE\textbf{\texttt{-sqrt(4900+c1)-45,146}}\label{code:trigger}
-\end{algorithmic}
-specifies the triggering point $\mathbf{p}_{\Gamma_1}$.
-{\tt\textbf{sqrt}} is the square root.
-The UAV reaches the triggering point within a given $\varepsilon$ (the tolerance), and the algorithm switches to the next stage $\Gamma_2$.
-We note that the triggering point is in function of the parameter {\tt\textbf{c1}}.
-This is necessary; an change in a parameter in one stage affects the overall flight.
-
-Let us assume the scenario has two computations.
-One computation is the CNN object detection algorithm, and it can be planned by one parameter $c_{1,2}$, the fps rate.
-Another computation is the variable key-size encryption algorithm.
-It can be planned by one parameter $c_{1,2}$, the key-size.
-Then in the plan
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:trigger}
-  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset}
-  \STATE\textbf{\texttt{[2,10]}}\label{code:qos1set}
-  \STATE\textbf{\texttt{[32,448]}}\label{code:qos2set}
-\end{algorithmic}
-line~\ref{code:teeset} corresponds to the trajectory $\varphi_1$'s contraints set $\mathcal{C}_1=[-3\cdot10^3,0]$.
-The algorithm selects $c_{1,1}\in\mathcal{C}_1$.
-Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathcal{S}_{1,1}$ for the computation parameter $c_{1,2}$.
-Line~\ref{code:qos1set} corresponds to the computation constraints set $\mathcal{S}_{1,2}$ for the computation parameter $c_{1,2}$.
-Lines~\ref{code:teeset}--\ref{code:qos2set} must follow the ascending order of the parameters.
-Lines~\ref{code:firstcircle}--\ref{code:qos2set} all describe the stage $\Gamma_1$.
-
-Once the UAV reaches the triggering point (line~\ref{code:trigger}) and there are no further lines, the algorithm terminates (the last triggering point is the final point).
-If there are further lines, the stage switches to $\Gamma_2$
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:qos2set}
-  \STATE\textbf{\texttt{0.05;1;x+sqrt(4900+c1)+45}}\label{code:tee2}
-  \STATE\textbf{\texttt{-sqrt(4900+c1)-45,11}}\label{code:trigger2}
-  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset2}
-  \STATE\textbf{\texttt{[2,10]}}
-  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset12}
-\end{algorithmic}
-line~\ref{code:tee2} corresponds to the trajectory $\varphi_2(\mathbf{p}_k,c_{1,1}):=x+\sqrt{4900+c_{1,1}}+45$, a linear equation that intersects the triggering point (line~\ref{code:trigger}).
-The gain is $k_e=5\cdot 10^{-2}$, and the rotation is opposite to line~\ref{code:firstcircle}.
-The algorithm computes $-E$ from the rotation matrix in Equation~(\ref{eq:pd}).
-
-The gain is different from the one used in $\varphi_1$ as different equations require different convergence rate.
-When we follow a circle it is useful to turn the rotation direction in advance.
-When we follow a straight line, it is preferable to turn the rotation direction closer to the line.
-The rotation is likewise different.
-In fact, the rotation matrix $E$ points upwards in the space.
-It guides the UAV in the counter-clockwise direction (see Figure~\ref{fig:tee1}; the UAV is traveling counter-clockwise).
-The rotation matrix $-E$ points downwards and guides the UAV in the clockwise direction.
-
-The triggering point of the stage $\Gamma_2$ at line~\ref{code:trigger2} also depends on the parameter {\tt\textbf{c1}}.
-Lines~\ref{code:teeset2}--\ref{code:qosset12} specifies the constraints sets.
-They are expressed the same way as lines~\ref{code:teeset}--\ref{code:qos2set}.
-They have to be specified explicitly for each stage, although they don't change.
-The current implementation of the algorithm has no other means to distinguish different constraints sets.
-
-Again, if there are further lines and UAV reaches the triggering point (line~\ref{code:trigger2}), the algorithm switches the stage to $\Gamma_3$
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:qosset12}
-  \STATE\textbf{\texttt{0.0003;90;(x+sqrt(4900+c1)-30)\^{}2}}
-  \textbf{\texttt{\hspace*{14ex}+(y-11)\^{}2-5625}}\label{code:tee3}
-  \STATE\textbf{\texttt{-sqrt(4900+c1)+105,11}}
-  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}
-  \STATE\textbf{\texttt{[2,10]}}
-  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset32}
-\end{algorithmic}
-line~\ref{code:tee3} corresponds to the trajectory $\varphi_3(\mathbf{p}_k,c_{1,1}):=(x+\sqrt{4900+c_{1,1}}-30)^2+(y-11)^2-5625$, a circle of fixed size that changes the coordinates in function of the parameter {\tt\textbf{c1}}.
-The rotation is counter-clockwise, alike $\varphi_1$.
-
-The lines
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:qosset32}
-  \STATE\textbf{\texttt{0.05;90;x+sqrt(4900+c1)-105}}\label{code:tee4}
-  \STATE\textbf{\texttt{-sqrt(4900+c1)+105,147}}
-  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}
-  \STATE\textbf{\texttt{[2,10]}}
-  \STATE\textbf{\texttt{[32,448]}}\label{code:qosset42}
-  \STATE\textbf{\texttt{0.0003;90;(x-sqrt(4900+c1)+105)\^{}2}}
-  \textbf{\texttt{\hspace*{14ex}+(y-147)\^{}2-4900+c1}}\label{code:tee5}
-  \STATE\textbf{\texttt{-3*sqrt(4900+c1)+105,147}}\label{code:triggerlast}
-  \STATE\textbf{\texttt{[-3*10\^{}3,0]}}\label{code:teeset5}
-\end{algorithmic}
-defines the stages $\Gamma_4$ and $\Gamma_5$.
-Line~\ref{code:tee4} corresponds to the trajectory $\varphi_4(\mathbf{p}_k,c_{1,1}):=x+\sqrt{4900+c_{1,1}}-105$.
-Line~\ref{code:tee5} corresponds to the trajectory $\varphi_4(\mathbf{p}_k,c_{0,1}):=(x-\sqrt{4900+c_{0,1}}+105)^2+(y-147)^2-4900+c_{0,1}$.
-
-We note that the survey scenario example changes the radius of the circular trajectory $\varphi_1$ through the parameter $c_{1,1}$.
-It also changes the radius of $\varphi_5$ in the same way (recall Assumption~\ref{assm:periodic}).
-The other trajectories ($\varphi_2,\varphi_3,\varphi_4$) displacement alters the distance between the lines in the survey.
-For simplicity, we suppose line~\ref{code:triggerlast} describes the final point.
-We further suppose the user does not desire to process any computation in the last stage $\Gamma_5$.
-To inhibit the computations
-\begin{algorithmic}[1]
-  \setcounterref{ALC@line}{code:teeset5}
-  \STATE\textbf{\texttt{[0,0]}}
-  \STATE\textbf{\texttt{[0,0]}}
-\end{algorithmic}
-
-If there are any following stages in the survey, they are constructed the same way.
-The stages $\Gamma_i$ for $i:=\{0,4,8,\dots\}$ contain trajectory circle with variable radius.
-For $i:=\{1,3,5,\dots\}$ trajectory line with variable displacement.
-For $i:=\{2,6,10,\dots\}$ trajectory circle with fixed radius and variable displacement.
-
-%We need a further abstraction before we can simulate a mission in Appendix~\ref{app:simulator}. The algorithm needs to know how to model the tasks--the software components.
-
-%\section{Simulator}
-%\label{app:simulator}
-
-%We discuss how to execute the initial mission plan and the component specification in the simulator.
-The reader can use the simulator to simulate different environmental interference and their effects on the mission.
-
-%The simulator is written in MATLAB and released under MIT license.
-It implements the algorithm (Subsection~\ref{sec:algo}) providing a position $\mathbf{p}_k$ at each time step $k$ and an energy sensor's value $y_k^a$.
-It is derived from empirical data.
-It is an abstraction of the physical observations.
-
-%The user is prompted to initialize the trajectory and the algortihm.
-
 \end{document}

### 2021-02-09 icra-2021.tex
fixing the text

@@
 
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:intro}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}  %
+\label{sec:intro}       %
+                        %
 Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of these scenarios is a UAV flying a path and performing some on-board computational tasks.
+A typical example of these scenarios is a UAV following a path and performing some on-board computational tasks.
 For instance, the UAV might detect ground patterns and notify other ground-based actors with little human interaction.
@@
   \end{tikzpicture}
-  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of both the path (\ref{sth:ii}~travels a more accurate survey than~\ref{sth:iii}), and computations (\ref{sth:i}~elaborates more images per second than~\ref{sth:ii}).
-In bottom left, the collected energy data of the UAV flying the scenario, along the power spectrum (bottom right) where the first frequency has been filtered.}
+  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of the path and computations all together.
+An initial plan~(in~\ref{sth:i}) is adapted computation-wise~(in~\ref{sth:ii}) and path-wise~(in~\ref{sth:iii}).
+In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario, along the power spectrum on the right.}
   \label{fig:il-abs}
@@
 
-Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations.
-To model the path we use multiple trajectories and denote each with a mathematical function.
+Unlike most of the past planning algorithms literature, our algorithm plans the path and computations all together.
+To model the path we use multiple mathematical functions.
 In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
-To model the computations we use a profiling tool presented in previous work~\cite{seewald2019coarse}.
-To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory.
-The use of vector fields for guidance is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
+To model the computations we use \powprof{}, a profiling tool presented in previous work~\cite{seewald2019coarse}.
+To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the path.
+The use of vector fields for guidance is indeed widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
 
@@
 Periodicity is often present due to repetitive patterns in the plan~\cite{seewald2020mechanical}.
-Indeed, UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue).
+Indeed, UAV scenarios often iterate over a set of tasks and paths (e.g., monitoring or search and rescue).
 Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
@@
 The plan is structured as follows.
-Trajectory-wise, the UAV flies in circles and lines covering a polygon.
-Computationally-wise, it detects obstacles using a convolutional neural network (CNN) and notifies grounded mobile robots employed for harvesting.
+Path-wise, the UAV flies in circles and lines covering a polygon.
+Computation-wise, it detects obstacles using a convolutional neural network (CNN) and notifies grounded mobile robots employed for harvesting.
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:il-abs} shows a slice of such plan.
-We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations (see Section~\ref{sec:experimental}), in presence of a standard battery.
+Figure~\ref{fig:il-abs} shows such plan.
+We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations in presence of a standard battery (see Section~\ref{sec:experimental}).
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Planning Overview}
-\label{sec:prob}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Planning Overview}  %
+\label{sec:prob}             %
+                             %
 The algorithm inputs a user-specified initial plan that consist of different stages.
-At each stage the UAV flies a trajectory, and does some computations.
-Per each stage the plan contains some parameters that allow to alter the path and computations along an energy budget.
+At each stage the plan contains some parameters that allow to alter the path and computations along an energy budget.
 The alterations are bounded.
-There is one trajectory constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations.
+There is one path constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations.
 In Figure~\ref{fig:il-abs}, there are two parameters.
-One relative to the trajectory (\ref{sth:ii}~has indeed a shorter distance between the survey lines then~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second then~\ref{sth:ii}).
-
-The algorithm outputs the control (the parameters) using output model predictive control (MPC)~\cite{rawlings2017model}.
-The UAV utilizes the control to influence its energy consumption to meet the energy budget.
+One relative to the path (\ref{sth:ii}~has a shorter distance between the lines than~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second than~\ref{sth:ii}).
+
+The algorithm outputs the control (the parameters) using output model predictive control (MPC)~\cite{rawlings2017model} where it checks the satisfaction of the battery constraints.
 The control is data-driven.
@@
 Bold lower-case letters indicates vectors.
-$c_{i,j}$ specifies the $j$-th parameter of the $i$-th parameters set $c_i$.
-$c_{i,j}^0$ is the optimal value of the parameter $c_{i,j}$ w.r.t.
-a given cost function $l$, and $\underline{c}_{i,j},\overline{c}_{i,j}$ its lower and upper bounds.
+$c_{i,j}$ the $j$-th parameter of the $i$-th parameters set $c_i$.
+$\underline{c}_{i,j},\overline{c}_{i,j}$ are the lower and upper bounds of the parameter $c_{i,j}$.
 The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list $\langle c_i \rangle$ of $n$ parameters.
 
-Let us assume that the trajectory at stage $i$ can be altered with $\rho$ trajectory parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computations parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
-We then express the trajectory as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the trajectory parameters.
+Let us assume that the path at stage $i$ can be altered with $\rho$ path parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computations parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
+We then express the path as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the path parameters.
 The function returns a metric of the distance between the point and the nominal trajectory.
 We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of trajectory parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
+We discuss the concrete meaning of the value of path parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
 
@@
   \input{\figpath/traj1.tikz}
-  \caption{The notation on a small initial slice of the plan of Figure~\ref{fig:il-abs} in 2D.}
+  \caption{Plan definition notation shown on an initial slice of the plan of Figure~\ref{fig:il-abs} in 2D.}
   \label{fig:traj1}
@@
   \end{split}\end{equation*}
-  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the trajectory constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
-$\mathbf{p}_k$ is a point of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t.
+  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the path constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
+$\mathbf{p}_k$ is a point of a UAV flying at an altitude $h\in\mathbb{R}_{>0}$\footnote{The altitude might change at different flying phases and under different atmospheric conditions} w.r.t.
 some inertial navigation frame $\mathcal{O}_W$.
-In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are trajectories.
+In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are paths.
 $\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
 They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
-The constaints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the trajectories $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\rho}$ (gray area in the figure).
+The constraints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the paths $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\rho}$ (gray area in the figure).
 This area is bounded by $\underline{c}_i,\overline{c}_i$, and can be different per each stage (in Figure~\ref{fig:traj1}, the area relative to $\Gamma_4$ is bounded by $\underline{c}_4,\overline{c}_4$).
@@
 
-\begin{figure}[h]
-  \center
-  \begin{tikzpicture}[shorten >=1pt,node distance=23ex,on grid,auto] 
-    \node        (q_dots0) {$\cdots$};
-    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
-    \node        (q_dots1) [right=of q_0] {$\cdots$};   
-    \path[->]
-    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1^\rho,\dots,c_{i-1}^\rho)$} (q_0)
-    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1^\rho,\dots,c_{i}^\rho)$} (q_dots1)    
-    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
-    ; %end path
-  \end{tikzpicture}
-  \caption{Detail of the stage $\Gamma_i$ in the FSM}
-  \label{fig:state-machine2}
-\end{figure}
-
-Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
+%\begin{figure}[h]
+%  \center
+%  \begin{tikzpicture}[shorten >=1pt,node distance=23ex,on grid,auto] 
+%    \node        (q_dots0) {$\cdots$};
+%    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
+%    \node        (q_dots1) [right=of q_0] {$\cdots$};   
+%    \path[->]
+%    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1^\rho,\dots,c_{i-1}^\rho)$} (q_0)
+%    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1^\rho,\dots,c_{i}^\rho)$} (q_dots1)    
+%    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
+%    ; %end path
+%  \end{tikzpicture}
+%  \caption{Detail of the stage $\Gamma_i$ in the FSM}
+%  \label{fig:state-machine2}
+%\end{figure}
+
+%Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
 
@@
 \begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the trajectory parameters $c_1^\rho$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
+  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the path parameters $c_1^\rho$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
   \begin{equation*}\begin{split}
@@
 Physically, this means that the plan is approximately periodic.
-The justification for this assumptions originates from empirical data (we refer the reader back to the illustrative abstract in Figure~\ref{fig:il-abs}).
-It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over trajectories and computations attending some triggering events (such as detections).
+The justification for this assumptions originates from empirical data (we refer the reader back to Figure~\ref{fig:il-abs}).
+It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over paths and computations attending some events (such as detections).
 We will see this assumption being eased in practice for non-periodic plans in Section~\ref{sec:experimental}.
@@
   \end{equation*}
-  where the trajectories in the first column are evaluated on $\mathbf{p},c_1^\rho$, in the second on $\mathbf{p}+\mathbf{d},c_1^\rho$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1^\rho$.
+  where the paths in the first column are evaluated on $\mathbf{p},c_1^\rho$, in the second on $\mathbf{p}+\mathbf{d},c_1^\rho$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1^\rho$.
 \end{prop}
 \begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+e_j$ and $e_j$ is the $j$-th constant difference.
-It is the same for trajectories selected at each period.
+It is the same for paths selected at each period.
 This is equivalent to Assumption~\ref{assm:periodic}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Periodic Energy Model}
-\label{sec:energy-model}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                                 %
+\section{Periodic Energy Model}  %
+\label{sec:energy-model}         %
+                                 %
 We refer to the instantaneous energy consumption evolution simply as the energy signal.
@@
 
-Once we illustrate the energy model, we enhance it with the energy contribution of the trajectory in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
-
-Let us consider a periodic signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the energy signal
+Once we illustrate the energy model, we enhance it with the energy contribution of the path in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
+
+Let us consider a periodic energy signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the energy signal
 \begin{equation}\label{eq:fourier}
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency ($T$ is the period from Definition~\ref{def:period}), and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
@@
 
-The state $\mathbf{q}$ are the energy coefficients
+The state $\mathbf{q}$ contains the energy coefficients
 \begin{equation}\label{eq:state-details}\begin{split}
@@
 \begin{proof}
-The equality of the signal and output is achieved by a proper choice of items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
 We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess.
@@
 
-Let us consider for practical reasons the discretized version $A_d:=A\Delta t+I$ of the matrix $A$.
-We denote the continuous and discrete time with the standard notation $t,k$.
-We use the forward Euler approximation with a small enough value of the time step $\Delta t$.
+Let us consider for practical reasons the discretized version $A_d$ of the matrix $A$. We denote the continuous and discrete time with the standard notation (such as $t,k$).
 
@@
 Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and the energy (for the remaining $\sigma$).
+$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and the power (for the remaining $\sigma$).
+%Indeed an alteration of the path affects the overall flying time (and consequently the energy). An alteration the the computations affects the instantaneous energy consumption.
 
@@
 
-\subsection{Trajectory parameters energy contribution}
+\subsection{Path parameters energy contribution}
 \label{sec:model}
@@
   \input{\figpath/traj2.tikz}
-  \caption{The alteration of the trajectory parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path from Figure~\ref{fig:il-abs}).}
+  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path in Figure~\ref{fig:il-abs}).}
   \label{fig:tee1}
@@
 
-Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
+%Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
 For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
@@
 \end{equation}
-delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
-$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory.
+delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
+$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the path.
 Physically, this means the UAV is flying exactly over the nominal trajectory.
-The trajectory parameters allows to change the trajectory.
-They are a way to alter the nominal trajectory in the initial plan and thus alter the energy.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the trajectory parameters such that $\varphi_i$ has the highest instantaneous energy consumption, while still respecting the energy budget.
-In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan. The sequence of these parameters (control sequence) forms the path $\mathcal{P}$.
-
-The scaling factors for the trajectory parameters from Equation~(\ref{eq:state-control}) are derived empirically (e.g., using the simulator).
+The path parameters allows to change the path.
+They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by e.g., changing the flying time in the example in Figure~\ref{fig:il-abs}.
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that $\varphi_i$ has the highest energy consumption, while still respecting the energy budget.
+In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan.
+
+We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
+\begin{equation}\label{eq:pd}
+  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
+    0&1\\-1&0
+  \end{bmatrix},
+\end{equation}
+where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
+
+The scaling factors for the path parameters from Equation~(\ref{eq:state-control}) are derived empirically.
 For the example in Figure~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
@@
 $\forall j\in[\rho]^+$. Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
-
-We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
-\begin{equation}\label{eq:pd}
-  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
-    0&1\\-1&0
-  \end{bmatrix},
-\end{equation}
-where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
 

### 2021-02-09 icra-2021.tex
added the proof the the theorem

@@
 \begin{proof}
-  The proof is based on mathematical induction. 
-  Base case: *
-
-  Induction step: *
-
+  From Definition~\ref{def:valid} we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the path is valid, and from Proposition~\ref{prop:rank} we know that the path is periodic.
+Hence if the set $\mathcal{J}$ is valid, then also the set $i[j-n+1,j]\subseteq[l]^+$ is valid for a given $i$.
+From Assumption~\ref{assm:valid} we note that $i\in[l/n]^+$ and thus under the assumptions $\mathcal{J}=[l]^+$.
+Due to the periodicity, Lemma~\ref{lem:eqv} tells us that we can use the proposed approach to model the energy.
 \end{proof}
+
+We can thus output a valid control sequence for the initial plan $\Gamma$.
+For practical means, we consider some realistic constraints to the energy of a flying UAV.
+We illustrate such constraints in the following subsection.
 

### 2021-02-09 icra-2021.tex
improvements to the text

@@
 
-Let us consider for practical reasons the discretized version $A_d$ of the matrix $A$. We denote the continuous and discrete time with the standard notation (such as $t,k$).
+Let us consider for practical reasons the discretized version of the system in Equation~\ref{eq:state-perf}.
 
@@
 
-We note that while the trajectory can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation constraint set.
+We note that while the path can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation constraint set.
 
@@
 
-%%%%%%%%%%%%%%%%%%%
-\section{Algorithm}
-\label{sec:algo}
-
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Algorithm}  %
+\label{sec:algo}     %
+                     %
 The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on a valid path: to solve Problem~\ref{pb}.
@@
 \begin{proof}
-  From Definition~\ref{def:valid} we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the path is valid, and from Proposition~\ref{prop:rank} we know that the path is periodic.
+  From Definition~\ref{def:valid}, Assumption~\ref{assm:valid}, we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the path is valid, and from Proposition~\ref{prop:rank} we know that the path is periodic.
 Hence if the set $\mathcal{J}$ is valid, then also the set $i[j-n+1,j]\subseteq[l]^+$ is valid for a given $i$.
-From Assumption~\ref{assm:valid} we note that $i\in[l/n]^+$ and thus under the assumptions $\mathcal{J}=[l]^+$.
-Due to the periodicity, Lemma~\ref{lem:eqv} tells us that we can use the proposed approach to model the energy.
+From the assumption we note that $i\in[l/n]^+$ and, due to the proposition, $\mathcal{J}=[l]^+$.
+Due to the periodicity, Lemma~\ref{lem:eqv} allows us to use the proposed approach to model the energy.
 \end{proof}
@@
 We can thus output a valid control sequence for the initial plan $\Gamma$. 
-For practical means, we consider some realistic constraints to the energy of a flying UAV.
-We illustrate such constraints in the following subsection.
+%The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available. 
+For practical means, we consider some realistic constraints to the energy of a flying UAV. We illustrate such constraints in the following subsection.
 
@@
 
-The control constraint set is the trajectory constraint set for the trajectory parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
+The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
 \begin{equation*}
@@
 The algorithm first initializes the position, energy coefficients, and control (line~\ref{alg:init}).
-
-The position is updated at line~\ref{alg:pos}, using the expression from Equation~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
-The expression depends on the trajectory $\varphi_i$ from stage $\Gamma_i$.
-The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$.
+It updates the position at line~\ref{alg:pos}, using the expression from Equation~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
+The expression depends on the path $\varphi_i$ from stage $\Gamma_i$.
+The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (we recall the FSM in Definition~\ref{def:mission}).
 
@@
 \end{split}\end{equation}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of the matrix $C$ from Equation~(\ref{eq:state-details}) on the diagonal, and $\mathbf{u}$ ($\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i$) is defined in Equation~(\ref{eq:state-control}).
-
-We note from Lemma~\ref{lem:eqv} that the expression in Equation~(\ref{eq:cost}) denotes the square of the predicted instantaneous energy consumption.
-Moreover, higher the horizon, higher the complexity and the accuracy of the control.
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}), and $\mathbf{u}$ is defined in Equation~(\ref{eq:state-control}).
+
+We note from Lemma~\ref{lem:eqv} that the expression in Equation~(\ref{eq:cost}) denotes the square of the predicted power.
+Moreover, higher the horizon, higher the complexity and the robustness of the control to the output constraints.
 
@@
 \end{algorithmic} 
-where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of trajectory and computational parameters are reduced by the this step if they don't meet the constraints).
-To evaluate the inclusion in the output control set, the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution} (we note that the condition can be written $\overline{c}_i\notin\mathcal{U}_k,\, C\mathbf{q}_k\notin\mathcal{Y}_k$).
-
-We finally note that one can express the tradeoffs between trajectory and computation parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with the constraints
+where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computational parameters are reduced by the steps if they don't meet the constraints).
+To evaluate the inclusion in the output control set, the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution}.
+
+We finally note that one can express the tradeoffs between parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with the constraints
 \begin{equation*}
@@
 where $r_i\in\mathbb{R}^n$ and $R_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $R_i$ is the identity matrix, there is no relation between the parameters).
-
-The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available using the subroutine.
-
-%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Results}
-\label{sec:experimental}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}         %
+\label{sec:experimental}  %
 

### 2021-02-09 icra-2021.tex
fixing algorithm section further

@@
 
-  abstract\\
-  abstract\\
   abstract\\
@@
 An initial plan~(in~\ref{sth:i}) is adapted computation-wise~(in~\ref{sth:ii}) and path-wise~(in~\ref{sth:iii}).
-In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario, along the power spectrum on the right.}
+In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario, along its power spectrum.}
   \label{fig:il-abs}
@@
 
+\vspace*{-2ex}
 Planning algorithms literature for mobile robots includes topics such as trajectory generation and path planning.
@@
 To model the computations we use \powprof{}, a profiling tool presented in previous work~\cite{seewald2019coarse}.
-To guide the UAV we use a vector field~\cite{de2017guidance} that converges smoothly to the path.
-The use of vector fields for guidance is indeed widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
+To guide the UAV we use a vector field~\cite{de2017guidance} that converges to the path.
+The use of vector fields for guidance is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
 
@@
 
-\begin{defn}[Valid control sequence and path]\label{def:valid}
+\begin{defn}[Validity]\label{def:valid}
   Given a close strictly positive discrete interval $\mathcal{J}:=[j-n+1,j]$ (for $j\in\mathbb{Z}_{>0},j\leq l$ and $n$ given in Assumption~\ref{assm:periodic}), a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $\mathcal{J}$ if for every stage $\Gamma_{i-1},\,i\in\mathcal{J}$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
 
-  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path} on $\mathcal{J}$
+  The plan resulting from such control sequence is a \emph{valid plan} on $\mathcal{J}$. It generates the \emph{valid path}
   \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,\forall i\in\mathcal{J},\,\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\},
+   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,\forall i\in\mathcal{J},\,\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\}.
   \end{split}\end{equation*}
 \end{defn}
-where we recall that $\mathbf{u}_k=\begin{bmatrix}c_k^\rho & c_k^\sigma\end{bmatrix}^T$ from Equation~(\ref{eq:state-control}).
-
-Let us consider the assumption that at least one period in the user-defined initial plan is valid.
+
+Let us consider the assumption that the plan is valid on at least one period.
 
 \begin{assm}[Period validity]\label{assm:valid}
-  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n]^+$ s.t. the period $\Gamma_{(i-1)n+1},\dots,\Gamma_{in}$ is valid.
+  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n]^+$ s.t. the subplan $\Gamma_{(i-1)n+1},\dots,\Gamma_{in}$ is valid.
 \end{assm}
 
-Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
+Let us proof that if the plan is periodic and valid on at least one period, then the plan is valid.
 
 \begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
+  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (the plan is valid on a period, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
 Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
@@
 \begin{proof}
-  From Definition~\ref{def:valid}, Assumption~\ref{assm:valid}, we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the path is valid, and from Proposition~\ref{prop:rank} we know that the path is periodic.
-Hence if the set $\mathcal{J}$ is valid, then also the set $i[j-n+1,j]\subseteq[l]^+$ is valid for a given $i$.
+  From Definition~\ref{def:valid}, Assumption~\ref{assm:valid}, we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the plan is valid, and from Proposition~\ref{prop:rank} we know that the plan is periodic.
+Hence if the set $\mathcal{J}$ delimits a valid plan, then also the set $i[j-n+1,j]\subseteq[l]^+$ does for a given $i$.
 From the assumption we note that $i\in[l/n]^+$ and, due to the proposition, $\mathcal{J}=[l]^+$.
-Due to the periodicity, Lemma~\ref{lem:eqv} allows us to use the proposed approach to model the energy.
+Finally, due to the periodicity, Lemma~\ref{lem:eqv} allows us to use the proposed approach to model the energy.
 \end{proof}
 
-We can thus output a valid control sequence for the initial plan $\Gamma$. 
-%The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available. 
-For practical means, we consider some realistic constraints to the energy of a flying UAV. We illustrate such constraints in the following subsection.
+The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available. 
+For practical means indeed, we consider some realistic constraints to the energy of a flying UAV. We illustrate such constraints in the following subsection.
 
@@
 \end{equation*}
-and $\max{\mathcal{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption. $b_{k-1}$ can be determined using a sensor.
+and $b_kQ_cV$ is the maximum instantaneous energy consumption.
 
@@
 The expression depends on the path $\varphi_i$ from stage $\Gamma_i$.
-The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (we recall the FSM in Definition~\ref{def:mission}).
+The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (FSM in Definition~\ref{def:mission}).
 
 The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
-The a priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
-At line~\ref{alg:mpc}, the algorithm uses robust output feedback model predictive control (MPC)~\cite{rawlings2017model} to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function
+A priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
+At line~\ref{alg:mpc}, the algorithm uses MPC to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function (higher the horizon, higher the complexity and the robustness of the control to the output constraints)
 \begin{equation}\label{eq:cost}\begin{split}
@@
 \end{split}\end{equation}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}), and $\mathbf{u}$ is defined in Equation~(\ref{eq:state-control}).
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}), and $B$, $\mathbf{u}$ are defined in Equation~(\ref{eq:state-control}).
 
 We note from Lemma~\ref{lem:eqv} that the expression in Equation~(\ref{eq:cost}) denotes the square of the predicted power.
-Moreover, higher the horizon, higher the complexity and the robustness of the control to the output constraints.
-
-We further note that at every step of the summary on line~\ref{alg:mpc} the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
-In particular, at each steps it performs the subroutine
+
+We further note that at every step of the sum on line~\ref{alg:mpc}, the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
+In particular, it performs a subroutine
 \begin{algorithmic}
@@
 where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computational parameters are reduced by the steps if they don't meet the constraints).
-To evaluate the inclusion in the output control set, the algorithm evolves the state from its previous estimate similarly as at line~\ref{alg:evolution}.
 

### 2021-02-10 icra-2021.tex
fixed issue with control in the formula

@@
     0&    &       &  \\
+     & A_1&       &  \\
      &    & \ddots&  \\
@@
   \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T\hspace*{-1ex},\\
-  B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ & & & & & \end{bmatrix}\\
-  \mathbf{u}&:=\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i,\,\,\,
+  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),B=\begin{bmatrix} 0 &\hspace*{-.5ex} \cdots\hspace*{-.5ex} & 0 & 1 &\hspace*{-1ex} \cdots\hspace*{-1ex} & 1 \\ & & & & & \end{bmatrix}\\
+  \hat{\mathbf{u}}_k&:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i,\,\,\,
 \end{split}\end{equation}
@@
 $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and the power (for the remaining $\sigma$).
+$\hat{\mathbf{u}}_k$ is then the difference in the instantaneous power contribution.
 %Indeed an alteration of the path affects the overall flying time (and consequently the energy). An alteration the the computations affects the instantaneous energy consumption.
@@
 For the example in Figure~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
-The variation of the control hence results in an approximate measure of the plans' time variation
+The variation of the control hence results in an approximate measure of the plans' time variation with factors
 \begin{equation}\label{eq:scale-traj}\begin{split}
-  \nu_{i,j}&=\left((\overline{t}-\underline{t}))/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
-  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
+  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
+  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
 \end{split}\end{equation} 
 %Whenever the trajectory parameters are not equally distributed, one can define $(y_{\overline{c}_i}-y_{\underline{c}_i})$ as a the highest (and lowest) levels of specific trajectory parameters. 
-$\forall j\in[\rho]^+$. Moreover, let $\nu_{i,1},\dots,\nu_{i,\rho}$ be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
+$\forall j\in[\rho]^+$. Moreover, let the factors be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
 
@@
 
-The scaling factors that quantifies the energy contribution of the computations parameters are derived similarly to Equation~(\ref{eq:scale-traj})
+The scaling factors add the computational energy component to the model in Equation~(\ref{eq:state-perf}). They are derived similarly to Equation~(\ref{eq:scale-traj})
 \begin{equation*}\begin{split}
@@
 \end{split}\end{equation*}
-$\forall j\in[\rho+1,\rho+\sigma]$. Moreover, let $\nu_{i,\rho+1},\dots,\nu_{i,\rho+\sigma}$ be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
-
-The factors thus add the computational energy component to the model in Equation~(\ref{eq:state-perf}).
+$\forall j\in[\rho+1,\rho+\sigma]$. Moreover, let the factors be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
 

### 2021-02-10 scripts/SIM8.m
trying the controller policy proposed by Ulrik

@@ -1,0 +1,680 @@
+
+% SIM7
+
+% complete simulation of the algo with control (new physics, from Hector)
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','0','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 0; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001  .006 .07 .006 .07];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+
+strp2 = 3;
+r = strp2; % model size (the bigger the more precise)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = strp3(1); % positive gain constant to be also determined experimentally
+kvv = strp3(2);
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+% guidance
+kd = strp3(3);
+
+% physics init
+w =  ws*[cosd(wd);sind(wd)]; % wind vector (x, y axis velocity)
+
+h = 20; % initial altitude
+vv = 0; % initial vertical velocity
[…]

### 2021-02-11 scripts/SIM8.m
improving the controller

@@ -35,7 +35,7 @@ clear answer;
 
 % gains
 %       kp, kvv  kd,  ke1, ke2, ke3, ke4
-strp3 = [5   5  .001  .006 .07 .006 .07];
+strp3 = [5   5  .001 .006  .1  .006  .1];
 %         
 
 vd = strp(1); % initial UAV direction
@@ -104,10 +104,10 @@ Q = ones(size(q,1));
 R = 1;
 
 % soc
-kb = .0018; % battery coefficient
+kb = .00183; % battery coefficient
 b = @(y) -kb*(int_v-sqrt(int_v^2-4*res*y))/(2*res*qc);
-soc = linspace(1,.9099,94);
-soc = [soc linspace(.9,.78,134)];
+soc = linspace(1,.9,93);
+soc = [soc linspace(.84,.76,135)];
 soc = [soc linspace(.77,.57,10)]; % sudden battery drop
 soc = [soc linspace(.56,.47,762)];
 
@@ -370,7 +370,7 @@ while true
             qq0 = q0; % state
             
             for j=k-1:k+N-2 % MPC
-            
+                                
                 for jj=j+delta_T:delta_T:j+1
                     qq1 = Ad*qq0+B*u(eeu,eest_u_old);
                     yy1 = C*qq1;
@@ -378,38 +378,21 @@ while true
                     qq0 = qq1;
                 end
                 
-                if yy1>b0*qc*int_v % reduction of control needed
-                        
-                    while yy1+C*B*u(est_u(c1,max_c2),eeu) > b0*qc*int_v
-                                
-                        % speeding up a bit (we can do this because 
-                        % how the control works
-                        if max_c2 <= min_c2
-                            break;
-                        else
-                            max_c2 = max_c2-deltas(2);
-                        end
-                    end
-
-                else
-                    while yy1+C*B*u(est_u(c1,max_c2),eeu) <= b0*qc*int_v
-                                
-                        if max_c2 >= mmax_c2
-                            break;
-                        else
-                            max_c2 = max_c2+deltas(2);
-                        end
-                    end
-                    bat_success = bat_success+1;
+                ccost = [];
+                
+                for ctl=min_c2:deltas(2):mmax_c2
+                    ccost = [ccost;yy1+C*B*u(est_u(c1,ctl),eeu)];
                 end
                 
-                if j == k+N-2
[…]

### 2021-02-14 icra-2021.tex
updated the path figure
fixing the results figures

@@
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
+        {\footnotesize\input{\figpath/results/new_physics/trajs.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (-3,-4) {\footnotesize {(a) path simulation, {\color{red}+} is the UAV location after 200 seconds}};
@@
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3_detail_3.tikz}};
+        {\footnotesize\input{\figpath/results/new_physics/model.tikz}};
     \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(\textlabel{a}{fig:evol-static-plan:a}) slice of the simulated energy along the estimated model}};

### 2021-02-14 scripts/SIM6.m

@@ -460,6 +460,28 @@ csvwrite(strcat('perioddata_simulation',strp5,'.csv'),log_period);
 csvwrite(strcat('data_simulation',strp5,'.csv'),[strp.' r ...
     strp3 strp4]);
 
+return;
+
+csvwrite(strcat('evol_simulation',strp5,'.csv'),[...
+    linspace(0,200,length(log_yy)).' log_yy]);
+    
+
+
+%% pure evolution
+
+% this part takes the coefficients at 200 s estimated with KF above and
+% evolve them to see if the model match the data
+
+qq0 = log_q(:,200/delta_T);
+log_yy = [log_y(200/delta_T)];
+Ad = A*delta_T/10+eye(2*r+1);
+for ii=200+delta_T:delta_T/10:400
+    qq0 = Ad*qq0;
+    log_yy = [log_yy; C*qq0];
+end
+
+figure;
+plot(log_yy)
 
 
 %% functions

### 2021-02-14 icra-2021.tex
results figures ready

--- 2021-02-10 icra-2021.tex
@@
 
-\begin{figure*}
-  \hspace*{-2ex}
-  \begin{tikzpicture}
-    \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3,-4) {\footnotesize {(a) path simulation, {\color{red}+} is the UAV location after 200 seconds}};
-    \node[inner sep=0pt] () at (8.3,-.02)
-        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (5.6,-4) {\footnotesize {(b) energy evolution simulation for 200 seconds interval}};
-  \end{tikzpicture}
-  \caption[Path and energy simulation of a static plan]{Path and energy simulations with different atmospheric conditions.
-Simulations are performed from collected data by variations of wind speed and direction.
-The path and computations are static}
-  \label{fig:sim-static-plan}
-\end{figure*}
-\begin{figure*}
-  \hspace*{-3.4ex}
-  \begin{tikzpicture}
-    \node[inner sep=0pt] () at (0,0)
-        {\footnotesize\input{\figpath/results/ener_sim3_detail_3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(\textlabel{a}{fig:evol-static-plan:a}) slice of the simulated energy along the estimated model}};
-    \node[inner sep=0pt] () at (6,0)
-        {\footnotesize\input{\figpath/results/evol_sim3_3.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(\textlabel{b}{fig:evol-static-plan:b}) model evolution at different $k$s}};
-    \node[inner sep=0pt] () at (10.8,.05)
-        {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
-    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.3,-4) {\footnotesize {(\textlabel{c}{fig:evol-static-plan:c}) path I coefficients evolution}};
-  \end{tikzpicture}
-  \caption[] {Evolution of the simulated energy data from Figure~\ref{fig:sim-static-plan}, using the estimation first in~\ref{fig:evol-static-plan:a}, the data with no estimation predicting the future in~\ref{fig:evol-static-plan:b}, and evolution of the estimated coefficients in~\ref{fig:evol-static-plan:c}}
-  \label{fig:evol-static-planned}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 *
+
+\begin{figure}[h!]
+  \footnotesize
+  \input{\figpath/results/new_physics/trajs.tikz}
+  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
+In I, II the path is static.
+It is dynamically adapted with the algorithm in I.d, with the path parameter radius of the circle $c_1$ and computation parameter frames-per-second rate $c_2$}
+  \label{fig:trajs}
+\end{figure}
+\begin{figure}[h!]
+  \footnotesize
+  \input{\figpath/results/new_physics/model.tikz}
+  \caption[Energy estimation and evolution of the state]{Energy estimation process for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
+  \label{fig:model}
+\end{figure}
+\begin{figure}[h!]
+  \footnotesize
+  \input{\figpath/results/new_physics/ener.tikz}
+  \caption[] {The model after 200 seconds of estimation on top along the energy and the algorithm that dynamically adapts path when the UAV cannot reach the end of the plan, and adapts the computation when the battery is discharged (smaller plot on right)}
+  \label{fig:ener}
+\end{figure}
 

### 2021-02-14 iros-2021.tex
cleaning
late night fixes

--- 2021-02-14 icra-2021.tex
@@
     DOI={10.1109/IRC.2020.00028},
-    url={https://adamseew.bitbucket.io/short/mechanical2020}
+    url={https://adamseewald.cc/short/mechanical2020}
   }
@@
     DOI={10.1007/s10766-019-00645-y},
-    url={https://adamseew.bitbucket.io/short/coarse2019}
+    url={https://adamseewald.cc/short/coarse2019}
   }
@@
     DOI={10.1145/3359061.3362775},
-    url={https://adamseew.bitbucket.io/short/component2019}
+    url={https://adamseewald.cc/short/component2019}
   }
@@
     DOI={10.1109/IRC.2020.00054},
-    url={https://adamseew.bitbucket.io/short/energy2020}
+    url={https://adamseewald.cc/short/energy2020}
   }
@@
     DOI={10.3929/ethz-b-000450120},
-    url={https://adamseew.bitbucket.io/short/beyond2020}
+    url={https://adamseewald.cc/short/beyond2020}
   }
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \footnotesize
@@
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[ht]
   \footnotesize
   \input{\figpath/results/new_physics/model.tikz}
-  \caption[Energy estimation and evolution of the state]{Energy estimation process for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
+  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
   \label{fig:model}
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[ht]
   \footnotesize
   \input{\figpath/results/new_physics/ener.tikz}
-  \caption[] {The model after 200 seconds of estimation on top along the energy and the algorithm that dynamically adapts path when the UAV cannot reach the end of the plan, and adapts the computation when the battery is discharged (smaller plot on right)}
+  \caption[] {The models after 200 seconds on top.
+The algorithm that uses the model I to dynamically adapt the path (when the final time and battery time doesn't match) and the computation (when the battery is discharged--the smaller plot on right) on bottom}
   \label{fig:ener}

### 2021-02-15 iros-2021.tex
added text to the results section

@@
   }
-
   @inproceedings{seewald2020beyond,
@@
 The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
-It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
+It eventually enterss the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
 
@@
 
-The computations are implemented by software components, e.g., ROS nodes in a ROS based system.
+The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS based system~\cite{quigley2009ros}.
 The user implements these nodes such that they change the computational load with node-specific ROS parameters, the computations parameters.
@@
 Let us hence consider the state of charge (SoC) $b$ of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation*}
+\begin{equation}\label{eq:bat}
   b_k=b_{k-1}-k_b\left(V-
@@
   \right)/(2R_rQ_c),
-\end{equation*}
+\end{equation}
 where $k_b$ is the battery coefficient determined experimentally,  $V\in\mathbb{R}$ is the internal battery 
@@
 
-\begin{defn}[Output, control constrain sets]
+\begin{defn}[Output, control constrain sets]\label{def:const}
 The output constrain set is then the set
@@
         \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
-        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B(\mathrm{diag}(\nu_i)(\mathbf{u}_k-\mathbf{u}_{k-1})-\tau_i)$\label{alg:evolution}
+        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B\mathbf{u}$\label{alg:evolution}
         \STATE $\mathbf{q}_{k}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k}$ and sensor data\label{alg:kalman_end}
@@
 
-*
-
-\begin{figure}[ht]
+\begin{figure}[h]
+  \centering
   \footnotesize
@@
 In I, II the path is static.
-It is dynamically adapted with the algorithm in I.d, with the path parameter radius of the circle $c_1$ and computation parameter frames-per-second rate $c_2$}
+It is dynamically replanned with the algorithm in I.d.
+The algorithm adapts path parameter radius of the circle $c_1$ and computation parameter fps rate $c_2$}
   \label{fig:trajs}
 \end{figure}
+
+The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (subfigures of Figure~\ref{fig:il-abs}).
+We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario.
+The UAV was flying in standard atmospheric conditions in a pattern similar to the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
+We later extended the UAV to carry a companion computer, Nvidia Jetson Nano, running ROS middleware.
+The companion implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network (FCN)~\cite{ullah2018pednet}, and the other communicates with a ground station.
+
 \begin{figure}[ht]
+  \centering
   \footnotesize
@@
 \end{figure}
-\begin{figure}[ht]
+\begin{figure}[h]
+  \centering
   \footnotesize
   \input{\figpath/results/new_physics/ener.tikz}
-  \caption[] {The models after 200 seconds on top.
-The algorithm that uses the model I to dynamically adapt the path (when the final time and battery time doesn't match) and the computation (when the battery is discharged--the smaller plot on right) on bottom}
+  \caption[Energy models of different static and dynamic plans] {The energy models of the paths I, II in Figure~\ref{fig:trajs} after 200 seconds on top.
+Of the dynamic plan I.d which replans the path (when the final time and battery time do not match) and the computation (when the battery is discharged--the smaller plot on right) on bottom}
   \label{fig:ener}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future Work}
-\label{sec:conclusion}
-
-*
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\balance
-\bibliographystyle{IEEEtran}
-\bibliography{\jobname}
-
+We implemented a realistic simulator to simulate the empirical data of a given flying plan and atmospheric conditions.
+We show the effects of different conditions in Figure~\ref{fig:trajs}.
+Both paths I and II are flying the same plan.
+The path I is flying with a constant wind speed of 5 meters per second and wind direction of 90 degrees (north).
+Path II is flying under the same conditions but a wind direction of 0 degrees (east).
+The energy evolutions of the paths are the top two subfigures of Figure~\ref{fig:ener}.
+
+We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
+Left figures illustrate an initial slice of the estimation of the data and period $T$ (Proposition~\ref{prop:rank}).
+We used order $r$ equal to 3.
+We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate to model the evolution of the data.
+On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a stable estimation.
+We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ neglecting the others.
+It hence approximates the non-periodicity with a linear model.
+
+\subsection{Implementation of the Planning Strategy}
+
+The practical implementation is based on observations of different variations of path and computations.
+
+A variation of path alters the overall flying time.
+We hence use the factors $\nu_1,\tau_1$ in Equation~(\ref{eq:scale-traj}) to map the coefficient to the remaining time.
+We compare this time with the time needed to completely deplete the battery from Equation~(\ref{eq:bat}) and reduce the parameter $c_1$ whenever the latest is lower.
+The parameter $c_1$ is equal for all the stages: it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and shifts the other paths accordingly.
+It results in shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively (subfigure I.d of Figure~\ref{fig:trajs} with the variation of the parameter in time on the right--a reduction in $c_1$ has reduced the flying time).
+
+A variation of computations affects directly the power and we thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
+We observed a low effect on the power of the communication ROS node.
+Nevertheless, the detection node varies between 5 and 10 watts for the lowest and highest fps.
+We implemented fps rate parameter $c_2$ and used factors  $\nu_2,\tau_2$ to map $c_2$ to the data from \powprof{} (subfigure I.d of Figure~\ref{fig:trajs}--the fps is replanned to meet the constraints).
+
+We have tested the validity of Theorem~\ref{thm:state-vs-energy} showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}.
+We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half.
+The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters.
+We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion and Future Work}  %
+\label{sec:conclusion}                %
+                                      %
+In this paper, we presented a planning algorithm for autonomous UAVs with a limited power source.
+The algorithm plans the path with computations dynamically and all together.
+We collected some empirical data of a fixed-wing UAV flying an agricultural scenario and build a simulator to show-case the algorithm in different conditions.
+The algorithm estimates the energy with KF and optimizes the path and computations using MPC.
+It evolves the state to verify the satisfaction of battery and time constraints.
+It uses a plan where at each stage the UAV flies a path and does some computations.
+It guides the UAV using a vector field.
+Finally, it exploits our earlier computational energy model varying the level of computations in the function of the current battery level.
+
+We are currently extending the results of this paper with an existing flying controller.
+We are further investigating the validity of the energy model on some other energy-critical mobile robots.
+For instance, we briefly investigated some possible implications on planetary rovers in~\cite{seewald2020beyond}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{IEEEtran}  %
+\bibliography{\jobname}       %
+                              %
 \leavevmode\thispagestyle{empty}\newpage
-\nobalance
 

### 2021-02-15 iros-2021.tex
added abstract

@@
 \begin{abstract}
-
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract\\
-  abstract
+  The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously.
+The planning strategy is based on a differential periodic energy model which is empirically motivated and formally proved.
+The model is enriched with the time and energy contribution of the path and computations.
+The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the battery state due to e.g., adverse atmospheric conditions.
 \end{abstract}
@@
 
-\vspace*{-2ex}
 Planning algorithms literature for mobile robots includes topics such as trajectory generation and path planning.
@@
 Figure~\ref{fig:il-abs} shows such plan.
-We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations in presence of a standard battery (see Section~\ref{sec:experimental}).
+%We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations in presence of a standard battery (see Section~\ref{sec:experimental}).
 

### 2021-02-15 iros-2021.tex
some fixes to the text

@@
 
-Unlike most of the past planning algorithms literature, our algorithm plans the path and computations all together.
+Unlike most of the past planning algorithms literature, our algorithm plans the path and computations simultaneously.
 To model the path we use multiple mathematical functions.
@@
 
-To achieve the energy-aware dynamic planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty.
+To achieve the energy-aware dynamic planning, we further introduce and formally prove a differential periodic energy model that accounts for the uncertainty.
 We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
@@
 Path-wise, the UAV flies in circles and lines covering a polygon.
-Computation-wise, it detects obstacles using a convolutional neural network (CNN) and notifies grounded mobile robots employed for harvesting.
+Computation-wise, it detects obstacles using a neural network and notifies grounded mobile robots employed for, e.g., harvesting.
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
@@
 We discuss the concrete meaning of the value of path parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
-
-\begin{figure}[h]
-  \centering
-  \input{\figpath/traj1.tikz}
-  \caption{Plan definition notation shown on an initial slice of the plan of Figure~\ref{fig:il-abs} in 2D.}
-  \label{fig:traj1}
-\end{figure}
 
@@
 
-  The \emph{plan} is a finite state machine (FSM) $\Gamma$ where the state-transition function $\delta:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
-  \begin{equation*}\delta(\Gamma_i,\mathbf{p}_k):=\begin{cases}
+  \begin{figure}[t]
+    \centering
+    \input{\figpath/traj1.tikz}
+    \caption{Plan definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
+    \label{fig:traj1}
+  \end{figure}
+
+  The \emph{plan} is a finite state machine (FSM) $\Gamma$ where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+  \begin{equation*}s(\Gamma_i,\mathbf{p}_k):=\begin{cases}
     \Gamma_{i+1} & \text{if }\mathbf{p}_k=\mathbf{p}_{\Gamma_i}\\
@@
   Consider an initial plan $\Gamma$ from Definition~\ref{def:mission} that satisfies Assumption~\ref{assm:periodic}.
-We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and in the guidance to the path resulting from such plan for the UAV planning problem.
+We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and in the guidance to the path resulting from such plan.
 \end{pb}
@@
 Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and the power (for the remaining $\sigma$).
-$\hat{\mathbf{u}}_k$ is then the difference in the instantaneous power contribution.
+$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and power (for the remaining $\sigma$).
+$B\mathbf{u}$ is then the difference in the instantaneous power contribution.
 %Indeed an alteration of the path affects the overall flying time (and consequently the energy). An alteration the the computations affects the instantaneous energy consumption.
 
-We elucidate how we derive these factors in the next two subsections.
+We elucidate how we derive the factors in the next two subsections.
 
@@
 They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by e.g., changing the flying time in the example in Figure~\ref{fig:il-abs}.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that $\varphi_i$ has the highest energy consumption, while still respecting the energy budget.
+In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
 In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan.
@@
 The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS based system~\cite{quigley2009ros}.
-The user implements these nodes such that they change the computational load with node-specific ROS parameters, the computations parameters.
+The user implements these nodes such that they change the computational load with node-specific ROS parameters--computations parameters.
 In a generic software component system, the user maps the computational load to the arguments.
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is a CNN object detector, the computation parameter $c_{i,\rho+1}$ might correspond to frames-per-second (fps) rate.
+For instance, if the computation is an object detector, the computation parameter $c_{i,\rho+1}$ might correspond to frames-per-second (fps) rate.
 The tool then changes the detection frequency.
@@
 \begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (the plan is valid on a period, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
+  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{prop:rank} hold (the plan is valid on a period, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
 Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
@@
 The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available. 
-For practical means indeed, we consider some realistic constraints to the energy of a flying UAV. We illustrate such constraints in the following subsection.
+For practical means indeed, we consider some realistic constraints to the energy of a flying UAV in the following subsection.
 
@@
 The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
-A priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
+A priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter (KF)~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
 At line~\ref{alg:mpc}, the algorithm uses MPC to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function (higher the horizon, higher the complexity and the robustness of the control to the output constraints)
@@
 
-We note from Lemma~\ref{lem:eqv} that the expression in Equation~(\ref{eq:cost}) denotes the square of the predicted power.
-
-We further note that at every step of the sum on line~\ref{alg:mpc}, the algorithm has to evolve the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
+We note that at every step of the sum on line~\ref{alg:mpc}, the algorithm evolves the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
 In particular, it performs a subroutine
@@
 \end{algorithmic} 
-where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computational parameters are reduced by the steps if they don't meet the constraints).
+where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computations parameters are reduced by the steps if they don't meet the constraints).
 
@@
 It is dynamically replanned with the algorithm in I.d.
-The algorithm adapts path parameter radius of the circle $c_1$ and computation parameter fps rate $c_2$}
+The algorithm adapts path parameter radius of the circle $c_1$ and computation parameter fps rate $c_2$.}
   \label{fig:trajs}
@@
 The UAV was flying in standard atmospheric conditions in a pattern similar to the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
-We later extended the UAV to carry a companion computer, Nvidia Jetson Nano, running ROS middleware.
-The companion implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network (FCN)~\cite{ullah2018pednet}, and the other communicates with a ground station.
+We later extended the UAV to carry a companion computer, Nvidia Jetson Nano~\cite{nano}, running ROS.
+The companion implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
 
@@
   \input{\figpath/results/new_physics/model.tikz}
-  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right}
+  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
   \label{fig:model}
@@
   \input{\figpath/results/new_physics/ener.tikz}
-  \caption[Energy models of different static and dynamic plans] {The energy models of the paths I, II in Figure~\ref{fig:trajs} after 200 seconds on top.
-Of the dynamic plan I.d which replans the path (when the final time and battery time do not match) and the computation (when the battery is discharged--the smaller plot on right) on bottom}
+  \caption[Energy models of different static and dynamic plans] {The energy models of the paths I, II in Figure~\ref{fig:trajs} after 200 seconds on top against the simulated data.
+Of the dynamic plan I.d which replans the path (when the final time and battery time do not match) and the computation (when the battery is discharged--the smaller plot on right) on bottom.}
   \label{fig:ener}
@@
 We used order $r$ equal to 3.
-We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate to model the evolution of the data.
-On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a stable estimation.
-We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ neglecting the others.
+We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate.
+On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate.
+We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
 It hence approximates the non-periodicity with a linear model.
@@
 We compare this time with the time needed to completely deplete the battery from Equation~(\ref{eq:bat}) and reduce the parameter $c_1$ whenever the latest is lower.
-The parameter $c_1$ is equal for all the stages: it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and shifts the other paths accordingly.
+We implemented the path parameter $c_1$ equal for all the stages: it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and shifts the other paths accordingly.
 It results in shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively (subfigure I.d of Figure~\ref{fig:trajs} with the variation of the parameter in time on the right--a reduction in $c_1$ has reduced the flying time).
+The path constraint set is set to $\underline{c}_1=$ -1000 and $\overline{c}_1=$ 0.
 
@@
 We implemented fps rate parameter $c_2$ and used factors  $\nu_2,\tau_2$ to map $c_2$ to the data from \powprof{} (subfigure I.d of Figure~\ref{fig:trajs}--the fps is replanned to meet the constraints).
+The computation constraint set is set to $\underline{c}_2=$ 2 and $\overline{c}_2=$ 10.
 
@@
 In this paper, we presented a planning algorithm for autonomous UAVs with a limited power source.
-The algorithm plans the path with computations dynamically and all together.
+The algorithm plans the path with computations dynamically and simultaneously.
 We collected some empirical data of a fixed-wing UAV flying an agricultural scenario and build a simulator to show-case the algorithm in different conditions.
@@
 It guides the UAV using a vector field.
-Finally, it exploits our earlier computational energy model varying the level of computations in the function of the current battery level.
+Finally, it exploits the computational energy model varying the level of computations in the function of the current battery level.
 
@@
 We are further investigating the validity of the energy model on some other energy-critical mobile robots.
-For instance, we briefly investigated some possible implications on planetary rovers in~\cite{seewald2020beyond}.
+For instance, we briefly investigated some possible implications on planetary exploration rovers in~\cite{seewald2020beyond}.
 

### 2021-02-16 iros-2021.tex
fixed font size in two figures
minor style changes

@@
   The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously.
-The planning strategy is based on a differential periodic energy model which is empirically motivated and formally proved.
-The model is enriched with the time and energy contribution of the path and computations.
-The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the battery state due to e.g., adverse atmospheric conditions.
+The planning strategy is based on a periodic energy model that is empirically motivated and formally proved.
+The model is enhanced with the time and energy contribution of the path and computations.
+The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the power source due to, e.g., adverse atmospheric conditions.
 \end{abstract}
@@
 
-To achieve the energy-aware dynamic planning, we further introduce and formally prove a differential periodic energy model that accounts for the uncertainty.
+To achieve the energy-aware dynamic planning, we further introduce and formally prove a periodic energy model that accounts for the uncertainty.
 We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
@@
     \centering
+    \footnotesize
     \input{\figpath/traj1.tikz}
@@
   \centering
+  \footnotesize
   \input{\figpath/traj2.tikz}
@@
 We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
-Left figures illustrate an initial slice of the estimation of the data and period $T$ (Proposition~\ref{prop:rank}).
+Left figures illustrate an initial slice of the model and period estimation (Proposition~\ref{prop:rank}).
 We used order $r$ equal to 3.
@@
 The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters.
-We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively.
+We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively, and a horizon $N$ equal to period $T$.
 
@@
 
-We are currently extending the results of this paper with an existing flying controller.
+We are currently extending the results of this paper with an existing flight controller.
 We are further investigating the validity of the energy model on some other energy-critical mobile robots.

### 2021-02-16 iros-2021.tex
implemented the internal review 1 (figures pending)

@@
 The model is enhanced with the time and energy contribution of the path and computations.
-The algorithm replans both in the function of the battery state accounting for uncertainty and rescuing the UAV from a possible failure in case of unexpected changes of the power source due to, e.g., adverse atmospheric conditions.
+The algorithm replans both in function of the battery state accounting for uncertainty.
+The dynamic planning allows to exploit all the available resources, yet avoid possible in-flight failure in case of unexpected battery drops due to, e.g., adverse atmospheric conditions.
 \end{abstract}
@@
   \end{tikzpicture}
-  \caption{An initial plan of an agricultural scenario replanned dynamically in terms of the path and computations all together.
+  \caption{Dynamic replanning of an agricultural scenario in terms of the path and computations simultaneously.
 An initial plan~(in~\ref{sth:i}) is adapted computation-wise~(in~\ref{sth:ii}) and path-wise~(in~\ref{sth:iii}).
-In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario, along its power spectrum.}
+In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario is shown along its power spectrum.}
   \label{fig:il-abs}
@@
 $\underline{c}_{i,j},\overline{c}_{i,j}$ are the lower and upper bounds of the parameter $c_{i,j}$.
-The set $\langle c_{i,1},c_{i,2},...,c_{i,n}\rangle$ is an ordered list $\langle c_i \rangle$ of $n$ parameters.
-
-Let us assume that the path at stage $i$ can be altered with $\rho$ path parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computations parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
+
+Let us assume that the path at stage $i$ can be altered with $\rho$ path parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computation parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
 We then express the path as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the path parameters.
 The function returns a metric of the distance between the point and the nominal trajectory.
-We express the computations as the value of the computations parameters.
-We discuss the concrete meaning of the value of path parameters in Subsection~\ref{sec:model}, and computations parameters in Subsection~\ref{sec:computations-model}.
+We express the computations as the value of the computation parameters.
+We discuss the concrete meaning of the value of path parameters in Subsection~\ref{sec:model}, and computation parameters in Subsection~\ref{sec:computations-model}.
 
@@
   \begin{equation*}\begin{split}
-    \Gamma_i:=\{\langle&\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho}),c_{i,\rho+1},\dots,c_{i,\rho+\sigma}\rangle\\\mid
-    &\,\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathcal{C}_i,\,\\
+    \Gamma_i:=\{\varphi_i(\mathbf{p}_k,c_i^\rho),c_i^\sigma\mid
+    \,&\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_i^\rho)\in\mathcal{C}_i,\,\\
       &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathcal{S}_{i,j}\,\},
@@
 
-In order to formulate the problem, we considerate the next assumption.
-
-\begin{assm}[Plan periodicity]\label{assm:periodic}
-  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$, the current levels of the path parameters $c_1^\rho$, and a shift $\mathbf{d}:=(x_d,y_d)$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
-  \begin{equation*}\begin{split}
-    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)\approx\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho),\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
-  \end{split}\end{equation*}
-\end{assm}
-
-Physically, this means that the plan is approximately periodic.
-The justification for this assumptions originates from empirical data (we refer the reader back to Figure~\ref{fig:il-abs}).
-It indeed lays in the autonomous nature of the UAVs scenario we are interested into planning, with the UAV being expected to iterate over paths and computations attending some events (such as detections).
-We will see this assumption being eased in practice for non-periodic plans in Section~\ref{sec:experimental}.
+In order to simplify the problem formulation, we consider some primitive paths. All the other paths are build from these paths with a shift $\mathbf{d}:=(x_d,y_d)$.
+
+Given $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) primitive paths $\varphi_1,\dots\varphi_n$, a generic starting point $\mathbf{p}$ and the current levels of the path parameters $c_1^\rho$, all the other paths $\varphi_{n+1},\dots,\varphi_l$ are build
+\begin{equation}\label{eq:primitive}\begin{split}
+  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
+\end{split}\end{equation}
+$\forall i\in[l/n-1]^+,j\in[n]^+$, where $e_j\in\mathbb{R}$ is the $j$-th constant difference.
 
 \begin{defn}[Period]\label{def:period}
-  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Assumption~\ref{assm:periodic}.
+  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Equation~(\ref{eq:primitive}).
 \end{defn}
 
-From Assumption~\ref{assm:periodic} follows the next proposition.
-
-\begin{prop}[Necessary and sufficient condition for periodicity]\label{prop:rank}
-  The plan $\Gamma$ is periodic if
-  \begin{equation*}\begin{split}
-    &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
-  \end{split}\end{equation*}
-  Moreover, if the plan $\Gamma$ is periodic, then
-  \begin{equation*}
-    \mathrm{rank}\begin{bmatrix}
-        \varphi_1 & \varphi_{n+1} & \cdots & \varphi_{(l-n)+1} \\ 
-        %\varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
-        \vdots & \vdots & \ddots & \vdots \\
-        \varphi_n & \varphi_{2n} & \cdots & \varphi_l   
-      \end{bmatrix}=2,
-  \end{equation*}
-  where the paths in the first column are evaluated on $\mathbf{p},c_1^\rho$, in the second on $\mathbf{p}+\mathbf{d},c_1^\rho$, and in the last on $\mathbf{p}+(l/n-1)\mathbf{d},c_1^\rho$.
-\end{prop}
-\begin{proof}($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+e_j$ and $e_j$ is the $j$-th constant difference.
-It is the same for paths selected at each period.
-This is equivalent to Assumption~\ref{assm:periodic}.
-
-($\Longleftarrow$) The column rank of the matrix in the proposition is the dimension of its column space.
-It denotes the size of the set of all the possible linear combination of the column vectors.
-We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (from $\Longrightarrow$).
-\end{proof}
-
-The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for periodicity.
-The algorithm finds $n$ initializing it to one and finding the value which satisfies the proposition.
-It then measures the time between the stages and assumes the initial period is one.
-The periods might be different for different $j$s due to atmospheric interferences.
+The algorithm measures the time between the paths and assumes the initial period is one. The periods might be different for different $j$s due to atmospheric interferences.
+
+One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Equation~(\ref{eq:primitive}).
+If there is no such value, (e.g., when the plan is composed of only one path), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Figure~\ref{fig:il-abs}).
 
 \begin{pb}[UAV planning problem]\label{pb}
-  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission} that satisfies Assumption~\ref{assm:periodic}.
-We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and in the guidance to the path resulting from such plan.
+  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}.
+We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
 \end{pb}
@@
 
-We proof a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
+We prove a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
 We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
 
-Once we illustrate the energy model, we enhance it with the energy contribution of the path in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
+After having illustrated the energy model, we enhance it with the energy contribution of the path in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
 
@@
 
-Let us consider for practical reasons the discretized version of the system in Equation~\ref{eq:state-perf}.
-
-Let us suppose that at time instant $k$ the plan reached the $i$-th stage $\Gamma_i$.
-
-The control along with the input matrix
+%Let us consider for practical reasons the discretized version of the system in Equation~\ref{eq:state-perf}.
+
+Let us suppose that at time instant $k$ the plan reached the $i$-th stage $\Gamma_i$ and the control
+\begin{equation}\label{eq:state-control2}
+  \mathbf{u}_k=\begin{bmatrix}c_k^\rho & c_k^\sigma\end{bmatrix}^T,
+\end{equation}
+where $\mathbf{u}_k\in\mathbb{R}^n$ with $n=\rho+\sigma$ differs from the nominal control $\mathbf{u}$ in Equation~(\ref{eq:state-perf}).
+We include the control in the nominal control exploiting the following observation.
+
+We observe that a change in path parameters affects the energy indirectly.
+It alters the time when the UAV reaches the final point $\mathbf{p}_{\Gamma_l}$.
+We use this information later in the algorithm to check that the battery discharge time is greater and replan the path parameters accordingly.
+A change in computation parameters affects the energy directly.
+It alters the instantaneous energy consumption as more computations require more power (and vice versa).
+We replan the computation parameters to maximize the instantaneous energy consumption against the maximum battery discharge rate.
+
+The nominal control and the input matrix
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T\hspace*{-1ex},\\
   \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),B=\begin{bmatrix} 0 &\hspace*{-.5ex} \cdots\hspace*{-.5ex} & 0 & 1 &\hspace*{-1ex} \cdots\hspace*{-1ex} & 1 \\ & & & & & \end{bmatrix}\\
-  \hat{\mathbf{u}}_k&:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i,\,\,\,
+  \hat{\mathbf{u}}_k&:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i.
 \end{split}\end{equation}
-where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$.
-Matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-$\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_{i,1} & \cdots & \tau_{i,\rho+\sigma}\end{bmatrix}^T$ are scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and power (for the remaining $\sigma$).
-$B\mathbf{u}$ is then the difference in the instantaneous power contribution.
+The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
+$\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and power (for the remaining $\sigma$).
+The nominal control $\mathbf{u}$ is then the difference of these contributions of two consecutive controls $\mathbf{u}_{k-1},\mathbf{u}_k$ applied to the system.
+$B\mathbf{u}$ merely includes the difference in power into the model in Equation~(\ref{eq:state-perf}).
+
 %Indeed an alteration of the path affects the overall flying time (and consequently the energy). An alteration the the computations affects the instantaneous energy consumption.
 
-We elucidate how we derive the factors in the next two subsections.
+We clarify how we derive the factors $\nu_i,\tau_i$ in the next two subsections.
 
@@
 
-\subsection{Computations parameters energy contribution}
+\subsection{Computation parameters energy contribution}
 \label{sec:computations-model}
 
-Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computations parameters which characterize the computations.
-We assess the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
+Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
+We estimate the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
 For this purpose, we assume the UAV carries an embedded board that runs the computations.
-The tool measures the instantaneous energy consumption of a subset of possible computations parameters within the computation constraint sets and builds an energy model: a linear interpolation, one per each computation.
-
-The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS based system~\cite{quigley2009ros}.
-The user implements these nodes such that they change the computational load with node-specific ROS parameters--computations parameters.
-In a generic software component system, the user maps the computational load to the arguments.
+Our tool measures the instantaneous energy consumption of a subset of possible computation parameters within the computation constraint sets and builds an energy model: a linear interpolation, one per each computation.
+
+The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS-based system~\cite{quigley2009ros}.
+The user implements these nodes such that they change the computational load according to node-specific ROS parameters--the computation parameters.
+In a generic software component system, the user maps the computational load to the arguments~\cite{seewald2019component}.
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
 For instance, if the computation is an object detector, the computation parameter $c_{i,\rho+1}$ might correspond to frames-per-second (fps) rate.
-The tool then changes the detection frequency.
+The tool then measures power according to the detection frequency.
 
@@
                      %
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on a valid path: to solve Problem~\ref{pb}.
-
-\begin{defn}[Validity]\label{def:valid}
-  Given a close strictly positive discrete interval $\mathcal{J}:=[j-n+1,j]$ (for $j\in\mathbb{Z}_{>0},j\leq l$ and $n$ given in Assumption~\ref{assm:periodic}), a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $\mathcal{J}$ if for every stage $\Gamma_{i-1},\,i\in\mathcal{J}$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.
-
-  The plan resulting from such control sequence is a \emph{valid plan} on $\mathcal{J}$. It generates the \emph{valid path}
-  \begin{equation*}\begin{split}\label{eq:mission-valid}
-   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,\forall i\in\mathcal{J},\,\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\}.
-  \end{split}\end{equation*}
-\end{defn}
-
-Let us consider the assumption that the plan is valid on at least one period.
-
-\begin{assm}[Period validity]\label{assm:valid}
-  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n]^+$ s.t. the subplan $\Gamma_{(i-1)n+1},\dots,\Gamma_{in}$ is valid.
-\end{assm}
-
-Let us proof that if the plan is periodic and valid on at least one period, then the plan is valid.
-
-\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
-  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{prop:rank} hold (the plan is valid on a period, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic).
-Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
-\end{thm}
-\begin{proof}
-  From Definition~\ref{def:valid}, Assumption~\ref{assm:valid}, we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the plan is valid, and from Proposition~\ref{prop:rank} we know that the plan is periodic.
-Hence if the set $\mathcal{J}$ delimits a valid plan, then also the set $i[j-n+1,j]\subseteq[l]^+$ does for a given $i$.
-From the assumption we note that $i\in[l/n]^+$ and, due to the proposition, $\mathcal{J}=[l]^+$.
-Finally, due to the periodicity, Lemma~\ref{lem:eqv} allows us to use the proposed approach to model the energy.
-\end{proof}
-
-The algorithm can assess the validity of the plan using Theorem~\ref{thm:state-vs-energy}, but still find that there is no control available. 
-For practical means indeed, we consider some realistic constraints to the energy of a flying UAV in the following subsection.
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such control--to solve Problem~\ref{pb}.
+
+A valid control sequence has to respect the energy constraints. We consider some realistic constraints to the energy of a flying UAV in the following subsection.
 
@@
 \end{algorithmic} 
-where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computations parameters are reduced by the steps if they don't meet the constraints).
+where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints).
 
@@
 
-\begin{figure}[h]
+The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see subfigures of Figure~\ref{fig:il-abs}).
+We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario.
+The UAV was flying in standard atmospheric conditions in a pattern similar to the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
+We later extended the UAV to carry a companion computer, Nvidia Jetson Nano~\cite{nano}, running ROS.
+The companion computer implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
+
+We implemented a realistic simulator to simulate the empirical data of a given plan and atmospheric conditions.
+We show the effects of different conditions in Figure~\ref{fig:trajs}.
+Both paths I and II are flying the same plan.
+Path I is flying with a constant wind speed of 5 meters per second and wind direction of 90 degrees (north).
+Path II is flying under the same conditions but a wind direction of 0 degrees (east).
+The energy evolutions of the paths are the top two subfigures of Figure~\ref{fig:ener}.
+
+We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
+Left figures illustrate an initial slice of the model and period estimation (Definition~\ref{def:period}).
+We used order $r$ equal to 3.
+We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate.
+On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate.
+We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
+It hence approximates the non-periodicity with a linear model.
+
+\begin{figure}[t]
   \centering
@@
 \end{figure}
-
-The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (subfigures of Figure~\ref{fig:il-abs}).
-We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario.
-The UAV was flying in standard atmospheric conditions in a pattern similar to the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
-We later extended the UAV to carry a companion computer, Nvidia Jetson Nano~\cite{nano}, running ROS.
-The companion implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
-
-\begin{figure}[ht]
+\begin{figure}[t]
   \centering
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[t]
   \centering
@@
 
-We implemented a realistic simulator to simulate the empirical data of a given flying plan and atmospheric conditions.
-We show the effects of different conditions in Figure~\ref{fig:trajs}.
-Both paths I and II are flying the same plan.
-The path I is flying with a constant wind speed of 5 meters per second and wind direction of 90 degrees (north).
-Path II is flying under the same conditions but a wind direction of 0 degrees (east).
-The energy evolutions of the paths are the top two subfigures of Figure~\ref{fig:ener}.
-
-We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
-Left figures illustrate an initial slice of the model and period estimation (Proposition~\ref{prop:rank}).
-We used order $r$ equal to 3.
-We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate.
-On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate.
-We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
-It hence approximates the non-periodicity with a linear model.
-
 \subsection{Implementation of the Planning Strategy}
@@
 The practical implementation is based on observations of different variations of path and computations.
-
 A variation of path alters the overall flying time.
@@
 
-We have tested the validity of Theorem~\ref{thm:state-vs-energy} showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}.
+We have tested the validity of the algorithm showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}.
 We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half.
 The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters.
-We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively, and a horizon $N$ equal to period $T$.
+We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively, and the horizon $N$ equal to the period $T$.
 
@@
 The algorithm plans the path with computations dynamically and simultaneously.
-We collected some empirical data of a fixed-wing UAV flying an agricultural scenario and build a simulator to show-case the algorithm in different conditions.
-The algorithm estimates the energy with KF and optimizes the path and computations using MPC.
+We collected empirical data of a fixed-wing UAV flying an agricultural scenario and build a simulator to test the algorithm in different conditions.
+The algorithm estimates the energy with a KF and optimizes the path and computations using MPC.
 It evolves the state to verify the satisfaction of battery and time constraints.
@@
 
-We are currently extending the results of this paper with an existing flight controller.
-We are further investigating the validity of the energy model on some other energy-critical mobile robots.
-For instance, we briefly investigated some possible implications on planetary exploration rovers in~\cite{seewald2020beyond}.
+We are currently extending the results of this paper to work with a standard flight controller.
+We are further investigating the validity of the energy model on other energy-critical mobile robots.
+Such as on planetary exploration rovers in~\cite{seewald2020beyond}.
 
@@
                               %
+\leavevmode\thispagestyle{empty}\newpage
 \leavevmode\thispagestyle{empty}\newpage

### 2021-02-17 iros-2021.tex
notation fixes

@@
   A&=\left[\begin{array}{cccc}
-    0&    &       &  \\
-     & A_1&       &  \\
-     &    & \ddots&  \\
+    0&                     &       & \makebox(-5,-5){*}  \\
+     & A_1                 &       &  \\
+     & \makebox(-25,-15){*}& \ddots&  \\
      &                     &       & A_r 
-  \end{array}\right],\,A_j\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},\\
+  \end{array}\right],\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},\\
   C&=(1/T)\left[\begin{array}{cccccc}
@@
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),B=\begin{bmatrix} 0 &\hspace*{-.5ex} \cdots\hspace*{-.5ex} & 0 & 1 &\hspace*{-1ex} \cdots\hspace*{-1ex} & 1 \\ & & & & & \end{bmatrix}\\
-  \hat{\mathbf{u}}_k&:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i.
+  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),\,\,\,\hat{\mathbf{u}}_k:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i\\
+  B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ 
+    & & & \makebox(-15,-3){*} & &\end{bmatrix}.
 \end{split}\end{equation}
 The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-$\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time (for the first $\rho$ parameters) and power (for the remaining $\sigma$).
+$\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time for the first $\rho$ parameters, and power for the remaining $\sigma$ (we use the same notation for the path and computation scaling factors as for the path and computation parameters).
 The nominal control $\mathbf{u}$ is then the difference of these contributions of two consecutive controls $\mathbf{u}_{k-1},\mathbf{u}_k$ applied to the system.
@@
 \begin{equation}\label{eq:area}
-  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathcal{C}_i\},
+  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1}^\rho)\in\mathcal{C}_i\},
 \end{equation}

### 2021-02-17 iros-2021.tex
added data for some new simulations

@@
 The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-$\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time for the first $\rho$ parameters, and power for the remaining $\sigma$ (we use the same notation for the path and computation scaling factors as for the path and computation parameters).
+$\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time for the first $\rho$ parameters, and power for the remaining $\sigma$ (we use the same notation for the path and computation scaling factors as for the parameters).
 The nominal control $\mathbf{u}$ is then the difference of these contributions of two consecutive controls $\mathbf{u}_{k-1},\mathbf{u}_k$ applied to the system.
@@
 Both paths I and II are flying the same plan.
-Path I is flying with a constant wind speed of 5 meters per second and wind direction of 90 degrees (north).
-Path II is flying under the same conditions but a wind direction of 0 degrees (east).
+Path I is flying with a constant wind speed of 5 meters per second and wind direction of 0 degrees.
+Path II is flying under the same conditions but a wind direction of 90 degrees.
 The energy evolutions of the paths are the top two subfigures of Figure~\ref{fig:ener}.

### 2021-02-17 scripts/SIM10.m

@@ -1,0 +1,683 @@
+
+% SIM10
+
+% simulation of the algorithm, path II, static
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','90','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 90; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001 .006  .1  .006  .1];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+
+strp2 = 3;
+r = strp2; % model size (the bigger the more precise)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = strp3(1); % positive gain constant to be also determined experimentally
+kvv = strp3(2);
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+% guidance
+kd = strp3(3);
+
+% physics init
+w =  ws*[cosd(wd);sind(wd)]; % wind vector (x, y axis velocity)
+
+h = 20; % initial altitude
+vv = 0; % initial vertical velocity
+p = [start_x;start_y]; % position
+theta = deg2rad(vd); % initial angle
+
[…]

### 2021-02-17 scripts/SIM11.m

@@ -1,0 +1,684 @@
+
+% SIM11
+
+% simulation of the algorithm, path I, static
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','0','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 0; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001 .006  .1  .006  .1];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+
+strp2 = 3;
+r = strp2; % model size (the bigger the more precise)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = strp3(1); % positive gain constant to be also determined experimentally
+kvv = strp3(2);
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+% guidance
+kd = strp3(3);
+
+% physics init
+w =  ws*[cosd(wd);sind(wd)]; % wind vector (x, y axis velocity)
+
+h = 20; % initial altitude
+vv = 0; % initial vertical velocity
+p = [start_x;start_y]; % position
+theta = deg2rad(vd); % initial angle
+
[…]

### 2021-02-17 scripts/SIM8.m

@@ -1,7 +1,7 @@
 
-% SIM7
+% SIM8
 
-% complete simulation of the algo with control (new physics, from Hector)
+% simulation of the algorithm, path I, dynamic
 
 
 
@@ -390,7 +390,7 @@ while true
                 end
                 
                 bat_t = N; % getting the time when the battery is gonna be
-                       % fully discharged (we already did up to N!)
+                           % fully discharged (we already did up to N!)
             else
                 bat_t = 0;
             end
@@ -435,7 +435,7 @@ while true
             eeu = est_u(c1,c2);
                 
             if bat_success ~= floor(N+1e-3)  % 1e^-3 because when it's
-                                                 % integer it would do -1
+                                             % integer it would do -1
                 bat_flag = 1; % battery low  
             end   
             

### 2021-02-17 scripts/SIM9.m

@@ -1,0 +1,683 @@
+
+% SIM9
+
+% simulation of the algorithm, path II, dynamic
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','90','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 90; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001 .006  .1  .006  .1];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+
+strp2 = 3;
+r = strp2; % model size (the bigger the more precise)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = strp3(1); % positive gain constant to be also determined experimentally
+kvv = strp3(2);
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+% guidance
+kd = strp3(3);
+
+% physics init
+w =  ws*[cosd(wd);sind(wd)]; % wind vector (x, y axis velocity)
+
+h = 20; % initial altitude
+vv = 0; % initial vertical velocity
[…]

### 2021-02-18 iros-2021.tex
updated figures with latest data
consistency check

@@
 These are fixed values that are not replanned by the algorithm.
-Our goal is to complete the plan with the highest possible parameters as the UAV flies and its batteries drain.
+Our goal is to complete the plan with the highest possible parameters configuration as the UAV flies and its batteries drain.
 
@@
 The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
-It eventually enterss the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
+It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
 
@@
 We prove a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
-We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.
+We show after the main results how this approach allows us variability in terms of non-periodic signals.
 
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency ($T$ is the period from Definition~\ref{def:period}), and $a,b\in\mathbb{R}$ the Fourier series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
 
@@
 where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros.
+In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros (*).
 
@@
 \begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),\,\,\,\hat{\mathbf{u}}_k:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i\\
+  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),\,\,\,\hat{\mathbf{u}}_k:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i,\\
   B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ 
@@
 \end{split}\end{equation}
-The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
+The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros (*) except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
 $\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time for the first $\rho$ parameters, and power for the remaining $\sigma$ (we use the same notation for the path and computation scaling factors as for the parameters).
@@
 \end{equation}
-delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}).
+delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Figure~\ref{fig:tee1}).
 $\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the path.
@@
 The path parameters allows to change the path.
-They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by e.g., changing the flying time in the example in Figure~\ref{fig:il-abs}.
+They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by changing the flying time in the example in Figure~\ref{fig:il-abs}.
 In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
@@
 In both cases, with ROS~\cite{zamanakos2020energy} or with generic software components system~\cite{seewald2019component}, the tool performs automatic modeling.
-For instance, if the computation is an object detector, the computation parameter $c_{i,\rho+1}$ might correspond to frames-per-second (fps) rate.
+For instance, if the computation is an object detector, a computation parameter $c_{1,2}$ might correspond to frames-per-second (fps) rate.
 The tool then measures power according to the detection frequency.
@@
                      %
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such control--to solve Problem~\ref{pb}.
+The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Problem~\ref{pb}.
 
@@
 
-We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$.
+We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}$.
 This is generally untrue.
@@
     \FOR{$i\in[l]^+$}\label{alg:stages-loop}
-      \WHILE{$\mathbf{p}_{k-1}\neq\mathbf{p}_{\Gamma_i}$}
+      \WHILE{$\mathbf{p}_{k-1}\neq\mathbf{p}_{\Gamma_i}$}\label{alg:while}
         \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
@@
 At line~\ref{alg:mpc}, the algorithm uses MPC to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function (higher the horizon, higher the complexity and the robustness of the control to the output constraints)
-\begin{equation}\label{eq:cost}\begin{split}
+\begin{equation*}\label{eq:cost}\begin{split}
   V_f(\mathbf{q}_k)&:=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,\\
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k+B\mathbf{u})^T\mathrm{diag}(C)(\mathbf{q}_k+B\mathbf{u}),\hspace*{-2ex}
-\end{split}\end{equation}
+  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k+B\mathbf{u})^T\mathrm{diag}(C)(\mathbf{q}_k+B\mathbf{u}),\hspace*{-2.5ex}
+\end{split}\end{equation*}
 where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}), and $B$, $\mathbf{u}$ are defined in Equation~(\ref{eq:state-control}).
@@
 \end{algorithmic} 
-where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps (the maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints).
+where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps.
+The maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints (or increased if with $\overline{c}_i+\delta$ the constraints are still respected).
 
@@
 
-The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see subfigures of Figure~\ref{fig:il-abs}).
+The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Figure~\ref{fig:il-abs}).
 We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario.
-The UAV was flying in standard atmospheric conditions in a pattern similar to the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
-We later extended the UAV to carry a companion computer, Nvidia Jetson Nano~\cite{nano}, running ROS.
-The companion computer implements two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
+The UAV was flying in standard atmospheric conditions like the path \hyperref[fig:trajs-I-static]{5.I} in Figure~\ref{fig:trajs}, or the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
+We later extended the UAV to carry a companion computer, NVIDIA Jetson Nano~\cite{nano}, running ROS.
+The companion computer has two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Neural Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
+
+\begin{figure}[t]
+  \centering
+  \footnotesize
+  \input{\figpath/results/new_physics2/trajs.tikz}
+  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
+In \hyperref[fig:trajs-I-static]{5.I} and \hyperref[fig:trajs-II-static]{5.II} the path is static.
+It is dynamically replanned with the algorithm in \hyperref[fig:trajs-dyn-i]{5.i} and \hyperref[fig:trajs-dyn-ii]{5.ii}.
+The algorithm adapts path parameter radius of the circle $c_{1,1}$ and computation parameter fps rate $c_{1,2}$.}
+  \label{fig:trajs}
+\end{figure}
+\begin{figure}[h]
+  \centering
+  \footnotesize
+  \input{\figpath/results/new_physics2/model.tikz}
+  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
+  \label{fig:model}
+\end{figure}
+\begin{figure}[h!]
+  \centering
+  \footnotesize
+  \input{\figpath/results/new_physics2/ener.tikz}
+  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{7.I} and \hyperref[fig:ener:static-II]{7.II}).
+Below are the energy evolutions from the algorithm (\hyperref[fig:ener-dyn-i]{7.i} and \hyperref[fig:ener-dyn-ii]{7.ii}).
+It replans the path when the final time and battery time do not match, and the computation when the battery is discharged.}
+  \label{fig:ener}
+\end{figure}
 
@@
 We show the effects of different conditions in Figure~\ref{fig:trajs}.
-Both paths I and II are flying the same plan.
-Path I is flying with a constant wind speed of 5 meters per second and wind direction of 0 degrees.
-Path II is flying under the same conditions but a wind direction of 90 degrees.
-The energy evolutions of the paths are the top two subfigures of Figure~\ref{fig:ener}.
+Both paths \hyperref[fig:trajs-I-static]{5.I} and \hyperref[fig:trajs-II-static]{5.II} are flying the same plan with different initial parameters values.
+Path \hyperref[fig:trajs-I-static]{5.I} is flying with a constant wind speed of 5 meters per second, wind direction of 0 degrees, and an initial path parameter $c_{1,1}$ value of 0.
+Path  \hyperref[fig:trajs-II-static]{5.II} is flying under the same conditions but a wind direction of 90 degrees and the initial path parameter value of -1000.
+The energy evolutions of these two paths are the top two subfigures \hyperref[fig:ener:static-I]{7.I} and \hyperref[fig:ener:static-II]{7.II} of Figure~\ref{fig:ener}.
+The simulated energy data are in black, the model evolution in red.
 
@@
 We used order $r$ equal to 3.
-We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum plot shows that 3 frequencies are adequate.
-On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 1 minute is sufficient to obtain a consistent state estimate.
-We performed some trials with non-periodic signals and observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
+We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
+On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 2 periods are sufficient to obtain a consistent state estimate.
+With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
 It hence approximates the non-periodicity with a linear model.
 
-\begin{figure}[t]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics/trajs.tikz}
-  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
-In I, II the path is static.
-It is dynamically replanned with the algorithm in I.d.
-The algorithm adapts path parameter radius of the circle $c_1$ and computation parameter fps rate $c_2$.}
-  \label{fig:trajs}
-\end{figure}
-\begin{figure}[t]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics/model.tikz}
-  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
-  \label{fig:model}
-\end{figure}
-\begin{figure}[t]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics/ener.tikz}
-  \caption[Energy models of different static and dynamic plans] {The energy models of the paths I, II in Figure~\ref{fig:trajs} after 200 seconds on top against the simulated data.
-Of the dynamic plan I.d which replans the path (when the final time and battery time do not match) and the computation (when the battery is discharged--the smaller plot on right) on bottom.}
-  \label{fig:ener}
-\end{figure}
-
 \subsection{Implementation of the Planning Strategy}
 
-The practical implementation is based on observations of different variations of path and computations.
-A variation of path alters the overall flying time.
-We hence use the factors $\nu_1,\tau_1$ in Equation~(\ref{eq:scale-traj}) to map the coefficient to the remaining time.
-We compare this time with the time needed to completely deplete the battery from Equation~(\ref{eq:bat}) and reduce the parameter $c_1$ whenever the latest is lower.
-We implemented the path parameter $c_1$ equal for all the stages: it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and shifts the other paths accordingly.
-It results in shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively (subfigure I.d of Figure~\ref{fig:trajs} with the variation of the parameter in time on the right--a reduction in $c_1$ has reduced the flying time).
-The path constraint set is set to $\underline{c}_1=$ -1000 and $\overline{c}_1=$ 0.
-
-A variation of computations affects directly the power and we thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
+The practical implementation is based on observations of different variations of paths and computations.
+A variation of path alters the overall flying time, which we reflect in the factors $\nu_{1,1},\tau_{1,1}$ from Equation~(\ref{eq:scale-traj}).
+We compare the remaining flight time with the time needed to completely deplete the battery from Equation~(\ref{eq:bat}).
+We reduce or increase the parameter to optimize the battery time.
+The path parameter $c_{1,1}$ is equal for all the stages and it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and therefore shifts the other paths accordingly.
+It results in a shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively.
+The path constraint set is set to $\underline{c}_{1,1}=$ -1000 and $\overline{c}_{1,1}=$ 0 equal for all the stages.
+
+A variation of computations affects directly the power.
+We thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
 We observed a low effect on the power of the communication ROS node.
 Nevertheless, the detection node varies between 5 and 10 watts for the lowest and highest fps.
-We implemented fps rate parameter $c_2$ and used factors  $\nu_2,\tau_2$ to map $c_2$ to the data from \powprof{} (subfigure I.d of Figure~\ref{fig:trajs}--the fps is replanned to meet the constraints).
-The computation constraint set is set to $\underline{c}_2=$ 2 and $\overline{c}_2=$ 10.
-
-We have tested the validity of the algorithm showing the dynamic adaptation in the subfigure I.d of Figure~\ref{fig:ener}.
+We implemented fps rate parameter $c_{1,2}$ with factors  $\nu_{1,2},\tau_{1,2}$ mapping $c_{1,2}$ to the data from \powprof{}.
+The computation constraint set is set to $\underline{c}_{1,2}=$ 2 and $\overline{c}_{1,2}=$ 10 equal for all the stages.
+
+We have tested the validity of the algorithm showing the dynamic adaptation in the subfigures \hyperref[fig:trajs-dyn-i]{5.i} and \hyperref[fig:trajs-dyn-ii]{5.ii} of Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{7.i} and \hyperref[fig:ener-dyn-ii]{7.ii} of Figure~\ref{fig:ener} energy-wise.
+For the first path (Subfigure \hyperref[fig:trajs-I-static]{5.I}) the plan starts at the highest configuration of parameters.
 We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half.
-The algorithm tries to maximize the parameter $c_2$ when the battery is discharging (plot on right) and reduces the path with parameter $c_1$ as the original plan cannot be completed with the current configuration of parameters.
-We used reductions $\delta$ of 500 and 2 for $c_1$ and $c_2$ respectively, and the horizon $N$ equal to the period $T$.
+The algorithm optimizes the path in the proximity of the drops to ensure that the flight is completed.
+Moreover, it maximizes the parameter $c_{1,2}$ when the battery is discharging (green line) respecting the output constraint (Definition~\ref{def:const}).
+We simulated the opposite scenario for the second path (Subfigure \hyperref[fig:trajs-II-static]{5.II}).
+The plan starts at the lowest configuration of parameters but the battery behaves linearly.
+We note that the path parameter is increased as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter is optimized for the battery discharge rate.
+For both cases, we used reductions $\delta$ of 500 and 2 for $c_{1,1}$ and $c_{1,2}$ respectively, and the horizon $N$ equal to the period $T$.
 
@@
 The algorithm plans the path with computations dynamically and simultaneously.
-We collected empirical data of a fixed-wing UAV flying an agricultural scenario and build a simulator to test the algorithm in different conditions.
+We collected empirical data of a fixed-wing UAV flying an agricultural scenario and built a simulator to test the algorithm in different conditions.
 The algorithm estimates the energy with a KF and optimizes the path and computations using MPC.
@@
 We are currently extending the results of this paper to work with a standard flight controller.
-We are further investigating the validity of the energy model on other energy-critical mobile robots.
+We are further investigating the validity of the algorithm on other energy-critical mobile robots.
 Such as on planetary exploration rovers in~\cite{seewald2020beyond}.
@@
                               %
-\leavevmode\thispagestyle{empty}\newpage
 \leavevmode\thispagestyle{empty}\newpage

### 2021-02-19 iros-2021.tex
minor fixes

@@
 \begin{defn}[Stage, plan, triggering, and final point]\label{def:mission}
-  The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined as the ordered list
+  The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined
   \begin{equation*}\begin{split}
@@
 \label{sec:experimental}  %
+
+In this section, we discuss our experimental setup, the implementation strategy, and some results.
+
+\subsection{Experimental setup}
 
@@
 
+\subsection{Algorithm evaluation}
+
+\subsubsection*{Periodic energy model}
+
 We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
@@
 
-\subsection{Implementation of the Planning Strategy}
+\subsubsection*{Implementation of the planning strategy}
 
@@
 The computation constraint set is set to $\underline{c}_{1,2}=$ 2 and $\overline{c}_{1,2}=$ 10 equal for all the stages.
+
+\subsubsection*{Dynamic adaptation of the path and computation parameters}
 

### 2021-02-20 iros-2021.tex
implemented Hector's suggestion about FSM

@@
   \center
-  \begin{tikzpicture}[shorten >=1pt,node distance=12ex,on grid,auto] 
-    \node        (q_dots0) {$\cdots$};
+  \begin{tikzpicture}[shorten >=.5pt,node distance=10.5ex,on grid,auto]
+    \footnotesize
+    \node[state,initial] (q_i) {$\Gamma_1$}; 
+    \node        [right=of q_i] (q_dots0) {$\cdots$};
     \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
-    \node[state] (q_1) [right=of q_0] {$\Gamma_{i+1}$};
-    \node        (q_dots1) [right=of q_1] {$\cdots$};   
+    \node        (q_dots1) [right=of q_0] {$\cdots$};
+    \node[state,accepting] (q_f) [right=of q_dots1] {$\Gamma_f$};
     \path[->]
+    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_dots0)
     (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
-    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_1)    
-    (q_0) edge [loop above] node {$\mathbf{p}_{k_1}$} (q_0)
-    (q_1) edge node {$\mathbf{p}_{\Gamma_{i+1}}$} (q_dots1)
-    (q_1) edge [loop above] node {$\mathbf{p}_{k_2}$} (q_1)
+    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_dots1)
+    (q_dots1) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
+    (q_i) edge [loop above] node {$\mathbf{p}_{k_1}$} (q_i)
+    (q_0) edge [loop above] node {$\mathbf{p}_{k_2}$} (q_0)
+    (q_f) edge [loop above] node {$\mathbf{p}_{k_3}$} (q_f)
     ; %end path 
     \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
-    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma$};
+    (q_i.south west) -- (q_f.south west) node [black,midway,yshift=-9ex]{$\Gamma$};
   \end{tikzpicture}
@@
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to the stage $\Gamma_i$.
-The UAV remains in the stage with any generic point $\mathbf{p}_{k_1}$.
+The UAV remains in the stage with any generic point $\mathbf{p}_{k_2}$.
 It eventually enters the stage $\Gamma_{i+1}$ with the triggering point $\mathbf{p}_{\Gamma_i}$ and so on, until it reaches the final point.
+The stage $\Gamma_f$ is the accepting stage (it indicates that the UAV has completed the plan).
 

### 2021-02-21 iros-2021.tex
proof reading

@@
 
-In the spirit of reducing costs and resources, we showcase the algorithm using the problem of dynamic planning for a precision agriculture fixed-wing UAV.
+In the spirit of reducing costs and resources, we showcase the algorithm using dynamic planning for a precision agriculture fixed-wing UAV.
 Precision agriculture is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
@@
 Path-wise, the UAV flies in circles and lines covering a polygon.
-Computation-wise, it detects obstacles using a neural network and notifies grounded mobile robots employed for, e.g., harvesting.
+Computation-wise, it detects hazards using a neural network and notifies grounded mobile robots employed for, e.g., harvesting.
 The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
@@
 We then derive some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information in Appendixes.
+Finally, we provide some additional information in Appendix.
 
@@
 
-The algorithm outputs the control (the parameters) using output model predictive control (MPC)~\cite{rawlings2017model} where it checks the satisfaction of the battery constraints.
+The algorithm outputs the control (the parameters) using model predictive control (MPC)~\cite{rawlings2017model} where it checks the satisfaction of the battery constraints.
 The control is data-driven.
@@
   where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the path constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
-$\mathbf{p}_k$ is a point of a UAV flying at an altitude $h\in\mathbb{R}_{>0}$\footnote{The altitude might change at different flying phases and under different atmospheric conditions} w.r.t.
+$\mathbf{p}_k$ is a point of a UAV flying at an altitude $h\in\mathbb{R}_{>0}$
+  %\footnote{The altitude might change at different flying phases and under different atmospheric conditions}
+  w.r.t.
 some inertial navigation frame $\mathcal{O}_W$.
@@
     \input{\figpath/traj1.tikz}
-    \caption{Plan definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
+    \caption{Definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
     \label{fig:traj1}
@@
 
-In order to simplify the problem formulation, we consider some primitive paths. All the other paths are build from these paths with a shift $\mathbf{d}:=(x_d,y_d)$.
-
-Given $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) primitive paths $\varphi_1,\dots\varphi_n$, a generic starting point $\mathbf{p}$ and the current levels of the path parameters $c_1^\rho$, all the other paths $\varphi_{n+1},\dots,\varphi_l$ are build
+In order to simplify the problem formulation, we consider some primitive paths. All the other paths are built from these paths with a shift $\mathbf{d}:=(x_d,y_d)$.
+
+Given $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) primitive paths $\varphi_1,\dots\varphi_n$, a generic starting point $\mathbf{p}$ and the current levels of the path parameters $c_1^\rho$, all the other paths $\varphi_{n+1},\dots,\varphi_l$ are built
 \begin{equation}\label{eq:primitive}\begin{split}
@@
 One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Equation~(\ref{eq:primitive}).
-If there is no such value, (e.g., when the plan is composed of only one path), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Figure~\ref{fig:il-abs}).
+If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Figure~\ref{fig:il-abs}).
 
@@
 \end{split}\end{equation}
-where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transition matrix, and $C\in\mathbb{R}^m$ is the output matrix.
 In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros (*).
@@
   \input{\figpath/traj2.tikz}
-  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the path in Figure~\ref{fig:il-abs}).}
+  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Figure~\ref{fig:il-abs}).}
   \label{fig:tee1}
@@
 
-Let us assume that the set
+The set
 \begin{equation}\label{eq:area}
-  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1}^\rho)\in\mathcal{C}_i\},
+  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i}^\rho)\in\mathcal{C}_i\},
 \end{equation}
 delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Figure~\ref{fig:tee1}).
-$\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the path.
+$\varphi_i$ is a function of the two coordinates and the path parameters, and is equal to zero when a point $\mathbf{p}_k$ is on the path.
 Physically, this means the UAV is flying exactly over the nominal trajectory.
@@
 where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps.
+Both conditions of the loop have to be respected.
 The maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints (or increased if with $\overline{c}_i+\delta$ the constraints are still respected).
@@
 
-In this section, we discuss our experimental setup, the implementation strategy, and some results.
+In this section, we discuss our experimental setup, the implementation strategy, and the results.
 
@@
 We later extended the UAV to carry a companion computer, NVIDIA Jetson Nano~\cite{nano}, running ROS.
-The companion computer has two ROS nodes; one detects obstacles using PedNet, a Fully Convolutional Neural Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
+The companion computer has two ROS nodes; one detects hazards using PedNet, a Fully Convolutional Neural Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
 
@@
   \footnotesize
-  \input{\figpath/results/new_physics2/model.tikz}
-  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
-  \label{fig:model}
+  \input{\figpath/results/new_physics2/ener.tikz}
+  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
+Below are the energy evolutions from the algorithm (\hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii}).
+It replans the path when the final time and battery time do not match, and the computation when the battery is discharged.}
+  \label{fig:ener}
 \end{figure}
@@
   \footnotesize
-  \input{\figpath/results/new_physics2/ener.tikz}
-  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{7.I} and \hyperref[fig:ener:static-II]{7.II}).
-Below are the energy evolutions from the algorithm (\hyperref[fig:ener-dyn-i]{7.i} and \hyperref[fig:ener-dyn-ii]{7.ii}).
-It replans the path when the final time and battery time do not match, and the computation when the battery is discharged.}
-  \label{fig:ener}
+  \input{\figpath/results/new_physics2/model.tikz}
+  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
+  \label{fig:model}
 \end{figure}
@@
 Path  \hyperref[fig:trajs-II-static]{5.II} is flying under the same conditions but a wind direction of 90 degrees and the initial path parameter value of -1000.
-The energy evolutions of these two paths are the top two subfigures \hyperref[fig:ener:static-I]{7.I} and \hyperref[fig:ener:static-II]{7.II} of Figure~\ref{fig:ener}.
+The energy evolutions of these two paths are the top two subfigures \hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II} of Figure~\ref{fig:ener}.
 The simulated energy data are in black, the model evolution in red.
@@
 We reduce or increase the parameter to optimize the battery time.
-The path parameter $c_{1,1}$ is equal for all the stages and it changes the radius of the first circle (the change is illustrated in Figure~\ref{fig:tee1}) in the current period and therefore shifts the other paths accordingly.
+The path parameter $c_{1,1}$ is equal for all the stages and it changes the radius of the first circle in the current period and therefore shifts the other paths accordingly (the change is illustrated in Figure~\ref{fig:tee1}).
 It results in a shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively.
@@
 
-We have tested the validity of the algorithm showing the dynamic adaptation in the subfigures \hyperref[fig:trajs-dyn-i]{5.i} and \hyperref[fig:trajs-dyn-ii]{5.ii} of Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{7.i} and \hyperref[fig:ener-dyn-ii]{7.ii} of Figure~\ref{fig:ener} energy-wise.
+We have tested the validity of the algorithm showing the dynamic adaptation in the subfigures \hyperref[fig:trajs-dyn-i]{5.i} and \hyperref[fig:trajs-dyn-ii]{5.ii} of Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii} of Figure~\ref{fig:ener} energy-wise.
 For the first path (Subfigure \hyperref[fig:trajs-I-static]{5.I}) the plan starts at the highest configuration of parameters.
@@
 We simulated the opposite scenario for the second path (Subfigure \hyperref[fig:trajs-II-static]{5.II}).
-The plan starts at the lowest configuration of parameters but the battery behaves linearly.
+The plan starts at the lowest configuration of parameters and the battery behaves linearly.
 We note that the path parameter is increased as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter is optimized for the battery discharge rate.

### 2021-02-22 scripts/SIM8_casadi.m
mpc implementation using casadi

@@ -1,0 +1,754 @@
+
+% SIM8
+
+% simulation of the algorithm, path I, dynamic
+% optimal control (MPC) implemented with casadi
+
+addpath('../../../../../casadi-linux-matlabR2014b-v3.5.5');
+% UPDATE THE PATH WITH CASADI SOURCE !
+import casadi.* % import casadi for optimal control
+
+
+
+%% init
+
+
+%%% initializing all the params %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% prompts with data for input
+
+% asking data about the path
+
+answer = inputdlg(...
+    {'vehicle direction [deg]:','wind speed [m/s]:',...
+     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+     'max power [W]:','min power [W]:','triggering point radius [m]'
+    }, ...
+    'path initialization',[1 40],...
+    {'270','5','0','-100','220','36','16','20'});
+
+if isempty(answer)
+    strp = [270; 5; 0; -100; 220; 36; 16; 20];
+else
+    strp = str2double(answer);
+end
+
+clear answer;
+
+
+%%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% gains
+%       kp, kvv  kd,  ke1, ke2, ke3, ke4
+strp3 = [5   5  .001 .006  .1  .006  .1];
+%         
+
+vd = strp(1); % initial UAV direction
+ws = strp(2); % wind speed
+wd = strp(3); % wind direction
+start_x = strp(4); % starting position x
+start_y = strp(5); % y
+max_pw = strp(6); % maximum reachable power
+min_pw = strp(7); % minimum
+trig_eps = [strp(8);strp(8)]; % radius of the triggering point (it's a 
+                              % circular area)
+
+strp2 = 3;
+r = strp2; % model size (the bigger the more precise)
+
+% dynamics control
+
+m = 1; % mass of the aircraft [kg]
+W = m*9.8; % weight force [N]
+
+cl = 9.8/15^2; % coefficient to be determined experimentally
+cth = 15/50; % same
+
+kp = strp3(1); % positive gain constant to be also determined experimentally
+kvv = strp3(2);
+th_nominal = 50; % nominal vlalue of the throttle
+th_delta = 0;
+hd = 25; % desired altitude [m]
+
+% guidance
+kd = strp3(3);
+
+% physics init
[…]

### 2021-02-22 scripts/SIM8_casadi.m
fixing issues in the casadi implementation

@@ -416,49 +416,67 @@ while true
                 dt = delta_T;
                 
                 opti = casadi.Opti(); % define opt problem
-                Q = opti.variable(7,hh);
+                S = opti.variable(7,hh);
                 U = opti.variable(2,hh-1);
                
-                initcon = Q(:,1) == qq0;
-                initcon = U(1,1) == c1;
-                initcon = U(2,1) == max_c2; % start with max param
+                initcon = S(:,1) == qq0;
+                initcon = U(1,:) == c1; % path param changed in 
+                                        % function of the battery t
+                                        % in the while loop
+                initcon = U(2,1) == mmax_c2; % start with max param
                 opti.subject_to(initcon);
-                opti.subject_to(U(2,:) >= min_c2);
-                opti.subject_to(U(2,:) <= mmax_c2);
-                opti.subject_to(U(1,:) == c1); % path param changed in 
-                                               % function of the battery t
+                
+                opti.subject_to(min_c2 <= U(2,:) <= mmax_c2);
+                
                 L = 0; % cost (l,Vf)
+                result_rk4 = [];
                 
                 for j=1:hh-1
                     eest_u_old = eeu;
                     eeu = est_u(c1,U(2,j));
                     
-                    result_rk4 = F_RK4(Q(:,j),u(eeu,eest_u_old),delta_T);
+                    result_rk4 = F_RK4(S(:,j),u(eeu,eest_u_old),delta_T);
                     
                     con{j+1} = ...
-                        Q(:,j+1) == F_RK4(result_rk4,... % state const
+                        S(:,j+1) == F_RK4(result_rk4,... % state const
                                           u(eeu,eest_u_old),delta_T); 
-                    b0 = b0+delta_T*b(C*result_rk4); 
-                    bcon{j+1} = C*result_rk4 <= b0*qc*int_v; % battery 
-                                                             % const
+                    b0 = b0-delta_T*b(C*result_rk4); % battery dynamics
+
                     opti.subject_to(con{j+1});
-                    opti.subject_to(bcon{j+1});
                     
                     L = L+.5*(result_rk4+B*u(eeu,eest_u_old)).'*diag(C)*...
                     (result_rk4+B*u(eeu,eest_u_old)); % cost update (l)
                 end
                 
-                result_rk4 = F_RK4(Q(:,j),[0;0],delta_T);
+                opti.subject_to(C*result_rk4 > b0*qc*int_v);% battery const 
+                
+                result_rk4 = F_RK4(S(:,j),[0;0],delta_T);
[…]

### 2021-03-20 energy-planning.tex
changing the name

--- 2021-02-21 iros-2021.tex
@@
   \begin{algorithmic}[1]
-    \STATE $\mathbf{p}_{k-1}\gets \mathbf{p}_0, \mathbf{q}_{k-1}\gets \mathbf{q}_0$
-    \STATE $\mathbf{u}_{k-2},\mathbf{u}_{k-1}\gets \{\emptyset\}$\label{alg:init}
+    \STATE $\mathbf{p}_{k}\gets \mathbf{p}_0, \mathbf{q}_{k}\gets \mathbf{q}_0$
+    \STATE $\mathbf{u}_{k}\gets \overline{c}_i$\label{alg:init}
     \FOR{$i\in[l]^+$}\label{alg:stages-loop}
-      \WHILE{$\mathbf{p}_{k-1}\neq\mathbf{p}_{\Gamma_i}$}\label{alg:while}
-        \STATE $\mathbf{u}_k\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k-1}^{k+N-2}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N-1})}}$\label{alg:mpc}
-        \STATE $\hat{\mathbf{q}}_{k}\gets A\mathbf{q}_{k-1}+B\mathbf{u}$\label{alg:evolution}
-        \STATE $\mathbf{q}_{k}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k}$ and sensor data\label{alg:kalman_end}
-        \STATE $\mathbf{p}_{k}\gets\mathbf{p}_{k-1}\dot{\mathbf{p}}_d(\mathbf{p}_{k-1})/v$ \label{alg:pos}
+      \WHILE{$\mathbf{p}_{k}\neq\mathbf{p}_{\Gamma_i}$}\label{alg:while}
+        \STATE $\mathbf{u}_{k+1}\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k+1}^{k+N-1}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N})}}$\label{alg:mpc}
+        \STATE $\hat{\mathbf{q}}_{k+1}\gets A\mathbf{q}_{k}+B\mathbf{u}$\label{alg:evolution}
+        \STATE $\mathbf{q}_{k+1}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k_1}$ and sensor data\label{alg:kalman_end}
+        \STATE $\mathbf{p}_{k+1}\gets\mathbf{p}_{k}\dot{\mathbf{p}}_d(\mathbf{p}_{k})/v$ \label{alg:pos}
         \STATE $k\gets k+1$
@@
 \begin{equation*}\label{eq:cost}\begin{split}
-  V_f(\mathbf{q}_k)&:=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,\\
-  l(\mathbf{q}_k,\mathbf{u}_k)&:=(1/2)(\mathbf{q}_k+B\mathbf{u})^T\mathrm{diag}(C)(\mathbf{q}_k+B\mathbf{u}),\hspace*{-2.5ex}
+  V_f(\mathbf{q}_k)&=l(\mathbf{q}_k,\mathbf{u}_k)=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,
 \end{split}\end{equation*}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}), and $B$, $\mathbf{u}$ are defined in Equation~(\ref{eq:state-control}).
+where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}).
 
@@
 Both conditions of the loop have to be respected.
-The maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints (or increased if with $\overline{c}_i+\delta$ the constraints are still respected).
+The maximum values of path and computation parameters are reduced by the steps if they don't meet the constraints.
 
@@
   \footnotesize
-  \input{\figpath/results/new_physics2/trajs.tikz}
+  \input{\figpath/results/new_physics2/trajs_revised.tikz}
   \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
@@
   \footnotesize
-  \input{\figpath/results/new_physics2/ener.tikz}
+  \input{\figpath/results/new_physics2/ener_revised.tikz}
   \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
@@
 We note that the path parameter is increased as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter is optimized for the battery discharge rate.
-For both cases, we used reductions $\delta$ of 500 and 2 for $c_{1,1}$ and $c_{1,2}$ respectively, and the horizon $N$ equal to the period $T$.
+For both cases, we used reductions $\delta$ of 500 and 2 for $c_{1,1}$ and $c_{1,2}$ respectively, and the horizon $N$ equal to 6 seconds.
 

### 2021-03-20 scripts/SIM6.m

@@ -472,8 +472,8 @@ csvwrite(strcat('evol_simulation',strp5,'.csv'),[...
 % this part takes the coefficients at 200 s estimated with KF above and
 % evolve them to see if the model match the data
 
-qq0 = log_q(:,200/delta_T);
-log_yy = [log_y(200/delta_T)];
+qq0 = log_q(:,22890);
+log_yy = [log_y(22890)];
 Ad = A*delta_T/10+eye(2*r+1);
 for ii=200+delta_T:delta_T/10:400
     qq0 = Ad*qq0;

### 2021-03-20 scripts/SIM8_casadi.m

@@ -19,21 +19,21 @@ import casadi.* % import casadi for optimal control
 
 % asking data about the path
 
-answer = inputdlg(...
-    {'vehicle direction [deg]:','wind speed [m/s]:',...
-     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
-     'max power [W]:','min power [W]:','triggering point radius [m]'
-    }, ...
-    'path initialization',[1 40],...
-    {'270','5','0','-100','220','36','16','20'});
+%answer = inputdlg(...
+%    {'vehicle direction [deg]:','wind speed [m/s]:',...
+%     'wind direction [deg]:','start coordinate x [m]:','y [m]:',...
+%     'max power [W]:','min power [W]:','triggering point radius [m]'
+%    }, ...
+%    'path initialization',[1 40],...
+%    {'270','5','0','-100','220','36','16','20'});
 
-if isempty(answer)
-    strp = [270; 5; 0; -100; 220; 36; 16; 20];
-else
-    strp = str2double(answer);
-end
+%if isempty(answer)
+strp = [270; 5; 0; -100; 220; 36; 16; 20];
+%else
+%    strp = str2double(answer);
+%end
 
-clear answer;
+%clear answer;
 
 
 %%% physics data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -107,6 +107,7 @@ P0 = ones(size(q0,1)); % covariance guess
 % process noise and sensor noise
 Q = ones(size(q,1));
 R = 1;
+N = 6; % MPC horizon (6 seconds)
 
 % soc
 kb = .00183; % battery coefficient
@@ -143,9 +144,6 @@ c1_old = c1;
 
 min_c2 = 2;
 max_c2 = 10;
-mmax_c2 = max_c2; % needs to be stored twice because the algorithm reduces
-                  % exactly the max_c2 and then if it wants to increase it,
-                  % it needs to know the original value
 c2 = max_c2; % computational parameter
 c2_old = c2;
 
@@ -223,15 +221,11 @@ syms x y;
 last_trig = [175;161]; % the last triggering point
 % next are just some simulation utilities
 reached = 0; % reached the end of the simulation
-
-                                                 
[…]

### 2021-03-20 scripts/SIM9_casadi2.m

@@ -6,7 +6,7 @@
 
 %% casadi opt control
 
-addpath('../../../../../casadi-linux-matlabR2014b-v3.5.5/');
+addpath('../../../../../');
 % UPDATE THE PATH WITH CASADI SOURCE !
 
 
@@ -366,7 +366,7 @@ while true
                     C,u,est_u,k,delta_T,r);
                 
                 old_c2 = c2;
-                c2 = round(c_chain(2,1)); % getting c2
+                c2 = c_chain(2,1); % getting c2
                 
                 log_q_chain = [log_q_chain;k*delta_T  C*q_chain];
                 log_c_chain = [log_c_chain;k*delta_T  c_chain(2,:)];
@@ -633,6 +633,7 @@ function [c_chain q_chain] = mpc(min_c1,max_c1,min_c2,max_c2,c1,c2,N,eu,b0,b,...
     opti = casadi.Opti(); % define opt problem
     Q = opti.variable(2*r+1,N);
     U = opti.variable(2,N-1);
+    L = opti.variable(1,N);
     log_Q = opti.variable(2*r+1,hh);
     log_b = opti.variable(1,hh);
                     
@@ -660,6 +661,8 @@ function [c_chain q_chain] = mpc(min_c1,max_c1,min_c2,max_c2,c1,c2,N,eu,b0,b,...
         
         if mod(jj,1/delta_T) == 0 % every sum in the MPC
             
+            L(jjj) = C*dQ;
+            
             if (jjj < N)                
                 eeeu = est_u(U(1,jjj),U(2,jjj));
             end
@@ -672,7 +675,7 @@ function [c_chain q_chain] = mpc(min_c1,max_c1,min_c2,max_c2,c1,c2,N,eu,b0,b,...
                                        
     end
                 
-    opti.minimize(-sum(U(2,:).^2));
+    opti.minimize(-sum(L.^2));
     opti.solver('ipopt');
                 
     try

### 2021-03-20 scripts/animate.m

@@ -3,7 +3,7 @@
 % load the data
 
 % change the following 2
-load('3casadi_4.mat'); % load the data
+load('new_data_to_sort/3casadi_4.mat'); % load the data
 filename = '3casadi_4';
 
 n_coefs = 2*r+1;
@@ -97,9 +97,8 @@ for j=1:1/delta_T:k % path
     if (j-1)*delta_T >= 85
         data_mpc_q = log_q_chain(log_q_chain(:,1) == (j-1)*delta_T,:);
         data_mpc_q = data_mpc_q(2:end);
-        data_mpc_q = imresize(data_mpc_q,[1 (1/delta_T)*N]);
         data_mpc_q = [linspace((j-1)*delta_T,(j-1+N*(1/delta_T))*...
-            delta_T,length(data_mpc_q)).' data_mpc_q.'];
+            delta_T,N).' data_mpc_q.'];
     end
     
     if ~isnan(data_mpc_q)
@@ -115,6 +114,7 @@ for j=1:1/delta_T:k % path
     
     grid on
     xlim([0 k*delta_T]);
+    ylim([25 50]);
     ax = gca;
     ax.FontName = 'Helvetica';
     ax.FontSize = 24;
@@ -161,6 +161,7 @@ for j=1:1/delta_T:k % path
     nexttile,plot(linspace(0,j*delta_T,length(c1_data)),c1_data,...
         'Color','k','LineWidth',1.2)
     grid on
+    ylim([-1000 0]);
     xlim([0 k*delta_T]);
     ax = gca;
     ax.FontName = 'Helvetica';
@@ -175,6 +176,7 @@ for j=1:1/delta_T:k % path
         'Color','k','LineWidth',1.2)
     hold off
     grid on
+    ylim([2 10]);
     xlim([0 k*delta_T]);
     ax = gca;
     ax.FontName = 'Helvetica';

### 2021-12-02 energy-planning.tex
updating the paper with the contents from my phd thesis

@@
 %%
+%% Energy-Aware Planning-Scheduling for Autonomous Aerial Robots 
 %%
-%% 
-%%
-
-\documentclass[letterpaper,10pt,conference]{ieeeconf}
-\IEEEoverridecommandlockouts
+
+\documentclass[letterpaper,10pt,journal,twoside]{IEEEtran} 
+%\IEEEoverridecommandlockouts
 
@@
 \usetikzlibrary{automata,positioning,decorations.pathreplacing,backgrounds}
-\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
+%\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
 \usepackage{pifont}
@@
 %% pseudocode package
-\usepackage{algorithm,algorithmic}
+\usepackage{algorithm}
+\usepackage[noend]{algorithmic}
 
 % counter to mantain the line numbering
-\renewcommand\thealgorithm{}
 \newcommand{\setalglineno}[1]{%
@@
 %% packages for subfigures (eventually)
-\usepackage[tight,footnotesize]{subfigure}
+%\usepackage[tight,footnotesize]{subfigure}
+\usepackage[font=footnotesize]{caption}
+\usepackage[font=footnotesize]{subcaption}
 %\usepackage[caption=false]{caption}
@@
 \makeatother
-\usepackage{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
 \makeatletter
@@
 \newtheorem{rem}{Remark}
+\newtheorem{obs}{Observation}
 
@@
 \begin{filecontents}{\jobname.bib}
-  @inproceedings{seewald2020mechanical,
-    title={Mechanical and Computational Energy Estimation of a Fixed-Wing Drone}, 
-    author={Seewald, Adam and Garcia de Marina, Hector and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
-    pages={135--142},
-    year={2020},
-    organization={IEEE},
-    DOI={10.1109/IRC.2020.00028},
-    url={https://adamseewald.cc/short/mechanical2020}
-  }
-
-  @article{seewald2019coarse,
-    title={Coarse-Grained Computation-Oriented Energy Modeling for Heterogeneous Parallel Embedded Systems},
-    author={Seewald, Adam and Schultz, Ulrik Pagh and Ebeid, Emad and Midtiby, Henrik Skov},
-    journal={International Journal of Parallel Programming},
-    pages={1--22},
-    year={2019},
-    publisher={Springer},
-    DOI={10.1007/s10766-019-00645-y},
-    url={https://adamseewald.cc/short/coarse2019}
-  }
-  @inproceedings{seewald2019component,
-    title={Component-based computation-energy modeling for embedded systems},
-    author={Seewald, Adam and Schultz, Ulrik Pagh and Roeder, Julius and Rouxel, Benjamin and Grelck, Clemens},
-    booktitle={Proceedings Companion of the 2019 ACM SIGPLAN International Conference on Systems, Programming, Languages, and Applications: Software for Humanity},
-    pages={5--6},
-    year={2019},
-    organization={ACM},
-    DOI={10.1145/3359061.3362775},
-    url={https://adamseewald.cc/short/component2019}
-  }
-  @inproceedings{hajjaj2014review,
-    title={Review of research in the area of agriculture mobile robots},
-    author={Hajjaj, Sami Salama Hussen and Sahari, Khairul Salleh Mohamed},
-    booktitle={The 8th International Conference on Robotic, Vision, Signal Processing \& Power Applications},
-    pages={107--117},
-    year={2014},
-    organization={Springer}
-  }
-  @inproceedings{qingchun2012study,
-    title={Study on strawberry robotic harvesting system},
-    author={Qingchun, Feng and Wengang, Zheng and Quan, Qiu and Kai, Jiang and Rui, Guo},
-    booktitle={2012 IEEE International Conference on Computer Science and Automation Engineering (CSAE)},
-    volume={1},
-    pages={320--324},
-    year={2012},
-    organization={IEEE}
-  }
-  @article{edan2000robotic,
-    title={Robotic melon harvesting},
-    author={Edan, Yael and Rogozin, Dima and Flash, Tamar and Miles, Gaines E},
-    journal={IEEE Transactions on Robotics and Automation},
-    volume={16},
-    number={6},
-    pages={831--835},
-    year={2000},
-    publisher={IEEE}
-  }
-  @inproceedings{aljanobi2010setup,
-    title={A setup of mobile robotic unit for fruit harvesting},
-    author={Aljanobi, AA and Al-Hamed, SA and Al-Suhaibani, SA},
-    booktitle={19th International Workshop on Robotics in Alpe-Adria-Danube Region (RAAD 2010)},
-    pages={105--108},
-    year={2010},
-    organization={IEEE}
-  }
-  @article{de2011design,
-    title={Design and control of an apple harvesting robot},
-    author={De-An, Zhao and Jidong, Lv and Wei, Ji and Ying, Zhang and Yu, Chen},
-    journal={Biosystems engineering},
-    volume={110},
-    number={2},
-    pages={112--122},
-    year={2011},
-    publisher={Elsevier}
-  }
-  @article{dong2011development,
-    title={Development of a row guidance system for an autonomous robot for white asparagus harvesting},
-    author={Dong, Fuhong and Heinemann, Wolfgang and Kasper, Roland},
-    journal={Computers and Electronics in Agriculture},
-    volume={79},
-    number={2},
-    pages={216--225},
-    year={2011},
-    publisher={Elsevier}
-  }
-  @inproceedings{li2008analysis,
-    title={Analysis of workspace and kinematics for a tomato harvesting robot},
-    author={Li, Zhiguo and Liu, Jizhan and Li, Pingping and Li, Wei},
-    booktitle={2008 International Conference on Intelligent Computation Technology and Automation (ICICTA)},
-    volume={1},
-    pages={823--827},
-    year={2008},
-    organization={IEEE}
-  }
-  @article{puri2017agriculture,
-    title={Agriculture drones: A modern breakthrough in precision agriculture},
-    author={Puri, Vikram and Nayyar, Anand and Raja, Linesh},
-    journal={Journal of Statistics and Management Systems},
-    volume={20},
-    number={4},
-    pages={507--518},
-    year={2017},
-    publisher={Taylor \& Francis}
-  }
-  @inproceedings{mei2005case,
-    title={A case study of mobile robot's energy consumption and conservation techniques},
-    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Y Charlie and Lee, CS George},
-    booktitle={ICAR'05. Proceedings., 12th International Conference on Advanced Robotics, 2005.},
-    pages={492--497},
-    year={2005},
-    organization={IEEE}
-  }
-  @inproceedings{mei2004energy,
-    title={Energy-efficient motion planning for mobile robots},
-    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Y Charlie and Lee, CS George},
-    booktitle={IEEE International Conference on Robotics and Automation, 2004. Proceedings. ICRA'04. 2004},
-    volume={5},
-    pages={4344--4349},
-    year={2004},
-    organization={IEEE}
-  }
-  @article{mei2006deployment,
-    title={Deployment of mobile robots with energy and timing constraints},
-    author={Mei, Yongguo and Lu, Yung-Hsiang and Hu, Yu Charlie and Lee, CS George},
-    journal={IEEE Transactions on robotics},
-    volume={22},
-    number={3},
-    pages={507--522},
-    year={2006},
-    publisher={IEEE}
-  }
-  @inproceedings{kreciglowa2017energy,
-    title={Energy efficiency of trajectory generation methods for stop-and-go aerial robot navigation},
-    author={Kreciglowa, Nadia and Karydis, Konstantinos and Kumar, Vijay},
-    booktitle={2017 International Conference on Unmanned Aircraft Systems (ICUAS)},
-    pages={656--662},
-    year={2017},
-    organization={IEEE}
-  }
-  @article{sadrpour2013mission,
-    title={Mission Energy Prediction for Unmanned Ground Vehicles Using Real-time Measurements and Prior Knowledge},
-    author={Sadrpour, Amir and Jin, Jionghua and Ulsoy, A Galip},
-    journal={Journal of Field Robotics},
-    volume={30},
-    number={3},
-    pages={399--414},
-    year={2013},
-    publisher={Wiley Online Library}
-  }
-  @inproceedings{sadrpour2013experimental,
-    title={Experimental validation of mission energy prediction model for unmanned ground vehicles},
-    author={Sadrpour, Amir and Jin, Judy and Ulsoy, A Galip},
-    booktitle={2013 American Control Conference},
-    pages={5960--5965},
-    year={2013},
-    organization={IEEE}
-  }
-  @inproceedings{kim2005energy,
-    title={Energy-saving 3-step velocity control algorithm for battery-powered wheeled mobile robots},
-    author={Kim, Chong Hui and Kim, Byung Kook},
-    booktitle={Proceedings of the 2005 IEEE international conference on robotics and automation},
-    pages={2375--2380},
-    year={2005},
-    organization={IEEE}
-  }
-  @inproceedings{kim2008minimum,
-    title={Minimum-energy translational trajectory planning for battery-powered three-wheeled omni-directional mobile robots},
-    author={Kim, Hongjun and Kim, Byung-Kook},
-    booktitle={2008 10th International Conference on Control, Automation, Robotics and Vision},
-    pages={1730--1735},
-    year={2008},
-    organization={IEEE}
-  }
-  @book{wahab2015energy,
-    title={Energy modeling of differential drive robots},
-    author={Wahab, Mudasser and Rios-Gutierrez, Fernando and El Shahat, Adel},
-    year={2015},
-    publisher={IEEE}
-  }
-  @online{px4,
-    author={PX4},
-    title={{PX4} open-source autopilot},
-    url={https://px4.io/},
-    urldate={2016-09-01}
-  }
-  @online{papa,
-    author={Paparazzi},
-    title={{UAV} open-source project},
-    url={http://wiki.paparazziuav.org/},
-    urldate={2016-09-01}
-  }
-  @online{nano,
-    author={NVIDIA},
-    title={{NVIDIA Jetson Nano} developer kit},
-    url={https://developer.nvidia.com/embedded/jetson-nano-developer-kit},
-    urldate={2020-02-02}
-  }
-  @online{opterra,
-    author={Horizon Hobby},
-    title={{Opterra} 2m Wing BNF Basic},
-    url={https://www.horizonhobby.com/opterra-2m-wing-bnf-basic-p-efl11150},
-    urldate={2020-02-02}
-  }
-  @online{meier2013mavlink,
-    title={Mavlink: Micro air vehicle communication protocol},
-    author={Meier, Lorenz and Camacho, J and Godbolt, B and Goppert, J and Heng, L and Lizarraga, M and others},
-    url={https://mavlink.io/},
-    urldate={2020-02-02}
-  }
-  @article{ullah2018pednet,
-    title={Pednet: A spatio-temporal deep convolutional neural network for pedestrian segmentation},
-    author={Ullah, Mohib and Mohammed, Ahmed and Alaya Cheikh, Faouzi},
-    journal={Journal of Imaging},
-    volume={4},
-    number={9},
-    pages={107},
-    year={2018},
-    publisher={Multidisciplinary Digital Publishing Institute}
-  }
-  @inproceedings{sandler2018mobilenetv2,
-    title={Mobilenetv2: Inverted residuals and linear bottlenecks},
-    author={Sandler, Mark and Howard, Andrew and Zhu, Menglong and Zhmoginov, Andrey and Chen, Liang-Chieh},
-    booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
-    pages={4510--4520},
-    year={2018}
-  }
-  @inproceedings{quigley2009ros,
-    title={ROS: an open-source Robot Operating System},
-    author={Quigley, Morgan and Conley, Ken and Gerkey, Brian and Faust, Josh and Foote, Tully and Leibs, Jeremy and Wheeler, Rob and Ng, Andrew Y},
-    booktitle={ICRA workshop on open source software},
-    volume={3},
-    number={3.2},
-    pages={5},
-    year={2009}
-  }
-  @book{stengel1994optimal,
-    title={Optimal control and estimation},
-    author={Stengel, Robert F},
-    year={1994},
-    publisher={Courier Corporation}
-  }
-  @book{simon2006optimal,
-    title={Optimal state estimation: Kalman, H infinity, and nonlinear approaches},
-    author={Simon, Dan},
-    year={2006},
-    publisher={John Wiley \& Sons}
-  }
-  @inproceedings{de2017guidance,
-    title={Guidance algorithm for smooth trajectory tracking of a fixed wing UAV flying in wind flows},
-    author={De Marina, Hector Garcia and Kapitanyuk, Yuri A and Bronz, Murat and Hattenberger, Gautier and Cao, Ming},
-    booktitle={2017 IEEE international conference on robotics and automation (ICRA)},
-    pages={5740--5745},
-    year={2017},
-    organization={IEEE}
-  }
-  @book{rawlings2017model,
-    title={Model predictive control: theory, computation, and design},
-    author={Rawlings, James Blake and Mayne, David Q and Diehl, Moritz},
-    volume={2},
-    year={2017},
-    publisher={Nob Hill Publishing Madison, WI}
-  }
-  @inproceedings{morbidi2016minimum,
-    title={Minimum-energy path generation for a quadrotor UAV},
-    author={Morbidi, Fabio and Cano, Roel and Lara, David},
-    booktitle={2016 IEEE International Conference on Robotics and Automation (ICRA)},
-    pages={1492--1498},
-    year={2016},
-    organization={IEEE}
-  }
-  @inproceedings{daponte2019review,
-    title={A review on the use of drones for precision agriculture},
-    author={Daponte, Pasquale and De Vito, Luca and Glielmo, Luigi and Iannelli, Luigi and Liuzza, Davide and Picariello, Francesco and Silano, Giuseppe},
-    booktitle={IOP Conference Series: Earth and Environmental Science},
-    volume={275},
-    number={1},
-    pages={012022},
-    year={2019},
-    organization={IOP Publishing}
-  }
-  @inproceedings{zamanakos2020energy,
-    title={Energy-Aware Design of Vision-Based Autonomous Tracking and Landing of a UAV}, 
-    author={Zamanakos, Georgios and Seewald, Adam and Midtiby, Henrik Skov and Schultz, Ulrik Pagh},
-    booktitle={2020 Fourth IEEE International Conference on Robotic Computing (IRC)},
-    pages={294--297},
-    year={2020},
-    organization={IEEE},
-    DOI={10.1109/IRC.2020.00054},
-    url={https://adamseewald.cc/short/energy2020}
-  }
-  @inproceedings{seewald2020beyond,
-    title={Beyond Traditional Energy Planning: the Weight of Computations in Planetary Exploration}, 
-    author={Seewald, Adam},
-    booktitle={IROS Workshop on Planetary Exploration Robots: Challenges and Opportunities (PLANROBO20)},
-    pages={3},
-    year={2020},
-    publisher={ETH Zurich, Department of Mechanical and Process Engineering},
-    DOI={10.3929/ethz-b-000450120},
-    url={https://adamseewald.cc/short/beyond2020}
-  }
-  @inproceedings{lindemann2005smoothly,
-    title={Smoothly blending vector fields for global robot navigation},
-    author={Lindemann, Stephen R and LaValle, Steven M},
-    booktitle={Proceedings of the 44th IEEE Conference on Decision and Control},
-    pages={3553--3559},
-    year={2005},
-    organization={IEEE}
-  }
-  @article{gonccalves2010vector,
-    title={Vector fields for robot navigation along time-varying curves in $n$-dimensions},
-    author={Gon{\c{c}}alves, Vin{\'\i}cius M and Pimenta, Luciano CA and Maia, Carlos A and Dutra, Bruno CO and Pereira, Guilherme AS},
-    journal={IEEE Transactions on Robotics},
-    volume={26},
-    number={4},
-    pages={647--659},
-    year={2010},
-    publisher={IEEE}
-  }
-  @inproceedings{panagou2014motion,
-    title={Motion planning and collision avoidance using navigation vector fields},
-    author={Panagou, Dimitra},
-    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
-    pages={2513--2518},
-    year={2014},
-    organization={IEEE}
-  }
-  @inproceedings{zhou2014vector,
-    title={Vector field following for quadrotors using differential flatness},
-    author={Zhou, Dingjiang and Schwager, Mac},
-    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
-    pages={6567--6572},
-    year={2014},
-    organization={IEEE}
-  }
-  @article{kapitanyuk2017guiding,
-    title={A guiding vector-field algorithm for path-following control of nonholonomic mobile robots},
-    author={Kapitanyuk, Yuri A and Proskurnikov, Anton V and Cao, Ming},
-    journal={IEEE Transactions on Control Systems Technology},
-    volume={26},
-    number={4},
-    pages={1372--1385},
-    year={2017},
-    publisher={IEEE}
-  }
-  @book{kuo1967automatic,
-    title={Automatic Control Systems},
-    author={Kuo, B.C.},
-    isbn={9780130549730},
-    lccn={67016388},
-    series={Electrical engineering series},
-    year={1967},
-    publisher={Prentice-Hall}
-  }
-  @article{moler2003nineteen,
-    title={Nineteen dubious ways to compute the exponential of a matrix, twenty-five years later},
-    author={Moler, Cleve and Van Loan, Charles},
-    journal={SIAM review},
-    volume={45},
-    number={1},
-    pages={3--49},
-    year={2003},
-    publisher={SIAM}
-  }
-  @book{ogata2002modern,
-    title={Modern Control Engineering},
-    author={Ogata, K.},
-    isbn={9780130432452},
-    lccn={2001021683},
-    year={2002},
-    publisher={Prentice Hall}
-  }
-  @article{rizvi2017general,
-    title={A general-purpose graphics processing unit (gpgpu)-accelerated robotic controller using a low power mobile platform},
-    author={Rizvi, Syed Tahir Hussain and Cabodi, Gianpiero and Patti, Denis and Gulzar, Muhammad Majid},
-    journal={Journal of Low Power Electronics and Applications},
-    volume={7},
-    number={2},
-    pages={10},
-    year={2017},
-    publisher={Multidisciplinary Digital Publishing Institute}
-  }
-  @article{abramov2012real,
-    title={Real-time segmentation of stereo videos on a portable system with a mobile gpu},
-    author={Abramov, Alexey and Pauwels, Karl and Papon, Jeremie and Worgotter, Florentin and Dellen, Babette},
-    journal={IEEE Transactions on Circuits and Systems for Video Technology},
-    volume={22},
-    number={9},
-    pages={1292--1305},
-    year={2012},
-    publisher={IEEE}
-  }
-  @inproceedings{jaramillo2019visual,
-    title={Visual saliency with foveated images for fast object detection and recognition in mobile robots using low-power embedded GPUs},
-    author={Jaramillo-Avila, Uziel and Aitken, Jonathan M and Anderson, Sean R},
-    booktitle={2019 19th International Conference on Advanced Robotics (ICAR)},
-    pages={773--778},
-    year={2019},
-    organization={IEEE}
-  }
-  @inproceedings{satria2016real,
-    title={Real-time system-level implementation of a telepresence robot using an embedded GPU platform},
-    author={Satria, Muhammad Teguh and Gurumani, Swathi and Zheng, Wang and Tee, Keng Peng and Koh, Augustine and Yu, Pan and Rupnow, Kyle and Chen, Deming},
-    booktitle={2016 Design, Automation \& Test in Europe Conference \& Exhibition (DATE)},
-    pages={1445--1448},
-    year={2016},
-    organization={IEEE}
-  }
+
 \end{filecontents}
 
-\title{\LARGE \bf
-Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs
-}
+\definecolor{c00FFFF}{RGB}{0,255,255}
+
+\begin{document}
+
+\title{Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots}
 
@@
 \author{
-  Adam Seewald$^{1}$, Hector Garcia de Marina$^{2}$, and Ulrik Pagh Schultz$^{1}$
-  \thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).
+  Adam Seewald$^{\text{1}}$, Hector Garcia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
+  %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
+  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
+  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
+  \thanks{$^{\text{1}}$A.
+S., H.
+S.
+M., and U.
+P.
+S.
+are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense.
+Email: {\tt\footnotesize ads@mmmi.sdu.dk};}
+  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
+  \thanks{Digital Object Identifier (DOI): see top of this page.}
 }
-  \thanks{$^{1}$Adam Seewald, Ulrik Pagh Schultz are with the SDU UAS Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense, Denmark.
-Email: {\tt\small ads@mmmi.sdu.dk}.}
-  \thanks{$^{2}$Hector Garcia de Marina is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
-}
-
-\definecolor{c00FFFF}{RGB}{0,255,255}
-
-\begin{document}
+
+\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted Month, Year}
+{Seewald \MakeLowercase{\textit{et al.}}: Planning-Scheduling for Aerial Robots} 
+% Use only for final RAL version
 
@@
 \maketitle
-
-\thispagestyle{empty}
-\pagestyle{empty}
 
@@
 \end{abstract}
+
+\begin{IEEEkeywords}
+  Aerial Systems: Perception and Autonomy, Optimization and Optimal Control, Planning, Scheduling and Coordination, Planning under Uncertainty
+\end{IEEEkeywords}
 
@@
                         %
-Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets.
-A typical example of these scenarios is a UAV following a path and performing some on-board computational tasks.
-For instance, the UAV might detect ground patterns and notify other ground-based actors with little human interaction.
-We refer to such computational tasks that can be dynamically replanned and adapted as \emph{computations}.
-We are interested in the energy optimization of the path and computations under uncertainty (atmospheric interferences) and refer to it as energy-aware dynamic planning.
-Such planning would find optimal tradeoffs between the path, computations, and energy requirements.
-Current generic planning solutions for outdoor UAVs do not plan the path and computations dynamically, nor are they energy-aware.
-They are often semi-autonomous: the path and computations are static and usually defined using planning software~\cite{daponte2019review} (for instance~\cite{papa} and~\cite{px4}).
-Such a state of practice has prompted us to propose an \emph{energy-aware dynamic planning algorithm} for UAVs.
-The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV planning problem.
+\IEEEPARstart{U}{se cases} involving aerial robots span broadly.
+They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets.
+A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some on-board computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
+Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}).
+Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
+In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
+We refer to computational tasks that can be scheduled with an energy impact as computations.
+We are interested in the simultaneous energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling.
+Generic mobile robotics studies that deal with planning-scheduling energy awareness are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}.
+Yet, aerial robots are particularly affected by various energy considerations.
+Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}.
+Such a state of practice has prompted us to propose a planning-scheduling approach for autonomous aerial robots.
+It combines the past body of knowledge, addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
+Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
+Figure~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t.
+the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defect~(\ref{sth:iii}).
 
@@
   \centering
+  \vspace*{-6.5ex}
   \begin{tikzpicture}
     \node[inner sep=0pt] () at (0,0)
-        {\footnotesize \input{\figpath/il_abs.tikz}};
-    \node[inner sep=0pt] () at (-1.9,-5.5)
-        {\footnotesize \input{\figpath/il_abs_energy1.tikz}};
-    \node[inner sep=0pt] () at (1.9,-5.5)
-        {\footnotesize \input{\figpath/il_abs_spectrum1.tikz}};
+        {\scriptsize \input{\figpath/new/il_abs.tikz}};
+    \node[inner sep=0pt] () at (-2,-5.67)
+        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
+    \node[inner sep=0pt] () at (2.1,-5.67)
+        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
   \end{tikzpicture}
-  \caption{Dynamic replanning of an agricultural scenario in terms of the path and computations simultaneously.
-An initial plan~(in~\ref{sth:i}) is adapted computation-wise~(in~\ref{sth:ii}) and path-wise~(in~\ref{sth:iii}).
-In the bottom left, the collected energy data of a physical UAV (Opterra fixed-wing drone) flying the scenario is shown along its power spectrum.}
+  \caption{An illustrative example of planning-scheduling.
+An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}).
+Follow the collected energy data of a physical aerial robot flying the use case.}
   \label{fig:il-abs}
+  \vspace*{-4.5ex}
 \end{figure}
 
-Planning algorithms literature for mobile robots includes topics such as trajectory generation and path planning.
-Generally, the algorithms select an energy-optimized trajectory~\cite{mei2004energy}, e.g., by maximizing the operational time~\cite{wahab2015energy}.
-However, they apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence for the energy consumption also being significantly influenced by computations~\cite{mei2005case}.
-Given the availability of powerful GPU-equipped mobile hardware~\cite{rizvi2017general}, the use of computations is expected to increase in the near future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
-More complex planning, which includes a broader concept of the plan being a set of tasks and a path, all focus on the trajectory~\cite{mei2005case,mei2006deployment} and apply to a small number of robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
-For UAVs specifically, rotorcrafts have also gained interest in terms of algorithms for energy-optimized trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}.
-
-Unlike most of the past planning algorithms literature, our algorithm plans the path and computations simultaneously.
-To model the path we use multiple mathematical functions.
-In Figure~\ref{fig:il-abs}, the path contains multiple circles and lines.
-To model the computations we use \powprof{}, a profiling tool presented in previous work~\cite{seewald2019coarse}.
-To guide the UAV we use a vector field~\cite{de2017guidance} that converges to the path.
-The use of vector fields for guidance is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding,de2017guidance}.
-
-To achieve the energy-aware dynamic planning, we further introduce and formally prove a periodic energy model that accounts for the uncertainty.
-We use Fourier analysis to derive the model, and state estimation to address the uncertainty.
-Periodicity is often present due to repetitive patterns in the plan~\cite{seewald2020mechanical}.
-Indeed, UAV scenarios often iterate over a set of tasks and paths (e.g., monitoring or search and rescue).
-Given that the plan is periodic, we expect the energy consumption to approximately evolve periodically.
-In Figure~\ref{fig:il-abs}, some collected energy data from a UAV flying a survey scenario along its power spectrum motivates our choice.
-
-In the spirit of reducing costs and resources, we showcase the algorithm using dynamic planning for a precision agriculture fixed-wing UAV.
-Precision agriculture is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}.
-The plan is structured as follows.
-Path-wise, the UAV flies in circles and lines covering a polygon.
-Computation-wise, it detects hazards using a neural network and notifies grounded mobile robots employed for, e.g., harvesting.
-The algorithm alters the plan; it controls the processing rate and the radius of the circles (affecting the distance between the lines).
-Figure~\ref{fig:il-abs} shows such plan.
-%We observe that not only the path but also the computations significantly impact the energy, with a potential extension of up to 13 minutes over an hour by switching from the highest to the lowest level of computations in presence of a standard battery (see Section~\ref{sec:experimental}).
-
-The remainder of the paper is organized as follows.
-The overview of dynamic planning, some preliminaries, and problem definition are provided in Section~\ref{sec:prob}.
-We show a suitable model for the energy in Section~\ref{sec:energy-model}, and propose the algorithm in Section~\ref{sec:algo}.
-In Section~\ref{sec:experimental}, we present the results and showcases the performances.
-We then derive some conclusions in Section~\ref{sec:conclusion}.
-Finally, we provide some additional information in Appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Planning Overview}  %
+There are numerous planning algorithms applied to a variety of robots.
+An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}.
+Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
+In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
+In this context, planning-scheduling energy awareness is a recent research direction.
+Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
+These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}.
+We extend the relevant literature to the case of CPP with aerial robots.
+
+Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering.
+Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}.
+Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa.
+The occurrence happens frequently with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
+It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
+
+To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc).
+Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
+Both the variations trajectories are derived for future time instants employing computations and motion energies and battery models.
+The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules.
+In Figure~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in the energy models for the computations, motion, and battery models in Section~\ref{sec:energy-model}.
+
+The remaining sections of the letter are then organized as follows. Section~\ref{sec:prob} provides basic constructs. These include the concepts of %computations and motion energies, 
+plan, stages, triggering and final points, and path functions, as well as the problem formulation.
+Section~\ref{sec:algo} describes in detail the planning-scheduling.
+Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives.
+Appendices provide supplementary information.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Problem Formulation}  %
 \label{sec:prob}               %
                                %
-The algorithm inputs a user-specified initial plan that consist of different stages.
+\begin{figure}[t]
+  \footnotesize
+  \begin{minipage}[l]{0.35\columnwidth}
+    \caption{Definitions \ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$.
+$\mathbf{p}_{\Gamma_1},\dots$ are triggering points, in which proximity happens change of stages $\Gamma_1,\dots$.
+Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
+    \label{fig:traj1}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.6\columnwidth}
+    \centering
+    \vspace*{-4.5ex}
+    \input{\figpath/new/traj1.tikz}
+  \end{minipage}
+  \vspace*{-3.5ex}
+\end{figure}
+
+Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries.
+For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.
+
+%---
+
+\subsection{Preliminaries}
+\label{sec:prelim}
+
+\begin{defn}[Plan]\label{def:plan}
+  Given a generic point $\mathbf{p}(t)\in\mathbb{R}^2$ w.r.t.
+a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
+    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
+    \Gamma_i & \text{otherwise}
+  \end{cases}.\end{equation*}
+\end{defn}
+
+Here, $\Gamma_i$ are \emph{stages}, and $\mathbb{Z}$ indicates the set of integers.
+At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
+Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.
+$\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and
+after Definition~\ref{def:trigs}.
+
+\begin{defn}[Stage]\label{def:stage}
+  The $i$th \emph{stage} $\Gamma_i$ at time instant $t$ of a plan $\Gamma$ is
+  \begin{equation*}\begin{split}
+    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
+    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
+      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
+  \end{split}\end{equation*}
+  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}.
+$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
+\end{defn}
+
+The notation $[\,\cdot\,]$ indicates positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
+For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.
+
+The function $\varphi_i$ is the \emph{path function}, specifying the path.
+These are stage-dependent mathematical functions the aerial robot tracks as it travels the motion for the coverage.
+The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bound of a parameter $\cdot\,$, i.e.,
+\begin{equation}
+  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
+\end{equation}
+
+\begin{defn}[Path functions]
+  \label{def:paths}
+  $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}%\,\forall i\in\{1,2,\dots\}
+  $ are \emph{path functions}, forming the path. They are a function of $\mathbf{p}(t)$ and path parameters $c_i^\rho(t)$ and are continuous and twice differentiable.
+\end{defn}
+
+The change of stages happens in the proximity of given points termed \emph{triggering points}, whereas the plan is complete at the occurrence of the \emph{final point}.
+
+\begin{defn}[Triggering and final points]
+  \label{def:trigs}
+  The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ allows the transition between stages.
+The \emph{final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
+\end{defn}
+
+The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
+
+Figure \ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:plan}--\ref{def:trigs}.
+$\varphi_1,\dots,\varphi_6$ are path functions.
+$\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
+They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
+The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure.
+The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
+
+A convenient way of defining $\Gamma$ is specifying a set of stages, a shift, and a final point. The set is termed \emph{primitive stages} and iterated with the shift up to reaching the final point.
+
+\begin{defn}[Primitive stages]
+  \label{def:primitive}
+  Given the number of \emph{primitive stages} $n\in\mathbb{Z}_{>0}$, a \emph{shift} $\mathbf{d}\in\mathbb{R}^2$, and a final point $\mathbf{p}_{\Gamma_l}$, the stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ %with the path functions $\varphi_1,\dots\varphi_n$ and the parameters $c_1,c_2,\dots,c_n$
+  are primitive if they form the remainder of the plan with $\mathbf{d}$ up to $\mathbf{p}_{\Gamma_l}$. 
+\end{defn}
+
+Here, $c_i$ indicates a row vector that contains both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$, where $\,\cdot\,'$ is the transpose of $\cdot\,$.
+The path parameters in the definition have a constant distance per each value in $[n]_{>0}$, i.e.,
+\begin{equation}\label{eq:primitive}\begin{split}
+  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
+\end{split}\end{equation}
+holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$.
+$e_j\in\mathbb{R}$ given a shift $\mathbf{d}$, initial point $\mathbf{p}$, and initial value of path parameters $c_1^\rho$.
+
+\begin{figure}[h!]
+  \center
+  \vspace*{-2.2ex}
+  \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
+    \footnotesize
+    \node[state,initial] (q_i) {$\Gamma_1$}; 
+    \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
+    \node        [right=of q_2] (q_dots0) {$\cdots$};
+    \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
+    \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
+    \path[->]
+    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
+    (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
+    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
+    (q_0) edge [bend right=65] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
+    (q_i) edge [bend left=-65] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+    (q_2) edge [bend left=-45] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+    (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
+    (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
+    (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
+    (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
+    (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
+    ; %end path 
+    %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
+    %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
+  \end{tikzpicture}
+  \vspace*{-2.3ex}
+  \caption[Definition of a plan with a loop]{Definition of a plan $\Gamma$ with periodic patterns.
+Stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$ are iterated with a shift $\mathbf{d}$.}
+  \vspace*{-1ex}
+  \label{fig:state-machine-loop}
+\end{figure}
+
+Figure \ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}.
+A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
+$t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{\geq 0}$.
+$\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.
+
+\subsection{Problem formulation}
+\label{sec:pbfor}
+
+The problem of planning-scheduling is composed of two sub-problems.
+One is to form a static plan that visits each point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.
+
+\begin{pb}[Coverage problem]
+  \label{pb:cov-pb}
+  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each vertex $v_i:=(x_{v_i},y_{v_i}),\forall i\in[|v|]_{>0}$
+  %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
+  is a point w.r.t.
+$\mathcal{O}_W$.
+Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the minimum turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given.
+The \emph{coverage problem} is the problem of finding a plan $\Gamma$ that covers the polygon.
+\end{pb}
+
+For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ indicates the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
+.
+
+\begin{pb}[Planning problem]
+  \label{pb}
+  Consider an initial plan $\Gamma$ in Definition~\ref{def:plan}.
+The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
+\end{pb}
+
+%The algorithm inputs a user-specified initial plan that consist of different stages.
 At each stage the plan contains some parameters that allow to alter the path and computations along an energy budget.
@@
 
-The algorithm outputs the control (the parameters) using model predictive control (MPC)~\cite{rawlings2017model} where it checks the satisfaction of the battery constraints.
+%The algorithm outputs the control (the parameters) using model predictive control (MPC)~\cite{rawlings2017model} where it checks the satisfaction of the battery constraints.
 The control is data-driven.
@@
 
-\subsection{Plan definition}
-\label{sec:prelim}
-
-Let us adopt the following mathematical notation.
+%\subsection{Plan definition}
+%\label{sec:prelim}
+
+%Let us adopt the following mathematical notation.
 Given an integer $a$, $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$.
@@
 
-Let us assume that the path at stage $i$ can be altered with $\rho$ path parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computation parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
+%Let us assume that the path at stage $i$ can be altered with $\rho$ path parameters $c_i^\rho:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$, and the computations with $\sigma$ computation parameters $c_i^\sigma:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,c_{i,\rho+\sigma}\}$.
 We then express the path as a continuous twice differentiable function $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}$ of a point and the path parameters.
@@
 
-\begin{defn}[Stage, plan, triggering, and final point]\label{def:mission}
-  The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined
-  \begin{equation*}\begin{split}
-    \Gamma_i:=\{\varphi_i(\mathbf{p}_k,c_i^\rho),c_i^\sigma\mid
-    \,&\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_i^\rho)\in\mathcal{C}_i,\,\\
-      &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathcal{S}_{i,j}\,\},
-  \end{split}\end{equation*}
-  where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the path constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
+%\begin{defn}[Stage, plan, triggering, and final point]\label{def:mission}
+%  The $i$-th \emph{stage} $\Gamma_i$ at time instant $k$ of a plan $\Gamma$ is defined
+%  \begin{equation*}\begin{split}
+%    \Gamma_i:=\{\varphi_i(\mathbf{p}_k,c_i^\rho),c_i^\sigma\mid
+%    \,&\exists\,\,\mathbf{p}_k,\,\varphi_i(\mathbf{p}_k,c_i^\rho)\in\mathcal{C}_i,\,\\
+%      &\,\forall j\in[\sigma]^+,\,c_{i,\rho+j}\in\mathcal{S}_{i,j}\,\},
+%\end{split}\end{equation*}
+%where $\mathcal{C}_i:=[\underline{c}_i,\overline{c}_i]\subseteq\mathbb{R}$ is the path constraint set, and $\mathcal{S}_{i,j}:=[\underline{c}_{i,\rho+j},\overline{c}_{i,\rho+j}]\subseteq\mathbb{Z}_{\geq 0}$ the $j$-th computation constraint set.
 $\mathbf{p}_k$ is a point of a UAV flying at an altitude $h\in\mathbb{R}_{>0}$
 %\footnote{The altitude might change at different flying phases and under different atmospheric conditions}
-  w.r.t.
-some inertial navigation frame $\mathcal{O}_W$.
-In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are paths.
+%w.r.t. some inertial navigation frame $\mathcal{O}_W$.
+
+%In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are paths.
 $\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
@@
 
-  \begin{figure}[t]
-    \centering
-    \footnotesize
-    \input{\figpath/traj1.tikz}
-    \caption{Definition notation shown on an initial slice of the plan in Figure~\ref{fig:il-abs}.}
-    \label{fig:traj1}
-  \end{figure}
-
-  The \emph{plan} is a finite state machine (FSM) $\Gamma$ where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
-  \begin{equation*}s(\Gamma_i,\mathbf{p}_k):=\begin{cases}
-    \Gamma_{i+1} & \text{if }\mathbf{p}_k=\mathbf{p}_{\Gamma_i}\\
-    \Gamma_i & \text{otherwise}
-  \end{cases}.\end{equation*}
-  The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
+%The \emph{plan} is a finite state machine (FSM) $\Gamma$ where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+%\begin{equation*}s(\Gamma_i,\mathbf{p}_k):=\begin{cases}
+%  \Gamma_{i+1} & \text{if }\mathbf{p}_k=\mathbf{p}_{\Gamma_i}\\
+%  \Gamma_i & \text{otherwise}
+%\end{cases}.\end{equation*}
+%The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
 In Figure~\ref{fig:traj1}, $\mathbf{p}_{\Gamma_1}$ allows the transition between $\Gamma_1$ and $\Gamma_2$, $\mathbf{p}_{\Gamma_4}$ between $\Gamma_4$ and $\Gamma_5$, and $\mathbf{p}_{\Gamma_5}$ between $\Gamma_5$ and $\Gamma_6$.
 The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$ is called \emph{final point}.
-\end{defn}
-
-\begin{figure}[h]
-  \center
-  \begin{tikzpicture}[shorten >=.5pt,node distance=10.5ex,on grid,auto]
-    \footnotesize
-    \node[state,initial] (q_i) {$\Gamma_1$}; 
-    \node        [right=of q_i] (q_dots0) {$\cdots$};
-    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
-    \node        (q_dots1) [right=of q_0] {$\cdots$};
-    \node[state,accepting] (q_f) [right=of q_dots1] {$\Gamma_f$};
-    \path[->]
-    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_dots0)
-    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
-    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_dots1)
-    (q_dots1) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
-    (q_i) edge [loop above] node {$\mathbf{p}_{k_1}$} (q_i)
-    (q_0) edge [loop above] node {$\mathbf{p}_{k_2}$} (q_0)
-    (q_f) edge [loop above] node {$\mathbf{p}_{k_3}$} (q_f)
-    ; %end path 
-    \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
-    (q_i.south west) -- (q_f.south west) node [black,midway,yshift=-9ex]{$\Gamma$};
-  \end{tikzpicture}
-  \caption{The plan defined as a FSM}
-  \label{fig:state-machine}
-\end{figure}
-
-A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages with the FSM.
+%\end{defn}
+
+%\begin{figure}[h]
+%  \center
+%  \begin{tikzpicture}[shorten >=.5pt,node distance=10.5ex,on grid,auto]
+%    \footnotesize
+%    \node[state,initial] (q_i) {$\Gamma_1$}; 
+%    \node        [right=of q_i] (q_dots0) {$\cdots$};
+%    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
+%    \node        (q_dots1) [right=of q_0] {$\cdots$};
+%    \node[state,accepting] (q_f) [right=of q_dots1] {$\Gamma_f$};
+%    \path[->]
+%    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_dots0)
+%    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
+%    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_dots1)
+%    (q_dots1) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
+%    (q_i) edge [loop above] node {$\mathbf{p}_{k_1}$} (q_i)
+%    (q_0) edge [loop above] node {$\mathbf{p}_{k_2}$} (q_0)
+%    (q_f) edge [loop above] node {$\mathbf{p}_{k_3}$} (q_f)
+%    ; %end path 
+%    \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
+%    (q_i.south west) -- (q_f.south west) node [black,midway,yshift=-9ex]{$\Gamma$};
+%  \end{tikzpicture}
+%  \caption{The plan defined as a FSM}
+%  \label{fig:state-machine}
+%\end{figure}
+
+%A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages with the FSM.
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to the stage $\Gamma_i$.
@@
 
-\subsection{Problem formulation}
-
-In order to simplify the problem formulation, we consider some primitive paths. All the other paths are built from these paths with a shift $\mathbf{d}:=(x_d,y_d)$.
-
-Given $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) primitive paths $\varphi_1,\dots\varphi_n$, a generic starting point $\mathbf{p}$ and the current levels of the path parameters $c_1^\rho$, all the other paths $\varphi_{n+1},\dots,\varphi_l$ are built
-\begin{equation}\label{eq:primitive}\begin{split}
-  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
-\end{split}\end{equation}
-$\forall i\in[l/n-1]^+,j\in[n]^+$, where $e_j\in\mathbb{R}$ is the $j$-th constant difference.
-
-\begin{defn}[Period]\label{def:period}
-  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Equation~(\ref{eq:primitive}).
-\end{defn}
-
-The algorithm measures the time between the paths and assumes the initial period is one. The periods might be different for different $j$s due to atmospheric interferences.
-
-One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Equation~(\ref{eq:primitive}).
+%\subsection{Problem formulation}
+
+%In order to simplify the problem formulation, we consider some primitive paths. All the other paths are built from these paths with a shift $\mathbf{d}:=(x_d,y_d)$.
+
+%Given $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) primitive paths $\varphi_1,\dots\varphi_n$, a generic starting point $\mathbf{p}$ and the current levels of the path parameters $c_1^\rho$, all the other paths $\varphi_{n+1},\dots,\varphi_l$ are built
+%\begin{equation}\label{eq:primitive}\begin{split}
+%  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\\ &\,\,\,\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
+%\end{split}\end{equation}
+%$\forall i\in[l/n-1]^+,j\in[n]^+$, where $e_j\in\mathbb{R}$ is the $j$-th constant difference.
+
+%\begin{defn}[Period]\label{def:period}
+%  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Equation~(\ref{eq:primitive}).
+%\end{defn}
+
+%The algorithm measures the time between the paths and assumes the initial period is one. The periods might be different for different $j$s due to atmospheric interferences.
+
+%One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Equation~(\ref{eq:primitive}).
 If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Figure~\ref{fig:il-abs}).
 
-\begin{pb}[UAV planning problem]\label{pb}
-  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}.
+%\begin{pb}[UAV planning problem]\label{pb}
+%  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}.
 We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
-\end{pb}
+%\end{pb}
 
@@
                                  %
-\section{Periodic Energy Model}  %
+\section{Energy Models}  %
 \label{sec:energy-model}         %
                                  %
-We refer to the instantaneous energy consumption evolution simply as the energy signal.
+The solution to Problem~\ref{pb} requires accurate energy models, predicting the impact of given path and computations parameters on the battery at future time instants.
+To this end, Sections~\ref{sec:mod-mot}--\ref{sec:mod-bat} provide models for the motion and computations energies and battery.
+
+\subsection{Energy model for the motion}
+\label{sec:mod-mot}
+
+Let us return to the collected energy data and spectrum analysis in Figure~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
+Energy data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
+It indicates that to model the energy, three frequencies are adequate.
+
+%We refer to the instantaneous energy consumption evolution simply as the energy signal.
 We model the energy using energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize such energy signal.
@@
 
-We prove a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
+%We prove a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
 We show after the main results how this approach allows us variability in terms of non-periodic signals.
 
-After having illustrated the energy model, we enhance it with the energy contribution of the path in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
-
-Let us consider a periodic energy signal of period $T$, and a Fourier series of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of modeling of the energy signal
+%After having illustrated the energy model, we enhance it with the energy contribution of the path in Subsection~\ref{sec:model}, and of the computations in Subsection~\ref{sec:computations-model}.
+
+An intuitive way of modeling the energy data is thus a Fourier series of a given order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{R}_{>0}$
 \begin{equation}\label{eq:fourier}
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the Fourier series coefficients.
-
-The energy signal can be modeled by Equation~(\ref{eq:fourier}) and by the output of a linear model
-\begin{equation}\label{eq:state-perf}\begin{split}
-  \dot{\mathbf{q}}&=A\mathbf{q}+B\mathbf{u},\\
-  y&=C\mathbf{q},
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the series coefficients.
+
+The model in Equation~(\ref{eq:fourier}) does not the quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules results in different instantaneous energy.
+For this latter purpose, we use another model
+\begin{subequations}\label{eq:state-perf}\begin{align}
+  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t),\label{eq:state-perf-q}\\
+  y(t)&=C\mathbf{q}(t),\label{eq:state-perf-y}
+\end{align}\end{subequations}
+where $y(t)\in\mathbb{R}$ is the instantaneous energy consumption. The state $\mathbf{q}\in\mathbb{R}^m$ with $m:=2r+1$ contains energy coefficients
+\begin{equation}
+  \mathbf{q}(t)=\begin{bmatrix}
+    \alpha_0(t) & \alpha_1(t) & \beta_1(t) & \cdots & \alpha_r(t) & \beta_r(t)
+  \end{bmatrix}'.
+\end{equation}
+
+The state transition matrix
+\begin{equation}\label{eq:mat_A}
+  A=\begin{bmatrix}
+    0            & 0^{1\times 2}& \dots & 0^{1\times 2} \\
+    0^{2\times 1}& A_1          & \dots & 0^{2\times 2} \\
+    \vdots       & \vdots       & \ddots& \vdots        \\
+    0^{2\times 1}& 0^{2\times 2}& \dots & A_r 
+  \end{bmatrix},\,\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},
+\end{equation}
+where $A\in\mathbb{R}^{m\times m}$ contains $r$ sub-matrices $A_j$ and $0^{i\times j}$ is a zero matrix of $i$ rows and $j$ columns.
+In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros.
+
+The output matrix\vspace*{-2ex}
+\begin{equation}\label{eq:mat_C}
+  C=(1/T)\Big[1 \,\,\, \overbrace{\begin{matrix}1 & 0 &\cdots & 1 & 0\end{matrix}}^{2r}\Big],
+\end{equation}
+where $C\in\mathbb{R}^m$ (the first value in the first column is one, the pattern one--zero is then repeated $2r$ times).
+
+%\begin{equation}\label{eq:state-details}\begin{split}
+%  A&=\left[\begin{array}{cccc}
+%    0&                     &       & \makebox(-5,-5){*}  \\
+%     & A_1                 &       &  \\
+%     & \makebox(-25,-15){*}& \ddots&  \\
+%     &                     &       & A_r 
+%  \end{array}\right],\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},\\
+%  C&=(1/T)\left[\begin{array}{cccccc}
+%    1 & 1 & 0 &\cdots & 1 & 0
+%  \end{array}\right],
+%\end{split}\end{equation}
+%where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transition matrix, and $C\in\mathbb{R}^m$ is the output matrix.
+In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros (*).
+
+%The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
+
+Under some conditions, the models in Equations~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal.
+
+\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Equations~(\ref{eq:mat_A}--\ref{eq:mat_C}), and the initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
+  \begin{equation*}
+  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}'.
+  \end{equation*} 
+  $h$ in Equations~(\ref{eq:fourier}) is equal to $y$ in Equation~(\ref{eq:state-perf}).
+\end{lem}
+%\begin{proof}
+%The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess.
+%\end{proof}
+%Appendix~\ref{app:proof-eqv} contains a proof of Lemma~\ref{lem:eqv}.
+
+To define the nominal control and the output matrix, we exploit the effect of variation of path and computations parameters on the energy. 
+%We assume a variation in computations parameters $c_i^\sigma$ affects the instantaneous energy, i.e., different schedules of power-demanding computational tasks have different power drains from the computing hardware.
+
+\begin{lem}[Parameters, energy relation]\label{lem:new}
+  Given $c_i(t)$ parameters at two following time instants $t\in\{t_j,t_{j+1}\}\subset\mathbb{R}_{\geq 0}$ s.t.
+$t_j<t_{j+1}$ for an arbitrary stage $\Gamma_i$, a change in parameters $c_i(t_j)\neq c_i(t_{j+1})$ results in different overall and instantaneous energies for path and computations parameters respectively.
+\end{lem}
+
+Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains proofs of Lemmas~\ref{lem:eqv}--\ref{lem:new}.
+
+Using the same notation from Lemma~\ref{lem:new}, the nominal control in Equation~(\ref{eq:state-perf})
+\begin{equation}
+  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
+\end{equation}
+for all time instants. $\hat{\mathbf{u}}$ is then a scale transformation
+\begin{equation}
+  \hat{\mathbf{u}}(t):=\mathrm{diag}(\nu_i)c_i(t)+\tau_i
+\end{equation}
+where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere.
+$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Definition~\ref{def:stage}) to time and power domains.
+
+Let us assume that the time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
+  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
+  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
+\end{align}\end{subequations} 
+$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$.
+
+Similarly to Equation~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with scaling factors
+\begin{subequations}\label{eq:scale-comp}\begin{align}
+  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
+  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
+\end{align}\end{subequations}
+$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Section~\ref{sec:mod-com} and quantifies the power of the computing hardware.
+
+The input matrix then includes the change in energy, i.e.,
+\begin{equation}\label{eq:mat_B}
+  B=\begin{bmatrix}
+      0^{1\times\rho} & 1      & \cdots & 1      \\
+      0^{1\times\rho} & 0      & \cdots & 0      \\ 
+      \vdots          & \vdots & \ddots & \vdots \\
+      0^{1\times\rho} & 0      & \cdots & 0   
+  \end{bmatrix},
+\end{equation}
+where $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
+
+\subsection{Energy model for the computations}
+\label{sec:mod-com}
+
+Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware or software specific parameters.
+This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis aiding to quantify the computations energy of any combination of computations $c_i^\sigma$ withing the bounds (see Definition~\ref{def:stage}).
+
+The model relies on an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source M.I.T.
+license.
+It is segmented into two layers.
+In the \emph{measurement layer} the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piece-wise linear regression.
+
+Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperometer, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
+
+\begin{defn}[Measurement layer]\label{def:meas}
+  Given a measuring device, computations parameters, and initial and final time instants, the \emph{measurement layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
+\end{defn}
+
+Here, the notation $\mathcal{T}$ encloses all the time intervals from initial $t_0$ to final $t_f$, i.e., $\mathcal{T}:=[t_0,t_f]$.
+
+\begin{defn}[Predictive layer]\label{def:pred}
+  Given a measuring device and computations parameters the \emph{predictive layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns and energy measure.
+\end{defn}
+
+The energy measures in Definitions~\ref{def:meas}--\ref{def:pred} can be either average or overall energy.
+Additionally, the tool supports the measures of battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}.
+The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Equation~(\ref{eq:scale-comp}) assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
+\begin{equation}\label{eq:piece-wise-reg}\begin{split}
+  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
 \end{split}\end{equation}
-where $y\in\mathbb{R}$ is the instantaneous energy consumption.
-
-The state $\mathbf{q}$ contains the energy coefficients
-\begin{equation}\label{eq:state-details}\begin{split}
-  \mathbf{q}&=\left[\begin{array}{cccccc}
-    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
-  \end{array}\right]^T,\\
-  A&=\left[\begin{array}{cccc}
-    0&                     &       & \makebox(-5,-5){*}  \\
-     & A_1                 &       &  \\
-     & \makebox(-25,-15){*}& \ddots&  \\
-     &                     &       & A_r 
-  \end{array}\right],\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},\\
-  C&=(1/T)\left[\begin{array}{cccccc}
-    1 & 1 & 0 &\cdots & 1 & 0
-  \end{array}\right],
-\end{split}\end{equation}
-where $\mathbf{q}\in\mathbb{R}^m$ with $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transition matrix, and $C\in\mathbb{R}^m$ is the output matrix.
-In matrix $A$, the top left entry is zero, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zeros (*).
-
-The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
-
-\begin{lem}[Signal, output equality]\label{lem:eqv}Suppose control $\mathbf{u}$ is a zero vector, matrices $A,C$ are described by Equation~(\ref{eq:state-details}), and the initial guess $\mathbf{q}_0$ is
+where the notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
+The measuring device in both $\mathbf{g}$ and $g$ is implicit.
+
+\subsection{Battery model}
+\label{sec:mod-bat}
+
+The battery model predicts the battery SoC in function of a given load for future time instants.
+There are multiple possible models in the literature~\cite{rao2003battery}, with varying accuracy, complexity, and easy of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of ease of implementation and accuracy.
+
+We model a Li-ion battery of an aerial robot flying with an abstract model referred to as ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+
+\begin{lem}[Battery SoC]\label{lem:bat}
+  Given the internal battery voltage $V\in\mathbb{R}$ measured in volts, resistance $R_r$ in ohms, constant nominal capacity $Q_c$ in amperes per hour, and a battery coefficient $k_b$, the \emph{battery SoC} evolves
   \begin{equation*}
-  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}^T.
+    \dot{b}(y(t))=-k_b\left(V-
+  \sqrt{
+    V^2-
+    4R_ry(t)}
+  \right)/(2R_rQ_c).
   \end{equation*}
-  Then, the signal $h$ in Equation~(\ref{eq:fourier}) is equal to the output $y$ in Equation~(\ref{eq:state-perf}).
 \end{lem}
-\begin{proof}
-The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
-We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess.
-\end{proof}
+
+Appendix~\ref{app:proof-bat} contains a proof of Lemma~\ref{lem:bat}.
+
+Equation~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$. Let us re-evaluate the output constraint with Lemma~\ref{lem:bat}.
+
+\begin{defn}[Output constraint]
+  \label{def:const}
+  \begin{equation*}
+    \mathcal{Y}(t):=\{y\mid y\in[0,b(y(t))Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+  \end{equation*}
+  is the \emph{output constraint}, where $b(y(t))Q_cV$ is the maximum instantaneous energy consumption.
+\end{defn}
 
@@
 
-Let us suppose that at time instant $k$ the plan reached the $i$-th stage $\Gamma_i$ and the control
-\begin{equation}\label{eq:state-control2}
-  \mathbf{u}_k=\begin{bmatrix}c_k^\rho & c_k^\sigma\end{bmatrix}^T,
-\end{equation}
-where $\mathbf{u}_k\in\mathbb{R}^n$ with $n=\rho+\sigma$ differs from the nominal control $\mathbf{u}$ in Equation~(\ref{eq:state-perf}).
+%Let us suppose that at time instant $k$ the plan reached the $i$-th stage $\Gamma_i$ and the control
+%\begin{equation}\label{eq:state-control2}
+%  \mathbf{u}_k=\begin{bmatrix}c_k^\rho & c_k^\sigma\end{bmatrix}^T,
+%\end{equation}
+%where $\mathbf{u}_k\in\mathbb{R}^n$ with $n=\rho+\sigma$ differs from the nominal control $\mathbf{u}$ in Equation~(\ref{eq:state-perf}).
 We include the control in the nominal control exploiting the following observation.
 
-We observe that a change in path parameters affects the energy indirectly.
+%We observe that a change in path parameters affects the energy indirectly.
 It alters the time when the UAV reaches the final point $\mathbf{p}_{\Gamma_l}$.
@@
 
-The nominal control and the input matrix
-\begin{equation}\label{eq:state-control}\begin{split}
-  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),\,\,\,\hat{\mathbf{u}}_k:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i,\\
-  B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ 
-    & & & \makebox(-15,-3){*} & &\end{bmatrix}.
-\end{split}\end{equation}
-The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros (*) except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
+%The nominal control and the input matrix
+%\begin{equation}\label{eq:state-control}\begin{split}
+%  \mathbf{u}&=(\hat{\mathbf{u}}_k-\hat{\mathbf{u}}_{k-1}),\,\,\,\hat{\mathbf{u}}_k:=\mathrm{diag}(\nu_i)\mathbf{u}_k+\tau_i,\\
+%  B&=\begin{bmatrix} 0 & \cdots & 0 & 1 & \cdots & 1 \\ 
+%    & & & \makebox(-15,-3){*} & &\end{bmatrix}.
+%\end{split}\end{equation}
+%The matrix $B\in\mathbb{R}^{m\times n}$ contains zeros (*) except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
 $\hat{\mathbf{u}}_k$ is a scale transformation with $\nu_i=\begin{bmatrix}\nu_i^\rho & \nu_i^\sigma\end{bmatrix}^T$ and $\tau_i=\begin{bmatrix}\tau_i^\rho & \tau_i^\sigma\end{bmatrix}^T$ scaling factors quantifying the contribution to the plan of a given parameter in terms of time for the first $\rho$ parameters, and power for the remaining $\sigma$ (we use the same notation for the path and computation scaling factors as for the parameters).
@@
 
-We clarify how we derive the factors $\nu_i,\tau_i$ in the next two subsections.
-
-\subsection{Path parameters energy contribution}
-\label{sec:model}
-
-\begin{figure}[h]
-  \centering
-  \footnotesize
-  \input{\figpath/traj2.tikz}
-  \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Figure~\ref{fig:il-abs}).}
-  \label{fig:tee1}
-\end{figure}
+%We clarify how we derive the factors $\nu_i,\tau_i$ in the next two subsections.
+
+%\subsection{Path parameters energy contribution}
+%\label{sec:model}
 
@@
 
-The set
-\begin{equation}\label{eq:area}
-  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i}^\rho)\in\mathcal{C}_i\},
-\end{equation}
-delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Figure~\ref{fig:tee1}).
+%The set
+%\begin{equation}\label{eq:area}
+%  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i}^\rho)\in\mathcal{C}_i\},
+%\end{equation}
+%delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Figure~\ref{fig:tee1}).
 $\varphi_i$ is a function of the two coordinates and the path parameters, and is equal to zero when a point $\mathbf{p}_k$ is on the path.
@@
 They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by changing the flying time in the example in Figure~\ref{fig:il-abs}.
-In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
+%In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
 In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan.
 
-We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
-\begin{equation}\label{eq:pd}
-  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
-    0&1\\-1&0
-  \end{bmatrix},
-\end{equation}
-where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
+%We derive the new position $\mathbf{p}_{k+1}$ computing the vector field $\nabla\varphi_i:=\begin{bmatrix}\partial\varphi_i/\partial x & \partial\varphi_i/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
+%\begin{equation}\label{eq:pd}
+%  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varphi_i-k_e\varphi_i\nabla\varphi_i,\,\,\,E=\begin{bmatrix}
+%    0&1\\-1&0
+%  \end{bmatrix},
+%\end{equation}
+%where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
 The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
 
-The scaling factors for the path parameters from Equation~(\ref{eq:state-control}) are derived empirically.
+%The scaling factors for the path parameters from Equation~(\ref{eq:state-control}) are derived empirically.
 For the example in Figure~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
 The variation of the control hence results in an approximate measure of the plans' time variation with factors
-\begin{equation}\label{eq:scale-traj}\begin{split}
-  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
-  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
-\end{split}\end{equation} 
+%\begin{equation}\label{eq:scale-traj}\begin{split}
+%  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
+%  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
+%\end{split}\end{equation} 
 %Whenever the trajectory parameters are not equally distributed, one can define $(y_{\overline{c}_i}-y_{\underline{c}_i})$ as a the highest (and lowest) levels of specific trajectory parameters. 
-$\forall j\in[\rho]^+$. Moreover, let the factors be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
-
-\subsection{Computation parameters energy contribution}
-\label{sec:computations-model}
-
-Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
+%$\forall j\in[\rho]^+$. Moreover, let the factors be zero when the parameters set $c_i^\rho=\{\emptyset\}$.
+
+%\subsection{Computation parameters energy contribution}
+%\label{sec:computations-model}
+
+%Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
 We estimate the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
 
-For this purpose, we assume the UAV carries an embedded board that runs the computations.
+%For this purpose, we assume the UAV carries an embedded board that runs the computations.
 Our tool measures the instantaneous energy consumption of a subset of possible computation parameters within the computation constraint sets and builds an energy model: a linear interpolation, one per each computation.
 
-The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS-based system~\cite{quigley2009ros}.
+%The computations are implemented by software components, e.g., Robot Operating System (ROS) nodes in a ROS-based system~\cite{quigley2009ros}.
 The user implements these nodes such that they change the computational load according to node-specific ROS parameters--the computation parameters.
@@
 
-We note that while the path can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation constraint set.
-
-Let us define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool.
-
-The scaling factors add the computational energy component to the model in Equation~(\ref{eq:state-perf}). They are derived similarly to Equation~(\ref{eq:scale-traj})
-\begin{equation*}\begin{split}
-  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
-  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
-\end{split}\end{equation*}
-$\forall j\in[\rho+1,\rho+\sigma]$. Moreover, let the factors be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Algorithm}  %
+%We note that while the path can differ for each stage, the tasks remain the same. However, the user can inhibit or enable a computation varying its computation constraint set.
+
+%Let us define $g:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained using the tool.
+
+%The scaling factors add the computational energy component to the model in Equation~(\ref{eq:state-perf}). They are derived similarly to Equation~(\ref{eq:scale-traj})
+%\begin{equation*}\begin{split}
+%  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
+%  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
+%\end{split}\end{equation*}
+%$\forall j\in[\rho+1,\rho+\sigma]$. Moreover, let the factors be zero when the parameters set $c_i^\sigma=\{\emptyset\}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Planning-Scheduling}  %
 \label{sec:algo}               %
                                %
-The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Problem~\ref{pb}.
-
-A valid control sequence has to respect the energy constraints. We consider some realistic constraints to the energy of a flying UAV in the following subsection.
-
-\subsection{Output and control constraint sets}
-
-We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}$.
+This section solves Problems~\ref{pb:cov-pb}--\ref{pb}, i.e., derives a plan in Section~\ref{sec:cov-algo}, and re-plans the plan energy-wise in Section~\ref{sec:repla-algo}.
+
+\subsection{Coverage path planning}
+\label{sec:cov-algo}
+
+There are various approaches in the literature to solve CPP problems, such as Problem~\ref{pb:cov-pb}.
+Approaches that ensure the completeness of the cover are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
+
+An intuitive way to solve the problem is with a back-and-forth motion, sweeping the space delimited by $v$ we term $\mathcal{Q}^v$.
+Although abundant in both mobile ground-based~\cite{choset2001coverage,choset2005principles,lavalle2006planning} and aerial~\cite{araujo2013multiple,artemenko2016energy,cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
+These robots have reduced maneuverability~\cite{dille2013efficient,mannadiar2010optimal,xu2011optimal,xu2014efficient} and are generally unable to fly quick turns~\cite{wang2017curvature}.
+
+To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius.
+It is similar to another motion in the literature termed \emph{Zamboni motion}~\cite{araujo2013multiple},
+but additionally allows variable CPP at the very core of this work.
+The motion, termed \emph{Zamboni-like motion}, is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Figure~\ref{fig:zambo}).
+Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates an edge formed by vertices $v_x,v_y$.
+
+\begin{algorithm}[h]
+  \begin{algorithmic}[1]
+    \small
+    %\STATE $j\gets-1$
+
+    \FORALL{$i\in\mathcal{T}$}
+      \STATE \textbf{if} $\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+
+%      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}}}
+
+%        \RETURN{$\Gamma$}\vspace*{.3ex}
+%      \ENDIF
+
+      \vspace*{.8ex}
+      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_j}$}
+        \STATE $j\gets j+1$\vspace*{.3ex}
+        \IF{$j\notin[n]_{>0}$}
+          \STATE $j\gets 1$\vspace*{.3ex}
+          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Def.~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
+          parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
+
+          \STATE $\mathbf{p}_{|\Gamma|+1}\gets$ other intersection %in Eq.~(\ref{eq:t1}) 
+          of $\varphi_{|\Gamma|+1}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+2}\gets$ circle %in Eq.~(\ref{eq:v2}) 
+          whose left most point lays on $\mathbf{p}_{|\Gamma|+1}$\vspace*{.3ex}\label{alg2:circ1}
+
+          \STATE $\mathbf{p}_{|\Gamma|+2}\gets$ other inter. %in Eq~(\ref{eq:t2}) 
+          of $\varphi_{|\Gamma|+2}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+3}\gets$ line %in Eq.~(\ref{eq:v3}) 
+          par. to $\varphi_{|\Gamma|+1}$ that inter. $\mathbf{p}_{|\Gamma|+2}$\vspace*{.3ex}
+
+          \STATE $\mathbf{p}_{|\Gamma|+3}\gets$ other inter. %in Eq~(\ref{eq:t3})
+          of $\varphi_{|\Gamma|+3}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+4}\gets$ circle in Eq.\hspace*{.7ex}(\ref{eq:second-circ-gene}) 
+          whose right most point lays\vspace*{.3ex} \hspace*{1em}on $\mathbf{p}_{|\Gamma|+3}$\vspace*{.3ex}\label{alg2:circ2}
+
+          \STATE $\mathbf{p}_{|\Gamma|+4}\gets$ other inter. %in Eq~(\ref{eq:last-trig-gene}) 
+          of $\varphi_{|\Gamma|+4}$ and $v$\vspace*{.3ex}\label{alg2:trig4}
+
+          \vspace*{.8ex}
+          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\ref{def:stage}}\label{alg2:last}
+
+        \ENDIF
+      \ENDIF
+    \ENDFOR
+  \end{algorithmic}
+  \caption{Zamboni-like motion for CPP}\label{alg2}
+\end{algorithm}
+
+Algorithm~\ref{alg2} illustrates the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+
+%\begin{enumerate*}[label={(\alph*)},font={\textit}]
+%  \item place a line $\varphi_i$ parallel to ${}^{v_1}|_{v_{|v|}}$ that intersects edges ${}^{v_{|v|}}|_{v_{|v-1|}},{}^{v_1}|_{v_2}$ (i.e., first and last),
+%  \item place a circle $\varphi_{i+1}$ whose left most point lays at $\mathbf{p}_{\Gamma_i}$, the intersection of $\varphi_i$ and the edge ${}^{v_{|v|}}|_{v_{|v-1|}}$.
+$\varphi_{i+1}$ intersects $v$ again at $\mathbf{p}_{\Gamma_{i+1}}$,
+%  \item place a line $\varphi_{i+2}$ parallel to $\varphi_i$ that intersects $v$ at $\mathbf{p}_{\Gamma_{i+1}},\mathbf{p}_{\Gamma_{i+2}}$,
+%  \item finally, place a circle $\varphi_{i+3}$ whose right most point lays at $\mathbf{p}_{\Gamma_{i+2}}$ and intersects $v$ again at $\mathbf{p}_{\Gamma_{i+3}}$.
+%\end{enumerate*}
+
+%For ease of notation, the procedure assume that the polygon $v$ is constructed in such a way that the lines $\varphi_{k+1},\varphi_{k+3}$ are never disconnected. %These are
+%\begin{subequations}\label{eq:line-gene}\begin{align}
+%  \varphi_{k+1}&:=x-x_{\Gamma_1}-\lfloor i/4\rfloor x_\mathbf{d},\label{eq:v1}\\
+%  \varphi_{k+3}&:=x-x_{\Gamma_2}-\lfloor i/4\rfloor x_\mathbf{d}\label{eq:v3},
+%\end{align}
+%\end{subequations}
+%where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$, and $\lfloor\,\cdot\,\rfloor$ is the integer division (it has a different meaning with parameters set $c_i$, see Equation~\ref{eq:piece-wise-reg}).
+The circles are
+%\begin{subequations}\label{eq:circ-gene}\begin{align}
+%  \begin{split}\varphi_{i+1}:=(&x-x_{\Gamma_1}-r_1-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_1}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_1^2,\end{split}\label{eq:v2}\\
+%  \begin{split}\varphi_{i+3}:=(&x-x_{\Gamma_2}+r_2-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_3}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_2^2,\label{eq:second-circ-gene}\end{split}
+%\end{align}
+%\end{subequations}
+%where $r_1,r_2\in\mathbb{R}_{>0}$ s.t. $r_1>r_2>\underline{r}$ are radiuses. $r_1=r_2+x_\mathbf{d}/2$, whereas $r_2$ is in Equation~(\ref{eq:r2}).
+
+%Similarly, the triggering points are
+%\begin{subequations}\label{eq:trigs-gene}\begin{align}
+%  \mathbf{p}_{\Gamma_i}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t1}\\
+%  \mathbf{p}_{\Gamma_{i+1}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t2}\\
+%  \mathbf{p}_{\Gamma_{i+2}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t3}\\
+%  \mathbf{p}_{\Gamma_{i+3}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2(r_1\hspace*{-.35ex}-\hspace*{-.35ex}r_2)+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d})\label{eq:last-trig-gene}.
+%\end{align}
+%\end{subequations}
+
+\begin{figure}[t]
+  \footnotesize
+  \begin{minipage}[l]{0.25\columnwidth}
+    \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Figure~\ref{fig:il-abs}).}
+    \label{fig:tee1}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.7\columnwidth}
+    \centering
+    \vspace*{-4.5ex}
+    \input{\figpath/new/traj2.tikz}
+  \end{minipage}
+  \vspace*{-4.5ex}
+\end{figure}
+\begin{figure}[t]
+  \footnotesize
+  \begin{minipage}[l]{0.73\columnwidth}
+    \centering
+    \vspace*{-2ex}
+    \input{\figpath/new/traj3.tikz}
+  \end{minipage}\hfill
+  \begin{minipage}[l]{0.25\columnwidth}
+    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Alg.~\ref{alg2}) can be (re)planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
+    \label{fig:zambo}
+  \end{minipage}
+  \vspace*{-4.5ex}
+\end{figure}
+
+To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
+\begin{equation}\label{eq:r2}
+  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
+\end{equation}
+is in function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ and $r$ is a given ideal turning radius along with the minimum radius (see Problem~\ref{pb:cov-pb}). The center than also changes
+\begin{equation}\label{eq:second-circ-gene}
+  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
+\end{equation}
+where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$.
+Figure~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
+The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$ in Definition~\ref{def:primitive}).
+
+Algorithm~\ref{alg2} initialize $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the given final point $\mathbf{p}_{\Gamma_l}$.
+Initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
+the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Figure~\ref{fig:zambo}.
+
+\subsection{Coverage (re)planning-scheduling}
+\label{sec:repla-algo}
+
+Past literature in planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
+We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use a technique in the literature named output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.
+
+An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories, $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ given initial and final cost functions
+\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
+  \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
+  \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
+  c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
+  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
+  \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
+  b(y(t_0))&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat}.
+\end{align}\end{subequations}
+
+Here, Equation~(\ref{eq:dyn-evol}) is the differential periodic energy model in Equation~(\ref{eq:state-perf}).
+Equation~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}.
+Equation~(\ref{eq:batt-const-mpc}) is the state and output constraints in Lemma~\ref{lem:bat} that requires to evolve the battery model.
+Equation~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation% (e.g., linear Kalman filter)
+with the very first estimate given. Equation~(\ref{eq:ocp-outp-bat}) is the battery SoC, estimated via a flight controller.
+
+\begin{algorithm}[t]
+  \begin{algorithmic}[1]
+    \small
+    \FORALL{$i\in\mathcal{T}$}
+      \makeatletter
+      \setcounter{ALC@line}{15}
+      \makeatother
+      \STATE $\mathbf{q}(\mathcal{K}\setminus\{i+N\}),c_j(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_j(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(i+\hspace*{-.1ex}N),i+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_j(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{i,i+h,\dots,i+N\}$\vspace*{.3ex}\label{alg:mpc}
+
+      \vspace*{.8ex}
+      \STATE $k\gets i$\vspace*{.3ex}\label{alg:bat1}
+      \WHILE{$b_d(C\mathbf{q}(k))>0$}\vspace*{.3ex}
+        \IF{$k\in\mathcal{K}$}
+          \STATE $\mathbf{q}(k+h)\gets${ solve model in Eq.~(\ref{eq:state-perf-q})}\vspace*{.3ex}\label{alg:evol}
+        \ENDIF
+        \STATE $b_d(C\mathbf{q}(k+h))\gets${ solve model in Lem.~\ref{lem:bat}}\vspace*{.3ex}
+        \STATE $k\gets k+h$\vspace*{.3ex}
+      \ENDWHILE
+      \STATE $t_b\gets k-i$\vspace*{.3ex}\label{alg:bat2}
+      \STATE $t_s\gets(\mathrm{diag}(\nu_j^\rho)\vspace*{.3ex}c_j^\rho(i)+\tau_j^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
+      \STATE $t_r\gets(t_s/\overline{t})(\overline{t}-i)$\vspace*{.3ex}
+      \IF{$t_r<t_b$}
+        \STATE $c_j^{\rho}(i)\gets${ find }$c_j^{\rho}${ with }$t_c\in[0,t_b]${, otherwise take }$\underline{c}_j^\rho$\vspace*{.3ex}\label{alg:traj2}
+      \ENDIF
+
+      \vspace*{.8ex}
+      \STATE $\hat{\mathbf{q}}(i+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$y(i)$\vspace*{.3ex}\label{alg:klm1}
+      \STATE $\hat{y}(i+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(i+h)$\vspace*{.3ex}\label{alg:klm2}
+    \ENDFOR
+  \end{algorithmic}
+  \caption{Coverage (re)planning-scheduling}\label{alg}
+\end{algorithm}
+
+Algorithm~\ref{alg} implements Equation~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware (re)planning-scheduling of $\Gamma$ from Algorithm~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Algorithm~\ref{alg2}.
+
+Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transformed version of the OCP in Equation~(\ref{eq:ocp-output-mpc}) into a non-linear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
+Its solution leads to both trajectories of parameters and states for future $N$ instants.
+Here, the sets $\mathcal{K},\mathcal{T}$ have possibly a different step $h$, tuning the precision.
+The functions $l_d,b_d$ are merely the discretized versions of Equation~(\ref{eq:ocp-costs}) and Lemma~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc~\cite{iserles2009first}.
+
+Lines~\ref{alg:bat1}--\ref{alg:bat2} estimate the time needed to completely drain the battery, exploiting the SoC already predicted previously on Line~\ref{alg:mpc}.
+The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using Lemma~\ref{lem:new} and scaling factors from Equation~(\ref{eq:scale-traj}).
+Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensors readings $y$ (e.g., linear Kalman filter~\cite{kalman1960new}).
+
+%The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Problem~\ref{pb}.
+
+%A valid control sequence has to respect the energy constraints. We consider some realistic constraints to the energy of a flying UAV in the following subsection.
+
+%\subsection{Output and control constraint sets}
+
+%We stated earlier the output $y$--the instantaneous energy consumption--evolves in $\mathbb{R}$.
 This is generally untrue.
@@
 
-Let us hence consider the state of charge (SoC) $b$ of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
-\begin{equation}\label{eq:bat}
-  b_k=b_{k-1}-k_b\left(V-
-  \sqrt{
-    V^2-
-    4R_ry_k}
-  \right)/(2R_rQ_c),
-\end{equation}
-where $k_b$ is the battery coefficient determined experimentally,  $V\in\mathbb{R}$ is the internal battery 
+%Let us hence consider the state of charge (SoC) $b$ of a UAV battery with a simplistic difference equation~\cite{seewald2020mechanical}
+%\begin{equation}\label{eq:bat}
+%  b_k=b_{k-1}-k_b\left(V-
+%  \sqrt{
+%    V^2-
+%    4R_ry_k}
+%  \right)/(2R_rQ_c),
+%\end{equation}
+%where $k_b$ is the battery coefficient determined experimentally,  $V\in\mathbb{R}$ is the internal battery 
 % and $\tilde{V}\in\mathbb{R}$ the stabilized 
-voltage measured in volts, $R_r\in\mathbb{R}$ the resistance measured in ohms, and $Q_c\in\mathbb{R}$ the constant nominal capacity measured in amperes per hour.
-
-\begin{defn}[Output, control constrain sets]\label{def:const}
-The output constrain set is then the set
-\begin{equation*}
-  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,b_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
-\end{equation*}
-and $b_kQ_cV$ is the maximum instantaneous energy consumption.
-
-The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
-\begin{equation*}
-  \mathcal{U}_k:=\begin{cases}
-    \mathcal{C}_i & \text{for } c_{i,j} \text{ with } j\leq\rho\\
-    \mathcal{S}_{i,j-\rho} & \text{for } c_{i,j} \text{ with } \rho<j\leq\sigma
-  \end{cases}.
-\end{equation*}
-\end{defn}
-
-\subsection{Deployment algorithm}
-
-\begin{algorithm}[t]
-  \caption{Energy-Aware Dynamic Planning}\label{alg}
-  \begin{algorithmic}[1]
-    \STATE $\mathbf{p}_{k}\gets \mathbf{p}_0, \mathbf{q}_{k}\gets \mathbf{q}_0$
-    \STATE $\mathbf{u}_{k}\gets \overline{c}_i$\label{alg:init}
-    \FOR{$i\in[l]^+$}\label{alg:stages-loop}
-      \WHILE{$\mathbf{p}_{k}\neq\mathbf{p}_{\Gamma_i}$}\label{alg:while}
-        \STATE $\mathbf{u}_{k+1}\gets\argmax_{\mathbf{u}}\hspace*{-1ex}{\displaystyle{\sum\limits_{j=k+1}^{k+N-1}}\hspace*{-1ex}{l(\mathbf{q}_j,\mathbf{u}_j)+V_f(\mathbf{q}_{k+N})}}$\label{alg:mpc}
-        \STATE $\hat{\mathbf{q}}_{k+1}\gets A\mathbf{q}_{k}+B\mathbf{u}$\label{alg:evolution}
-        \STATE $\mathbf{q}_{k+1}\gets$ the estimate of the state from $\hat{\mathbf{q}}_{k_1}$ and sensor data\label{alg:kalman_end}
-        \STATE $\mathbf{p}_{k+1}\gets\mathbf{p}_{k}\dot{\mathbf{p}}_d(\mathbf{p}_{k})/v$ \label{alg:pos}
-        \STATE $k\gets k+1$
-      \ENDWHILE
-    \ENDFOR
-  \end{algorithmic} 
-\end{algorithm}
-
-The algorithm first initializes the position, energy coefficients, and control (line~\ref{alg:init}).
+%voltage measured in volts, $R_r\in\mathbb{R}$ the resistance measured in ohms, and $Q_c\in\mathbb{R}$ the constant nominal capacity measured in amperes per hour.
+
+%\begin{defn}[Output, control constrain sets]\label{def:const}
+%The output constrain set is then the set
+%\begin{equation*}
+%  \mathcal{Y}_k:=\{y_k\mid y_k\in[0,b_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+%\end{equation*}
+%and $b_kQ_cV$ is the maximum instantaneous energy consumption.
+
+%The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
+%\begin{equation*}
+%  \mathcal{U}_k:=\begin{cases}
+%    \mathcal{C}_i & \text{for } c_{i,j} \text{ with } j\leq\rho\\
+%    \mathcal{S}_{i,j-\rho} & \text{for } c_{i,j} \text{ with } \rho<j\leq\sigma
+%  \end{cases}.
+%\end{equation*}
+%\end{defn}
+
+%\subsection{Deployment algorithm}
+
+%The algorithm first initializes the position, energy coefficients, and control (line~\ref{alg:init}).
 It updates the position at line~\ref{alg:pos}, using the expression from Equation~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
@@
 
-The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
+%The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
 A priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter (KF)~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
-At line~\ref{alg:mpc}, the algorithm uses MPC to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function (higher the horizon, higher the complexity and the robustness of the control to the output constraints)
-\begin{equation*}\label{eq:cost}\begin{split}
-  V_f(\mathbf{q}_k)&=l(\mathbf{q}_k,\mathbf{u}_k)=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,
-\end{split}\end{equation*}
-where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}).
-
-We note that at every step of the sum on line~\ref{alg:mpc}, the algorithm evolves the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
+%At line~\ref{alg:mpc}, the algorithm uses MPC to select the control $\mathbf{u}_k$ for a given horizon $N\in\mathbb{Z}_{>0}$ from the cost function (higher the horizon, higher the complexity and the robustness of the control to the output constraints)
+%\begin{equation*}\label{eq:cost}\begin{split}
+%  V_f(\mathbf{q}_k)&=l(\mathbf{q}_k,\mathbf{u}_k)=(1/2)\mathbf{q}_k^T\mathrm{diag}(C)\mathbf{q}_k,
+%\end{split}\end{equation*}
+%where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}).
+
+%We note that at every step of the sum on line~\ref{alg:mpc}, the algorithm evolves the state to check if the output satisfies the output constraint set, and if the control satisfies the control constraint set.
 In particular, it performs a subroutine
-\begin{algorithmic}
-  \WHILE{$\overline{c}_i\notin\mathcal{U}_k,\, y_k\notin\mathcal{Y}_k$}\label{alg2:while}
-    \STATE $\overline{c}_i\gets\overline{c}_i-\delta$
-  \ENDWHILE
-  \STATE $\mathbf{u}_k\gets\overline{c}_i$
-\end{algorithmic} 
-where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps.
+%\begin{algorithmic}
+%  \WHILE{$\overline{c}_i\notin\mathcal{U}_k,\, y_k\notin\mathcal{Y}_k$}\label{alg2:while}
+%    \STATE $\overline{c}_i\gets\overline{c}_i-\delta$
+%  \ENDWHILE
+%  \STATE $\mathbf{u}_k\gets\overline{c}_i$
+%\end{algorithmic} 
+%where $\delta\in\mathbb{R}^\rho\times\mathbb{Z}_{\geq 0}^\sigma$ are reduction steps.
 Both conditions of the loop have to be respected.
@@
 
-We finally note that one can express the tradeoffs between parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with the constraints
-\begin{equation*}
-  R_i\mathbf{u}_k-r_i\geq 0,
-\end{equation*}
-where $r_i\in\mathbb{R}^n$ and $R_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $R_i$ is the identity matrix, there is no relation between the parameters).
+%We finally note that one can express the tradeoffs between parameters (e.g., a decrement in the distance between the lines in a survey scenario is related to a decrement in the number of detections per second) enriching the control constraint set with the constraints
+%\begin{equation*}
+%  R_i\mathbf{u}_k-r_i\geq 0,
+%\end{equation*}
+%where $r_i\in\mathbb{R}^n$ and $R_i\in\mathbb{R}^{n\times n}$ expresses the relation between the parameters (if $R_i$ is the identity matrix, there is no relation between the parameters).
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{.4\textwidth}
+    \centering
+    \footnotesize
+    \input{\figpath/results/new_physics2/trajs2.tikz}
+    \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
+    \label{fig:trajs}
+  \end{subfigure}\hspace*{3ex}
+  \begin{subfigure}{.54\textwidth}
+    \centering
+    \footnotesize
+    \input{\figpath/results/new_physics2/ener2.tikz}
+    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$) and parameters ($T,b_0$) evolutions}
+    \label{fig:ener}
+  \end{subfigure}
+  \footnotesize
+  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground hazards detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}), i.e., wind speed and direction, battery behavior, and parameters initial values.}
+  \label{fig:res}
+\end{figure*}
 
@@
 
-In this section, we discuss our experimental setup, the implementation strategy, and the results.
-
-\subsection{Experimental setup}
-
-The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Figure~\ref{fig:il-abs}).
-We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario.
-The UAV was flying in standard atmospheric conditions like the path \hyperref[fig:trajs-I-static]{5.I} in Figure~\ref{fig:trajs}, or the first ``non-adapted'' part of Figure~\ref{fig:il-abs}.
-We later extended the UAV to carry a companion computer, NVIDIA Jetson Nano~\cite{nano}, running ROS.
+%$\subsection{Experimental setup}
+
+%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Figure~\ref{fig:il-abs}). 
+Figure~\ref{fig:il-abs} details the data of a physical flight  
+%We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
+in standard atmospheric conditions. 
+Figure~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
+The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}).
+The scheduler varies a computation parameter $c_{i,2}$ relative to ground hazards detection rate from two to ten frames-per-second (FPS).
+The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros} as well as the scheduler itself.
+The planner varies the path parameter $c_{i,1}$ in Equation~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
+
+%We later extended these UAV to carry a companion computer, NVIDIA Jetson Nano~\cite{nano}, running ROS.
 The companion computer has two ROS nodes; one detects hazards using PedNet, a Fully Convolutional Neural Network~\cite{ullah2018pednet}, and the other communicates with a ground station.
 
-\begin{figure}[t]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics2/trajs_revised.tikz}
-  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
+%\begin{figure}[t]
+%  \centering
+%  \footnotesize
+%  \input{\figpath/results/new_physics2/trajs_revised.tikz}
+%  \caption[Path of a static and dynamic plan]{Path simulations with variations of wind speed and direction.
 In \hyperref[fig:trajs-I-static]{5.I} and \hyperref[fig:trajs-II-static]{5.II} the path is static.
@@
 The algorithm adapts path parameter radius of the circle $c_{1,1}$ and computation parameter fps rate $c_{1,2}$.}
-  \label{fig:trajs}
-\end{figure}
-\begin{figure}[h]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics2/ener_revised.tikz}
-  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
+%  \label{fig:trajs}
+%\end{figure}
+%\begin{figure}[h]
+%  \centering
+%  \footnotesize
+%  \input{\figpath/results/new_physics2/ener_revised.tikz}
+%  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
 Below are the energy evolutions from the algorithm (\hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii}).
 It replans the path when the final time and battery time do not match, and the computation when the battery is discharged.}
-  \label{fig:ener}
-\end{figure}
-\begin{figure}[h!]
-  \centering
-  \footnotesize
-  \input{\figpath/results/new_physics2/model.tikz}
-  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
-  \label{fig:model}
-\end{figure}
-
-We implemented a realistic simulator to simulate the empirical data of a given plan and atmospheric conditions.
-We show the effects of different conditions in Figure~\ref{fig:trajs}.
-Both paths \hyperref[fig:trajs-I-static]{5.I} and \hyperref[fig:trajs-II-static]{5.II} are flying the same plan with different initial parameters values.
-Path \hyperref[fig:trajs-I-static]{5.I} is flying with a constant wind speed of 5 meters per second, wind direction of 0 degrees, and an initial path parameter $c_{1,1}$ value of 0.
-Path  \hyperref[fig:trajs-II-static]{5.II} is flying under the same conditions but a wind direction of 90 degrees and the initial path parameter value of -1000.
-The energy evolutions of these two paths are the top two subfigures \hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II} of Figure~\ref{fig:ener}.
-The simulated energy data are in black, the model evolution in red.
-
-\subsection{Algorithm evaluation}
-
-\subsubsection*{Periodic energy model}
-
-We showcase the energy model from Section~\ref{sec:energy-model} in Figure~\ref{fig:model}.
-Left figures illustrate an initial slice of the model and period estimation (Definition~\ref{def:period}).
-We used order $r$ equal to 3.
-We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
-On the right of Figure~\ref{fig:model}, we show the states $\alpha_0,...,\beta_3$ in time, concluding that approximately 2 periods are sufficient to obtain a consistent state estimate.
-With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
+%  \label{fig:ener}
+%\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \footnotesize
+%  \input{\figpath/results/new_physics2/model.tikz}
+%  \caption[Energy estimation and evolution of the state]{Energy estimation for the first 6 seconds on the left side, the evolution of the state $\mathbf{q}$ on the right.}
+%  \label{fig:model}
+%\end{figure}
+
+%We implemented a realistic simulator to simulate the empirical data of a given plan and atmospheric conditions. We show the effects of different conditions in Figure~\ref{fig:trajs}.
+
+Figure~\ref{fig:trajs} illustrate same plan $\Gamma$ under different conditions.
+Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, wind direction of zero degrees, and an initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
+Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
+
+Figure~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
+illustrate the power ($y(i)$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and the energy model ($C\mathbf{q}(i)$ on Line~\ref{alg:evol}).
+Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line) drop at approximately one minute and a half and four minutes and a half.
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Definition~\ref{def:const}).
+Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario.
+The lowest configuration of parameters and no battery defects.
+The path parameter increases as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter decreases mapping the battery discharge rate.
+For both cases scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature, oder $r$ is three (see Figure~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
+%\subsection{Algorithm evaluation}
+%\subsubsection*{Periodic energy model}
+The figure further details the energy model (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model ($C\hat{\mathbf{q}}(i)$), power ($y(i)$), and period ($T$).% We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
+The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods are sufficient to obtain a consistent state estimate.
+%With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
 It hence approximates the non-periodicity with a linear model.
 
-\subsubsection*{Implementation of the planning strategy}
-
-The practical implementation is based on observations of different variations of paths and computations.
+%\subsubsection*{Implementation of the planning strategy}
+
+%The practical implementation is based on observations of different variations of paths and computations.
 A variation of path alters the overall flying time, which we reflect in the factors $\nu_{1,1},\tau_{1,1}$ from Equation~(\ref{eq:scale-traj}).
@@
 
-A variation of computations affects directly the power.
+%A variation of computations affects directly the power.
 We thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
@@
 
-\subsubsection*{Dynamic adaptation of the path and computation parameters}
-
-We have tested the validity of the algorithm showing the dynamic adaptation in the subfigures \hyperref[fig:trajs-dyn-i]{5.i} and \hyperref[fig:trajs-dyn-ii]{5.ii} of Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii} of Figure~\ref{fig:ener} energy-wise.
+%\subsubsection*{Dynamic adaptation of the path and computation parameters}
+
+%Subfigures \hyperref[fig:trajs-dyn-i]{5.i}--\hyperref[fig:trajs-dyn-ii]{5.ii} in Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii} of Figure~\ref{fig:ener} energy-wise.
 For the first path (Subfigure \hyperref[fig:trajs-I-static]{5.I}) the plan starts at the highest configuration of parameters.
-We simulated two unexpected battery drops at approximately 1 minute and a half and 4 minutes and a half.
-The algorithm optimizes the path in the proximity of the drops to ensure that the flight is completed.
-Moreover, it maximizes the parameter $c_{1,2}$ when the battery is discharging (green line) respecting the output constraint (Definition~\ref{def:const}).
-We simulated the opposite scenario for the second path (Subfigure \hyperref[fig:trajs-II-static]{5.II}).
-The plan starts at the lowest configuration of parameters and the battery behaves linearly.
-We note that the path parameter is increased as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter is optimized for the battery discharge rate.
-For both cases, we used reductions $\delta$ of 500 and 2 for $c_{1,1}$ and $c_{1,2}$ respectively, and the horizon $N$ equal to 6 seconds.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Future Work}  %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions and Future Directions}  %
 \label{sec:conclusion}                       %
                                              %
-In this paper, we presented a planning algorithm for autonomous UAVs with a limited power source.
-The algorithm plans the path with computations dynamically and simultaneously.
-We collected empirical data of a fixed-wing UAV flying an agricultural scenario and built a simulator to test the algorithm in different conditions.
-The algorithm estimates the energy with a KF and optimizes the path and computations using MPC.
-It evolves the state to verify the satisfaction of battery and time constraints.
-It uses a plan where at each stage the UAV flies a path and does some computations.
-It guides the UAV using a vector field.
-Finally, it exploits the computational energy model varying the level of computations in the function of the current battery level.
-
-We are currently extending the results of this paper to work with a standard flight controller.
-We are further investigating the validity of the algorithm on other energy-critical mobile robots.
-Such as on planetary exploration rovers in~\cite{seewald2020beyond}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}  %
-\bibliography{\jobname}       %
+The letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending relevant past literature.
+It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
+Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates energy of the computing hardware via the \powprof{} tool.
+The approach compromises two algorithms: one derives a static coverage plan, whereas the other (re)plans-schedules the plan on a finite horizon via MPC.
+It evolves the state of the energy model while optimizing the battery usage.
+The plan compromise multiple stages, where at each the aerial robot flies a path and does some computations, allowing further extensibility in terms of constructs and approaches.
+
+Indeed, we are currently extending the results to a standard flight controller.
+The guidance on the coverage needs alike further investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
+Here, our initial investigation led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\small\bibliographystyle{IEEEtran}  %
+\bibliography{../../books/phd-thesis/backmatter/references}}             %
                                      %
-\leavevmode\thispagestyle{empty}\newpage
+%\leavevmode\thispagestyle{empty}\newpage
 
@@
 
+\section{Proof of Lemma~\ref{lem:new}}
+\label{app:proof-new}
+
+\section{Proof of Lemma~\ref{lem:bat}}
+\label{app:proof-bat}
+
+%The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}
+%\begin{equation}
+%  \dot{b}(y(t))=-I(y(t))/Q_c
+%\end{equation}
+%where  $y(t)\in\mathbb{R}_{\geq 0}$ is a power drain, $I(y(t))\in\mathbb{R}$ the internal current, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
+The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohms representing the battery resistance.
+The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V_e,V\in\mathbb{R}$ the the external and internal battery voltages measured in volts.
+The latter can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
+
+%Using simply
+
 \end{document}

### 2021-12-02 scripts/SIM8_casadi2.m

@@ -6,7 +6,7 @@
 
 %% casadi opt control
 
-addpath('../../../../../casadi-linux-matlabR2014b-v3.5.5/');
+addpath('../../../../../');
 % UPDATE THE PATH WITH CASADI SOURCE !
 
 

### 2021-12-04 energy-planning.tex
polishing and fixes

@@
 \author{
-  Adam Seewald$^{\text{1}}$, Hector Garcia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
+  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, %Henrik Skov Midtiby$^{\text{1}}$, 
+  and Ulrik Pagh Schultz$^{\text{1}}$
   %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
@@
   \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
-  \thanks{$^{\text{1}}$A.
-S., H.
-S.
-M., and U.
-P.
-S.
-are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense.
-Email: {\tt\footnotesize ads@mmmi.sdu.dk};}
-  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Computense de Madrid, Spain.}
+  \thanks{$^{\text{1}}$A. S. %, H. S. M.,
+  and U. P. S. are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense. Email: {\tt\footnotesize ads@mmmi.sdu.dk};} 
+  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Complutense de Madrid, Spain.}
   \thanks{Digital Object Identifier (DOI): see top of this page.}
@@
 \begin{abstract}
-  The paper presents a planning algorithm for autonomous UAVs with energy constraints and solves the problem of dynamic planning of the path and computations simultaneously.
-The planning strategy is based on a periodic energy model that is empirically motivated and formally proved.
-The model is enhanced with the time and energy contribution of the path and computations.
-The algorithm replans both in function of the battery state accounting for uncertainty.
-The dynamic planning allows to exploit all the available resources, yet avoid possible in-flight failure in case of unexpected battery drops due to, e.g., adverse atmospheric conditions.
+  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots, which plans in-flight a coverage path and simultaneously schedules onboard computational tasks.
+It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model.
+The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool.
+Accounting for uncertainty, an initial ``plan-schedule'' is replanned and rescheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
 \end{abstract}
@@
 They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets.
-A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some on-board computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
+A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some onboard computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
 Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}).
@@
 Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
-Figure~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t.
-the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defect~(\ref{sth:iii}).
+Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t.
+the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
 
@@
   \centering
-  \vspace*{-6.5ex}
+  \vspace*{-6.8ex}
   \begin{tikzpicture}
@@
   \end{tikzpicture}
-  \caption{An illustrative example of planning-scheduling.
+  \caption{Illustrative example of planning-scheduling.
 An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}).
@@
   \label{fig:il-abs}
-  \vspace*{-4.5ex}
+  \vspace*{-3.7ex}
 \end{figure}
@@
 Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa.
-The occurrence happens frequently with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
+The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
 
-To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc).
+To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.).
 Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
@@
 The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules.
-In Figure~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in the energy models for the computations, motion, and battery models in Section~\ref{sec:energy-model}.
-
-The remaining sections of the letter are then organized as follows. Section~\ref{sec:prob} provides basic constructs. These include the concepts of %computations and motion energies, 
-plan, stages, triggering and final points, and path functions, as well as the problem formulation.
-Section~\ref{sec:algo} describes in detail the planning-scheduling.
-Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives.
+In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model} for the computations and motion energies and battery models.
+
+The remaining sections of the letter are then organized as follows.
+Sec.~\ref{sec:prob} provides basic constructs, such as the concepts of the plan, stages, triggering and final points, and path functions, as well as the problem formulation.
+Sec.~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
+Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives.
 Appendices provide supplementary information.
@@
   \begin{minipage}[l]{0.35\columnwidth}
-    \caption{Definitions \ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$.
-$\mathbf{p}_{\Gamma_1},\dots$ are triggering points, in which proximity happens change of stages $\Gamma_1,\dots$.
+    \caption{Defs.~\ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$.
+$\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$.
 Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
@@
   \end{minipage}
-  \vspace*{-3.5ex}
+  \vspace*{-4.5ex}
 \end{figure}
 
-Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries.
+Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries.
 For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.
 
-%---
-
+\vspace*{-2ex}
 \subsection{Preliminaries}
@@
 
-Here, $\Gamma_i$ are \emph{stages}, and $\mathbb{Z}$ indicates the set of integers.
+Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ indicates the set of integers.
 At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
-Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.
+Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.
 $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and
@@
   where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}.
-$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
+$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter $c_{i,j}$ constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
 \end{defn}
@@
 
-The function $\varphi_i$ is the \emph{path function}, specifying the path.
-These are stage-dependent mathematical functions the aerial robot tracks as it travels the motion for the coverage.
-The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bound of a parameter $\cdot\,$, i.e.,
+The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
+the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bounds of a parameter $\cdot\,$, i.e.,
 \begin{equation}
@@
 
+%'\>o-O</'
+
 \begin{defn}[Path functions]
   \label{def:paths}
-  $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R}%\,\forall i\in\{1,2,\dots\}
+  $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R},\,\forall i\in\{1,2,\dots\}
   $ are \emph{path functions}, forming the path. They are a function of $\mathbf{p}(t)$ and path parameters $c_i^\rho(t)$ and are continuous and twice differentiable.
@@
 
-The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
-
-Figure \ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:plan}--\ref{def:trigs}.
-$\varphi_1,\dots,\varphi_6$ are path functions.
-$\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
-They are all relative to different stages $\Gamma_1,\Gamma_2,\dots$.
+The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Def.~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
+
+Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\ref{def:trigs}.
+$\varphi_0,\dots,\varphi_5$ are path functions.
+$\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines.
+They are relative to different stages $\Gamma_1,\Gamma_2,\dots$ but $\Gamma_0$, the stating stage.
 The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure.
-The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
+%The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
 
@@
 \begin{figure}[h!]
-  \center
+  \footnotesize
+  \begin{minipage}[l]{0.75\columnwidth}
     \vspace*{-2.2ex}
     \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
-    \footnotesize
+      \scriptsize
       \node[state,initial] (q_i) {$\Gamma_1$}; 
@@
       (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
-    (q_0) edge [bend right=65] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
-    (q_i) edge [bend left=-65] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
-    (q_2) edge [bend left=-45] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+      (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
+      (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+      (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
       (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
@@
     \end{tikzpicture}
-  \vspace*{-2.3ex}
-  \caption[Definition of a plan with a loop]{Definition of a plan $\Gamma$ with periodic patterns.
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.2\columnwidth}
+    \centering
+    \caption{Plan $\Gamma$ with $n$ primitve stages  in Def~\ref{def:primitive}.}
+    \label{fig:state-machine-loop}
+  \end{minipage}
+  \vspace*{-3.5ex}
+\end{figure}
+%\begin{figure}[h!]
+%  \center
+%  \vspace*{-2.2ex}
+%  \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
+%    \scriptsize
+%    \node[state,initial] (q_i) {$\Gamma_1$}; 
+%    \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
+%    \node        [right=of q_2] (q_dots0) {$\cdots$};
+%    \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
+%    \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
+%    \path[->]
+%    (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
+%    (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
+%    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
+%    (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
+%    (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+%    (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+%    (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
+%    (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
+%    (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
+%    (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
+%    (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
+%    ; %end path 
+    %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
+    %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
+%  \end{tikzpicture}
+%  \vspace*{-2.3ex}
+%  \caption[Definition of a plan with a loop]{Definition of a plan $\Gamma$ with periodic patterns.
 Stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$ are iterated with a shift $\mathbf{d}$.}
-  \vspace*{-1ex}
-  \label{fig:state-machine-loop}
-\end{figure}
-
-Figure \ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}.
+%  \vspace*{-1ex}
+%  \label{fig:state-machine-loop}
+%\end{figure}
+
+Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}.
 A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
@@
 
+\vspace*{-2ex}
 \subsection{Problem formulation}
@@
   \label{pb}
-  Consider an initial plan $\Gamma$ in Definition~\ref{def:plan}.
+  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}.
 The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
@@
 There is one path constraint set which bounds the path and multiple computation constraint sets, one per each computation parameter, that bound computations.
-In Figure~\ref{fig:il-abs}, there are two parameters.
+In Fig.~\ref{fig:il-abs}, there are two parameters.
 One relative to the path (\ref{sth:ii}~has a shorter distance between the lines than~\ref{sth:iii}), and the other one to the computations (\ref{sth:i}~processes more images per second than~\ref{sth:ii}).
@@
 
-%In Figure~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are paths.
+%In Fig.~\ref{fig:traj1}, $\varphi_1,\dots,\varphi_6$ are paths.
 $\varphi_1$ and $\varphi_5$ are circles, while $\varphi_2$, $\varphi_4$, and $\varphi_6$ are lines.
@@
 The constraints set $\mathcal{C}_1,\mathcal{C}_2,\dots$ forms the area where the paths $\varphi_1,\varphi_2,\dots$ can be altered with the parameters $c_{i,1},\dots,c_{i,\rho}$ (gray area in the figure).
-This area is bounded by $\underline{c}_i,\overline{c}_i$, and can be different per each stage (in Figure~\ref{fig:traj1}, the area relative to $\Gamma_4$ is bounded by $\underline{c}_4,\overline{c}_4$).
+This area is bounded by $\underline{c}_i,\overline{c}_i$, and can be different per each stage (in Fig.~\ref{fig:traj1}, the area relative to $\Gamma_4$ is bounded by $\underline{c}_4,\overline{c}_4$).
 
@@
 %The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
-In Figure~\ref{fig:traj1}, $\mathbf{p}_{\Gamma_1}$ allows the transition between $\Gamma_1$ and $\Gamma_2$, $\mathbf{p}_{\Gamma_4}$ between $\Gamma_4$ and $\Gamma_5$, and $\mathbf{p}_{\Gamma_5}$ between $\Gamma_5$ and $\Gamma_6$.
+In Fig.~\ref{fig:traj1}, $\mathbf{p}_{\Gamma_1}$ allows the transition between $\Gamma_1$ and $\Gamma_2$, $\mathbf{p}_{\Gamma_4}$ between $\Gamma_4$ and $\Gamma_5$, and $\mathbf{p}_{\Gamma_5}$ between $\Gamma_5$ and $\Gamma_6$.
 The last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$ is called \emph{final point}.
@@
 
-%A slice of the plan in Figure~\ref{fig:state-machine} shows the transition between the stages with the FSM.
+%A slice of the plan in Fig.~\ref{fig:state-machine} shows the transition between the stages with the FSM.
 The triggering point $\mathbf{p}_{\Gamma_{i-1}}$ allows the transition to the stage $\Gamma_i$.
@@
 
-%Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).
+%Generally, one can express the triggering points in function of the $i$-th trajectory parameters $c_{i}^{\rho}$, or any previous trajectory parameters, propagating the information therein if necessary (see Fig.~\ref{fig:state-machine2}).
 
@@
 %\begin{defn}[Period]\label{def:period}
-%  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Equation~(\ref{eq:primitive}).
+%  The period $T\in\mathbb{R}_{> 0}$ is the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Eq.~(\ref{eq:primitive}).
 %\end{defn}
@@
 
-%One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Equation~(\ref{eq:primitive}).
-If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Figure~\ref{fig:il-abs}).
+%One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Eq.~(\ref{eq:primitive}).
+If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Def.~\ref{def:period} can be determined empirically from energy data (such as these shown in Fig.~\ref{fig:il-abs}).
 
 %\begin{pb}[UAV planning problem]\label{pb}
-%  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}.
+%  Consider an initial plan $\Gamma$ from Def.~\ref{def:mission}.
 We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-                                 %
+\vspace*{-1ex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Energy Models}  %
@@
                          %
-The solution to Problem~\ref{pb} requires accurate energy models, predicting the impact of given path and computations parameters on the battery at future time instants.
-To this end, Sections~\ref{sec:mod-mot}--\ref{sec:mod-bat} provide models for the motion and computations energies and battery.
-
+The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of given path and computations parameters on the battery at future time instants.
+To this end, Secs.~\ref{sec:mod-mot}--\ref{sec:mod-bat} provide models for the motion and computations energies and battery.
+
+\vspace*{-2ex}
 \subsection{Energy model for the motion}
@@
 
-Let us return to the collected energy data and spectrum analysis in Figure~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
+Let us return to the collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
 Energy data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
@@
 
-%We prove a relation between the energy signal and the energy coefficients in Lemma~\ref{lem:eqv}.
+%We prove a relation between the energy signal and the energy coefficients in Lem.~\ref{lem:eqv}.
 We show after the main results how this approach allows us variability in terms of non-periodic signals.
@@
 
-%The linear model in Equation~(\ref{eq:state-perf}) allows us to include the control in the model of Equation~(\ref{eq:fourier}).
-
-Under some conditions, the models in Equations~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal.
-
-\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Equations~(\ref{eq:mat_A}--\ref{eq:mat_C}), and the initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
+%The linear model in Eq.~(\ref{eq:state-perf}) allows us to include the control in the model of Eq.~(\ref{eq:fourier}).
+
+Under favorable conditions, %the 
+models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal.
+
+\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), and the initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
   \begin{equation*}
@@
   \end{equation*} 
-  $h$ in Equations~(\ref{eq:fourier}) is equal to $y$ in Equation~(\ref{eq:state-perf}).
+  $h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
 \end{lem}
@@
 %\end{proof}
-%Appendix~\ref{app:proof-eqv} contains a proof of Lemma~\ref{lem:eqv}.
+%Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
 
@@
 
-Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains proofs of Lemmas~\ref{lem:eqv}--\ref{lem:new}.
-
-Using the same notation from Lemma~\ref{lem:new}, the nominal control in Equation~(\ref{eq:state-perf})
+Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains proofs of Lems.~\ref{lem:eqv}--\ref{lem:new}.
+
+Using the same notation from Lemma~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
 \begin{equation}
@@
 where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere.
-$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Definition~\ref{def:stage}) to time and power domains.
+$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Def.~\ref{def:stage}) to time and power domains.
 
@@
 
-Similarly to Equation~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with scaling factors
+Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with scaling factors
 \begin{subequations}\label{eq:scale-comp}\begin{align}
@@
 \end{align}\end{subequations}
-$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Section~\ref{sec:mod-com} and quantifies the power of the computing hardware.
+$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Sec.~\ref{sec:mod-com} and quantifies the power of the computing hardware.
 
@@
 Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware or software specific parameters.
-This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis aiding to quantify the computations energy of any combination of computations $c_i^\sigma$ withing the bounds (see Definition~\ref{def:stage}).
+This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis aiding to quantify the computations energy of any combination of computations $c_i^\sigma$ withing the bounds (see Def.~\ref{def:stage}).
 
@@
 
-The energy measures in Definitions~\ref{def:meas}--\ref{def:pred} can be either average or overall energy.
-Additionally, the tool supports the measures of battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}.
-The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Equation~(\ref{eq:scale-comp}) assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
+The energy measures in Defs.~\ref{def:meas}--\ref{def:pred} can be either average or overall energy.
+Additionally, the tool supports the measures of battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}.
+The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}) assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
 \begin{equation}\label{eq:piece-wise-reg}\begin{split}
@@
 
-Appendix~\ref{app:proof-bat} contains a proof of Lemma~\ref{lem:bat}.
-
-Equation~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$. Let us re-evaluate the output constraint with Lemma~\ref{lem:bat}.
+Appendix~\ref{app:proof-bat} contains a proof of Lem.~\ref{lem:bat}.
+
+Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$. Let us re-evaluate the output constraint with Lem.~\ref{lem:bat}.
 
@@
 
-%Let us consider for practical reasons the discretized version of the system in Equation~\ref{eq:state-perf}.
+%Let us consider for practical reasons the discretized version of the system in Eq.~\ref{eq:state-perf}.
 
@@
 %\end{equation}
-%where $\mathbf{u}_k\in\mathbb{R}^n$ with $n=\rho+\sigma$ differs from the nominal control $\mathbf{u}$ in Equation~(\ref{eq:state-perf}).
+%where $\mathbf{u}_k\in\mathbb{R}^n$ with $n=\rho+\sigma$ differs from the nominal control $\mathbf{u}$ in Eq.~(\ref{eq:state-perf}).
 We include the control in the nominal control exploiting the following observation.
@@
 The nominal control $\mathbf{u}$ is then the difference of these contributions of two consecutive controls $\mathbf{u}_{k-1},\mathbf{u}_k$ applied to the system.
-$B\mathbf{u}$ merely includes the difference in power into the model in Equation~(\ref{eq:state-perf}).
+$B\mathbf{u}$ merely includes the difference in power into the model in Eq.~(\ref{eq:state-perf}).
 
@@
 
-%Equation~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
-For instance, when the trajectory $\varphi_1$ is a circle (see Figure~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
-It thus simulates the lowering of instantaneous energy consumption ($\nu_{1,1}c_{1,1}>\nu_{1,1}c_{1,1}^-$) for a given $\nu_{1,1}$, that is then summed to the first coefficient $\alpha_0$ in Equation~(\ref{eq:state-details}), shifting the modeled energy.
+%Eq.~(\ref{eq:state-control}) accounts for the energy due to the change of parameters $\mathbf{u}_k-\mathbf{u}_{k-1}$.
+For instance, when the trajectory $\varphi_1$ is a circle (see Fig.~\ref{fig:tee1}), a decrement in the trajectory parameter $c_{1,1}$--the radius of the circle--adds a negative contribution.
+It thus simulates the lowering of instantaneous energy consumption ($\nu_{1,1}c_{1,1}>\nu_{1,1}c_{1,1}^-$) for a given $\nu_{1,1}$, that is then summed to the first coefficient $\alpha_0$ in Eq.~(\ref{eq:state-details}), shifting the modeled energy.
 
@@
 %\end{equation}
-%delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Figure~\ref{fig:tee1}).
+%delimits the area where the $i$-th path $\varphi_i$ is free to evolve using the path parameters $c_i^\rho$ (the gray area in Fig.~\ref{fig:tee1}).
 $\varphi_i$ is a function of the two coordinates and the path parameters, and is equal to zero when a point $\mathbf{p}_k$ is on the path.
@@
 The path parameters allows to change the path.
-They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by changing the flying time in the example in Figure~\ref{fig:il-abs}.
-%In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
-In Figure~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan.
+They are a way to alter the nominal trajectory in the initial plan and thus alter the energy by changing the flying time in the example in Fig.~\ref{fig:il-abs}.
+%In fact, the algorithm uses the set from Eq.~(\ref{eq:area}) to find the path parameters such that the plan consisting of flying $\varphi_i$ has the highest energy, while still respecting the constraints.
+In Fig.~\ref{fig:tee1}, the parameter radius of the circle $c_{1,1}$ is replanned as, e.g., averse atmospheric conditions do not allow to terminate the plan.
 
@@
 %where $E$ specifies the rotation (it influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.
-The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Figure~\ref{fig:tee1}).
-
-%The scaling factors for the path parameters from Equation~(\ref{eq:state-control}) are derived empirically.
-For the example in Figure~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
+The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading $\dot{\mathbf{p}}$ due to the atmospheric interferences (wind $w\in\mathbb{R}$ in the top of Fig.~\ref{fig:tee1}).
+
+%The scaling factors for the path parameters from Eq.~(\ref{eq:state-control}) are derived empirically.
+For the example in Fig.~\ref{fig:tee1}, we can obtain the scaling factor $\nu_{1,1}$ measuring the time needed to compute the path with the lowest configuration $\underline{c}_1$, $\underline{t}$ and the highest $\overline{t}$.
 The variation of the control hence results in an approximate measure of the plans' time variation with factors
@@
 
-%Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
+%Let us recall from Def.~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
 We estimate the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
@@
 
-%The scaling factors add the computational energy component to the model in Equation~(\ref{eq:state-perf}). They are derived similarly to Equation~(\ref{eq:scale-traj})
+%The scaling factors add the computational energy component to the model in Eq.~(\ref{eq:state-perf}). They are derived similarly to Eq.~(\ref{eq:scale-traj})
 %\begin{equation*}\begin{split}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Planning-Scheduling}  %
-\label{sec:algo}               %
-                               %
-This section solves Problems~\ref{pb:cov-pb}--\ref{pb}, i.e., derives a plan in Section~\ref{sec:cov-algo}, and re-plans the plan energy-wise in Section~\ref{sec:repla-algo}.
-
-\subsection{Coverage path planning}
-\label{sec:cov-algo}
-
-There are various approaches in the literature to solve CPP problems, such as Problem~\ref{pb:cov-pb}.
-Approaches that ensure the completeness of the cover are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
-
-An intuitive way to solve the problem is with a back-and-forth motion, sweeping the space delimited by $v$ we term $\mathcal{Q}^v$.
-Although abundant in both mobile ground-based~\cite{choset2001coverage,choset2005principles,lavalle2006planning} and aerial~\cite{araujo2013multiple,artemenko2016energy,cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
-These robots have reduced maneuverability~\cite{dille2013efficient,mannadiar2010optimal,xu2011optimal,xu2014efficient} and are generally unable to fly quick turns~\cite{wang2017curvature}.
-
-To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius.
-It is similar to another motion in the literature termed \emph{Zamboni motion}~\cite{araujo2013multiple},
-but additionally allows variable CPP at the very core of this work.
-The motion, termed \emph{Zamboni-like motion}, is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Figure~\ref{fig:zambo}).
-Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates an edge formed by vertices $v_x,v_y$.
-
-\begin{algorithm}[h]
-  \begin{algorithmic}[1]
-    \small
-    %\STATE $j\gets-1$
-
-    \FORALL{$i\in\mathcal{T}$}
-      \STATE \textbf{if} $\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
-
-%      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}}}
-
-%        \RETURN{$\Gamma$}\vspace*{.3ex}
-%      \ENDIF
-
-      \vspace*{.8ex}
-      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_j}$}
-        \STATE $j\gets j+1$\vspace*{.3ex}
-        \IF{$j\notin[n]_{>0}$}
-          \STATE $j\gets 1$\vspace*{.3ex}
-          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Def.~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
-          parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
-
-          \STATE $\mathbf{p}_{|\Gamma|+1}\gets$ other intersection %in Eq.~(\ref{eq:t1}) 
-          of $\varphi_{|\Gamma|+1}$ and $v$\vspace*{.3ex}
-
-          \STATE $\varphi_{|\Gamma|+2}\gets$ circle %in Eq.~(\ref{eq:v2}) 
-          whose left most point lays on $\mathbf{p}_{|\Gamma|+1}$\vspace*{.3ex}\label{alg2:circ1}
-
-          \STATE $\mathbf{p}_{|\Gamma|+2}\gets$ other inter. %in Eq~(\ref{eq:t2}) 
-          of $\varphi_{|\Gamma|+2}$ and $v$\vspace*{.3ex}
-
-          \STATE $\varphi_{|\Gamma|+3}\gets$ line %in Eq.~(\ref{eq:v3}) 
-          par. to $\varphi_{|\Gamma|+1}$ that inter. $\mathbf{p}_{|\Gamma|+2}$\vspace*{.3ex}
-
-          \STATE $\mathbf{p}_{|\Gamma|+3}\gets$ other inter. %in Eq~(\ref{eq:t3})
-          of $\varphi_{|\Gamma|+3}$ and $v$\vspace*{.3ex}
-
-          \STATE $\varphi_{|\Gamma|+4}\gets$ circle in Eq.\hspace*{.7ex}(\ref{eq:second-circ-gene}) 
-          whose right most point lays\vspace*{.3ex} \hspace*{1em}on $\mathbf{p}_{|\Gamma|+3}$\vspace*{.3ex}\label{alg2:circ2}
-
-          \STATE $\mathbf{p}_{|\Gamma|+4}\gets$ other inter. %in Eq~(\ref{eq:last-trig-gene}) 
-          of $\varphi_{|\Gamma|+4}$ and $v$\vspace*{.3ex}\label{alg2:trig4}
-
-          \vspace*{.8ex}
-          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\ref{def:stage}}\label{alg2:last}
-
-        \ENDIF
-      \ENDIF
-    \ENDFOR
-  \end{algorithmic}
-  \caption{Zamboni-like motion for CPP}\label{alg2}
-\end{algorithm}
-
-Algorithm~\ref{alg2} illustrates the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
-
-%\begin{enumerate*}[label={(\alph*)},font={\textit}]
-%  \item place a line $\varphi_i$ parallel to ${}^{v_1}|_{v_{|v|}}$ that intersects edges ${}^{v_{|v|}}|_{v_{|v-1|}},{}^{v_1}|_{v_2}$ (i.e., first and last),
-%  \item place a circle $\varphi_{i+1}$ whose left most point lays at $\mathbf{p}_{\Gamma_i}$, the intersection of $\varphi_i$ and the edge ${}^{v_{|v|}}|_{v_{|v-1|}}$.
-$\varphi_{i+1}$ intersects $v$ again at $\mathbf{p}_{\Gamma_{i+1}}$,
-%  \item place a line $\varphi_{i+2}$ parallel to $\varphi_i$ that intersects $v$ at $\mathbf{p}_{\Gamma_{i+1}},\mathbf{p}_{\Gamma_{i+2}}$,
-%  \item finally, place a circle $\varphi_{i+3}$ whose right most point lays at $\mathbf{p}_{\Gamma_{i+2}}$ and intersects $v$ again at $\mathbf{p}_{\Gamma_{i+3}}$.
-%\end{enumerate*}
-
-%For ease of notation, the procedure assume that the polygon $v$ is constructed in such a way that the lines $\varphi_{k+1},\varphi_{k+3}$ are never disconnected. %These are
-%\begin{subequations}\label{eq:line-gene}\begin{align}
-%  \varphi_{k+1}&:=x-x_{\Gamma_1}-\lfloor i/4\rfloor x_\mathbf{d},\label{eq:v1}\\
-%  \varphi_{k+3}&:=x-x_{\Gamma_2}-\lfloor i/4\rfloor x_\mathbf{d}\label{eq:v3},
-%\end{align}
-%\end{subequations}
-%where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$, and $\lfloor\,\cdot\,\rfloor$ is the integer division (it has a different meaning with parameters set $c_i$, see Equation~\ref{eq:piece-wise-reg}).
-The circles are
-%\begin{subequations}\label{eq:circ-gene}\begin{align}
-%  \begin{split}\varphi_{i+1}:=(&x-x_{\Gamma_1}-r_1-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_1}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_1^2,\end{split}\label{eq:v2}\\
-%  \begin{split}\varphi_{i+3}:=(&x-x_{\Gamma_2}+r_2-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_3}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_2^2,\label{eq:second-circ-gene}\end{split}
-%\end{align}
-%\end{subequations}
-%where $r_1,r_2\in\mathbb{R}_{>0}$ s.t. $r_1>r_2>\underline{r}$ are radiuses. $r_1=r_2+x_\mathbf{d}/2$, whereas $r_2$ is in Equation~(\ref{eq:r2}).
-
-%Similarly, the triggering points are
-%\begin{subequations}\label{eq:trigs-gene}\begin{align}
-%  \mathbf{p}_{\Gamma_i}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t1}\\
-%  \mathbf{p}_{\Gamma_{i+1}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t2}\\
-%  \mathbf{p}_{\Gamma_{i+2}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t3}\\
-%  \mathbf{p}_{\Gamma_{i+3}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2(r_1\hspace*{-.35ex}-\hspace*{-.35ex}r_2)+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d})\label{eq:last-trig-gene}.
-%\end{align}
-%\end{subequations}
-
 \begin{figure}[t]
@@
   \begin{minipage}[l]{0.25\columnwidth}
-    \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Figure~\ref{fig:il-abs}).}
+    \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Fig.~\ref{fig:il-abs}).}
     \label{fig:tee1}
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Planning-Scheduling}  %
+\label{sec:algo}               %
+                               %
+This section solves Problems~\ref{pb:cov-pb}--\ref{pb}, i.e., derives a plan in Sec.~\ref{sec:cov-algo}, and re-plans the plan energy-wise in Sec.~\ref{sec:repla-algo}.
+
+\subsection{Coverage path planning}
+\label{sec:cov-algo}
+
+There are various approaches in the literature to solve CPP problems, such as Pb.~\ref{pb:cov-pb}.
+Approaches that ensure the completeness of the cover are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
+
+An intuitive way to solve the problem is with a back-and-forth motion, sweeping the space delimited by $v$ we term $\mathcal{Q}^v$.
+Although abundant in both mobile ground-based~\cite{choset2001coverage,choset2005principles,lavalle2006planning} and aerial~\cite{araujo2013multiple,artemenko2016energy,cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
+These robots have reduced maneuverability~\cite{dille2013efficient,mannadiar2010optimal,xu2011optimal,xu2014efficient} and are generally unable to fly quick turns~\cite{wang2017curvature}.
+
+To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius.
+It is similar to another motion in the literature termed \emph{Zamboni motion}~\cite{araujo2013multiple},
+but additionally allows variable CPP at the very core of this work.
+The motion, termed \emph{Zamboni-like motion}, is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}).
+Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates an edge formed by vertices $v_x,v_y$.
+
+Algorithm~\ref{alg2} illustrates the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+
+%\begin{enumerate*}[label={(\alph*)},font={\textit}]
+%  \item place a line $\varphi_i$ parallel to ${}^{v_1}|_{v_{|v|}}$ that intersects edges ${}^{v_{|v|}}|_{v_{|v-1|}},{}^{v_1}|_{v_2}$ (i.e., first and last),
+%  \item place a circle $\varphi_{i+1}$ whose left most point lays at $\mathbf{p}_{\Gamma_i}$, the intersection of $\varphi_i$ and the edge ${}^{v_{|v|}}|_{v_{|v-1|}}$.
+$\varphi_{i+1}$ intersects $v$ again at $\mathbf{p}_{\Gamma_{i+1}}$,
+%  \item place a line $\varphi_{i+2}$ parallel to $\varphi_i$ that intersects $v$ at $\mathbf{p}_{\Gamma_{i+1}},\mathbf{p}_{\Gamma_{i+2}}$,
+%  \item finally, place a circle $\varphi_{i+3}$ whose right most point lays at $\mathbf{p}_{\Gamma_{i+2}}$ and intersects $v$ again at $\mathbf{p}_{\Gamma_{i+3}}$.
+%\end{enumerate*}
+
+%For ease of notation, the procedure assume that the polygon $v$ is constructed in such a way that the lines $\varphi_{k+1},\varphi_{k+3}$ are never disconnected. %These are
+%\begin{subequations}\label{eq:line-gene}\begin{align}
+%  \varphi_{k+1}&:=x-x_{\Gamma_1}-\lfloor i/4\rfloor x_\mathbf{d},\label{eq:v1}\\
+%  \varphi_{k+3}&:=x-x_{\Gamma_2}-\lfloor i/4\rfloor x_\mathbf{d}\label{eq:v3},
+%\end{align}
+%\end{subequations}
+%where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$, and $\lfloor\,\cdot\,\rfloor$ is the integer division (it has a different meaning with parameters set $c_i$, see Eq.~\ref{eq:piece-wise-reg}).
+The circles are
+%\begin{subequations}\label{eq:circ-gene}\begin{align}
+%  \begin{split}\varphi_{i+1}:=(&x-x_{\Gamma_1}-r_1-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_1}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_1^2,\end{split}\label{eq:v2}\\
+%  \begin{split}\varphi_{i+3}:=(&x-x_{\Gamma_2}+r_2-\lfloor i/4\rfloor x_\mathbf{d})^2+\\ (&y-y_{\Gamma_3}-\lfloor i/4\rfloor y_\mathbf{d})^2-r_2^2,\label{eq:second-circ-gene}\end{split}
+%\end{align}
+%\end{subequations}
+%where $r_1,r_2\in\mathbb{R}_{>0}$ s.t. $r_1>r_2>\underline{r}$ are radiuses. $r_1=r_2+x_\mathbf{d}/2$, whereas $r_2$ is in Eq.~(\ref{eq:r2}).
+
+%Similarly, the triggering points are
+%\begin{subequations}\label{eq:trigs-gene}\begin{align}
+%  \mathbf{p}_{\Gamma_i}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t1}\\
+%  \mathbf{p}_{\Gamma_{i+1}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t2}\\
+%  \mathbf{p}_{\Gamma_{i+2}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2r_1+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d}),\label{eq:t3}\\
+%  \mathbf{p}_{\Gamma_{i+3}}&\hspace*{-.35ex}:=(x_{\Gamma_1}\hspace*{-.35ex}+\hspace*{-.35ex}2(r_1\hspace*{-.35ex}-\hspace*{-.35ex}r_2)+\lfloor i/4\rfloor x_\mathbf{d},y_{\Gamma_3}\hspace*{-.35ex}+\hspace*{-.35ex}\lfloor i/4\rfloor y_\mathbf{d})\label{eq:last-trig-gene}.
+%\end{align}
+%\end{subequations}
+
+\begin{algorithm}[t]
+  \begin{algorithmic}[1]
+    \small
+    %\STATE $j\gets-1$
+
+    \FORALL{$i\in\mathcal{T}$}
+      \STATE \textbf{if} $\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+
+%      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}}}
+
+%        \RETURN{$\Gamma$}\vspace*{.3ex}
+%      \ENDIF
+
+      \vspace*{.8ex}
+      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_j}$}
+        \STATE $j\gets j+1$\vspace*{.3ex}
+        \IF{$j\notin[n]_{>0}$}
+          \STATE $j\gets 1$\vspace*{.3ex}
+          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Def.~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
+          parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
+
+          \STATE $\mathbf{p}_{|\Gamma|+1}\gets$ other intersection %in Eq.~(\ref{eq:t1}) 
+          of $\varphi_{|\Gamma|+1}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+2}\gets$ circle %in Eq.~(\ref{eq:v2}) 
+          whose left most point lays on $\mathbf{p}_{|\Gamma|+1}$\vspace*{.3ex}\label{alg2:circ1}
+
+          \STATE $\mathbf{p}_{|\Gamma|+2}\gets$ other inter. %in Eq~(\ref{eq:t2}) 
+          of $\varphi_{|\Gamma|+2}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+3}\gets$ line %in Eq.~(\ref{eq:v3}) 
+          par. to $\varphi_{|\Gamma|+1}$ that inter. $\mathbf{p}_{|\Gamma|+2}$\vspace*{.3ex}
+
+          \STATE $\mathbf{p}_{|\Gamma|+3}\gets$ other inter. %in Eq~(\ref{eq:t3})
+          of $\varphi_{|\Gamma|+3}$ and $v$\vspace*{.3ex}
+
+          \STATE $\varphi_{|\Gamma|+4}\gets$ circle in Eq.\hspace*{.7ex}(\ref{eq:second-circ-gene}) 
+          whose right most point lays\vspace*{.3ex} \hspace*{1em}on $\mathbf{p}_{|\Gamma|+3}$\vspace*{.3ex}\label{alg2:circ2}
+
+          \STATE $\mathbf{p}_{|\Gamma|+4}\gets$ other inter. %in Eq~(\ref{eq:last-trig-gene}) 
+          of $\varphi_{|\Gamma|+4}$ and $v$\vspace*{.3ex}\label{alg2:trig4}
+
+          \vspace*{.8ex}
+          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\ref{def:stage}}\label{alg2:last}
+
+        \ENDIF
+      \ENDIF
+    \ENDFOR
+  \end{algorithmic}
+  \caption{Zamboni-like motion for CPP}\label{alg2}
+\end{algorithm}
+
+To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
+\begin{equation}\label{eq:r2}
+  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
+\end{equation}
+is in function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ and $r$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}). The center than also changes
+\begin{equation}\label{eq:second-circ-gene}
+  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
+\end{equation}
+where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$.
+Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
+The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$ in Def.~\ref{def:primitive}).
+
+Alg.~\ref{alg2} initialize $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the given final point $\mathbf{p}_{\Gamma_l}$.
+Initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
+the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Fig.~\ref{fig:zambo}.
+
 \begin{figure}[t]
@@
   \begin{minipage}[l]{0.25\columnwidth}
-    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Alg.~\ref{alg2}) can be (re)planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
+    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Alg.~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
     \label{fig:zambo}
@@
 
-To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
-\begin{equation}\label{eq:r2}
-  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
-\end{equation}
-is in function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ and $r$ is a given ideal turning radius along with the minimum radius (see Problem~\ref{pb:cov-pb}). The center than also changes
-\begin{equation}\label{eq:second-circ-gene}
-  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
-\end{equation}
-where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$.
-Figure~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
-The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$ in Definition~\ref{def:primitive}).
-
-Algorithm~\ref{alg2} initialize $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
-The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the given final point $\mathbf{p}_{\Gamma_l}$.
-Initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
-the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Figure~\ref{fig:zambo}.
-
-\subsection{Coverage (re)planning-scheduling}
+\subsection{Coverage re-planning-scheduling}
 \label{sec:repla-algo}
@@
 Past literature in planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
-We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Def.~\ref{def:meas}).
 Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use a technique in the literature named output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.
@@
 
-Here, Equation~(\ref{eq:dyn-evol}) is the differential periodic energy model in Equation~(\ref{eq:state-perf}).
-Equation~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}.
-Equation~(\ref{eq:batt-const-mpc}) is the state and output constraints in Lemma~\ref{lem:bat} that requires to evolve the battery model.
-Equation~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation% (e.g., linear Kalman filter)
-with the very first estimate given. Equation~(\ref{eq:ocp-outp-bat}) is the battery SoC, estimated via a flight controller.
+Here, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
+Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Def.~\ref{def:stage}.
+Eq.~(\ref{eq:batt-const-mpc}) is the state and output constraints in Lem.~\ref{lem:bat} that requires to evolve the battery model.
+Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation% (e.g., linear Kalman filter)
+with the very first estimate given. Eq.~(\ref{eq:ocp-outp-bat}) is the battery SoC, estimated via a flight controller.
 
@@
       \STATE $k\gets i$\vspace*{.3ex}\label{alg:bat1}
-      \WHILE{$b_d(C\mathbf{q}(k))>0$}\vspace*{.3ex}
+      \WHILE{$b_d(y(k))>0$}\vspace*{.3ex}
         \IF{$k\in\mathcal{K}$}
@@
         \ENDIF
-        \STATE $b_d(C\mathbf{q}(k+h))\gets${ solve model in Lem.~\ref{lem:bat}}\vspace*{.3ex}
+        \STATE $b_d(y(k+h))\gets${ solve model in Lem.~\ref{lem:bat}}\vspace*{.3ex}
         \STATE $k\gets k+h$\vspace*{.3ex}
@@
       \vspace*{.8ex}
-      \STATE $\hat{\mathbf{q}}(i+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$y(i)$\vspace*{.3ex}\label{alg:klm1}
+      \STATE $\hat{\mathbf{q}}(i+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(i)$\vspace*{.3ex}\label{alg:klm1}
       \STATE $\hat{y}(i+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(i+h)$\vspace*{.3ex}\label{alg:klm2}
@@
   \end{algorithmic}
-  \caption{Coverage (re)planning-scheduling}\label{alg}
+  \caption{Coverage re-planning-scheduling}\label{alg}
 \end{algorithm}
 
-Algorithm~\ref{alg} implements Equation~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware (re)planning-scheduling of $\Gamma$ from Algorithm~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Algorithm~\ref{alg2}.
-
-Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transformed version of the OCP in Equation~(\ref{eq:ocp-output-mpc}) into a non-linear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
+Alg.~\ref{alg} implements Eq.~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware re-planning-scheduling of $\Gamma$ from Alg.~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Alg.~\ref{alg2}.
+
+Line~\ref{alg:mpc} in Alg.~\ref{alg} contains a transformed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a non-linear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
 Its solution leads to both trajectories of parameters and states for future $N$ instants.
 Here, the sets $\mathcal{K},\mathcal{T}$ have possibly a different step $h$, tuning the precision.
-The functions $l_d,b_d$ are merely the discretized versions of Equation~(\ref{eq:ocp-costs}) and Lemma~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc~\cite{iserles2009first}.
+The functions $l_d,b_d$ are merely the discretized versions of Eq.~(\ref{eq:ocp-costs}) and Lem.~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc~\cite{iserles2009first}.
 
 Lines~\ref{alg:bat1}--\ref{alg:bat2} estimate the time needed to completely drain the battery, exploiting the SoC already predicted previously on Line~\ref{alg:mpc}.
-The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using Lemma~\ref{lem:new} and scaling factors from Equation~(\ref{eq:scale-traj}).
-Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensors readings $y$ (e.g., linear Kalman filter~\cite{kalman1960new}).
-
-%The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Problem~\ref{pb}.
+The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using Lem.~\ref{lem:new} and scaling factors from Eq.~(\ref{eq:scale-traj}).
+Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$ (with, e.g., linear Kalman filter~\cite{kalman1960new}).
+
+%The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Pb.~\ref{pb}.
 
@@
 
-%The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
+%The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Def.~\ref{def:mission})
 %\begin{equation*}
@@
 %The algorithm first initializes the position, energy coefficients, and control (line~\ref{alg:init}).
-It updates the position at line~\ref{alg:pos}, using the expression from Equation~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
+It updates the position at line~\ref{alg:pos}, using the expression from Eq.~(\ref{eq:pd}) and the velocity $v\in\mathbb{R}_{\geq 0}$.
 The expression depends on the path $\varphi_i$ from stage $\Gamma_i$.
-The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (FSM in Definition~\ref{def:mission}).
-
-%The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Equation~(\ref{eq:state-perf}).
+The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (FSM in Def.~\ref{def:mission}).
+
+%The energy coefficients are updated at line~\ref{alg:evolution}, using the expression from Eq.~(\ref{eq:state-perf}).
 A priori state estimate $\hat{\mathbf{q}}_k$ is refined using a state estimator--such as Kalman filter (KF)~\cite{simon2006optimal}--and the data from an energy sensor (line~\ref{alg:kalman_end}).
@@
 %\end{split}\end{equation*}
-%where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Equation~(\ref{eq:state-details}).
+%where $\mathrm{diag}(C)$ is a diagonal matrix with the items of $C$ from Eq.~(\ref{eq:state-details}).
 
@@
     \footnotesize
-    \input{\figpath/results/new_physics2/trajs2.tikz}
+    \input{\figpath/results/new_physics2/trajs3.tikz}
     \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
@@
     \footnotesize
-    \input{\figpath/results/new_physics2/ener2.tikz}
+    \input{\figpath/results/new_physics2/ener3.tikz}
     \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$) and parameters ($T,b_0$) evolutions}
@@
 
-%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Figure~\ref{fig:il-abs}). 
-Figure~\ref{fig:il-abs} details the data of a physical flight  
+%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
+Fig.~\ref{fig:il-abs} details the data of a physical flight  
 %We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
 in standard atmospheric conditions. 
-Figure~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
-Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
-The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}).
+Fig.~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Upper-case roman numerals I,II indicate the plans are static (i.e., solely Alg.~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
+The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Sec.~\ref{sec:mod-com}).
 The scheduler varies a computation parameter $c_{i,2}$ relative to ground hazards detection rate from two to ten frames-per-second (FPS).
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros} as well as the scheduler itself.
-The planner varies the path parameter $c_{i,1}$ in Equation~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
+The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algs.~\ref{alg2}--\ref{alg}).
 
@@
 %  \input{\figpath/results/new_physics2/ener_revised.tikz}
-%  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Figure~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
+%  \caption[Energy models of different static and dynamic plans] {The energy models of the paths from Fig.~\ref{fig:trajs} for 200 seconds against the simulated data (\hyperref[fig:ener:static-I]{6.I} and \hyperref[fig:ener:static-II]{6.II}).
 Below are the energy evolutions from the algorithm (\hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii}).
@@
 
-%We implemented a realistic simulator to simulate the empirical data of a given plan and atmospheric conditions. We show the effects of different conditions in Figure~\ref{fig:trajs}.
-
-Figure~\ref{fig:trajs} illustrate same plan $\Gamma$ under different conditions.
+%We implemented a realistic simulator to simulate the empirical data of a given plan and atmospheric conditions. We show the effects of different conditions in Fig.~\ref{fig:trajs}.
+
+Fig.~\ref{fig:trajs} illustrate same plan $\Gamma$ under different conditions.
 Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, wind direction of zero degrees, and an initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
@@
 
-Figure~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
-illustrate the power ($y(i)$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and the energy model ($C\mathbf{q}(i)$ on Line~\ref{alg:evol}).
+Fig.~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
+illustrate the power ($y(i)$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and the energy model ($C\mathbf{q}(i)$ on Line~\ref{alg:evol}).
 Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line) drop at approximately one minute and a half and four minutes and a half.
-Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Definition~\ref{def:const}).
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Def.~\ref{def:const}).
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario.
@@
 The path parameter increases as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter decreases mapping the battery discharge rate.
-For both cases scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature, oder $r$ is three (see Figure~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
+For both cases scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature, oder $r$ is three (see Fig.~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
 %\subsection{Algorithm evaluation}
 %\subsubsection*{Periodic energy model}
-The figure further details the energy model (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model ($C\hat{\mathbf{q}}(i)$), power ($y(i)$), and period ($T$).% We motivate this choice again with Figure~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
+The figure further details the energy model (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}(i)$), power ($\Upsilon(i)$), and period ($T$).% We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
 The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods are sufficient to obtain a consistent state estimate.
@@
 %The practical implementation is based on observations of different variations of paths and computations.
-A variation of path alters the overall flying time, which we reflect in the factors $\nu_{1,1},\tau_{1,1}$ from Equation~(\ref{eq:scale-traj}).
-We compare the remaining flight time with the time needed to completely deplete the battery from Equation~(\ref{eq:bat}).
+A variation of path alters the overall flying time, which we reflect in the factors $\nu_{1,1},\tau_{1,1}$ from Eq.~(\ref{eq:scale-traj}).
+We compare the remaining flight time with the time needed to completely deplete the battery from Eq.~(\ref{eq:bat}).
 We reduce or increase the parameter to optimize the battery time.
-The path parameter $c_{1,1}$ is equal for all the stages and it changes the radius of the first circle in the current period and therefore shifts the other paths accordingly (the change is illustrated in Figure~\ref{fig:tee1}).
+The path parameter $c_{1,1}$ is equal for all the stages and it changes the radius of the first circle in the current period and therefore shifts the other paths accordingly (the change is illustrated in Fig.~\ref{fig:tee1}).
 It results in a shorter or longer distance between the survey lines and in an increment or reduction of the flying time respectively.
@@
 %A variation of computations affects directly the power.
-We thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
+We thus select the highest computation which satisfies the constraints from Def.~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
 We observed a low effect on the power of the communication ROS node.
@@
 
-%Subfigures \hyperref[fig:trajs-dyn-i]{5.i}--\hyperref[fig:trajs-dyn-ii]{5.ii} in Figure~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii} of Figure~\ref{fig:ener} energy-wise.
+%Subfigures \hyperref[fig:trajs-dyn-i]{5.i}--\hyperref[fig:trajs-dyn-ii]{5.ii} in Fig.~\ref{fig:trajs} path-wise, and \hyperref[fig:ener-dyn-i]{6.i} and \hyperref[fig:ener-dyn-ii]{6.ii} of Fig.~\ref{fig:ener} energy-wise.
 For the first path (Subfigure \hyperref[fig:trajs-I-static]{5.I}) the plan starts at the highest configuration of parameters.
@@
 Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates energy of the computing hardware via the \powprof{} tool.
-The approach compromises two algorithms: one derives a static coverage plan, whereas the other (re)plans-schedules the plan on a finite horizon via MPC.
+The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC.
 It evolves the state of the energy model while optimizing the battery usage.
@@
 
-\section{Proof of Lemma~\ref{lem:eqv}}
+\section{Proof of Lem.~\ref{lem:eqv}}
 \label{app:proof-eqv}
 
-We propose a formal proof of Lemma~\ref{lem:eqv}.
-The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ in Equation~(\ref{eq:state-details}).
+We propose a formal proof of Lem.~\ref{lem:eqv}.
+The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ in Eq.~(\ref{eq:state-details}).
 We write these elements such that the coefficients of the series $a_0,\dots,b_r$ are the same as the coefficients of the state $\alpha_0,\dots,\beta_r$.
 
-Let us re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
+Let us re-write the Fourier series expression in Eq.~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
 With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively.
@@
 The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$.
-Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
+Both the solution and the system in Eq.~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
 To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
@@
 
-We apply the approach in terms of Equation~(\ref{eq:state-perf}), under the assumptions made in the lemma (the control is a zero vector); $\dot{\mathbf{q}}=A\mathbf{q}$.
+We apply the approach in terms of Eq.~(\ref{eq:state-perf}), under the assumptions made in the lemma (the control is a zero vector); $\dot{\mathbf{q}}=A\mathbf{q}$.
 The linear combination of the initial guess and the generic solution
@@
 
-Let us consider the second expression in Equation~(\ref{eq:proof-comb}).
+Let us consider the second expression in Eq.~(\ref{eq:proof-comb}).
 It represents the linear combination of all the coefficients of the state at time $t$.
@@
 
-We proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Equation~(\ref{eq:proof-output}) is equivalent to Equation~(\ref{eq:proof-complex}).
+We proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
 
@@
 
-Thereby we start by proofing that the first terms of the Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+Thereby we start by proofing that the first terms of the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
 We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
@@
 
-Then, we proof that all the terms in the sum of both the Equations~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+Then, we proof that all the terms in the sum of both the Eqs.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
 
@@
 The initial guess is build such that the sum of the coefficients is the same in both the signals.
-In the output matrix, the frequency $1/T$ accounts for the period in Equation~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier}).
+In the output matrix, the frequency $1/T$ accounts for the period in Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier}).
 At time instant zero, the coefficients $b_j$ are not present and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$ (thus we multiply by a half the corresponding coefficients in $\mathbf{q}_0$).
@@
 
-\section{Proof of Lemma~\ref{lem:new}}
+\section{Proof of Lem.~\ref{lem:new}}
 \label{app:proof-new}
 
-\section{Proof of Lemma~\ref{lem:bat}}
+\section{Proof of Lem.~\ref{lem:bat}}
 \label{app:proof-bat}

### 2021-12-05 energy-planning.tex
fixes and polishing (2)

@@
 The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool.
-Accounting for uncertainty, an initial ``plan-schedule'' is replanned and rescheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
+Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
 \end{abstract}
@@
   \begin{minipage}[l]{0.35\columnwidth}
-    \caption{Defs.~\ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$.
+    \caption{Defs.~\ref{def:plan}--\hyperref[def:trigs]{4} on a slice of the plan $\Gamma$.
 $\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$.
@@
 Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries.
-For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.
+For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.
 
@@
 
-Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ indicates the set of integers.
+Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ denotes the set of integers.
 At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
@@
 
-The notation $[\,\cdot\,]$ indicates positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
+The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
 For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.
@@
 The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
-the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bounds of a parameter $\cdot\,$, i.e.,
+the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ denotes the upper/lower bounds of a parameter $\cdot\,$, i.e.,
 \begin{equation}
@@
 \end{equation}
-
-%'\>o-O</'
 
@@
 
-Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\ref{def:trigs}.
+Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\hyperref[def:trigs]{4}.
 $\varphi_0,\dots,\varphi_5$ are path functions.
 $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines.
-They are relative to different stages $\Gamma_1,\Gamma_2,\dots$ but $\Gamma_0$, the stating stage.
-The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure.
+They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$.
+%The constraint set $\mathcal{C}_{4,1}$ forms the area where
+It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure.
 %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
@@
 
-Here, $c_i$ indicates a row vector that contains both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$, where $\,\cdot\,'$ is the transpose of $\cdot\,$.
-The path parameters in the definition have a constant distance per each value in $[n]_{>0}$, i.e.,
+In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
 \begin{equation}\label{eq:primitive}\begin{split}
@@
 Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}.
-A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
-$t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{\geq 0}$.
+A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
+$t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{> 0}$.
 $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.
@@
 \vspace*{-2ex}
-\subsection{Problem formulation}
+\subsection{Energy-aware planning-scheduling problem}
 \label{sec:pbfor}
@@
 
-For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ indicates the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
+For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ denotes the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
 .
 
-\begin{pb}[Planning problem]
+\begin{pb}[Re-planning-scheduling problem]
   \label{pb}
   Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}.
-The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
+The \emph{re-planning-scheduling problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
 \end{pb}
+
+Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$.
+The notation $\,\cdot\,'$ denotes the transpose of $\cdot\,$.
 
@@
                          %
-The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of given path and computations parameters on the battery at future time instants.
-To this end, Secs.~\ref{sec:mod-mot}--\ref{sec:mod-bat} provide models for the motion and computations energies and battery.
+The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants.
+To this end, Secs.~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the motion and computations energies and battery.
 
@@
 Let us return to the collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
-Energy data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
+The data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
 It indicates that to model the energy, three frequencies are adequate.
@@
 
-The model in Equation~(\ref{eq:fourier}) does not the quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules results in different instantaneous energy.
+The model in Equation~(\ref{eq:fourier}) does not quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules result in different instantaneous energy.
 For this latter purpose, we use another model
@@
 
-Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains proofs of Lems.~\ref{lem:eqv}--\ref{lem:new}.
-
-Using the same notation from Lemma~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
+Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains the proofs of Lemmas.~\ref{lem:eqv}--\hyperref[lem:new]{2}.
+
+Using the same notation from Lem.~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
 \begin{equation}
@@
 
-Let us assume that the time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
+Let us assume for ease of notation that the coverage time evolves linearly.
+Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
   \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
@@
 
-Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with scaling factors
+Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with %scaling factors
 \begin{subequations}\label{eq:scale-comp}\begin{align}
@@
 \end{equation}
-where $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.
-
+where $B\in\mathbb{R}^{m\times n}$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones.
+
+\vspace*{-1.5ex}
 \subsection{Energy model for the computations}
@@
 
-Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware or software specific parameters.
-This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis aiding to quantify the computations energy of any combination of computations $c_i^\sigma$ withing the bounds (see Def.~\ref{def:stage}).
-
-The model relies on an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source M.I.T.
-license.
+Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
+This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Def.~\ref{def:stage}).
+
+The model compromises an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source MIT license.
 It is segmented into two layers.
-In the \emph{measurement layer} the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piece-wise linear regression.
-
-Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperometer, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
+In the \emph{measurement layer}, the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piecewise linear regression.
+
+Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
 
@@
 \begin{defn}[Predictive layer]\label{def:pred}
-  Given a measuring device and computations parameters the \emph{predictive layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns and energy measure.
+  Given a measuring device and computations parameters, the \emph{predictive layer} is the function $g:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns an energy measure.
 \end{defn}
 
-The energy measures in Defs.~\ref{def:meas}--\ref{def:pred} can be either average or overall energy.
-Additionally, the tool supports the measures of battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}.
-The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}) assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
+The energy measures in Defs.~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall.
+Additionally, the tool supports the battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}.
+The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
 \begin{equation}\label{eq:piece-wise-reg}\begin{split}
@@
 \end{split}\end{equation}
-where the notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
+where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
 The measuring device in both $\mathbf{g}$ and $g$ is implicit.
@@
 
-The battery model predicts the battery SoC in function of a given load for future time instants.
-There are multiple possible models in the literature~\cite{rao2003battery}, with varying accuracy, complexity, and easy of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of ease of implementation and accuracy.
-
-We model a Li-ion battery of an aerial robot flying with an abstract model referred to as ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+The battery model predicts the battery SoC in the function of a given load at future time instants.
+There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two.
+
+We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
 
@@
 
-Appendix~\ref{app:proof-bat} contains a proof of Lem.~\ref{lem:bat}.
-
-Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$. Let us re-evaluate the output constraint with Lem.~\ref{lem:bat}.
-
-\begin{defn}[Output constraint]
-  \label{def:const}
+App.~\ref{app:proof-bat} contains the proof of Lem.~\ref{lem:bat}.
+
+Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, conflicting with the findings in Lem.~\ref{lem:bat}.
+
+\begin{defn}[Output constraint]\label{def:const}
   \begin{equation*}
@@
   \end{equation*}
-  is the \emph{output constraint}, where $b(y(t))Q_cV$ is the maximum instantaneous energy consumption.
+  is the \emph{output constraint}, where $b(y(t))Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Lem.~\ref{lem:bat}.
 \end{defn}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Planning-Scheduling}  %
+\label{sec:algo}               %
+                               %
 \begin{figure}[t]
@@
   \begin{minipage}[l]{0.25\columnwidth}
-    \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Fig.~\ref{fig:il-abs}).}
+    \caption{Alteration of the path parameter $c_{i,1}$, the radius of the circle (i.e., the alteration of the plan in Fig.~\ref{fig:il-abs}).
+    }
     \label{fig:tee1}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Planning-Scheduling}  %
-\label{sec:algo}               %
-                               %
-This section solves Problems~\ref{pb:cov-pb}--\ref{pb}, i.e., derives a plan in Sec.~\ref{sec:cov-algo}, and re-plans the plan energy-wise in Sec.~\ref{sec:repla-algo}.
-
-\subsection{Coverage path planning}
+The section solves Problems~\ref{pb:cov-pb}--\hyperref[pb]{2}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise %respectively
+in Secs.~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
+
+\vspace*{-1.4ex}
+\subsection{Coverage}
 \label{sec:cov-algo}
@@
 To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius.
-It is similar to another motion in the literature termed \emph{Zamboni motion}~\cite{araujo2013multiple},
-but additionally allows variable CPP at the very core of this work.
-The motion, termed \emph{Zamboni-like motion}, is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}).
-Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates an edge formed by vertices $v_x,v_y$.
-
-Algorithm~\ref{alg2} illustrates the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work.
+The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}).
+
+Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
+Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$.
+Nonetheless, complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.
 
@@
           \vspace*{.8ex}
-          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\ref{def:stage}}\label{alg2:last}
+          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}
 
@@
 \end{equation}
-is in function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ and $r$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}). The center than also changes
+and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ where $r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}).
+The center also changes
 \begin{equation}\label{eq:second-circ-gene}
@@
 
-Alg.~\ref{alg2} initialize $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+Alg.~\ref{alg2} initializes $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
 The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the given final point $\mathbf{p}_{\Gamma_l}$.
-Initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
+The initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
 the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Fig.~\ref{fig:zambo}.
@@
 
-\subsection{Coverage re-planning-scheduling}
+\vspace*{-1.4ex}
+\subsection{Re-planning-scheduling}
 \label{sec:repla-algo}
@@
 
-An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories, $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ given initial and final cost functions
+An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
 \begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
@@
   \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
-  b(y(t_0))&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat}.
+  b(y(t_0))&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat},
 \end{align}\end{subequations}
-
-Here, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
+where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ given initial and final cost functions.
+Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
 Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Def.~\ref{def:stage}.
-Eq.~(\ref{eq:batt-const-mpc}) is the state and output constraints in Lem.~\ref{lem:bat} that requires to evolve the battery model.
-Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation% (e.g., linear Kalman filter)
-with the very first estimate given. Eq.~(\ref{eq:ocp-outp-bat}) is the battery SoC, estimated via a flight controller.
+Eq.~(\ref{eq:batt-const-mpc}) is the state and output constraints in Def.~\ref{def:const} that evolves the battery model in Lem.~\ref{lem:bat}.
+Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
+(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.
 
@@
       \STATE $t_b\gets k-i$\vspace*{.3ex}\label{alg:bat2}
+      \vspace*{-1.4ex}
       \STATE $t_s\gets(\mathrm{diag}(\nu_j^\rho)\vspace*{.3ex}c_j^\rho(i)+\tau_j^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
@@
 
-Alg.~\ref{alg} implements Eq.~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware re-planning-scheduling of $\Gamma$ from Alg.~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Alg.~\ref{alg2}.
-
-Line~\ref{alg:mpc} in Alg.~\ref{alg} contains a transformed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a non-linear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
+Line~\ref{alg:mpc} in Alg.~\ref{alg} contains a transformed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
 Its solution leads to both trajectories of parameters and states for future $N$ instants.
-Here, the sets $\mathcal{K},\mathcal{T}$ have possibly a different step $h$, tuning the precision.
-The functions $l_d,b_d$ are merely the discretized versions of Eq.~(\ref{eq:ocp-costs}) and Lem.~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc~\cite{iserles2009first}.
+Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude), tuning the precision.
+The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:ocp-costs}) and Lem.~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc.~\cite{iserles2009first}.
 
@@
 The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using Lem.~\ref{lem:new} and scaling factors from Eq.~(\ref{eq:scale-traj}).
-Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$ (with, e.g., linear Kalman filter~\cite{kalman1960new}).
+Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear
+Kalman filter~\cite{kalman1960new}.
+
+Alg.~\ref{alg} implements Eq.~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware re-planning-scheduling of $\Gamma$ from Alg.~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Alg.~\ref{alg2}.
 
@@
     \input{\figpath/results/new_physics2/ener3.tikz}
-    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$) and parameters ($T,b_0$) evolutions}
+    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$), and parameters ($T,b_0$) evolutions}
     \label{fig:ener}
@@
 
+\vspace*{-1.6ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:experimental}  %
-
+                          %
 %$\subsection{Experimental setup}
@@
 in standard atmospheric conditions. 
-Fig.~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Fig.~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R).
 Upper-case roman numerals I,II indicate the plans are static (i.e., solely Alg.~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
-The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Sec.~\ref{sec:mod-com}).
-The scheduler varies a computation parameter $c_{i,2}$ relative to ground hazards detection rate from two to ten frames-per-second (FPS).
+The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Sec.~\ref{sec:mod-com}).
+The scheduler varies a computation parameter $c_{i,2}$ relative to the ground hazards detection rate from two to ten frames-per-second (FPS).
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros} as well as the scheduler itself.
 The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algs.~\ref{alg2}--\ref{alg}).
+The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.
 
@@
 
-Fig.~\ref{fig:trajs} illustrate same plan $\Gamma$ under different conditions.
-Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, wind direction of zero degrees, and an initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
+Fig.~\ref{fig:trajs} illustrates the same plan $\Gamma$ under different conditions.
+Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
 Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
@@
 Fig.~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
-illustrate the power ($y(i)$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and the energy model ($C\mathbf{q}(i)$ on Line~\ref{alg:evol}).
-Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line) drop at approximately one minute and a half and four minutes and a half.
+illustrates first the power ($\Upsilon(i)$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and then the energy model ($y(i)$ on Line~\ref{alg:evol}).
+Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line, the battery behavior $b_0(i)$) drop at approximately one minute and a half and four minutes and a half.
 Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Def.~\ref{def:const}).
@@
 The path parameter increases as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter decreases mapping the battery discharge rate.
-For both cases scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature, oder $r$ is three (see Fig.~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
+For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,kang2009linear,stastny2018nonlinear,chao2011collision}, order $r$ is three (see Fig.~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
 %\subsection{Algorithm evaluation}
 %\subsubsection*{Periodic energy model}
-The figure further details the energy model (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}(i)$), power ($\Upsilon(i)$), and period ($T$).% We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
+The figure further details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}(i)$), power ($\Upsilon(i)$), and period ($T$).
+% We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
 The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods are sufficient to obtain a consistent state estimate.
@@
 It hence approximates the non-periodicity with a linear model.
+
+Output MPC on Line~\ref{alg:mpc} relies on a software framework for nonlinear optimization called CasADi~\cite{andersson2012casadi,andersson2012bcasadi,andersson2019casadi}, and the popular NLP solver IPOPT~\cite{wachter2006implementation}.
 
@@
 
+\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
-Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates energy of the computing hardware via the \powprof{} tool.
+Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool.
 The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC.
-It evolves the state of the energy model while optimizing the battery usage.
+It evolves the state of the energy model while optimizing battery usage and remedying possible defects.
 The plan compromise multiple stages, where at each the aerial robot flies a path and does some computations, allowing further extensibility in terms of constructs and approaches.
 
-Indeed, we are currently extending the results to a standard flight controller.
-The guidance on the coverage needs alike further investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
-Here, our initial investigation led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
+Indeed, we are currently extending the results to a standard flight controller. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
+and distributed planning-scheduling merits alike further investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
+Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
+
+%'\>o-O</'
 

### 2021-12-08 energy-planning.tex
fixes and proofreading of the appendices

@@
 
-\usepackage{afterpage}
+%\usepackage{afterpage}
 
@@
 
-\usepackage{balance}
+%\usepackage{balance}
 
@@
 \author{
-  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, %Henrik Skov Midtiby$^{\text{1}}$, 
-  and Ulrik Pagh Schultz$^{\text{1}}$
+  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
   %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
@@
   \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
-  \thanks{$^{\text{1}}$A. S. %, H. S. M.,
-  and U. P. S. are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense. Email: {\tt\footnotesize ads@mmmi.sdu.dk};} 
+  \thanks{$^{\text{1}}$A.
+S., H.
+S.
+M.,  and U.
+P.
+S.
+are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense.
+Email: {\tt\footnotesize ads@mmmi.sdu.dk};}
   \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Complutense de Madrid, Spain.}
@@
 
-Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains the proofs of Lemmas.~\ref{lem:eqv}--\hyperref[lem:new]{2}.
+Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contain the proofs of Lemmas~\ref{lem:eqv}--\hyperref[lem:new]{2}.
 
@@
 \begin{equation}
-  \hat{\mathbf{u}}(t):=\mathrm{diag}(\nu_i)c_i(t)+\tau_i
+  \hat{\mathbf{u}}(t):=\mathrm{diag}(\nu_i)c_i(t)+\tau_i,
 \end{equation}
@@
   \footnotesize
-  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground hazards detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}), i.e., wind speed and direction, battery behavior, and parameters initial values.}
+  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}), i.e., wind speed and direction, battery behavior, and parameters initial values.}
   \label{fig:res}
@@
 The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Sec.~\ref{sec:mod-com}).
-The scheduler varies a computation parameter $c_{i,2}$ relative to the ground hazards detection rate from two to ten frames-per-second (FPS).
+The scheduler varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames-per-second (FPS).
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros} as well as the scheduler itself.
@@
 
+% appendix, title all on one line
+\renewcommand{\thesectiondis}[2]{\Alph{section}:}
+
+\vspace*{-1ex}
 \section{Proof of Lem.~\ref{lem:eqv}}
-\label{app:proof-eqv}
-
-We propose a formal proof of Lem.~\ref{lem:eqv}.
-The proof justifies the choice of the items of the matrices $A,C$ and of the initial guess $\mathbf{q}_0$ in Eq.~(\ref{eq:state-details}).
-We write these elements such that the coefficients of the series $a_0,\dots,b_r$ are the same as the coefficients of the state $\alpha_0,\dots,\beta_r$.
-
-Let us re-write the Fourier series expression in Eq.~(\ref{eq:fourier}) in its complex form with the well-known Euler's formula $e^{it}=\cos{t}+i\sin{t}$.
-With $t=\omega jt$, we find the expression for $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively.
-This leads~\cite{kuo1967automatic}
-\begin{equation}\begin{split}\label{eq:proof-complex}
-  h(t)=a_0/T+&(1/T)\sum_{j=1}^{r}{e^{i\omega jt}(a_j-ib_j)}+\\&(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}(a_j+ib_j)},
- \end{split}\end{equation}
-where $i$ is the imaginary unit.
-
-The solution at time $t$ can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$.
-Both the solution and the system in Eq.~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
-To solve the matrix exponential $e^{At}$, we use the eigenvectors matrix decomposition method~\cite{moler2003nineteen}.
-
-The method works on the similarity transformation $A=VDV^{-1}$.
+\label{app:proof-eqv}{\small
+
+The proof justifies the items of $A, C,$ and $\mathbf{q}_0$ in Lem.~(\ref{lem:eqv}), s.t.
+the coefficients of the series $a_0,\dots,b_r$ equal the coefficients $\alpha_0,\dots,\beta_r$ of the state $\mathbf{q}$.
+
+Firstly, it is convenient to re-write Eq.~(\ref{eq:fourier}) in complex form, with, e.g., $e^{it}=\cos{t}+i\sin{t}$.
+Given $t=\omega jt$, $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively~\cite{kuo1967automatic}.
+Then
+\vspace*{-.8ex}\begin{equation}\label{eq:proof-complex}\vspace*{-.8ex}
+  h(t)\hspace*{-.4ex}=\hspace*{-.4ex}a_0/T\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}-\hspace*{-.4ex}ib_j)}\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}+\hspace*{-.4ex}ib_j)},\vspace*{-.8ex}
+\end{equation}
+where $i$ is this time the imaginary unit.
+
+Secondly, the solution at $t$ of Eq.~(\ref{eq:state-perf}) can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$~\cite{ogata2002modern}.
+%Both the solution and the system in Eq.~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
+Here, a method to solve the matrix exponential $e^{At}$ is the eigenvectors matrix decomposition method~\cite{moler2003nineteen} by exploiting the similarity transformation $A=VDV^{-1}$.
 The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}.
-We consider the non-singular matrix $V$, whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_0 & v_1^0 & v_1^1 & \dots & v_r^0 & v_r^1\end{bmatrix}$.
-We then consider the diagonal matrix of eigenvalues $D=\mathrm{diag}{(\lambda_0,\lambda_1^0,\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)}$.
-$\lambda_0$ is the eigenvalue associated to the first item of $A$.
+
+Within this expression, we consider the non-singular matrix $V$, whose columns are eigenvectors of $A$, $V:=[\begin{matrix}v_0 & v_1^0 & v_1^1 & \dots\end{matrix}$ $\begin{matrix}v_r^0 & v_r^1\end{matrix}]$, and the diagonal matrix of eigenvalues, $D=\mathrm{diag}(\lambda_0,\lambda_1^0,$ $\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)$.
+$V$ is built s.t.
+$\lambda_0$ is the eigenvalue associated with the first item of $A$.
 $\lambda_j^0,\lambda_j^1$ are the two eigenvalues associated with the block $A_j$.
-We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, and $AV=VD$.
-
-We apply the approach in terms of Eq.~(\ref{eq:state-perf}), under the assumptions made in the lemma (the control is a zero vector); $\dot{\mathbf{q}}=A\mathbf{q}$.
-The linear combination of the initial guess and the generic solution
-\begin{equation}\label{eq:proof-comb}\begin{split}
-  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}}\\
-  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}
-\end{split}\end{equation}
-where $F=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is a properly sized vector of ones.
-
-Let us consider the second expression in Eq.~(\ref{eq:proof-comb}).
-It represents the linear combination of all the coefficients of the state at time $t$.
-It can also be expressed in the following form
-\begin{equation}\label{eq:proof-output}\begin{split}
-  F\mathbf{q}(t)/T=\gamma_0 e^{\lambda_0t}v_0/T+&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+\\&(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
-\end{split}\end{equation}
-
-We proof that the eigenvalues $\mathbf{\lambda}$ and eigenvectors $V$ are such that Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
-
-The matrix $A$ is a block diagonal matrix, so we can express its determinant as the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
-We proof the first determinant and the others separately.
-
-Thereby we start by proofing that the first terms of the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
-We find the eigenvalue from $\det(0)=0$, which is $\lambda_0=0$.
-The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=\begin{bmatrix} 0 & \cdots & 0 \end{bmatrix}\,\,\,\forall v_0$, thus we choose $v_0=\begin{bmatrix}1 & 0 & \cdots & 0\end{bmatrix}$.
-We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal, $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.
-
-Then, we proof that all the terms in the sum of both the Eqs.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
-
-For the first block $A_1$, we find the eigenvalues from $\det(A_1-\lambda I)=0$.
-The polynomial $\lambda^2+\omega^2$, gives two complex roots--the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
-The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}0 & -i&1&0&\cdots&0\end{bmatrix}^T$.
-The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}0&i&1&0&\cdots&0\end{bmatrix}^T$.
+$Av_j=\lambda_jv_j\,,\forall j\in[m]_{>0}$, and so $AV=VD$.
+
+%The approach in terms of Eq.~(\ref{eq:state-perf}) %, under the assumptions made in the lemma (the control is a zero vector);
+%is $\dot{\mathbf{q}}=A\mathbf{q}$.
+The linear combination of the initial guess in Lem.~\ref{lem:new} and the generic solution of Eq.~(\ref{eq:state-perf})
+\vspace*{-1.6ex}\begin{subequations}\label{eq:proof-comb}\begin{align}
+  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}},\\\vspace*{-.8ex}
+  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}},\vspace*{-.8ex}
+\end{align}\end{subequations}
+where $F:=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is simply a properly sized vector of ones.
+
+The second expression in Eq.~(\ref{eq:proof-comb}) is the linear combination of all the coefficients of the state at time $t$. By dividing the expression with the period
+\vspace*{-1.6ex}\begin{equation}\label{eq:proof-output}
+  F\mathbf{q}(t)/T\hspace*{-.4ex}=\hspace*{-.4ex}\gamma_0 e^{\lambda_0t}v_0/T+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
+\end{equation}
+
+Finally, we prove that the eigenvalues $\lambda_0,\lambda_1^0,\lambda_1^1,\dots$ and eigenvectors in $v_0,v_1^0,v_1^1,\dots$ are such that Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
+
+The matrix $A$ is a block diagonal matrix, s.t. its determinant is the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
+
+The first terms of the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+The eigenvalue from $\det(0)=0$ is $\lambda_0=0$.
+The corresponding eigenvector can be chosen arbitrarily $(0-\lambda_0)v_0=\begin{bmatrix} 0 & \cdots & 0 \end{bmatrix}\,\,\,\forall v_0$, e.g., $v_0=\begin{bmatrix}1 & 0 & \cdots & 0\end{bmatrix}$.
+We find the value $\gamma_0$ of the vector $\gamma$ so that the terms are equal, e.g., $\gamma_0=\begin{bmatrix}a_0 & 0 & \cdots & 0\end{bmatrix}$.
+
+All the terms in the sum of both the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+For the first block $A_1$, the eigenvalues are found by $\det(A_1-\lambda I)=0$.
+The polynomial $\lambda^2+\omega^2$, gives two complex roots, the two eigenvalues $\lambda_1^0=i\omega$ and $\lambda_1^1=-i\omega$.
+The eigenvector associated with the eigenvalue $\lambda_1^0$ is $v_1^0=\begin{bmatrix}0 & -i&1&0&\cdots&0\end{bmatrix}'$.
+The eigenvector associated with the eigenvalue $\lambda_1^1$ is $v_1^1=\begin{bmatrix}0&i&1&0&\cdots&0\end{bmatrix}'$.
 Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences
-\begin{equation*}\begin{cases}
+\begin{equation}\begin{cases}
   e^{i\omega t}(a_1-ib_1)&=\gamma_1 e^{i\omega t}v_1^0\\
   e^{-i\omega t}(a_1+ib_1)&=\gamma_1 e^{i\omega t}v_1^1
-\end{cases}\end{equation*}
-hold. They hold for $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+\end{cases},\end{equation}
+hold, e.g., $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
 
@@
 
-The initial guess is build such that the sum of the coefficients is the same in both the signals.
-In the output matrix, the frequency $1/T$ accounts for the period in Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier}).
-At time instant zero, the coefficients $b_j$ are not present and the coefficients $a_j$ are doubled for each $j=1,2,\dots,r$ (thus we multiply by a half the corresponding coefficients in $\mathbf{q}_0$).
-To match the outputs $h(t)=y(t)$--or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$--we define $C=(1/T)\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
-We thus conclude that the signal and the output are equal, hence the lemma holds.
-
-\qed
-
-We note for practical reasons that the signal would still be periodic with another linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
-
+The initial guess is constructed s.t.
+the sum of the coefficients is the same in both Eq.~(\ref{eq:proof-output}) and~(\ref{eq:proof-complex}).
+In the output matrix, the frequency $1/T$ accounts for the period% in Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier})
+.
+At time instant zero, the coefficients $b_j$ are not present, and the coefficients $a_j$ are doubled for each $j=[r]_{>0}$ (thus we multiply by one-half the corresponding coefficients in $\mathbf{q}_0$).
+To match the outputs $h(t)=y(t)$, or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$, $C=(1/T)\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
+Eq.~(\ref{eq:proof-output}) and Eq.~(\ref{eq:proof-complex}) are thus equal.
+Eq.~(\ref{eq:proof-complex}) is merely the complex form of Eq.~(\ref{eq:fourier}).
+
+%\qed
+%Periodicity is preserved with other linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
+}
+
+\vspace*{-1ex}
 \section{Proof of Lem.~\ref{lem:new}}
-\label{app:proof-new}
-
+\label{app:proof-new}{\small
+
+A change in computations parameters in Lem.~\ref{lem:new} results in different schedules on the computing hardware, which we assumed in Sec.~\ref{sec:intro} affects the instantaneous energy, i.e., computations are energy expensive computational tasks.
+
+A change in the path parameters in Lem.~\ref{lem:new} alters the flight time, and consequently, the energy.
+The proof quantifies this time: consider the plan $\overline{\Gamma}$ in Fig.~\ref{fig:zambo}.
+It is composed of four primitive paths and the highest configuration of path parameter $c_{i,1}$.
+Let assume that the time to travel $\varphi_4(\overline{c}_{i,1})$ is $t_3\in\mathbb{R}_{>0}$, $\varphi_1,\varphi_3$, the two lines, is $2t_1\in\mathbb{R}_{>0}$, and $\varphi_2$ is $t_2\in\mathbb{R}_{>0}$.
+Further, assume that $v$ is covered merely by the set of primitive paths in Fig.~\ref{fig:zambo}.
+The coverage time is $t_{\overline{\Gamma}}=7(2t_1+t_2+t_3)+t_1$.
+
+Conversely, assume the time needed to travel $\varphi_4(\underline{c}_{i,1})$ is $t_4\in\mathbb{R}_{>0}$.
+Then $t_{\underline{\Gamma}}=3(2t_1+t_2+t_4)+t_1$, and $t_{\overline{\Gamma}}>t_{\underline{\Gamma}}$ even under the unrealistic assumption $t_3\approxeq t_4$.
+
+%\qed
+}
+
+\vspace*{-1ex}
 \section{Proof of Lem.~\ref{lem:bat}}
-\label{app:proof-bat}
-
-%The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}
-%\begin{equation}
-%  \dot{b}(y(t))=-I(y(t))/Q_c
-%\end{equation}
-%where  $y(t)\in\mathbb{R}_{\geq 0}$ is a power drain, $I(y(t))\in\mathbb{R}$ the internal current, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
-The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohms representing the battery resistance.
-The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V_e,V\in\mathbb{R}$ the the external and internal battery voltages measured in volts.
-The latter can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
-
-%Using simply
+\label{app:proof-bat}{\small
+
+The proof justifies the expression in Lem.~\ref{lem:bat}.
+
+The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
+\begin{equation}
+  \dot{b}(y(t))=-I(y(t))/Q_c,
+\end{equation}
+where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity in Lem.~\ref{lem:bat}.
+The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ in Lem.~\ref{lem:bat}, representing the battery resistance.
+The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts.
+The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
+
+If the voltage of the power drain is stable, Kirchhoff's circuit laws lead to $V_sI_l=V_eI$, where $I_l$ is the current required by the load measured in amperes.
+Combining $V_e,V_sI_l$ results in the quadratic expression $R_rI^2-VI+V_sI_l=0$.
+Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero)% results in
+\begin{equation}
+I(y)=(V-\sqrt{V^2-4R_ry(t)})/(2R_r),
+\end{equation} 
+as in Lem.~\ref{lem:bat}.
+
+%\qed
+
+}
+
+\leavevmode\thispagestyle{empty}\newpage
+\leavevmode\thispagestyle{empty}\newpage
 

### 2021-12-08 energy-planning.tex
proofreading before internal review

@@
 
-%% citation packege
+%% citation package
 \usepackage{cite}
@@
 
-% counter to mantain the line numbering
+% counter to maintain the line numbering
 \newcommand{\setalglineno}[1]{%
@@
 An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}).
-Follow the collected energy data of a physical aerial robot flying the use case.}
+Follow the collected energy data of a physical aerial robot flying the coverage.}
   \label{fig:il-abs}
@@
 
-To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (e.g., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.).
+To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.).
 Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
@@
 The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model} for the computations and motion energies and battery models.
+In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
@@
 Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives.
-Appendices provide supplementary information.
+Appendices provide supplementary material.
 
@@
     \centering
-    \caption{Plan $\Gamma$ with $n$ primitve stages  in Def~\ref{def:primitive}.}
+    \caption{Plan $\Gamma$ with $n$ primitive stages  in Def~\ref{def:primitive}.}
     \label{fig:state-machine-loop}
@@
 
-Let us return to the collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
+Collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs} illustrate the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
 The data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
@@
 
-\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), and the initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
+\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
   \begin{equation*}
@@
 
-Let us assume for ease of notation that the coverage time evolves linearly.
+Let assume for ease of notation that the coverage time evolves linearly.
 Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
@@
 \end{align}\end{subequations} 
-$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$.
+$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$)
 
@@
 
-Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
+Let assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
 
@@
 
-We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' ECM in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
 
@@
 It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work.
-The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}).
-
-Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
+The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
+
+Let assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
 Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
@@
 
-    \FORALL{$i\in\mathcal{T}$}
-      \STATE \textbf{if} $\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+    \FORALL{$t\in\mathcal{T}$}
+      \STATE \textbf{if} $\mathbf{p}(t)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
 
@@
       \vspace*{.8ex}
-      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_j}$}
-        \STATE $j\gets j+1$\vspace*{.3ex}
-        \IF{$j\notin[n]_{>0}$}
-          \STATE $j\gets 1$\vspace*{.3ex}
+      \IF{$\mathbf{p}(t)=\mathbf{p}_{\Gamma_i}$}
+        \STATE $i\gets i+1$\vspace*{.3ex}
+        \IF{$i\notin[n]_{>0}$}
+          \STATE $i\gets 1$\vspace*{.3ex}
           \STATE $\varphi_{|\Gamma|+1}\gets$ line in Def.~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
@@
 \end{equation}
-and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$ where $r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}).
+and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
+$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}).
 The center also changes
@@
 Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
-The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$ in Def.~\ref{def:primitive}).
-
-Alg.~\ref{alg2} initializes $j$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
-The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the given final point $\mathbf{p}_{\Gamma_l}$.
+The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$.% in Def.~\ref{def:primitive}).
+
+Alg.~\ref{alg2} initializes $i$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the final point $\mathbf{p}_{\Gamma_l}$.
 The initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
@@
 
-Past literature in planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
+Past literature on planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
 We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Def.~\ref{def:meas}).
@@
 \end{align}\end{subequations}
-where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ given initial and final cost functions.
+where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ are given initial and final cost functions.
 Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
 Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Def.~\ref{def:stage}.
-Eq.~(\ref{eq:batt-const-mpc}) is the state and output constraints in Def.~\ref{def:const} that evolves the battery model in Lem.~\ref{lem:bat}.
+Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Def.~\ref{def:const} that evolves the battery model in Lem.~\ref{lem:bat}.
 Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
@@
     \small
-    \FORALL{$i\in\mathcal{T}$}
+    \FORALL{$t\in\mathcal{T}$}
       \makeatletter
@@
       \makeatother
-      \STATE $\mathbf{q}(\mathcal{K}\setminus\{i+N\}),c_j(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_j(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(i+\hspace*{-.1ex}N),i+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_j(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{i,i+h,\dots,i+N\}$\vspace*{.3ex}\label{alg:mpc}
+      \STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}\label{alg:mpc}
 
       \vspace*{.8ex}
-      \STATE $k\gets i$\vspace*{.3ex}\label{alg:bat1}
+      \STATE $k\gets t$\vspace*{.3ex}\label{alg:bat1}
       \WHILE{$b_d(y(k))>0$}\vspace*{.3ex}
-        \IF{$k\in\mathcal{K}$}
+        \IF{$k+h\notin\mathcal{K}$}
           \STATE $\mathbf{q}(k+h)\gets${ solve model in Eq.~(\ref{eq:state-perf-q})}\vspace*{.3ex}\label{alg:evol}
@@
       \ENDWHILE
-      \STATE $t_b\gets k-i$\vspace*{.3ex}\label{alg:bat2}
+      \STATE $t_b\gets k-t$\vspace*{.3ex}\label{alg:bat2}
       \vspace*{-1.4ex}
-      \STATE $t_s\gets(\mathrm{diag}(\nu_j^\rho)\vspace*{.3ex}c_j^\rho(i)+\tau_j^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
-      \STATE $t_r\gets(t_s/\overline{t})(\overline{t}-i)$\vspace*{.3ex}
+      \STATE $t_s\gets(\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
+      \STATE $t_r\gets(t_s/\overline{t})(\overline{t}-t)$\vspace*{.3ex}
       \IF{$t_r<t_b$}
-        \STATE $c_j^{\rho}(i)\gets${ find }$c_j^{\rho}${ with }$t_c\in[0,t_b]${, otherwise take }$\underline{c}_j^\rho$\vspace*{.3ex}\label{alg:traj2}
+        \STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_c\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
       \ENDIF
@@
       \vspace*{.8ex}
-      \STATE $\hat{\mathbf{q}}(i+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(i)$\vspace*{.3ex}\label{alg:klm1}
-      \STATE $\hat{y}(i+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(i+h)$\vspace*{.3ex}\label{alg:klm2}
+      \STATE $\hat{\mathbf{q}}(t+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(t)$\vspace*{.3ex}\label{alg:klm1}
+      \STATE $\hat{y}(t+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(t+h)$\vspace*{.3ex}\label{alg:klm2}
     \ENDFOR
@@
   \footnotesize
-  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}), i.e., wind speed and direction, battery behavior, and parameters initial values.}
+  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}): wind speed and direction, battery behavior, and parameters initial values.}
   \label{fig:res}
@@
 Fig.~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
-illustrates first the power ($\Upsilon(i)$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and then the energy model ($y(i)$ on Line~\ref{alg:evol}).
-Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line, the battery behavior $b_0(i)$) drop at approximately one minute and a half and four minutes and a half.
+illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
+Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
 Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Def.~\ref{def:const}).
@@
 %\subsubsection*{Periodic energy model}
-The figure further details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}(i)$), power ($\Upsilon(i)$), and period ($T$).
+The figure further details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
 % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
@@
                                              %
-The letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending relevant past literature.
+The letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature.
 It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
@@
 It evolves the state of the energy model while optimizing battery usage and remedying possible defects.
-The plan compromise multiple stages, where at each the aerial robot flies a path and does some computations, allowing further extensibility in terms of constructs and approaches.
+The plan compromise multiple stages, where at each the aerial robot flies a path and runs the computations, allowing further extensibility in terms of constructs and approaches.
 
@@
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-
-%'\>o-O</'
 
@@
 The linear combination of the initial guess in Lem.~\ref{lem:new} and the generic solution of Eq.~(\ref{eq:state-perf})
-\vspace*{-1.6ex}\begin{subequations}\label{eq:proof-comb}\begin{align}
+\vspace*{-1.6ex}\begin{subequations}\begin{align}
   F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}},\\\vspace*{-.8ex}
-  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}},\vspace*{-.8ex}
+  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}\label{eq:proof-comb},\vspace*{-.8ex}
 \end{align}\end{subequations}
@@
 
-The second expression in Eq.~(\ref{eq:proof-comb}) is the linear combination of all the coefficients of the state at time $t$. By dividing the expression with the period
+Eq.~(\ref{eq:proof-comb}) is the linear combination of all the coefficients of the state at time $t$. By dividing the expression with the period
 \vspace*{-1.6ex}\begin{equation}\label{eq:proof-output}
@@
 
-Finally, we prove that the eigenvalues $\lambda_0,\lambda_1^0,\lambda_1^1,\dots$ and eigenvectors in $v_0,v_1^0,v_1^1,\dots$ are such that Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
-
-The matrix $A$ is a block diagonal matrix, s.t. its determinant is the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
+Finally, we prove that the eigenvalues $\lambda_0,\lambda_1^0,\lambda_1^1,\dots$ and eigenvectors in $v_0,v_1^0,v_1^1,\dots$ are s.t.
+Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
+
+The matrix $A$ is a block diagonal matrix: its determinant is the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
 
@@
 To match the outputs $h(t)=y(t)$, or equivalently $F\mathbf{q}(t)/T=C\mathbf{q}(t)$, $C=(1/T)\begin{bmatrix}1 & 1 & 0 & \cdots & 1 & 0\end{bmatrix}$.
-Eq.~(\ref{eq:proof-output}) and Eq.~(\ref{eq:proof-complex}) are thus equal.
+Eq.~(\ref{eq:proof-output}) and~(\ref{eq:proof-complex}) are thus equal.
 Eq.~(\ref{eq:proof-complex}) is merely the complex form of Eq.~(\ref{eq:fourier}).
@@
 Combining $V_e,V_sI_l$ results in the quadratic expression $R_rI^2-VI+V_sI_l=0$.
-Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero)% results in
+Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) leads to% results in
 \begin{equation}
@@
 \end{document}
+
+%'\>o-O</'

### 2021-12-10 energy-planning.tex
language improvements in abstract and intro, minor fix in App. B

@@
 \begin{abstract}
-  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots, which plans in-flight a coverage path and simultaneously schedules onboard computational tasks.
+  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots that plans a coverage path and schedules simultaneously onboard computational tasks.
 It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model.
 The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool.
-Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
+Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery autonomously and in-flight.
+While exploiting all the available resources, the approach remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, increases the overall fault tolerance, and improves the power savings.
 \end{abstract}
@@
 They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets.
-A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running some onboard computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
+A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running assigned computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
 Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}).
 Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
-In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
+Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
+%In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
 We refer to computational tasks that can be scheduled with an energy impact as computations.
@@
 Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}.
-Such a state of practice has prompted us to propose a planning-scheduling approach for autonomous aerial robots.
-It combines the past body of knowledge, addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
+Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
 Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
@@
 
-There are numerous planning algorithms applied to a variety of robots.
+There are numerous planning approaches applied to a variety of robots.
 An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}.
-Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
+Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
 In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
@@
 Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives.
-Appendices provide supplementary material.
+Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
 
@@
 
-Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contain the proofs of Lemmas~\ref{lem:eqv}--\hyperref[lem:new]{2}.
+Apps.~\ref{app:proof-eqv}--\ref{app:proof-new} contain the proofs of Lemmas~\ref{lem:eqv}--\hyperref[lem:new]{2}.
 
@@
 Conversely, assume the time needed to travel $\varphi_4(\underline{c}_{i,1})$ is $t_4\in\mathbb{R}_{>0}$.
-Then $t_{\underline{\Gamma}}=3(2t_1+t_2+t_4)+t_1$, and $t_{\overline{\Gamma}}>t_{\underline{\Gamma}}$ even under the unrealistic assumption $t_3\approxeq t_4$.
+Then $t_{\underline{\Gamma}}=3(2t_1+t_2+t_4)+t_1$, and $t_{\overline{\Gamma}}>t_{\underline{\Gamma}}$.
+%even under the unrealistic assumption $t_3\approxeq t_4$.
+If $c_{i,1}(t_j),{c}_{i,1}(t_{j+1})$ are $\overline{c}_{i,1},\underline{c}_{i,1}$ in an arbitrary order, Lem.~\ref{lem:new} is satisfied.
+Furthermore, for any combination $c_{i,1}(t_j)\neq{c}_{i,1}(t_{j+1})$ Lem.~\ref{lem:new} is satisfied, i.e., each variation of $c_{i,1}$ alters $r_2$ in Eq.~(\ref{eq:r2}) and the length of the cover with the Zamboni-like motion.
 
@@
 \begin{equation}
-I(y)=(V-\sqrt{V^2-4R_ry(t)})/(2R_r),
+I(y(t))=(V-\sqrt{V^2-4R_ry(t)})/(2R_r),
 \end{equation} 

### 2022-02-17 energy-planning.tex
implemented Hector's comments

@@
 \newtheorem{exmp}{Example}[section]
-\newtheorem{pb}{Problem}[section]
+\newtheorem*{pb}{Problem}%[section]
 \newtheorem{rem}{Remark}
 \newtheorem{obs}{Observation}
+\newtheorem*{ctb}{Contribution}
 
@@
 
+\vspace*{-4.65ex}
+
 \begin{abstract}
-  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots that plans a coverage path and schedules simultaneously onboard computational tasks.
-It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model.
-The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool.
-Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery autonomously and in-flight.
-While exploiting all the available resources, the approach remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, increases the overall fault tolerance, and improves the power savings.
+  This letter presents an online planning-scheduling approach for battery-powered autonomous aerial robots.
+The approach plans a coverage path and schedules simultaneously onboard computational tasks.
+It further derives a novel variable coverage motion robust to airborne constraints and an empirically motivated energy model.
+The model is enhanced with the energy contribution of the schedule, utilizing a previously proposed automatic modeling tool.
+Data show how an initial flight plan is adjusted online in the function of the available battery, accounting for uncertainty.
+Here, the proposed approach additionally remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  Aerial Systems: Perception and Autonomy, Optimization and Optimal Control, Planning, Scheduling and Coordination, Planning under Uncertainty
+  Aerial Systems: Perception and Autonomy, %Optimization and Optimal Control, 
+  Planning, %Scheduling and Coordination, 
+  Planning under Uncertainty
 \end{IEEEkeywords}
@@
                         %
-\IEEEPARstart{U}{se cases} involving aerial robots span broadly.
-They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets.
-A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running assigned computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}.
-Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}).
+\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
+An instance is coverage path planning (CPP) in the literature~\cite{choset2001coverage,galceran2013survey}, consisting of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey}, running assigned computational tasks.
+Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction.
 Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
@@
 We refer to computational tasks that can be scheduled with an energy impact as computations.
-We are interested in the simultaneous energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling.
-Generic mobile robotics studies that deal with planning-scheduling energy awareness are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}.
+We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling.
+Studies that deal with planning-scheduling energy awareness for mobile robots are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}.
 Yet, aerial robots are particularly affected by various energy considerations.
-Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}.
+Indeed it would be generally required to land to recharge the battery.
 Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
-Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
-Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t.
-the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
+Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
+Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan and schedule~(\ref{sth:i}), that is optimized respecting the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
 
@@
   \end{tikzpicture}
-  \caption{Illustrative example of planning-scheduling.
-An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}).
-Follow the collected energy data of a physical aerial robot flying the coverage.}
+  \caption{%Illustrative example of planning-scheduling. 
+  An initial plan~(in~\ref{sth:i}) is re-planned online changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
+Follow the collected energy data of a physical aerial robot flying the static coverage.}
   \label{fig:il-abs}
@@
 These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}.
-We extend the relevant literature to the case of CPP with aerial robots.
 
@@
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
+\begin{ctb}
+  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies, and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
+\end{ctb}
 
@@
 Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
-Both the variations trajectories are derived for future time instants employing computations and motion energies and battery models.
+Both the variations trajectories are derived for future time instants employing computations and overall energies and battery models.
 The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
-The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+The overall wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of different plans and schedules.
+In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the overall energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
 The remaining sections of the letter are then organized as follows.
-Sec.~\ref{sec:prob} provides basic constructs, such as the concepts of the plan, stages, triggering and final points, and path functions, as well as the problem formulation.
-Sec.~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
-Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives.
-Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
+Section~\ref{sec:prob} provides basic constructs, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as the problem formulation.
+Section~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
+Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives.
+%Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
 
@@
   \begin{minipage}[l]{0.35\columnwidth}
-    \caption{Defs.~\ref{def:plan}--\hyperref[def:trigs]{4} on a slice of the plan $\Gamma$.
-$\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$.
-Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
+    \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$.
+$\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens change of stages $\Gamma_i$.
+Each contains a path function $\varphi_i$ and $j$ parameters to alter the path and schedule $c_{i,1},\dots,c_{i,j}$.}
     \label{fig:traj1}
@@
 
-Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries.
-For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.
-
-\vspace*{-2ex}
+Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries.
+For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} composed of \emph{stages}.
+At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
+Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.%with information about the path and the schedule.
+
 \subsection{Preliminaries}
@@
 
-\begin{defn}[Plan]\label{def:plan}
-  Given a generic point $\mathbf{p}(t)\in\mathbb{R}^2$ w.r.t.
-a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
-  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
-    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
-    \Gamma_i & \text{otherwise}
-  \end{cases}.\end{equation*}
-\end{defn}
-
-Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ denotes the set of integers.
-At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
-Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.
-$\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and
-after Definition~\ref{def:trigs}.
+%Here, $\Gamma_i$ is a \emph{stage}, $\varepsilon_i$ is a stage-dependent value detailed 
+%along with $\mathbf{p}_{\Gamma_i}$ in and 
+%after Definition~\ref{def:trigs}.
 
 \begin{defn}[Stage]\label{def:stage}
-  The $i$th \emph{stage} $\Gamma_i$ at time instant $t$ of a plan $\Gamma$ is
+  Given a generic point $\mathbf{p}\in\mathbb{R}^2$ w.r.t.
+a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ at time instant $t$ %of a plan $\Gamma$
+  is
   \begin{equation*}\begin{split}
@@
 
-The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
-For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.
-
-The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
-the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ denotes the upper/lower bounds of a parameter $\cdot\,$, i.e.,
+For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality.
+$\mathbb{Z},\mathbb{R}$ are the sets of integers and reals.% respectively.
+
+The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$, $\,\cdot\,'$ the transpose of $\cdot\,$, and $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ the upper/lower bounds of a parameter $\cdot\,$, i.e.,
 \begin{equation}
@@
 \end{equation}
+
+The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
+the coverage.
 
@@
 
-The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Def.~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
-
-Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\hyperref[def:trigs]{4}.
+The plan merges the concepts from Definitions~\ref{def:stage}--\hyperref[def:trigs]{3}. %via a .
+
+\begin{defn}[Plan]\label{def:plan}
+  The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
+    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
+    \Gamma_i & \text{otherwise}
+  \end{cases}.\end{equation*}
+\end{defn}
+
+The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
+
+Fig.~\ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}.
 $\varphi_0,\dots,\varphi_5$ are path functions.
@@
 
-Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}.
+Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}.
 A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
-$t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{> 0}$.
-$\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.
-
-\vspace*{-2ex}
+$t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$.
+$\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.
+
 \subsection{Energy-aware planning-scheduling problem}
@@
 The problem of planning-scheduling is composed of two sub-problems.
-One is to form a static plan that visits each point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.
-
-\begin{pb}[Coverage problem]
+One is to form a static plan that visits every point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.
+
+\begin{pb}[Coverage and re-planning-scheduling problem]
   \label{pb:cov-pb}
-  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each vertex $v_i:=(x_{v_i},y_{v_i}),\forall i\in[|v|]_{>0}$
+  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each %vertex $v_i:=(x_{v_i},y_{v_i})%,\forall i\in[|v|]_{>0}$
   %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
-  is a point w.r.t.
-$\mathcal{O}_W$.
-Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the minimum turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given.
-The \emph{coverage problem} is the problem of finding a plan $\Gamma$ that covers the polygon.
+  is a point w.r.t. $\mathcal{O}_W$. 
+  Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} the optimal parameters $c_i$ in time.
 \end{pb}
 
-For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ denotes the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
-.
-
-\begin{pb}[Re-planning-scheduling problem]
-  \label{pb}
-  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}.
+%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
+%.
+
+%\begin{pb}[Re-planning-scheduling problem]
+%  \label{pb}
+%  Consider an initial plan $\Gamma$ in Definition~\ref{def:plan}.
 The \emph{re-planning-scheduling problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
-\end{pb}
-
-Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$.
-The notation $\,\cdot\,'$ denotes the transpose of $\cdot\,$.
+%\end{pb}
+
+Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. %The notation .
 
@@
 %One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Eq.~(\ref{eq:primitive}).
-If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Def.~\ref{def:period} can be determined empirically from energy data (such as these shown in Fig.~\ref{fig:il-abs}).
+If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Fig.~\ref{fig:il-abs}).
 
 %\begin{pb}[UAV planning problem]\label{pb}
-%  Consider an initial plan $\Gamma$ from Def.~\ref{def:mission}.
+%  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}.
 We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
@@
 
-\vspace*{-1ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
                          %
-The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants.
-To this end, Secs.~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the motion and computations energies and battery.
-
-\vspace*{-2ex}
-\subsection{Energy model for the motion}
+The solution to the problem requires energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants.
+To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies and battery evolution.
+
+\subsection{Overall energy model% for the motion
+}
 \label{sec:mod-mot}
 
-Collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs} illustrate the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift.
-The data exhibit periodic behavior, an observation further backed by the power spectrum analysis.
-It indicates that to model the energy, three frequencies are adequate.
+Collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs} illustrate the energy of a static coverage plan. %$\Gamma$ with four primitive path functions iterated with a shift. 
+Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibit periodic behavior with a constant set of frequencies, independent of the shift.
+The hypothesis is further backed by the power spectrum analysis, indicating that to model the energy, three frequencies are adequate.
 
@@
 
-The model in Equation~(\ref{eq:fourier}) does not quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules result in different instantaneous energy.
-For this latter purpose, we use another model
+%The model in 
+Equation~(\ref{eq:fourier}) does not account for the variation of parameters, where, e.g., two schedules result in different instantaneous energies.
+%The model in Equation~(\ref{eq:fourier}) does not quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules result in different instantaneous energy. 
+For this latter purpose, we use the dynamics %another model
 \begin{subequations}\label{eq:state-perf}\begin{align}
@@
 
-Under favorable conditions, %the 
-models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal.
-
-\begin{lem}[Signal, output equality]\label{lem:eqv}Given $\mathbf{u}$ a zero vector, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
+To define the nominal control and the output matrix, we exploit the effect of variation of path and computations parameters on the energy. 
+%We assume a variation in computations parameters $c_i^\sigma$ affects the instantaneous energy, i.e., different schedules of power-demanding computational tasks have different power drains from the computing hardware.
+%\begin{lem}[Parameters, energy relation]\label{lem:new}
+  Given $c_i(t)$ parameters at two following time instants $t\in\{t_j,t_{j+1}\}\subset\mathbb{R}_{\geq 0}$ s.t.
+$t_j<t_{j+1}$ for an arbitrary stage $\Gamma_i$, a change in parameters $c_i(t_j)\neq c_i(t_{j+1})$ results in different overall and instantaneous energies for path and computations parameters respectively.
+%\end{lem}
+
+%Apps.~\ref{app:proof-eqv}--\ref{app:proof-new} contain the proofs of Lemmas~\ref{lem:eqv}--\hyperref[lem:new]{2}.
+
+%Using the same notation from Lem.~\ref{lem:new}, 
+%
+%\begin{equation}\label{eq:nom-cont}
+%  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
+%\end{equation}
+%for all time instants. 
+The nominal control and input matrix in Eq.~(\ref{eq:state-perf}) simply includes the change in energy for all time instants, i.e.,
+\begin{equation}\label{eq:mat_B}
+  \mathbf{u}(t_{j+1})\hspace*{-.5ex}:=\hspace*{-.5ex}\hat{\mathbf{u}}(t_{j+1})\hspace*{-.5ex}-\hspace*{-.5ex}\hat{\mathbf{u}}(t_j),\,\,\,B=\begin{bmatrix}
+      0^{1\times\rho} & 1      & \cdots & 1      \\
+      0^{1\times\rho} & 0      & \cdots & 0      \\ 
+      \vdots          & \vdots & \ddots & \vdots \\
+      0^{1\times\rho} & 0      & \cdots & 0   
+  \end{bmatrix},
+\end{equation}
+shifts the base frequency $\alpha_0$ assuming the energy of the computations does not alter the other frequencies.
+$B\in\mathbb{R}^{m\times n}$ with $n:=\rho+\sigma$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones.
+Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible, as we discuss briefly in Section~\ref{sec:conclusion}.
+The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
+conditions.
+
+The %Under favorable conditions, %the 
+models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
+%\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
+when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
+and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
   \begin{equation*}
-  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}'.
+  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',
   \end{equation*} 
-  $h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
-\end{lem}
+  %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
+%\end{lem}
 %\begin{proof}
@@
 %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
-
-To define the nominal control and the output matrix, we exploit the effect of variation of path and computations parameters on the energy. 
-%We assume a variation in computations parameters $c_i^\sigma$ affects the instantaneous energy, i.e., different schedules of power-demanding computational tasks have different power drains from the computing hardware.
-
-\begin{lem}[Parameters, energy relation]\label{lem:new}
-  Given $c_i(t)$ parameters at two following time instants $t\in\{t_j,t_{j+1}\}\subset\mathbb{R}_{\geq 0}$ s.t.
-$t_j<t_{j+1}$ for an arbitrary stage $\Gamma_i$, a change in parameters $c_i(t_j)\neq c_i(t_{j+1})$ results in different overall and instantaneous energies for path and computations parameters respectively.
-\end{lem}
-
-Apps.~\ref{app:proof-eqv}--\ref{app:proof-new} contain the proofs of Lemmas~\ref{lem:eqv}--\hyperref[lem:new]{2}.
-
-Using the same notation from Lem.~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
-\begin{equation}
-  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
-\end{equation}
-for all time instants. $\hat{\mathbf{u}}$ is then a scale transformation
+i.e., $h,y$ are both harmonic signals with the same frequencies.
+
+$\hat{\mathbf{u}}$ in Eq.~(\ref{eq:mat_B}) is then a scale transformation
 \begin{equation}
@@
 where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere.
-$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Def.~\ref{def:stage}) to time and power domains.
+$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors that transform parameters domain (see Definition~\ref{def:stage}) to time and power domains.
 
@@
 \end{align}\end{subequations}
-$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Sec.~\ref{sec:mod-com} and quantifies the power of the computing hardware.
-
-The input matrix then includes the change in energy, i.e.,
-\begin{equation}\label{eq:mat_B}
-  B=\begin{bmatrix}
-      0^{1\times\rho} & 1      & \cdots & 1      \\
-      0^{1\times\rho} & 0      & \cdots & 0      \\ 
-      \vdots          & \vdots & \ddots & \vdots \\
-      0^{1\times\rho} & 0      & \cdots & 0   
-  \end{bmatrix},
-\end{equation}
-where $B\in\mathbb{R}^{m\times n}$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones.
-
-\vspace*{-1.5ex}
+$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Section~\ref{sec:mod-com} and quantifies the power of the computing hardware.
+
 \subsection{Energy model for the computations}
@@
 Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
-This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Def.~\ref{def:stage}).
+This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
 
@@
 
-The energy measures in Defs.~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall.
-Additionally, the tool supports the battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}.
-The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
+The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall.
+Additionally, the \powprof{} tool supports the battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}.
+The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
 \begin{equation}\label{eq:piece-wise-reg}\begin{split}
@@
 There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two.
-
 We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' ECM in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
 
-\begin{lem}[Battery SoC]\label{lem:bat}
-  Given the internal battery voltage $V\in\mathbb{R}$ measured in volts, resistance $R_r$ in ohms, constant nominal capacity $Q_c$ in amperes per hour, and a battery coefficient $k_b$, the \emph{battery SoC} evolves
-  \begin{equation*}
-    \dot{b}(y(t))=-k_b\left(V-
-  \sqrt{
-    V^2-
-    4R_ry(t)}
-  \right)/(2R_rQ_c).
-  \end{equation*}
-\end{lem}
-
-App.~\ref{app:proof-bat} contains the proof of Lem.~\ref{lem:bat}.
-
-Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, conflicting with the findings in Lem.~\ref{lem:bat}.
-
-\begin{defn}[Output constraint]\label{def:const}
-  \begin{equation*}
-    \mathcal{Y}(t):=\{y\mid y\in[0,b(y(t))Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
-  \end{equation*}
-  is the \emph{output constraint}, where $b(y(t))Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Lem.~\ref{lem:bat}.
-\end{defn}
+The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
+\begin{equation}\label{eq:batdyn}
+  \dot{b}(y(t))=-k_bI(y(t))/Q_c,
+\end{equation}
+where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
+$k_b$ is a battery coefficient added to~\cite{hasan2018exogenous,zhang2018online} and derived experimentally.
+The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohm, representing the battery resistance.
+The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts.
+The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
+
+If the voltage of the power drain is stable, Kirchhoff's circuit laws lead to $V_sI_l=V_eI$, where $I_l$ is the current required by the load measured in amperes.
+Combining $V_e,V_sI_l$ results in the quadratic expression $R_rI^2-VI+V_sI_l=0$.
+Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) %leads to%
+results in 
+\begin{equation}
+I(y(t))=(V-\sqrt{V^2-4R_ry(t)})/(2R_r).
+\end{equation} 
+%as in Lem.~\ref{lem:bat}.
+%
+%\begin{lem}[Battery SoC]\label{lem:bat}
+%  Given the internal battery voltage $V\in\mathbb{R}$ measured in volts, resistance $R_r$ in ohms, constant nominal capacity $Q_c$ in amperes per hour, and 
+%thus given a battery coefficient $k_b$, the \emph{battery SoC} evolves
+%\begin{equation*}\label{eq:batdyn}
+%  \dot{b}(t)=-k_b\left(V-
+%  \sqrt{
+%    V^2-
+%    4R_ry(t)}
+%  \right)/(2R_rQ_c).
+%\end{equation*}
+%\end{lem}
+
+%App.~\ref{app:proof-bat} contains the proof of Lem.~\ref{lem:bat}.
+
+Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, %conflicting with the the findings in this section. 
+yet, aerial robots usually use a battery.
+We thus use instead
+%\begin{defn}[Output constraint]\label{def:const}
+\begin{equation}\label{eq:output-const}
+  \mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
+\end{equation}
+%the \emph{output constraint}, 
+where $b\,Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Eq.~(\ref{eq:batdyn}).
+%\end{defn}
 
@@
 
-%Let us recall from Def.~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
+%Let us recall from Definition~\ref{def:mission} that the $i$-th stage $\Gamma_i$ of the plan $\Gamma$ contains the computation parameters which characterize the computations.
 We estimate the energy cost of these computations using \powprof{}, the open-source modeling tool adapted from earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
@@
 
-The section solves Problems~\ref{pb:cov-pb}--\hyperref[pb]{2}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise %respectively
-in Secs.~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
-
-\vspace*{-1.4ex}
+The section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
+%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
+
 \subsection{Coverage}
@@
 
-There are various approaches in the literature to solve CPP problems, such as Pb.~\ref{pb:cov-pb}.
-Approaches that ensure the completeness of the cover are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
+There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). These that ensure the completeness %of the cover 
+are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
 
@@
 It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work.
-The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
+The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
 
@@
     \FORALL{$t\in\mathcal{T}$}
-      \STATE \textbf{if} $\mathbf{p}(t)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
-
-%      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Def.~\ref{def:trigs}}}
+      \STATE \textbf{if} $\mathbf{p}(t)=\mathbf{p}_{\Gamma_l}${ in Definition~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+
+%      \IF{$\mathbf{p}(i)=\mathbf{p}_{\Gamma_l}${ in Definition~\ref{def:trigs}}}
 
@@
         \STATE $i\gets i+1$\vspace*{.3ex}
-        \IF{$i\notin[n]_{>0}$}
+        \IF{$i\notin[n]_{>0}$}\label{alg2:cond}
           \STATE $i\gets 1$\vspace*{.3ex}
-          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Def.~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
+          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Definition~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
           parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
@@
           \vspace*{.8ex}
-          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}
+          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Definitions~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}
 
@@
 and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
-$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Pb.~\ref{pb:cov-pb}).
+$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}).
 The center also changes
@@
 Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
-The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$.% in Def.~\ref{def:primitive}).
-
-Alg.~\ref{alg2} initializes $i$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$).% in Definition~\ref{def:primitive}).
+
+Algorithm~\ref{alg2} initializes $i$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
 The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the final point $\mathbf{p}_{\Gamma_l}$.
@@
   \begin{minipage}[l]{0.25\columnwidth}
-    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Alg.~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
+    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
     \label{fig:zambo}
@@
 
-\vspace*{-1.4ex}
 \subsection{Re-planning-scheduling}
@@
 Past literature on planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
-We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Def.~\ref{def:meas}).
-Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use a technique in the literature named output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.
-
-An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
-\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
-  \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
-  \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
-  c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
-  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
-  \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
-  b(y(t_0))&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat},
-\end{align}\end{subequations}
-where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ and $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ are given initial and final cost functions.
-Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
-Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Def.~\ref{def:stage}.
-Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Def.~\ref{def:const} that evolves the battery model in Lem.~\ref{lem:bat}.
-Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
-(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.
+We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use %a technique in the literature named
+output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$~\cite{rawlings2017model}.
 
@@
         \ENDIF
-        \STATE $b_d(y(k+h))\gets${ solve model in Lem.~\ref{lem:bat}}\vspace*{.3ex}
+        \STATE $b_d(y(k+h))\gets${ solve model in Eq.~(\ref{eq:batdyn})}\vspace*{.3ex}
         \STATE $k\gets k+h$\vspace*{.3ex}
@@
 
-Line~\ref{alg:mpc} in Alg.~\ref{alg} contains a transformed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
+An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
+\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
+  \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
+  \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
+  c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
+  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
+  \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
+  b(t_0)&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat},
+\end{align}\end{subequations}
+where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial initial cost function with the quadratic expression
+\begin{equation}\label{eq:insta-cost-mpc}
+  l(\mathbf{q}(t),c_i(t),t)=\mathbf{q}'(t)Q\mathbf{q}(t)+c_i'(t)Rc_i(t),
+\end{equation}
+where $Q\in\mathbb{R}^{m\times m},R\in\mathbb{R}^{n\times n}$ are given positive semidefinite matrices.%, resulting in the convexity of the cost $l$~\citep{nocedal2006numerical}.
+A useful property to guarantee a solution~\citep{beck2014introduction}.
+The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression but with no control~\cite{rawlings2017model}
+\begin{equation}\label{eq:final-cost-mpc}
+  l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T),
+\end{equation}
+where $Q_f\in\mathbb{R}^{m\times m}$ is a given positive semidefinite matrix.
+
+Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
+The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
+
+Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}.
+Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolves the battery model in Eq.~(\ref{eq:batdyn}).
+Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
+(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.
+
+Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transcribed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
 Its solution leads to both trajectories of parameters and states for future $N$ instants.
 Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude), tuning the precision.
-The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:ocp-costs}) and Lem.~\ref{lem:bat}, with, e.g., Runge-Kutta methods, Euler method, etc.~\cite{iserles2009first}.
+The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}), with, e.g., Runge-Kutta or Euler methods~\cite{iserles2009first}.
 
 Lines~\ref{alg:bat1}--\ref{alg:bat2} estimate the time needed to completely drain the battery, exploiting the SoC already predicted previously on Line~\ref{alg:mpc}.
-The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using Lem.~\ref{lem:new} and scaling factors from Eq.~(\ref{eq:scale-traj}).
-Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear
+The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using %Lem.~\ref{lem:new} and
+scaling factors from Eq.~(\ref{eq:scale-traj}). Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
 Kalman filter~\cite{kalman1960new}.
 
-Alg.~\ref{alg} implements Eq.~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware re-planning-scheduling of $\Gamma$ from Alg.~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Alg.~\ref{alg2}.
-
-%The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Pb.~\ref{pb}.
+Algorithm~\ref{alg} implements Eq.~(\ref{eq:ocp-output-mpc}) for the purpose of energy-aware re-planning-scheduling of $\Gamma$ from Algorithm~\ref{alg2}, i.e, Lines~\ref{alg:mpc}--\ref{alg:klm2} continue after Line~\ref{alg2:last} in Algorithm~\ref{alg2}.
+
+%The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to guide the UAV on the path resulting from such sequence--to solve Problem~\ref{pb}.
 
@@
 
-%The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Def.~\ref{def:mission})
+%The control constraint set is the path constraint set for the path parameters and computation constraint sets for the computation parameters (Definition~\ref{def:mission})
 %\begin{equation*}
@@
 The expression depends on the path $\varphi_i$ from stage $\Gamma_i$.
-The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (FSM in Def.~\ref{def:mission}).
+The algorithm iterates all the stages in the plan $\Gamma$ (line~\ref{alg:stages-loop}), and enters the next stage $\Gamma_{i+1}$ when the UAV reaches the triggering point $\mathbf{p}_{\Gamma_i}$ (FSM in Definition~\ref{def:mission}).
 
@@
 
-\vspace*{-1.6ex}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Simulations} %
 \label{sec:experimental}        %
@@
 
+Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), complement physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}, and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
+The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Section~\ref{sec:mod-com}).
+The scheduler, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames-per-second (FPS).
+The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented through ROS.
+The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
+The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.
+
 %The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
-Fig.~\ref{fig:il-abs} details the data of a physical flight  
+Fig.~\ref{fig:il-abs} details the data of the physical flight  
 %We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
 in standard atmospheric conditions. 
-Fig.~\ref{fig:res} extends the flight with NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R).
-Upper-case roman numerals I,II indicate the plans are static (i.e., solely Alg.~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
-The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Sec.~\ref{sec:mod-com}).
-The scheduler varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames-per-second (FPS).
-The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros} as well as the scheduler itself.
-The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algs.~\ref{alg2}--\ref{alg}).
-The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.
+Fig.~\ref{fig:res} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
 
@@
 Fig.~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
-illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Alg.~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
+illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
 Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
-Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Def.~\ref{def:const}).
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Eq.~(\ref{eq:output-const})).
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario.
@@
 The path parameter increases as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter decreases mapping the battery discharge rate.
-For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,kang2009linear,stastny2018nonlinear,chao2011collision}, order $r$ is three (see Fig.~\ref{fig:il-abs}) and the costs $l_d,l_f$ are merely squared controls.
+For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,kang2009linear,stastny2018nonlinear,chao2011collision}, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
 %\subsection{Algorithm evaluation}
@@
 %A variation of computations affects directly the power.
-We thus select the highest computation which satisfies the constraints from Def.~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
+We thus select the highest computation which satisfies the constraints from Definition~\ref{def:const} in the line~\ref{alg:mpc} of the algorithm.
 We observed a low effect on the power of the communication ROS node.
@@
 
-\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Further future directions include the study of different energy models.
+Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage dependent energy models.
+In a unconventional setting with, e.g., multiple agent utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\appendices
+%\appendices
 
 % appendix, title all on one line
-\renewcommand{\thesectiondis}[2]{\Alph{section}:}
-
-\vspace*{-1ex}
-\section{Proof of Lem.~\ref{lem:eqv}}
-\label{app:proof-eqv}{\small
-
-The proof justifies the items of $A, C,$ and $\mathbf{q}_0$ in Lem.~(\ref{lem:eqv}), s.t.
+%\renewcommand{\thesectiondis}[2]{\Alph{section}:}
+
+%\vspace*{-1ex}
+%\section{Proof of Lem.~\ref{lem:eqv}}
+%\label{app:proof-eqv}{\small
+
+%The proof justifies the items of $A, C,$ and $\mathbf{q}_0$ in Lem.~(\ref{lem:eqv}), s.t.
 the coefficients of the series $a_0,\dots,b_r$ equal the coefficients $\alpha_0,\dots,\beta_r$ of the state $\mathbf{q}$.
 
-Firstly, it is convenient to re-write Eq.~(\ref{eq:fourier}) in complex form, with, e.g., $e^{it}=\cos{t}+i\sin{t}$.
+%Firstly, it is convenient to re-write Eq.~(\ref{eq:fourier}) in complex form, with, e.g., $e^{it}=\cos{t}+i\sin{t}$.
 Given $t=\omega jt$, $\cos{\omega jt}=(e^{i\omega jt}+e^{-i\omega jt})/2$ and $\sin{\omega jt}=(e^{i\omega jt}-e^{-i\omega jt})/(2i)$ by substitution of $\sin{\omega jt}$ and $\cos{\omega jt}$ respectively~\cite{kuo1967automatic}.
 Then
-\vspace*{-.8ex}\begin{equation}\label{eq:proof-complex}\vspace*{-.8ex}
-  h(t)\hspace*{-.4ex}=\hspace*{-.4ex}a_0/T\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}-\hspace*{-.4ex}ib_j)}\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}+\hspace*{-.4ex}ib_j)},\vspace*{-.8ex}
-\end{equation}
-where $i$ is this time the imaginary unit.
-
-Secondly, the solution at $t$ of Eq.~(\ref{eq:state-perf}) can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$~\cite{ogata2002modern}.
+%\vspace*{-.8ex}\begin{equation}\label{eq:proof-complex}\vspace*{-.8ex}
+%  h(t)\hspace*{-.4ex}=\hspace*{-.4ex}a_0/T\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}-\hspace*{-.4ex}ib_j)}\hspace*{-.4ex}+\hspace*{-.4ex}(1/T)\sum_{j=1}^{r}{e^{-i\omega jt}\hspace*{-.3ex}(a_j\hspace*{-.4ex}+\hspace*{-.4ex}ib_j)},\vspace*{-.8ex}
+%\end{equation}
+%where $i$ is this time the imaginary unit.
+
+%Secondly, the solution at $t$ of Eq.~(\ref{eq:state-perf}) can be expressed $\mathbf{q}=e^{At}\mathbf{q}_0$~\cite{ogata2002modern}.
 %Both the solution and the system in Eq.~(\ref{eq:state-perf}) are well established expressions derived using standard textbooks~\cite{kuo1967automatic, ogata2002modern}.
-Here, a method to solve the matrix exponential $e^{At}$ is the eigenvectors matrix decomposition method~\cite{moler2003nineteen} by exploiting the similarity transformation $A=VDV^{-1}$.
+%Here, a method to solve the matrix exponential $e^{At}$ is the eigenvectors matrix decomposition method~\cite{moler2003nineteen} by exploiting the similarity transformation $A=VDV^{-1}$.
 The power series definition of $e^{At}$ implies $e^{At}=Ve^{Dt}V^{-1}$~\cite{moler2003nineteen}.
 
-Within this expression, we consider the non-singular matrix $V$, whose columns are eigenvectors of $A$, $V:=[\begin{matrix}v_0 & v_1^0 & v_1^1 & \dots\end{matrix}$ $\begin{matrix}v_r^0 & v_r^1\end{matrix}]$, and the diagonal matrix of eigenvalues, $D=\mathrm{diag}(\lambda_0,\lambda_1^0,$ $\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)$.
+%Within this expression, we consider the non-singular matrix $V$, whose columns are eigenvectors of $A$, $V:=[\begin{matrix}v_0 & v_1^0 & v_1^1 & \dots\end{matrix}$ $\begin{matrix}v_r^0 & v_r^1\end{matrix}]$, and the diagonal matrix of eigenvalues, $D=\mathrm{diag}(\lambda_0,\lambda_1^0,$ $\lambda_1^1,\dots,\lambda_r^0,\lambda_r^1)$.
 $V$ is built s.t.
@@
 %is $\dot{\mathbf{q}}=A\mathbf{q}$.
-The linear combination of the initial guess in Lem.~\ref{lem:new} and the generic solution of Eq.~(\ref{eq:state-perf})
-\vspace*{-1.6ex}\begin{subequations}\begin{align}
-  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}},\\\vspace*{-.8ex}
-  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}\label{eq:proof-comb},\vspace*{-.8ex}
-\end{align}\end{subequations}
-where $F:=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is simply a properly sized vector of ones.
-
-Eq.~(\ref{eq:proof-comb}) is the linear combination of all the coefficients of the state at time $t$. By dividing the expression with the period
-\vspace*{-1.6ex}\begin{equation}\label{eq:proof-output}
-  F\mathbf{q}(t)/T\hspace*{-.4ex}=\hspace*{-.4ex}\gamma_0 e^{\lambda_0t}v_0/T+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
-\end{equation}
-
-Finally, we prove that the eigenvalues $\lambda_0,\lambda_1^0,\lambda_1^1,\dots$ and eigenvectors in $v_0,v_1^0,v_1^1,\dots$ are s.t.
+%The linear combination of the initial guess in Lem.~\ref{lem:new} and the generic solution of Eq.~(\ref{eq:state-perf})
+%\vspace*{-1.6ex}\begin{subequations}\begin{align}
+%  F\mathbf{q}(0)&=\gamma_0 v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j v_j^k}},\\\vspace*{-.8ex}
+%  F\mathbf{q}(t)&=\gamma_0 e^{\lambda_0 t} v_0+\sum_{k=0}^{1}{\sum_{j=1}^{r}{\gamma_j e^{\lambda_j t} v_j^k}}\label{eq:proof-comb},\vspace*{-.8ex}
+%\end{align}\end{subequations}
+%where $F:=\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ is simply a properly sized vector of ones.
+
+%Eq.~(\ref{eq:proof-comb}) is the linear combination of all the coefficients of the state at time $t$. By dividing the expression with the period
+%\vspace*{-1.6ex}\begin{equation}\label{eq:proof-output}
+%  F\mathbf{q}(t)/T\hspace*{-.4ex}=\hspace*{-.4ex}\gamma_0 e^{\lambda_0t}v_0/T+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^0t}v_j^0}+(1/T)\sum_{j=1}^r{\gamma_j e^{\lambda_j^1t}v_j^1}.
+%\end{equation}
+
+%Finally, we prove that the eigenvalues $\lambda_0,\lambda_1^0,\lambda_1^1,\dots$ and eigenvectors in $v_0,v_1^0,v_1^1,\dots$ are s.t.
 Eq.~(\ref{eq:proof-output}) is equivalent to Eq.~(\ref{eq:proof-complex}).
 
-The matrix $A$ is a block diagonal matrix: its determinant is the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
-
-The first terms of the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+%The matrix $A$ is a block diagonal matrix: its determinant is the multiplication of the determinants of its blocks $\det{(A)}=\det{(0)}\times\det{(A_1)}\times\cdots\times\det{(A_r)}$.
+
+%The first terms of the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
 The eigenvalue from $\det(0)=0$ is $\lambda_0=0$.
@@
 
-All the terms in the sum of both the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
+%All the terms in the sum of both the Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) match.
 For the first block $A_1$, the eigenvalues are found by $\det(A_1-\lambda I)=0$.
@@
 Again, we find the values $\gamma_1$ of the vector $\gamma$ such that the equivalences
-\begin{equation}\begin{cases}
-  e^{i\omega t}(a_1-ib_1)&=\gamma_1 e^{i\omega t}v_1^0\\
-  e^{-i\omega t}(a_1+ib_1)&=\gamma_1 e^{i\omega t}v_1^1
-\end{cases},\end{equation}
-hold, e.g., $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
-
-The proof for the remaining $r-1$ blocks is equivalent.
-
-The initial guess is constructed s.t.
+%\begin{equation}\begin{cases}
+%  e^{i\omega t}(a_1-ib_1)&=\gamma_1 e^{i\omega t}v_1^0\\
+%  e^{-i\omega t}(a_1+ib_1)&=\gamma_1 e^{i\omega t}v_1^1
+%\end{cases},\end{equation}
+%hold, e.g., $\gamma_1=\begin{bmatrix}b_1&a_1\end{bmatrix}$.
+
+%The proof for the remaining $r-1$ blocks is equivalent.
+
+%The initial guess is constructed s.t.
 the sum of the coefficients is the same in both Eq.~(\ref{eq:proof-output}) and~(\ref{eq:proof-complex}).
 In the output matrix, the frequency $1/T$ accounts for the period% in Eq.~(\ref{eq:proof-complex}) and~(\ref{eq:proof-output}) and~(\ref{eq:fourier})
-.
+%.
 At time instant zero, the coefficients $b_j$ are not present, and the coefficients $a_j$ are doubled for each $j=[r]_{>0}$ (thus we multiply by one-half the corresponding coefficients in $\mathbf{q}_0$).
@@
 %Periodicity is preserved with other linear combination of coefficients (for instance, $C=d\begin{bmatrix}1 & 0 & 1 & \cdots & 0 & 1\end{bmatrix}$, or $d\begin{bmatrix}1 & \cdots & 1\end{bmatrix}$ for a constant value $d\in\mathbb{R}$).
-}
-
-\vspace*{-1ex}
-\section{Proof of Lem.~\ref{lem:new}}
-\label{app:proof-new}{\small
-
-A change in computations parameters in Lem.~\ref{lem:new} results in different schedules on the computing hardware, which we assumed in Sec.~\ref{sec:intro} affects the instantaneous energy, i.e., computations are energy expensive computational tasks.
-
-A change in the path parameters in Lem.~\ref{lem:new} alters the flight time, and consequently, the energy.
+%}
+
+%\vspace*{-1ex}
+%\section{Proof of Lem.~\ref{lem:new}}
+%\label{app:proof-new}{\small
+
+%A change in computations parameters in Lem.~\ref{lem:new} results in different schedules on the computing hardware, which we assumed in Section~\ref{sec:intro} affects the instantaneous energy, i.e., computations are energy expensive computational tasks.
+
+%A change in the path parameters in Lem.~\ref{lem:new} alters the flight time, and consequently, the energy.
 The proof quantifies this time: consider the plan $\overline{\Gamma}$ in Fig.~\ref{fig:zambo}.
@@
 
-Conversely, assume the time needed to travel $\varphi_4(\underline{c}_{i,1})$ is $t_4\in\mathbb{R}_{>0}$.
+%Conversely, assume the time needed to travel $\varphi_4(\underline{c}_{i,1})$ is $t_4\in\mathbb{R}_{>0}$.
 Then $t_{\underline{\Gamma}}=3(2t_1+t_2+t_4)+t_1$, and $t_{\overline{\Gamma}}>t_{\underline{\Gamma}}$.
 %even under the unrealistic assumption $t_3\approxeq t_4$.
-If $c_{i,1}(t_j),{c}_{i,1}(t_{j+1})$ are $\overline{c}_{i,1},\underline{c}_{i,1}$ in an arbitrary order, Lem.~\ref{lem:new} is satisfied.
+%If $c_{i,1}(t_j),{c}_{i,1}(t_{j+1})$ are $\overline{c}_{i,1},\underline{c}_{i,1}$ in an arbitrary order, Lem.~\ref{lem:new} is satisfied.
 Furthermore, for any combination $c_{i,1}(t_j)\neq{c}_{i,1}(t_{j+1})$ Lem.~\ref{lem:new} is satisfied, i.e., each variation of $c_{i,1}$ alters $r_2$ in Eq.~(\ref{eq:r2}) and the length of the cover with the Zamboni-like motion.
@@
 %\qed
-}
-
-\vspace*{-1ex}
-\section{Proof of Lem.~\ref{lem:bat}}
-\label{app:proof-bat}{\small
-
-The proof justifies the expression in Lem.~\ref{lem:bat}.
-
-The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
-\begin{equation}
-  \dot{b}(y(t))=-I(y(t))/Q_c,
-\end{equation}
-where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity in Lem.~\ref{lem:bat}.
-The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ in Lem.~\ref{lem:bat}, representing the battery resistance.
-The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts.
-The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
-
-If the voltage of the power drain is stable, Kirchhoff's circuit laws lead to $V_sI_l=V_eI$, where $I_l$ is the current required by the load measured in amperes.
-Combining $V_e,V_sI_l$ results in the quadratic expression $R_rI^2-VI+V_sI_l=0$.
-Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) leads to% results in
-\begin{equation}
-I(y(t))=(V-\sqrt{V^2-4R_ry(t)})/(2R_r),
-\end{equation} 
-as in Lem.~\ref{lem:bat}.
+%}
+
+%\vspace*{-1ex}
+%\section{Proof of Lem.~\ref{lem:bat}}
+%\label{app:proof-bat}{\small
+
+%The proof justifies the expression in Lem.~\ref{lem:bat}.
 
@@
 
-}
-
-\leavevmode\thispagestyle{empty}\newpage
-\leavevmode\thispagestyle{empty}\newpage
+%}
+
+%\leavevmode\thispagestyle{empty}\newpage
+%\leavevmode\thispagestyle{empty}\newpage
 

### 2022-02-17 energy-planning.tex
proofreading

@@
   \caption{%Illustrative example of planning-scheduling. 
-  An initial plan~(in~\ref{sth:i}) is re-planned online changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
+  An initial plan~(in~\ref{sth:i}) is re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
 Follow the collected energy data of a physical aerial robot flying the static coverage.}
@@
 \begin{ctb}
-  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies, and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
+  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
 \end{ctb}
@@
 The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
-The overall wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of different plans and schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the overall energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+The overall wraps the past two in a cohesive model that uses dynamics %differential %and periodic
+modeling to predict future energy behavior of different plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed wing %aerial robot 
+flying CPP motivates the overall energy model: the evolution is periodic, an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
@@
 Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible, as we discuss briefly in Section~\ref{sec:conclusion}.
-The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
+The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
 conditions.
@@
 
-Let assume for ease of notation that the coverage time evolves linearly.
+For ease of notation, we assume that the coverage time evolves linearly.
 Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
@@
 \end{align}\end{subequations} 
-$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$)
+$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$).
 
@@
 
-Let assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
+We assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
 
@@
 
-The section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
+This section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
 %in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
@@
 
-Let assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
+We assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
 Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
 The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$.
-Nonetheless, complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.
+Nonetheless, a complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.
 
@@
           \STATE $\varphi_{|\Gamma|+1}\gets$ line in Definition~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
-          parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
+          parallel to ${}^{v_1}|_{v_{|v|}}$ that\vspace*{.5ex} \hspace*{1em}intersects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}
 
@@
           \vspace*{.8ex}
-          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Definitions~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}
+          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}}\label{alg2:last}
 
@@
 \end{align}\end{subequations}
-where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial initial cost function with the quadratic expression
+where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial cost function with the quadratic expression
 \begin{equation}\label{eq:insta-cost-mpc}
@@
 Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
-The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
+The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., the time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
 
 Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}.
-Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolves the battery model in Eq.~(\ref{eq:batdyn}).
+Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolve the battery model in Eq.~(\ref{eq:batdyn}).
 Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
@@
 Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
-Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
+Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
 
@@
                                              %
-The letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature.
+This letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature.
 It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
@@
 Indeed, we are currently extending the results to a standard flight controller. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
-and distributed planning-scheduling merits alike further investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
+and distributed planning-scheduling merit alike additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
@@
 Further future directions include the study of different energy models.
-Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage dependent energy models.
-In a unconventional setting with, e.g., multiple agent utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.
+In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
 
@@
 It is composed of four primitive paths and the highest configuration of path parameter $c_{i,1}$.
-Let assume that the time to travel $\varphi_4(\overline{c}_{i,1})$ is $t_3\in\mathbb{R}_{>0}$, $\varphi_1,\varphi_3$, the two lines, is $2t_1\in\mathbb{R}_{>0}$, and $\varphi_2$ is $t_2\in\mathbb{R}_{>0}$.
+We assume that the time to travel $\varphi_4(\overline{c}_{i,1})$ is $t_3\in\mathbb{R}_{>0}$, $\varphi_1,\varphi_3$, the two lines, is $2t_1\in\mathbb{R}_{>0}$, and $\varphi_2$ is $t_2\in\mathbb{R}_{>0}$.
 Further, assume that $v$ is covered merely by the set of primitive paths in Fig.~\ref{fig:zambo}.

### 2022-02-17 energy-planning.tex
implementing Ulrik's comments

@@
 
-\vspace*{-4.65ex}
+\vspace*{-4.6ex}
 
 \begin{abstract}
-  This letter presents an online planning-scheduling approach for battery-powered autonomous aerial robots.
-The approach plans a coverage path and schedules simultaneously onboard computational tasks.
-It further derives a novel variable coverage motion robust to airborne constraints and an empirically motivated energy model.
-The model is enhanced with the energy contribution of the schedule, utilizing a previously proposed automatic modeling tool.
-Data show how an initial flight plan is adjusted online in the function of the available battery, accounting for uncertainty.
-Here, the proposed approach additionally remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
+  In this letter, we present an online planning-scheduling approach for battery-powered autonomous aerial robots.
+The approach consists of simultaneously planning a coverage path and scheduling onboard computational tasks.
+We further derive a novel variable coverage motion robust to airborne constraints and an empirically motivated energy model.
+The model includes the energy contributions of the schedule based on an automatic computational energy modeling tool.
+Our experiments show how an initial flight plan is adjusted online as a function of the available battery, accounting for uncertainty.
+Our approach furthermore remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
 \end{abstract}
@@
                         %
-\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
-An instance is coverage path planning (CPP) in the literature~\cite{choset2001coverage,galceran2013survey}, consisting of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey}, running assigned computational tasks.
-Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction.
-Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
+\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They comprise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
+One such use case is coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}, which consists of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey} while running assigned computational tasks.
+Here, the aerial robot might detect ground patterns and notify other ground-based actors.
+%with little human interaction.
+Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground vehicles~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, information collection prior to an operation as well as damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
 Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
 %In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
-We refer to computational tasks that can be scheduled with an energy impact as computations.
-We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling.
-Studies that deal with planning-scheduling energy awareness for mobile robots are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}.
-Yet, aerial robots are particularly affected by various energy considerations.
-Indeed it would be generally required to land to recharge the battery.
-Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
-Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
-Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan and schedule~(\ref{sth:i}), that is optimized respecting the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
+We refer to onboard computational tasks that can be scheduled with an energy impact as \emph{computations}.
+We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware \emph{planning-scheduling}.
+The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~\cite{ho2018towards,ho2019learning,ho2019qos} and frequency and voltage of the computing hardware~\cite{mei2005case,brateman2006energy,zhang2007low}.
+We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
+Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
 
@@
   \caption{%Illustrative example of planning-scheduling. 
-  An initial plan~(in~\ref{sth:i}) is re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
-Follow the collected energy data of a physical aerial robot flying the static coverage.}
+  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
+  On the bottom-left it shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan, whereas on the bottom-right the spectrum analysis showing the periodicity of the data exploited in the overall energy model.
+  %Follow the collected energy data of a physical aerial robot flying the static coverage.
+  }
   \label{fig:il-abs}
-  \vspace*{-3.7ex}
+  \vspace*{-2ex}
 \end{figure}
@@
 An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}.
-Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
-In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
-In this context, planning-scheduling energy awareness is a recent research direction.
+Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
+In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
+In this context, planning-scheduling energy awareness is a recent research direction% energy awareness for mobile robots are scarce
+~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}.
 Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
 These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}.
-
-Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering.
+These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery.
+Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
+Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
+
+Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering.
 Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}.
-Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa.
+Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
 The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
@@
 
-To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.).
-Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
-Both the variations trajectories are derived for future time instants employing computations and overall energies and battery models.
-The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
-The overall wraps the past two in a cohesive model that uses dynamics %differential %and periodic
-modeling to predict future energy behavior of different plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed wing %aerial robot 
-flying CPP motivates the overall energy model: the evolution is periodic, an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
+Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
+Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
+The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules.
+In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed wing %aerial robot
+flying CPP motivates the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
@@
 Section~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
-Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives.
-%Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
-
+Section~\ref{sec:experimental} presents the results, %and showcases the performances,
+and Section~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
+
+\vspace*{-1ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\vspace*{-1ex}
 \subsection{Preliminaries}
@@
 
-For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality.
-$\mathbb{Z},\mathbb{R}$ are the sets of integers and reals.% respectively.
+For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are %the sets of 
+integers and reals.% respectively.
 
@@
 
+\vspace*{-1.2ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\vspace*{-1.2ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-18 energy-planning.tex
implementing Ulrik's comments

@@
   The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
-  On the bottom-left it shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan, whereas on the bottom-right the spectrum analysis showing the periodicity of the data exploited in the overall energy model.
+  Bottom-left shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here.
+Bottom-right shows a spectrum analysis of the energy data, revealing the periodicity of the data exploited in the overall energy model.
   %Follow the collected energy data of a physical aerial robot flying the static coverage.
@@
   \label{fig:il-abs}
-  \vspace*{-2ex}
+  \vspace*{-4ex}
 \end{figure}
@@
 
-For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are %the sets of 
-integers and reals.% respectively.
-
-The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$, $\,\cdot\,'$ the transpose of $\cdot\,$, and $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ the upper/lower bounds of a parameter $\cdot\,$, i.e.,
+For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ indicates its members are positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are %the sets of 
+integers and reals. % respectively.
+Bold letters indicate vectors. 
+The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of a parameter $x$, i.e.,
 \begin{equation}
-  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
+  \underline{x}\leq x\leq\overline{x}.
 \end{equation}
@@
   \label{def:trigs}
-  The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ allows the transition between stages.
+  The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ describes the transition between stages.
 The \emph{final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
@@
   \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
-    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
-    \Gamma_i & \text{otherwise}
-  \end{cases}.\end{equation*}
+    \Gamma_{i+j} & \text{if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},\\
+    \Gamma_i & \text{otherwise}.
+  \end{cases}\end{equation*}
 \end{defn}
 
-The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.
+The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of a non-existent circle over $\mathbf{p}_{\Gamma_i}$.
 
@@
 $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines.
-They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$.
+They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$ (the starting stage) and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$.
 %The constraint set $\mathcal{C}_{4,1}$ forms the area where
-It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure.
+It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$ illustrated by the gray area in the figure.
 %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
@@
   Given the number of \emph{primitive stages} $n\in\mathbb{Z}_{>0}$, a \emph{shift} $\mathbf{d}\in\mathbb{R}^2$, and a final point $\mathbf{p}_{\Gamma_l}$, the stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ %with the path functions $\varphi_1,\dots\varphi_n$ and the parameters $c_1,c_2,\dots,c_n$
-  are primitive if they form the remainder of the plan with $\mathbf{d}$ up to $\mathbf{p}_{\Gamma_l}$. 
+  are \emph{primitive} if they form the remainder of the plan with $\mathbf{d}$ up to $\mathbf{p}_{\Gamma_l}$. 
 \end{defn}
-
-In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
+\noindent In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
 \begin{equation}\label{eq:primitive}\begin{split}
@@
 $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$.
-$\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.
+$\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot awaits the starting command.
 
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} the optimal parameters $c_i$ in time.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the optimal parameters $c_i$ in time.
 \end{pb}
@@
 The solution to the problem requires energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants.
-To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies and battery evolution.
+To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies as well as battery evolution.
 
@@
 
-Collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs} illustrate the energy of a static coverage plan. %$\Gamma$ with four primitive path functions iterated with a shift. 
-Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibit periodic behavior with a constant set of frequencies, independent of the shift.
+The collected energy data and corresponding spectrum analysis in Fig.~\ref{fig:il-abs} show the energy of a static coverage plan.
+It is relative to one flight of a series of flights for CPP exhibiting periodic behavior in a precision agriculture use case~\cite{seewald2020mechanical}.
+%$\Gamma$ with four primitive path functions iterated with a shift.
+Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibits periodic behavior with a constant set of frequencies, independent of the shift.
 The hypothesis is further backed by the power spectrum analysis, indicating that to model the energy, three frequencies are adequate.
@@
 
-An intuitive way of modeling the energy data is thus a Fourier series of a given order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{R}_{>0}$
+An intuitive way of modeling the energy data is a Fourier series of a given order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{R}_{>0}$
 \begin{equation}\label{eq:fourier}
@@
 
-Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
-This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
+Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, such as regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
+This section presents an energy model based on our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
 
@@
 
-The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall.
+The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules.
 Additionally, the \powprof{} tool supports the battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}.
@@
 The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts.
-The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.
+The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on the SoC~\cite{hasan2018exogenous}.
 
@@
 
-This section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
+This section solves the problem described in Section~\ref{sec:pbfor}. It provides a plan %$\Gamma$ 
+and re-plans-schedules such plan energy-wise. %respectively
 %in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
@@
 
-There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). These that ensure the completeness %of the cover 
+There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). Those that ensure the completeness %of the cover 
 are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
@@
 
-To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
-\begin{equation}\label{eq:r2}
-  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
-\end{equation}
-and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
-$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}).
-The center also changes
-\begin{equation}\label{eq:second-circ-gene}
-  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
-\end{equation}
-where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$.
-Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
-The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$).% in Definition~\ref{def:primitive}).
-
-Algorithm~\ref{alg2} initializes $i$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
-The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the final point $\mathbf{p}_{\Gamma_l}$.
-The initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
-the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Fig.~\ref{fig:zambo}.
-
 \begin{figure}[t]
@@
 \end{figure}
+
+To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
+\begin{equation}\label{eq:r2}
+  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
+\end{equation}
+is expressed as a function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
+$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}).
+The center also changes
+\begin{equation}\label{eq:second-circ-gene}
+  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
+\end{equation}
+where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$.
+Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP.
+The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$).% in Definition~\ref{def:primitive}).
+
+Algorithm~\ref{alg2} initializes $i$ to minus one and builds the first four primitive functions $\varphi_1,\dots,\varphi_4$.
+The remaining $\Gamma$ is built with the shift $\mathbf{d}$ up to the final point $\mathbf{p}_{\Gamma_l}$.
+The initial point is $\mathbf{p}_{\Gamma_1}$, placed s.t.
+the line $\varphi_1$ is at the same distance from an eventual previous line, e.g., $x_{\mathbf{p}_{\Gamma_1}}=x_{v_1}+x_{\mathbf{d}}/2$ in Fig.~\ref{fig:zambo}.
 
@@
   \label{fig:res}
+  \vspace*{-3ex}
 \end{figure*}
 
-\vspace*{-1.2ex}
+\vspace*{-1.5ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), complement physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}, and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
-The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Section~\ref{sec:mod-com}).
-The scheduler, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames-per-second (FPS).
-The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented through ROS.
+Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
+These simulations complement early data of physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}.
+The computing hardware carries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}).
+The scheduler, implemented using the Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames per second (FPS).
+The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS.
 The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
@@
 Fig.~\ref{fig:res} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
-Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.
+Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.
 
@@
 Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Eq.~(\ref{eq:output-const})).
-Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario.
-The lowest configuration of parameters and no battery defects.
-The path parameter increases as soon as the algorithm estimated enough data (two periods $T$) and the computation parameter decreases mapping the battery discharge rate.
+Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario: the lowest configuration of parameters and no battery defects.
+The path parameter increases as soon as the algorithm has estimated enough data (two periods $T$) and the computation parameter decreases matching the battery discharge rate.
 For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,kang2009linear,stastny2018nonlinear,chao2011collision}, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
@@
 % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
-The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods are sufficient to obtain a consistent state estimate.
+The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
+estimate.
 %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
@@
 
-\vspace*{-1.2ex}
+\vspace*{-1.5ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 It evolves the state of the energy model while optimizing battery usage and remedying possible defects.
-The plan compromise multiple stages, where at each the aerial robot flies a path and runs the computations, allowing further extensibility in terms of constructs and approaches.
-
-Indeed, we are currently extending the results to a standard flight controller. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
-and distributed planning-scheduling merit alike additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
+The plan compromise multiple stages, where at each stage the aerial robot flies a path and runs the computations, allowing %further
+extensibility in terms of constructs and approaches.
+
+Indeed, we are currently extending the results to a standard flight controller to enable physical experiments.
+The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections),
+and distributed planning-scheduling merit additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-
 Further future directions include the study of different energy models.
-Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.
-In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
 

### 2022-02-18 energy-planning.tex
proofreading

@@
 
-There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). Those that ensure the completeness %of the cover 
+There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). Those that ensure %the 
+completeness %of the cover 
 are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
@@
 
-Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
+Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R) and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
 These simulations complement early data of physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}.

### 2022-02-24 energy-planning.tex
fixes to references

@@
 %% references (generates a bib file for bibtex)
-\begin{filecontents}{\jobname.bib}
-
-\end{filecontents}
+%\begin{filecontents}{\jobname.bib}
+
+%\end{filecontents}
 
@@
 \begin{IEEEkeywords}
-  Aerial Systems: Perception and Autonomy, %Optimization and Optimal Control, 
-  Planning, %Scheduling and Coordination, 
-  Planning under Uncertainty
+  %Aerial Systems: Perception and Autonomy, %Optimization and Optimal Control, 
+  %Planning, %Scheduling and Coordination, 
+  %Planning under Uncertainty
+  Motion and Path Planning, 
+  Energy and Environ- ment-Aware Automation
 \end{IEEEkeywords}
@@
 %with little human interaction.
-Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground vehicles~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, information collection prior to an operation as well as damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
-Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
+Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground vehicles~\cite{%qingchun2012study,
+dong2011development, de2011design%,aljanobi2010setup, 
+%li2008analysis, 
+%edan2000robotic
+}, information collection prior to an operation as well as damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
+Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial%, peng2019evaluating,
+%wang2020yolo
+,alexey2021autonomous}.
 %In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
@@
 We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware \emph{planning-scheduling}.
-The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~\cite{ho2018towards,ho2019learning,ho2019qos} and frequency and voltage of the computing hardware~\cite{mei2005case,brateman2006energy,zhang2007low}.
+The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~\cite{ho2019qos} and frequency and voltage of the computing hardware~\cite{mei2005case,brateman2006energy,zhang2007low}.
 We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
@@
 Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
-In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}.
-In this context, planning-scheduling energy awareness is a recent research direction% energy awareness for mobile robots are scarce
+In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{%abramov2012real,
+%satria2016real,
+jaramillo2019visual}. In this context, planning-scheduling energy awareness is a recent research direction% energy awareness for mobile robots are scarce
 ~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}.
 Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
-These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}.
-These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery.
+These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019qos}, and anytime planning~\cite{sudhakar2020balancing}.
+These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery.
 Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
-Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures.
+Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial
+robot%s
+ remedying in-flight failures.
 
@@
 The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
-It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
+It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
 \begin{ctb}
@@
 To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
-Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}.
+Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}.
 Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
-The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
+The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
+hinz2019comparison,mousavi2014various}.
 The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules.
@@
 
-\vspace*{-1ex}
+\vspace*{-2ex}
 \subsection{Preliminaries}
@@
 
-Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, such as regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
+Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,%goraczko2008energy%calore2015energy,
+yang2017designing} or different techniques, such as regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
 This section presents an energy model based on our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
@@
 
+\vspace*{-1.4ex}
 \subsection{Battery model}
@@
 The battery model predicts the battery SoC in the function of a given load at future time instants.
-There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two.
-We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' ECM in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.
-
-The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
+There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{%moura2017battery,
+marcicki2013design}, to abstract models~\cite{%xing2014state,
+%he2011evaluation,
+hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two. 
+We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' ECM in the literature~\cite{%he2011evaluation,
+hinz2019comparison,mousavi2014various}.
+
+The battery SoC changes according to~\cite{hasan2018exogenous%,zhang2018online
+}, i.e.,
 \begin{equation}\label{eq:batdyn}
@@
 where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
-$k_b$ is a battery coefficient added to~\cite{hasan2018exogenous,zhang2018online} and derived experimentally.
+$k_b$ is a battery coefficient added to~\cite{hasan2018exogenous%,zhang2018online
+} and derived experimentally.
 The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohm, representing the battery resistance.
@@
 
+\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\vspace*{-1.4ex}
 \subsection{Coverage}
@@
 An intuitive way to solve the problem is with a back-and-forth motion, sweeping the space delimited by $v$ we term $\mathcal{Q}^v$.
-Although abundant in both mobile ground-based~\cite{choset2001coverage,choset2005principles,lavalle2006planning} and aerial~\cite{araujo2013multiple,artemenko2016energy,cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
-These robots have reduced maneuverability~\cite{dille2013efficient,mannadiar2010optimal,xu2011optimal,xu2014efficient} and are generally unable to fly quick turns~\cite{wang2017curvature}.
+Although abundant in both mobile ground-based~\cite{choset2001coverage,%choset2005principles,
+lavalle2006planning} and aerial~\cite{araujo2013multiple,%artemenko2016energy,
+cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
+These robots have reduced maneuverability~\cite{dille2013efficient,mannadiar2010optimal,%xu2011optimal,
+xu2014efficient} and are generally unable to fly quick turns~\cite{wang2017curvature}.
 
@@
 
+\vspace*{-1.4ex}
 \subsection{Re-planning-scheduling}
@@
 Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude), tuning the precision.
-The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}), with, e.g., Runge-Kutta or Euler methods~\cite{iserles2009first}.
+The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}), with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}
+.
 
@@
 scaling factors from Eq.~(\ref{eq:scale-traj}). Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
-Kalman filter~\cite{kalman1960new}.
+Kalman filter%~\cite{kalman1960new}
+.
 
@@
   \centering
+  \vspace*{-4ex}
   \begin{subfigure}{.4\textwidth}
@@
 %$\subsection{Experimental setup}
+\vspace*{-.2ex}
 
 Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R) and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
-These simulations complement early data of physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}.
+These simulations complement early data of physical flights of a static coverage plan with the open-source Paparazzi flight controller%~\cite{papa}
+.
 The computing hardware carries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}).
-The scheduler, implemented using the Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames per second (FPS).
+The scheduler, implemented using the Robot Operating System (ROS) middleware%~\cite{quigley2009ros}
+, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames per second (FPS).
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS.
@@
 The path parameter increases as soon as the algorithm has estimated enough data (two periods $T$) and the computation parameter decreases matching the battery discharge rate.
-For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,kang2009linear,stastny2018nonlinear,chao2011collision}, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
+For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,%kang2009linear,
+stastny2018nonlinear%,chao2011collision
+}, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
 %\subsection{Algorithm evaluation}
@@
 
-Output MPC on Line~\ref{alg:mpc} relies on a software framework for nonlinear optimization called CasADi~\cite{andersson2012casadi,andersson2012bcasadi,andersson2019casadi}, and the popular NLP solver IPOPT~\cite{wachter2006implementation}.
+Output MPC on Line~\ref{alg:mpc} relies on a software framework for nonlinear optimization called CasADi~\cite{andersson2012casadi%,andersson2012bcasadi,andersson2019casadi
+}, and the popular NLP solver IPOPT~\cite{wachter2006implementation}.
 
@@
 
+\vspace*{-2ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\small\bibliographystyle{IEEEtran}  %
-\bibliography{../../books/phd-thesis/backmatter/references}}             %
+%\bibliography{../../books/phd-thesis/backmatter/references}}
+\bibliography{energy-planning}}             %
                                      %      

### 2022-02-24 energy-planning.tex
proofreading

@@
 \usepackage{booktabs}
-\usepackage{flushend}
+%\usepackage{flushend}
 \usepackage{tikz}
@@
 Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial
-robot%s
+robot %s
 remedying in-flight failures.
@@
 The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed wing %aerial robot
+In Fig.~\ref{fig:il-abs}, collected energy data (bottom-left) and spectrum analysis (right) of a fixed wing %aerial robot
 flying CPP motivates the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
@@
 Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries.
-For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} composed of \emph{stages}.
+For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot contains a \emph{plan} composed of \emph{stages}.
 At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the optimal parameters $c_i$ in time.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the optimal trajectory of parameters $c_i$ in time.
 \end{pb}
@@
 \end{equation}
-where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere.
+where $\mathrm{diag}(x)$ is a diagonal matrix with items of a set $x$ on the diagonal and zeros elsewhere.
 $\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors that transform parameters domain (see Definition~\ref{def:stage}) to time and power domains.
@@
 yang2017designing} or different techniques, such as regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters.
-This section presents an energy model based on our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
-
-The model compromises an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source MIT license.
+This section presents an energy model based on our early studies~\cite{seewald2019component,seewald2019coarse}, which relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).
+
+The model compromises an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed %~\cite{powprofiler} 
+under the open-source MIT license.
 It is segmented into two layers.
@@
 results in 
-\begin{equation}
+\begin{equation}\label{eq:batdyn2}
 I(y(t))=(V-\sqrt{V^2-4R_ry(t)})/(2R_r).
@@
 %the \emph{output constraint}, 
-where $b\,Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Eq.~(\ref{eq:batdyn}).
+where $b\,Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Eq.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
 %\end{defn}
@@
 
-Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transcribed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be easily solved with available NLP solvers~\cite{rawlings2017model}.
+Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transcribed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be %easily 
+solved with available NLP solvers~\cite{rawlings2017model}.
 Its solution leads to both trajectories of parameters and states for future $N$ instants.
@@
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario: the lowest configuration of parameters and no battery defects.
-The path parameter increases as soon as the algorithm has estimated enough data (two periods $T$) and the computation parameter decreases matching the battery discharge rate.
+The path parameter increases as soon as the algorithm has estimated enough data %(two periods $T$)
+and the computation parameter decreases matching the battery discharge rate.
 For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,%kang2009linear,
@@
 Output MPC on Line~\ref{alg:mpc} relies on a software framework for nonlinear optimization called CasADi~\cite{andersson2012casadi%,andersson2012bcasadi,andersson2019casadi
-}, and the popular NLP solver IPOPT~\cite{wachter2006implementation}.
+}, and the popular NLP solver IPOPT~\cite{wachter2006implementation}; both are open-source.
 
@@
 
-\vspace*{-2ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
+
 %\leavevmode\thispagestyle{empty}\newpage

### 2022-05-05 review/response-reviewers-comments.tex
a first implementation of the comments from reviewer 1

\documentclass[10pt]{letter}
\usepackage[utf8]{inputenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{xcolor}
\definecolor{foo}{RGB}{0,51,102}
\usepackage[colorlinks=true,linkcolor=foo,urlcolor=foo]{hyperref}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{cleveref}
\usepackage{tabto}
\usepackage{graphicx}
\usepackage[left=1.1in,right=1.1in,top=.9in,bottom=.9in,%
            footskip=.25in]{geometry}
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
  \fancyhf{}%
    \fancyfoot[C]{%\fontfamily{phv}\selectfont\small\thepage
    }%
    \renewcommand{\headrulewidth}{0pt} % line at the header
    \renewcommand{\footrulewidth}{0pt} % line at the footer (both not visible)
}
\renewcommand\familydefault{\sfdefault}
\renewcommand\sfdefault{phv}
\normalfont
\usepackage{endnotes}

\usepackage{hyperendnotes}
\let\footnote=\endnote
\makeatletter
\def\enoteheading{
  \mbox{}\par\vskip-2.3\baselineskip\noindent\rule{.5\textwidth}{0.4pt}\par\vskip\baselineskip}
\makeatother
\renewcommand\enoteformat{%
  \raggedright
  \leftskip=1.8em
  \vspace{-1.8em}
  \makebox[0pt][r]{\theenmark. \rule{0pt}{\dimexpr\ht\strutbox+\baselineskip}}%
}

\interfootnotelinepenalty=10000

\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

\usepackage{advdate}
\newcommand{\yesterday}{{\AdvanceDate[-1]\today}}

%% pseudocode package
\usepackage{algorithm}
\usepackage[noend]{algorithmic}

% counter to maintain the line numbering
\newcommand{\setalglineno}[1]{%
  \setcounter{ALC@line}{\numexpr#1-1}}

% for adjustwidth environment
\usepackage[strict]{changepage}

% for formal definitions
\usepackage{framed}

% environment derived from framed.sty: see leftbar environment definition
\definecolor{formalshade}{rgb}{0.95,0.95,1}

\newenvironment{formal}{%
  \def\FrameCommand{%
    \hspace{1pt}%
    {\color{blue}\vrule width 2pt}%
    {\color{formalshade}\vrule width 4pt}%
    \colorbox{formalshade}%
  }%
  \MakeFramed{\advance\hsize-\width\FrameRestore}%
  \noindent\hspace{-4.55pt}% disable indenting first paragraph
  \begin{adjustwidth}{}{7pt}%
  \vspace{2pt}\vspace{2pt}%
}
{%
  \vspace{2pt}\end{adjustwidth}\endMakeFramed%
}

\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{plain}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\begin{document}
\pagestyle{plain}
\fontfamily{phv}\selectfont

%\vspace{4em}
%{\center{Adam Seewald \\Dept. \\University of Southern Denmark \\Campusvej 55 \\5230 Odense \\Denmark %\\\href{https://adamseewald.cc}{adamseewald.cc}, \href{mailto:adam@seewald.email}{adam@seewald.email}, \href{tel:+4527849313}{+45 2784 9313}\\
%}}

%\vspace{3em}

%\begin{flushright}Odense, Denmark, \yesterday\end{flushright}

%\vspace{2em}

%Dr. Hanna Kurniawati \\
%Reliable Robot Control (R2C) Lab, Cognitive Robotics Department\\
%Delft University of Technology\\
%Mekelweg 2 \\
%2628 CD Delft \\
%The Netherlands

{\centering Response to the editor and the referees}

\vspace{5em}

Dear Referees, Dr. Kurniawati:

\vspace{1em}

We greatly appreciate your time and effort in providing us with an invaluable assessment of our work, helping us to improve both the quality and presentation of our energy-aware planning-scheduling for the aerial robotics domain. We have been able to address all your comments and questions in a revised version that we have attached once again for your kind consideration.

The document is then split into two sections, each for one review. The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version. The quotes from the revised version are incorporated here in a box with a gray background and a thick blue left border.

Thank you for your time and consideration.

\vspace{1em}

\noindent Kind regards,

\begin{flushright}
Authors of the manuscript 22-0795\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\\
%\includegraphics[scale=.35]{seewald_sig}
\end{flushright}

\vspace{5em}

{First review}

\vspace{1em}

The paper addresses the problem of planning-scheduling for aerial robots with energy awareness for coverage path planning, in which a robot follows a path to cover a polygon. The objective is to maximize the configuration of parameters and satisfy constraints. The authors pose the optimization problem as an MPC and solve for the optimal parameters. They also present an energy model and propose a solution that adjusts the flight path and computational tasks online to deal with energy limitations. This approach extends the energy-aware planning-scheduling to UAVs.

Overall, the paper addresses a very interesting problem and the proposed solution is well-structured.
Related work is well reviewed in this letter. Below are some detailed comments and questions.

{\color{blue}We would like to thank the first referee for assessing our work with great detail, proposing edits, and posing important questions. These helped us to strengthen our contribution and clarify aspects we did not consider in the first version.}

Major Comments:

1. By definition, $t_s$ is the estimated time to complete the coverage, and $t_r$ is the remaining time to complete coverage at time instant $t$. Shouldn't we have $t_r=t_s-t$? However, in line 25 of
algorithm 2, $t_r=(t_s/\overline{t})(\overline{t}-t)$. Let's assume that $t_s=\underline{t}$. At time instant $t=\underline{t}$, by line 25, $t_r=(\underline{t}/\overline{t})(\overline{t}-\underline{t})=\underline{t}-\underline{t}^2/\overline{t}>0$. This does not make sense since the remaining time $t_r$ should equal to $0$. Could you clarify this?

{\color{blue}Thank you for underlying this issue. It is indeed an incorrect transcription of the algorithm, which we have corrected in the revised version. For the sake of clarity, we have further merged line 24 with 25.

\begin{formal}
  \begin{algorithmic}[1]
    \small
      \makeatletter
      \setcounter{ALC@line}{23}
      \makeatother
      \color{blue}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}

      \vspace*{.8ex}
    \end{algorithmic}
  \end{formal}

}

2. Line 24-27 of algorithm 2 only re-plans $c_i^\rho$. What about $c_i^\sigma$? Since the re-planning is conducted after solving the MPC, optimality can not be claimed for the re-planning. It's possible that there are multiple options to adjust the parameters during re-planning: 1. simultaneously adjusting both $c_i^\rho$ and $c_i^\sigma$; 2. only adjust $c_i^\rho$; 3. only adjust $c_i^\sigma$. It might be useful to consider all of these cases and discuss how they affect optimality.

{\color{blue} Thank you for the comment as well as for proposing a way to address the issue. It is correct that in Lines 24--27 we re-plan solely $c_i^\rho$, i.e., the parameters related to the path. The remaining parameters $c_i^\sigma$ related to the computations are then re-planned utilizing the model predictive controller (MPC) in Line 16. The reason why we do not use MPC to plan both the parameters is due to the practical feasibility of re-planning in flight, %While an initial version of the algorithm optimized both via MPC, to assess the satisfaction of the battery constraint w.r.t. the path parameters, in the worst case, we would have to increase the MPC horizon up to the end of the flight.
and due to the different effects of the computation and path parameters on the energy consumption. While the computation parameters have an immediate effect, i.e., they affect the instantaneous energy consumption, the path parameters affect the flight time and thus the overall energy consumption. Concretely and by assumption, a change in the computations alters the schedule, hence the power drained by the computing hardware on the aerial robot, whereas a change in the path parameters alters the time when the aerial robot terminates the coverage.

We have thus decided to utilize a hybrid approach. We employ MPC for the schedule (computations parameters $c_i^\sigma$) and a greedy approach for the coverage (path parameters $c_i^\rho$). Similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}19}] in the revised manuscript).
Nonetheless, as underlined in your observation, this was not clear from the text. We have updated the algorithm in Line 16.

\begin{formal}
\begin{algorithmic}[1]
  \small
    \makeatletter
    \setcounter{ALC@line}{15}
    \makeatother
    \color{blue}\STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i^\sigma(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$\newline \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~({\color{red}18})\newline \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}

    \vspace*{.8ex}
  \end{algorithmic}
\end{formal}

  We have altered the introduction and the problem formulation in Section II to address the observation. We have further added an explanatory text in Section IV.B as well as in the conclusion. In the introduction we have stated explicitly that we utilize both the heuristics and optimal control.

  \begin{formal}
  {\color{black} [...] our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds [...]} Hybrid approaches~[{\color{green}18}] are also available, where the techniques are mixed.
  \vspace*{1ex}
  \end{formal}

  We have altered the problem formulation, clearly stating that the objective is to find energy-aware trajectory of parameters rather than optimal.

  \begin{formal}
    {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time.}
    \vspace*{1ex}
  \end{formal}

  We have then altered Section IV.B.

  \begin{formal}
  \color{black}
  Past literature on planning-scheduling often relies on %optimal control and 
  optimization {\color{blue} as well as heuristics-}related approaches~[{\color{green}13}],~[{\color{green}14}],~[{\color{green}19}],~[{\color{green}23}]. We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters [...] {\color{blue} We utilize MPC to derive the trajectory of the computations parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}

  An optimal control problem (OCP) that selects the highest configuration of {\color{blue} $c_i^\rho$} and respects the constraints [...]

  Line~{\color{red}16} in Algorithm~{\color{red}2} contains [...] a nonlinear program (NLP) that can be solved with available NLP solvers~[{\color{green}47}]. Its solution leads to both trajectories of {\color{blue} computation} parameters and states [...]

  Lines~{\color{red}17}--{\color{red}23} estimate the time [...] to [...] drain the battery, [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned accordingly on Lines~{\color{red}24}--{\color{red}26} using {\color{blue} the heuristics with the} %Lem.~\ref{lem:new} and 
  scaling factors from Eq.~({\color{red}10}) [...]

  \vspace*{1ex}
  \end{formal}

  Finally, we have altered the conclusion.

  \begin{formal}
  \color{black}
  Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.
  \vspace*{1ex}
  \end{formal}
}

3. It is not clear how the parameters of the initial path are obtained. Do the authors use random parameters from the constraint set, or use the highest configuration of parameters? Could you explain the reason for not using the energy-aware planning for the initial trajectory?

{\color{blue}
Thank you for observing this omission. We have utilized the highest and the lowest configurations of parameters for the experiments denoted with roman numerals i, I and ii, II respectively, simulating planning-scheduling in the best- and worst-case scenario. Nonetheless, we do agree it might be advantageous to utilize the algorithm in an 'ideal' simulation first, hence estimate the initial parameters.

We have explicitly stated how we obtain the initial configurations in Section V.

\begin{formal}
  \color{black} [...] {\color{blue} The initial values of path and computations parameters are chosen to represent the highest and lowest configurations in the search space in {\color{red}I}--{\color{red}i} and {\color{red}II}--{\color{red}ii} respectively, modeling the behavior of the best- and worst-case scenario. Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
  \vspace*{1ex}
\end{formal}

}

4. The simulation shows some promising results. However, the organization of Fig.~6 makes it difficult to read. For example, what is the top right plot in Fig.~6(b) showing? I understand that there are a number of figures to present and the space is limited, but I would suggest adding legends and axis titles to the plots if possible. You could also consider rewriting the caption of Fig.~6 to make it descriptive enough to be understood. Otherwise, readers have to repeatedly refer to the main text to understand what a specific plot is presenting.

{\color{blue} [!]}

5. In line 26, shouldn’t the re-planning take place when $t_r>t_b$? In line 27, it is unclear how
re-planning is performed. I would suggest having more discussion on this.

{\color{blue} Thank you for noting the issue as well as for suggesting more discussion. The former is a typo, and we have fixed the if statement in Algorithm 2.

\begin{formal}
  \begin{algorithmic}[1]
    \small
      \makeatletter
      \setcounter{ALC@line}{24}
      \makeatother
      \IF{$t_r>t_b$}
        \color{blue}\STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_r\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
      \color{black}\ENDIF
      \vspace*{.8ex}
    \end{algorithmic}
  \end{formal}

  To clarify the re-planning of the path parameters, we have added explanatory text in Section IV-B.

  \begin{formal}
    \color{black} [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned [...] on Lines~{\color{red}24}--{\color{red}26} [...] {\color{blue}Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~{\color{red}2} but implemented in Sec.~{\color{red}V})}.
    \vspace*{1ex}
  \end{formal}

  We have then detailed the actual value of $\delta_i$ in Section~V.

  \begin{formal}
    \color{black} [...] The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized 
    in the greedy approach}.

    [...] scaling factors are derived empirically %, 
    {\color{blue}similarly to $\delta_i$ set to two hundred fifty}
    \vspace*{1ex}
  \end{formal}
}

6. The following paper is related to this letter and the authors could consider referencing it.
\begin{itemize}
  \item Di Franco, Carmelo, and Giorgio Buttazzo. ``Coverage path planning for UAVs photogrammetry with energy and resolution constraints.'' Journal of Intelligent Robotic Systems 83, no. 3 (2016): 445-462.
\end{itemize}

{\color{blue} [!]}

Minor Comments:

1. In Definition II.1, it would be useful to clarify the use of $j$ and $k$ in the formula of $\Gamma_i$. I assume the authors are saying $c^\rho_i=[c_{i,1},c_{i,2},\dots,c_{i,\rho}]$ and $c^\sigma_i=[c_{i,1},c_{i,2},\dots,c_{i,\sigma}]$, but the definition of $\Gamma_i$ is not quite clear.

{\color{blue} [!]}

2. By definition $[\rho]=\{0,1,2,...,\rho\}$ is a $\rho+1$ tuple, implying that $c^\rho_i$, as the second variable of the path function, is a $\rho+1$ vector in Definition II.1. However, in Definition II.2, it is claimed that the
second variable of the path function is a $\rho$-vector.

{\color{blue} [!]}

3. I noticed a typo under Definition II.1. ``\dots is the $j$th path parameter $c_{i,j}$ constraint set'', should $c_{i,j}$ be removed?

{\color{blue} [!]}

4. In Definition II.1, the use of $\mathbf{p}(t)$ is confusing. I assume $\mathbf{p}$ is an arbitrary point on the path, but $\mathbf{p}(t)$ usually refers to a trajectory.

{\color{blue} [!]}

5. I noticed a typo ``computations parameters'', I think it should be ``computation parameters''

{\color{blue} [!]}

6. Could you please explain how you obtain matrix $A$ and $C$ in (6) and (7), or put some reference?

{\color{blue} [!]}

7. In line 16 of Algorithm 2, $\mathcal{K}={t,t+h,\dots,t+N}$. It should be ${t,t+1,\dots,t+N}$?

{\color{blue} [!]}

8. The definition of $h$ in algorithm 2 is not clear with ``the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$''. Could you clarify how $h$ is obtained? Is $h$ set to 1, or specified by users?

{\color{blue} [!]}

9. By Definition III.2, $g(\cdot)$ has two variables, but equation (12) only has one variable. I assume a time variable is missing

{\color{blue} [!]}

10. There is a typo in the axis title of parameters in Fig. 6(a). The title should be $c_{i,1}$ instead of k$c_{i,1}$

{\color{blue} [!]}

11. The way that the authors define $\tau_{i,j}$ and $\nu_{i,j}$ in (10a) and (10b) implies path parameter
$c_{i,j}$, $j\in\{1,2,\dots,\rho\}$ contributes equally to $t_s$ (defined in line 24 in Algorithm 2). It is difficult to determine if this assumption is reasonable, since $\rho=1$ in the numerical simulations.

{\color{blue} [!]}

\vspace{2em}

{Second reviwew}

\vspace{1em}

\vspace{2em}

\end{document}

### 2022-05-05 energy-planning.tex
a first implementation of the comments from reviewer 1

@@
 
-To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
+To guarantee energy awareness, our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
 Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}.
-Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
+{\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
 The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the optimal trajectory of parameters $c_i$ in time.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time.
 \end{pb}
@@
 
-Past literature on planning-scheduling often relies on optimal control and optimization related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
-We similarly derive an optimal control problem returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+Past literature on planning-scheduling often relies on %optimal control and 
+optimization {\color{blue} as well as heuristics-}related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
+We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
 Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use %a technique in the literature named
 output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$~\cite{rawlings2017model}.
+{\color{blue} We utilize MPC to derive the trajectory of the computations parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
 
@@
       \makeatother
-      \STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}\label{alg:mpc}
+      \color{blue}\STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i^\sigma(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}\label{alg:mpc}
 
       \vspace*{.8ex}
-      \STATE $k\gets t$\vspace*{.3ex}\label{alg:bat1}
+      \color{black}\STATE $k\gets t$\vspace*{.3ex}\label{alg:bat1}
       \WHILE{$b_d(y(k))>0$}\vspace*{.3ex}
@@
       \STATE $t_b\gets k-t$\vspace*{.3ex}\label{alg:bat2}
-      \vspace*{-1.4ex}
-      \STATE $t_s\gets(\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
-      \STATE $t_r\gets(t_s/\overline{t})(\overline{t}-t)$\vspace*{.3ex}
-      \IF{$t_r<t_b$}
-        \STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_c\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
-      \ENDIF
-
+      \vspace*{-2.4ex}
+      %\STATE $t_s\gets(\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]$\vspace*{.3ex}\label{alg:traj1}
+      %\STATE $t_r\gets(t_s/\overline{t})(\overline{t}-t)$\vspace*{.3ex}
+      \color{blue}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}
+      \IF{$t_r>t_b$}
+        \color{blue}\STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_r\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
+      \color{black}\ENDIF
       \vspace*{.8ex}
-      \STATE $\hat{\mathbf{q}}(t+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(t)$\vspace*{.3ex}\label{alg:klm1}
-      \STATE $\hat{y}(t+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(t+h)$\vspace*{.3ex}\label{alg:klm2}
+      \color{black}\STATE $\hat{\mathbf{q}}(t+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(t)$\vspace*{.3ex}\label{alg:klm1}
+      \color{black}\STATE $\hat{y}(t+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(t+h)$\vspace*{.3ex}\label{alg:klm2}
     \ENDFOR
@@
 
-An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
+An optimal control problem (OCP) that selects the highest configuration of {\color{blue} $c_i^\rho$} and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
 \begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
@@
 solved with available NLP solvers~\cite{rawlings2017model}.
-Its solution leads to both trajectories of parameters and states for future $N$ instants.
+Its solution leads to both trajectories of {\color{blue} computation} parameters and states for future $N$ instants.
 Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude), tuning the precision.
@@
 Lines~\ref{alg:bat1}--\ref{alg:bat2} estimate the time needed to completely drain the battery, exploiting the SoC already predicted previously on Line~\ref{alg:mpc}.
-The coverage is then replanned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using %Lem.~\ref{lem:new} and
-scaling factors from Eq.~(\ref{eq:scale-traj}). Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
+The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using {\color{blue} the heuristics with the} %Lem.~\ref{lem:new} and
+scaling factors from Eq.~(\ref{eq:scale-traj}). 
+{\color{blue} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Sec.~\ref{sec:experimental})}.
+Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
 Kalman filter%~\cite{kalman1960new}
@@
 The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
-The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.
+The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized
+in the greedy approach}.
 
@@
 Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
+{\color{blue} The initial values of path and computations parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenario.
+Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
 
@@
 The path parameter increases as soon as the algorithm has estimated enough data %(two periods $T$)
-and the computation parameter decreases matching the battery discharge rate.
-For both cases, scaling factors are derived empirically, the horizon $N$ is set to six seconds similarly to relevant literature~\cite{gavilan2015iterative,%kang2009linear,
+and the computation parameter decreases matching the battery discharge rate. For both cases, scaling factors are derived empirically %, 
+{\color{blue}similarly to $\delta_i$ set to two hundred fifty}, 
+the horizon $N$ is set to six seconds {\color{blue} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
 stastny2018nonlinear%,chao2011collision
@@
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-Further future directions include the study of different energy models.
+Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.
 Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.

### 2022-05-05 scripts/SIM9_casadi2.m

@@ -6,7 +6,7 @@
 
 %% casadi opt control
 
-addpath('../../../../../');
+addpath('../../../../../casadi-linux-matlabR2014b-v3.5.5/');
 % UPDATE THE PATH WITH CASADI SOURCE !
 
 

### 2022-05-09 review/response-reviewers-comments.tex
implemented the comments from the first reviewer

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 % environment derived from framed.sty: see leftbar environment definition
-\definecolor{formalshade}{rgb}{0.95,0.95,1}
+\definecolor{formalshade}{rgb}{1,0.95,0.95}
 
@@
     \hspace{1pt}%
-    {\color{blue}\vrule width 2pt}%
+    {\color{red}\vrule width 2pt}%
     {\color{formalshade}\vrule width 4pt}%
@@
 \rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
+\usepackage{mathtools}
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
 
@@
 The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version.
-The quotes from the revised version are incorporated here in a box with a gray background and a thick blue left border.
+The quotes from the revised version are incorporated here in a box with a light red background and a thick red left border.
 
@@
 
+\newpage
+
 {First review}
 
-\vspace{1em}
+\vspace{3em}
+
+{\hspace*{-4.5em}\textbf{[R1]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue}We would like to thank the first referee for assessing our work with great detail, proposing edits, and posing important questions.
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1]}\vspace*{-1.9em}}
+
+We would like to thank the first referee for assessing our work with great detail, proposing edits, and posing important questions.
 These helped us to strengthen our contribution and clarify aspects we did not consider in the first version.}
 
+\vspace{2em}
+
 Major Comments:
+
+{\hspace*{-4.5em}\textbf{[R1:1]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue}Thank you for underlying this issue.
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:1]}\vspace*{-1.9em}}
+
+Thank you for underlying this issue.
 It is indeed an incorrect transcription of the algorithm, which we have corrected in the revised version.
@@
 
+{\hspace*{-4.5em}\textbf{[R1:2]}\vspace*{-1.9em}}
+
 2.
@@
 
-{\color{blue} Thank you for the comment as well as for proposing a way to address the issue.
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:2]}\vspace*{-1.9em}}
+
+Thank you for the comment as well as for proposing a way to address the issue.
 It is correct that in Lines 24--27 we re-plan solely $c_i^\rho$, i.e., the parameters related to the path.
@@
 We have thus decided to utilize a hybrid approach.
-We employ MPC for the schedule (computations parameters $c_i^\sigma$) and a greedy approach for the coverage (path parameters $c_i^\rho$).
+We employ MPC for the schedule (computation parameters $c_i^\sigma$) and a greedy approach for the coverage (path parameters $c_i^\rho$).
 Similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}19}] in the revised manuscript).
@@
   optimization {\color{blue} as well as heuristics-}related approaches~[{\color{green}13}],~[{\color{green}14}],~[{\color{green}19}],~[{\color{green}23}].
-We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters [...] {\color{blue} We utilize MPC to derive the trajectory of the computations parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
+We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters [...] {\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
 
@@
   Lines~{\color{red}17}--{\color{red}23} estimate the time [...] to [...] drain the battery, [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned accordingly on Lines~{\color{red}24}--{\color{red}26} using {\color{blue} the heuristics with the} %Lem.~\ref{lem:new} and
-  scaling factors from Eq.~({\color{red}10}) [...]
+  scaling factors from Eq.~({\color{red}11}) [...]
 
@@
 
+{\hspace*{-4.5em}\textbf{[R1:3]}\vspace*{-1.9em}}
+
 3.
@@
 {\color{blue}
+
+{\hspace*{-4.5em}{[R1:3]}\vspace*{-1.9em}}
+
 Thank you for observing this omission.
-We have utilized the highest and the lowest configurations of parameters for the experiments denoted with roman numerals i, I and ii, II respectively, simulating planning-scheduling in the best- and worst-case scenario.
-Nonetheless, we do agree it might be advantageous to utilize the algorithm in an 'ideal' simulation first, hence estimate the initial parameters.
+We have utilized the highest and the lowest configurations of parameters for the experiments denoted with roman numerals i, I and ii, II respectively, simulating planning-scheduling in the best- and worst-case scenarios.
+Nonetheless, we do agree it might be advantageous to utilize the algorithm in an 'ideal' simulation first, to estimate the initial parameters.
 
-We have explicitly stated how we obtain the initial configurations in Section V.
+We have explicitly stated how we obtain the initial configurations in Section V and outlined the possibility of utilizing the methodology to estimate the initial parameters.
 
 \begin{formal}
-  \color{black} [...] {\color{blue} The initial values of path and computations parameters are chosen to represent the highest and lowest configurations in the search space in {\color{red}I}--{\color{red}i} and {\color{red}II}--{\color{red}ii} respectively, modeling the behavior of the best- and worst-case scenario.
+  \color{black} [...] {\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in {\color{red}I}--{\color{red}i} and {\color{red}II}--{\color{red}ii} respectively, modeling the behavior of the best- and worst-case scenario.
 Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
@@
 }
+
+{\hspace*{-4.5em}\textbf{[R1:4]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:4]}\vspace*{-1.9em}}
+
+[!]}
+
+{\hspace*{-4.5em}\textbf{[R1:5]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} Thank you for noting the issue as well as for suggesting more discussion. The former is a typo, and we have fixed the if statement in Algorithm 2.
+{\hspace*{-4.5em}{[R1:5]}\vspace*{-1.9em}}
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:5]}\vspace*{-1.9em}}
+
+Thank you for noting the issue as well as for suggesting more discussion. The former is a typo, and we have fixed the if statement in Algorithm 2.
 
@@
 
+{\hspace*{-4.5em}\textbf{[R1:6]}\vspace*{-1.9em}}
+
 6. The following paper is related to this letter and the authors could consider referencing it.
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:6]}\vspace*{-1.9em}}
+
+Thank you for proposing Di Franco and Buttazzo's past work to our attention.
+We have considered another past study by the authors ``Energy-aware coverage path planning of UAVs'' from 2015, and the proposed work appears to be an extension.
+Both studies do not account for the energy contribution of the computations but interestingly propose the variability of the cover by changing the distance of the survey lines in the boustrophedon motion.
+Whilst similar to our Zamboni-like motion, the cover variability is not achieved in flight nor applies to constrained aerial robots such as fixed wings--which we consider due to a narrower computation-motion energy difference--but rather rotary wings (they utilize boustrophedon motion).
+
+We have updated the introductory section to include the work comparing both the studies to ours.
+
+\begin{formal}
+  \color{black} [...] {\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution [{\color{green}25}], and deals with aspects such as the quality of the cover [{\color{green}26}], but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots [...]
+  \vspace*{1ex}
+\end{formal}
+
+We have also updated Section IV-A to explicitly state that the variability of the cover is already considered for rotary wings utilizing the boustrophedon motion.
+
+\begin{formal}
+  \color{black} [...] this section details a [...] motion with a wide turning radius. It is similar to another motion in the literature, the Zamboni
+  motion [{\color{green}42}], but additionally allows variable CPP [...] {\color{blue} Although cover variability is already considered in the literature [{\color{green}25}], it is limited to boustrophedon motion for rotary wings.} The novel motion is termed Zamboni-like motion [...]
+  \vspace*{1ex}
+\end{formal}
+}
+
+\vspace{2em}
 
 Minor Comments:
+
+{\hspace*{-4.5em}\textbf{[R1:7]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:7]}\vspace*{-1.9em}}
+
+Thank you for underlying this issue regarding the definition of stage.
+We are using the indices $j$ and $k$ to indicate that there might be a different constraint per each parameter and the numbers of parameters $\rho$ and $\sigma$ to indicate that there might be a different number of parameters.
+Nonetheless, we acknowledge the necessity to exemplify these in a better manner.
+
+We have altered the definition for this purpose.
+
+\begin{formal}
+  \color{black} 
+  \textbf{Definition}~II.1~(Stage)\textbf{.}~[...] the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$ 
+    is
+  \begin{equation*}\begin{split}
+      \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
+      ,c_i^\rho)},c_i^\sigma\mid
+      \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
+        &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
+  \end{split}\end{equation*}
+  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}.
+$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
+  constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
+{\color{blue}Indices $j$ and $k$ serves to differentiate path and computation parameters constraints and to indicate that each parameter can have a different constraint set.}
+  \vspace*{1ex}
+\end{formal}
+
+}
+
+{\hspace*{-4.5em}\textbf{[R1:8]}\vspace*{-1.9em}}
 
@@
 By definition $[\rho]=\{0,1,2,...,\rho\}$ is a $\rho+1$ tuple, implying that $c^\rho_i$, as the second variable of the path function, is a $\rho+1$ vector in Definition II.1.
-However, in Definition II.2, it is claimed that the
-second variable of the path function is a $\rho$-vector.
+However, in Definition II.2, it is claimed that the second variable of the path function is a $\rho$-vector.
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:8]}\vspace*{-1.9em}}
+
+Thank you for noticing this inconsistency in the notation.
+We have utilized $[\rho]_{>0}$ with the subscript to indicate a $\rho$ tuple.
+We have updated the explanatory text after the definition of the stage accordingly.
+
+\begin{formal}
+  \color{black}
+  [...] The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{blue}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} [...]
+  \vspace*{1ex}
+\end{formal}
+}
+
+{\hspace*{-4.5em}\textbf{[R1:9]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:9]}\vspace*{-1.9em}}
+
+Thank you for noticing the typo. We have removed $c_{i,j}$ from Definition II.1.}
+
+{\hspace*{-4.5em}\textbf{[R1:10]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:10]}\vspace*{-1.9em}}
+
+Thank you for underlying the issue.
+We have not realized this possible source of additional confusion and decided to utilize only $\mathbf{p}$ to designate a point.
+We have altered the occurrence in the remainder of the work, for consistency.
+Apart from Definition II.1 that we showed in point 7, the occurrence was in the definition of path functions.
+
+\begin{formal}
+  \color{black}
+  \textbf{Definition~II.2~}(Path~functions)\textbf{.}~$\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R},\,\forall i\in\{1,2,\dots\}
+  $ are \emph{path functions}, forming the path. They are a function of {\color{blue}$\mathbf{p}%(t)
+  $} and path parameters $c_i^\rho%(t)
+  $ and are continuous and twice differentiable.
+  \vspace*{1ex}
+\end{formal}
+
+In the state-transition function.
+
+\begin{formal}
+  \color{black}
+  [...] the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
+  \begin{equation*}{\color{blue}s(\Gamma_i,\mathbf{p}%(t)
+    )}:=\begin{cases}
+    \Gamma_{i+j} & {\color{blue}\text{if }\norm{\mathbf{p}%(t)
+    -\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},}\\
+    \Gamma_i & \text{otherwise}.
+  \end{cases}\end{equation*}
+\end{formal}
+
+Finally in Algorithm 1 in lines 2 and 3.
+
+\begin{formal}
+  \begin{algorithmic}[1]
+    \small
+      \makeatletter
+      \setcounter{ALC@line}{1}
+      \makeatother
+      \STATE \textbf{if} $\mathbf{p}%(t)
+      =\mathbf{p}_{\Gamma_l}${ in Definition~{\color{red}II.3}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+      \vspace*{.8ex}
+      \STATE \textbf{if} $\mathbf{p}%(t)
+      =\mathbf{p}_{\Gamma_i}$ \textbf{then}
+    \end{algorithmic}
+  \end{formal}
+
+}
+
+{\hspace*{-4.5em}\textbf{[R1:11]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:11]}\vspace*{-1.9em}}
+
+Thank you once again for noticing the typo.
+We have changed the occurrences of ``computations parameters'' with ``computation parameters'', whilst keeping computations when the occurrence indicates multiple computations or when we utilize it to underline, e.g., the energy or schedule of multiple computations.}
+
+{\hspace*{-4.5em}\textbf{[R1:12]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:12]}\vspace*{-1.9em}}
+
+Thank you for noticing that a citation and clarification are missing regarding the energy models.
+The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}3}) and Equation ({\color{red}4}) are equal under some conditions (the value of the initial guess is described by Equation ({\color{red}9}) and the model is not perturbed by the control).
+
+We have elaborated further in Section III-A to reflect the observation and added a reference to the corresponding author's previous work.
+
+\begin{formal}
+  {\color{black}
+  [...] {\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
+  models in Eqs.~({\color{red}3}--{\color{red}4}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
+  and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$}}
+    {\color{blue}\begin{equation}\tag{9}
+    {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
+    \end{equation}}
+    %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
+  %\end{lem}
+  %\begin{proof}
+  %The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$.
+We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess.
+  %\end{proof}
+  %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
+  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies{\color{blue}~[{\color{green}33}]}.}
+  \vspace*{1ex}
+\end{formal}
+}
+
+{\hspace*{-4.5em}\textbf{[R1:13]}\vspace*{-1.9em}}
 
 7. In line 16 of Algorithm 2, $\mathcal{K}={t,t+h,\dots,t+N}$. It should be ${t,t+1,\dots,t+N}$?
-
-{\color{blue} [!]}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:13]}\vspace*{-1.9em}}
+
+Thank you for underlying the necessity of further explanation for the steps in $\mathcal{K},\mathcal{T}$ in both the points 7 and 8.
+The step for $\mathcal{T}$ is utilized to decide the granularity of re-planning, i.e., how often does the aerial robot finds the configurations of path and computations parameters, whereas the step in $\mathcal{K}$ denotes the integration step for the models in MPC.
+
+Practically, we use a step of one for $\mathcal{T}$, running the re-planning every second, and an integration step of 1/100 fraction of a second, since we express $t_f$ and $N$ both in seconds.
+We find the parameters so that the re-planning is feasible in real-time and that the numerical simulation does not diverge.
+
+This was not clear in the text, so we have updated Section IV-B according to the observation.
+
+\begin{formal}
+  \color{black} [...] Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{blue}: 
+  the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning in $\mathcal{K}$, $\mathcal{T}$ respectively.}
+  \vspace*{1ex}
+\end{formal}
+
+We have then updated Section V.
+
+\begin{formal}
+  \color{black} [...] {\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
+  \vspace*{1ex}
+\end{formal}
+
+}
+
+{\hspace*{-4.5em}\textbf{[R1:14]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
+
+{\hspace*{-4.5em}{[R1:14]}\vspace*{-1.9em}}
+
+[!]}
+
+{\hspace*{-4.5em}\textbf{[R1:15]}\vspace*{-1.9em}}
 
@@
 
-{\color{blue} [!]}
+{\color{blue}
 
-11. The way that the authors define $\tau_{i,j}$ and $\nu_{i,j}$ in (10a) and (10b) implies path parameter
-$c_{i,j}$, $j\in\{1,2,\dots,\rho\}$ contributes equally to $t_s$ (defined in line 24 in Algorithm 2).
+{\hspace*{-4.5em}{[R1:15]}\vspace*{-1.9em}}
+
+[!]}
+
+{\hspace*{-4.5em}\textbf{[R1:16]}\vspace*{-1.9em}}
+
+11.
+The way that the authors define $\tau_{i,j}$ and $\nu_{i,j}$ in (10a) and (10b) implies path parameter $c_{i,j}$, $j\in\{1,2,\dots,\rho\}$ contributes equally to $t_s$ (defined in line 24 in Algorithm 2).
 It is difficult to determine if this assumption is reasonable, since $\rho=1$ in the numerical simulations.
 
-{\color{blue} [!]}
+{\color{blue}
 
-\vspace{2em}
+{\hspace*{-4.5em}{[R1:16]}\vspace*{-1.9em}}
+
+[!]}
+
+\newpage
 
 {Second reviwew}
+
+\vspace{3em}
+
+{\hspace*{-4.5em}\textbf{[R2]}\vspace*{-1.9em}}
+
+Contributions:
+
+The contributions of this paper are 1) an energy model that predicts the impact of the effect of changes to the path or computation energy on the battery in the future 2) introduction of Zamboni-like motion patterns that can be replanned while on the path itself 3) an optimal control problem and solution to solve the re-planning coverage problem to decide how to change the computations and the path to optimize the energy usage
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2]}\vspace*{-1.9em}}
+
+[!]
+}
+
+Related work:
+
+- Good and varied connections made to situate this work in the field.
+
+{\hspace*{-4.5em}\textbf{[R2:1]}\vspace*{-1.9em}}
+
+- Not made clear how this is different from other relevant works such as work cited ``C.
+Di Franco and G.
+Buttazzo, ``Energy-aware coverage path planning of UAVs,'' in Int.
+Conf.
+on Autonomous Robot Syst.
+and Competitions.
+IEEE, 2015, pp.
+111–117''; especially when stating ``These studies are focused on ground-based robots [9], [19], [23], [24], yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery''; since this is not the first with aerial robots, what about this research is different from other work on energy aware CPP?
+Summarize clearly differences in related work in UAV literature.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:1]}\vspace*{-1.9em}}
+
+[!]
+}
+
+Strengths:
+
+- This paper addresses a very interesting and practical issue when using UAVs: how to change the behavior of the fixed-wing UAV computations and path w.r.t.
+to how much battery is left to optimize energy usage.
+
+- Clear preliminaries section helps with understanding technical detail.
+
+- Synthesizes techniques and ideas from various different topics/domains into the challenging replanning coverage problem.
+
+- Technical solution of optimal control problem to manage both computing workloads and path plan interesting and relevant contribution.
+
+- Good simulations with modeling different wind speeds/directions.
+
+Weaknesses:
+
+{\hspace*{-4.5em}\textbf{[R2:2]}\vspace*{-1.9em}}
+
+- High-level comment: the paper would benefit from restructuring for clarity to better convey the interesting technical ideas.
+At present, difficult to understand the insights behind the main contributions.
+For example, ``the re-planning-scheduling problem is finding the optimal trajectory of parameters $c_i$ in time.'' -- optimal w.r.t.
+what objective function?
+Total energy?
+Mission duration?
+Make this clear in the problem definition section.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:2]}\vspace*{-1.9em}}
+
+[!]
+}
+
+  {\hspace*{-4.5em}\textbf{[R2:3]}\vspace*{-1.9em}}
+
+  Also, ``The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds [12] and frequency and voltage of the computing hardware [9], [13], [14].
+We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage'' --$>$ What are the actual computation inputs that can be changed?
+It is unclear throughout the paper what $c_i^\sigma$ is.
+
+  {\color{blue}
+
+  {\hspace*{-4.5em}{[R2:3]}\vspace*{-1.9em}}
+
+  [!]}
+
+  {\hspace*{-4.5em}\textbf{[R2:4]}\vspace*{-1.9em}}
+
+  In addition, what is the performance metric we want to observe improving using the algorithm 2 in the numerical experiments (comparing i, ii to I, II baselines)?
+
+  {\color{blue}
+
+  {\hspace*{-4.5em}{[R2:4]}\vspace*{-1.9em}}
+
+  [!]}
+
+{\hspace*{-4.5em}\textbf{[R2:5]}\vspace*{-1.9em}}
+
+- Paper would benefit from clear indication of what the performance metric we want to see improve.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:5]}\vspace*{-1.9em}}
+
+[!]}
+
+  {\hspace*{-4.5em}\textbf{[R2:6]}\vspace*{-1.9em}}
+
+  Average results from more numeric experiments (e.g., average flights competed on baseline vs.
+with new algorithm) would also really benefit the paper.
+Paper would also be greatly strengthened by actual physical experiments on UAV.
+
+  {\color{blue}
+
+  {\hspace*{-4.5em}{[R2:6]}\vspace*{-1.9em}}
+
+  [!]}
+
+{\hspace*{-4.5em}\textbf{[R2:7]}\vspace*{-1.9em}}
+
+- ``the Zamboni motion [40], but additionally allows variable CPP at the very core of this work.'' -- need to clarify more why Algorithm 1/Zamboni-like motion is different from Zamboni motion.
+What is the   insight that allows the Zamboni motion to be recalculated/replanned at each stage that isn't possible with regular Zamboni motion in reference [40]?
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:7]}\vspace*{-1.9em}}
+
+[!]}
+
+Specific edits/typos:
+
+{\hspace*{-4.5em}\textbf{[R2:8]}\vspace*{-1.9em}}
+
+- ``Such use cases arise in, e.g., precision agriculture [4], where harvesting involves ground vehicles [5], [6], information collection prior to an operation as well as damage prevention during the operation involve aerial robots'' is unclear/grammatically incorrect.
+--$>$	``Such use cases arise in precision agriculture [4] where information collection prior to an harvesting operation and damage prevention during the operation involve aerial robots''
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:8]}\vspace*{-1.9em}}
+
+[!]
+}
+
+{\hspace*{-4.5em}\textbf{[R2:9]}\vspace*{-1.9em}}
+
+- Figure 1 not clear; are we supposed to be able to differentiate between i, ii, and iii paths?
+Not able to differentiate currently, so unable to understand key takeaway of figure.
+What is the meaning of the colors (green for i, red for ii/iii)?
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:9]}\vspace*{-1.9em}}
+
+[!]}
+
+{\hspace*{-4.5em}\textbf{[R2:10]}\vspace*{-1.9em}}
+
+- ``i.e., when the motion energy contribution far outreaches the computations or vice-versa.
+The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quad-copters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).'' --$>$ clarify which example is to which case (motion energy $>$ computing energy for quadrotor, motion energy $<$ computing energy for lighter-than-air)
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:10]}\vspace*{-1.9em}}
+
+[!]}
+
+{\hspace*{-4.5em}\textbf{[R2:11]}\vspace*{-1.9em}}
+
+- ordering of figures in Figure 6 is confusing. Consider lumping each case in a separate row (I, i, II, ii).
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:11]}\vspace*{-1.9em}}
+
+[!]
+}
+
+{\hspace*{-4.5em}\textbf{[R2:12]}\vspace*{-1.9em}}
+
+Overall, the paper addresses a very interesting topic and brings together many different techniques to solve a challenging problem.
+It could be strengthened with more attention to clarity to convey the technical insights and more experiments showing an improvement in a performance metric of interest.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[R2:12]}\vspace*{-1.9em}}
+
+[!]}
 

### 2022-05-09 energy-planning.tex
implemented the comments from the first reviewer

@@
 These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery.
+{\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution~\cite{difranco2015energy}, and deals with aspects such as the quality of the cover~\cite{difranco2016coverage}, but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.}
 Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
@@
 At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
-Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.%with information about the path and the schedule.
+Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computation}-specific \emph{parameters}.%with information about the path and the schedule.
 
@@
   Given a generic point $\mathbf{p}\in\mathbb{R}^2$ w.r.t.
-a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ at time instant $t$ %of a plan $\Gamma$
+a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$
   is
   \begin{equation*}\begin{split}
-    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
+    \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
+    ,c_i^\rho)},c_i^\sigma\mid
     \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
@@
   \end{split}\end{equation*}
-  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}.
-$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter $c_{i,j}$ constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
+  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}.
+$\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
+  constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
+{\color{blue}Indices $j$ and $k$ serves to differentiate path and computation parameters constraints and to indicate that each parameter can have a different constraint set.}
 \end{defn}
@@
 Bold letters indicate vectors. 
-The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of a parameter $x$, i.e.,
+The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{blue}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of a parameter $x$, i.e.,
 \begin{equation}
@@
   $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R},\,\forall i\in\{1,2,\dots\}
-  $ are \emph{path functions}, forming the path. They are a function of $\mathbf{p}(t)$ and path parameters $c_i^\rho(t)$ and are continuous and twice differentiable.
+  $ are \emph{path functions}, forming the path. They are a function of {\color{blue}$\mathbf{p}%(t)
+  $} and path parameters $c_i^\rho%(t)
+  $ and are continuous and twice differentiable.
 \end{defn}
@@
   The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
-  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
-    \Gamma_{i+j} & \text{if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},\\
+  \begin{equation*}{\color{blue}s(\Gamma_i,\mathbf{p}%(t)
+    )}:=\begin{cases}
+    \Gamma_{i+j} & {\color{blue}\text{if }\norm{\mathbf{p}%(t)
+    -\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},}\\
     \Gamma_i & \text{otherwise}.
@@
 
-Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. %The notation .
+Here, $c_i$ denotes a row vector with both the path and computation parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. %The notation .
 
@@
                          %
-The solution to the problem requires energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants.
+The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery at future time instants.
 To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies as well as battery evolution.
@@
 
-To define the nominal control and the output matrix, we exploit the effect of variation of path and computations parameters on the energy. 
+To define the nominal control and the output matrix, we exploit the effect of variation of path and computation parameters on the energy. 
 %We assume a variation in computations parameters $c_i^\sigma$ affects the instantaneous energy, i.e., different schedules of power-demanding computational tasks have different power drains from the computing hardware.
@@
   Given $c_i(t)$ parameters at two following time instants $t\in\{t_j,t_{j+1}\}\subset\mathbb{R}_{\geq 0}$ s.t.
-$t_j<t_{j+1}$ for an arbitrary stage $\Gamma_i$, a change in parameters $c_i(t_j)\neq c_i(t_{j+1})$ results in different overall and instantaneous energies for path and computations parameters respectively.
+$t_j<t_{j+1}$ for an arbitrary stage $\Gamma_i$, a change in parameters $c_i(t_j)\neq c_i(t_{j+1})$ results in different overall and instantaneous energies for path and computation parameters respectively.
 %\end{lem}
@@
 
-The %Under favorable conditions, %the 
+{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
 models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
@@
 and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
-  \begin{equation*}
-  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',
-  \end{equation*} 
+  {\color{blue}\begin{equation}
+  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
+  \end{equation}}
   %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
@@
 %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
-i.e., $h,y$ are both harmonic signals with the same frequencies.
+i.e., $h,y$ are both harmonic signals with the same frequencies{\color{blue}~\cite{seewaldphdthesis}}.
 
@@
 
-Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with %scaling factors
+Similarly to Eq.~(\ref{eq:scale-traj}), computation parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with %scaling factors
 \begin{subequations}\label{eq:scale-comp}\begin{align}
@@
 It is segmented into two layers.
-In the \emph{measurement layer}, the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piecewise linear regression.
+In the \emph{measurement layer}, the tool measures a discrete set of computation parameters and infers the energy of the remaining in the \emph{predictive layer} via a piecewise linear regression.
 
@@
 \begin{defn}[Measurement layer]\label{def:meas}
-  Given a measuring device, computations parameters, and initial and final time instants, the \emph{measurement layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
+  Given a measuring device, computation parameters, and initial and final time instants, the \emph{measurement layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
 \end{defn}
@@
 \begin{defn}[Predictive layer]\label{def:pred}
-  Given a measuring device and computations parameters, the \emph{predictive layer} is the function $g:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns an energy measure.
+  Given a measuring device and computation parameters, the \emph{predictive layer} is the function $g:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns an energy measure.
 \end{defn}
@@
 It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work.
+{\color{blue} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}
 The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
@@
     \FORALL{$t\in\mathcal{T}$}
-      \STATE \textbf{if} $\mathbf{p}(t)=\mathbf{p}_{\Gamma_l}${ in Definition~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}
+      \color{blue}\STATE \textbf{if} $\mathbf{p}%(t)
+      =\mathbf{p}_{\Gamma_l}${ in Definition~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}\color{black}
 
@@
       \vspace*{.8ex}
-      \IF{$\mathbf{p}(t)=\mathbf{p}_{\Gamma_i}$}
+      \color{blue}\IF{$\mathbf{p}%(t)
+      =\mathbf{p}_{\Gamma_i}$}\color{black}
         \STATE $i\gets i+1$\vspace*{.3ex}
@@
 output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$~\cite{rawlings2017model}.
-{\color{blue} We utilize MPC to derive the trajectory of the computations parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
+{\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
 
@@
 Its solution leads to both trajectories of {\color{blue} computation} parameters and states for future $N$ instants.
-Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude), tuning the precision.
+Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{blue}:
+the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning in $\mathcal{K}$, $\mathcal{T}$ respectively.}
 The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}), with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}
@@
 Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
-{\color{blue} The initial values of path and computations parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenario.
+{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenario.
 Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
@@
 }, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
+{\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
 %\subsection{Algorithm evaluation}

### 2022-05-09 review/response-letter.tex
addressed some more comments from reviewer 2

--- 2022-05-09 review/response-reviewers-comments.tex
@@
 
-%\begin{flushright}Odense, Denmark, \yesterday\end{flushright}
+\begin{flushright}%Odense, Denmark, 
+  \yesterday\end{flushright}
 
-%\vspace{2em}
+\vspace{2em}
 
@@
 
-{\centering Response to the editor and the referees}
+{\centering Response letter to the editor and the referees}
 
@@
 
-We greatly appreciate your time and effort in providing us with an invaluable assessment of our work, helping us to improve both the quality and presentation of our energy-aware planning-scheduling for the aerial robotics domain.
+We greatly appreciate your time and effort in providing us with an invaluable assessment of our work, helping us to significantly improve both the quality and presentation of our energy-aware planning-scheduling for the aerial robotics domain.
 We have been able to address all your comments and questions in a revised version that we have attached once again for your kind consideration.
 
-The document is then split into two sections, each for one review.
+The response letter is split into two sections, each for one review.
 The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version.
@@
 We would like to thank the first referee for assessing our work with great detail, proposing edits, and posing important questions.
-These helped us to strengthen our contribution and clarify aspects we did not consider in the first version.}
+These helped us to strengthen our contribution and clarify aspects we did not consider in the first version.
+
+In this work, we choose to leverage planning-scheduling to aerial robotics, as we believe this is a relevant application and advantageous system for our devised approach.
+We are thus excited to see the referee sharing similar findings while bringing up numerous important points.}
 
@@
 We have utilized the highest and the lowest configurations of parameters for the experiments denoted with roman numerals i, I and ii, II respectively, simulating planning-scheduling in the best- and worst-case scenarios.
-Nonetheless, we do agree it might be advantageous to utilize the algorithm in an 'ideal' simulation first, to estimate the initial parameters.
+Nonetheless, we do agree it might be advantageous to utilize the algorithm in an ideal simulation first, to estimate the initial parameters.
 
@@
 
-[!]
+We would like to thank the second referee, especially for the summary of our work and the kind commentary on the relevance and difficulty of accounting for both motion and computations energies in planning for aerial robots.
+Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots broadly.
+To that end, we are excited to comment on and alter the manuscript as necessary, as the second referee brings up a lot of great points.
+
 }
+
+\vspace{2em}
 
@@
 
-[!]
+Thank you for proposing Di Franco and Buttazzo's past study to our attention.
+We have considered the work in the original manuscript in terms of the coverage algorithm in Section IV-A, utilizing it as a reference for aerial coverage.
+We have not included it in the introductory material as the work does not account for the energy expenditure of computations, nonetheless, we agree on the necessity to clarify this in the introduction.
+To this end, we have added explanatory text in the introduction that--aside the proposed work--includes the follow-up work by the same set of authors proposed by the first referee.
+
+\begin{formal}
+  \color{black} [...] {\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution [{\color{green}25}], and deals with aspects such as the quality of the cover [{\color{green}26}], but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots [...]
+  \vspace*{1ex}
+\end{formal}
+
+We have then explicitly stated the work in Section~IV-A
+in terms of the variability of the cover.
+
+\begin{formal}
+  \color{black} [...] this section details a [...] motion with a wide turning radius. It is similar to another motion in the literature, the Zamboni
+  motion [{\color{green}42}], but additionally allows variable CPP [...] {\color{blue} Although cover variability is already considered in the literature [{\color{green}25}], it is limited to boustrophedon motion for rotary wings.} The novel motion is termed Zamboni-like motion [...]
+  \vspace*{1ex}
+\end{formal}
+
 }
+
+\vspace{2em}
 
@@
 - Good simulations with modeling different wind speeds/directions.
+
+\vspace{2em}
 
@@
 
+\vspace{2em}
+
 Specific edits/typos:
@@
 
-[!]
+Thank you for spotting the issue in the introductory section. We have corrected the sentence.
+
+\begin{formal}
+  \color{black} [...] Such use cases arise in precision agriculture~[{\color{green}4}] where {\color{blue}information collection prior to an harvesting operation and} damage prevention during the operation involve aerial robots~[{\color{green}5}],~[{\color{green}6}].
+
+  \vspace*{1ex}
+\end{formal}
+
 }

### 2022-05-09 energy-planning.tex
addressed some more comments from reviewer 2

@@
 %with little human interaction.
-Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground vehicles~\cite{%qingchun2012study,
-dong2011development, de2011design%,aljanobi2010setup, 
+Such use cases arise in%, e.g., 
+precision agriculture~\cite{hajjaj2014review} 
+where 
+{\color{blue}information collection prior to an harvesting operation and}
+%harvesting involves ground vehicles~\cite{%qingchun2012study,
+%dong2011development, de2011design%,aljanobi2010setup, 
 %li2008analysis, 
 %edan2000robotic
-}, information collection prior to an operation as well as damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
+%}, information collection prior to an operation as well as 
+damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
 Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial%, peng2019evaluating,

### 2022-05-11 review/response-letter.tex
addressing comments from reviewer 2 (2)

@@
   \end{split}\end{equation*}
-  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}.
+  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~{\color{red}V})}.
 $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
@@
 
-  [!]}
+  Thank you for underlying the need to state clearly what the computations parameters refer to.
+We have not realized this point was not stated explicitly in the original version earlier than in the experimental setup.
+Our purpose is to alter the granularity at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.
+
+  In our experimental setup, these are the detection rate--meaning we vary the frequency at which a convolutional neural network trained to detect specific hazards runs from two to ten frames per second.
+These two values are determined empirically, by sampling different boundary configurations and their energy consumption via the modeling tool we describe in Section III-B.
+We have varied other parameters as well, such as the encryption, utilizing a binary value simply indicating whether the encryption is or is not enabled, and the size of the key in a variable key-size encryption algorithm.
+However, we have not observed a significant energy drain changing these parameters, conversely to the parameter detection rate.
+Thus we utilized merely the computation parameter 'detection rate' in our current experimental setup.
+
+  We have updated the introductory material to state concretely what computational input is being varied.
+
+  \begin{formal}\color{black}
+    [...] The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~[{\color{green}10}] and frequency and voltage of the computing hardware~[{\color{green}7}], [{\color{green}11}], [{\color{green}12}].
+We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
+    {\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.} [...]
+    \vspace*{1ex}
+  \end{formal}
+
+  We have further included the concrete meaning of parameters in Section II.
+
+  \begin{formal}
+    \color{black} 
+    \textbf{Definition}~II.1~(Stage)\textbf{.}~[...] the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$ 
+      is
+    \begin{equation*}\begin{split}
+        \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
+        ,c_i^\rho)},c_i^\sigma\mid
+        \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
+          &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
+    \end{split}\end{equation*}
+    where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~{\color{red}V})}.
+[...]
+    \vspace*{1ex}
+  \end{formal}
+
+  }
 
@@
 
-[!]}
+Thank you for underlying this possible source of confusion. We have fixed the text to clearly state whether the category is in the former or latter occurrence.
+
+\begin{formal}
+  \color{black} [...] there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
+The {\color{blue}former} occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the latter with} lighter-than-air aerial robots (e.g., blimps).
+[...]
+  \vspace*{1ex}
+\end{formal}}
 
@@
 }
+
+\vspace*{2em}
 

### 2022-05-11 energy-planning.tex
addressing comments from reviewer 2 (2)

@@
 We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
+{\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
 Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
@@
 Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps).
+The {\color{blue}former} occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the latter with} lighter-than-air aerial robots (e.g., blimps).
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
@@
   \end{split}\end{equation*}
-  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}.
+  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~\ref{sec:experimental})}.
 $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$

### 2022-05-16 review/response-letter.tex
fixed Figure 6 with reviewers comments (need to fix refs in text with the figure)

@@
   \color{black} [...] there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The {\color{blue}former} occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the latter with} lighter-than-air aerial robots (e.g., blimps).
+The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
 [...]

### 2022-05-16 energy-planning.tex
fixed Figure 6 with reviewers comments (need to fix refs in text with the figure)

@@
 Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The {\color{blue}former} occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the latter with} lighter-than-air aerial robots (e.g., blimps).
+The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
@@
 
+\begin{figure*}
+  %\vspace*{-4ex}
+  \centering
+  \footnotesize
+  \input{\figpath/results/new_physics2/new_trajs-ener_I-II.tikz}
+  \label{fig:1}
+  \caption{.}
+  \vspace*{-3ex}
+\end{figure*}
+
+\begin{figure*}
+  %\vspace*{-4ex}
+  \centering
+  \footnotesize
+  \input{\figpath/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
+  \label{fig:2}
+  \caption{.}
+  \vspace*{-3ex}
+\end{figure*}
+
 \vspace*{-1.5ex}

### 2022-05-17 review/response-letter.tex
almost finished implementing all the reviewers comments

@@
 \usepackage{graphicx}
+\usepackage{tikz}
 \usepackage[left=1.1in,right=1.1in,top=.9in,bottom=.9in,%
@@
 \usepackage{endnotes}
-
+\usepackage{float,graphicx}
 \usepackage{hyperendnotes}
@@
   \begin{formal}
-    {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time.}
+    {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.}
     \vspace*{1ex}
@@
 
-[!]}
+Thank you for the concern regarding the readability of the figure.
+We have split the figure to address the concern into two Figures, 6 and 7.
+Subfigures that are related are then on a separate row, each for one case.
+I,II in Figure 6 are related to CPP at boundary values of path parameters and varying atmospheric conditions, and i,ii Figure 7 are related to planning-scheduling of I,II with varying battery conditions.
+We have rewritten the captions, adding additional commentary to ease the understanding.
+
+\begin{formal}
+  \footnotesize
+  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
+  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations.
+In \hyperref[fig:stat]{a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}.
+In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
+In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}
+
+  \input{../figures/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
+  \vspace*{-.6ex}
+  {\color{blue}
+  Fig.~7:~Planning-scheduling of CPP and ground patterns detections% with PedNet CNN
+  , utilizing the lowest configuration {\color{red}I} as a starting point in {\color{red}i} and the highest {\color{red}II} in {\color{red}ii} while varying atmospheric (same as Fig.~{\color{red}6}) and battery conditions.
+In {\color{red}a} are the re-planned trajectories, in {\color{red}b} the parameters, and in {\color{red}c} the energy w.r.t.
+the battery.}
+  \vspace*{1ex}
+\end{formal}
+}
 
@@
 
-[!]}
+Thank you for noticing the typo. We have fixed the axis title.
+}
 
@@
 
-[!]
+Thank you for the high-level comment and for proposing to state clearly the objective function.
+Regarding the objective function, we have integrated the problem definition accordingly, whereas we have altered the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further explanatory commentary.
+
+\begin{formal}
+  {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.}
+  \vspace*{1ex}
+\end{formal}
 }
@@
 
-[!]}
+Thank you for suggesting adding a clear indication of what performance metrics are being utilized.
+Indeed this information was missing in the original manuscript.
+We have added explanatory text in Problem Formulation to address the point.
+
+\begin{formal}\color{black}
+  The problem %of planning-scheduling 
+is composed of two sub-problems{\color{blue}: }%. One is 
+to form a %static 
+plan that visits every point in space, {\color{blue}and }%the other to
+re-plan and re-schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
+{\color{blue} The performance metric the re-planning-scheduling %in the letter 
+improves is %then
+the quality of the plan-schedule against battery SoC, e.g., the weighted average value of parameters divided by remaining %battery 
+SoC.% at the end of the flight.
+\vspace*{1ex}
+}
+\end{formal}
+}
 
@@
 
-[!]
+Thank you for underlying the issue.
+We have attempted to optimize the space but overloaded the figure and significantly reduced its readability.
+We have reordered Figure 6 to address the issue.
+We have first split the figure into two Figures, 6 and 7.
+In both, we utilize one row per case.
+Figure 6 contains cases I and II related to static coverage at the two boundary configurations under varying wind speeds and directions.
+
+\begin{formal}
+  \footnotesize
+  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
+  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations.
+In \hyperref[fig:stat]{a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}.
+In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
+In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}
+\end{formal}
+
+Figure 7 contains cases i and ii that start from I and II but employ the planning-scheduling in the letter varying battery conditions.
+
+\begin{formal}
+  \footnotesize
+  \input{../figures/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
+  \vspace*{-.6ex}
+  {\color{blue}
+  Fig.~7:~Planning-scheduling of CPP and ground patterns detections% with PedNet CNN
+  , utilizing the lowest configuration {\color{red}I} as a starting point in {\color{red}i} and the highest {\color{red}II} in {\color{red}ii} while varying atmospheric (same as Fig.~{\color{red}6}) and battery conditions.
+In {\color{red}a} are the re-planned trajectories, in {\color{red}b} the parameters, and in {\color{red}c} the energy w.r.t.
+the battery.}
+  \vspace*{1ex}
+\end{formal}
 }

### 2022-05-17 energy-planning.tex
almost finished implementing all the reviewers comments

@@
 
-The problem of planning-scheduling is composed of two sub-problems.
-One is to form a static plan that visits every point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.
+The problem %of planning-scheduling 
+is composed of two sub-problems{\color{blue}: }%. One is 
+to form a %static 
+plan that visits every point in space, {\color{blue}and }%the other to
+re-plan and re-schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
+{\color{blue} The performance metric the re-planning-scheduling %in the letter 
+improves is %then
+the quality of the plan-schedule against battery SoC, e.g., weighted average value of parameters divided by remaining %battery 
+SoC.% at the end of the flight.
+}
 
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.
 \end{pb}
@@
 The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules.
-Additionally, the \powprof{} tool supports the battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}.
+Additionally, the \powprof{} tool supports the battery SoC detailed in Section~\ref{sec:mod-bat}.
 The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
@@
 
+%\begin{figure*}
+%  \centering
+%  \vspace*{-4ex}
+%  \begin{subfigure}{.4\textwidth}
+%    \centering
+%    \footnotesize
+%    \input{\figpath/results/new_physics2/trajs3.tikz}
+%    \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
+%    \label{fig:trajs}
+%  \end{subfigure}\hspace*{3ex}
+%  \begin{subfigure}{.54\textwidth}
+%    \centering
+%    \footnotesize
+%    \input{\figpath/results/new_physics2/ener3.tikz}
+%    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$), and parameters ($T,b_0$) evolutions}
+%    \label{fig:ener}
+%  \end{subfigure}
+%  \footnotesize
+%  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}): wind speed and direction, battery behavior, and parameters initial values.}
+%  \label{fig:res}
+%  \vspace*{-3ex}
+%\end{figure*}
 \begin{figure*}
-  \centering
   \vspace*{-4ex}
-  \begin{subfigure}{.4\textwidth}
-    \centering
-    \footnotesize
-    \input{\figpath/results/new_physics2/trajs3.tikz}
-    \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
-    \label{fig:trajs}
-  \end{subfigure}\hspace*{3ex}
-  \begin{subfigure}{.54\textwidth}
-    \centering
-    \footnotesize
-    \input{\figpath/results/new_physics2/ener3.tikz}
-    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$), and parameters ($T,b_0$) evolutions}
-    \label{fig:ener}
-  \end{subfigure}
-  \footnotesize
-  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}): wind speed and direction, battery behavior, and parameters initial values.}
-  \label{fig:res}
-  \vspace*{-3ex}
-\end{figure*}
-
-\begin{figure*}
-  %\vspace*{-4ex}
   \centering
@@
   \input{\figpath/results/new_physics2/new_trajs-ener_I-II.tikz}
-  \label{fig:1}
-  \caption{.}
+  \captionsetup{labelfont={color=blue}}
+  \vspace*{-.6ex}
+  \caption{\color{blue}CPP with Zamboni-like motion using two boundary configurations.
+In \hyperref[fig:stat]{a} are the trajectories of the coverage--the highest in \hyperref[fig:trajs-I-static]{I} and the lowest in \hyperref[fig:trajs-II-static]{II}.
+In \hyperref[fig:stat]{b} are the energy and the period evolutions for both \hyperref[fig:trajs-I-static]{I} and \hyperref[fig:trajs-II-static]{II} with different atmospheric conditions.
+In \hyperref[fig:stat]{c} are the states that compose the energy model for \hyperref[fig:trajs-I-static]{I}.}
+  \label{fig:stat}
   \vspace*{-3ex}
 \end{figure*}
-
 \begin{figure*}
@@
   \input{\figpath/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
-  \label{fig:2}
-  \caption{.}
-  \vspace*{-3ex}
+  \captionsetup{labelfont={color=blue}}
+  \vspace*{-.6ex}
+  \caption{\color{blue}
+  Planning-scheduling of CPP and ground patterns detections% with PedNet CNN
+  , utilizing the lowest configuration \hyperref[fig:trajs-I-static]{I} as a starting point in \hyperref[fig:trajs-dyn-i]{i} and the highest \hyperref[fig:trajs-II-static]{II} in \hyperref[fig:trajs-dyn-ii]{ii} while varying atmospheric (same as Fig.~\ref{fig:stat}) and battery conditions.
+In \hyperref[fig:dyn]{a} are the re-planned trajectories, in \hyperref[fig:dyn]{b} the parameters, and in \hyperref[fig:dyn]{c} the energy w.r.t.
+the battery.
+  }
+  \label{fig:dyn}
+  \vspace*{-4ex}
 \end{figure*}
@@
 in standard atmospheric conditions. 
-Fig.~\ref{fig:res} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Fig.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
 Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.
@@
 
-Fig.~\ref{fig:trajs} illustrates the same plan $\Gamma$ under different conditions.
+Fig.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
+illustrate the same plan $\Gamma$ under different conditions.
 Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection).
@@
 
-Fig.~\ref{fig:ener} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
+Fig.~%\ref{fig:ener}
+{\color{blue}\hyperref[fig:stat]{6b}--\hyperref[fig:dyn]{7c}} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
 illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
-Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery (green line, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
-Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ when the battery is discharging, respecting the output constraint (Eq.~(\ref{eq:output-const})).
+Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery ({\color{blue}see} green line {\color{blue}in Fig.~\hyperref[fig:dyn]{7c}}, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ {\color{blue}(see Fig.~\hyperref[fig:dyn]{7b})} when the battery is discharging, respecting the output constraint (Eq.~(\ref{eq:output-const})).
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario: the lowest configuration of parameters and no battery defects.
@@
 %\subsubsection*{Periodic energy model}
-The figure further details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
+%The figure
+{\color{blue} Fig.~\hyperref[fig:stat]{6c}} %further 
+details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
 % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
-The bottom detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
+The {\color{blue} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state
 estimate.

### 2022-05-18 review/response-letter.tex
implementing the final points from the reviews

@@
 \begin{formal}
-  \color{black} [...] {\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in {\color{red}I}--{\color{red}i} and {\color{red}II}--{\color{red}ii} respectively, modeling the behavior of the best- and worst-case scenario.
+  \color{black} [...] {\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in {\color{red}I}--{\color{red}i} and {\color{red}II}--{\color{red}ii} respectively, modeling the behavior of the best- and worst-case scenarios.
 Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}

### 2022-05-18 energy-planning.tex
implementing the final points from the reviews

@@
 Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
-{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenario.
+{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenarios.
 Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
@@
 illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
+{\color{blue} Fig.~\hyperref[fig:stat]{6b}} %further 
+details then the energy model's estimate (%see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}
+{\color{blue}${\hat{y}}$}) on an initial slice%of the model (${\hat{y}}$)
+, power ($\Upsilon$), and period ($T$).
+{\color{blue} Fig.~\hyperref[fig:stat]{6c}} illustrates the evolutions of the state $\mathbf{q}$ in time {\color{blue}for \hyperref[fig:ener:static-I]{I}}, concluding that approximately two periods suffice for a consistent %state
+estimate.
+
 Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery ({\color{blue}see} green line {\color{blue}in Fig.~\hyperref[fig:dyn]{7c}}, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
@@
 The path parameter increases as soon as the algorithm has estimated enough data %(two periods $T$)
-and the computation parameter decreases matching the battery discharge rate. For both cases, scaling factors are derived empirically %, 
+and the computation parameter decreases matching the battery discharge rate. 
+{\color{blue}
+Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
+Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
+45 and 35 for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
+For both cases, scaling factors are derived empirically %, 
 {\color{blue}similarly to $\delta_i$ set to two hundred fifty}, 
@@
 stastny2018nonlinear%,chao2011collision
-}, order $r$ is three (see Fig.~\ref{fig:il-abs}), and the matrices $Q,R,Q_f$ are chosen such that the cost is merely squared control.
-{\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
+}, order $r$ is three% (see Fig.~\ref{fig:il-abs})
+, and %the matrices 
+$Q,R,Q_f$ are chosen such that the cost is %merely 
+squared control. {\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
 %\subsection{Algorithm evaluation}
@@
 %The figure
-{\color{blue} Fig.~\hyperref[fig:stat]{6c}} %further 
-details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
+%{\color{blue} Fig.~\hyperref[fig:stat]{6c}} %further 
+%details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
 % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
-The {\color{blue} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state
-estimate.
+%The {\color{blue} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state
+%estimate.
 %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others.
 It hence approximates the non-periodicity with a linear model.
+
+{\color{blue}
+Additional results are reported~\cite{seewaldphdthesis} utilizing simulation capabilities of the Paparazzi flight controller.
+Data are split into two sets of four flights each, one similar to \hyperref[fig:trajs-dyn-i]{i} and the other to \hyperref[fig:trajs-dyn-ii]{ii}, i.e., initial parameters are at boundary configurations.
+These results have an average performance metric of 1.81 and 1.24 for flights similar to \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-i]{ii} respectively.}
 

### 2022-05-18 review/response-letter.tex
implemented ALL the reviewers comments

@@
   {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations.
-In \hyperref[fig:stat]{a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}.
+In {\color{red}a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}.
 In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
@@
   %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
-  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies{\color{blue}~[{\color{green}33}]}.}
+  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies. {\color{blue}Further details are proposed in the first author's Ph.D. thesis~[{\color{green}31}]}.
+  }
   \vspace*{1ex}
@@
 
-[!]}
+Thank you for noticing the issue.
+We use the predictive layer function $g(\cdot)$ to return the energy of any possible configuration of computation parameters, independently of the time, given a measuring device (i.e., the computing hardware can measure the energy of different components such as overall, CPU, GPU, memory, etc.).
+
+To construct the predictive layer, we utilize a discrete set of measuring layers $\mathbf{g}(\cdot)$, each containing the time in the form of an interval that specifies for how long a given configuration on a measuring device has to be profiled.
+
+The two variables of $g$ are then the configuration and the specific measuring device, indicated by a positive integer value.
+We have not realized there might arise confusion between $\mathbf{g}$ and $g$ and thus decided to use $\gamma$ for the measuring layer instead of $\mathbf{g}$ and add further commentary after the equation.
+
+\begin{formal}
+  \color{black}
+  [...] notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
+{\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~({\color{red}13})}.
+  \vspace*{1ex}
+\end{formal}
+
+}
 
@@
 
-[!]}
+Thank you once again for underlying this point. The assumption was not clearly stated in the manusctipt, and we have thus added additional commentary before the equations.
+
+\begin{formal}\color{black}
+  {\color{blue}W}e assume that the coverage time evolves linearly{ \color{blue}and that the }path parameters{ \color{blue}contribute to it equally.} $c_i^\rho$ can be {\color{blue}then} transformed into a time measure with scaling factors
+  [...]
+  \vspace*{1ex}
+\end{formal}
+}
 
@@
 
-  [!]}
+  Thank you for noticing the comparison was missing in the manuscript.
+We utilize as a performance metric the weighted average configuration of parameters against the battery state of charge at the end of the flight.
+We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.
+
+  \begin{formal}
+    {\color{blue}
+Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, {\color{red}I} would not be able to complete the flight, and {\color{red}II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
+Nonetheless, performance metrics of {\color{red}i} and {\color{red}ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
+45 and 35 for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}
+    \vspace*{1ex}
+  \end{formal}
+  }
 
@@
 
-  [!]}
+  Thank you for this point; we have reduced the number of experimental results due to space constraints.
+Nonetheless, we agree that additional results would further justify the need for planning-scheduling in the aerial robotics domain.
+To this end, we have added the average result for eight flights derived utilizing the flight simulation capabilities of the open-source Paparazzi flight controller.
+These results are derived in two equally sized sets, each similar to flights i and ii in the manuscript.
+The results are described thoroughly in the corresponding author's Ph.D.
+thesis (reference [{\color{green}31}], Section 6.3.2.
+
+  We have altered the numerical simulation section accordingly.
+
+  \begin{formal}
+    {\color{blue}
+    Additional results are reported~[{\color{green}31}] utilizing simulation capabilities of the Paparazzi flight controller.
+Data are split into two sets of four flights each, one similar to {\color{red}i} and the other to {\color{red}ii}, i.e., initial parameters are at boundary configurations.
+    These results have an average performance metric of 1.81 and 1.24 for flights similar to {\color{red}i} and {\color{red}ii} respectively.}
+
+    \vspace*{1ex}
+  \end{formal}
+  }
 
@@
 
-[!]}
+Thank you for underlying this point.
+We have not realized that it was not clear in the original manuscript.
+We use the concept of path parameters as inputs to the path functions that compose the coverage path to ultimately alter the coverage quality dynamically, throughout the flight.
+
+We have added explanatory text to Section IV-A to make this point clear.
+
+\begin{formal}
+  \color{black}
+  [...] It is similar to another motion in the literature, the \emph{Zamboni motion}~[{\color{green}41}], but additionally allows variable CPP %at the very core of this work
+  {\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
+  {\color{blue} Although cover variability is already considered in the literature~[{\color{green}41}], it is limited to boustrophedon motion for rotary wings.}
+  The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~{\color{red}II.5}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.
+[...]% (see Fig.~\ref{fig:zambo}).
+  \vspace*{1ex}
+\end{formal}
+}
 
@@
 
-[!]}
+Thank you for noticing the issue regarding poor clarity. We have altered the figure and added a legend to clarify the meaning of i, ii, and iii as different stages in planning-scheduling.
+
+\begin{formal}
+\color{black}
+  {\color{blue}\scriptsize \input{../figures/il_abs_new_review.tikz}}
+  {\color{black}\footnotesize%Illustrative example of planning-scheduling. 
+  Fig.~1:~The figure shows an initial plan~(in~{\color{red}i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~{\color{red}ii}) and changing the number of fly-bys or other motion aspects~(in~{\color{red}sth:iii}).
+  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
+  the spectrum analysis of the energy data, revealing the periodicity %of the data 
+  exploited in the %overall 
+  energy model.
+  %Follow the collected energy data of a physical aerial robot flying the static coverage.
+  }
+  \vspace*{1ex}
+\end{formal}
+
+}
 
@@
 
-[!]}
+Thank you once again for the commentary as well as for bringing up a lot of important points.
+We are indeed excited about the potential of planning-scheduling for the aerial robotics domain to address autonomy and other criticalities arising in a number of use cases.
+We would like to propose a revised version of the manuscript for your kind consideration, where we incorporate the points and additional experimental results.}
 

### 2022-05-18 energy-planning.tex
implemented ALL the reviewers comments

@@
 \author{
-  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
-  %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
-  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
-  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
+  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
+  \thanks{The work was partly funded by E.U. grant No. 779882 (TeamPlay); H. G. work is supported by Ramon y Cajal grant No. RYC2020-030090-I.}
+  %\thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
+  %\thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
   \thanks{$^{\text{1}}$A.
-S., H.
 S.
-M.,  and U.
-P.
-S.
-are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense.
-Email: {\tt\footnotesize ads@mmmi.sdu.dk};}
-  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Complutense de Madrid, Spain.}
-  \thanks{Digital Object Identifier (DOI): see top of this page.}
+is with the Dept.
+of Mech.
+Eng.
+and Mater.
+Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS.
+Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
+  \thanks{$^{\text{2}}$H. G. is with the Dept. of Comput. Archit. and Technol., University of Granada, Spain;} 
+  \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
+  University of Southern Denmark.}
+  %\thanks{Digital Object Identifier (DOI): see top of this page.}
 }
@@
   \centering
-  \vspace*{-6.8ex}
-  \begin{tikzpicture}
-    \node[inner sep=0pt] () at (0,0)
-        {\scriptsize \input{\figpath/new/il_abs.tikz}};
-    \node[inner sep=0pt] () at (-2,-5.67)
-        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
-    \node[inner sep=0pt] () at (2.1,-5.67)
-        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
-  \end{tikzpicture}
+  \vspace*{-9.8ex}
+ %\begin{tikzpicture}
+ %  \node[inner sep=0pt] () at (0,0)
+        {\color{blue}\scriptsize \input{\figpath/il_abs_new.tikz}}
+ %  \node[inner sep=0pt] () at (-2,-5.67)
+ %      {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
+ %  \node[inner sep=0pt] () at (2.1,-5.67)
+ %      {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
+ %\end{tikzpicture}
   \caption{%Illustrative example of planning-scheduling. 
-  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}).
-  Bottom-left shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here.
-Bottom-right shows a spectrum analysis of the energy data, revealing the periodicity of the data exploited in the overall energy model.
+  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-bys or other motion aspects~(in~\ref{sth:iii}).
+  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
+  the spectrum analysis of the energy data, revealing the periodicity %of the data 
+  exploited in the %overall 
+  energy model.
   %Follow the collected energy data of a physical aerial robot flying the static coverage.
@@
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
-\begin{ctb}
-  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
-\end{ctb}
+%\begin{ctb}
+%  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
+%\end{ctb}
 
@@
 %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
-i.e., $h,y$ are both harmonic signals with the same frequencies{\color{blue}~\cite{seewaldphdthesis}}.
+i.e., $h,y$ are %both 
+harmonic signals with the same frequencies{\color{blue}. Further details are proposed in the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.
 
@@
 
-For ease of notation, we assume that the coverage time evolves linearly.
-Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
+%For ease of notation, 
+{\color{blue}W}e assume that the coverage time evolves linearly{ \color{blue}and that the }path parameters{ \color{blue}contribute to it equally.} $c_i^\rho$ can be {\color{blue}then} transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
   \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
@@
 \begin{defn}[Measurement layer]\label{def:meas}
-  Given a measuring device, computation parameters, and initial and final time instants, the \emph{measurement layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
+  Given a measuring device, computation parameters, and initial and final time instants, the \emph{measurement layer} is the function $\gamma:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
 \end{defn}
@@
 \begin{equation}\label{eq:piece-wise-reg}\begin{split}
-  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
+  g(c_i^\sigma)=(&\gamma(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
 \end{split}\end{equation}
 where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
-The measuring device in both $\mathbf{g}$ and $g$ is implicit.
+{\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~(\ref{eq:piece-wise-reg})}.
 
@@
 To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius.
-It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work.
+It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP %at the very core of this work
+{\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
 {\color{blue} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}

### 2022-05-19 review/response-letter.tex
optimizing space (1)

@@
   \begin{formal}
-    {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.}
+    {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery SoC}.}
     \vspace*{1ex}
@@
 $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
-  constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
-{\color{blue}Indices $j$ and $k$ serves to differentiate path and computation parameters constraints and to indicate that each parameter can have a different constraint set.}
+  constraint set, %and 
+  $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ %is 
+  the $k$th computation parameter constraint set.
+{\color{blue}Indices $j,k$ serves~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
   \vspace*{1ex}
@@
 \begin{formal}
-  {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.}
+  {\color{black} [...] the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery SoC}.}
   \vspace*{1ex}
@@
   The problem %of planning-scheduling 
-is composed of two sub-problems{\color{blue}: }%. One is 
+  is {\color{blue}split into }%composed of 
+  two sub-problems{\color{blue}: }%. One is 
   to form a %static 
   plan that visits every point in space, {\color{blue}and }%the other to
-re-plan and re-schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
+  re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
   {\color{blue} The performance metric the re-planning-scheduling %in the letter 
   improves is %then
-the quality of the plan-schedule against battery SoC, e.g., the weighted average value of parameters divided by remaining %battery 
+  the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
   SoC.% at the end of the flight.
@@
     \vspace*{1ex}
+  \end{formal}
+
+  We have then reorganized the conclusion, underlining the intent to perform physical experiments at future instances.
+
+  \begin{formal}
+  \color{black}
+  {\color{blue}To enable physical experiments}, we are currently extending the results to a standard flight controller.
   \end{formal}
@@
   \color{black} [...] there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
+The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
 [...]

### 2022-05-19 energy-planning.tex
optimizing space (1)

@@
   \centering
-  \vspace*{-9.8ex}
+  \vspace*{-9ex}
  %\begin{tikzpicture}
@@
   \label{fig:il-abs}
-  \vspace*{-4ex}
+  \vspace*{-3.5ex}
 \end{figure}
@@
 Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}.
-Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
+%Indeed
+{\color{blue}T}here are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
+The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
 It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
@@
 {\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
-The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
+The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware% energy modeling
+~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
 hinz2019comparison,mousavi2014various}.
 The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data (bottom-left) and spectrum analysis (right) of a fixed wing %aerial robot
+In Fig.~\ref{fig:il-abs}, collected energy data ({\color{blue}top-right}) and spectrum analysis ({\color{blue}below}) of a fixed wing %aerial robot
 flying CPP motivates the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
-The remaining sections of the letter are then organized as follows.
-Section~\ref{sec:prob} provides basic constructs, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as the problem formulation.
+The %remaining sections of the letter are 
+{\color{blue}remainder is} then organized as follows.
+Section~\ref{sec:prob} provides basic constructs%, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as
+{ \color{blue}and} the problem formulation.
 Section~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
@@
                                %
+%Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries. 
+%For CPP and, e.g., pattern detections in precision agriculture, 
+{\color{blue}W}e assume %that %aerial 
+{\color{blue}the }robot contains a \emph{plan} composed of \emph{stages}. At each, %stage, %the aerial robot 
+{\color{blue}it }travels a path and runs a schedule on the computing hardware. Both are %to be 
+altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computation}-specific \emph{parameters}.%with information about the path and the schedule.
+
 \begin{figure}[t]
   \footnotesize
-  \begin{minipage}[l]{0.35\columnwidth}
+  \begin{minipage}[l]{0.40\columnwidth}
     \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$.
@@
   \end{minipage}\hfill
-  \begin{minipage}[c]{0.6\columnwidth}
+  \begin{minipage}[c]{0.56\columnwidth}
     \centering
-    \vspace*{-4.5ex}
+    \vspace*{-4ex}
     \input{\figpath/new/traj1.tikz}
@@
 \end{figure}
-
-Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries.
-For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot contains a \emph{plan} composed of \emph{stages}.
-At each stage, the aerial robot travels a path and runs a schedule on the computing hardware.
-Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computation}-specific \emph{parameters}.%with information about the path and the schedule.
 
@@
 $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
-  constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
-{\color{blue}Indices $j$ and $k$ serves to differentiate path and computation parameters constraints and to indicate that each parameter can have a different constraint set.}
+  constraint set, %and 
+  $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ %is 
+  the $k$th computation parameter constraint set.
+{\color{blue}Indices $j,k$ serves~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
 \end{defn}
@@
 Bold letters indicate vectors. 
-The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{blue}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of a parameter $x$, i.e.,
-\begin{equation}
-  \underline{x}\leq x\leq\overline{x}.
-\end{equation}
-
-The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
+The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{blue}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of %a parameter
+$x$, i.e.,
+%\begin{equation}
+  $\underline{x}\leq x\leq\overline{x}$.
+%\end{equation}
+
+The function $\varphi_i$ is a \emph{path function}{\color{blue}--a }%specifying the path. These are 
+stage-dependent mathematical function %s 
+the %aerial 
+robot tracks as it travels %the motion for 
 the coverage.
@@
   $} and path parameters $c_i^\rho%(t)
-  $ and are continuous and twice differentiable.
+  $ and are continuous.% and twice differentiable.
 \end{defn}
@@
   The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ describes the transition between stages.
-The \emph{final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
+\emph{Final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
 \end{defn}
@@
 %The constraint set $\mathcal{C}_{4,1}$ forms the area where
-It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$ illustrated by the gray area in the figure.
-%The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
+It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$ --%illustrated by 
+the gray area.% in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
 
@@
   \begin{minipage}[l]{0.75\columnwidth}
-    \vspace*{-2.2ex}
-    \begin{tikzpicture}[shorten >=.5pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-3ex}\footnotesize{$\Gamma_0$}]
+    \vspace*{-2.7ex}
+    \begin{tikzpicture}[shorten >=.3pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-.8ex}\footnotesize{$\Gamma_0$}\hspace*{-.5ex}]
       \scriptsize
@@
   \end{minipage}
-  \vspace*{-3.5ex}
+  \vspace*{-4ex}
 \end{figure}
@@
 
-Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}.
-A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
+Fig.~\ref{fig:state-machine-loop} illustrates the concept. %s in Definition~\ref{def:primitive}. 
+A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (%containing 
+{\color{blue}with }primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
 $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$.
@@
 The problem %of planning-scheduling 
-is composed of two sub-problems{\color{blue}: }%. One is 
+is {\color{blue}split into }%composed of 
+two sub-problems{\color{blue}: }%. One is 
 to form a %static 
 plan that visits every point in space, {\color{blue}and }%the other to
-re-plan and re-schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
+re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
 {\color{blue} The performance metric the re-planning-scheduling %in the letter 
 improves is %then
-the quality of the plan-schedule against battery SoC, e.g., weighted average value of parameters divided by remaining %battery 
+the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
 SoC.% at the end of the flight.
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery state of charge (SoC)}.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery SoC}.
 \end{pb}
@@
 \end{equation}
-where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the series coefficients.
+where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy% consumption
+, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ %the %series 
+coefficients.
 
@@
 For this latter purpose, we use the dynamics %another model
-\begin{subequations}\label{eq:state-perf}\begin{align}
+\begin{subequations}\label{eq:state-perf}
+  \begin{align}
   \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t),\label{eq:state-perf-q}\\
   y(t)&=C\mathbf{q}(t),\label{eq:state-perf-y}
-\end{align}\end{subequations}
+\end{align}
+\end{subequations}
 where $y(t)\in\mathbb{R}$ is the instantaneous energy consumption. The state $\mathbf{q}\in\mathbb{R}^m$ with $m:=2r+1$ contains energy coefficients
@@
 The state transition matrix
-\begin{equation}\label{eq:mat_A}
+\begin{equation}\label{eq:mat_A}{\small
   A=\begin{bmatrix}
@@
     0^{2\times 1}& 0^{2\times 2}& \dots & A_r 
-  \end{bmatrix},\,\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix},
+  \end{bmatrix},\,\,A_j:=\begin{bmatrix}0 & \omega j \\ -\omega j & 0\end{bmatrix}},
 \end{equation}
@@
 
-The output matrix\vspace*{-2ex}
+The output matrix\vspace*{-3ex}
 \begin{equation}\label{eq:mat_C}
@@
 The nominal control and input matrix in Eq.~(\ref{eq:state-perf}) simply includes the change in energy for all time instants, i.e.,
-\begin{equation}\label{eq:mat_B}
+\begin{equation}\label{eq:mat_B}{\small
   \mathbf{u}(t_{j+1})\hspace*{-.5ex}:=\hspace*{-.5ex}\hat{\mathbf{u}}(t_{j+1})\hspace*{-.5ex}-\hspace*{-.5ex}\hat{\mathbf{u}}(t_j),\,\,\,B=\begin{bmatrix}
@@
       0^{1\times\rho} & 0      & \cdots & 0   
-  \end{bmatrix},
+  \end{bmatrix}},
 \end{equation}
@@
 $B\in\mathbb{R}^{m\times n}$ with $n:=\rho+\sigma$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones.
-Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible, as we discuss briefly in Section~\ref{sec:conclusion}.
+Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible %, as we discuss briefly in
+{\color{blue}(see }Section~\ref{sec:conclusion}{\color{blue})}.
 The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
@@
 where $\mathrm{diag}(x)$ is a diagonal matrix with items of a set $x$ on the diagonal and zeros elsewhere.
-$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors that transform parameters domain (see Definition~\ref{def:stage}) to time and power domains.
+$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors{\color{blue},} %that
+transform{\color{blue}ing} parameters %domain 
+(see Definition~\ref{def:stage}) to time and power domains.
 
@@
 Additionally, the \powprof{} tool supports the battery SoC detailed in Section~\ref{sec:mod-bat}.
-The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
+The function $g$ in Definition~\ref{def:pred} is contained in the %computations scaling
+factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
 \begin{equation}\label{eq:piece-wise-reg}\begin{split}
@@
 %\begin{defn}[Output constraint]\label{def:const}
-\begin{equation}\label{eq:output-const}
-  \mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
-\end{equation}
+%\begin{equation}\label{eq:output-const}
+  $\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\}$, 
+%\end{equation}
 %the \emph{output constraint}, 
-where $b\,Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Eq.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
+where $b\,Q_cV$, the maximum instantaneous energy %consumption
+measured in watts, is derived from Eq.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
 %\end{defn}
@@
 An intuitive way to solve the problem is with a back-and-forth motion, sweeping the space delimited by $v$ we term $\mathcal{Q}^v$.
-Although abundant in both mobile ground-based~\cite{choset2001coverage,%choset2005principles,
-lavalle2006planning} and aerial~\cite{araujo2013multiple,%artemenko2016energy,
+Although abundant in both mobile ground-based~\cite{choset2001coverage%,%choset2005principles,
+%lavalle2006planning
+} and aerial~\cite{araujo2013multiple,%artemenko2016energy,
 cabreira2018energy,difranco2015energy} robotics literature, the motion, called \emph{boustrophedon motion}~\cite{choset2001coverage}, is unsuitable for aerial robots broadly, especially for fixed-wing aerial robots.
@@
 
-We assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$.
-Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
-The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$.
-Nonetheless, a complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.
+We assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex %in 
+clockwise% order
+, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$. 
+Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ %per each 
+{\color{blue}at }discretized time step{\color{blue}s}, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected.
+%as it swipes $\mathcal{Q}^{v}$.
+%Nonetheless, a
+{\color{blue}C}omplex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and %subsequently 
+covering each cell~\cite{choset2001coverage}.% with the novel motion.
 
@@
 
-\begin{figure}[t]
-  \footnotesize
-  \begin{minipage}[l]{0.73\columnwidth}
-    \centering
-    \vspace*{-2ex}
-    \input{\figpath/new/traj3.tikz}
-  \end{minipage}\hfill
-  \begin{minipage}[l]{0.25\columnwidth}
-    \caption{Zamboni-like motion: ($\overline{\Gamma}$) with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) with $r_2$ in Eq.~(\ref{eq:r2}).}
-    \label{fig:zambo}
-  \end{minipage}
-  \vspace*{-4.5ex}
-\end{figure}
-
 To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
-\begin{equation}\label{eq:r2}
-  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
-\end{equation}
+%\begin{equation}\label{eq:r2}
+  $r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},$ 
+%\end{equation}
 is expressed as a function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
@@
 
-\vspace*{-1.4ex}
+\begin{figure}[t]
+  \vspace*{-1ex}
+  \footnotesize
+  \begin{minipage}[l]{0.7\columnwidth}
+    \centering
+    \input{\figpath/new/traj3.tikz}
+  \end{minipage}\hfill
+  \begin{minipage}[l]{0.26\columnwidth}
+    \caption{Zamboni-li- ke motion: $\overline{\Gamma}$ with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) {\color{blue}via} $r_2$.% in Eq.~(\ref{eq:r2}).
+    }
+    \label{fig:zambo}
+  \end{minipage}
+  \vspace*{-5ex}
+\end{figure}
+
 \subsection{Re-planning-scheduling}
@@
 We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
-Since the final time instant and the exact value of the state $\mathbf{q}$ are not known, we use %a technique in the literature named
-output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$~\cite{rawlings2017model}.
+Since the final time %instant
+and the %exact 
+value of the state $\mathbf{q}$ are not known, we use %a technique in the literature named 
+output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.%~\cite{rawlings2017model}.
 {\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
@@
 A useful property to guarantee a solution~\citep{beck2014introduction}.
-The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression but with no control~\cite{rawlings2017model}
-\begin{equation}\label{eq:final-cost-mpc}
-  l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T),
-\end{equation}
+The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression %but with no control %~\cite{rawlings2017model}
+%\begin{equation}\label{eq:final-cost-mpc}
+  $l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T)$, 
+%\end{equation}
 where $Q_f\in\mathbb{R}^{m\times m}$ is a given positive semidefinite matrix.
@@
 Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}.
-Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolve the battery model in Eq.~(\ref{eq:batdyn}).
-Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
-(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.
+Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints %in Eq.~(\ref{eq:output-const})
+that evolve the battery model in Eq.~(\ref{eq:batdyn}). Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
+(%the very 
+first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.
 
 Line~\ref{alg:mpc} in Algorithm~\ref{alg} contains a transcribed version of the OCP in Eq.~(\ref{eq:ocp-output-mpc}) into a nonlinear program (NLP) that can be %easily 
-solved with available NLP solvers~\cite{rawlings2017model}.
+solved with available NLP solvers%~\cite{rawlings2017model}
+.
 Its solution leads to both trajectories of {\color{blue} computation} parameters and states for future $N$ instants.
@@
 the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning in $\mathcal{K}$, $\mathcal{T}$ respectively.}
-The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}), with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}
-.
+The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}).%, with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}.
 
@@
 {\color{blue} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Sec.~\ref{sec:experimental})}.
-Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the energy model's state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
+Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the %energy model's 
+state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
 Kalman filter%~\cite{kalman1960new}
@@
 
-\vspace*{-1.5ex}
+\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS.
-The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
+The planner varies the path parameter $c_{i,1}$ in %Eq.~(\ref{eq:r2})
+between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
 The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized
@@
 Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery ({\color{blue}see} green line {\color{blue}in Fig.~\hyperref[fig:dyn]{7c}}, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
-Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ {\color{blue}(see Fig.~\hyperref[fig:dyn]{7b})} when the battery is discharging, respecting the output constraint (Eq.~(\ref{eq:output-const})).
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ {\color{blue}(see Fig.~\hyperref[fig:dyn]{7b})} when the battery is discharging, respecting the output constraint% (Eq.~(\ref{eq:output-const}))
+.
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario: the lowest configuration of parameters and no battery defects.
@@
                                              %
-This letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature.
+This letter provides a planning-scheduling approach for autonomous aerial robots.% powered by a limited power source, extending past literature.
 It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
 Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool.
-The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC.
+The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC {\color{blue} and a greedy approach}.
 It evolves the state of the energy model while optimizing battery usage and remedying possible defects.
@@
 
-Indeed, we are currently extending the results to a standard flight controller to enable physical experiments.
-The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections),
-and distributed planning-scheduling merit additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots.
+{\color{blue}To enable physical experiments}, we are currently extending the results to a standard flight controller.
+%The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections),
+%and distributed planning-scheduling merit additional investigation, as well as 
+The study of the implications of planning-scheduling on other energy-critical mobile robots {\color{blue}merit additional investigation}.
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.
-Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.% Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
 

### 2022-05-19 review/response-letter.tex
optimizing space (2)

@@
   %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
-  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies. {\color{blue}Further details are proposed in the first author's Ph.D. thesis~[{\color{green}31}]}.
+  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies. {\color{blue}Further details see the first author's Ph.D. thesis~[{\color{green}31}]}.
   }
@@
   {\color{black}\footnotesize%Illustrative example of planning-scheduling. 
-  Fig.~1:~The figure shows an initial plan~(in~{\color{red}i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~{\color{red}ii}) and changing the number of fly-bys or other motion aspects~(in~{\color{red}sth:iii}).
-  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
-  the spectrum analysis of the energy data, revealing the periodicity %of the data 
+  Fig.~1:~An initial plan~(in~{\color{red}i}) {\color{blue}is} re-planned online, changing the %resolution, 
+  detection rate or other computational aspects~(in~{\color{red}ii}) and %changing 
+  the number of fly-bys or other motion aspects~(in~{\color{red}iii}). 
+  {\color{blue}Top-right} %shows 
+  {\color{blue}are} the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
+  the spectrum analysis, %of the %energy 
+  %data, 
+  revealing the periodicity %of the data 
   exploited in the %overall 

### 2022-05-19 energy-planning.tex
optimizing space (2)

@@
 \begin{document}
+\bstctlcite{IEEEexample:BSTcontrol}
 
@@
   Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
-  \thanks{The work was partly funded by E.U. grant No. 779882 (TeamPlay); H. G. work is supported by Ramon y Cajal grant No. RYC2020-030090-I.}
-  %\thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
-  %\thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
+  \thanks{The work was partly funded by EU grant No. 779882 (TeamPlay). The work for H. G. is supported by the Ramon y Cajal grant No. RYC2020-030090-I.}
+  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
+  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
   \thanks{$^{\text{1}}$A.
 S.
-is with the Dept.
-of Mech.
-Eng.
-and Mater.
-Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS.
+is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS.
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
-  \thanks{$^{\text{2}}$H. G. is with the Dept. of Comput. Archit. and Technol., University of Granada, Spain;} 
+  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology, University of Granada, Spain;} 
   \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
   University of Southern Denmark.}
-  %\thanks{Digital Object Identifier (DOI): see top of this page.}
+  \thanks{Digital Object Identifier (DOI): see top of this page.}
 }
@@
 
-\vspace*{-4.6ex}
+\vspace*{-5ex}
 
@@
 
+\vspace*{-.5ex}
 \begin{IEEEkeywords}
@@
 
+\vspace*{-2.6ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{%Illustrative example of planning-scheduling. 
-  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-bys or other motion aspects~(in~\ref{sth:iii}).
-  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
-  the spectrum analysis of the energy data, revealing the periodicity %of the data 
+  %The figure shows 
+  An initial plan~(in~\ref{sth:i}) {\color{blue}is} re-planned online, changing the %resolution, 
+  detection rate or other computational aspects~(in~\ref{sth:ii}) and %changing 
+  the number of fly-bys or other motion aspects~(in~\ref{sth:iii}). 
+  {\color{blue}Top-right} %shows 
+  {\color{blue}are} the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
+  the spectrum analysis, %of the %energy 
+  %data, 
+  revealing the periodicity %of the data 
   exploited in the %overall 
@@
   \label{fig:il-abs}
-  \vspace*{-3.5ex}
+  \vspace*{-4ex}
 \end{figure}
@@
 Section~\ref{sec:prob} provides basic constructs%, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as
-{ \color{blue}and} the problem formulation.
-Section~\ref{sec:algo} describes in detail the methodology of planning-scheduling.
-Section~\ref{sec:experimental} presents the results, %and showcases the performances,
+{ \color{blue}and} %the problem formulation.
+Section~\ref{sec:algo} describes %in detail 
+the methodology of planning-scheduling. Section~\ref{sec:experimental} presents the results, %and showcases the performances, 
 and Section~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
@@
   \footnotesize
-  \begin{minipage}[l]{0.40\columnwidth}
+  \begin{minipage}[l]{0.38\columnwidth}
     \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$.
@@
   \end{minipage}\hfill
-  \begin{minipage}[c]{0.56\columnwidth}
+  \begin{minipage}[c]{0.6\columnwidth}
     \centering
@@
   \end{minipage}\hfill
-  \begin{minipage}[c]{0.2\columnwidth}
+  \begin{minipage}[c]{0.18\columnwidth}
     \centering
@@
 i.e., $h,y$ are %both 
-harmonic signals with the same frequencies{\color{blue}. Further details are proposed in the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.
+harmonic signals with the same frequencies{\color{blue}. For further details see the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.
 
@@
 
-The battery model predicts the battery SoC in the function of a given load at future time instants.
-There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{%moura2017battery,
+The battery model predicts the battery SoC in the function of a given load at future time 
+instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{blue}and} accuracy %, and ease of implementation 
+ranging from accurate but costly physical models~\cite{%moura2017battery,
 marcicki2013design}, to abstract models~\cite{%xing2014state,
 %he2011evaluation,
-hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two. 
-We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' ECM in the literature~\cite{%he2011evaluation,
+hinz2019comparison,mousavi2014various} %that have
+{\color{blue}with} compelling trade-offs in terms of the latter two. 
+We model a Li-ion battery %of an aerial robot 
+in-flight with an abstract ``Rint'' ECM in the literature~\cite{%he2011evaluation,
 hinz2019comparison,mousavi2014various}.
@@
 
-If the voltage of the power drain is stable, Kirchhoff's circuit laws lead to $V_sI_l=V_eI$, where $I_l$ is the current required by the load measured in amperes.
-Combining $V_e,V_sI_l$ results in the quadratic expression $R_rI^2-VI+V_sI_l=0$.
-Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) %leads to%
+If the voltage %of the power drain 
+is stable, Kirchhoff's circuit laws lead to $V_sI_l=V_eI$, where $I_l$ is the current required by the load %measured 
+in amperes. Combining $V_e,V_sI_l$ results in the %quadratic 
+expression $R_rI^2-$ $VI+V_sI_l=0$. Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) %leads to% 
 results in 
@@
 %\begin{defn}[Output constraint]\label{def:const}
-%\begin{equation}\label{eq:output-const}
-  $\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\}$, 
-%\end{equation}
+\begin{equation}\label{eq:output-const}
+  {\small\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},} 
+\end{equation}
 %the \emph{output constraint}, 
@@
   \footnotesize
-  \begin{minipage}[l]{0.25\columnwidth}
+  \begin{minipage}[l]{0.21\columnwidth}
     \caption{Alteration of the path parameter $c_{i,1}$, the radius of the circle (i.e., the alteration of the plan in Fig.~\ref{fig:il-abs}).
@@
   \end{minipage}\hfill
-  \begin{minipage}[c]{0.7\columnwidth}
+  \begin{minipage}[c]{0.77\columnwidth}
     \centering
@@
 
-      \vspace*{.8ex}
+      %\vspace*{.8ex}
       \color{blue}\IF{$\mathbf{p}%(t)
@@
 To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
-%\begin{equation}\label{eq:r2}
-  $r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},$ 
-%\end{equation}
+\vspace*{-1ex}
+\begin{equation}\label{eq:r2}
+  {\small r_2(c_{i,1}):=\sqrt{\smash[b]{r^2+c_{i,1}}},}
+  \vspace*{-.4ex}
+\end{equation}
 is expressed as a function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.

### 2022-05-20 review/response-letter.tex
proofreading

@@
 We have thus decided to utilize a hybrid approach.
-We employ MPC for the schedule (computation parameters $c_i^\sigma$) and a greedy approach for the coverage (path parameters $c_i^\rho$).
-Similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}19}] in the revised manuscript).
+We employ MPC for the schedule (computation parameters $c_i^\sigma$) and a heuristics-based greedy approach for the coverage (path parameters $c_i^\rho$).
+Similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).
 Nonetheless, as underlined in your observation, this was not clear from the text. We have updated the algorithm in Line 16.
@@
 
-  We have altered the introduction and the problem formulation in Section II to address the observation.
-We have further added an explanatory text in Section IV.B as well as in the conclusion.
+  We have altered the introduction and the problem formulation in Section II to address the observation, and further added an explanatory text in Section IV.B as well as in the conclusion.
 In the introduction we have stated explicitly that we utilize both the heuristics and optimal control.
@@
   \begin{formal}
-  {\color{black} [...] our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds [...]} Hybrid approaches~[{\color{green}18}] are also available, where the techniques are mixed.
+  {\color{black} [...] our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds [...]} Hybrid approaches~[{\color{green}17}] are also available, where the techniques are mixed.
   \vspace*{1ex}
@@
   Past literature on planning-scheduling often relies on %optimal control and 
-  optimization {\color{blue} as well as heuristics-}related approaches~[{\color{green}13}],~[{\color{green}14}],~[{\color{green}19}],~[{\color{green}23}].
+  optimization {\color{blue} as well as heuristics-based} approaches~[{\color{green}11}],~[{\color{green}12}],~[{\color{green}17}],~[{\color{green}21}].
 We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters [...] {\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
@@
 
-  Line~{\color{red}16} in Algorithm~{\color{red}2} contains [...] a nonlinear program (NLP) that can be solved with available NLP solvers~[{\color{green}47}].
+  Line~{\color{red}16} in Algorithm~{\color{red}2} contains [...] a nonlinear program (NLP) that can be solved with available NLP solvers.
 Its solution leads to both trajectories of {\color{blue} computation} parameters and states [...]
@@
   Lines~{\color{red}17}--{\color{red}23} estimate the time [...] to [...] drain the battery, [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned accordingly on Lines~{\color{red}24}--{\color{red}26} using {\color{blue} the heuristics with the} %Lem.~\ref{lem:new} and
-  scaling factors from Eq.~({\color{red}11}) [...]
+  scaling factors from Eq.~({\color{red}10}) [...]
 
@@
   \color{black}
-  Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.
+  [...] Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.
   \vspace*{1ex}
@@
 Thank you for the concern regarding the readability of the figure.
-We have split the figure to address the concern into two Figures, 6 and 7.
-Subfigures that are related are then on a separate row, each for one case.
+We have split the figure into two figures, 6 and 7.
+Sub-figures that are related are then on a separate row, each for one case.
 I,II in Figure 6 are related to CPP at boundary values of path parameters and varying atmospheric conditions, and i,ii Figure 7 are related to planning-scheduling of I,II with varying battery conditions.
@@
 In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
-In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}
+In {\color{red}c} are the states of the energy model for {\color{red}I}.}
 
@@
 
-Thank you for noting the issue as well as for suggesting more discussion. The former is a typo, and we have fixed the if statement in Algorithm 2.
+Thank you for noticing the issue as well as for suggesting more discussion. The former is a typo, and we have fixed the if statement in Algorithm 2.
 
@@
   \begin{formal}
-    \color{black} [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned [...] on Lines~{\color{red}24}--{\color{red}26} [...] {\color{blue}Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~{\color{red}2} but implemented in Sec.~{\color{red}V})}.
+    \color{black} [...] The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned [...] on Lines~{\color{red}24}--{\color{red}26} [...] {\color{blue}Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~{\color{red}2} but implemented in Section~{\color{red}V})}.
     \vspace*{1ex}
@@
 Both studies do not account for the energy contribution of the computations but interestingly propose the variability of the cover by changing the distance of the survey lines in the boustrophedon motion.
-Whilst similar to our Zamboni-like motion, the cover variability is not achieved in flight nor applies to constrained aerial robots such as fixed wings--which we consider due to a narrower computation-motion energy difference--but rather rotary wings (they utilize boustrophedon motion).
+Whilst similar to our Zamboni-like motion, the cover variability is not achieved in flight nor applies to constrained aerial robots such as fixed wings--which we consider due to a narrower computation-motion energy difference--but rather rotary wings.
 
@@
 \begin{formal}
-  \color{black} [...] {\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution [{\color{green}25}], and deals with aspects such as the quality of the cover [{\color{green}26}], but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots [...]
+  \color{black} [...] {\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution [{\color{green}23}], and deals with aspects such as the quality of the cover [{\color{green}24}], but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots [...]
   \vspace*{1ex}
@@
   \color{black} [...] this section details a [...] motion with a wide turning radius. It is similar to another motion in the literature, the Zamboni
-  motion [{\color{green}42}], but additionally allows variable CPP [...] {\color{blue} Although cover variability is already considered in the literature [{\color{green}25}], it is limited to boustrophedon motion for rotary wings.} The novel motion is termed Zamboni-like motion [...]
+  motion [{\color{green}40}], but additionally allows variable CPP [...] {\color{blue} Although cover variability is already considered in the literature [{\color{green}23}], it is limited to boustrophedon motion for rotary wings.} The novel motion is termed Zamboni-like motion [...]
   \vspace*{1ex}
@@
 
-Thank you for underlying this issue regarding the definition of stage.
+Thank you for underlying the issue regarding the definition of stage.
 We are using the indices $j$ and $k$ to indicate that there might be a different constraint per each parameter and the numbers of parameters $\rho$ and $\sigma$ to indicate that there might be a different number of parameters.
@@
   $} and path parameters $c_i^\rho%(t)
-  $ and are continuous and twice differentiable.
+  $ and are continuous.
   \vspace*{1ex}
@@
 
-We have elaborated further in Section III-A to reflect the observation and added a reference to the corresponding author's previous work.
+We have elaborated further in Section III-A to reflect the observation and added a reference to the corresponding author's Ph.D. thesis (reference [{\color{green}31}], Section 4.3.1).
 
@@
   [...] {\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
-  models in Eqs.~({\color{red}3}--{\color{red}4}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
+  models in Eqs.~({\color{red}2}--{\color{red}3}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
   and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$}}
-    {\color{blue}\begin{equation}\tag{9}
+    {\color{blue}\begin{equation}\tag{8}
     {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
@@
 Practically, we use a step of one for $\mathcal{T}$, running the re-planning every second, and an integration step of 1/100 fraction of a second, since we express $t_f$ and $N$ both in seconds.
-We find the parameters so that the re-planning is feasible in real-time and that the numerical simulation does not diverge.
+We find the parameters so that the re-planning is feasible in real-time and so that the numerical simulation does not diverge.
 
@@
   \color{black} [...] Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{blue}: 
-  the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning in $\mathcal{K}$, $\mathcal{T}$ respectively.}
+  the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning for $\mathcal{K}$ and $\mathcal{T}$ respectively.}
   \vspace*{1ex}
@@
 \begin{formal}
-  \color{black} [...] {\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
+  \color{black} [...] {\color{blue} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
   \vspace*{1ex}
@@
   [...] notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
-{\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~({\color{red}13})}.
+{\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~({\color{red}12})}.
   \vspace*{1ex}
@@
 We would like to thank the second referee, especially for the summary of our work and the kind commentary on the relevance and difficulty of accounting for both motion and computations energies in planning for aerial robots.
-Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots broadly.
-To that end, we are excited to comment on and alter the manuscript as necessary, as the second referee brings up a lot of great points.
+Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots.
+We are thus excited to comment on and alter the manuscript as necessary, as the second referee brings up a lot of great points.
 
@@
 Thank you for the high-level comment and for proposing to state clearly the objective function.
-Regarding the objective function, we have integrated the problem definition accordingly, whereas we have altered the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further explanatory commentary.
+Regarding the objective function, we have integrated the problem definition accordingly, whereas we have altered the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further commentary.
 
@@
   Thank you for underlying the need to state clearly what the computations parameters refer to.
-We have not realized this point was not stated explicitly in the original version earlier than in the experimental setup.
+We have not realized this point was not stated explicitly earlier than in the experimental setup.
 Our purpose is to alter the granularity at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.
@@
 Nonetheless, performance metrics of {\color{red}i} and {\color{red}ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
-45 and 35 for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}
+45 and 35 percent for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}
     \vspace*{1ex}
@@
 
-Thank you for suggesting adding a clear indication of what performance metrics are being utilized.
+Thank you for suggesting adding a clear indication of what performance metric is being utilized.
 Indeed this information was missing in the original manuscript.
@@
 is {\color{blue}split into }%composed of 
-  two sub-problems{\color{blue}: }%. One is 
+two%sub-problems.
+{\color{blue}: }%. One is 
 to form a %static 
-  plan that visits every point in space, {\color{blue}and }%the other to
+plan that visits every point in space {\color{blue}and }%the other to
 re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
-  {\color{blue} The performance metric the re-planning-scheduling %in the letter 
-  improves is %then
-  the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
-  SoC.% at the end of the flight.
-\vspace*{1ex}
-}
+{\color{blue} 
+The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
+%The performance metric the re-planning-scheduling %in the letter 
+%improves is %then
+%the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
+%SoC.% at the end of the flight.
+}
+\vspace*{1ex}
 \end{formal}
@@
 The results are described thoroughly in the corresponding author's Ph.D.
-thesis (reference [{\color{green}31}], Section 6.3.2.
+thesis (reference [{\color{green}31}], Section 6.3.2).
 
@@
   \color{black}
-  [...] It is similar to another motion in the literature, the \emph{Zamboni motion}~[{\color{green}41}], but additionally allows variable CPP %at the very core of this work
+  [...] It is similar to another motion in the literature, the \emph{Zamboni motion}~[{\color{green}40}], but additionally allows variable CPP %at the very core of this work
   {\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
-  {\color{blue} Although cover variability is already considered in the literature~[{\color{green}41}], it is limited to boustrophedon motion for rotary wings.}
+  {\color{blue} Although cover variability is already considered in the literature~[{\color{green}23}], it is limited to boustrophedon motion for rotary wings.}
   The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~{\color{red}II.5}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.
@@
 \begin{formal}
-  \color{black} [...] there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
+  \color{black} [...] There are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
 The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
@@
 We have reordered Figure 6 to address the issue.
-We have first split the figure into two Figures, 6 and 7.
+We have first split the figure into two figures, 6 and 7.
 In both, we utilize one row per case.
@@
 In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
-In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}
+In {\color{red}c} are the states of the energy model for {\color{red}I}.}
 \end{formal}

### 2022-05-20 energy-planning.tex
proofreading

@@
 We further derive a novel variable coverage motion robust to airborne constraints and an empirically motivated energy model.
-The model includes the energy contributions of the schedule based on an automatic computational energy modeling tool.
+The model includes the energy contribution of the schedule based on an automatic computational energy modeling tool.
 Our experiments show how an initial flight plan is adjusted online as a function of the available battery, accounting for uncertainty.
@@
 %with little human interaction.
-Such use cases arise in%, e.g., 
+Such use cases arise in %, e.g., 
 precision agriculture~\cite{hajjaj2014review} 
@@
 $\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens change of stages $\Gamma_i$.
-Each contains a path function $\varphi_i$ and $j$ parameters to alter the path and schedule $c_{i,1},\dots,c_{i,j}$.}
+Each contains a path function $\varphi_i$ and parameters to alter the path and schedule $c_{i,1},\dots$.}
     \label{fig:traj1}
@@
 %The constraint set $\mathcal{C}_{4,1}$ forms the area where
-It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$ --%illustrated by 
+It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$--%illustrated by 
 the gray area.% in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.
@@
     \centering
-    \caption{Plan $\Gamma$ with $n$ primitive stages  in Def~\ref{def:primitive}.}
+    \caption{Plan $\Gamma$ with $n$ primitive stages in Def.~\ref{def:primitive}.}
     \label{fig:state-machine-loop}
@@
 is {\color{blue}split into }%composed of 
-two sub-problems{\color{blue}: }%. One is 
+two%sub-problems.
+{\color{blue}: }%. One is 
 to form a %static 
-plan that visits every point in space, {\color{blue}and }%the other to
+plan that visits every point in space {\color{blue}and }%the other to
 re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
-{\color{blue} The performance metric the re-planning-scheduling %in the letter 
-improves is %then
-the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
-SoC.% at the end of the flight.
+{\color{blue} 
+The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
+%The performance metric the re-planning-scheduling %in the letter 
+%improves is %then
+%the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
+%SoC.% at the end of the flight.
 }
@@
 Past literature on planning-scheduling often relies on %optimal control and 
-optimization {\color{blue} as well as heuristics-}related approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
+optimization {\color{blue} as well as heuristics-based} approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
 We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
@@
 where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial cost function with the quadratic expression
+\vspace*{-.5ex}
 \begin{equation}\label{eq:insta-cost-mpc}
   l(\mathbf{q}(t),c_i(t),t)=\mathbf{q}'(t)Q\mathbf{q}(t)+c_i'(t)Rc_i(t),
+  \vspace*{-.5ex}
 \end{equation}
@@
 The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression %but with no control %~\cite{rawlings2017model}
-%\begin{equation}\label{eq:final-cost-mpc}
-  $l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T)$, 
-%\end{equation}
+\vspace*{-.5ex}
+\begin{equation}\label{eq:final-cost-mpc}
+  l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T), 
+  \vspace*{-.5ex}
+\end{equation}
 where $Q_f\in\mathbb{R}^{m\times m}$ is a given positive semidefinite matrix.
 
-Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}).
-The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., the time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
+Eq.~(\ref{eq:dyn-evol}) is the model in Eq.~(\ref{eq:state-perf}). {\color{blue}It} requires a value of the period $T$, which is %simply 
+the time needed to fly the four primitive paths in the Zamboni-like motion{\color{blue}, or }%, i.e., 
+the time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
 
@@
 Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{blue}:
-the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning in $\mathcal{K}$, $\mathcal{T}$ respectively.}
+the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning for $\mathcal{K}$ and $\mathcal{T}$ respectively.}
 The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}).%, with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}.
@@
 scaling factors from Eq.~(\ref{eq:scale-traj}). 
-{\color{blue} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Sec.~\ref{sec:experimental})}.
+{\color{blue} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Section~\ref{sec:experimental})}.
 Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the %energy model's 
-state with current energy sensor reading $\Upsilon$, with, e.g., %linear 
+state with %current 
+energy sensor reading $\Upsilon$, {\color{blue}using}, e.g., %linear 
 Kalman filter%~\cite{kalman1960new}
@@
 In \hyperref[fig:stat]{b} are the energy and the period evolutions for both \hyperref[fig:trajs-I-static]{I} and \hyperref[fig:trajs-II-static]{II} with different atmospheric conditions.
-In \hyperref[fig:stat]{c} are the states that compose the energy model for \hyperref[fig:trajs-I-static]{I}.}
+In \hyperref[fig:stat]{c} are the states of the energy model for \hyperref[fig:trajs-I-static]{I}.}
   \label{fig:stat}
@@
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS.
-The planner varies the path parameter $c_{i,1}$ in %Eq.~(\ref{eq:r2})
+The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2})
 between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
@@
 Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
-45 and 35 for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
+45 and 35 percent for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
 For both cases, scaling factors are derived empirically %, 
@@
 $Q,R,Q_f$ are chosen such that the cost is %merely 
-squared control. {\color{blue} $h$ is set to one-hundredth of a second and to one second in $\mathcal{K}, \mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
+squared control. {\color{blue} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
 %\subsection{Algorithm evaluation}

### 2022-05-20 review/response-letter.tex
updated w/ Hector's comments

@@
 
-The response letter is split into two sections, each for one review.
+The response letter is split into three sections, the first two for each review and the third for the editor's report.
 The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version.
@@
 
-In this work, we choose to leverage planning-scheduling to aerial robotics, as we believe this is a relevant application and advantageous system for our devised approach.
-We are thus excited to see the referee sharing similar findings while bringing up numerous important points.}
+%In this work, we choose to leverage planning-scheduling to aerial robotics, as we believe this is a relevant application and advantageous system for our devised approach.
+We are thus excited to see the referee sharing similar findings while bringing up numerous important points.
+}
 
@@
 Thank you for the comment as well as for proposing a way to address the issue.
-It is correct that in Lines 24--27 we re-plan solely $c_i^\rho$, i.e., the parameters related to the path.
-The remaining parameters $c_i^\sigma$ related to the computations are then re-planned utilizing the model predictive controller (MPC) in Line 16.
-The reason why we do not use MPC to plan both the parameters is due to the practical feasibility of re-planning in flight, %While an initial version of the algorithm optimized both via MPC, to assess the satisfaction of the battery constraint w.r.t.
-the path parameters, in the worst case, we would have to increase the MPC horizon up to the end of the flight.
-and due to the different effects of the computation and path parameters on the energy consumption.
-While the computation parameters have an immediate effect, i.e., they affect the instantaneous energy consumption, the path parameters affect the flight time and thus the overall energy consumption.
-Concretely and by assumption, a change in the computations alters the schedule, hence the power drained by the computing hardware on the aerial robot, whereas a change in the path parameters alters the time when the aerial robot terminates the coverage.
+We do not use the model predictive controller (MPC) to plan both the parameters due to the practical feasibility of re-planning in flight and the different effects of the computation and path parameters on the energy consumption.
+The computation parameters have an immediate effect, i.e., they affect instantaneous energy consumption, whereas the path parameters affect the flight time, i.e., they affect the overall energy consumption.
+Concretely and by assumption, a change in the computations alters the schedule, and therefore the drained power by the computing hardware on the aerial robot, whereas a change in the path parameters alters the time when the aerial robot terminates the coverage.
 
 We have thus decided to utilize a hybrid approach.
-We employ MPC for the schedule (computation parameters $c_i^\sigma$) and a heuristics-based greedy approach for the coverage (path parameters $c_i^\rho$).
-Similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).
-Nonetheless, as underlined in your observation, this was not clear from the text. We have updated the algorithm in Line 16.
+We employ MPC for the schedule (computation parameters $c_i^\sigma$) in Line 16 and a heuristics-based greedy approach for the coverage (path parameters $c_i^\rho$) in Lines 24–27.
+A similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).
+
+We have updated the algorithm in Line 16, reflecting the observation as this was not in the original manuscript.
 
@@
 
-  We have altered the introduction and the problem formulation in Section II to address the observation, and further added an explanatory text in Section IV.B as well as in the conclusion.
+  We have updated the introduction and the problem formulation in Section II to address the observation, and further added an explanatory text in Section IV.B as well as in the conclusion.
 In the introduction we have stated explicitly that we utilize both the heuristics and optimal control.
@@
 
-  We have altered the problem formulation, clearly stating that the objective is to find energy-aware trajectory of parameters rather than optimal.
+  We have updated the problem formulation, clearly stating that the objective is to find energy-aware trajectory of parameters rather than optimal.
 
@@
 
-  We have then altered Section IV.B.
+  We have then updated Section IV.B.
 
@@
 
-  Finally, we have altered the conclusion.
+  Finally, we have updated the conclusion.
 
@@
 In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions.
-In {\color{red}c} are the states of the energy model for {\color{red}I}.}
-
+In {\color{red}c} are the states of the energy model for {\color{red}I}.
+  \vspace*{1ex}
+  }
+\end{formal}
+\begin{formal}
+  \footnotesize
   \input{../figures/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
@@
 
-Thank you for proposing Di Franco and Buttazzo's past work to our attention.
+Thank you for bringing Di Franco and Buttazzo's past work to our attention.
 We have considered another past study by the authors ``Energy-aware coverage path planning of UAVs'' from 2015, and the proposed work appears to be an extension.
-Both studies do not account for the energy contribution of the computations but interestingly propose the variability of the cover by changing the distance of the survey lines in the boustrophedon motion.
+%Both studies do not account for the energy contribution of the computations but interestingly propose the variability of the cover by changing the distance of the survey lines in the boustrophedon motion.
 Whilst similar to our Zamboni-like motion, the cover variability is not achieved in flight nor applies to constrained aerial robots such as fixed wings--which we consider due to a narrower computation-motion energy difference--but rather rotary wings.
@@
 
-We have altered the definition for this purpose.
+We have updated the definition for this purpose.
 
@@
 We have not realized this possible source of additional confusion and decided to utilize only $\mathbf{p}$ to designate a point.
-We have altered the occurrence in the remainder of the work, for consistency.
+We have updated the occurrence in the remainder of the work, for consistency.
 Apart from Definition II.1 that we showed in point 7, the occurrence was in the definition of path functions.
@@
 Thank you for noticing that a citation and clarification are missing regarding the energy models.
-The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}3}) and Equation ({\color{red}4}) are equal under some conditions (the value of the initial guess is described by Equation ({\color{red}9}) and the model is not perturbed by the control).
+The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}2}) and Equation ({\color{red}3}) match under some conditions (the value of the initial guess is described by Equation ({\color{red}8}) and the model is not perturbed by the control).
+
+$A$ is then a skew-symmetric matrix that contains sub-matrices $A_j$ utilized for the periodic behavior with the frequencies $\omega:=2\pi/T$ ($T$ is the period).
+Each frequency is multiplied by $j$ from one up to the order $r$, where $j$ is the index of the sub-matrix, i.e., there are $r$ frequencies modeling the periodicity one the base frequency.
 
@@
 We would like to thank the second referee, especially for the summary of our work and the kind commentary on the relevance and difficulty of accounting for both motion and computations energies in planning for aerial robots.
-Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots.
+%Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots.
 We are thus excited to comment on and alter the manuscript as necessary, as the second referee brings up a lot of great points.
@@
 
-Thank you for proposing Di Franco and Buttazzo's past study to our attention.
+Thank you for bringing Di Franco and Buttazzo's past study to our attention.
 We have considered the work in the original manuscript in terms of the coverage algorithm in Section IV-A, utilizing it as a reference for aerial coverage.
@@
 Thank you for the high-level comment and for proposing to state clearly the objective function.
-Regarding the objective function, we have integrated the problem definition accordingly, whereas we have altered the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further commentary.
+Regarding the objective function, we have integrated the problem definition accordingly, whereas we have improved the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further commentary.
 
@@
 We have not realized this point was not stated explicitly earlier than in the experimental setup.
-Our purpose is to alter the granularity at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.
+Our purpose is to alter the granularity (specific examples are provided below) at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.
 
@@
   Thank you for noticing the comparison was missing in the manuscript.
-We utilize as a performance metric the weighted average configuration of parameters against the battery state of charge at the end of the flight.
+We utilize as a performance metric the weighted average configuration of parameters divided by the battery state of charge at the end of the flight, meaning the higher the average value of parameters and the lowest the battery state of charge the better (all the resources are being utilized).
 We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.
 
-  \begin{formal}
+  \begin{formal}\color{black}[...] 
     {\color{blue}
@@
 \begin{formal}\color{black}
+
   The problem %of planning-scheduling 
   is {\color{blue}split into }%composed of 
-two%sub-problems.
-{\color{blue}: }%. One is 
-to form a %static 
-plan that visits every point in space {\color{blue}and }%the other to
-re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
-{\color{blue} 
-The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
+  %two%sub-problems.
+  {\color{blue}the derivation }%. One is 
+  %to form a %static 
+  {\color{blue} of} a {\color{blue}coverage} plan %that visits every point in space 
+  {\color{blue}and its} {\color{blue}energy-aware} %other to
+  re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
+  in-flight. %in an energy-aware way. %{\color{blue}, whereas }
+  {\color{blue} 
+  The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
+  the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
   %The performance metric the re-planning-scheduling %in the letter 
@@
 Nonetheless, we agree that additional results would further justify the need for planning-scheduling in the aerial robotics domain.
-To this end, we have added the average result for eight flights derived utilizing the flight simulation capabilities of the open-source Paparazzi flight controller.
+To this end, we have added the average result for eight flights derived utilizing the flight simulation capabilities of the open-source Paparazzi flight control software for autonomous aerial vehicles.
 These results are derived in two equally sized sets, each similar to flights i and ii in the manuscript.
@@
 
-  We have altered the numerical simulation section accordingly.
+  We have updated the numerical simulation section accordingly.
 
@@
   {\color{blue}To enable physical experiments}, we are currently extending the results to a standard flight controller.
+  \vspace*{-.8ex}
   \end{formal}
@@
 
-Thank you for noticing the issue regarding poor clarity. We have altered the figure and added a legend to clarify the meaning of i, ii, and iii as different stages in planning-scheduling.
+Thank you for noticing the issue regarding poor clarity. We have updated the figure and added a legend to clarify the meaning of i, ii, and iii as different stages in planning-scheduling.
 
@@
 In {\color{red}c} are the states of the energy model for {\color{red}I}.}
+  \vspace*{1ex}
 \end{formal}
@@
 We are indeed excited about the potential of planning-scheduling for the aerial robotics domain to address autonomy and other criticalities arising in a number of use cases.
-We would like to propose a revised version of the manuscript for your kind consideration, where we incorporate the points and additional experimental results.}
+We hope our updates according to the suggestions and comments have helped to improve the technical insights of our work.
+%We would like to propose a revised version of the manuscript for your kind consideration, where we incorporate the points and additional experimental results.}
+}
 
@@
 
+\newpage
+
+{Associate Editor}
+
+\vspace{3em}
+
+{\hspace*{-4.5em}\textbf{[AE]}\vspace*{-1.9em}}
+
+This paper received two quality reviews.
+Both reviewers have a favorable impression of the work with specific suggestions for improvement.
+The authors should take care to address the concerns of the reviewers in a revised version.
+Both reviewers specifically mention a related work that should be cited, as well as specific concerns to improve the clarity of the technical contribution of the work.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[AE]}\vspace*{-1.9em}}
+
+We thank the editor for handling our manuscript on planning-scheduling for the aerial robotics domain and the summary of the main concerns from the two reviews. 
+We have incorporated all of the points proposed to strengthen and improve our contribution, making numerous modifications to the manuscript.
+Regarding the related work, we have updated the manuscript to include detailed commentary on how our approach differs.
+
+We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and are excited to bring the revision version for your kind consideration.
+}
+
 \end{document}

### 2022-05-20 energy-planning.tex
updated w/ Hector's comments

@@
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
-  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology, University of Granada, Spain;} 
+  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
   \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
@@
 is {\color{blue}split into }%composed of 
-two%sub-problems.
-{\color{blue}: }%. One is 
-to form a %static 
-plan that visits every point in space {\color{blue}and }%the other to
-re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
+%two%sub-problems.
+{\color{blue}the derivation }%. One is 
+%to form a %static 
+{\color{blue} of} a {\color{blue}coverage} plan %that visits every point in space 
+{\color{blue}and its} {\color{blue}energy-aware} %other to
+re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
+in-flight. %in an energy-aware way. %{\color{blue}, whereas }
 {\color{blue} 
-The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
+The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
+the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
 %The performance metric the re-planning-scheduling %in the letter 
@@
 %SoC.% at the end of the flight.
-}
+}\vspace*{-2ex}
 
@@
                          %
-The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery at future time instants.
-To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies as well as battery evolution.
+The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
+Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies {\color{blue}and }%as well as 
+battery evolution.
 

### 2022-05-21 review/response-letter.tex
fixed some issues w/ performance metric, response letter

@@
 
-Dear Referees, Dr. Kurniawati:
+Dear Referees, Editors:
 
@@
 
-The response letter is split into three sections, the first two for each review and the third for the editor's report.
-The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version.
+The response letter is split into three sections, the first for the associate editor's report and the second and third each for one review.
+The associate editor's and referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version.
 The quotes from the revised version are incorporated here in a box with a light red background and a thick red left border.
@@
 \vspace{5em}
+
+\newpage
+
+{Associate Editor}
+
+\vspace{3em}
+
+{\hspace*{-4.5em}\textbf{[AE]}\vspace*{-1.9em}}
+
+This paper received two quality reviews.
+Both reviewers have a favorable impression of the work with specific suggestions for improvement.
+The authors should take care to address the concerns of the reviewers in a revised version.
+Both reviewers specifically mention a related work that should be cited, as well as specific concerns to improve the clarity of the technical contribution of the work.
+
+{\color{blue}
+
+{\hspace*{-4.5em}{[AE]}\vspace*{-1.9em}}
+
+We thank the editor for handling our manuscript on planning-scheduling for the aerial robotics domain and the summary of the main concerns from the two reviews. 
+We have incorporated all of the points proposed to strengthen and improve our contribution.
+Regarding the related work, we have updated the manuscript to include detailed commentary on how our approach differs.
+
+We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and would like to bring the revision version for your kind consideration.}
 
@@
   Thank you for noticing the comparison was missing in the manuscript.
-We utilize as a performance metric the weighted average configuration of parameters divided by the battery state of charge at the end of the flight, meaning the higher the average value of parameters and the lowest the battery state of charge the better (all the resources are being utilized).
+We utilize as a performance metric the weighted average configuration of parameters divided by the battery state of charge at the end of the flight both expressed in percent, meaning the higher the average value of parameters and the lower the battery state of charge the better (all the resources are being utilized).
+For example, if the parameter is the detection and it varies between 2 and 10 frames per second, 2 corresponds to 0, whereas 10 to 100.
+Similarly, 0 then corresponds to no and 100 to full charge for the battery state of charge.
 We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.
@@
 \begin{formal}\color{black}
-
 The problem %of planning-scheduling 
@@
 {\color{blue}and its} {\color{blue}energy-aware} %other to
-  re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
-  in-flight. %in an energy-aware way. %{\color{blue}, whereas }
-  {\color{blue} 
-  The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
-  the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
+re-plan{\color{blue}ing}~and\\ -schedul{\color{blue}ing~}%the plan 
+in-flight.~The %in an energy-aware way. %{\color{blue}, whereas }
+{\color{blue} 
+re-planning-scheduling improves a performance metric--%, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
+the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
+The objective is~%then
+high~average~parameters configuration and battery usage with successful %area 
+coverage.
 %The performance metric the re-planning-scheduling %in the letter 
@@
 
-\newpage
-
-{Associate Editor}
-
-\vspace{3em}
-
-{\hspace*{-4.5em}\textbf{[AE]}\vspace*{-1.9em}}
-
-This paper received two quality reviews.
-Both reviewers have a favorable impression of the work with specific suggestions for improvement.
-The authors should take care to address the concerns of the reviewers in a revised version.
-Both reviewers specifically mention a related work that should be cited, as well as specific concerns to improve the clarity of the technical contribution of the work.
-
-{\color{blue}
-
-{\hspace*{-4.5em}{[AE]}\vspace*{-1.9em}}
-
-We thank the editor for handling our manuscript on planning-scheduling for the aerial robotics domain and the summary of the main concerns from the two reviews. 
-We have incorporated all of the points proposed to strengthen and improve our contribution, making numerous modifications to the manuscript.
-Regarding the related work, we have updated the manuscript to include detailed commentary on how our approach differs.
-
-We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and are excited to bring the revision version for your kind consideration.
-}
-
 \end{document}

### 2022-05-21 energy-planning.tex
fixed some issues w/ performance metric, response letter

@@
 
+\vspace*{-.7ex}
 \subsection{Energy-aware planning-scheduling problem}
@@
 {\color{blue}and its} {\color{blue}energy-aware} %other to
-re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
-in-flight. %in an energy-aware way. %{\color{blue}, whereas }
+re-plan{\color{blue}ing}~and~-schedul{\color{blue}ing~}%the plan 
+in-flight.~The %in an energy-aware way. %{\color{blue}, whereas }
 {\color{blue} 
-The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
-the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
+re-planning-scheduling improves a performance metric--%, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
+the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
+The objective is~%then
+high~average~parame- ters configuration and battery usage with successful %area 
+coverage.
 %The performance metric the re-planning-scheduling %in the letter 
@@
 %SoC.% at the end of the flight.
-}\vspace*{-2ex}
+}\vspace*{-2.7ex}
 

### 2022-05-21 review/response-letter.tex
proofreading

@@
   the $k$th computation parameter constraint set.
-{\color{blue}Indices $j,k$ serves~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
+{\color{blue}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
   \vspace*{1ex}
@@
   models in Eqs.~({\color{red}2}--{\color{red}3}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
-  and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$}}
+  and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{blue}the} initial time instant $t_0$}}
     {\color{blue}\begin{equation}\tag{8}
@@
 \begin{formal}
-  \color{black} [...] Such use cases arise in precision agriculture~[{\color{green}4}] where {\color{blue}information collection prior to an harvesting operation and} damage prevention during the operation involve aerial robots~[{\color{green}5}],~[{\color{green}6}].
+  \color{black} [...] Such use cases arise in precision agriculture~[{\color{green}4}] where {\color{blue}information collection prior to a harvesting operation and} damage prevention during the operation involve aerial robots~[{\color{green}5}],~[{\color{green}6}].
 

### 2022-05-21 energy-planning.tex
proofreading

@@
 where 
-{\color{blue}information collection prior to an harvesting operation and}
+{\color{blue}information collection prior to a harvesting operation and}
 %harvesting involves ground vehicles~\cite{%qingchun2012study,
@@
 An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}.
-Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
+Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard {\color{blue}computations}~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
 In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{%abramov2012real,
@@
 ~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}.
-Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
+Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency {\color{blue}and} voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
 These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019qos}, and anytime planning~\cite{sudhakar2020balancing}.
@@
 The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
-It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
+It is a common theme {\color{blue}in} wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
 %\begin{ctb}
@@
 Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}.
-{\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
+{\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path{\color{blue}s} and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
 The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware% energy modeling
@@
 In Fig.~\ref{fig:il-abs}, collected energy data ({\color{blue}top-right}) and spectrum analysis ({\color{blue}below}) of a fixed wing %aerial robot
-flying CPP motivates the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
@@
     \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$.
-$\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens change of stages $\Gamma_i$.
+$\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens {\color{blue}the} change of stages $\Gamma_i$.
 Each contains a path function $\varphi_i$ and parameters to alter the path and schedule $c_{i,1},\dots$.}
@@
   the $k$th computation parameter constraint set.
-{\color{blue}Indices $j,k$ serves~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
+{\color{blue}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
 \end{defn}
@@
 The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
-Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies {\color{blue}and }%as well as 
+Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} {\color{blue}thus} provide models for the overall and computations energies {\color{blue}and }%as well as 
 battery evolution.
@@
 when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
-and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
+and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{blue}the} initial time instant $t_0$
   {\color{blue}\begin{equation}
@@
 where $b\,Q_cV$, the maximum instantaneous energy %consumption
-measured in watts, is derived from Eq.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
+measured in watts, is derived from Eq{\color{blue}s}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
 %\end{defn}
@@
 in standard atmospheric conditions. 
-Fig.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Fig{\color{blue}s}.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
 Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.
@@
 
-Fig.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
+Fig{\color{blue}s}.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
 illustrate the same plan $\Gamma$ under different conditions.
@@
 
-Fig.~%\ref{fig:ener}
+Fig{\color{blue}s}.~%\ref{fig:ener}
 {\color{blue}\hyperref[fig:stat]{6b}--\hyperref[fig:dyn]{7c}} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 

### 2022-05-22 review/response-letter.tex
proofreading (2)

@@
 
-Dear Referees, Editors:
+Dear Referees and Editors:
 
@@
 We thank the editor for handling our manuscript on planning-scheduling for the aerial robotics domain and the summary of the main concerns from the two reviews.
-We have incorporated all of the points proposed to strengthen and improve our contribution.
+We have incorporated all of the points and made numerous modifications to improve the readability.
 Regarding the related work, we have updated the manuscript to include detailed commentary on how our approach differs.
 
-We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and would like to bring the revision version for your kind consideration.}
+We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and would like to bring the revised version for your kind consideration.}
 
@@
 We employ MPC for the schedule (computation parameters $c_i^\sigma$) in Line 16 and a heuristics-based greedy approach for the coverage (path parameters $c_i^\rho$) in Lines 24–27.
-A similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).
+%A similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).
 
@@
 
-  We have updated the introduction and the problem formulation in Section II to address the observation, and further added an explanatory text in Section IV.B as well as in the conclusion.
-In the introduction we have stated explicitly that we utilize both the heuristics and optimal control.
+We have updated the introduction and the problem formulation in Section II to address the observation and further added an explanatory text in Section IV.B as well as in the conclusion.
+In the introduction, we have stated explicitly that we utilize both heuristics and optimal control.
 
@@
 
-  We have updated the problem formulation, clearly stating that the objective is to find energy-aware trajectory of parameters rather than optimal.
+  We have updated the problem formulation, clearly stating that the objective is to find an energy-aware trajectory of parameters rather than optimal.
 
@@
   \begin{formal}
-    \color{black} [...] The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized 
+    \color{black} [...] The set of parameters is unaltered through{\color{blue}out} the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized
     in the greedy approach}.
@@
 $A$ is then a skew-symmetric matrix that contains sub-matrices $A_j$ utilized for the periodic behavior with the frequencies $\omega:=2\pi/T$ ($T$ is the period).
-Each frequency is multiplied by $j$ from one up to the order $r$, where $j$ is the index of the sub-matrix, i.e., there are $r$ frequencies modeling the periodicity one the base frequency.
+Each frequency is multiplied by $j$ from one up to the order $r$, where $j$ is the index of the sub-matrix, i.e., there are $r$ frequencies modeling the periodicity and the base frequency.
 
@@
 
-Thank you for underlying the necessity of further explanation for the steps in $\mathcal{K},\mathcal{T}$ in both the points 7 and 8.
-The step for $\mathcal{T}$ is utilized to decide the granularity of re-planning, i.e., how often does the aerial robot finds the configurations of path and computations parameters, whereas the step in $\mathcal{K}$ denotes the integration step for the models in MPC.
+Thank you for underlying the necessity of further explanation for the steps in $\mathcal{K},\mathcal{T}$ in both points 7 and 8.
+The step for $\mathcal{T}$ is utilized to decide the granularity of re-planning, i.e., how often the aerial robot finds the configurations of path and computations parameters, whereas the step in $\mathcal{K}$ denotes the integration step for the models in MPC.
 
@@
 
-Thank you once again for underlying this point. The assumption was not clearly stated in the manusctipt, and we have thus added additional commentary before the equations.
+Thank you once again for underlying this point. The assumption was not clearly stated in the manuscript, and we have thus added additional commentary before the equations.
 
@@
 We have not included it in the introductory material as the work does not account for the energy expenditure of computations, nonetheless, we agree on the necessity to clarify this in the introduction.
-To this end, we have added explanatory text in the introduction that--aside the proposed work--includes the follow-up work by the same set of authors proposed by the first referee.
+To this end, we have added explanatory text in the introduction that--aside from the proposed work--includes the follow-up work by the same set of authors proposed by the first referee.
 
@@
 
-  We have then reorganized the conclusion, underlining the intent to perform physical experiments at future instances.
+  We have then reorganized the conclusion, underlining the intent to perform physical experiments in future instances of our work.
 

### 2022-05-22 energy-planning.tex
proofreading (2)

@@
 completeness %of the cover 
-are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
+are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.
 
@@
 value of the state $\mathbf{q}$ are not known, we use %a technique in the literature named 
-output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.%~\cite{rawlings2017model}.
+output model predictive control (MPC) that derives the configuration for a finite horizon on an estimated state $\hat{\mathbf{q}}$, i.e., $t_f:=t_0+N$ for a given $N\in\mathbb{R}_{>0}$.
+%~\cite{rawlings2017model}.
 {\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
@@
 \end{equation}
-where $Q\in\mathbb{R}^{m\times m},R\in\mathbb{R}^{n\times n}$ are given positive semidefinite matrices.%, resulting in the convexity of the cost $l$~\citep{nocedal2006numerical}.
+where $Q\in\mathbb{R}^{m\times m},R\in\mathbb{R}^{n\times n}$ are given positive semidefinite matrices.
+%, resulting in the convexity of the cost $l$~\citep{nocedal2006numerical}.
 A useful property to guarantee a solution~\citep{beck2014introduction}.
@@
 The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2})
-between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}).
-The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along $\delta_i$ %utilized
+between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}). The set of parameters is unaltered 
+through{\color{blue}out} the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along with $\delta_i$ %utilized 
 in the greedy approach}.
@@
                                              %
-This letter provides a planning-scheduling approach for autonomous aerial robots.% powered by a limited power source, extending past literature.
+This letter provides a planning-scheduling approach for autonomous aerial robots.
+% powered by a limited power source, extending past literature.
 It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings.
@@
 %and distributed planning-scheduling merit additional investigation, as well as 
-The study of the implications of planning-scheduling on other energy-critical mobile robots {\color{blue}merit additional investigation}.
+The study of the implications of planning-scheduling on other energy-critical mobile robots {\color{blue}merits additional investigation}.
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.

### 2022-05-22 review/response-letter.tex
proofreading (3)

@@
 
-We have updated the introduction and the problem formulation in Section II to address the observation and further added an explanatory text in Section IV.B as well as in the conclusion.
+We have updated the introduction and the problem formulation in Section II to address the observation and further added an explanatory text in Section IV-B as well as in the conclusion.
 In the introduction, we have stated explicitly that we utilize both heuristics and optimal control.
@@
 
-  We have then updated Section IV.B.
+  We have then updated Section IV-B.
 
@@
 However, we have not observed a significant energy drain changing these parameters, conversely to the parameter detection rate.
-Thus we utilized merely the computation parameter 'detection rate' in our current experimental setup.
+Thus we utilized merely the computation parameter `detection rate' in our current experimental setup.
 
@@
 
-  \begin{formal}\color{black}
-    [...] The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~[{\color{green}10}] and frequency and voltage of the computing hardware~[{\color{green}7}], [{\color{green}11}], [{\color{green}12}].
-We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
-    {\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.} [...]
+  \begin{formal}{\color{black}
+    [...] The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~[{\color{green}10}] and frequency and voltage of the computing hardware~[{\color{green}7}],
+    {\color{black}[{\color{green}11}], [{\color{green}12}].
+We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.}
+    {\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.} \color{black}[...]}
     \vspace*{1ex}

### 2022-07-11 energy-planning.tex
implemented the comments from the second round of reviews for the camera ready version

@@
 
-\documentclass[letterpaper,10pt,journal,twoside]{IEEEtran} 
-%\IEEEoverridecommandlockouts
+\newcommand{\CLASSINPUTtoptextmargin}{19mm}
+\newcommand{\CLASSINPUTbottomtextmargin}{19mm}
+\newcommand{\CLASSINPUTinnersidemargin}{19mm}
+\newcommand{\CLASSINPUToutersidemargin}{19mm}
+
+\documentclass[letterpaper,10pt,conference,twoside]{IEEEtran}
+\IEEEoverridecommandlockouts
 
@@
 \usepackage{amsmath}
+\makeatletter
+\def\maketag@@@#1{\hbox{\m@th\normalfont\normalsize#1}}
+\makeatother
+
 \usepackage{mathtools}
@@
 
-\title{Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots}
+\title{\vspace{6mm}\bfseries\LARGE Energy-Aware Planning-Scheduling for Autonomous Aerial Robots}
 
@@
   Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
-  \thanks{The work was partly funded by EU grant No. 779882 (TeamPlay). The work for H. G. is supported by the Ramon y Cajal grant No. RYC2020-030090-I.}
-  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
-  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
-  \thanks{$^{\text{1}}$A.
-S.
+  \thanks{The work was partly funded by EU grant \textnumero 779882 (TeamPlay). The work for H.\vspace*{.4ex}G. is supported by the Ramon y Cajal grant \textnumero RYC2020-030090-I.}
+  \thanks{$^{\text{1}}$A.\hspace*{.4ex}S.
 is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS.
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
-  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
-  \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
+  \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
+  \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with the\hspace*{.5ex}SDU\hspace*{.3ex}UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
   University of Southern Denmark.}
-  \thanks{Digital Object Identifier (DOI): see top of this page.}
 }
-
-\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted Month, Year}
-{Seewald \MakeLowercase{\textit{et al.}}: Planning-Scheduling for Aerial Robots} 
-% Use only for final RAL version
 
@@
 
-\vspace*{-5ex}
-
+\vspace*{-.6ex}
 \begin{abstract}
-  In this letter, we present an online planning-scheduling approach for battery-powered autonomous aerial robots.
+  In this paper, we present an online planning-scheduling approach for battery-powered autonomous aerial robots.
 The approach consists of simultaneously planning a coverage path and scheduling onboard computational tasks.
@@
 Our experiments show how an initial flight plan is adjusted online as a function of the available battery, accounting for uncertainty.
-Our approach furthermore remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
+Our approach %furthermore
+  remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
 \end{abstract}
 
-\vspace*{-.5ex}
-\begin{IEEEkeywords}
+%\vspace*{-.5ex}
+%\begin{IEEEkeywords}
   %Aerial Systems: Perception and Autonomy, %Optimization and Optimal Control, 
@@
   %Planning under Uncertainty
-  Motion and Path Planning, 
-  Energy and Environ- ment-Aware Automation
-\end{IEEEkeywords}
+%  Motion and Path Planning, 
+%  Energy and Environ- ment-Aware Automation
+%\end{IEEEkeywords}
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\vspace*{-2.6ex}
+%\IEEEpeerreviewmaketitle
+
+\vspace*{-.6ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
                         %
-\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They comprise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
+Use cases involving aerial robots span broadly. They comprise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
 One such use case is coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}, which consists of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey} while running assigned computational tasks.
@@
 where 
-{\color{blue}information collection prior to a harvesting operation and}
+{\color{black}information collection prior to a harvesting operation and}
 %harvesting involves ground vehicles~\cite{%qingchun2012study,
@@
 We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
-{\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
-Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).
+{\color{black} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
+Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., %unexpected
+battery defects~(\ref{sth:iii}).
 
@@
   \centering
-  \vspace*{-9ex}
+  \vspace*{-5ex}
  %\begin{tikzpicture}
  %  \node[inner sep=0pt] () at (0,0)
-        {\color{blue}\scriptsize \input{\figpath/il_abs_new.tikz}}
+        {\color{black}\scriptsize \input{\figpath/il_abs_new.tikz}}
  %  \node[inner sep=0pt] () at (-2,-5.67)
@@
  %\end{tikzpicture}
+  \vspace*{.6ex}
   \caption{%Illustrative example of planning-scheduling. 
   %The figure shows 
-  An initial plan~(in~\ref{sth:i}) {\color{blue}is} re-planned online, changing the %resolution, 
+  An initial plan~(in~\ref{sth:i}) {\color{black}is} re-planned online, changing the %resolution, 
   detection rate or other computational aspects~(in~\ref{sth:ii}) and %changing 
   the number of fly-bys or other motion aspects~(in~\ref{sth:iii}). 
-  {\color{blue}Top-right} %shows 
-  {\color{blue}are} the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
+  {\color{black}Top-right} %shows 
+  {\color{black}are} the energy data of a %physical 
+  fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{black}; %below is 
+  }%. Bottom-right shows 
   the spectrum analysis, %of the %energy 
@@
   \label{fig:il-abs}
-  \vspace*{-4ex}
+  \vspace*{-3.8ex}
 \end{figure}
@@
 An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}.
-Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard {\color{blue}computations}~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
+Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard {\color{black}computations}~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}.
 In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{%abramov2012real,
@@
 ~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}.
-Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency {\color{blue}and} voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
+Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency {\color{black}and} voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms.
 These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019qos}, and anytime planning~\cite{sudhakar2020balancing}.
 These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery.
-{\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution~\cite{difranco2015energy}, and deals with aspects such as the quality of the cover~\cite{difranco2016coverage}, but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.}
+{\color{black}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution~\cite{difranco2015energy}, and deals with aspects such as the quality of the cover~\cite{difranco2016coverage}, but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.}
 Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints.
-Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial
+Numerical simulations and experimental data of %both
+static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial 
 robot %s
@@
 Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering.
-Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}.
+Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical,zamanakos2020energy}.
 %Indeed
-{\color{blue}T}here are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
-The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
-It is a common theme {\color{blue}in} wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
+{\color{black}T}here are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa.
+The {\color{black}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{black}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps).
+It is %a
+common %theme 
+{\color{black}in} %wider 
+planning-scheduling literature, focusing on %energy-
+efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
 %\begin{ctb}
@@
 
-To guarantee energy awareness, our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
+To guarantee energy awareness, our approach uses optimal control {\color{black} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.).
 Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}.
-{\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path{\color{blue}s} and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
+{\color{black}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path{\color{black}s} and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models.
 The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware% energy modeling
@@
 The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules.
-In Fig.~\ref{fig:il-abs}, collected energy data ({\color{blue}top-right}) and spectrum analysis ({\color{blue}below}) of a fixed wing %aerial robot
-flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+In Fig.~\ref{fig:il-abs}, collected energy data ({\color{black}top-right}) and spectrum analysis ({\color{black}below}) of a fixed wing %aerial robot
+flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Sec.~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
 The %remaining sections of the letter are 
-{\color{blue}remainder is} then organized as follows.
-Section~\ref{sec:prob} provides basic constructs%, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as
-{ \color{blue}and} %the problem formulation.
-Section~\ref{sec:algo} describes %in detail 
-the methodology of planning-scheduling. Section~\ref{sec:experimental} presents the results, %and showcases the performances, 
-and Section~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
-
-\vspace*{-1ex}
+{\color{black}remainder is} then organized as follows.
+Sec.~\ref{sec:prob} provides basic constructs%, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as
+{ \color{black}and} %the problem formulation.
+Sec.~\ref{sec:algo} describes %in detail 
+the methodology of planning-scheduling. Sec.~\ref{sec:experimental} presents the results, %and showcases the performances, 
+and Sec.~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
                                %
-%Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries. 
+%Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries. 
 %For CPP and, e.g., pattern detections in precision agriculture, 
-{\color{blue}W}e assume %that %aerial 
-{\color{blue}the }robot contains a \emph{plan} composed of \emph{stages}. At each, %stage, %the aerial robot 
-{\color{blue}it }travels a path and runs a schedule on the computing hardware. Both are %to be 
-altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computation}-specific \emph{parameters}.%with information about the path and the schedule.
+{\color{black}W}e assume %that %aerial 
+{\color{black}the }robot contains a \emph{plan} composed of \emph{stages}. At each, %stage, %the aerial robot 
+{\color{black}it }travels a path and runs a schedule on the computing hardware. Both are %to be 
+altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computation}-specific \emph{parameters}.%with information about the path and the schedule.
 
@@
   \footnotesize
-  \begin{minipage}[l]{0.38\columnwidth}
+  \begin{minipage}[t]{0.65\columnwidth}
+    \centering
+    \input{\figpath/new/traj1.tikz}
+  \end{minipage}
+  \begin{minipage}[t]{0.012\columnwidth}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.328\columnwidth}
+    \vspace*{-28.2ex}
     \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$.
-$\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens {\color{blue}the} change of stages $\Gamma_i$.
+$\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens {\color{black}the} change of stages $\Gamma_i$.
 Each contains a path function $\varphi_i$ and parameters to alter the path and schedule $c_{i,1},\dots$.}
     \label{fig:traj1}
-  \end{minipage}\hfill
-  \begin{minipage}[c]{0.6\columnwidth}
-    \centering
+  \end{minipage}
   \vspace*{-4ex}
-    \input{\figpath/new/traj1.tikz}
-  \end{minipage}
-  \vspace*{-4.5ex}
 \end{figure}
 
-\vspace*{-2ex}
 \subsection{Preliminaries}
@@
   \begin{equation*}\begin{split}
-    \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
+    \Gamma_i:=\{{\color{black}\varphi_i(\mathbf{p}%(t)
     ,c_i^\rho)},c_i^\sigma\mid
@@
   \end{split}\end{equation*}
-  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~\ref{sec:experimental})}.
+  where $c_i^\rho${\color{black}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{black}$:=\{c_{i,\rho+1},c_{i,\rho+2},$ $\dots,c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{black}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Sec.~\ref{sec:experimental})}.
 $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$
@@
   the $k$th computation parameter constraint set.
-{\color{blue}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
+{\color{black}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
 \end{defn}
@@
 Bold letters indicate vectors. 
-The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{blue}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of %a parameter
+The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, {\color{black}$[x]_{>0}$ strictly positive naturals, i.e., $\{1,2,\dots,x\}$,} $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of %a parameter
 $x$, i.e.,
@@
 
-The function $\varphi_i$ is a \emph{path function}{\color{blue}--a }%specifying the path. These are 
+The function $\varphi_i$ is a \emph{path function}{\color{black}--a }%specifying the path. These are 
 stage-dependent mathematical function %s 
@@
   $\varphi_i:\mathbb{R}^2\times\mathbb{R}^\rho\rightarrow\mathbb{R},\,\forall i\in\{1,2,\dots\}
-  $ are \emph{path functions}, forming the path. They are a function of {\color{blue}$\mathbf{p}%(t)
+  $ are \emph{path functions}, forming the path. They are a function of {\color{black}$\mathbf{p}%(t)
   $} and path parameters $c_i^\rho%(t)
@@
   The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
-  \begin{equation*}{\color{blue}s(\Gamma_i,\mathbf{p}%(t)
+  \begin{equation*}{\color{black}s(\Gamma_i,\mathbf{p}%(t)
     )}:=\begin{cases}
-    \Gamma_{i+j} & {\color{blue}\text{if }\norm{\mathbf{p}%(t)
+    \Gamma_{i+j} & {\color{black}\text{if }\norm{\mathbf{p}%(t)
     -\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},}\\
@@
 
-A convenient way of defining $\Gamma$ is specifying a set of stages, a shift, and a final point. The set is termed \emph{primitive stages} and iterated with the shift up to reaching the final point.
+A convenient way of defining $\Gamma$ is specifying a set of stages, a shift, and a final point. The set is termed \emph{primitive stages} and iterated with the shift up to %reaching 
+the final point.
 
@@
 \noindent In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
-\begin{equation}\label{eq:primitive}\begin{split}
-  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
-\end{split}\end{equation}
+\begin{equation}\small\label{eq:primitive}
+  \varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
+\end{equation}
 holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$.
@@
 
-\begin{figure}[h!]
-  \footnotesize
-  \begin{minipage}[l]{0.75\columnwidth}
-    \vspace*{-2.7ex}
-    \begin{tikzpicture}[shorten >=.3pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-.8ex}\footnotesize{$\Gamma_0$}\hspace*{-.5ex}]
-      \scriptsize
-      \node[state,initial] (q_i) {$\Gamma_1$}; 
-      \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
-      \node        [right=of q_2] (q_dots0) {$\cdots$};
-      \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
-      \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
-      \path[->]
-      (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
-      (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
-      (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
-      (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
-      (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
-      (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
-      (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
-      (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
-      (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
-      (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
-      (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
-      ; %end path 
-      %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
-      %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
-    \end{tikzpicture}
-  \end{minipage}\hfill
-  \begin{minipage}[c]{0.18\columnwidth}
-    \centering
-    \caption{Plan $\Gamma$ with $n$ primitive stages in Def.~\ref{def:primitive}.}
-    \label{fig:state-machine-loop}
-  \end{minipage}
-  \vspace*{-4ex}
-\end{figure}
+%\begin{figure}[h!]
+%  \footnotesize
+%  \begin{minipage}[l]{0.75\columnwidth}
+%    \vspace*{-2.7ex}
+%    \begin{tikzpicture}[shorten >=.3pt,node distance=12.5ex,on grid,auto,initial text=\hspace*{-.8ex}\footnotesize{$\Gamma_0$}\hspace*{-.5ex}]
+%      \scriptsize
+%      \node[state,initial] (q_i) {$\Gamma_1$}; 
+%      \node[state] (q_2) [right=of q_i] {$\Gamma_2$}; 
+%      \node        [right=of q_2] (q_dots0) {$\cdots$};
+%      \node[state] (q_0) [right=of q_dots0] {$\Gamma_n$};
+%      \node[state,accepting] (q_f) [right=of q_0] {$\Gamma_f$};
+%      \path[->]
+%      (q_i) edge node {$\mathbf{p}_{\Gamma_{1}}$} (q_2)
+%      (q_2) edge node {$\mathbf{p}_{\Gamma_{2}}$} (q_dots0)
+%      (q_dots0) edge node{$\mathbf{p}_{\Gamma_{n-1}}$} (q_0)
+%      (q_0) edge [bend right=60] node [above] {$\mathbf{p}_{\Gamma_n}$} (q_i)
+%      (q_i) edge [bend left=-60] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+%      (q_2) edge [bend left=-40] node [above] {$\mathbf{p}_{\Gamma_l}$} (q_f)
+%      (q_0) edge node {$\mathbf{p}_{\Gamma_{l}}$} (q_f)    
+%      (q_i) edge [loop above] node {$\mathbf{p}(t_1)$} (q_i)
+%      (q_2) edge [loop above] node {$\mathbf{p}(t_2)$} (q_2)
+%      (q_0) edge [loop above] node {$\mathbf{p}(t_3)$} (q_0)
+%      (q_f) edge [loop above] node {$\mathbf{p}(t_4)$} (q_f)
+%      ; %end path 
+%      %\draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=47pt},yshift=0pt]
+%      %(q_i.south west) -- (q_f.south west) node [black,midway,yshift=-19ex]{$\Gamma$};
+%    \end{tikzpicture}
+%  \end{minipage}\hfill
+%  \begin{minipage}[c]{0.18\columnwidth}
+%    \centering
+%    \caption{Plan $\Gamma$ with $n$ primitive stages in Def.~\ref{def:primitive}.}
+%    \label{fig:state-machine-loop}
+%  \end{minipage}
+%  \vspace*{-4ex}
+%\end{figure}
 %\begin{figure}[h!]
@@
 
-Fig.~\ref{fig:state-machine-loop} illustrates the concept. %s in Definition~\ref{def:primitive}. 
-A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (%containing 
-{\color{blue}with }primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
+%Fig.~\ref{fig:state-machine-loop} illustrates the concept. %s in Definition~\ref{def:primitive}. 
+%A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (%containing 
+%{\color{black}with }primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$.
 $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$.
@@
 The problem %of planning-scheduling 
-is {\color{blue}split into }%composed of 
+is {\color{black}split into }%composed of 
 %two%sub-problems.
-{\color{blue}the derivation }%. One is 
+{\color{black}the derivation }%. One is 
 %to form a %static 
-{\color{blue} of} a {\color{blue}coverage} plan %that visits every point in space 
-{\color{blue}and its} {\color{blue}energy-aware} %other to
-re-plan{\color{blue}ing}~and~-schedul{\color{blue}ing~}%the plan 
-in-flight.~The %in an energy-aware way. %{\color{blue}, whereas }
-{\color{blue} 
-re-planning-scheduling improves a performance metric--%, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
-the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
+{\color{black} of} a {\color{black}coverage} plan %that visits every point in space 
+{\color{black}and its} {\color{black}energy-aware} %other to
+re-plan{\color{black}ing}~and~-schedul{\color{black}ing~}%the plan 
+in-flight.~The %in an energy-aware way. %{\color{black}, whereas }
+{\color{black} 
+re-planning-scheduling increases a unitless performance metric--%, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
+the weighted average of parameters divided by the remaining battery state of charge (SoC) at the end of flight, both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
 The objective is~%then
-high~average~parame- ters configuration and battery usage with successful %area 
+high~average~parameters configuration and battery usage with successful %area 
 coverage.
@@
 %SoC.% at the end of the flight.
-}\vspace*{-2.7ex}
+}
 
@@
   Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
-  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{blue}energy-aware} trajectory of parameters $c_i$ in time{\color{blue}, optimizing battery SoC}.
+  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the {\color{black}energy-aware} trajectory of parameters $c_i$ in time{\color{black}.}%, optimizing battery SoC}.
 \end{pb}
@@
 The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
-Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} {\color{blue}thus} provide models for the overall and computations energies {\color{blue}and }%as well as 
+Sec.~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} {\color{black}thus} provide models for the overall and computations energies {\color{black}and }%as well as 
 battery evolution.
@@
 For this latter purpose, we use the dynamics %another model
-\begin{subequations}\label{eq:state-perf}
+\begin{subequations}\label{eq:state-perf}\vspace*{-3ex}
   \begin{align}
@@
 Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible %, as we discuss briefly in
-{\color{blue}(see }Section~\ref{sec:conclusion}{\color{blue})}.
-The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
+{\color{black}(see }Sec.~\ref{sec:conclusion}{\color{black})}.
+The dynamics in Eq.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Sec.~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
 conditions.
 
-{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
-models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
+{\color{black}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
+models in Eq.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
 %\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
 when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
-and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{blue}the} initial time instant $t_0$
-  {\color{blue}\begin{equation}
+and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{black}the} initial time instant $t_0$
+  {\color{black}\begin{equation}
   {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
@@
 i.e., $h,y$ are %both 
-harmonic signals with the same frequencies{\color{blue}. For further details see the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.
+harmonic signals with the same frequencies{\color{black}. For further details see the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.
 
@@
 where $\mathrm{diag}(x)$ is a diagonal matrix with items of a set $x$ on the diagonal and zeros elsewhere.
-$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors{\color{blue},} %that
-transform{\color{blue}ing} parameters %domain 
+$\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors{\color{black},} %that
+transform{\color{black}ing} parameters %domain 
 (see Definition~\ref{def:stage}) to time and power domains.
@@
 %For ease of notation, 
-{\color{blue}W}e assume that the coverage time evolves linearly{ \color{blue}and that the }path parameters{ \color{blue}contribute to it equally.} $c_i^\rho$ can be {\color{blue}then} transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
+{\color{black}W}e assume that the coverage time evolves linearly{ \color{black}and that the }path parameters{ \color{black}contribute to it equally.} $c_i^\rho$ can be {\color{black}then} transformed into a time measure with scaling factors\begin{subequations}%\small
+  \label{eq:scale-traj}\begin{align}
   \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
@@
 Similarly to Eq.~(\ref{eq:scale-traj}), computation parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with %scaling factors
-\begin{subequations}\label{eq:scale-comp}\begin{align}
+\begin{subequations}%\small
+  \label{eq:scale-comp}\begin{align}
   \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
@@
 \end{align}\end{subequations}
-$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Section~\ref{sec:mod-com} and quantifies the power of the computing hardware.
-
+$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Sec.~\ref{sec:mod-com} and quantifies the power of the computing hardware.
+
+\vspace*{.4ex}
 \subsection{Energy model for the computations}
@@
 
-The model compromises an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed %~\cite{powprofiler} 
+The model compromises a %n automatic 
+modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed %~\cite{powprofiler} 
 under the open-source MIT license.
@@
 
-We assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
+We assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a %specific 
+component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.
 
@@
 
-Here, the notation $\mathcal{T}$ encloses all the time intervals from initial $t_0$ to final $t_f$, i.e., $\mathcal{T}:=[t_0,t_f]$.
+The notation $\mathcal{T}$ encloses all the time intervals from initial $t_0$ to final $t_f$, i.e., $\mathcal{T}:=[t_0,t_f]$.
 
@@
 The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules.
-Additionally, the \powprof{} tool supports the battery SoC detailed in Section~\ref{sec:mod-bat}.
+Additionally, the \powprof{} tool supports the battery SoC detailed in Sec.~\ref{sec:mod-bat}.
 The function $g$ in Definition~\ref{def:pred} is contained in the %computations scaling
 factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
-\begin{equation}\label{eq:piece-wise-reg}\begin{split}
+\begin{equation}%\small
+  \label{eq:piece-wise-reg}\begin{split}
   g(c_i^\sigma)=(&\gamma(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
 \end{split}\end{equation}
-where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals.
-{\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~(\ref{eq:piece-wise-reg})}.
-
-\vspace*{-1.4ex}
+where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ %are 
+the corresponding two time intervals. {\color{black}M}easuring device in $\gamma$ and $g$ is {\color{black}not %explicitly 
+stated in Eq.~(\ref{eq:piece-wise-reg})}.
+
 \subsection{Battery model}
@@
 The battery model predicts the battery SoC in the function of a given load at future time 
-instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{blue}and} accuracy %, and ease of implementation 
+instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{black}and} accuracy %, and ease of implementation 
 ranging from accurate but costly physical models~\cite{%moura2017battery,
@@
 hinz2019comparison,mousavi2014various} %that have
-{\color{blue}with} compelling trade-offs in terms of the latter two. 
+{\color{black}with} compelling trade-offs in terms of the latter two. 
 We model a Li-ion battery %of an aerial robot 
@@
 expression $R_rI^2-$ $VI+V_sI_l=0$. Solving the expression utilizing the negative solution (when $I_l$ is zero, $I$ should also be zero) %leads to% 
-results in 
+results in \vspace*{-1ex}
 \begin{equation}\label{eq:batdyn2}
@@
 \begin{equation}\label{eq:output-const}
-  {\small\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},} 
+  {%\small
+  \mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},} 
 \end{equation}
@@
 where $b\,Q_cV$, the maximum instantaneous energy %consumption
-measured in watts, is derived from Eq{\color{blue}s}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
+measured in watts, is derived from Eq{\color{black}s}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}), i.e., the computation parameters in Algorithm~\ref{alg2} and Eq.~(\ref{eq:ocp-output-mpc}) later in Sec.~\ref{sec:repla-algo} will have an energy constraint.
 %\end{defn}
@@
 
-\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \footnotesize
-  \begin{minipage}[l]{0.21\columnwidth}
-    \caption{Alteration of the path parameter $c_{i,1}$, the radius of the circle (i.e., the alteration of the plan in Fig.~\ref{fig:il-abs}).
-    }
+  \begin{minipage}[c]{0.23\columnwidth}
+    \vspace*{-6.6ex}
+    \caption{Change of the path parameter $c_{i,1}$, the radius of the circle (i.e., the alteration of the plan in Fig.~\ref{fig:il-abs}).}
     \label{fig:tee1}
   \end{minipage}\hfill
-  \begin{minipage}[c]{0.77\columnwidth}
+  \begin{minipage}[c]{0.05\columnwidth}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.71\columnwidth}
     \centering
-    \vspace*{-4.5ex}
     \input{\figpath/new/traj2.tikz}
   \end{minipage}
-  \vspace*{-4.5ex}
+  \vspace*{-4.2ex}
 \end{figure}
 
-This section solves the problem described in Section~\ref{sec:pbfor}. It provides a plan %$\Gamma$ 
+This section solves the problem %described 
+in Sec.~\ref{sec:pbfor}. It provides a plan %$\Gamma$ 
 and re-plans-schedules such plan energy-wise. %respectively
-%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
+%in Sec.~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.
 
@@
 
-There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). Those that ensure %the 
+There are various approaches in the literature to solve CPP problems (e.g., Sec.~\ref{sec:pbfor}). Those that ensure %the 
 completeness %of the cover 
@@
 It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP %at the very core of this work
-{\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
-{\color{blue} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}
-The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
+{\color{black} by dynamically altering the distance between the survey lines with the path parameters}. 
+{\color{black} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}
+The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths% (see Definition~\ref{def:primitive})
+: two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
 
@@
 Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ %per each 
-{\color{blue}at }discretized time step{\color{blue}s}, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
+{\color{black}at }discretized time step{\color{black}s}, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.
 The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected.
@@
 %Nonetheless, a
-{\color{blue}C}omplex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and %subsequently 
+{\color{black}C}omplex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells %to be easily covered 
+and %subsequently 
 covering each cell~\cite{choset2001coverage}.% with the novel motion.
@@
     \FORALL{$t\in\mathcal{T}$}
-      \color{blue}\STATE \textbf{if} $\mathbf{p}%(t)
+      \color{black}\STATE \textbf{if} $\mathbf{p}%(t)
       =\mathbf{p}_{\Gamma_l}${ in Definition~\ref{def:trigs}} \textbf{then return }$\Gamma$\vspace*{.3ex}\color{black}
@@
       %\vspace*{.8ex}
-      \color{blue}\IF{$\mathbf{p}%(t)
+      \color{black}\IF{$\mathbf{p}%(t)
       =\mathbf{p}_{\Gamma_i}$}\color{black}
@@
           \STATE $\varphi_{|\Gamma|+4}\gets$ circle in Eq.\hspace*{.7ex}(\ref{eq:second-circ-gene}) 
-          whose right most point lays\vspace*{.3ex} \hspace*{1em}on $\mathbf{p}_{|\Gamma|+3}$\vspace*{.3ex}\label{alg2:circ2}
+          whose right most point\vspace*{.3ex} \hspace*{1em}lays on $\mathbf{p}_{|\Gamma|+3}$\vspace*{.3ex}\label{alg2:circ2}
 
@@
 is expressed as a function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages.
-$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}).
+$r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Sec.~\ref{pb:cov-pb}).
 The center also changes
@@
   \begin{minipage}[l]{0.26\columnwidth}
-    \caption{Zamboni-li- ke motion: $\overline{\Gamma}$ with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) {\color{blue}via} $r_2$.% in Eq.~(\ref{eq:r2}).
+    \caption{Zamboni-li- ke motion: $\overline{\Gamma}$ with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) {\color{black}via} $r_2$.% in Eq.~(\ref{eq:r2}).
     }
@@
 Past literature on planning-scheduling often relies on %optimal control and 
-optimization {\color{blue} as well as heuristics-based} approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
-We similarly derive an optimal control problem {\color{blue}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+optimization {\color{black} as well as heuristics-based} approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
+We similarly derive an optimal control problem {\color{black}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
 Since the final time %instant
@@
 %~\cite{rawlings2017model}.
-{\color{blue} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
+{\color{black} We utilize MPC to derive the trajectory of the computation parameters and the greedy approach with heuristics remaining coverage time for the path parameters.}
 
@@
       \makeatother
-      \color{blue}\STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i^\sigma(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}\label{alg:mpc}
+      \color{black}\STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i^\sigma(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$ \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.4ex}N),t+\hspace*{-.4ex}N)}+\hspace*{-.5ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${\hspace*{.4ex}in\hspace*{.4ex}Eq.\hspace*{.4ex}(\ref{eq:ocp-output-mpc}) \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}\label{alg:mpc}
 
@@
       %\STATE $t_r\gets(t_s/\overline{t})(\overline{t}-t)$\vspace*{.3ex}
-      \color{blue}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}
+      \color{black}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}
       \IF{$t_r>t_b$}
-        \color{blue}\STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_r\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
+        \color{black}\STATE $c_i^{\rho}(t)\gets${ find }$c_i^{\rho}${ with }$t_r\in[0,t_b]${, otherwise take }$\underline{c}_i^\rho$\vspace*{.3ex}\label{alg:traj2}
       \color{black}\ENDIF
       \vspace*{.8ex}
-      \color{black}\STATE $\hat{\mathbf{q}}(t+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(t)$\vspace*{.3ex}\label{alg:klm1}
-      \color{black}\STATE $\hat{y}(t+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(t+h)$\vspace*{.3ex}\label{alg:klm2}
+      \color{black}\STATE $\hat{\mathbf{q}}(t+h)\gets${ estimate }$\mathbf{q}${ in Eq.~(\ref{eq:state-perf-q}) with energy sensor }$\Upsilon(t)$\vspace*{-1.8ex}\label{alg:klm1}
+      \color{black}\STATE $\hat{y}(t+h)\gets${ derive }$y${ from Eq.~(\ref{eq:state-perf-y}) with est. state }$\hat{\mathbf{q}}(t+h)$%\vspace*{.3ex}
+      \label{alg:klm2}
     \ENDFOR
@@
 
-An optimal control problem (OCP) that selects the highest configuration of {\color{blue} $c_i^\rho$} and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
-\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
+An optimal control problem (OCP) that selects %the %highest configuration of 
+{\color{black} $c_i^\rho$} %and respects the constraints
+\begin{subequations}\small\label{eq:ocp-output-mpc}\begin{align}
   \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
   \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
+  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t)\text{, i.e., constraint in Eq.~(\ref{eq:output-const})},\label{eq:batt-const-mpc}\\
   c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
-  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
   \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
@@
 \end{align}\end{subequations}
-where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial cost function with the quadratic expression
+where $\mathbf{q}(t)$ and $c_i(t)$ are the state and parameters trajectories and $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial cost function with the quadratic expression
 \vspace*{-.5ex}
@@
 
-Eq.~(\ref{eq:dyn-evol}) is the model in Eq.~(\ref{eq:state-perf}). {\color{blue}It} requires a value of the period $T$, which is %simply 
-the time needed to fly the four primitive paths in the Zamboni-like motion{\color{blue}, or }%, i.e., 
-the time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.
+Eq.~(\ref{eq:dyn-evol}) is the model in Eq.~(\ref{eq:state-perf}). {\color{black}It} requires a value of the period $T$, which is %simply 
+the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., the time %elapsed
+between two positive evaluations of the condition on Line~\ref{alg2:cond}.
 
@@
 .
-Its solution leads to both trajectories of {\color{blue} computation} parameters and states for future $N$ instants.
-Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{blue}:
+Its solution leads to both trajectories of {\color{black} computation} parameters and states for future $N$ instants.
+Here, the sets $\mathcal{K},\mathcal{T}$ have possibly different steps $h$ (not to be confused with the altitude){\color{black}:
 the set $\mathcal{K}$ is used for the numerical simulation, whereas $\mathcal{T}$ is for re-planning, meaning that $h$ tunes the precision and the frequency of re-planning for $\mathcal{K}$ and $\mathcal{T}$ respectively.}
-The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc}) and Eq.~(\ref{eq:batdyn}).%, with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}.
+The functions $l_d,b_d$ are the discretized versions of Eq.~(\ref{eq:insta-cost-mpc})~and~(\ref{eq:batdyn}).%, with, e.g., Runge-Kutta or Euler methods%~\cite{iserles2009first}.
 
 Lines~\ref{alg:bat1}--\ref{alg:bat2} estimate the time needed to completely drain the battery, exploiting the SoC already predicted previously on Line~\ref{alg:mpc}.
-The {\color{blue}path parameters and thus the} coverage is then re{\color{blue}-}planned accordingly on Lines~\ref{alg:traj1}--\ref{alg:traj2} using {\color{blue} the heuristics with the} %Lem.~\ref{lem:new} and
-scaling factors from Eq.~(\ref{eq:scale-traj}). 
-{\color{blue} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Section~\ref{sec:experimental})}.
+The {\color{black}path parameters and thus the} coverage is then re{\color{black}-}planned %accordingly
+on Lines~\ref{alg:traj1}--\ref{alg:traj2} using {\color{black} the heuristics with the} %Lem.~\ref{lem:new} and 
+scaling factors from Eq.~(\ref{eq:scale-traj}) with $c_{i}^{\rho}(t_0)$ given. 
+{\color{black} Concretely, these lines implement the greedy approach by decreasing the path parameters of a given value $\delta_i$ or similarly increasing the parameters when $t_r\leq t_b$ within the bounds (this latter analogous case is not shown explicitly in Algorithm~\ref{alg2} but implemented in Sec.~\ref{sec:experimental})}.
 Lines~\ref{alg:klm1}--\ref{alg:klm2} estimate the %energy model's 
 state with %current 
-energy sensor reading $\Upsilon$, {\color{blue}using}, e.g., %linear 
+energy sensor reading $\Upsilon$, {\color{black}using}, e.g., %linear 
 Kalman filter%~\cite{kalman1960new}
@@
 \begin{figure*}
-  \vspace*{-4ex}
   \centering
   \footnotesize
+  \begin{minipage}[t]{0.63\columnwidth}
     \input{\figpath/results/new_physics2/new_trajs-ener_I-II.tikz}
-  \captionsetup{labelfont={color=blue}}
-  \vspace*{-.6ex}
-  \caption{\color{blue}CPP with Zamboni-like motion using two boundary configurations.
-In \hyperref[fig:stat]{a} are the trajectories of the coverage--the highest in \hyperref[fig:trajs-I-static]{I} and the lowest in \hyperref[fig:trajs-II-static]{II}.
-In \hyperref[fig:stat]{b} are the energy and the period evolutions for both \hyperref[fig:trajs-I-static]{I} and \hyperref[fig:trajs-II-static]{II} with different atmospheric conditions.
-In \hyperref[fig:stat]{c} are the states of the energy model for \hyperref[fig:trajs-I-static]{I}.}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.36\columnwidth}
+    \vspace*{-53.8ex}
+    \centering
+    \caption{\color{black}Results for path, energy, and energy models of two boundary configurations, the lowest \hyperref[fig:trajs-I-static]{I} and the highest \hyperref[fig:trajs-II-static]{II}, without energy-aware planning-scheduling.
+The use case is that of coverage path planning with Zamboni-like motion and ground hazards detection scheduling.
+In \hyperref[fig:stat]{a} are the trajectories of the coverage.
+In \hyperref[fig:stat]{b} are the energy and the period evolutions for both \hyperref[fig:trajs-I-static]{I} and \hyperref[fig:trajs-II-static]{II} with different atmospheric conditions (i.e., different wind speed and direction) and initial guesses, and in \hyperref[fig:stat]{c} the states of the energy model for \hyperref[fig:trajs-I-static]{I}.}
     \label{fig:stat}
-  \vspace*{-3ex}
+  \end{minipage}
+  \vspace*{-2ex}
 \end{figure*}
@@
   \footnotesize
+  \begin{minipage}[t]{0.63\columnwidth}
     \input{\figpath/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
-  \captionsetup{labelfont={color=blue}}
-  \vspace*{-.6ex}
-  \caption{\color{blue}
-  Planning-scheduling of CPP and ground patterns detections% with PedNet CNN
-  , utilizing the lowest configuration \hyperref[fig:trajs-I-static]{I} as a starting point in \hyperref[fig:trajs-dyn-i]{i} and the highest \hyperref[fig:trajs-II-static]{II} in \hyperref[fig:trajs-dyn-ii]{ii} while varying atmospheric (same as Fig.~\ref{fig:stat}) and battery conditions.
-In \hyperref[fig:dyn]{a} are the re-planned trajectories, in \hyperref[fig:dyn]{b} the parameters, and in \hyperref[fig:dyn]{c} the energy w.r.t.
-the battery.
-  }
+  %\captionsetup{labelfont={color=blue}}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.36\columnwidth}
+    \vspace*{-53.1ex}
+    \centering
+    \caption{Energy-aware plan- ning-scheduling using the lowest configuration \hyperref[fig:trajs-I-static]{I} as a starting point in \hyperref[fig:trajs-dyn-i]{i} and the highest \hyperref[fig:trajs-II-static]{II} in \hyperref[fig:trajs-dyn-ii]{ii} while varying atmospheric (same as Fig.~\ref{fig:stat}) and battery conditions.
+In \hyperref[fig:dyn]{a} are the re-planned trajectories, showing the re-planning in the proximity of simulated battery drops.
+In \hyperref[fig:dyn]{b} are the parameters evolutions, and in \hyperref[fig:dyn]{c} the energy w.r.t.
+the battery.}
     \label{fig:dyn}
-  \vspace*{-4ex}
+  \end{minipage}
+  \vspace*{-3ex}
 \end{figure*}
 
-\vspace*{-1.4ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 .
-The computing hardware carries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}).
+The computing hardware carries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Sec.~\ref{sec:mod-com}).
 The scheduler, implemented using the Robot Operating System (ROS) middleware%~\cite{quigley2009ros}
 , varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames per second (FPS).
-The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS.
-The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2})
+The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, %also
+implemented using ROS. The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2}) 
 between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}). The set of parameters is unaltered 
-through{\color{blue}out} the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{blue}, along with $\delta_i$ %utilized 
+through{\color{black}out} the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i${\color{black}, along with $\delta_i$ %utilized 
 in the greedy approach}.
@@
 in standard atmospheric conditions. 
-Fig{\color{blue}s}.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
-Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.
+Fig{\color{black}s}.~\ref{fig:stat}{\color{black}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling. %as described in this letter.
 
@@
 
-Fig{\color{blue}s}.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
+Fig{\color{black}s}.~{\color{black}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
 illustrate the same plan $\Gamma$ under different conditions.
@@
 Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).
-{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenarios.
+{\color{black} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenarios.
 Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
 
-Fig{\color{blue}s}.~%\ref{fig:ener}
-{\color{blue}\hyperref[fig:stat]{6b}--\hyperref[fig:dyn]{7c}} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
+Fig{\color{black}s}.~%\ref{fig:ener}
+{\color{black}\hyperref[fig:stat]{6b}--\hyperref[fig:dyn]{7c}} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 
 illustrates first the power ($\Upsilon$ on Line~\ref{alg:klm1} in Algorithm~\ref{alg}), and then the energy model ($y$ on Line~\ref{alg:evol}).
-{\color{blue} Fig.~\hyperref[fig:stat]{6b}} %further 
+{\color{black} Fig.~\hyperref[fig:stat]{6b}} %further 
 details then the energy model's estimate (%see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}
-{\color{blue}${\hat{y}}$}) on an initial slice%of the model (${\hat{y}}$)
+{\color{black}${\hat{y}}$}) on an initial slice%of the model (${\hat{y}}$)
 , power ($\Upsilon$), and period ($T$).
-{\color{blue} Fig.~\hyperref[fig:stat]{6c}} illustrates the evolutions of the state $\mathbf{q}$ in time {\color{blue}for \hyperref[fig:ener:static-I]{I}}, concluding that approximately two periods suffice for a consistent %state
+{\color{black} Fig.~\hyperref[fig:stat]{6c}} illustrates the evolutions of the state $\mathbf{q}$ in time {\color{black}for \hyperref[fig:ener:static-I]{I}}, concluding that approximately two periods suffice for a consistent %state
 estimate.
 
-Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery ({\color{blue}see} green line {\color{blue}in Fig.~\hyperref[fig:dyn]{7c}}, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
-Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ {\color{blue}(see Fig.~\hyperref[fig:dyn]{7b})} when the battery is discharging, respecting the output constraint% (Eq.~(\ref{eq:output-const}))
+Flight~\hyperref[fig:ener-dyn-i]{i} simulates a battery ({\color{black}see} green line {\color{black}in Fig.~\hyperref[fig:dyn]{7c}}, the battery behavior $b_0$) drop at approximately one minute and a half and four minutes and a half.
+Planner-scheduler optimizes the path in the proximity of the drops to ensure that the flight is completed, whereas it maximizes the parameter $c_{i,2}$ {\color{black}(see Fig.~\hyperref[fig:dyn]{7b})} when the battery is discharging, respecting the output constraint% (Eq.~(\ref{eq:output-const}))
 .
 Flight~\hyperref[fig:ener-dyn-ii]{ii} simulates the opposite scenario: the lowest configuration of parameters and no battery defects.
-The path parameter increases as soon as the algorithm has estimated enough data %(two periods $T$)
+The path parameter increases as soon as the algorithm has estimated enough data (two periods $T$)
 and the computation parameter decreases matching the battery discharge rate.
-{\color{blue}
-Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
+
+{\color{black}
+The performance metric is $\Sigma_{t\in\mathcal{T}}{\small (w_1c_{i,1}(t)+w_2c_{i,2}(t))}/$ $\small {\small |\mathcal{T}|\text{SoC}(t_f)}$. If the initial battery SoC %at $t_0$ 
+is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
 Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
@@
 For both cases, scaling factors are derived empirically %, 
-{\color{blue}similarly to $\delta_i$ set to two hundred fifty}, 
-the horizon $N$ is set to six seconds {\color{blue} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
+{\color{black}similarly to $\delta_i$ set to two hundred fifty}, 
+the horizon $N$ is set to six seconds {\color{black} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
 stastny2018nonlinear%,chao2011collision
 }, order $r$ is three% (see Fig.~\ref{fig:il-abs})
-, and %the matrices 
-$Q,R,Q_f$ are chosen such that the cost is %merely 
-squared control. {\color{blue} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
+, and the matrices $Q,R,Q_f$ are chosen such that the cost is merely 
+squared control. {\color{black} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
 %\subsection{Algorithm evaluation}
@@
 %The figure
-%{\color{blue} Fig.~\hyperref[fig:stat]{6c}} %further 
+%{\color{black} Fig.~\hyperref[fig:stat]{6c}} %further 
 %details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$).
 % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate.
-%The {\color{blue} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state
+%The {\color{black} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state
 %estimate.
@@
 
-{\color{blue}
+{\color{black}
 Additional results are reported~\cite{seewaldphdthesis} utilizing simulation capabilities of the Paparazzi flight controller.
@@
 
-\vspace*{-1.5ex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
                                              %
-This letter provides a planning-scheduling approach for autonomous aerial robots.
+This %letter 
+paper provides a planning-scheduling approach for autonomous aerial robots.
 % powered by a limited power source, extending past literature.
@@
 Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool.
-The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC {\color{blue} and a greedy approach}.
+The approach compromises two algorithms: one derives a static coverage plan, %whereas 
+the other re-plans-schedules the plan on a finite horizon via MPC {\color{black} and a greedy approach}.
 It evolves the state of the energy model while optimizing battery usage and remedying possible defects.
@@
 
-{\color{blue}To enable physical experiments}, we are currently extending the results to a standard flight controller.
+{\color{black}To enable physical experiments}, we are currently extending the results to a standard flight controller.
 %The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections),
 %and distributed planning-scheduling merit additional investigation, as well as 
-The study of the implications of planning-scheduling on other energy-critical mobile robots {\color{blue}merits additional investigation}.
+The study of the implications of planning-scheduling on other energy-critical mobile robots {\color{black}merits additional investigation}.
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-Further directions include {\color{blue}the use of a purely optimization-based technique, e.g., MPC derives both the path and computation parameters trajectories and} the study of different energy models.% Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+Further directions include {\color{black}the use of a purely optimization-based technique %, e.g., MPC derives both the path and computation parameters trajectories and}
+and the study of different energy models.% Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
 
@@
 
-%A change in computations parameters in Lem.~\ref{lem:new} results in different schedules on the computing hardware, which we assumed in Section~\ref{sec:intro} affects the instantaneous energy, i.e., computations are energy expensive computational tasks.
+%A change in computations parameters in Lem.~\ref{lem:new} results in different schedules on the computing hardware, which we assumed in Sec.~\ref{sec:intro} affects the instantaneous energy, i.e., computations are energy expensive computational tasks.
 

### 2022-07-11 energy-planning.tex
proofreading

@@
   Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
-  \thanks{The work was partly funded by EU grant \textnumero 779882 (TeamPlay). The work for H.\vspace*{.4ex}G. is supported by the Ramon y Cajal grant \textnumero RYC2020-030090-I.}
+  \thanks{The work was partly funded by EU grant \textnumero 779882 (TeamPlay). The work for H.\hspace*{.4ex}G. is supported by the Ramon y Cajal grant \textnumero RYC2020-030090-I.}
   \thanks{$^{\text{1}}$A.\hspace*{.4ex}S.
-is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS.
+is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the\hspace*{.6ex}SDU\hspace*{.4ex}UAS.
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
@@
   the number of fly-bys or other motion aspects~(in~\ref{sth:iii}). 
-  {\color{black}Top-right} %shows 
+  {\color{black}On the right} %shows 
   {\color{black}are} the energy data of a %physical 
-  fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{black}; %below is 
+  fixed-wing aerial robot flying a static coverage plan similar to the one illustrated\hspace*{.5ex}here\hspace*{.5ex}{\color{black}and %; %below is 
   }%. Bottom-right shows 
@@
 The collected energy data and corresponding spectrum analysis in Fig.~\ref{fig:il-abs} show the energy of a static coverage plan.
-It is relative to one flight of a series of flights for CPP exhibiting periodic behavior in a precision agriculture use case~\cite{seewald2020mechanical}.
-%$\Gamma$ with four primitive path functions iterated with a shift.
+It is relative to one flight of a series of flights for CPP %exhibiting periodic behavior
+in a precision agriculture use case~\cite{seewald2020mechanical}. %$\Gamma$ with four primitive path functions iterated with a shift. 
 Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibits periodic behavior with a constant set of frequencies, independent of the shift.
@@
 \end{equation}
-where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
+where $I(y(t))\hspace*{-.5ex}\in\hspace*{-.5ex}\mathbb{R}$ is the internal current measured~in~am- peres, $y(t)\hspace*{-.5ex}\in\hspace*{-.5ex}\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\hspace*{-.5ex}\in\hspace*{-.5ex}\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour.
 $k_b$ is a battery coefficient added to~\cite{hasan2018exogenous%,zhang2018online
@@
 where $b\,Q_cV$, the maximum instantaneous energy %consumption
-measured in watts, is derived from Eq{\color{black}s}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}), i.e., the computation parameters in Algorithm~\ref{alg2} and Eq.~(\ref{eq:ocp-output-mpc}) later in Sec.~\ref{sec:repla-algo} will have an energy constraint.
+measured in watts, is derived from Eq{\color{black}}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}), i.e., the computation parameters in Algorithm~\ref{alg2} and Eq.~(\ref{eq:ocp-output-mpc}) later in Sec.~\ref{sec:repla-algo} will have an energy constraint.
 %\end{defn}
@@
         \IF{$i\notin[n]_{>0}$}\label{alg2:cond}
-          \STATE $i\gets 1$\vspace*{.3ex}
+          \STATE $i\gets 1$\vspace*{0ex}
           \STATE $\varphi_{|\Gamma|+1}\gets$ line in Definition~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
@@
   \begin{minipage}[l]{0.26\columnwidth}
-    \caption{Zamboni-li- ke motion: $\overline{\Gamma}$ with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned ($\underline{\Gamma}$) {\color{black}via} $r_2$.% in Eq.~(\ref{eq:r2}).
+    \caption{Zamboni-li- ke motion: $\overline{\Gamma}$ with four primitive paths (Lines~\ref{alg2:circ1}--\ref{alg2:trig4} in Algorithm~\ref{alg2}) can be re-planned up to $\underline{\Gamma}$ {\color{black}with the radius} $r_2$.% in Eq.~(\ref{eq:r2}).
     }
@@
 optimization {\color{black} as well as heuristics-based} approaches~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}.
-We similarly derive an optimal control problem {\color{black}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0,t_f]$ (see Definition~\ref{def:meas}).
+We similarly derive an optimal control problem {\color{black}and a greedy approach} returning the trajectory of parameters $c_i(\mathcal{T})$ with $\mathcal{T}:=[t_0+h,t_f]$ (see Definition~\ref{def:meas}).
 Since the final time %instant
@@
       %\STATE $t_r\gets(t_s/\overline{t})(\overline{t}-t)$\vspace*{.3ex}
-      \color{black}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}
+      \color{black}\STATE $t_r\gets (\mathrm{diag}(\nu_i^\rho)\vspace*{.3ex}c_i^\rho(t-h)+\tau_i^\rho)[\overbrace{\begin{matrix}1&1&\cdots&1\end{matrix}}^{\rho}]-t$\vspace*{.3ex}\label{alg:traj1}
       \IF{$t_r>t_b$}
@@
 An optimal control problem (OCP) that selects %the %highest configuration of 
-{\color{black} $c_i^\rho$} %and respects the constraints
+{\color{black} $c_i^\sigma$} %and respects the constraints
 \begin{subequations}\small\label{eq:ocp-output-mpc}\begin{align}
@@
 The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, %also
-implemented using ROS. The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2}) 
+implemented in ROS. The planner varies the path parameter $c_{i,1}$ %in %Eq.~(\ref{eq:r2}) 
 between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}). The set of parameters is unaltered 
@@
 Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
-Further directions include {\color{black}the use of a purely optimization-based technique %, e.g., MPC derives both the path and computation parameters trajectories and}
-and the study of different energy models.% Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
+Further directions include {\color{black}the use of a purely optimization-based technique, %, e.g., MPC derives both the path and computation parameters trajectories and}
+the study of different energy models, and multi-agent planning-scheduling.% Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
 

### 2022-07-12 energy-planning.tex
fixed the affiliation

@@
   \thanks{$^{\text{1}}$A.\hspace*{.4ex}S.
-is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the\hspace*{.6ex}SDU\hspace*{.4ex}UAS.
+is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with SDU UAS.
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
   \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
-  \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with the\hspace*{.5ex}SDU\hspace*{.3ex}UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
+  \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
   University of Southern Denmark.}
@@
 {\color{black}
-The performance metric is $\Sigma_{t\in\mathcal{T}}{\small (w_1c_{i,1}(t)+w_2c_{i,2}(t))}/$ $\small {\small |\mathcal{T}|\text{SoC}(t_f)}$. If the initial battery SoC %at $t_0$ 
+The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1c_{i,1}(t)+w_2c_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$. If the initial battery SoC %at $t_0$ 
 is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).

### 2022-07-13 energy-planning.tex
fixed the affiliation, minor fix to refs

@@
   \thanks{$^{\text{1}}$A.\hspace*{.4ex}S.
-is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with SDU UAS.
+is with the Department of Mechanical Engineering and Materials Science, Yale University, CT, USA, but the work was performed while affiliated with SDU UAS.
 Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
-  \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
+  \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Engineering, Automation, and Robotics and with CITIC, University of Granada, Spain;} 
   \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 

### 2022-07-21 energy-planning.tex
proofreading, fixed readme

@@
 {\color{black} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
-Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., %unexpected
+Figure~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., %unexpected
 battery defects~(\ref{sth:iii}).
@@
 In Fig.~\ref{fig:il-abs}, collected energy data ({\color{black}top-right}) and spectrum analysis ({\color{black}below}) of a fixed wing %aerial robot
-flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Sec.~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
+flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.
 
@@
 Sec.~\ref{sec:algo} describes %in detail 
-the methodology of planning-scheduling. Sec.~\ref{sec:experimental} presents the results, %and showcases the performances, 
+the methodology of planning-scheduling. Sec.~\ref{sec:experimental} presents the results %and showcases the performances, 
 and Sec.~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.
@@
 re-planning-scheduling increases a unitless performance metric--%, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
-the weighted average of parameters divided by the remaining battery state of charge (SoC) at the end of flight, both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
+the weighted average of parameters divided by the remaining battery state of charge (SoC) at the end of the flight, both in percent (e.g., $\underline{c}_{i,j}$, $\overline{c}_{i,j}$ correspond to 0 and 100).
 The objective is~%then
@@
 {\color{black}(see }Sec.~\ref{sec:conclusion}{\color{black})}.
-The dynamics in Eq.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Sec.~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
+The dynamics in Eq.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allow us to use state estimation techniques, such as the Kalman filter in Sec.~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric
 conditions.
@@
 and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{black}the} initial time instant $t_0$
-  {\color{black}\begin{equation}
-  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
-  \end{equation}}
+\begin{equation}
+  \mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',
+\end{equation}
 %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
@@
 where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ %are 
-the corresponding two time intervals. {\color{black}M}easuring device in $\gamma$ and $g$ is {\color{black}not %explicitly 
+the corresponding two time intervals. {\color{black}The m}easuring device in $\gamma$ and $g$ is {\color{black}not %explicitly 
 stated in Eq.~(\ref{eq:piece-wise-reg})}.
@@
 
+\vspace*{.4ex}
 An optimal control problem (OCP) that selects %the %highest configuration of 
@@
 in standard atmospheric conditions. 
-Fig{\color{black}s}.~\ref{fig:stat}{\color{black}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
+Fig{\color{black}}.~\ref{fig:stat}{\color{black}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
 Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling. %as described in this letter.
@@
 
-Fig{\color{black}s}.~{\color{black}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
+Fig{\color{black}}.~{\color{black}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
 illustrate the same plan $\Gamma$ under different conditions.
@@
 
-Fig{\color{black}s}.~%\ref{fig:ener}
+Fig{\color{black}}.~%\ref{fig:ener}
 {\color{black}\hyperref[fig:stat]{6b}--\hyperref[fig:dyn]{7c}} %~\hyperref[fig:ener:static-I]{6.I}--\hyperref[fig:ener:static-II]{6.II} 

### 2022-07-21 energy-planning.tex
proofreading (2)

@@
 
-The battery model predicts the battery SoC in the function of a given load at future time 
+The battery model predicts the battery SoC as a function of a given load at future time 
 instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{black}and} accuracy %, and ease of implementation 
@@
 {\color{black}
-The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1c_{i,1}(t)+w_2c_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$. If the initial battery SoC %at $t_0$ 
-is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
+The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1\tilde{c}_{i,1}(t)+w_2\tilde{c}_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$ with {\small $\tilde{c}_{i,j}\hspace*{-.4ex}:=\hspace*{-.4ex}(c_{i,j}\hspace*{-.3ex}-\hspace*{-.3ex}\underline{c}_{i,j})/(\overline{c}_{i,j}\hspace*{-.3ex}-\hspace*{-.3ex}\underline{c}_{i,j})$}.
+If the initial battery SoC %at $t_0$
+is seventy percent and both the parameters are weighted equally, i.e., {\small $w_1\hspace*{-.3ex}=\hspace*{-.3ex}w_2\hspace*{-.3ex}=\hspace*{-.3ex}$} one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
 Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx.
